### 2016-09-01 Hhh/Hhh.tex
Adding template that doesn't really look very nice yet, and adding a few hhh bits

\chapter{\texorpdfstring{Search for \hhhtautaubb}{Search for H -> hh -> tautaubb}}
\label{sec:hhh}

In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of $\tau$ leptons is discussed. The results of this search are model-independent
upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$. In addition 
the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), these interpretations are made
in combination with the results of a search for \azhlltautau. This search will be summarised in this
chapter, but will not constitute the main focus.

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 (CITATION) has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. In some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by stringent existing limits. In regions where
the decay \hhh is enhanced, the \azh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htautau final state.

BLAH BLAH BLAH

\section{Datasets and Monte Carlo samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different MC event generators. The \texttt{MadGraph}
CITATION matrix element generator was used to generate samples of \wjets, \zellell, \ttbar and $ZZ$,$ZW$ and $WW$
events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
were used for the \wjets and \zellell backgrounds. This increases the number of background events
in signal regions with multiple jets. The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} CITATION generator. Samples of $gg\rightarrow$\hhhtautaubb
were generated in steps of 10 GeV between $m_H = 260 - 350$~GeV using \texttt{PYTHIA 6} CITATION. In all of the samples
\texttt{TAUOLA} CITATION is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all MC samples to model additional
interactions. 
\vfill

\section{Event selection and categorisation}
\label{sec:hhh_selection}

\section{Data to Monte Carlo correction factors}
\label{sec:hhh_datamc}

\section{Discriminating variable}
\label{sec:hhh_discr}

\section{Background estimation}
\label{sec:hhh_backgrounds}

\section{Systematic uncertainties}
\label{sec:hhh_uncs}

\section{\texorpdfstring{Overview of \azhlltautau}{Overview of A->Zh->lltautau}}
\label{sec:hhh_azh}

\section{Results}
\label{sec:hhh_results}

\subsection{Signal extraction}
\label{sec:hhh_results_extraction}

\subsection{Model-independent results}
\label{sec:hhh_results_modelindep}

\subsection{Model-dependent results}
\label{sec:hhh_results_modeldep}

### 2016-09-05 Hhh/Hhh.tex
Changing to hepthesis template

@@
-\chapter{\texorpdfstring{Search for \hhhtautaubb}{Search for H -> hh -> tautaubb}}
+\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
 \label{sec:hhh}
@@
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of $\tau$ leptons is discussed. The results of this search are model-independent
+a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. The results of this search are model-independent
 upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$. In addition 
 the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), these interpretations are made
-in combination with the results of a search for \azhlltautau. This search will be summarised in this
+in combination with the results of a search for \AtoZhtolltautau. This search will be summarised in this
 chapter, but will not constitute the main focus.
@@
 of \tanb, probing a region of phase space not yet excluded by stringent existing limits. In regions where
-the decay \hhh is enhanced, the \azh decay also has a large branching ratio, indicating the usefulness
+the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
 of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
-of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htautau final state.
+of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.
 
@@
 Signal and background events were generated using several different MC event generators. The \texttt{MadGraph}
-CITATION matrix element generator was used to generate samples of \wjets, \zellell, \ttbar and $ZZ$,$ZW$ and $WW$
+CITATION matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
 events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
-were used for the \wjets and \zellell backgrounds. This increases the number of background events
+were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
 in signal regions with multiple jets. The samples binned in jet multiplicity are combined with the
@@
 
-Single top samples were produced with the \texttt{POWHEG} CITATION generator. Samples of $gg\rightarrow$\hhhtautaubb
+Single top samples were produced with the \texttt{POWHEG} CITATION generator. Samples of $gg\rightarrow$\Htohhtobbtautau
 were generated in steps of 10 GeV between $m_H = 260 - 350$~GeV using \texttt{PYTHIA 6} CITATION. In all of the samples
@@
 
-\section{\texorpdfstring{Overview of \azhlltautau}{Overview of A->Zh->lltautau}}
+\section{\texorpdfstring{Overview of \AtoZhtolltautau}{Overview of A->Zh->lltautau}}
 \label{sec:hhh_azh}

### 2016-09-05 backmatter.tex
Changing to hepthesis template

%% You're recommended to use the eprint-aware biblio styles which
%% can be obtained from e.g. www.arxiv.org. The file mythesis.bib
%% is derived from the source using the SPIRES Bibtex service.
%\bibliographystyle{h-physrev}
%\bibliography{mythesis}

%% I prefer to put these tables here rather than making the
%% front matter seemingly interminable. No-one cares, anyway!
\listoffigures
\listoftables

%% If you have time and interest to generate a (decent) index,
%% then you've clearly spent more time on the write-up than the 
%% research ;-)
%\printindex

### 2016-09-05 frontmatter.tex
Changing to hepthesis template

%% Title
\titlepage[Imperial College London]{%
  A dissertation submitted to Imperial College London\\ for the degree of Doctor of Philosophy}

%% Abstract
%\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
%\end{abstract}

%% Declaration
%\begin{declaration}
%  \vspace*{1cm}
%  \begin{flushright}
%  \end{flushright}
%\end{declaration}

%% Acknowledgements
%\begin{acknowledgements}
%\end{acknowledgements}

%% Preface
%\begin{preface}
%\end{preface}

%% ToC
\tableofcontents

%% Strictly optional!
%% I don't want a page number on the following blank page either.
\thispagestyle{empty}

### 2016-10-05 Hhh/Hhh.tex
Adding some things for H->hh/A->Zh

@@
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. The results of this search are model-independent
-upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$. In addition 
-the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), these interpretations are made
-in combination with the results of a search for \AtoZhtolltautau. This search will be summarised in this
-chapter, but will not constitute the main focus.
+a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. This \Pgt-pair final states studied in this analysis
+are the \etau, \mutau and \tautau channels. The results of this search are model-independent
+upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, which use
+combine all three channels. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
+be covered. In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
+these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
+This search will be summarised in this chapter, but will not constitute the main focus.
+Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.
 
@@
 
-BLAH BLAH BLAH
-
 \section{Datasets and Monte Carlo samples}
@@
 Signal and background events were generated using several different MC event generators. The \texttt{MadGraph}
-CITATION matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
+\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
 events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
@@
 
-Single top samples were produced with the \texttt{POWHEG} CITATION generator. Samples of $gg\rightarrow$\Htohhtobbtautau
-were generated in steps of 10 GeV between $m_H = 260 - 350$~GeV using \texttt{PYTHIA 6} CITATION. In all of the samples
-\texttt{TAUOLA} CITATION is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6}.
+Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
+were generated in steps of 10 GeV between $m_H = 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
+\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
 Minimum bias events generated using \texttt{PYTHIA 6} are added to all MC samples to model additional
 interactions.
-\vfill
 
@@
 \label{sec:hhh_selection}
+A more detailed description of the physics objects used for this analysis is given in chapter FIXME:write object reco section
 
@@
 \label{sec:hhh_azh}
+In this section a summary of the \AtoZhtolltautau analysis, which is combined with the 
+analysis described so far for the purposes of model interpretations, is given.
+
+The search for \AtoZhtolltautau also uses the full dataset collected by the CMS experiment during
+the 2012 $p-p$ running period of the LHC. In this search the \mumu and \ee final states of the \PZ boson
+and the \emu, \etau, \mutau and \tautau channels of the \htotautau decay, leading to a total of
+eight final states.
+
+First the \PZ candidate is chosen as a pair of isolated electrons or muons, with opposite charge, and 
+invariant mass of the pair between 60-120 GeV. In case there is more than one possible pair, the 
+pair with invariant mass closest to the \PZ mass is chosen. The \htotautau decay is chosen by selecting
+an oppositely charged pair of isolated leptons in the four channels mentioned earlier. To ensure no overlap
+between different final states is possible, events with additional electrons or muons satisfying the
+$p_{\text{T}}$ and $\eta$ requirements are discarded.
+
+To reject some of the backgrounds from misidentified leptons and \ZZ production, a requirement is made
+on the scalar sum of the visible transverse momenta of the two $\tau$ candidates from the \htotautau decay.
+This selection changes by final state and has been chosen to optimise the analysis sensitivity to an 
+\AtoZh signal with $m_A = 220 - 350 $ GeV. Furthermore \ttbar events are discarded by rejecting
+events with at least one b-tagged jet.
+
+Remaining backgrounds from \ZZ, triboson and \ttbar\PZ production are estimated using
+Monte Carlo samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
+and \WZ+jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
+events, with at least one misidentified lepton, are estimated from control regions in data.
+
+For signal extraction, the mass of the A boson $m_A$, reconstructed by combining the
+4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate,as obtained by using the 
+\texttt{SVFit} algorithm.
+
+More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
 

### 2016-10-05 Hhh/HhhAZhThesisResources/draw2HDMXSecBR.py

@@ -1,0 +1,267 @@
+#!/usr/bin/env python
+import ROOT
+from array import array
+import CombineHarvester.CombineTools.plotting as plot
+import numpy as np
+
+def set_plot_style():
+  NRGBs = 5;
+  NCont = 255;
+  stops = {0.00,0.34,0.61,0.84,1.00}
+  red = {0.00,0.00,0.87,1.00,0.51}
+  green = {0.00,0.81,1.00,0.20,0.00} 
+  blue = {0.51,1.00,0.12,0.00,0.00}
+  ROOT.TColor.CreateGradientColorTable(NRGBs,np.array(stops),np.array(red),np.array(green),np.array(blue),NCont)
+  ROOT.gStyle.SetNumberContours(NCont)
+
+def DrawAxisHists(pads, axis_hists, def_pad=None):
+    for i, pad in enumerate(pads):
+        pad.cd()
+        axis_hists[i].Draw('AXIS')
+        axis_hists[i].Draw('AXIGSAME')
+    if def_pad is not None:
+        def_pad.cd()
+
+
+
+
+#plot.ModTDRStyle(r=0.17, l=0.12)
+#ROOT.gStyle.SetNdivisions(510, 'XYZ')
+set_plot_style()
+#plot.SetBirdPalette()
+
+ROOT.gStyle.SetCanvasBorderMode(0)
+ROOT.gStyle.SetCanvasColor(ROOT.kWhite)
+ROOT.gStyle.SetCanvasDefH(600)  # Height of canvas
+ROOT.gStyle.SetCanvasDefW(600)  # Width of canvas
+ROOT.gStyle.SetCanvasDefX(0)    # POsition on screen
+ROOT.gStyle.SetCanvasDefY(0)
+
+ROOT.gStyle.SetPadBorderMode(0)
+# ROOT.gStyle.SetPadBorderSize(Width_t size = 1)
+ROOT.gStyle.SetPadColor(ROOT.kWhite)
+ROOT.gStyle.SetPadGridX(False)
+ROOT.gStyle.SetPadGridY(False)
+ROOT.gStyle.SetGridColor(0)
+ROOT.gStyle.SetGridStyle(3)
+ROOT.gStyle.SetGridWidth(1)
[…]

### 2016-10-10 Hhh/Hhh.tex
Updating Hhh section

@@
 
-The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 (CITATION) has opened up
+The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
 new possibilities for probing the Higgs sector beyond the Standard Model. In some MSSM scenarios, and some more
@@
 Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
-were generated in steps of 10 GeV between $m_H = 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
+were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
 \texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
@@
 \label{sec:hhh_selection}
-A more detailed description of the physics objects used for this analysis is given in chapter FIXME:write object reco section
+A more detailed description of the physics objects used for this analysis is given in chapter FIXME:write object reco section, 
+in this section only an overview of the event selection is presented.
+
+\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu-tau channel}}
+\label{sec:hhh_selection_mutau}
+Events in the \mutau channel are first selected by requiring a muon and a 
+hadronic tau. The first step of this selection is a trigger which requires only a muon
+at L1. At the level of the HLT a hadronic tau is also required. This is reconstructed
+with a simpler version of the PF algorithm, and loose isolation requirements are 
+applied. In addition, loose ID and isolation requirements are applied to the muon at 
+this stage.
+
+In the offline event selection, an oppositely charged \mutau pair is required, 
+separated by $\Delta R > 0.5$.
+The muon is required to have a \pT of at 
+least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
+primary vertex. This means the impact parameters $d_{xy}$ and $d_{z}$ must be smaller
+than 0.045 and 0.2 cm respectively. Tight muon identification
+criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
+in section OBJECTS, are applied. The hadronic tau must have a \pT of at least
+20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
+the decay mode finding identification
+from the HPS algorithm, as described in section OBJECTS. Additionally
+the raw combined isolation, described in the same section, is required to be
+at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
+reduce the contribution of \Zmm background events, the hadronic tau is 
+also required to pass the tight working point of the anti-$\Pgm$ discriminator
+and the loose working point of the cut--based anti-$\Pe$ discriminator, both
+described in section OBJECTS.
+
+After this selection there is still a chance more than one possible 
+\mutau pair exists
+in the event. If this is the case, the combination with largest 
+\pT$^{\Pgm}$ + \pT$^{\Pgt_{h}}$ is chosen. In order to reduce \Zmm 
+backgrounds further, for cases where the reconstructed hadronic tau originates
+from a misidentified jet, the event is rejected if an opposite--charge pair 
+of lower \pT (at least 15 GeV) muons, passing looser ID and isolation requirements
+than the signal muon, can be formed. Additional vetos, requiring exactly one muon and 
+exactly zero electrons to pass \pT $>10$ GeV and tight ID and isolation requirements, 
+are applied to reduce the \WZ background.
+
+In addition to the requirements on the di--tau pair, at least 2 jets with \pT$ >20$ GeV are 
+required. No b--tagging requirements are applied at this stage, this will be discussed 
+in more detail in section \ref{sec:hhh_selection_categories}.
+
+\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e-tau channel}}
+\label{sec:hhh_selection_etau}
+Events in the \etau channel are selected by requiring an electron and a hadronic tau.
+As for the \mutau channel the first step of this selection is the trigger, which
+requires an electron at L1, and both an electron and a hadronic tau at HLT. The hadronic
+tau is reconstructed in a similar way to the \mutau channel, and loose ID and isolation requirements
+are also applied to the electron.
+
+Offline, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
+The electron should have a \pT of at least 24 GeV, $|\eta| < 2.1$, and should
+satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
+working point of the electron MVA ID discriminator described in section OBJECTS, and the
+relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
+hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
+where the loose working point is required, and the anti--$\Pe$ discriminator, where the medium
+working point of the MVA discriminator is required.
+
+If there is more than one possible \etau pair, the pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
+is taken. Similar additional vetos as in the \mutau channel are applied.
+the event is rejected if an opposite--charge pair of \pT $> 15$ GeV electrons, passing looser ID and
+isolation requirements than the signal electron requirements can be formed. To reduce the \WZ
+background events that have more than one electron or at least one muon passing \pT $>10$ GeV and tight ID and isolation
+requirements are rejected.
+
+In addition to the requirements on the di--tau pair, at least 2 jets with \pT $>20$ GeV are 
+required.
+
+\subsection{Categorisation}
+\label{sec:hhh_selection_categorisation}
+In both channels an selection on the transverse mass \mT between the electron/muon
+and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
+
+\begin{equation}\label{eqn:hhh_selection_mt}
+m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
+\end{equation}
+
+Where \pT is the transverse moment of the electron or muon, and $\Delta\phi$ the angle
+between the light lepton and the missing transverse energy.
+In both channels this quantity is required to be smaller than 30 GeV. In events
+where the missing energy and the light lepton are oriented back--to--back, \mT is
+large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
+events, as the W is very heavy, the lepton and neutrino are more likely to emitted back--to--back,
+therefore \mT will be large. For \Ztautau and \htautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
+the neutrinos are more likely to travel in the same direction as the visible decay products of 
+the tau, due to the smaller mass of the \Pgt compared with the \PW. Therefore requiring the
+transverse mass to be less than 30 GeV reduces the \Wjets background.
+%In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
+%background events. Because the missing energy can now originate from multiple
+%heavy objects (two tops) the missing transverse energy alignment is randomised. In some
+%cases the lepton and missing transverse energy can be very much like the W decay
+%topology, whereas in other cases \mT will be lower
+
+After applying the \mT selection, events are divided into three categories to maximise
+sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
+(at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
+The 2jet-0tag category does not collect much of the signal and is dominated by 
+backgrounds, the 2jet-2tag category is most sensitive to signal. 
+In signal events, the di--tau pair and di--jet pair 
+are the decay products of an 125 Gev Higgs boson, therefore their invariant
+masses should be close to 125 GeV. To reduce background contributions
+from events where the di--tau or di--jet mass is not compatible with
+125 GeV, requirements are made on the di--jet invariant mass and the di--tau
+invariant mass as reconstructed using the \texttt{SVFit} algorithm (ADD A SECTION ON THIS).
+By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
+large number of background events can be rejected, while retaining
+most of the signal. This is illustrated in figure SOMETHING.
 
@@
 between different final states is possible, events with additional electrons or muons satisfying the
-$p_{\text{T}}$ and $\eta$ requirements are discarded.
+\pT and $\eta$ requirements are discarded.
 
@@
 This selection changes by final state and has been chosen to optimise the analysis sensitivity to an 
-\AtoZh signal with $m_A = 220 - 350 $ GeV. Furthermore \ttbar events are discarded by rejecting
+\AtoZh signal with \mA $= 220 - 350 $ GeV. Furthermore \ttbar events are discarded by rejecting
 events with at least one b-tagged jet.
@@
 
-For signal extraction, the mass of the A boson $m_A$, reconstructed by combining the
+For signal extraction, the mass of the A boson \mA, reconstructed by combining the
 4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate,as obtained by using the 
-\texttt{SVFit} algorithm.
+\texttt{SVFit} algorithm. The expected and observed 95\% confidence level upper limits, for
+all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
+\caption{The 95\% confidence level expected (dashed) and observed (solid)
+upper limits on the $\sigma \times BR$ for the \AtoZhtolltautau process.
+The green and yellow bands indicate the $\pm 1 \sigma $ and $2\sigma$
+expectations \cite{CMS-HIG-14-034}.}
+\label{fig:AZhUpperLimits}
+\end{center}
+\end{figure}
 
@@
 \label{sec:hhh_results_modeldep}
+The results of the analysis are interpreted in two scenarios, the low \tanb MSSM
+scenario, and a type II two--Higgs doublet model (2HDM). 2HDM's are more general
+than the MSSM, are not mativated by supersymmetry, and there are several different types. 
+Of these different classes, type II 2HDM's are most studied
+as the couplings of the MSSM form a subset of the couplings in type II 2HDMs.
+
+\subsubsection{Interpretation in a type II 2HDM}
+\label{sec:hhh_results_modeldep_2HDM}
+A 2HDM of type II has more free parameters than a specified MSSM scenario: the physical masses of the Higgs bosons (\mh, \mH,
+\mA, \mHplus), the ratio of the vacuum expectation values of the two Higgs doublets (\tanb),
+the CP-even Higgs mixing angle ($\alpha$) and $m_{12}^{2} = m_{\PHiggsps}^{2}[\tan{\beta}/(1+\tan{\beta}^2)]$.
+To leave two free parameters, it is enough to fix the masses of the physical Higgs bosons. For this
+interpretation the assumption that \mA = \mH = \mHplus = $300$~GeV, and \mh = $125$~GeV, is made.
+
+The couplings of the Higgs bosons to quarks and leptons, and of heavy Higgs bosons to other
+particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.
+
+\begin{table}[htdp]
+\begin{center}
+\caption{Couplings in the type II 2HDM}
+\begin{tabular}{@{}ll@{}}
+%\toprule
+\textbf{Decay} & \textbf{Coupling}\\
+\midrule
+$\PHiggslight \rightarrow$ up--type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
+$\PHiggslight \rightarrow$ down--type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
+$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
+ & mixing angles, quartic couplings \\
+$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
+%\bottomrule
+\end{tabular}
+\label{tab:hhh_2HDM_couplings}
+\end{center}
+\end{table}
+
+FIXME: ALIGNMENT LIMIT
+
+The interpretations are made in the \cosba--\tanb plane. Figures \ref{fig:Hhh2HDMOverlaid}
+and \ref{fig:AZh2HDMOverlaid} show the observed and expected exclusion at 95\% confidence level for the \Htohh
+and \AtoZh analyses respectively, overlaid on the production cross--section times branching ratio.
+The exclusion contours have some interesting features, most of which can be explained by the couplings
+from table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
+of all particles are exactly standard model--like. This is reflected in the \Htohh and \AtoZh branching ratios, 
+which both vanish as \cosba approaches 0. This leads to the corridor of non--exclusion down the 
+centre of figures \ref{fig:Hhh2HDMOverlaid} and \ref{fig:AZh2HDMOverlaid}. Additionally,
+as the couplings of \PHiggslight to pairs of b--quarks and $\Pgt$ leptons are porportional 
+to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
+and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non--exclusion
+at \cosba $ > 0$ and low \tanb in the \AtoZh figure. A similar corridor is starting
+to become visible in the $\sigma \times BR$ structure of the \Htohh interpretation, but
+the analysis is not yet sensitive enough to actually see a full--blown corridor in this
+region.
+Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
+interpretation, these are a result of the complex \Htohh branching ratio (ADD FIGURE).
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhh2HDM.pdf}
+\caption{Search for \Htohhtobbtautau interpreted in a type II 
+2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
+and observed (solid line) exclusion contours at 95\% confidence level are overlaid
+on the cross--section of $gg\rightarrow \PHiggs$ production
+times the branching ratio of \PHiggs into \hhtobbtautau.
+Regions of the \cosba-\tanb plane where the cross--section times branching
+ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
+(see figure FIXME:add plot) are excluded.}
+\label{fig:Hhh2HDMOverlaid}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZh2HDM.pdf}
+\caption{Search for \AtoZhtolltautau interpreted in a type II 
+2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
+and observed (solid line) exclusion contours at 95\% confidence level are overlaid
+on the cross--section of $gg\rightarrow \PHiggsps$ production
+times the branching ratio of \PHiggsps into \Zhtolltautau.
+Regions of the \cosba-\tanb plane where the cross--section times branching
+ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
+(see figure FIXME:add plot) are excluded.}
+\label{fig:AZh2HDMOverlaid}
+\end{center}
+\end{figure}
+
+A combined interpretation of both analyses in this model is presented
+in figure \ref{fig:HhhAZh2HDM}. Some of the features discussed earlier
+in this section are also visible in this combined interpretation.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}
+\caption{Combined interpretation of searches for \AtoZhtolltautau and 
+\Htohhtobbtautau in a type II 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV.
+The shaded blue area bounded by the solid black line indicates the observed 
+95\% confidence level excluded region. The dashed black line indicates the expected
+exclusion, with the grey bands indicating the $\pm 1\sigma$ and $2\sigma$ 
+exclusion limits \cite{CMS-HIG-14-034}.}
+\label{fig:HhhAZh2HDM}
+\end{center}
+\end{figure}
+
+\subsubsection{Interpretation in the low \tanb MSSM scenario}
+\label{sec:hhh_results_modeldep_lowtb}
+The low \tanb MSSM scenario, as discussed in section FIXME: write theory section that mentions this
+is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb values
+as low as 1.
+
+The combined interpretation of both analyses in this model is presented in figure \ref{fig:HhhAZhMSSM}.
+The exclusion in this scenario is driven by the \AtoZh search, the \Htohh search is not
+very sensitive in this model (see figure FIXME add these plots). At 350 GeV the excluded
+region drops off, this is due to the turn--on of the
+$\PHiggsps \rightarrow \ttbar$ decay which becomes kinematically allowed in this region, 
+sharply decreasing the \AtoZh branching ratio.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}
+\caption{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
+interpreted in the low \tanb MSSM scenario. The shaded blue area bounded by
+the solid black line indicates the observed excluded region at 95\% confidence level.
+The dashed black line indicates the expected exclusion, with the grey bands showing
+the $\pm 1\sigma$ and $2\sigma$ expected exclusion \cite{CMS-HIG-14-034}. The area
+bounded by the red line is the region of phase space where \mh $\neq 125 \pm 3$ 
+GeV and is therefore not accessible.}
+\label{fig:HhhAZhMSSM}
+\end{center}
+\end{figure}

### 2016-10-16 Hhh/HhhAZhThesisResources/drawlowtbhighSecBR.py
Adding some low tanb plots

@@ -1,0 +1,204 @@
+#!/usr/bin/env python
+import ROOT
+from array import array
+import CombineHarvester.CombineTools.plotting as plot
+import numpy as np
+
+def set_plot_style():
+  NRGBs = 5;
+  NCont = 255;
+  stops = {0.00,0.34,0.61,0.84,1.00}
+  red = {0.00,0.00,0.87,1.00,0.51}
+  green = {0.00,0.81,1.00,0.20,0.00} 
+  blue = {0.51,1.00,0.12,0.00,0.00}
+  ROOT.TColor.CreateGradientColorTable(NRGBs,np.array(stops),np.array(red),np.array(green),np.array(blue),NCont)
+  ROOT.gStyle.SetNumberContours(NCont)
+
+def DrawAxisHists(pads, axis_hists, def_pad=None):
+    for i, pad in enumerate(pads):
+        pad.cd()
+        axis_hists[i].Draw('AXIS')
+        axis_hists[i].Draw('AXIGSAME')
+    if def_pad is not None:
+        def_pad.cd()
+
+
+set_plot_style()
+ROOT.gStyle.SetCanvasBorderMode(0)
+ROOT.gStyle.SetCanvasColor(ROOT.kWhite)
+ROOT.gStyle.SetCanvasDefH(600)  # Height of canvas
+ROOT.gStyle.SetCanvasDefW(600)  # Width of canvas
+ROOT.gStyle.SetCanvasDefX(0)    # POsition on screen
+ROOT.gStyle.SetCanvasDefY(0)
+
+ROOT.gStyle.SetPadBorderMode(0)
+# ROOT.gStyle.SetPadBorderSize(Width_t size = 1)
+ROOT.gStyle.SetPadColor(ROOT.kWhite)
+ROOT.gStyle.SetPadGridX(False)
+ROOT.gStyle.SetPadGridY(False)
+ROOT.gStyle.SetGridColor(0)
+ROOT.gStyle.SetGridStyle(3)
+ROOT.gStyle.SetGridWidth(1)
+
+# For the frame:
+ROOT.gStyle.SetFrameBorderMode(0)
+ROOT.gStyle.SetFrameBorderSize(1)
[…]

### 2016-10-16 Hhh/Hhh.tex
And updating kin fit description / adding some plots to go with it

@@
 interactions.
+
+To better model the \Ztautau background, an embedding technique is used. In this method, 
+\Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
+to decay the taus and tau polarisation effectes are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
+response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
+tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
+due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
+of the two muons originiating from the \PZ have been removed. This technique is also applied to 
+a \ttbar background samples to estimate the \ttbar contamination in the embedded sample. This contribution
+needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
+avoid double counting with the \ttbar monte carlo.
 
@@
 In addition to the requirements on the di--tau pair, at least 2 jets with \pT$ >20$ GeV are 
-required. No b--tagging requirements are applied at this stage, this will be discussed 
+required. No b--tagging requirements are applied at this stage, these will be discussed 
 in more detail in section \ref{sec:hhh_selection_categories}.
+
+Figure \ref{fig:Hhh_selection_kinematics_mt} shows some of the kinematic variables 
+of di-\Pgt candidates in the \mutau channel
+\begin{figure}[h!]
+\begin{center}
+ \subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_mt_2012.pdf}}
+  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}~\\
+  \subfloat[Muon $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_mt_2012.pdf}}
+  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_mt_2012.pdf}}~\\
+
+\end{center}
+\caption{Plots of muon and hadronic \Pgt \pT and $\eta$ in the \mutau channel.}
+\label{fig:Hhh_selection_kinematics_mt}
+\end{figure}
 
@@
 
+Figure \ref{fig:Hhh_selection_kinematics_et} shows some of the kinematic variables 
+of di-\Pgt candidates in the \etau channel
+\begin{figure}[h!]
+\begin{center}
+ \subfloat[Electron \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
+  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_et_2012.pdf}}~\\
+  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
+  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_et_2012.pdf}}~\\
+
+\end{center}
+\caption{Plots of electron and hadronic \Pgt \pT and $\eta$ in the \etau channel.}
+\label{fig:Hhh_selection_kinematics_et}
+\end{figure}
+
 \subsection{Categorisation}
-\label{sec:hhh_selection_categorisation}
+\label{sec:hhh_selection_categories}
+ADD b-jet plots?
 In both channels an selection on the transverse mass \mT between the electron/muon
@@
 
-Where \pT is the transverse moment of the electron or muon, and $\Delta\phi$ the angle
-between the light lepton and the missing transverse energy.
+In this eqation \pT is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
+between the light lepton and the missing transverse energy. The \mT distributions for the \etau
+and \mutau channels, using the selections as
+described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
+is shown in figure \ref{fig:Hhh_selection_mt}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012.pdf}}
+\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012.pdf}}
+\end{center}
+\caption{\mT distributions in the \mutau (left) and \etau (right) channels}
+\label{fig:Hhh_selection_mt}
+\end{figure}
+
 In both channels this quantity is required to be smaller than 30 GeV. In events
@@
 events, as the W is very heavy, the lepton and neutrino are more likely to emitted back--to--back,
-therefore \mT will be large. For \Ztautau and \htautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
+therefore \mT will be large. For \Ztautau and \htotautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
 the neutrinos are more likely to travel in the same direction as the visible decay products of 
 the tau, due to the smaller mass of the \Pgt compared with the \PW. Therefore requiring the
-transverse mass to be less than 30 GeV reduces the \Wjets background.
+transverse mass to be less than 30 GeV reduces the \Wjets background. This effect
+is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
+smaller diboson and single-top backgrounds are drawn together as 'electroweak backgrounds'.
 %In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
@@
 large number of background events can be rejected, while retaining
-most of the signal. This is illustrated in figure SOMETHING.
+most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
+the 2jet-2tag category.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\Pgt\Pgt}$ (\mutau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
+\subfloat[$m_{\Pgt\Pgt}$ (\etau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_et_2012.pdf}}~\\
+\subfloat[$m_{jj}$ (\mutau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
+\subfloat[$m_{jj}$ (\etau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_et_2012.pdf}}
+\end{center}
+\caption{Reconstructed di-\Pgt invariant mass (top) and di-jet invariant mass (bottom) in the 2jet-2tag category of the \mutau (left) and \etau (right)
+channels. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in an MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
+One can see that this signal peaks at around 125 GeV.}
+\label{fig:Hhh_selection_masscuts}
+\end{figure}
 
@@
 \label{sec:hhh_datamc}
+Monte Carlo samples are used for the estimation of some of the backgrounds and the signal, 
+and it is therefore important to correct for any mismodelling. The data to Monte Carlo
+correction factors used for this are estimated in dedicated control regions.
+
+A reweighting is applied to make the pile--up distribution in Monte Carlo
+match the distribution observed in data.DESCRIPTION
+
+Data and Monte Carlo identification, isolation, and trigger efficiencies
+are measured for electrons, muons and hadronic taus. The difference between
+the efficiencies in data and Monte Carlo are applied to Monte Carlo events as a
+scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
+
+For electrons and muons, these scale factors are measured using a 
+tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
+The hadronic taus identification, isolation and trigger efficiencies
+are measured via a similar method that makes use of
+$Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+
+FIXME: Tau es?
+
+FIXME: top pt reweighting
+FIXME: ttbar scale factor
+
+In the \etau channel a data to Monte Carlo scale factor is applied
+to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
+fake rate between data and MC. DERIVED HOW
+
+To correct for the difference in b--tagging efficiency and light jet mis--tagging
+rates between data and Monte Carlo \pT and $\eta$ dependent scale factors are 
+derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
+b-/c- jets and light jets. There are multiple possible ways to apply these
+scale factors, for this analysis this is done through a promote/demote method.
+
+In this method a demotion or promotion probability is assigned to every
+jet as in equation \ref{eqn:promotedemote}.
+
+\begin{align}\label{eqn:promotedemote}
+&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
+&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
+\end{align}.
+
+In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
+the b--tagging efficiency in Monte Carlo events for the type of jet (light, b- or c-)
+in consideration.
 
@@
 \label{sec:hhh_discr}
+The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
+reconstructed as the 4--body mass of the two jets and the two taus, however
+a more accurate result can be obtained by using a kinematic fitting 
+procedure that makes use of the 125 GeV mass constraint on the di--tau and
+di--jet candidates.
+
+In a kinematic fit constraints are made on the event kinematics, in the
+case of this analysis these constraints are
+$m(\Pgt_{1},\Pgt_{2}) = m_{h} = 125 $GeV and
+$m(b_{1},b_{2}) = m_{h} = 125 $ GeV.
+The kinematic observables related to the hadronic taus and jets
+are varied within their uncertainties to fulfill these 
+constraints. A $\chi^2$ cost term is introduced for each
+observable that is varied with respect to the measurement,
+the aim of the fit is to minimise this.
+
+For b-jets, the reconstructed direction in $\eta$ and $\phi$ is 
+assumed to be measured accurately in comparison with their energy.
+Therefore only the energy is varied in the fit. In addition, we assume
+that uncertainties in the energy measurement directly translate to
+uncertainties in the momentum measurement, therefore $\vec{\beta} = \vec{p}/E$ is
+also kept constant.
+
+Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})
+
+\begin{align}\label{eqn:kinfit_prefit}
+m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
+& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
+& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
+\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
+\end{align}
+
+When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
+rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
+and equation \ref{eqn:gamma_def}:
+
+\begin{equation}\label{eqn:gamma_def}
+\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}
+\end{equation}
+
+We get:
+
+\begin{align}\label{eqn:kinfit_variation}
+m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}}\notag\\
+&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
+\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
+&= E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
+\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
+\end{align}
+
+The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
+\begin{equation}\label{eqn:kinfit_bjetmass}
+m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}
+\end{equation}
+
+For each b-jet a $\chi^2$ term is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.
+
+For taus only the visible decay products are measured. Assuming the visible decay products of the \Pgt point in 
+the same direction as the \Pgt, a similar procedure as for the b-jets can be employed to constrain the mass of the second tau
+when varying the mass of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.
+
+Due to the missing energy associated with the \Pgt decays, additional constraints
+on the fit have to be used to reconstruct the correct tau energies. This is done by 
+enforcing that the heavy Higgs boson recoil from the fit is close to the reconstructed recoil.
+
+The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})
+
+\begin{equation}\label{eqn:kinfit_recoilmeas}
+\vec{p_{\text{T,recoil}}}^{measured} = -\vec{p_{\text{T,H}}}^{measured} = -\vec{p_{\text{T,miss}}}^{measured} - \vec{p_{\text{T},b_{1}}}^{measured} - \vec{p_{\text{T},b_{2}}}^{measured} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{measured} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{measured}
+\end{equation}
+
+With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
+\begin{equation}\label{eqn:kinfit_recoilfit}
+\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}
+\end{equation}
+
+A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
+
+\begin{equation}\label{eqn:kinfit_recoilchi2}
+\chi^2_{recoil} = (\vec{p_{text{T,recoil}}}^{\text{fit}} - \vec{p_{text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{text{T,recoil}}}^{\text{fit}} - \vec{p_{text{T,recoil}}}^{\text{measured}})
+\end{equation}
+
+where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
+the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET (OBJECT RECO),
+while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets.
+
+\begin{equation}\label{eqn:kinfit_recoilcov}
+V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
+\end{equation}
+
+The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})
+
+\begin{equation}\label{eqn:kinfit_chitot}
+\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}
+\end{equation}
+
+The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
+set to the best fit values found for them in the fit. These can then be added together to find
+the mass of the heavy Higgs boson as reconstructed by the kinematic fit.
+
+As illustrated in figure \ref{fig:kinfitvsmjj} the use of the kinematic fit greatly
+improves the resolution of the reconstructed heavy Higgs mass in signal events, when 
+compared with the simple 4-body mass reconstruction. It also shifts the mean of the
+distribution closer to the true value. From the right hand side of
+figure \ref{fig:kinfitvsmjj} one can see that the mass distribution for
+background events is less affected by the kinematic fit, although due to the
+invariant mass constraint the minimum of the reconstructed mass distribution
+is forced to 250 GeV.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/CMS-HIG-14-034_Figure-aux-020.pdf}}
+\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/mHvsmttbb_ttbar.pdf}}
+\end{center}
+\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
+4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
+the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
+accuracy of the mean of the mass distribution in signal events. \cite{HIG-14-034-additional}}%FIXME plots need to be remade as the bkg one was never released
+%on the public twiki so can't have the CMS label on
+\label{fig:kinfitvsmjj}
+\end{figure}
 
@@
 \label{sec:hhh_backgrounds}
+To estimated the shape and yield of backgrounds in this analysis, data--driven techniques are
+used where possible.
 

### 2016-10-16 Hhh/Hhh.tex
Fixing some cosmetics and adding Hhh bkg section

@@
 & = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
-\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
+&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
 \end{align}
@@
 &= E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
-\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
+&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
 \end{align}
@@
 \begin{equation}\label{eqn:kinfit_recoilmeas}
-\vec{p_{\text{T,recoil}}}^{measured} = -\vec{p_{\text{T,H}}}^{measured} = -\vec{p_{\text{T,miss}}}^{measured} - \vec{p_{\text{T},b_{1}}}^{measured} - \vec{p_{\text{T},b_{2}}}^{measured} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{measured} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{measured}
+\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}}
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilchi2}
-\chi^2_{recoil} = (\vec{p_{text{T,recoil}}}^{\text{fit}} - \vec{p_{text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{text{T,recoil}}}^{\text{fit}} - \vec{p_{text{T,recoil}}}^{\text{measured}})
+\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
 \end{equation}
@@
 \begin{center}
-\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/CMS-HIG-14-034_Figure-aux-020.pdf}}
+\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
 \subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/mHvsmttbb_ttbar.pdf}}
@@
 used where possible.
+
+\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
+\label{sec:hhh_backgrounds_ztt}
+The \Ztautau background is estimated using the embedded samples
+described in section \ref{sec:hhh_datasets}. To estimate the 
+yield of \Ztautau in each category, the total
+yield after the initial event selection (before subdividing into categories) as
+estimated in \Ztautau Monte Carlo samples is scaled by the efficiency with which 
+such events pass the category selection in the embedded sample. The shape of
+the \Ztautau background is taken from the embedded sample after applying the full
+category selection. The contamination from \ttbar backgrounds in the embedded
+sample is accounted for by subtracting this contamination, as evaluated using
+the dedicated \ttbar embedded samples, from the \Ztautau background.
+
+\subsection{\texorpdfstring{\ttbar}{ttbar}}
+Both the \ttbar shape and normalisation are estimated using Monte Carlo samples.
+These are checked against data in dedicated control regions. One such control
+region uses the \emu final state of the taus. In this control region
+a data-to-Monte Carlo scale factor is estimated and applied to the yield estimate from Monte Carlo.
+
+\subsection{\texorpdfstring{\Wjets}{W + jets}}
+\label{sec:hhh_backgrounds_wjets}
+The \Wjets background is greatly reduced by requiring \mT to
+be less than 30 GeV. To estimate the remaining contribution
+from \Wjets in the signal region a sideband with \mT greater
+than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
+Contributions from other backgrounds are subtracted 
+from the data in this region, and a high \mT to low \mT
+extrapolation factor is determined from the \Wjets Monte Carlo
+samples. The yield in the signal region is then the other-background-subtracted
+data yield in the high \mT region multiplied by this extrapolation factor.
+In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
+to give larger statistics for the \Wjets estimate after other backgrounds are
+subtracted. The method of extrapolating this yied estimate into
+the signal region is otherwise analogous.
+
+The \Wjets shape is taken from the Monte Carlo samples. To 
+increase the statistics for this estimate, the b-tagging definition
+in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
+working point for the purposes of shape estimation.
+
+\subsection{QCD}
+\label{sec:hhh_backgrounds_qcd}
+A fully data-driven method is used to estimate the QCD background. Data events
+passing the signal region selection cuts, but requiring the di-tau pair to be
+of the same sign, are used for this. Contributions from other backgrounds are 
+subtracted. Because the contribution from opposite- and same-sign QCD are
+not exactly the same an OS/SS ratio of 1.06 is measured using data in which
+the electron/muon isolation requirement was inverted.
+
+For the 2jet-0tag and 2jet-1tag categories the yield is taken directly from
+the same-sign subtracted data multiplied by the OS/SS ratio. In the 2jet-2tag
+category the statistics are too low for this, so another sideband is defined
+in which the electron/muon isolation requirement is inverted. This 
+sideband is then used to determine an extrapolation factor from events
+with 2 jets to events passing the 2jet-2tag category selection. This extrapolation
+factor is then applied to a QCD estimate as described above, but using the 2-jet 
+selection only, to obtain the yield in the 2jet-2tag category.
+
+The shapes in all categories are taken from same-sign data with the electron/muon
+isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
+inverting the light lepton isolation requirements, the category definition
+is loosened to obtain the shapes. For the purposes of QCD shape
+estimation, jets are considered b-tagged if they pass a looser b-tagging
+working point than the working point used elsewhere in the analysis.
+
+\subsection{Other backgrounds}
+\label{sec:hhh_backgrounds_other}
+The remaining backgrounds of \Zellell, di-boson and single-top
+events are small. Both shape and normalisation are
+estimated using Monte Carlo samples.
 
@@
 \label{sec:hhh_results_modelindep}
+
+Add combined plot + per channel comparison (?)
+Combined of mutau and etau only, or full combination even though not having
+worked on fully hadronic?
 

### 2016-10-18 Hhh/Hhh.tex
Filling in some more gaps in Hhh chapter

@@
 \begin{center}
-\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
-\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/mHvsmttbb_ttbar.pdf}}
+\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
+\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_ttbar.pdf}}
 \end{center}
@@
 \label{sec:hhh_uncs}
+Two types of systematic uncertainties are considered: normalisation
+uncertainties (which affect only the yield of a process), and shape
+uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}
+describes how these uncertainties are taken into account in the final result.
+
+\subsection{Normalisation uncertainties}
+\label{sec:hhh_uncs_norm}
+
+\subsubsection*{Luminosity uncertainty}
+The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
+2012 (LUMI POG CITATION?). This uncertainty is applied to all processes in which
+the normalisation is estimated using MC samples.
+
+\subsubsection*{Identification, isolation and trigger efficiencies}
+A systematic uncertainty due to the uncertainty in efficiency measurements
+for the leptons is derived by combining the uncertainties on these measurements
+in quadrature. For electrons and muons this leads to a 2\% uncertainty, for hadronic taus a 6\% 
+uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
+the \Pgt legs of the triggers. This uncertainty is applied to all processes for which
+the normalisation is estimated using MC samples.
+
+\subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
+The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
+$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$
+fake rate is close to 1, which is why it is not applied, but the uncertainty is 
+taken into account FIXME check if this is true!
+
+\subsubsection*{B-tag scale factors}
+The b-tag scale factors are varied within their uncertainties to determine the effect
+on the yields of each process. Both a b-tagging uncertainty and a fake mis-tagging
+uncertainty are obtained by considering the percentage by which these backgrounds
+change when the scale factors are varied within their uncertainty. The b-tagging
+efficiency uncertainty amounts to 1-10\% for most processes in most categories, except for the 2jet-2tag
+category where a 70\% uncertainty applies to the W background. Due to the nature
+of the estimation method, where other backgrounds are subtracted from the data to 
+obtain a W estimate, and the presence of large amounts of \ttbar, a 10\% change in the \ttbar
+yield can vary the W yield by such large amounts.
+The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.
+
+\subsubsection*{\MET resolution and response}
+Uncertainties on the \MET resolution and response are estimated by varying
+the recoil correction parameters within their estimated uncertainties. This 
+leads to a 1-10\% uncertainty (depending on category and process)
+
+\subsubsection*{Background normalisation}
+\begin{itemize}
+\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived
+from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples.
+In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
+\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
+\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
+\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
+\item \Wjets: As the \Wjets yield is estimated from a high \mT sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty range sfrom 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
+\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio.
+This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.
+\end{itemize}
+
+\subsection{Shape uncertainties}
+\label{sec:hhh_uncerts_shape}
+
+\subsubsection*{Tau energy scale}
+The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty.
+As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.
+
+\subsubsection*{Jet energy scale}
+The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the (\pT and $\eta$ dependent) uncertainty.
+Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty
 
@@
 
-Add combined plot + per channel comparison (?)
-Combined of mutau and etau only, or full combination even though not having
-worked on fully hadronic?
+The $m_{H}^{\text{kinfit}}$ distributions in the \mutau and \etau channel 
+are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
+respectively.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-a.pdf}}
+\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-b.pdf}}~\\
+\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-c.pdf}}
+\end{center}
+\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+of the \mutau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
+scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
+\label{fig:hhh_results_mhkinfit_mutau}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-a.pdf}}
+\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-b.pdf}}~\\
+\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-c.pdf}}
+\end{center}
+\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+of the \etau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
+scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
+\label{fig:hhh_results_mhkinfit_etau}
+\end{figure}
+
+None of these distributions show hints of an excess.
+
+The model-independent 95\% CL expected and observed upper limits are shown in 
+figure \ref{fig:hhh_results_modelindep}, with figure \ref{fig:hhh_results_modelindep_perchannel}
+showing the expected sensitivity per channel. These figures include the contribution from the 
+\tautau channel not described in this thesis. Figure \ref{fig:hhh_results_modelindep} shows that
+the expected upper limit on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
+from 0.2 pb at low mass to 0.4 pb at high mass. From figure \ref{fig:hhh_results_modelindep}
+we can see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
+the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
+less sensitive than the \mutau channel, but at low mass it is still more sensitive than the \tautau 
+channel.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}
+\caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
+for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.}
+\label{fig:hhh_results_modelindep}
+\end{center}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
+\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
+The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
+red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
+$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
+\label{fig:hhh_results_modelindep_perchannel}
+\end{center}
+\end{figure}
 
@@
 ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
-(see figure FIXME:add plot) are excluded.}
+(see figure \ref{fig:hhh_results_modelindep}) are excluded.}
 \label{fig:Hhh2HDMOverlaid}
@@
 ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
-(see figure FIXME:add plot) are excluded.}
+(see figure \ref{fig:AZhUpperLimits}) are excluded.}
 \label{fig:AZh2HDMOverlaid}
@@
 
+Figure \ref{fig:Hhhlowtanb} shows the cross-section times branching ratio
+of the \Htohhtobbtautau process in the MSSM low \tanb scenario. Comparing these values 
+to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} one
+can see that the cross-section times branching ratio in this model is, with exception of a few small 
+areas, lower than the upper limits set by this analysis. This analysis on its own is
+therefore not sensitive enough to exclude any of the \mA-\tanb region in this model. Note that
+at low \tanb ~ \mA and \mH are degenerate, and therefore \mH is not in the studied range of $260-350$ GeV
+throughout the entire \mA-\tanb plane shown here.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhhlowtbhigh.pdf}
+\caption{Cross-section times branching ratio of the \Htohhtobbtautau process
+in the low-\tanb MSSM scenario. No expected and observed exclusion contours
+have been overlaid on these figures as the cross-section times branching
+ratio is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
+\label{fig:Hhhlowtanb}
+\end{center}
+\end{figure}
+
+The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb region
+in this model by itself. The expected and observed 95\% CL exclusion contours are overlaid 
+on the cross-section times branching ratio for this process in the low \tanb MSSM scenario in
+figure \ref{fig:AZhlowtanbOverlaid}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
+near \mA $ = 350$ GeV arises from the fact that near this mass the decay $\PHiggsps \rightarrow t\bar{t}$ becomes
+kinematically allowed, resulting in a reduction of the \AtoZh branching ratio.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}
+\caption{Expected and observed 95 \% CL exclusion limits for the \AtoZhtolltautau analysis
+in the low \tanb MSSM scenario, overlaid on the cross-section times branching ratio. Areas where
+the cross-section times branching ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits}
+are excluded. The exclusion rapidly drops off at $m_A = 350$ GeV due to the turn-on of the
+$ \PHiggsps \rightarrow$ \ttbar process.}
+\label{fig:AZhlowtanbOverlaid}
+\end{center}
+\end{figure}
+
 The combined interpretation of both analyses in this model is presented in figure \ref{fig:HhhAZhMSSM}.
-The exclusion in this scenario is driven by the \AtoZh search, the \Htohh search is not
-very sensitive in this model (see figure FIXME add these plots). At 350 GeV the excluded
-region drops off, this is due to the turn--on of the
-$\PHiggsps \rightarrow \ttbar$ decay which becomes kinematically allowed in this region, 
-sharply decreasing the \AtoZh branching ratio.
+The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
+very sensitive in this model. Combining the two analyses we do see that a slightly larger amount
+of the \mA-\tanb plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
+described for figure \ref{fig:AZhlowtanbOverlaid} are also visible in this figure. A small region of phase
+space, at low \mA and low\tanb predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
+This region is therefore excluded, this is indicated by the red band.
 

### 2016-11-02 Detector/Detector.tex
Adding some more stuff

\chapter{The \acs{CMS} experiment and the \acs{LHC}}
\label{chap:CMSLHC}

\section{The \acs{LHC}}
\label{sec:CMSLHC_LHC}

The \acf{LHC} \cite{lhc-machine}  is a 26.7 km long synchrotron hadron accelerator and collider below the surface of the 
Franco-Swiss border near Geneva. It
is installed in the tunnel that previously housed the Large Electron Positron accelerator
that was operated by \acf{CERN} between 1989 and 2000.

The \ac{LHC} was designed to collide beams of protons with each other at centre-of-mass
energies of up to 14 TeV. It therefore consists of two rings in which the two beams
of protons are individually accelerated. In addition to colliding beams of protons, the \ac{LHC}
is also used for proton--lead and lead--lead collisions.

Protons originate from hydrogen gas, where electrons are stripped off the 
hydrogen atoms using an electric field. The protons then pass through an injector
chain which increases the energy of the protons in several steps. After the protons
are created from the hydrogen gas, they are accelerated to a centre of mass energy of
50 MeV in the Linac2 linear accelerator. They are then passed on to the
\acf{PSB} which accelerates the protons until they reach a centre of mass energy of 1.4 GeV.
The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
reached the protons are injected into the \ac{LHC}, where they are further accelerated to 
the required centre of mass energy. lbha blah blah. The beams collide at four points
around the ring, where the collisions are recorded by the ATLAS, CMS, ALICE, and LHCb detectors.

As the processes the \ac{LHC} was built to study have a small cross-section
compared with the total proton-proton inelastic cross-section (add figure!), the
LHC operates at high instantaneous luminosity. blah blah blah blah

After an initial testing phase, the \ac{LHC} becan its first physics run in May 2010 with 
a centre of mass energy of 7 TeV. The CMS experiment recorded an integrated luminosity of 45 pb$^{-1}$
during 2010. In 2011 the \ac{LHC} continued operating at a centre-of-mass energy of 7 TeV, delivering an integrated 
luminosity of 6.1 fb$^{-1}$ to the CMS experiment. The centre of mass energy was increased to 8 TeV
for the 2012 data-taking period, during which an integrated luminosity of 23.3 fb$^{-1}$ was delivered.
This completed Run 1 of the \ac{LHC}, after which the 2-year \ac{LS1} was used to 
upgrade the LHC and the detectors for collisions at a centre of mass energy of 13 TeV.

In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV

### 2016-11-02 Hhh/Hhh.tex
Adding some more stuff

@@
 
-\section{Datasets and Monte Carlo samples}
+\section{Datasets and \acl{MC} samples}
 \label{sec:hhh_datasets}
@@
 running period of the LHC. 
-Signal and background events were generated using several different MC event generators. The \texttt{MadGraph}
+Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
 \cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
@@
 \texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
-Minimum bias events generated using \texttt{PYTHIA 6} are added to all MC samples to model additional
+Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
 interactions.
@@
 
-Figure \ref{fig:Hhh_selection_kinematics_mt} shows some of the kinematic variables 
-of di-\Pgt candidates in the \mutau channel
-\begin{figure}[h!]
-\begin{center}
- \subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_mt_2012.pdf}}
-  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}~\\
-  \subfloat[Muon $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_mt_2012.pdf}}
-  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_mt_2012.pdf}}~\\
-
-\end{center}
-\caption{Plots of muon and hadronic \Pgt \pT and $\eta$ in the \mutau channel.}
-\label{fig:Hhh_selection_kinematics_mt}
-\end{figure}
+%Figure \ref{fig:Hhh_selection_kinematics_mt} shows some of the kinematic variables 
+%of di-\Pgt candidates in the \mutau channel
+%\begin{figure}[h!]
+%\begin{center}
+% \subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_mt_2012.pdf}}
+%  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}~\\
+%  \subfloat[Muon $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_mt_2012.pdf}}
+%  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_mt_2012.pdf}}~\\
+%
+%\end{center}
+%\caption{Plots of muon and hadronic \Pgt \pT and $\eta$ in the \mutau channel.}
+%\label{fig:Hhh_selection_kinematics_mt}
+%\end{figure}
 
@@
 
-Figure \ref{fig:Hhh_selection_kinematics_et} shows some of the kinematic variables 
-of di-\Pgt candidates in the \etau channel
+Figure \ref{fig:Hhh_selection_kinematics_etmt} shows some of the kinematic variables 
+of di-\Pgt candidates in the \etau and \mutau channels
 \begin{figure}[h!]
 \begin{center}
- \subfloat[Electron \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
-  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_et_2012.pdf}}~\\
-  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
-  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_et_2012.pdf}}~\\
+ \subfloat[Electron \pT (\etau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
+  \subfloat[Hadronic \Pgt \pT (\mutau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}
+%  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
+%  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_et_2012.pdf}}~\\
 
 \end{center}
-\caption{Plots of electron and hadronic \Pgt \pT and $\eta$ in the \etau channel.}
-\label{fig:Hhh_selection_kinematics_et}
+\caption{Plots of electron \pT in the \etau channel and hadronic \Pgt \pT in the \mutau channel.}
+\label{fig:Hhh_selection_kinematics_etmt}
 \end{figure}
@@
 and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
-
 \begin{equation}\label{eqn:hhh_selection_mt}
@@
 \end{equation}
-
 In this eqation \pT is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
@@
 
-\section{Data to Monte Carlo correction factors}
+\section{Data to \acl{MC} correction factors}
 \label{sec:hhh_datamc}
-Monte Carlo samples are used for the estimation of some of the backgrounds and the signal, 
-and it is therefore important to correct for any mismodelling. The data to Monte Carlo
+\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
+and it is therefore important to correct for any mismodelling. The data to \ac{MC} 
 correction factors used for this are estimated in dedicated control regions.
 
-A reweighting is applied to make the pile--up distribution in Monte Carlo
+A reweighting is applied to make the pile--up distribution in \ac{MC}
 match the distribution observed in data.DESCRIPTION
 
-Data and Monte Carlo identification, isolation, and trigger efficiencies
+Data and \ac{MC} identification, isolation, and trigger efficiencies
 are measured for electrons, muons and hadronic taus. The difference between
-the efficiencies in data and Monte Carlo are applied to Monte Carlo events as a
+the efficiencies in data and \ac{MC} are applied to \ac{MC} events as a
 scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
@@
 
-In the \etau channel a data to Monte Carlo scale factor is applied
+In the \etau channel a data to \ac{MC} scale factor is applied
 to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
-fake rate between data and MC. DERIVED HOW
+fake rate between data and \ac{MC}. DERIVED HOW
 
 To correct for the difference in b--tagging efficiency and light jet mis--tagging
-rates between data and Monte Carlo \pT and $\eta$ dependent scale factors are 
+rates between data and \ac{MC} \pT and $\eta$ dependent scale factors are 
 derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
@@
 jet as in equation \ref{eqn:promotedemote}.
-
 \begin{align}\label{eqn:promotedemote}
@@
 \end{align}.
-
 In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
-the b--tagging efficiency in Monte Carlo events for the type of jet (light, b- or c-)
+the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
 in consideration.
@@
 Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})
-
+~\vspace{-0.5\baselineskip}
 \begin{align}\label{eqn:kinfit_prefit}
@@
 \end{align}
-
 When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
@@
 and equation \ref{eqn:gamma_def}:
-
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:gamma_def}
@@
 \end{equation}
-
 We get:
-
+~\vspace{-0.5\baselineskip}
 \begin{align}\label{eqn:kinfit_variation}
@@
 The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_bjetmass}
@@
 \end{equation}
-
 For each b-jet a $\chi^2$ term is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.
@@
 The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})
-
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilmeas}
@@
 \end{equation}
-
 With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilfit}
@@
 \end{equation}
-
 A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
-
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilchi2}
@@
 \end{equation}
-
 where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
@@
 while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets. 
-
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilcov}
@@
 \end{equation}
-
 The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})
-
+~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_chitot}
@@
 \end{equation}
-
 The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
@@
 yield after the initial event selection (before subdividing into categories) as
-estimated in \Ztautau Monte Carlo samples is scaled by the efficiency with which 
+estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
 such events pass the category selection in the embedded sample. The shape of
@@
 \subsection{\texorpdfstring{\ttbar}{ttbar}}
-Both the \ttbar shape and normalisation are estimated using Monte Carlo samples.
+Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
 These are checked against data in dedicated control regions. One such control
 region uses the \emu final state of the taus. In this control region
-a data-to-Monte Carlo scale factor is estimated and applied to the yield estimate from Monte Carlo.
+a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.
 
@@
 from the data in this region, and a high \mT to low \mT
-extrapolation factor is determined from the \Wjets Monte Carlo
+extrapolation factor is determined from the \Wjets \ac{MC} 
 samples. The yield in the signal region is then the other-background-subtracted
@@
 
-The \Wjets shape is taken from the Monte Carlo samples. To 
+The \Wjets shape is taken from the \ac{MC} samples. To 
 increase the statistics for this estimate, the b-tagging definition
@@
 events are small. Both shape and normalisation are
-estimated using Monte Carlo samples.
+estimated using \ac{MC} samples.
 
@@
 Remaining backgrounds from \ZZ, triboson and \ttbar\PZ production are estimated using
-Monte Carlo samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
+\ac{MC} samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
 and \WZ+jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
@@
 \label{sec:hhh_results_extraction}
+The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable.
+For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
+of the observed data with the expected background distribution can be assessed. All bins
+of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
+methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
+and are used for all Higgs analyses in ATLAS and CMS.
+
+For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
+\begin{equation} \label{eqn:hhh_likelihood}
+\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot \Sigma_j p(~\theta_j|\theta_j)
+\end{equation}
+
+Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})
+
+\begin{equation}\label{eqn:hhh_poisson}
+\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
+\end{equation}
+
+The first term integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
+in all channels and categories. $s$ represents the number of expected signal events
+in each bin, and $b$ the number of expected background events. These are functions of 
+$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
+REFERENCE are represented by a nuisance parameter $\theta_j$. The signal strength
+modifier $\mu$ can represent different quantities depending on the normalisation of the 
+signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
+to 1 pb, so the signal strenght modifier represents
+the cross-section $\times$ branching ratio of a possible signal.
+
+IMPROVE THIS:
+The second term $p(~\theta|\theta)$ represents the pdf of the uncertainty on the nominal
+value of the nuisance parameter $~\theta$.
+
+To compare the data with the background only and signal + background hypothesis, a test
+statistic $~q_{\mu}$ can be defined. This is a single 
+number that is used to distinguish between the two hypotheses. The test
+statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
+in equation \ref{eqn:hhh_profilelikelihood}.
+
+\begin{equation}\label{eqn:hhh_profilelikelihood}
+q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
+\end{equation}
+
+Where we require $0 \leq \hat{\mu} \leq \mu$.
+
+In this equation $\mu$ is the signal strenght modifier being tested, $\hat{\theta_{\mu}}$ denotes the values of the
+nuisance parameters which maximise the likelihood for that particular $\mu$, while $\hat{mu}$ and $\hat{\theta}$ are
+the values of signal strength modifier and nuisance parameters which give the global maximum of the likelihood.
+The requirements on $\mu$ ensure that the signal strenght is non-negative ($ 0 \leq \hat{\mu}$) and that
+a one-sided confidence interval is constructed so as not to allow the observation of  a 
+signal with strength $\hat{mu} > \mu$ to cause rejection of the signal hypothesis ($ \hat{\mu} \leq \mu$).
+
+Describe pdfs
+
+The p-value for $\mu$ and for background-only ($\mu = 0$) can be determined as in equation \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}.
+
+\begin{equation}\label{eqn:hhh_pvaluesig}
+p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \Integral_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
+\end{equation}
+
+\begin{equation}\label{eqn:hhh_pvaluebkg}
+1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \Integral_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
+\end{equation}
+
+$CL_s$ is then defined as (equation \ref{eqn:hhh_cls})
+
+\begin{equation}\label{eqn:hhh_cls}
+CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
+\end{equation}
+
+The value of $\mu$ for which $CL_s(\mu) \leq \alpha$ then gives the upper limit 
+In the case of the analysis discussed in this chapter, the value of $\mu$ for which the upper 
+limit on cross-section times branching ratio for the \Htohhtobbtautau process reaches $1-\alpha$ is 
+said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
+quoted at 95\% confidence level, therefore the upper limit on cross-section times branching ratio
+for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
+equals 0.05. MODIFIED FREQUENTIST APPROACH.
+
+While the distribution of $f(q_{\mu})$ can always be determined by generating toy datasets,
+in the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
+This formula, known as the asymptotic approximation, allows for the calculation
+of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
+the properties of the Asimov dataset, a dataset in which the observation in 
+each bin exactly matches the background expectation.
 
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}
+\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
+\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}}
 \caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
-for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.}
+for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034} (left).
+The right hand side panel shows the expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau
+process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
+for the \etau channel and the black line the limit for all three channels combined. Up to around $m_H = 320$ GeV the \mutau channel is the most
+sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
 \label{fig:hhh_results_modelindep}
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
-\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
-The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
-red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
-$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
-\label{fig:hhh_results_modelindep_perchannel}
-\end{center}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
+%\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
+%The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
+%red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
+%$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
+%\label{fig:hhh_results_modelindep_perchannel}
+%\end{center}
+%\end{figure}
 
@@
 
-The interpretations are made in the \cosba--\tanb plane. Figures \ref{fig:Hhh2HDMOverlaid}
-and \ref{fig:AZh2HDMOverlaid} show the observed and expected exclusion at 95\% confidence level for the \Htohh
-and \AtoZh analyses respectively, overlaid on the production cross--section times branching ratio.
+The interpretations are made in the \cosba--\tanb plane. Figure \ref{fig:HhhAndAZh2HDMOverlaid}
+shows the observed and expected exclusion at 95\% confidence level for the \Htohh
+and \AtoZh analyses, overlaid on the production cross--section times branching ratio.
 The exclusion contours have some interesting features, most of which can be explained by the couplings
@@
 which both vanish as \cosba approaches 0. This leads to the corridor of non--exclusion down the 
-centre of figures \ref{fig:Hhh2HDMOverlaid} and \ref{fig:AZh2HDMOverlaid}. Additionally,
+centre of the plots in figure \ref{fig:HhhAndAZh2HDMOverlaid}. Additionally,
 as the couplings of \PHiggslight to pairs of b--quarks and $\Pgt$ leptons are porportional 
@@
 \begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhh2HDM.pdf}
-\caption{Search for \Htohhtobbtautau interpreted in a type II 
+\subfloat[\Htohhtobbtautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/Hhh2HDM.pdf}}
+\subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZh2HDM.pdf}}
+\caption{Search for \Htohhtobbtautau (left) and \AtoZhtolltautau (right) interpreted in a type II 
 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
 and observed (solid line) exclusion contours at 95\% confidence level are overlaid
-on the cross--section of $gg\rightarrow \PHiggs$ production
-times the branching ratio of \PHiggs into \hhtobbtautau.
+on the cross--section times branching ratio of the searched-for process.
 Regions of the \cosba-\tanb plane where the cross--section times branching
 ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
-(see figure \ref{fig:hhh_results_modelindep}) are excluded.}
-\label{fig:Hhh2HDMOverlaid}
+(see figure \ref{fig:hhh_results_modelindep} and \ref{fig:AZhUpperLimits}) are excluded.}
+\label{fig:HhhandAZh2HDMOverlaid}
 \end{center}
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZh2HDM.pdf}
-\caption{Search for \AtoZhtolltautau interpreted in a type II 
-2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
-and observed (solid line) exclusion contours at 95\% confidence level are overlaid
-on the cross--section of $gg\rightarrow \PHiggsps$ production
-times the branching ratio of \PHiggsps into \Zhtolltautau.
-Regions of the \cosba-\tanb plane where the cross--section times branching
-ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
-(see figure \ref{fig:AZhUpperLimits}) are excluded.}
-\label{fig:AZh2HDMOverlaid}
-\end{center}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZh2HDM.pdf}
+%\caption{Search for \AtoZhtolltautau interpreted in a type II 
+%2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
+%and observed (solid line) exclusion contours at 95\% confidence level are overlaid
+%on the cross--section of $gg\rightarrow \PHiggsps$ production
+%times the branching ratio of \PHiggsps into \Zhtolltautau.
+%Regions of the \cosba-\tanb plane where the cross--section times branching
+%ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
+%(see figure \ref{fig:AZhUpperLimits}) are excluded.}
+%\label{fig:AZh2HDMOverlaid}
+%\end{center}
+%\end{figure}
 
 A combined interpretation of both analyses in this model is presented
-in figure \ref{fig:HhhAZh2HDM}. Some of the features discussed earlier
+in the left-hand side panel of figure \ref{fig:HhhAZhMSSM2HDM}. Some of the features discussed earlier
 in this section are also visible in this combined interpretation.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}
-\caption{Combined interpretation of searches for \AtoZhtolltautau and 
-\Htohhtobbtautau in a type II 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV.
-The shaded blue area bounded by the solid black line indicates the observed 
-95\% confidence level excluded region. The dashed black line indicates the expected
-exclusion, with the grey bands indicating the $\pm 1\sigma$ and $2\sigma$ 
-exclusion limits \cite{CMS-HIG-14-034}.}
-\label{fig:HhhAZh2HDM}
-\end{center}
-\end{figure}
 
@@
 
-Figure \ref{fig:Hhhlowtanb} shows the cross-section times branching ratio
+The left-hand side panel of figure \ref{fig:HhhAndAZhlowtanb} shows the cross-section times branching ratio
 of the \Htohhtobbtautau process in the MSSM low \tanb scenario. Comparing these values 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhhlowtbhigh.pdf}
-\caption{Cross-section times branching ratio of the \Htohhtobbtautau process
-in the low-\tanb MSSM scenario. No expected and observed exclusion contours
-have been overlaid on these figures as the cross-section times branching
-ratio is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
-\label{fig:Hhhlowtanb}
-\end{center}
-\end{figure}
-
 The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb region
 in this model by itself. The expected and observed 95\% CL exclusion contours are overlaid 
-on the cross-section times branching ratio for this process in the low \tanb MSSM scenario in
-figure \ref{fig:AZhlowtanbOverlaid}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
+on the cross-section times branching ratio for this process in the low \tanb MSSM scenario in the right-hand side panel 
+of figure \ref{fig:HhhAndAzhlowtanb}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
 near \mA $ = 350$ GeV arises from the fact that near this mass the decay $\PHiggsps \rightarrow t\bar{t}$ becomes
@@
 \begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}
-\caption{Expected and observed 95 \% CL exclusion limits for the \AtoZhtolltautau analysis
-in the low \tanb MSSM scenario, overlaid on the cross-section times branching ratio. Areas where
-the cross-section times branching ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits}
-are excluded. The exclusion rapidly drops off at $m_A = 350$ GeV due to the turn-on of the
-$ \PHiggsps \rightarrow$ \ttbar process.}
-\label{fig:AZhlowtanbOverlaid}
+\subfloat[\Htohhtobbtautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/Hhhlowtbhigh.pdf}}
+\subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}}
+\caption{Cross-section times branching ratio of the \Htohhtobbtautau process (left) and of the
+\AtoZhtolltautau process (right) in the low-\tanb ~MSSM scenario. On the right-hand side
+plot the expected and observed 95\% CL exclusion limits for the \AtoZhtolltautau analysis in the low \tanb ~MSSM scenario
+have been overlaid on the cross-section times branching ratio. Areas where the cross-section times branching
+ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits} are excluded. The exclusion rapidly drops
+off at $m_A = 350$ GeV due to the turn-on of the $\PHiggsps \rightarrow$ \ttbar process.
+No expected and observed exclusion contours
+have been overlaid on the lef-hand side plot as the cross-section times branching
+ratio is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
+\label{fig:HhhAndAZhlowtanb}
 \end{center}
@@
 
-The combined interpretation of both analyses in this model is presented in figure \ref{fig:HhhAZhMSSM}.
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}
+%\caption{Expected and observed 95 \% CL exclusion limits for the \AtoZhtolltautau analysis
+%in the low \tanb MSSM scenario, overlaid on the cross-section times branching ratio. Areas where
+%the cross-section times branching ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits}
+%are excluded. The exclusion rapidly drops off at $m_A = 350$ GeV due to the turn-on of the
+%$ \PHiggsps \rightarrow$ \ttbar process.}
+%\label{fig:AZhlowtanbOverlaid}
+%\end{center}
+%\end{figure}
+
+The combined interpretation of both analyses in this model is presented in the right-hand side panel of
+figure \ref{fig:HhhAZhMSSM2HDM}.
 The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
@@
 
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}
+%\caption{Combined interpretation of searches for \AtoZhtolltautau and 
+%\Htohhtobbtautau in a type II 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV.
+%The shaded blue area bounded by the solid black line indicates the observed 
+%95\% confidence level excluded region. The dashed black line indicates the expected
+%exclusion, with the grey bands indicating the $\pm 1\sigma$ and $2\sigma$ 
+%exclusion limits \cite{CMS-HIG-14-034}.}
+%\label{fig:HhhAZh2HDM}
+%\end{center}
+%\end{figure}
+
 \begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}
+\subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
+\subfloat[low \tanb ~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
 \caption{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
-interpreted in the low \tanb MSSM scenario. The shaded blue area bounded by
+interpreted in a type II 2HDM assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV (left) and interpreted
+in the low \tanb ~MSSM scenario (right). The shaded blue area bounded by
 the solid black line indicates the observed excluded region at 95\% confidence level.
@@
 GeV and is therefore not accessible.}
-\label{fig:HhhAZhMSSM}
+\label{fig:HhhAZhMSSM2HDM}
 \end{center}

### 2016-11-03 Hhh/Hhh.tex
Adding more plots and some stats stuff

@@
 \label{sec:hhh}
-
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
@@
 A reweighting is applied to make the pile--up distribution in \ac{MC}
-match the distribution observed in data.DESCRIPTION
+match the distribution observed in data, as described in chapter OBJECT RECO.
 
@@
 tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
-The hadronic taus identification, isolation and trigger efficiencies
+The hadronic tau identification, isolation and trigger efficiencies
 are measured via a similar method that makes use of
@@
 
-FIXME: Tau es?
-
-FIXME: top pt reweighting
-FIXME: ttbar scale factor
+The energy scale for hadronic taus is determined by fitting the mass of the 
+hadronic tau candidate in $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+This fit is performed separately for each hadronic tau decay mode to obtain
+an energy scaling that is applied to reconstructed hadronic taus matched
+to generator-level hadronic tau decays in MC events.
 
@@
 to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
-fake rate between data and \ac{MC}. DERIVED HOW
+fake rate between data and \ac{MC}. This scale factor is derived separately
+for the 1-prong + 0$\pi^0$ hadronic tau decay mode, and 1-prong + at least one
+$\pi^0$ decay modes by fitting the visible mass of the \Pe+$\Pgt_{h}$ pair
+in $Z\rightarrow\Pgt\Pgt\rightarrow\Pe\Pgt_{h}$ events.
 
@@
 \begin{center}
-\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
+\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_signal.pdf}}
 \subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_ttbar.pdf}}
@@
 the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
-accuracy of the mean of the mass distribution in signal events. \cite{HIG-14-034-additional}}%FIXME plots need to be remade as the bkg one was never released
+accuracy of the mean of the mass distribution in signal events.}%FIXME plots need to be remade as the bkg one was never released
 %on the public twiki so can't have the CMS label on
@@
 \label{sec:hhh_backgrounds}
-To estimated the shape and yield of backgrounds in this analysis, data--driven techniques are
+To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
 used where possible. 
-
 \subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
@@
 the dedicated \ttbar embedded samples, from the \Ztautau background.
-
 \subsection{\texorpdfstring{\ttbar}{ttbar}}
@@
 a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.
-
 \subsection{\texorpdfstring{\Wjets}{W + jets}}
@@
 working point for the purposes of shape estimation.
-
 \subsection{QCD}
@@
 working point than the working point used elsewhere in the analysis.
-
 \subsection{Other backgrounds}
@@
 describes how these uncertainties are taken into account in the final result.
-
 \subsection{Normalisation uncertainties}
 \label{sec:hhh_uncs_norm}
-
 \subsubsection*{Luminosity uncertainty}
@@
 the normalisation is estimated using MC samples.
-
 \subsubsection*{Identification, isolation and trigger efficiencies}
@@
 the normalisation is estimated using MC samples.
-
 \subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
@@
 fake rate is close to 1, which is why it is not applied, but the uncertainty is 
-taken into account FIXME check if this is true!
-
+taken into account.
 \subsubsection*{B-tag scale factors}
@@
 The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.
-
 \subsubsection*{\MET resolution and response}
@@
 leads to a 1-10\% uncertainty (depending on category and process)
-
 \subsubsection*{Background normalisation}
@@
 \end{itemize}
-
 \subsection{Shape uncertainties}
 \label{sec:hhh_uncerts_shape}
-
 \subsubsection*{Tau energy scale}
@@
 As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.
-
 \subsubsection*{Jet energy scale}
@@
 Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty
-
 \section{\texorpdfstring{Overview of \AtoZhtolltautau}{Overview of A->Zh->lltautau}}
@@
 \begin{center}
-\includegraphics[width=0.85\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
+\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
 \caption{The 95\% confidence level expected (dashed) and observed (solid)
@@
 More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
+Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
+For the purposes of combining the results with the \Htohhtobbtautau search,
+some of these are correlated between the two analyses.
+This applies to the
+luminosity uncertainty and the uncertainties on b-tagging efficiency
+and light jet mistagging rate.
 
@@
 \label{sec:hhh_results}
-
 \subsection{Signal extraction}
@@
 \begin{equation} \label{eqn:hhh_likelihood}
-\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot \Sigma_j p(~\theta_j|\theta_j)
+\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
 \end{equation}
@@
 Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})
-
 \begin{equation}\label{eqn:hhh_poisson}
@@
 $\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
-REFERENCE are represented by a nuisance parameter $\theta_j$. The signal strength
+\ref{sec:hhh_uncs} are each represented by a nuisance parameter $\theta_j$. The signal strength
 modifier $\mu$ can represent different quantities depending on the normalisation of the 
@@
 
-IMPROVE THIS:
-The second term $p(~\theta|\theta)$ represents the pdf of the uncertainty on the nominal
-value of the nuisance parameter $~\theta$.
+The second term $p(\tilde{\theta}|\theta)$ represents the full set of 
+probability density functions of the uncertainties on the nominal
+values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
+as discussed in section\ref{sec:hhh_uncs}. The functional form of the probability density function
+depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
+For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
+uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
+an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
+yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
+technique. For each nuisance parameter that affects the shape of the fitted distribution, two additional
+templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
+parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
+the nominal and $\pm 1\sigma$ templates. Limitations in event statistics for shape templates
+are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
+shape template are allowed to float within their statistical uncertainty, independent of the other bins. These
+variations are controlled by log-normal constraints in the likelihood function.
 
-To compare the data with the background only and signal + background hypothesis, a test
-statistic $~q_{\mu}$ can be defined. This is a single 
+To compare the data with the background only and signal + background hypotheses, a test
+statistic $q_{\mu}$ can be defined. This is a single 
 number that is used to distinguish between the two hypotheses. The test
@@
 in equation \ref{eqn:hhh_profilelikelihood}.
-
 \begin{equation}\label{eqn:hhh_profilelikelihood}
@@
 
-Describe pdfs
-
-The p-value for $\mu$ and for background-only ($\mu = 0$) can be determined as in equation \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}.
+The probability of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
+and assuming the background-only hypothesis, is given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.
 
 \begin{equation}\label{eqn:hhh_pvaluesig}
-p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \Integral_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
+p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
 \end{equation}
@@
 \begin{equation}\label{eqn:hhh_pvaluebkg}
-1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \Integral_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
+1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
 \end{equation}
 
-$CL_s$ is then defined as (equation \ref{eqn:hhh_cls})
+Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability denstiy functions of $q_{\mu}$ under
+the signal+background and background-only hypotheses.
 
+Using this, $CL_s$ is defined as (equation \ref{eqn:hhh_cls})
 \begin{equation}\label{eqn:hhh_cls}
@@
 said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
-quoted at 95\% confidence level, therefore the upper limit on cross-section times branching ratio
-for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
-equals 0.05. MODIFIED FREQUENTIST APPROACH.
+quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
+%for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
+%equals 0.05. The use of $CL_s$ to set
+The use of $CL_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.
 
-While the distribution of $f(q_{\mu})$ can always be determined by generating toy datasets,
-in the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
+The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
+using toy MC datasets. These datasets are generated from the sum of signal+background or background only expectation respectively. 
+For each toy dataset the nuisance parameters fixed to the best-fit values found in the fit to observed data are taken as a starting
+point, and the effect of systematic uncertainties is then taken into account by varying the nuisance parameters within
+their uncertainty. The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background only)
+can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.
+
+This method of generating toy MC datasets is computationally intensive.
+In the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
 This formula, known as the asymptotic approximation, allows for the calculation
@@
 the properties of the Asimov dataset, a dataset in which the observation in 
-each bin exactly matches the background expectation.
+each bin exactly matches the predictions of the model. This method is used for the analysis
+described in this chapter, removing the need to generate toy datasets.
 
@@
 \begin{center}
-\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-a.pdf}}
-\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-b.pdf}}~\\
-\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-c.pdf}}
+\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_mt_0_shapes_postfit.pdf}}
+\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_mt_1_shapes_postfit.pdf}}~\\
+\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_mt_2_shapes_postfit.pdf}}
 \end{center}
 \caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \mutau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
-scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
+of the \mutau channel. The \Htohhtobbtautau signal for $m_{A} = 300 $GeV at \tanb=2 in the low \tanb~MSSM
+scenario, multiplied by 10, is also overlaid. Note that at low \tanb $m_{A}\neq m_{H}$, $m_{H}$ at the point
+in the MSSM scenario considered is around 316 GeV.}
 \label{fig:hhh_results_mhkinfit_mutau}
@@
 \begin{center}
-\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-a.pdf}}
-\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-b.pdf}}~\\
-\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-c.pdf}}
+\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_et_0_shapes_postfit.pdf}}
+\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_et_1_shapes_postfit.pdf}}~\\
+\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/htt_et_2_shapes_postfit.pdf}}
 \end{center}
 \caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \etau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
-scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
+of the \etau channel. The \Htohhtobbtautau signal for $m_{A} = 300 $GeV at \tanb=2 in the low \tanb~ MSSM
+scenario, multiplied by 10, is also overlaid. Note that at this low value of \tanb $m_{A}\neq m_{H}$, in 
+this case $m_{H}$ is around 316 GeV.}
 \label{fig:hhh_results_mhkinfit_etau}
@@
 
-The model-independent 95\% CL expected and observed upper limits are shown in 
-figure \ref{fig:hhh_results_modelindep}, with figure \ref{fig:hhh_results_modelindep_perchannel}
+The model-independent 95\% CL expected and observed upper limits are shown in the left-hand side 
+panel of figure \ref{fig:hhh_results_modelindep}, with the right-hand side of the same figure
 showing the expected sensitivity per channel. These figures include the contribution from the 
-\tautau channel not described in this thesis. Figure \ref{fig:hhh_results_modelindep} shows that
-the expected upper limit on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
-from 0.2 pb at low mass to 0.4 pb at high mass. From figure \ref{fig:hhh_results_modelindep}
-we can see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
+\tautau channel not described in this thesis. The expected upper limit
+on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
+from 0.2 pb at low mass to 0.4 pb at high mass. We can
+see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
 the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
@@
 \subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
-\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}}
+\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
 \caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
@@
 for the \etau channel and the black line the limit for all three channels combined. Up to around $m_H = 320$ GeV the \mutau channel is the most
-sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
+sensitive, with the \tautau channel being more sensitive at higher masses.}
 \label{fig:hhh_results_modelindep}
@@
 
-FIXME: ALIGNMENT LIMIT
-
 The interpretations are made in the \cosba--\tanb plane. Figure \ref{fig:HhhAndAZh2HDMOverlaid}
@@
 region.
-Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
-interpretation, these are a result of the complex \Htohh branching ratio (ADD FIGURE).
+%Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
+%interpretation, these are a result of the complex \Htohh branching ratio.
 

### 2016-11-05 Hhh/Hhh.tex
Adding latest changes to bbtautau chapter

@@
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. This \Pgt-pair final states studied in this analysis
-are the \etau, \mutau and \tautau channels. The results of this search are model-independent
-upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, which use
-combine all three channels. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
-be covered. In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
+a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis the \etau, \mutau and \tautau final states
+of the \Pgt-pair are studied, these final states are referred to as channels.
+The results of this search are model-independent
+upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
+which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
+be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
+In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
 these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
@@
 The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
-new possibilities for probing the Higgs sector beyond the Standard Model. In some MSSM scenarios, and some more
+new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
 generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
@@
 \cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
-events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
-were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
-in signal regions with multiple jets. The samples binned in jet multiplicity are combined with the
+events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
+were used for the \Wjets and \Zellell backgrounds. This increases the background event statistics
+in regions with multiple jets, which important for this analysis due to the presence of b-jets in the searched-for final state. 
+The samples binned in jet multiplicity are combined with the
 inclusive samples such that the fraction of events with each jet multiplicity is preserved.
@@
 of the two muons originiating from the \PZ have been removed. This technique is also applied to 
-a \ttbar background samples to estimate the \ttbar contamination in the embedded sample. This contribution
+a \ttbar background sample to estimate the \ttbar contamination in the embedded sample. This contribution
 needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
-avoid double counting with the \ttbar monte carlo.
+avoid double counting with the \ttbar \ac{MC}.
 
@@
 \label{sec:hhh_selection}
-A more detailed description of the physics objects used for this analysis is given in chapter FIXME:write object reco section, 
+A more detailed description of the physics objects used for this analysis is given in chapter OBJECTS
 in this section only an overview of the event selection is presented.
@@
 \label{sec:hhh_selection_mutau}
-Events in the \mutau channel are first selected by requiring a muon and a 
-hadronic tau. The first step of this selection is a trigger which requires only a muon
-at L1. At the level of the HLT a hadronic tau is also required. This is reconstructed
-with a simpler version of the PF algorithm, and loose isolation requirements are 
-applied. In addition, loose ID and isolation requirements are applied to the muon at 
-this stage.
+The first step of event selection in the \mutau channel is a trigger 
+which requires only a muon
+at L1. At the level of the HLT a hadronic tau, reconstructed using a simpler version of the
+PF algorithm, is also required. Loose isolation requirements are applied to this hadronic tau, and 
+loose ID and isolation requirements are applied to the muon at this stage.
 
@@
 separated by $\Delta R > 0.5$.
-The muon is required to have a \pT of at 
+The muon is required to have a \pT~of at 
 least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
@@
 criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
-in section OBJECTS, are applied. The hadronic tau must have a \pT of at least
+in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
 20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
@@
 than the signal muon, can be formed. Additional vetos, requiring exactly one muon and 
-exactly zero electrons to pass \pT $>10$ GeV and tight ID and isolation requirements, 
+exactly zero electrons to pass \pT $>10$ GeV and loose ID and isolation requirements, 
 are applied to reduce the \WZ background.
@@
 \label{sec:hhh_selection_etau}
-Events in the \etau channel are selected by requiring an electron and a hadronic tau.
-As for the \mutau channel the first step of this selection is the trigger, which
-requires an electron at L1, and both an electron and a hadronic tau at HLT. The hadronic
-tau is reconstructed in a similar way to the \mutau channel, and loose ID and isolation requirements
-are also applied to the electron.
+Events in the \etau channel are selected using a trigger which requires an electron at L1, and both an electron
+and a hadronic tau at HLT.
+The hadronic
+tau is reconstructed in a similar way as for the trigger in the \mutau channel, and loose ID and isolation requirements
+are also applied to the electron at this stage.
 
-Offline, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
-The electron should have a \pT of at least 24 GeV, $|\eta| < 2.1$, and should
+After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
+The electron should have a \pT~of at least 24 GeV, $|\eta| < 2.1$, and should
 satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
@@
 is taken. Similar additional vetos as in the \mutau channel are applied.
-the event is rejected if an opposite--charge pair of \pT $> 15$ GeV electrons, passing looser ID and
+the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
 isolation requirements than the signal electron requirements can be formed. To reduce the \WZ
-background events that have more than one electron or at least one muon passing \pT $>10$ GeV and tight ID and isolation
+background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
 requirements are rejected.
@@
 
-Figure \ref{fig:Hhh_selection_kinematics_etmt} shows some of the kinematic variables 
-of di-\Pgt candidates in the \etau and \mutau channels
-\begin{figure}[h!]
-\begin{center}
- \subfloat[Electron \pT (\etau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
-  \subfloat[Hadronic \Pgt \pT (\mutau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}
+%Figure \ref{fig:Hhh_selection_kinematics_etmt} shows some of the kinematic variables 
+%of di-\Pgt candidates in the \etau and \mutau channels
+%\begin{figure}[h!]
+%\begin{center}
+% \subfloat[Electron \pT (\etau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
+%  \subfloat[Hadronic \Pgt \pT (\mutau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}
 %  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
@@
 
-\end{center}
-\caption{Plots of electron \pT in the \etau channel and hadronic \Pgt \pT in the \mutau channel.}
-\label{fig:Hhh_selection_kinematics_etmt}
-\end{figure}
+%\end{center}
+%\caption{Plots of electron \pT in the \etau channel and hadronic \Pgt \pT in the \mutau channel.}
+%\label{fig:Hhh_selection_kinematics_etmt}
+%\end{figure}
 
@@
 \label{sec:hhh_selection_categories}
-ADD b-jet plots?
-In both channels an selection on the transverse mass \mT between the electron/muon
+In both channels a selection on the transverse mass \mT~between the electron/muon
 and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
@@
 \end{equation}
-In this eqation \pT is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
-between the light lepton and the missing transverse energy. The \mT distributions for the \etau
+In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
+between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
 and \mutau channels, using the selections as
 described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
-is shown in figure \ref{fig:Hhh_selection_mt}
+are shown in figure \ref{fig:Hhh_selection_mt}.
 
@@
 \end{center}
-\caption{\mT distributions in the \mutau (left) and \etau (right) channels}
+\caption{\mT~distributions in the \mutau (left) and \etau (right) channels}
 \label{fig:Hhh_selection_mt}
@@
 
-In both channels this quantity is required to be smaller than 30 GeV. In events
-where the missing energy and the light lepton are oriented back--to--back, \mT is
+This quantity is required to be smaller than 30 GeV in both channels. In events
+where the missing energy and the light lepton are oriented back--to--back, \mT~is
 large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
-events, as the W is very heavy, the lepton and neutrino are more likely to emitted back--to--back,
-therefore \mT will be large. For \Ztautau and \htotautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
+events, as the W is very heavy, the lepton and neutrino are more likely to be emitted back--to--back,
+therefore \mT~will be large. For \Ztautau and \htotautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
 the neutrinos are more likely to travel in the same direction as the visible decay products of 
@@
 is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
-smaller diboson and single-top backgrounds are drawn together as 'electroweak backgrounds'.
+smaller diboson and single-top backgrounds are combined into the `electroweak' background contribution, drawn in red.
 %In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
@@
 
-After applying the \mT selection, events are divided into three categories to maximise
+After applying the \mT~selection, events are divided into three categories to maximise
 sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
 (at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
+Jets are considered b-tagged if they pass the medium working point of the b-tagging discriminator described in section OBJECTS.
 The 2jet-0tag category does not collect much of the signal and is dominated by 
 backgrounds, the 2jet-2tag category is most sensitive to signal. 
+Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
+channels, illustrates this.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log.pdf}}
+\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log.pdf}}
+\end{center}
+\caption{Number of b-tagged jets in the 2-jet selection of the \mutau (left) and \etau (right) channels. The signal
+at \mH~=$300$~GeV and \tanb~=2, multiplied by a factor of 10, is overlaid on the figures.}
+\label{fig:Hhh_selection_bjets}
+\end{figure}
+
 In signal events, the di--tau pair and di--jet pair 
@@
 125 GeV, requirements are made on the di--jet invariant mass and the di--tau
-invariant mass as reconstructed using the \texttt{SVFit} algorithm (ADD A SECTION ON THIS).
+invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
+a likelihood-based estimate of the di-tau mass using the visible decay products
+of the taus and the reconstructed \MET. The use of this algorithm greatly
+improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
+which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
 By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
@@
 \begin{center}
-\subfloat[$m_{\Pgt\Pgt}$ (\mutau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
-\subfloat[$m_{\Pgt\Pgt}$ (\etau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_et_2012.pdf}}~\\
-\subfloat[$m_{jj}$ (\mutau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
-\subfloat[$m_{jj}$ (\etau channel)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_et_2012.pdf}}
+\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
+\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
 \end{center}
-\caption{Reconstructed di-\Pgt invariant mass (top) and di-jet invariant mass (bottom) in the 2jet-2tag category of the \mutau (left) and \etau (right)
-channels. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in an MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
-One can see that this signal peaks at around 125 GeV.}
+\caption{Reconstructed di-\Pgt invariant mass (left) and di-jet invariant mass (right) in the 2jet-2tag category of the \mutau
+channel. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in the low \tanb~ MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
+In both variables the signal peaks at around 125 GeV.}
 \label{fig:Hhh_selection_masscuts}
@@
 
-\section{Data to \acl{MC} correction factors}
+\section{\acl{MC} to data correction factors}
 \label{sec:hhh_datamc}
 \ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
-and it is therefore important to correct for any mismodelling. The data to \ac{MC} 
+and it is therefore important to correct for any mismodelling. The \ac{MC} to data 
 correction factors used for this are estimated in dedicated control regions.
@@
 A reweighting is applied to make the pile--up distribution in \ac{MC}
-match the distribution observed in data, as described in chapter OBJECT RECO.
+match the distribution observed in data, as described in chapter OBJECTS.
 
@@
 
-For electrons and muons, these scale factors are measured using a 
+For electrons and muons, these efficiencies are measured using a 
 tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
@@
 
-In the \etau channel a data to \ac{MC} scale factor is applied
+In the \etau channel a \ac{MC} to data scale factor is applied
 to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
@@
 $\pi^0$ decay modes by fitting the visible mass of the \Pe+$\Pgt_{h}$ pair
-in $Z\rightarrow\Pgt\Pgt\rightarrow\Pe\Pgt_{h}$ events.
+in events passing the selection of the \etau channel as described in section
+\ref{sec:hhh_selection_etau}, with the 2-jet requirement lifted.
+
+Differences in \MET resolution and response between data and \ac{MC} are accounted for by
+applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter OBJECTS
+gives more details on how these corrections are derived.
 
 To correct for the difference in b--tagging efficiency and light jet mis--tagging
-rates between data and \ac{MC} \pT and $\eta$ dependent scale factors are 
+rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
 derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
-b-/c- jets and light jets. There are multiple possible ways to apply these
-scale factors, for this analysis this is done through a promote/demote method.
+b-/c- jets and light jets. Multiple possible ways to apply these scale factors
+exist, for this analysis this is done through a promote/demote method.
 
@@
 &P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
-\end{align}.
+\end{align}
 In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
@@
 case of this analysis these constraints are
-$m(\Pgt_{1},\Pgt_{2}) = m_{h} = 125 $GeV and
+$m(\Pgt_{1},\Pgt_{2}) = m_{h} = 125 $~GeV and
 $m(b_{1},b_{2}) = m_{h} = 125 $ GeV.
@@
 observable that is varied with respect to the measurement,
-the aim of the fit is to minimise this.
+the aim of the fit is to minimise the sum of these $\chi^2$ terms.
 
@@
 assumed to be measured accurately in comparison with their energy.
-Therefore only the energy is varied in the fit. In addition, we assume
+Therefore only their energy is varied in the fit. In addition, we assume
 that uncertainties in the energy measurement directly translate to
@@
 \begin{align}\label{eqn:kinfit_variation}
-m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}}\notag\\
+m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}})\notag\\
 &= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
 \Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
-&= E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
-&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
+&= - E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
+&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}})
 \end{align}
@@
 \end{equation}
-For each b-jet a $\chi^2$ term is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.
+The $\chi^2$ term for each b-jet is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.
 
 For taus only the visible decay products are measured. Assuming the visible decay products of the \Pgt point in 
-the same direction as the \Pgt, a similar procedure as for the b-jets can be employed to constrain the mass of the second tau
+the same direction as the original \Pgt, a similar procedure as for the b-jets can be employed to constrain the mass of the second tau
 when varying the mass of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.
@@
 where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
-the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET (OBJECT RECO),
+the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET as discussed in the
+OBJECTS section,
 while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets. 
@@
 distribution closer to the true value. From the right hand side of
-figure \ref{fig:kinfitvsmjj} one can see that the mass distribution for
-background events is less affected by the kinematic fit, although due to the
+figure \ref{fig:kinfitvsmjj} we can see that the mass distribution for
+background events is affected less by the kinematic fit, although due to the
 invariant mass constraint the minimum of the reconstructed mass distribution
@@
 \caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
-4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
+4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $~GeV (left) and \ttbar background events (right) in 
 the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
-accuracy of the mean of the mass distribution in signal events.}%FIXME plots need to be remade as the bkg one was never released
-%on the public twiki so can't have the CMS label on
+accuracy of the mean of the mass distribution in signal events.}
 \label{fig:kinfitvsmjj}
@@
 Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
-These are checked against data in dedicated control regions. One such control
-region uses the \emu final state of the taus. In this control region
-a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.
+These are checked against data in dedicated control regions, one such control
+region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
+this control region and applied to the yield estimate from \ac{MC} in the signal region. 
 \subsection{\texorpdfstring{\Wjets}{W + jets}}
 \label{sec:hhh_backgrounds_wjets}
-The \Wjets background is greatly reduced by requiring \mT to
+The \Wjets background is greatly reduced by requiring \mT~to
 be less than 30 GeV. To estimate the remaining contribution
-from \Wjets in the signal region a sideband with \mT greater
+from \Wjets in the signal region a sideband with \mT~greater
 than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
 Contributions from other backgrounds are subtracted 
-from the data in this region, and a high \mT to low \mT
+from the data in this region, and a high-\mT~to low- \mT~
 extrapolation factor is determined from the \Wjets \ac{MC} 
 samples. The yield in the signal region is then the other-background-subtracted
-data yield in the high \mT region multiplied by this extrapolation factor.
-In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
+data yield in the high-\mT~region multiplied by this extrapolation factor.
+In the 2jet-2tag, a slightly different high-\mT~sideband of 60-120 GeV is used 
 to give larger statistics for the \Wjets estimate after other backgrounds are
@@
 A fully data-driven method is used to estimate the QCD background. Data events
-passing the signal region selection cuts, but requiring the di-tau pair to be
-of the same sign, are used for this. Contributions from other backgrounds are 
-subtracted. Because the contribution from opposite- and same-sign QCD are
-not exactly the same an OS/SS ratio of 1.06 is measured using data in which
-the electron/muon isolation requirement was inverted.
+passing the signal region selection cuts, but with the di-\Pgt candidates of
+same sign, are used for this. The contributions from other backgrounds are 
+subtracted, and the contribution from opposite- and same-sign QCD are
+not exactly the same an OS/SS ratio is applied to the data-other backgrounds in the same--sign region.
+The OS/SS ratio is measured using data with the 
+the electron/muon isolation requirements inverted.
 
@@
 The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
-2012 (LUMI POG CITATION?). This uncertainty is applied to all processes in which
+2012. This uncertainty is applied to all processes in which
 the normalisation is estimated using MC samples.
@@
 The b-tag scale factors are varied within their uncertainties to determine the effect
-on the yields of each process. Both a b-tagging uncertainty and a fake mis-tagging
+on the yields of each process. Both a b-tagging uncertainty and a light jet mis-tagging
 uncertainty are obtained by considering the percentage by which these backgrounds
@@
 the recoil correction parameters within their estimated uncertainties. This 
-leads to a 1-10\% uncertainty (depending on category and process)
+leads to a 1-10\% uncertainty, depending on category and process considered.
 \subsubsection*{Background normalisation}
@@
 \item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
-\item \Wjets: As the \Wjets yield is estimated from a high \mT sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty range sfrom 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
+\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
 \item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio.
@@
 \subsubsection*{Jet energy scale}
-The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the (\pT and $\eta$ dependent) uncertainty.
-Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty
+The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty.
+Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.
 \section{\texorpdfstring{Overview of \AtoZhtolltautau}{Overview of A->Zh->lltautau}}
@@
 the 2012 $p-p$ running period of the LHC. In this search the \mumu and \ee final states of the \PZ boson
-and the \emu, \etau, \mutau and \tautau channels of the \htotautau decay, leading to a total of
+and the \emu, \etau, \mutau and \tautau channels of the \htotautau decay are considered, leading to a total of
 eight final states.
@@
 between different final states is possible, events with additional electrons or muons satisfying the
-\pT and $\eta$ requirements are discarded.
+\pT~and $\eta$ requirements are discarded.
 
@@
 
-For signal extraction, the mass of the A boson \mA, reconstructed by combining the
-4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate,as obtained by using the 
+For signal extraction, the mass of the A boson \mA is used. This mass is reconstructed by combining the
+4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate as obtained by using the 
 \texttt{SVFit} algorithm. The expected and observed 95\% confidence level upper limits, for
@@
 \label{sec:hhh_results_extraction}
-The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable.
+The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable in this analysis.
 For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
@@
 \begin{equation} \label{eqn:hhh_likelihood}
-\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
+\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
 \end{equation}
 
-Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})
+Where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson}), with $n_i$ the number of 
+data events, whether observed or pseudo-data, in bin i.
 \begin{equation}\label{eqn:hhh_poisson}
-\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
+\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
 \end{equation}
 
-The first term integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
+The first term of equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
 in all channels and categories. $s$ represents the number of expected signal events
@@
 
-The second term $p(\tilde{\theta}|\theta)$ represents the full set of 
+The second term of equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
 probability density functions of the uncertainties on the nominal
@@
 In this equation $\mu$ is the signal strenght modifier being tested, $\hat{\theta_{\mu}}$ denotes the values of the
-nuisance parameters which maximise the likelihood for that particular $\mu$, while $\hat{mu}$ and $\hat{\theta}$ are
+nuisance parameters which maximise the likelihood for that particular $\mu$, while $\hat{\mu}$ and $\hat{\theta}$ are
 the values of signal strength modifier and nuisance parameters which give the global maximum of the likelihood.
-The requirements on $\mu$ ensure that the signal strenght is non-negative ($ 0 \leq \hat{\mu}$) and that
+The requirements on $\mu$ ensure that the signal strength is non-negative ($ 0 \leq \hat{\mu}$) and that
 a one-sided confidence interval is constructed so as not to allow the observation of  a 
-signal with strength $\hat{mu} > \mu$ to cause rejection of the signal hypothesis ($ \hat{\mu} \leq \mu$).
+signal with strength $\hat{\mu} > \mu$ to cause rejection of the signal hypothesis ($ \hat{\mu} \leq \mu$).
 
-The probability of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
-and assuming the background-only hypothesis, is given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.
+The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
+and assuming the background-only hypothesis, are given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.
 
@@
 
-Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability denstiy functions of $q_{\mu}$ under
+Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
 the signal+background and background-only hypotheses.
@@
 
-The value of $\mu$ for which $CL_s(\mu) \leq \alpha$ then gives the upper limit 
-In the case of the analysis discussed in this chapter, the value of $\mu$ for which the upper 
-limit on cross-section times branching ratio for the \Htohhtobbtautau process reaches $1-\alpha$ is 
-said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
+The value of $\mu$ for which $CL_s{\mu}$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
+confidence level $1-\alpha$. Upper limits at the LHC are generally
 quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
@@
 The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
-using toy MC datasets. These datasets are generated from the sum of signal+background or background only expectation respectively. 
-For each toy dataset the nuisance parameters fixed to the best-fit values found in the fit to observed data are taken as a starting
-point, and the effect of systematic uncertainties is then taken into account by varying the nuisance parameters within
-their uncertainty. The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background only)
+using toy MC datasets. These datasets are generated from the signal+background or background-only expectations respectively. 
+For each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to observed data.
+The rates of each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
+systematic uncertainties is taken into account by sampling a set of pseudo measurements $\tilde{\theta}'$ for each toy, based on the 
+pdf $p(\tilde{\theta}|\theta)$.
+The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background-only)
 can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.
@@
 
-The $m_{H}^{\text{kinfit}}$ distributions in the \mutau and \etau channel 
-are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
+The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to
+observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
 respectively.
@@
 \end{center}
-\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \mutau channel. The \Htohhtobbtautau signal for $m_{A} = 300 $GeV at \tanb=2 in the low \tanb~MSSM
-scenario, multiplied by 10, is also overlaid. Note that at low \tanb $m_{A}\neq m_{H}$, $m_{H}$ at the point
+\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+of the \mutau channel. The \Htohhtobbtautau signal for \mA $= 300 $~GeV at \tanb=2 in the low \tanb~MSSM
+scenario, multiplied by 10, is also overlaid. Note that at low \tanb \mA$\neq$\mH, ~\mH~ at the point
 in the MSSM scenario considered is around 316 GeV.}
@@
 \end{center}
-\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \etau channel. The \Htohhtobbtautau signal for $m_{A} = 300 $GeV at \tanb=2 in the low \tanb~ MSSM
-scenario, multiplied by 10, is also overlaid. Note that at this low value of \tanb $m_{A}\neq m_{H}$, in 
-this case $m_{H}$ is around 316 GeV.}
+\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+of the \etau channel. The \Htohhtobbtautau signal for \mA $ = 300 $~GeV at \tanb=2 in the low \tanb~ MSSM
+scenario, multiplied by 10, is also overlaid. Note that at this low value of \tanb \mA$\neq$ \mH, in 
+this case \mH is around 316 GeV.}
 \label{fig:hhh_results_mhkinfit_etau}
@@
 showing the expected sensitivity per channel. These figures include the contribution from the 
-\tautau channel not described in this thesis. The expected upper limit
+\tautau channel not described in this chapter. The expected upper limit
 on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
@@
 process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
-for the \etau channel and the black line the limit for all three channels combined. Up to around $m_H = 320$ GeV the \mutau channel is the most
+for the \etau channel and the black line the limit for all three channels combined. Up to around \mH$= 320$~GeV the \mutau channel is the most
 sensitive, with the \tautau channel being more sensitive at higher masses.}
@@
 \label{sec:hhh_results_modeldep}
-The results of the analysis are interpreted in two scenarios, the low \tanb MSSM
-scenario, and a type II two--Higgs doublet model (2HDM). 2HDM's are more general
-than the MSSM, are not mativated by supersymmetry, and there are several different types. 
-Of these different classes, type II 2HDM's are most studied
-as the couplings of the MSSM form a subset of the couplings in type II 2HDMs.
+The results of the analysis are interpreted in two scenarios, the low \tanb~MSSM
+scenario, and a type II two--Higgs doublet model (2HDM), both discussed in section THEORY
 
@@
 \label{sec:hhh_results_modeldep_2HDM}
-A 2HDM of type II has more free parameters than a specified MSSM scenario: the physical masses of the Higgs bosons (\mh, \mH,
+NOTE: move description of 2HDM to theory section + expand
+A 2HDM of type II has more free parameters than specific MSSM benchmark scenarios: the physical masses of the Higgs bosons (\mh, \mH,
 \mA, \mHplus), the ratio of the vacuum expectation values of the two Higgs doublets (\tanb),
@@
 
-The interpretations are made in the \cosba--\tanb plane. Figure \ref{fig:HhhAndAZh2HDMOverlaid}
+The interpretations are made in the \cosba--\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
 shows the observed and expected exclusion at 95\% confidence level for the \Htohh
@@
 of all particles are exactly standard model--like. This is reflected in the \Htohh and \AtoZh branching ratios, 
-which both vanish as \cosba approaches 0. This leads to the corridor of non--exclusion down the 
-centre of the plots in figure \ref{fig:HhhAndAZh2HDMOverlaid}. Additionally,
+which both vanish as \cosba~approaches 0. This leads to the corridor of non--exclusion down the 
+centre of the plots in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
 as the couplings of \PHiggslight to pairs of b--quarks and $\Pgt$ leptons are porportional 
@@
 and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non--exclusion
-at \cosba $ > 0$ and low \tanb in the \AtoZh figure. A similar corridor is starting
+at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
 to become visible in the $\sigma \times BR$ structure of the \Htohh interpretation, but
-the analysis is not yet sensitive enough to actually see a full--blown corridor in this
+the analysis is not yet sensitive enough to actually observe this corridor.
 region.
@@
 on the cross--section times branching ratio of the searched-for process.
-Regions of the \cosba-\tanb plane where the cross--section times branching
+Regions of the \cosba-\tanb~plane where the cross--section times branching
 ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
@@
 
-\subsubsection{Interpretation in the low \tanb MSSM scenario}
+\subsubsection{Interpretation in the low \tanb~MSSM scenario}
 \label{sec:hhh_results_modeldep_lowtb}
-The low \tanb MSSM scenario, as discussed in section FIXME: write theory section that mentions this
-is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb values
+The low \tanb~MSSM scenario, as discussed in section THEORY
+is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb~values
 as low as 1.
@@
 The left-hand side panel of figure \ref{fig:HhhAndAZhlowtanb} shows the cross-section times branching ratio
-of the \Htohhtobbtautau process in the MSSM low \tanb scenario. Comparing these values 
-to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} one
-can see that the cross-section times branching ratio in this model is, with exception of a few small 
+of the \Htohhtobbtautau process in the low \tanb~ MSSM scenario. Comparing these values 
+to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} we 
+can see that the cross-section times branching ratio in this model is, with exception of a few very small 
 areas, lower than the upper limits set by this analysis. This analysis on its own is
-therefore not sensitive enough to exclude any of the \mA-\tanb region in this model. Note that
-at low \tanb ~ \mA and \mH are degenerate, and therefore \mH is not in the studied range of $260-350$ GeV
-throughout the entire \mA-\tanb plane shown here.
+therefore not sensitive enough to exclude any of the \mA-\tanb~region in this model. Note that
+at low \tanb ~ \mA$\neq$ \mH, and therefore \mH~is not in the studied range of $260-350$ GeV
+throughout the entire \mA-\tanb~plane shown here.
 
-The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb region
+The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb~region
 in this model by itself. The expected and observed 95\% CL exclusion contours are overlaid 
-on the cross-section times branching ratio for this process in the low \tanb MSSM scenario in the right-hand side panel 
-of figure \ref{fig:HhhAndAzhlowtanb}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
+on the cross-section times branching ratio for this process in the low \tanb~MSSM scenario in the right-hand side panel 
+of figure \ref{fig:HhhAndAZhlowtanb}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
 near \mA $ = 350$ GeV arises from the fact that near this mass the decay $\PHiggsps \rightarrow t\bar{t}$ becomes
@@
 very sensitive in this model. Combining the two analyses we do see that a slightly larger amount
-of the \mA-\tanb plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
-described for figure \ref{fig:AZhlowtanbOverlaid} are also visible in this figure. A small region of phase
-space, at low \mA and low\tanb predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
+of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
+described for the plot on the right-hand-side of figure \ref{fig:HhhAndAZhlowtanb} are also visible in this figure. In a small region of phase
+space, at low \mA~and low\tanb, this scenario predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
 This region is therefore excluded, this is indicated by the red band.
@@
 bounded by the red line is the region of phase space where \mh $\neq 125 \pm 3$ 
-GeV and is therefore not accessible.}
+GeV and is therefore excluded.}
 \label{fig:HhhAZhMSSM2HDM}

### 2016-11-09 Detector/Detector.tex
Adding more detector stuff

@@
-\chapter{The \acs{CMS} experiment and the \acs{LHC}}
+\chapter{The \acs{LHC} and the \acs{CMS} experiment}
 \label{chap:CMSLHC}
@@
 
+The \ac{LHC} does not operate on its own, a chain of accelerators leads
+the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
+of the \ac{CERN} accelerator complex.
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
+\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
+\label{fig:lhc_schematic}
+\end{figure}
 Protons originate from hydrogen gas, where electrons are stripped off the 
@@
 reached the protons are injected into the \ac{LHC}, where they are further accelerated to 
-the required centre of mass energy. lbha blah blah. The beams collide at four points
+the required centre of mass energy. The beams collide at four points
 around the ring, where the collisions are recorded by the ATLAS, CMS, ALICE, and LHCb detectors.
 
-As the processes the \ac{LHC} was built to study have a small cross-section
-compared with the total proton-proton inelastic cross-section (add figure!), the
-LHC operates at high instantaneous luminosity. blah blah blah blah
+The processes the \ac{LHC} was built to study have a small cross-section
+compared with the total proton-proton inelastic cross-section, as seen from figure
+\ref{fig:stirling_xs}. For example, the production cross-section of the
+standard model Higgs boson is 9-10 orders of magniuted smaller than the total p--p cross section.
 
-After an initial testing phase, the \ac{LHC} becan its first physics run in May 2010 with 
+\begin{figure}[h!]
+\includegraphics[width=0.5\textwidth]{./Detector/Plots/crosssections2013.jpg}
+\caption{Total proton-proton cross section, and the cross-sections
+for several processes studied at the LHC \cite{stirling-crosssection}.
+The cross sections of these processes
+are often many orders of magnitude smaller than the total p--p cross section.}
+\label{fig:stirling_xs}
+\end{figure}
+
+In order to be able to study these relatively rare processes, 
+the LHC operates at high instantaneous luminosity, defined as in equation
+\ref{eqn:CMSLHC_luminosity}. 
+\begin{equation}\label{eqn:CMSLHC_luminosity}
+\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F
+\end{equation}
+
+In this equation, $N_b$ is the number of protons per bunch, $n_b$ the number of
+bunches per beam, $f_{\text{rev}}$ the revolution frequency, $\gamma$ the 
+Lorentz factor, $\epsilon_n$ the normalised beam
+emittance, $\beta^{*}$ the $\beta$-function at the interaction point and F a reduction
+factor due to the crossing angle.
+
+After an initial testing phase, the \ac{LHC} began its first physics run in May 2010 with 
 a centre of mass energy of 7 TeV. The CMS experiment recorded an integrated luminosity of 45 pb$^{-1}$
@@
 
-In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV
+In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV, and during 
+this year 4.2 fb$^{-1}$ was delivered. Collisions at a centre-of-mass energy of 13 TeV continued
+in 2016, when a total of 41.1 fb$^{-1}$ was delivered. 
+The integrated luminosity as a function of time is shown in figure \ref{fig:CMSLHC_intlumi},
+separated by running year.
+
+\begin{figure}[h!]
+\includegraphics[width=0.85\textwidth]{./Detector/Plots/int_lumi_cumulative_pp_2.pdf}
+\caption{Cumulative integrated luminosity for p--p collisions at the LHC, separated
+by running year \cite{cms-lumi-public}.}
+\label{fig:CMSLHC_intlumi}
+\end{figure}
+
+The data-taking efficiency of CMS is not 100\%, for example the detector might be
+switched off for part of the time collisions are ongoing. In 2012, the data-taking 
+efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.4 \%
+
+From all of the data that is recorded, a subset is used for analyses. Data is 
+certified as good for use in analyses if it is known that all relevant subdetectors
+were functioning correctly. The certification efficiency in 2012 was 90.4\%,
+leading to an integrated luminosity of 19.7 fb$^{-1}$ for which all subdetectors
+were working well, in 2015 it was 60.4 \%, leading to 2.3 fb$^{-1}$ of analysable data
+for which the full detector was operational. An additional 0.6 fb$^{-1}$ was taken
+with the magnet switched off. The certification efficiency for the full 2016 p--p running period was 95.4\%.
+
+The \ac{LHC} was designed for a nominal
+peak luminosity of $10^{32}$cm$^{-2}$s$^{-1}$ for proton-proton collisions. In 2012 peak
+luminosities of $7.7*10^{33}$cm$^{-2}$s$^{-1}$ were reached, with the peak luminosity in
+2015 being $5.1*10^{33}$cm$^{-2}$s$^{-1}$. Since July 2016
+the \ac{LHC} has been operating at instantaneous luminosities upwards of the 
+design luminosity, with peak luminosities of $1.5*10^{32}$cm$^{-2}$s$^{-1}$ reached
+in October 2016.
+
+Due to the high operating luminosity, multiple proton-proton collisions per 
+bunch crossing are likely to occur. The average number of interactions
+per bunch crossing is X in 2012, Y in 2015, Z in 2016. Additional 
+interactions on top of events of interest are referred to as pile-up.
+
+\section{The \acs{CMS} detector}
+\label{sec:CMSLHC_CMS}
+To meet the demands of the \ac{LHC} physics programme, the
+ \ac{CMS} detector was designed to be very perfomant in searches
+for physics at the TeV scale and to be able to 
+function in the challenging high-luminosity environment.
+The detector is 21.6 m long, 14.6 m in diameter, and weighs
+12500 tonnes \cite{cms-jinst}. It consists of several subdetectors, as illustrated
+in figure \ref{fig:cms_detector}. Surrounding the interaction
+point is the silicon tracker, a cylinder 5.8 m in lenght and 2.6 m in 
+diameter. Surrounding the silicon tracker
+the lead-tungstate \ac{ECAL} is found, which in turn is enclosed
+by a brass scintilator \ac{HCAL}.
+
+The tracking and calorimeter systems are surrounded by a superconducting
+solenoid, 13 meter long and 6 meter in diameter and operating at 3.8 Tesla.
+Charged particles are bent in this magnetic field, allowing for precise 
+measurement of their momentum. Gaseous muon detectors are embedded in the 
+iron return yoke of the solenoid.
+
+For the measurement of physical quantities, \ac{CMS} uses a coordinate
+system with the origin centred at the nominal collision point
+inside the experiment. The y-axis points vertically upward, the x-axis
+points radially inward toward the centre of the \ac{LHC} ring. The z-axis
+points along the beam direction. As such the transverse momentum and energy, 
+\pT and \ET are measured from the x- and y- components of the momentum and energy.
+The azimuthal angle $\phi$ is measured in the x-y plane with respect to the x-axis, 
+the polar angle $\theta$ measured with respect to the z-axis. A coordinate
+more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$.
+Distances in the $\eta-\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.
+
+The subsystems of the \ac{CMS} detector will be described in more detail in the 
+next sections.
+
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
+\caption{A blow-up view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
+different sub-parts of the detector.}
+\label{fig:cms_detector}
+\end{figure}
+
+\subsection{Tracker}
+\label{sec:CMSLHC_CMS_tracker}
+The tracker \cite{cms-jinst} is the subdetector closest to the interaction point. It
+is used for accurate reconstruction of charged particle trajectories and 
+the precise reconstruction of secondary vertices, which are important to be
+able to indentify heavy-flavour particles. This means a small impact parameter
+resolution needs to be achieved, for which a highly granular system is required. 
+Due to the large number of particles emerging from 
+each collision, an average of 1000 per bunch crossing (every 25 ns) at LHC design operation, the 
+system also needs to be fast-responding in order to reconstruct trajectories accurately.
+At the same time, this large particle flux calls for a 
+radiation-hard design that is able to survive in this harsh environment
+for a longer period of time. These requirements motivate the use of a silicon tracking
+system. When a charged particle passes through the silicon, an electron-hole pair
+is created, which drift under an applied electric field and produce a current
+that can be read out. %LEARN A BIT MORE ABOUT THIS
+
+The tracker provides coverage up to $|\eta| < 2.5$ and consists of
+several different components. A schematic of the tracking detector is given
+in figure \ref{fig:CMS_tracker}. The part of the tracking system
+closest to the interaction point is the silicon pixel detector, which 
+consists of 3 layers of pixels in the barrel of the detector, with 
+2 pixel endcap disks. The barrel layers sit at radii of 4.4, 7.3 and 10.2 cm 
+and extend up to $z=\pm 26.5$ cm, with the disks placed at $z=\pm 34.5$ cm and
+$z=\pm 46.5$ cm. The pixel detector consists of 66 million silicon pixels, each
+$100 \mu m \times 150 \mu m$ in size. The choice of this pixel size is driven
+by the achievable spatial resolution, which is $15-20 \mu m$ in the $r$ and $z$ directions.
+This allows for 3D vertex reconstruction. With this layout, the pixel tracker
+provides 3 precise position measurements along each charged particle trajectory.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.9\textwidth]{./Detector/Plots/Tracker.png}
+\caption{Schematic of the CMS tracker in the r-z plane, indicating the
+positions of the pixel and strip detectors \cite{cms-jinst}. Each line 
+on the plot represents a detector module}
+\label{fig:CMS_tracker}
+\end{center}
+\end{figure}
+
+Beyond the pixel detector the tracking system is made up of a silicon
+strip detector consisting of over 9 million multiple different subsystems. The first part of the
+silicon strip tracker consists of \ac{TIB} and \ac{TID}, providing 4 layers of
+silicon strip detectors in the barrel plus 3 disks at both ends. These two systems
+extend out towards a radius of 55 cm. The barrel layers and disks each consist
+of silicon strips which are 10 cm long, $80-141\mu m$ wide and $320 \mu m$ thick. The \ac{TIB} and \ac{TID}
+provide 4 measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu m$.
+The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of 6 layers of silicon strip sensors extending
+up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500 $\mu m$ thick, around 25 cm long and 122-183 $\mu m$ 
+wide and this subdetector provides 6 measurements of $r$ and $\phi$, with a resolution
+of 35-53 $\mu m$. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
+consisting of 9 disks of strips.In the \ac{TEC}, the thickness ranges from 320-500 $\mu m$ and the the strip width ranges from $97-184 \mu m$.
+In this way this part of the system provides up to 9 $\phi$ measurements.
+
+Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
+of 100 mrad, in order to provide measurements of the $z-$ coordinate in the barrel. This is achieved with a resolution of 230-530 $\mu m$.
+
+\subsection{ECAL}
+\label{sec:CMSLHC_CMS_ecal}
+The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
+made of nearly 70000 lead tungstate (PbWO$_4$) crystals. It has very
+good energy resolution ETC ETC. %Lead tungstate crystals were a good 
+%choice for the CMS \ac{ECAL}, satisfying the requirements of the 
+%LHC and the detector. 
+Despite being further away from the interaction
+point than the tracker, the materials in other parts of the detector
+still need to be radiation hard. In order to be able to place
+the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
+had to be constructed, and to provide excellent resolution a 
+highly granular system had to be designed. The short radiation
+length and small moli\'ere radius of lead tungstate %NEED TO FIND OUT ABOUT THOSE!
+combined with its radiation hardness and the short scintillation decay
+time in these crystals motivate the choice of lead tungstate.
+
+Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
+the geometry. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
+covers the pseudorapidity range up to $|\eta|<1.479$, with
+crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
+provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
+Each endcap is divided into two halves. In front of the endcaps 
+the preshower detector, covering $1.653<|\eta|<2.6$ is a sampling
+calorimeter whose main use is to neutral pions in the endcaps. Additionally
+it helps electron identification and improves the resolution
+of position determination. The preshower consists
+of lead radiators to initiate the shower, with silicon sensors
+measuring the deposited energy and shower profiles. %Too copied, improve
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.9\textwidth]{./Detector/Plots/ECAL.png}
+\caption{Layout of the \ac{ECAL}, indicating the position of the
+different components \cite{cms-jinst}.}
+\label{fig:CMS_ECAL}
+\end{center}
+\end{figure}
+
+\subsection{HCAL}
+\label{sec:CMSLHC_CMS_hcal}
+Figure \ref{fig:CMS_HCAL} shows an illustration of the \ac{HCAL}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.9\textwidth]{./Detector/Plots/HCAL.png}
+\caption{Illustration of the \ac{HCAL}, indicating the geometry
+of the detector \cite{cms-jinst}.}
+\label{fig:CMS_HCAL}
+\end{center}
+\end{figure}
+
+\subsection{Muon system}
+\label{sec:CMSLHC_CMS_muons}
+
+A cross-section of one quadrant of the detector, indicating
+the positions of the muon systems, is shown in figure \ref{fig:CMS_MuonSystem}.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystem.png}
+\caption{Cross-section of one quadrant of the CMS detector, indicating
+the positions of the different muon system components \cite{cms-tdr-vol1}.}
+\label{fig:CMS_MuonSystem}
+\end{center}
+\end{figure}
+%Because of the uncertainty in the eventual background rates and in the ability of the muon system to measure the correct beam-crossing time when the LHC reaches full luminosity, a com- plementary, dedicated trigger system consisting of resistive plate chambers (RPC) was added in both the barrel and endcap regions.
+The RPCs provide a fast, independent, and highly-segmented trigger with a sharp pT threshold over a large portion of the rapidity range (|η| < 1.6) of the muon system.
+The RPCs are double-gap chambers, operated in avalanche mode to ensure good operation at high rates.
+They produce a fast response, with good time resolution but coarser position reso- lution than the DTs or CSCs.
+They also help to resolve ambiguities in attempting to make tracks from multiple hits in a chamber.
+
+\subsection{Triggering}
+\label{sec:CMSLHC_CMS_trigger}
+
+\subsection{Data processing}
+\label{sec:CMSLHC_CMS_dataproc}

### 2016-11-23 Detector/Detector.tex
Adding more detector stuff

@@
 
-\subsection{ECAL}
+The tracker will be upgraded during the extended year-end technical stop in early 2017. %or just replaced?
+
+\subsection{\acl{ECAL}}
 \label{sec:CMSLHC_CMS_ecal}
 The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
-made of nearly 70000 lead tungstate (PbWO$_4$) crystals. It has very
-good energy resolution ETC ETC. %Lead tungstate crystals were a good 
-%choice for the CMS \ac{ECAL}, satisfying the requirements of the 
-%LHC and the detector. 
+made of nearly 76000 lead tungstate (PbWO$_4$) crystals. It has very
+good energy resolution, is highly granular and fast-responding, which
+are all needed to be able to detect $H\rightarrow \gamma\gamma$ decays.
+
 Despite being further away from the interaction
@@
 had to be constructed, and to provide excellent resolution a 
-highly granular system had to be designed. The short radiation
-length and small moli\'ere radius of lead tungstate %NEED TO FIND OUT ABOUT THOSE!
-combined with its radiation hardness and the short scintillation decay
-time in these crystals motivate the choice of lead tungstate.
+highly granular system had to be designed. The lead tungstate crystals have a 
+radiation length of 0.89 cm, a Moli\'ere radius of 2.2 cm, and 80\% of the light
+from the crystals is emitted in 25 ns. This short radiation
+length, small Moli\'ere radius and short scintillation decay time combined
+with the radiation hardness of the material motivate the choice of lead tungstate.
+
+%Moliere radius: characteristic constant of a material giving scale of transverse dimenstion
+%of fully contained EM showers. It is the radius of a cylinder containing on average 
+%90pct of the shower's energy deposition. Related to radiation length as 
+%molrad approx 0.0265X0 (Z+1.2) with Z the atomic number.
+%Radiation length: mean distance over which a high energy electron
+%loses all but 1/e of its energy by bremmstrahlung and 7/9 of th emean free path for pair production by 
+%a high energy photon.
+
+When a high energy electron or photon enters a crystal, it starts a
+shower producing a cascade of lower energy particles. Electrons lose
+energy through bremsstrahlung, with photons undergoing $\Pe^+ \Pe^-$ 
+pair production. The shower continues until the photon energy drops below the 
+$\Pe^+\Pe^-$ pair production threshold, and ionisation 
+starts to dominate for electrons. The shower ionises the crystals, 
+which return to their normal state by emitting scintillation light. 
+As the crystals are 25.8 radiation lengths long, most of the shower
+is contained inside them.
 
@@
 Each endcap is divided into two halves. In front of the endcaps 
-the preshower detector, covering $1.653<|\eta|<2.6$ is a sampling
-calorimeter whose main use is to neutral pions in the endcaps. Additionally
+the preshower detectors, covering $1.653<|\eta|<2.6$ is a sampling
+calorimeter whose main use is to indentify neutral pions in the endcaps. Additionally
 it helps electron identification and improves the resolution
-of position determination. The preshower consists
-of lead radiators to initiate the shower, with silicon sensors
-measuring the deposited energy and shower profiles. %Too copied, improve
+of position determination. Each of the two preshower detectors consist
+of two layers of lead radiators to initiate the shower, with silicon sensors
+placed after each layer of radiators to measure the deposited energy. The 
+total thickness of the preshower comprises 3 radiation lenghts.
 
@@
 
-\subsection{HCAL}
+To preserve the energy resolution, the \ac{ECAL} crystal and
+photodetector temperatures need to be kept stable within $\pm 0.05^o$C
+as the number of scintillation photons emitted by the crystals,
+and the amplification of the photodetectors are temperature dependent.
+The nominal operating temperature, $18^o$C, is ensured by 
+supplying the detector with water at this temperature.
+
+To record the light yield of the crystals, amplifying photodetectors
+need to be used. In the \ac{EB} avalance photodiodes are employed
+for this, with vacuum phototriodes used in the \ac{EE}.
+
+The energy resolution of the \ac{ECAL} can be parameterised as in
+equation \ref{eqn:ecalres}.
+
+\begin{equation}\label{eqn:ecalres}
+\frac{\sigma}{E} = \sqrt{(\frac{S}{\sqrt{E}})^2+(\frac{N}{E})^2+C^2}
+\end{equation}
+
+Where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
+The stochastic term arises from fluctuations in lateral shower containment and 
+fluctuations in scintillation, the noise term due to noise from the electronics
+and additional particles in the event, and the constant term comes
+from calibration errors, and non-uniformity of longitudinal response.
+
+The values of $S$, $N$ and $C$ have been measured in an electron
+test-beam, without a magnetic field or material in front of the \ac{ECAL}. These
+amounted to $S = 0.028$ GeV$^{0.5}$, $N = 0.12$ GeV, $C= 0.003$.
+
+\subsection{\acl{HCAL}}
 \label{sec:CMSLHC_CMS_hcal}
-Figure \ref{fig:CMS_HCAL} shows an illustration of the \ac{HCAL}.
+The \ac{ECAL} is surrounded by the \ac{HCAL}, important for the
+measurement of the energies of strongly interacting particles. As
+the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
+starting at a radius of 2.95 m the barrel region of the \ac{HCAL} consists
+of the \ac{HB}, which sits inside the magnet coil, and the \ac{HO}, sitting outside it, 
+to complement the \ac{HB}. The \ac{HB} and \ac{HO}  provide coverage up to $|\eta|<1.3$, 
+beyond which they are complemented by the \ac{HE} and the \ac{HF}. The \ac{HE} provides
+coverage between $1.3<|\eta|<3$ with the \ac{HF} extending this coverage up to $|\eta| = 5.2$
+The locations of the different subcomponents of the \ac{HCAL} are shown
+in figure \ref{fig:CMS_HCAL}.
 
@@
 \end{figure}
+
+The \ac{HB} is a sampling calorimeter made of brass absorber
+plates with
 

### 2016-11-23 Detector/Detector.tex
More HCAL stuff

@@
 
-The \ac{HB} is a sampling calorimeter made of brass absorber
-plates with
+The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
+plates with tiles of plastic scintillator as the active material. The tiles 
+are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
+beyond this range.
+The light from each tile is collected with a wavelength-shifting fibre, 
+which is eventually read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
+has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
+sufficient to identify for example late-starting showers. The \ac{HO}, sitting
+outside of the magnet and using the coil as an additional absorber, extends the 
+thickness to at least 11.8 interaction lenghts. 
+The active material again consists of plastic scintillator tiles which roughly
+map the granularity of the tiles in the \ac{HB}, read out by feeding the light
+to a hybrid photodiode via wavelength shifting fibres.
+%WTF: wavelength-shifting fibres
+
+The \ac{HF}, providing coverage in the very forward region, is 
+subjected to large radiation doses, requiring an extremely
+radiation hard active material. For this reason quartz
+fibres are used as active material. These fibres are embedded
+in the steel absorber structure. Charged particles from the
+shower initiated in the steel generate Cherenkov light in 
+the quartz fibres, which is read out by photomultiplier tubes.
+%Half of the fibres run over the full depth of the absorber
+%while the other half starts at a depth of 22 cm, this is
+%to distinguish electrons and photons (which deposit a large
+%fraction of their energy in the first 22cm) from hadrons.
+
+HCAL RESOLUTION!
 
@@
 \label{sec:CMSLHC_CMS_muons}
+One of the main physics goals of the \ac{CMS} experiment
+at design was to search for $H\rightarrow ZZ\rightarrow 4\mu$ decays. Muons
+suffer less from radiative losses in the tracker material, which means the most accurate
+4-body mass can be constructed when searching for muon final states.
+After discovery of the Higgs boson, the ZZ channel remains important
+for Higgs measurements, while many \ac{BSM} searches make use 
+they
 

### 2016-11-25 Detector/Detector.tex
Bit more on the trigger

@@
 
-The tracker will be upgraded during the extended year-end technical stop in early 2017. %or just replaced?
+The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. %or just replaced?
 
@@
 HCAL RESOLUTION!
+%UPGRADE
+During LS1, the \ac{HO} and \ac{HF} pmts were replaced
 
@@
 suffer less from radiative losses in the tracker material, which means the most accurate
-4-body mass can be constructed when searching for muon final states.
-After discovery of the Higgs boson, the ZZ channel remains important
-for Higgs measurements, while many \ac{BSM} searches make use 
-they
+4-body mass can be constructed when using the dimuon final state of the $Z$'s.
+Since the discovery of the Higgs boson the ZZ channel has continued to be an important
+final state for Higgs measurements, at the same time many \ac{BSM} searches also make use of 
+signatures with muons in the final state.
+All of this means that good muon identification efficiency and precise muon momentum resolution
+are very important. The \ac{CMS} muon system is made up out of three different subsystems which
+are all necessary to ensure the identification requirements can be met. It is located
+outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
+In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
+the \ac{CSC} covering the $1.2<|\eta|<2.4$ region. The \ac{RPC}, covering the same
+regions as both \ac{DT} and \ac{CSC}, is used as a dedicated triggering system.
 
 A cross-section of one quadrant of the detector, indicating
-the positions of the muon systems, is shown in figure \ref{fig:CMS_MuonSystem}.
+the positions of the \ac{DT},\ac{CSC} and \ac{RPC}, is shown in figure \ref{fig:CMS_MuonSystem}. 
 \begin{figure}[h!]
 \begin{center}
-\includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystem.png}
+\includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystemUpgrade.png}
 \caption{Cross-section of one quadrant of the CMS detector, indicating
-the positions of the different muon system components \cite{cms-tdr-vol1}.}
+the positions of the different muon system components \cite{cms-muon-upgrade}. The 
+fourth muon endcap stations were extended during \ac{LS1}, in Run 1 only the lower
+part existed.}
 \label{fig:CMS_MuonSystem}
@@
 \end{figure}
+
+The \ac{DT} consists of
+
+%UPGRADE
+During LS1, the endcaps of the muon system were upgraded. Each endcap received an additional muon station, extending ME/4 (figure \ref{fig:CMS_MuonSystem}) out towards
+$R\approx 700 $cm, in line with the other three muon stations \cite{cms-muon-upgrade}.
 %Because of the uncertainty in the eventual background rates and in the ability of the muon system to measure the correct beam-crossing time when the LHC reaches full luminosity, a com- plementary, dedicated trigger system consisting of resistive plate chambers (RPC) was added in both the barrel and endcap regions.
@@
 
-\subsection{Triggering}
+\subsection{Triggering and data processing}
 \label{sec:CMSLHC_CMS_trigger}
+When the \ac{LHC} is operating under standard conditions, protons are collided at a rate
+of 40 MHz. This rate is too high for the \ac{DAQ} system to read out every event. In
+addition this high collision rate produces such a large number of events that it would
+not be feasible to write every single event, with sizes of around 1 MB, to tape. A trigger
+system is therefore used to select events of interest for study, which reduces the rate
+at which events are written to disk to  $\mathcal{O}(1 \text{ kHz})$.
 
-\subsection{Data processing}
-\label{sec:CMSLHC_CMS_dataproc}
+The trigger system consists of two stages: the \ac{L1} trigger, which only makes use of
+front-end electronics 
+and reduces the event rate from 40 MHz to around 100 kHz, and the
+\ac{HLT}, which runs on a computer farm with around 13000 CPU cores \cite{cms-trigger}.
+During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
+replaced by a completely upgraded system, which provides amongst others 
+improved object isolation, hadronic tau identification, muon \pT resolution and
+jet finding.
+
+An overview of the data flow in the \ac{L1} trigger is given in figure \ref{fig:CMS_Trigger}.
+The \ac{L1} trigger only makes use of information from the calorimeters and the muon systems.
+The calorimeter trigger starts from \ac{HCAL} and \ac{ECAL} energy deposits, 
+which are fed to the first layer of the trigger. This layer maps onto
+columns of the detector, receiving data from many bunch crossings. These data are passed
+on to the second layer of the trigger in a way that bundles data from a single bunch crossing, but
+different columns of the detector, to be processed on one node in the second layer of the
+trigger. In this step basic object identification is performed.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./Detector/Plots/CMSTrigger.png}
+\caption{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-upgrade}.}
+\label{fig:CMS_Trigger}
+\end{center}
+\end{figure}

### 2016-11-26 Detector/Detector.tex
Adding more detector bits

@@
 the required centre of mass energy. The beams collide at four points
-around the ring, where the collisions are recorded by the ATLAS, CMS, ALICE, and LHCb detectors.
+around the ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
+CMS\cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
 
@@
 
-The energy resolution of the \ac{ECAL} can be parameterised as in
-equation \ref{eqn:ecalres}.
+The energy resolution of the \ac{ECAL} can be parameterised as
 
 \begin{equation}\label{eqn:ecalres}
-\frac{\sigma}{E} = \sqrt{(\frac{S}{\sqrt{E}})^2+(\frac{N}{E})^2+C^2}
+\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplusC},
 \end{equation}
 
-Where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
+where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
 The stochastic term arises from fluctuations in lateral shower containment and 
@@
 test-beam, without a magnetic field or material in front of the \ac{ECAL}. These
-amounted to $S = 0.028$ GeV$^{0.5}$, $N = 0.12$ GeV, $C= 0.003$.
+amounted to $S = 0.028$ GeV$^{\frac{1}{2}}$, $N = 0.12$ GeV, $C= 0.003$.
+%S = 2.83 %pm 0.03%, C = 0.26% pm 0.04%
 
@@
 
+The energy resolution of the \ac{HCAL} for single charged pions 
+was measured in a test beam \cite{cms-hcalecal}
+and can be parameterised as
+
+\begin{equation}\label{eqn:hcal_res}
+\frac{\sigma}{E} = \frac{S}{\sqrt{E}} \bigoplus C,
+\end{equation}
+
+where $S$ is the stochastic term, found to be 94.3\% %pm 1.2
+and $C$ is the constant term, measured to be 8.4\% %pm 1.0
 HCAL RESOLUTION!
@@
 In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
-the \ac{CSC} covering the $1.2<|\eta|<2.4$ region. The \ac{RPC}, covering the same
-regions as both \ac{DT} and \ac{CSC}, is used as a dedicated triggering system.
+the \ac{CSC} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
+regions as both \ac{DT} and \ac{CSCs}, is used as a dedicated triggering system.
 
 A cross-section of one quadrant of the detector, indicating
-the positions of the \ac{DT},\ac{CSC} and \ac{RPC}, is shown in figure \ref{fig:CMS_MuonSystem}. 
+the positions of the \ac{DT},\ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
+The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1}, providing
+additional layers of \ac{CSCs} and \ac{RPCs}.
+\ac{LS1}.
 \begin{figure}[h!]
@@
 
-The \ac{DT} consists of
+The \ac{DT} consists of layers of drift cells with a cross-section of $4.2 \times 1.3$ cm and
+2.4 m long. The cells are filled with a mixture of %85\% 
+Argon and carbon di-oxide gas.
+Muons passing through the chamber ionise the gas, freeing electrons
+which drift towards the anode wire running along the centre of the tube-shaped cell. 
+This gives rise to an electric signal. There are 4 \ac{DT} stations in each wedge of 
+the detector, each in turn consisting of 8 to 12 layers of drift tubes. Some of
+these layers are oriented parallel to the beam line, providing a measurement of $\phi$.
+There are also layers oriented orthogonal to the beam line, which give a measurement
+of the z-coordinate. Measurements of the spatial resolution were made
+during proton--proton running of the \ac{LHC} in 2010.
+The spatial resolution of the \ac{DT} is 80-120 $\mu$m per chamber for
+measurements in the $\phi$ direction, with the resolution of the $z$ measurement
+is 130-400 $\mu$m\cite{cms-muon-7tev}.
+%Drift lines distorted by magnetic field parallel to the wires
 
-%UPGRADE
-During LS1, the endcaps of the muon system were upgraded. Each endcap received an additional muon station, extending ME/4 (figure \ref{fig:CMS_MuonSystem}) out towards
-$R\approx 700 $cm, in line with the other three muon stations \cite{cms-muon-upgrade}.
+In the endcaps, where the muon rate is higher, the \ac{CSCs} provide
+measurements of the muon track. These detectors are radiation-hard,
+and have a fast response and fine segmentation.
+Each of the CSC modules is a wedge-shaped
+multi-wire proportional chamber %WTF
+with 6 gaseous chambers bounded by cathode planes, with
+sensitive strips placed on these plates in the
+radial direction, to measure the coordinate in the  $r-\phi$ plane
+of the muons. Anode wires in between the cathode planes
+run along the $\phi$ direction and provide a measurement of
+$\eta$. The resolution of the $r-\phi$ measurement is 40-120 $\mu$m \cite{cms-muon-7tev}.
+
+In addition to the \ac{DT} and \ac{CSCs}, the \ac{RPCs} provide coverage
+for $|\eta|<1.6$. These are made up of parallel plates, forming the anode and cathode,
+with a gas gap in between. Ionisation of the gas due to the passing
+muons is read out using aluminium strips running parallel to the 
+beam axis. The position resolution of the \ac{RPCs} is much poorer than
+that of the \ac{DT} and \ac{CSCs}, but their time response is very fast. As
+a result of this the \ac{RPCs} can be used as an independent muon trigger
+which can correctly identify the beam crossing from which the muon
+originated.
+
+To obtain precise muon momentum resolution, information from 
+the tracker hits has to be combined with measurements in the
+muon stations. The momentum resolution of the muon system
+alone is 9\% for muons with \pT up to 200 GeV, and varies with $\eta$ 
+between 15-40\% for muons with \pT of 1 TeV.
+
 %Because of the uncertainty in the eventual background rates and in the ability of the muon system to measure the correct beam-crossing time when the LHC reaches full luminosity, a com- plementary, dedicated trigger system consisting of resistive plate chambers (RPC) was added in both the barrel and endcap regions.
@@
 During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
-replaced by a completely upgraded system, which provides amongst others 
+replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides amongst others 
 improved object isolation, hadronic tau identification, muon \pT resolution and
-jet finding.
+jet finding with respect to the system used during Run 1.
+An overview of the data flow in the \ac{L1} trigger is given in figure \ref{fig:CMS_Trigger}.
 
-An overview of the data flow in the \ac{L1} trigger is given in figure \ref{fig:CMS_Trigger}.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./Detector/Plots/CMSTrigger.png}
+\caption{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
+\label{fig:CMS_Trigger}
+\end{center}
+\end{figure}
+
 The \ac{L1} trigger only makes use of information from the calorimeters and the muon systems.
@@
 different columns of the detector, to be processed on one node in the second layer of the
-trigger. In this step basic object identification is performed.
+trigger. In this step basic object identification is performed based on the energy
+deposits, so that a sorted list of the best candidates can be passed to the global trigger.
+Hits in the muon chambers are read out and passed to the track finder layer 
+of the muon trigger, which combines information from the \ac{CSC}, \ac{DT}
+and \ac{RPC} systems in regions of $\eta-\phi$.
+In further layers of the muon trigger the information from different
+regions is combined, until finally the global muon trigger
+can return a sorted list of the best muon candidates to the global trigger.
+The global trigger combines the information from the calorimeter and muon triggers
+to make a decision on whether the event should be sent to the \ac{HLT} or whether
+it should be discarded. A decision has to be made within 3.2 $\mu s$, the maximum time during
+which data can be stored in the front-end electronics before being lost.
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./Detector/Plots/CMSTrigger.png}
-\caption{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-upgrade}.}
-\label{fig:CMS_Trigger}
-\end{center}
-\end{figure}
+%The muon trigger is a tracking trigger that measures the momentum of muons using the magnetic field in the steel yoke of the CMS solenoid; thus its resolution degrades with increasing momentum.
+This can be improved by maximizing the number of chamber hits along a muon trajectory and by improving the precision and number of position and angular measurements participating in the track fit applied in the trigger logic.
+Moreover, isolation criteria can be applied using the energy deposits in the calorimeter in order to further reduce the rate of muons from heavy flavor jets.
+
+The \ac{HLT}, running on CPU nodes, makes use of the full information
+from the detector, including tracker hits. This means particles
+can be more accurately identified and their momentum is more
+precisely known. The algorithms used in the \ac{HLT} are usually simpler
+versions of those used in the full offline reconstruction. %Can't use full because time limited
+During the 2012 run of the \ac{LHC} the \ac{HLT} operated with an output
+capacity of around 1 kHz, for Run 2 this has increased. In August 2016, 
+the \ac{HLT} output rate was 1.2 kHz for immediate data processing, with
+an additional 0.6 kHz parked to be reconstructed and analysed when 
+more processing power is available\cite{CMS-PAS-HIG-16-037}. %ie at the end of run 2
+
+While the trigger system reduces the rate substantially, several
+petabytes of data are produced by \ac{CMS} each year, in addition to 
+even larger amounts of simulated datasets. To 
+make these large amounts of data easily available for analysis, 
+\ac{CMS} and the other \ac{LHC} experiments make use of the \ac{WLCG} \cite{lhc-wlcg}. 
+The \ac{WLCG} pools the resources of computer centres at universities and research
+laboratories around the world, based on a system of tiers. The Tier 0, at \ac{CERN} and
+thw Wigner Research Centre for Physics in Budapest, performs the full reconstruction
+and saves the data to tape. Datasets are copied to at least one Tier 1 centre, from
+where data can be distributed to Tier 2 centres. The Tier 2 centres are located
+at over 150 universities and research institutes around the world, providing 
+resources for analysis of the datasets to all researchers associated with the experiment.

### 2016-11-27 Detector/Detector.tex
Full detector chapter and first part of H->hh corrections

@@
 with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
-reached the protons are injected into the \ac{LHC}, where they are further accelerated to 
-the required centre of mass energy. The beams collide at four points
-around the ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
-CMS\cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
+reached the protons are injected into the \ac{LHC} in two counter-rotating
+beams. In the \ac{LHC} ring the beams are further accelerated to the required centre of mass energy
+by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
+of $\mathcal{O}(10^11)$ protons, spaced 25ns apart. The beams are kept in circulation
+using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
+a temperature of 1.9K and generating magnetic fields upwards of 8 T.
+The beams collide at four points
+around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
+CMS%\cite{cms-jinst} guess we've cited this already
+, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
 
@@
 In order to be able to study these relatively rare processes, 
-the LHC operates at high instantaneous luminosity, defined as in equation
+the LHC operates at high instantaneous luminosity, defined as
 \ref{eqn:CMSLHC_luminosity}. 
 \begin{equation}\label{eqn:CMSLHC_luminosity}
-\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F
+\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F.
 \end{equation}
@@
 bunch crossing are likely to occur. The average number of interactions
-per bunch crossing is X in 2012, Y in 2015, Z in 2016. Additional 
+per bunch crossing was 21 in 2012\cite{cms-lumi-public}. The average number of
+interactions per bunch crossing lowered again at the start of Run 2, with
+an average of 14 interactions per bunch crossing for the data collected
+during 2015. In the data-taking period up to August 2016 the average number of interactions
+per bunch crossing increased to 24\footnote{NoteToBeRemovedBeforeSubmission: Lumi pog letting us down 
+here, no references for what number to quote/no prescriptions for how to calculate it. Use of theoretical
+min bias cross section (80mb) vs min bias cross section tuned for pu reweighting (less than 70 mb both for
+2015 and 2016) can shift the average by 5 evts or more! The 2016 number uses the theoretical
+cross section (only reference to this are various sets of slides presented at conferences), 2015
+number based on the min bias cross section used for pu reweighting (iirc). Assuming the 2012 numer,
+for which there is a public figure, uses the theoretical mb cross section should probably re-calculate the
+number for 2015.}. Additional 
 interactions on top of events of interest are referred to as pile-up.
@@
 highly granular system had to be designed. The lead tungstate crystals have a 
-radiation length of 0.89 cm, a Moli\'ere radius of 2.2 cm, and 80\% of the light
+radiation length of 0.89 cm, a Moli\`ere radius of 2.2 cm, and 80\% of the light
 from the crystals is emitted in 25 ns. This short radiation
-length, small Moli\'ere radius and short scintillation decay time combined
+length, small Moli\`ere radius and short scintillation decay time combined
 with the radiation hardness of the material motivate the choice of lead tungstate.
@@
 \begin{equation}\label{eqn:ecalres}
-\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplusC},
+\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplus C,
 \end{equation}
@@
 The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
-plates with tiles of plastic scintillator as the active material. The tiles 
+plates with tiles of plastic scintillator as the active material. The brass used as 
+absorber fits the constraints imposed by the environment due to its short interaction length
+of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
 are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$

### 2016-11-27 Hhh/Hhh.tex
Removing table option
Full detector chapter and first part of H->hh corrections

@@
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis the \etau, \mutau and \tautau final states
-of the \Pgt-pair are studied, these final states are referred to as channels.
+a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
+uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
+period of the \ac{LHC}, the \etau, \mutau and \tautau final states
+of the \Pgt-pair are studied; these final states are referred to as channels. 
 The results of this search are model-independent
-upper limits on heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
+upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
 which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
@@
 In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
-these interpretations are made in combination with the results of a search for \AtoZhtolltautau. 
-This search will be summarised in this chapter, but will not constitute the main focus.
+these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
+My work focussed on checks for the \mutau and \etau channels, as well as being
+responsible for limit setting for the \Htohh analysis, and performing the model interpretations
+of the \Htohh and \AtoZh analyses, plus their combination.
 Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.
@@
 generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
-of \tanb, probing a region of phase space not yet excluded by stringent existing limits. In regions where
+of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
 the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
@@
 events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
-were used for the \Wjets and \Zellell backgrounds. This increases the background event statistics
-in regions with multiple jets, which important for this analysis due to the presence of b-jets in the searched-for final state. 
+were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
+in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
 The samples binned in jet multiplicity are combined with the
@@
 Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
-were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
+were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
+\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
+starts to dominate beyond this mass. In all of the samples
 \texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
@@
 \Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
-to decay the taus and tau polarisation effectes are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
+to decay the taus and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
 response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
@@
 \label{sec:hhh_selection}
-A more detailed description of the physics objects used for this analysis is given in chapter OBJECTS
-in this section only an overview of the event selection is presented.
+This section gives an overview of the event selection, a detailed description of the physics
+objecs used in this analysis is given in chapter OBJECTS.
 
@@
 which requires only a muon
-at L1. At the level of the HLT a hadronic tau, reconstructed using a simpler version of the
-PF algorithm, is also required. Loose isolation requirements are applied to this hadronic tau, and 
+at \ac{L1}. At the level of the \ac{HLT} a hadronic tau, reconstructed using a simpler version of the
+\ac{PF} algorithm, is also required. Loose isolation requirements are applied to this hadronic tau, and 
 loose ID and isolation requirements are applied to the muon at this stage.
@@
 the decay mode finding identification
-from the HPS algorithm, as described in section OBJECTS. Additionally
-the raw combined isolation, described in the same section, is required to be
+from the HPS algorithm. Additionally
+the raw combined isolation is required to be
 at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
@@
 also required to pass the tight working point of the anti-$\Pgm$ discriminator
-and the loose working point of the cut--based anti-$\Pe$ discriminator, both
-described in section OBJECTS.
+and the loose working point of the cut--based anti-$\Pe$ discriminator.
 
@@
 satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
-working point of the electron MVA ID discriminator described in section OBJECTS, and the
+working point of the electron MVA ID discriminator, and the
 relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
@@
 
-If there is more than one possible \etau pair, the pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
+If there is more than one possible \etau pair, The pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
 is taken. Similar additional vetos as in the \mutau channel are applied.
 the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
-isolation requirements than the signal electron requirements can be formed. To reduce the \WZ
+isolation requirements than the signal electron requirements, can be formed. To reduce the \WZ
 background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
@@
 \label{sec:hhh_selection_categories}
-In both channels a selection on the transverse mass \mT~between the electron/muon
+In both channels a selection on the transverse mass, \mT,~between the electron/muon
 and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
@@
 \end{equation}
-In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
-between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
+In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
+angle between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
 and \mutau channels, using the selections as
@@
 (at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
-Jets are considered b-tagged if they pass the medium working point of the b-tagging discriminator described in section OBJECTS.
+Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
 The 2jet-0tag category does not collect much of the signal and is dominated by 
-backgrounds, the 2jet-2tag category is most sensitive to signal. 
+backgrounds, the 2jet-2tag category is the most sensitive to signal. 
 Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
@@
 In signal events, the di--tau pair and di--jet pair 
-are the decay products of an 125 Gev Higgs boson, therefore their invariant
+are the decay products of a 125 GeV Higgs boson, therefore their invariant
 masses should be close to 125 GeV. To reduce background contributions
@@
 rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
-derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
+derived using the method described in ref. \cite{BTV8TeV}. There are separate scale factors for 
 b-/c- jets and light jets. Multiple possible ways to apply these scale factors
@@
 the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
-in consideration.
+under consideration.
 
@@
 The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
-reconstructed as the 4--body mass of the two jets and the two taus, however
+reconstructed as the 4--body mass of the two jets and the two taus; however
 a more accurate result can be obtained by using a kinematic fitting 
@@
 
-Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})
+Before the fit, from the mass constraint we have:
 ~\vspace{-0.5\baselineskip}
@@
 & = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
-&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
+&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}.
 \end{align}
@@
 rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
-and equation \ref{eqn:gamma_def}:
+and
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:gamma_def}
-\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}
+\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}.
 \end{equation}
@@
 
-The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
+The fitting procedure additionally modifies the masses of the b-jets as 
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_bjetmass}
-m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}
+m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}.
 \end{equation}
@@
 
-The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})
+The measured recoil is 
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilmeas}
-\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}}
+\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
 \end{equation}
-With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
+and the recoil from the fit is,
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilfit}
-\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}
+\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}.
 \end{equation}
@@
 OBJECTS section,
-while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets. 
+while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
 ~\vspace{-0.5\baselineskip}
@@
 \end{equation}
-The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})
+The total $\chi^2$ term that needs to be minimised in the fit can then be written as
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_chitot}
-\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}
+\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}.
 \end{equation}
-The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
+The results of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
 set to the best fit values found for them in the fit. These can then be added together to find
@@
 In the 2jet-2tag, a slightly different high-\mT~sideband of 60-120 GeV is used 
-to give larger statistics for the \Wjets estimate after other backgrounds are
+to give more events for the \Wjets estimate after other backgrounds are
 subtracted. The method of extrapolating this yied estimate into
@@
 
-The \Wjets shape is taken from the \ac{MC} samples. To 
-increase the statistics for this estimate, the b-tagging definition
+The shape of the \Wjets distribution is taken from the \ac{MC} samples. To 
+increase the number of events for this estimate, the b-tagging definition
 in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
@@
 A fully data-driven method is used to estimate the QCD background. Data events
-passing the signal region selection cuts, but with the di-\Pgt candidates of
-same sign, are used for this. The contributions from other backgrounds are 
+passing the signal region selection cuts, but with di-\Pgt candidates of
+the same sign, are used for this. The contributions from other backgrounds are 
 subtracted, and the contribution from opposite- and same-sign QCD are
@@
 the same-sign subtracted data multiplied by the OS/SS ratio. In the 2jet-2tag
-category the statistics are too low for this, so another sideband is defined
+category the number of available events is too low for this, so another sideband is defined
 in which the electron/muon isolation requirement is inverted. This 
@@
 
-\begin{table}[htdp]
+\begin{table}[htp]
 \begin{center}

### 2016-11-28 Detector/Detector.tex
First round of own comments on detector chapter

@@
 Franco-Swiss border near Geneva. It
-is installed in the tunnel that previously housed the Large Electron Positron accelerator
+is installed in the tunnel that previously hosted the Large Electron Positron accelerator
 that was operated by \acf{CERN} between 1989 and 2000.
@@
 chain which increases the energy of the protons in several steps. After the protons
-are created from the hydrogen gas, they are accelerated to a centre of mass energy of
+are created from the hydrogen gas, they are accelerated to an energy of
 50 MeV in the Linac2 linear accelerator. They are then passed on to the
-\acf{PSB} which accelerates the protons until they reach a centre of mass energy of 1.4 GeV.
+\acf{PSB} which accelerates the protons until they reach an energy of 1.4 GeV.
 The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
@@
 by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
-of $\mathcal{O}(10^11)$ protons, spaced 25ns apart. The beams are kept in circulation
+of $\mathcal{O}(10^{11})$ protons, spaced 25ns apart. The beams are kept in circulation
 using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
@@
 \ref{fig:stirling_xs}. For example, the production cross-section of the
-standard model Higgs boson is 9-10 orders of magniuted smaller than the total p--p cross section.
+standard model Higgs boson is 9-10 orders of magnitude smaller than the total p--p cross section.
 
@@
 the LHC operates at high instantaneous luminosity, defined as
-\ref{eqn:CMSLHC_luminosity}. 
+
 \begin{equation}\label{eqn:CMSLHC_luminosity}
@@
 
-After an initial testing phase, the \ac{LHC} began its first physics run in May 2010 with 
-a centre of mass energy of 7 TeV. The CMS experiment recorded an integrated luminosity of 45 pb$^{-1}$
-during 2010. In 2011 the \ac{LHC} continued operating at a centre-of-mass energy of 7 TeV, delivering an integrated 
-luminosity of 6.1 fb$^{-1}$ to the CMS experiment. The centre of mass energy was increased to 8 TeV
-for the 2012 data-taking period, during which an integrated luminosity of 23.3 fb$^{-1}$ was delivered.
+The \ac{LHC} began its first physics run in May 2010, colliding protons at
+a centre-of-mass energy of 7 TeV. The \ac{CMS} experiment recorded an integrated luminosity of 45 pb$^{-1}$
+during the rest of that year. In 2011 the \ac{LHC} continued operating at a centre-of-mass energy of 7 TeV, delivering
+6.1 fb$^{-1}$ to the \ac{CMS} experiment. The centre-of-mass energy was increased to 8 TeV
+for the 2012 data-taking period, during which the delivered integrated luminosity was 23.3 fb$^{-1}$.
 This completed Run 1 of the \ac{LHC}, after which the 2-year \ac{LS1} was used to 
-upgrade the LHC and the detectors for collisions at a centre of mass energy of 13 TeV.
+upgrade the \ac{LHC} and the detectors for collisions at a centre-of-mass energy of 13-14 TeV.
 
 In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV, and during 
-this year 4.2 fb$^{-1}$ was delivered. Collisions at a centre-of-mass energy of 13 TeV continued
-in 2016, when a total of 41.1 fb$^{-1}$ was delivered. 
+this year 4.2 fb$^{-1}$ was delivered. The \ac{LHC} operated at a centre-of-mass energy of 13 TeV 
+during 2016 too, when a total of 41.1 fb$^{-1}$ was delivered to \ac{CMS}.
 The integrated luminosity as a function of time is shown in figure \ref{fig:CMSLHC_intlumi},
@@
 \includegraphics[width=0.85\textwidth]{./Detector/Plots/int_lumi_cumulative_pp_2.pdf}
-\caption{Cumulative integrated luminosity for p--p collisions at the LHC, separated
+\caption{Cumulative integrated luminosity delivered to \ac{CMS} for p--p collisions at the \ac{LHC}, separated
 by running year \cite{cms-lumi-public}.}
@@
 
-From all of the data that is recorded, a subset is used for analyses. Data is 
+From all of the data that is recorded, only a subset is used for analysis. Data is 
 certified as good for use in analyses if it is known that all relevant subdetectors
-were functioning correctly. The certification efficiency in 2012 was 90.4\%,
-leading to an integrated luminosity of 19.7 fb$^{-1}$ for which all subdetectors
-were working well, in 2015 it was 60.4 \%, leading to 2.3 fb$^{-1}$ of analysable data
-for which the full detector was operational. An additional 0.6 fb$^{-1}$ was taken
-with the magnet switched off. The certification efficiency for the full 2016 p--p running period was 95.4\%.
+were functioning correctly. In 2012 the certification efficiency was 90.4\%
+meaning all subdetectors were working well for a dataset corresponding to 19.7 fb$^{-1}$.
+The certification efficiency was 60.4 \% in 2015, leading to 2.3 fb${-1}$ of 
+analysable data for which the full detector was operational. An additional 0.6 fb$^{-1}$
+was taken with the \ac{CMS} magnet switched off. For the full 2016 p--p running period
+the certification efficiency was 95.4\%, resulting in 36.26 fb$^{-1}$ of data marked good
+for use in analyses.
 
-The \ac{LHC} was designed for a nominal
-peak luminosity of $10^{32}$cm$^{-2}$s$^{-1}$ for proton-proton collisions. In 2012 peak
+The \ac{LHC} was designed for proton-proton collisions with a nominal
+peak luminosity of $10^{32}$cm$^{-2}$s$^{-1}$. In 2012 peak
 luminosities of $7.7*10^{33}$cm$^{-2}$s$^{-1}$ were reached, with the peak luminosity in
@@
 design luminosity, with peak luminosities of $1.5*10^{32}$cm$^{-2}$s$^{-1}$ reached
-in October 2016.
+in October 2016 \cite{cms-lumi-public}.
 
@@
 12500 tonnes \cite{cms-jinst}. It consists of several subdetectors, as illustrated
-in figure \ref{fig:cms_detector}. Surrounding the interaction
-point is the silicon tracker, a cylinder 5.8 m in lenght and 2.6 m in 
+in figure \ref{fig:cms_detector}.
+
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
+\caption{A blow-up view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
+different sub-parts of the detector.}
+\label{fig:cms_detector}
+\end{figure}
+
+Surrounding the interaction point is the silicon tracker, a cylinder 5.8 m in length and 2.6 m in 
 diameter. Surrounding the silicon tracker
@@
 points along the beam direction. As such the transverse momentum and energy, 
-\pT and \ET are measured from the x- and y- components of the momentum and energy.
+\pT~and~\ET are measured from the x- and y- components of the momentum and energy.
 The azimuthal angle $\phi$ is measured in the x-y plane with respect to the x-axis, 
@@
 next sections.
-
-\begin{figure}[h!]
-\includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
-\caption{A blow-up view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
-different sub-parts of the detector.}
-\label{fig:cms_detector}
-\end{figure}
 
@@
 Beyond the pixel detector the tracking system is made up of a silicon
-strip detector consisting of over 9 million multiple different subsystems. The first part of the
-silicon strip tracker consists of \ac{TIB} and \ac{TID}, providing 4 layers of
+strip detector consisting of multiple different subsystems. The first part of the
+silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing 4 layers of
 silicon strip detectors in the barrel plus 3 disks at both ends. These two systems
 extend out towards a radius of 55 cm. The barrel layers and disks each consist
-of silicon strips which are 10 cm long, $80-141\mu m$ wide and $320 \mu m$ thick. The \ac{TIB} and \ac{TID}
+of silicon strips which are 10 cm long, $80-141~\mu$m wide and $320~\mu$m thick. The \ac{TIB} and \ac{TID}
 provide 4 measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu m$.
 The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of 6 layers of silicon strip sensors extending
-up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500 $\mu m$ thick, around 25 cm long and 122-183 $\mu m$ 
+up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500~$\mu$m thick, around 25 cm long and 122-183 $\mu$m 
 wide and this subdetector provides 6 measurements of $r$ and $\phi$, with a resolution
-of 35-53 $\mu m$. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
-consisting of 9 disks of strips.In the \ac{TEC}, the thickness ranges from 320-500 $\mu m$ and the the strip width ranges from $97-184 \mu m$.
-In this way this part of the system provides up to 9 $\phi$ measurements.
+of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
+consisting of 9 disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
+This part of the system provides up to 9 $\phi$ measurements.
 
 Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
-of 100 mrad, in order to provide measurements of the $z-$ coordinate in the barrel. This is achieved with a resolution of 230-530 $\mu m$.
+of 100 mrad, in order to provide measurements of the $z-$ coordinate in the barrel. This is achieved with a resolution of 230-530 $\mu$m.
 
-The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. %or just replaced?
+The pixel tracker will be upgraded during the extended year-end technical stop in early 2017 \cite{cms-pixel-upgrade}. %or just replaced?
 
@@
 made of nearly 76000 lead tungstate (PbWO$_4$) crystals. It has very
-good energy resolution, is highly granular and fast-responding, which
-are all needed to be able to detect $H\rightarrow \gamma\gamma$ decays.
+good energy resolution, is highly granular and fast-responding, all qualities 
+which are needed to be able to detect $H\rightarrow \gamma\gamma$ decays.
 
@@
 Each endcap is divided into two halves. In front of the endcaps 
-the preshower detectors, covering $1.653<|\eta|<2.6$ is a sampling
-calorimeter whose main use is to indentify neutral pions in the endcaps. Additionally
-it helps electron identification and improves the resolution
+the preshower detectors, covering $1.653<|\eta|<2.6$ are sampling
+calorimeters whose main use is to indentify neutral pions in the endcaps. Additionally
+they help electron identification and improve the resolution
 of position determination. Each of the two preshower detectors consist
@@
 To preserve the energy resolution, the \ac{ECAL} crystal and
-photodetector temperatures need to be kept stable within $\pm 0.05^o$C
+photodetector temperatures need to be kept stable within $\pm 0.05^{\circ}$C
 as the number of scintillation photons emitted by the crystals,
 and the amplification of the photodetectors are temperature dependent.
-The nominal operating temperature, $18^o$C, is ensured by 
+The nominal operating temperature, $18^{\circ}$C, is ensured by 
 supplying the detector with water at this temperature.
@@
 \begin{equation}\label{eqn:ecalres}
-\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplus C,
+\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\oplus\frac{N}{E}\oplus C,
 \end{equation}
@@
 The values of $S$, $N$ and $C$ have been measured in an electron
-test-beam, without a magnetic field or material in front of the \ac{ECAL}. These
-amounted to $S = 0.028$ GeV$^{\frac{1}{2}}$, $N = 0.12$ GeV, $C= 0.003$.
+test-beam, without a magnetic field or material in front of the \ac{ECAL}, as 
+$S = 0.028$ GeV$^{\frac{1}{2}}$, $N = 0.12$ GeV and $C= 0.003$.
 %S = 2.83 %pm 0.03%, C = 0.26% pm 0.04%
@@
 \label{sec:CMSLHC_CMS_hcal}
-The \ac{ECAL} is surrounded by the \ac{HCAL}, important for the
+The \ac{ECAL} is surrounded by the \ac{HCAL}, which is important for the
 measurement of the energies of strongly interacting particles. As
 the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
-starting at a radius of 2.95 m the barrel region of the \ac{HCAL} consists
+starts at a radius of 2.95 m, space for the \ac{HCAL} inside the magnet
+coil is limited. Therefore the barrel region of the \ac{HCAL} consists
 of the \ac{HB}, which sits inside the magnet coil, and the \ac{HO}, sitting outside it, 
@@
 The light from each tile is collected with a wavelength-shifting fibre, 
-which is eventually read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
+which is read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
 has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
@@
 thickness to at least 11.8 interaction lenghts. 
-The active material again consists of plastic scintillator tiles which roughly
-map the granularity of the tiles in the \ac{HB}, read out by feeding the light
+Like in the \ac{HB} the active material consists of plastic scintillator tiles which roughly
+map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
 to a hybrid photodiode via wavelength shifting fibres.
@@
 \begin{equation}\label{eqn:hcal_res}
-\frac{\sigma}{E} = \frac{S}{\sqrt{E}} \bigoplus C,
+\frac{\sigma}{E} = \frac{S}{\sqrt{E}} \oplus C,
 \end{equation}
@@
 and $C$ is the constant term, measured to be 8.4\% %pm 1.0
-HCAL RESOLUTION!
+
 %UPGRADE
-During LS1, the \ac{HO} and \ac{HF} pmts were replaced
+During \ac{LS1}, the photomultiplier tubes of the \ac{HF} were upgraded. The photomultiplier- and
+read-out systems of other parts of the \ac{HCAL} will be upgraded in stages over the
+next few years \cite{cms-hcal-upgrade}.
 
@@
 All of this means that good muon identification efficiency and precise muon momentum resolution
-are very important. The \ac{CMS} muon system is made up out of three different subsystems which
+are very important. The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
 are all necessary to ensure the identification requirements can be met. It is located
@@
 In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
-the \ac{CSC} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
+the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
 regions as both \ac{DT} and \ac{CSCs}, is used as a dedicated triggering system.
@@
 additional layers of \ac{CSCs} and \ac{RPCs}.
-\ac{LS1}.
 \begin{figure}[h!]
@@
 
-The \ac{DT} consists of layers of drift cells with a cross-section of $4.2 \times 1.3$ cm and
-2.4 m long. The cells are filled with a mixture of %85\% 
-Argon and carbon di-oxide gas.
+The \ac{DT} consists of layers of drift cells which have a cross-section of $4.2 \times 1.3$ cm$^2$ and
+are 2.4 m long. The cells are filled with a mixture of %85\% 
+argon and carbon di-oxide gas.
 Muons passing through the chamber ionise the gas, freeing electrons
@@
 The spatial resolution of the \ac{DT} is 80-120 $\mu$m per chamber for
-measurements in the $\phi$ direction, with the resolution of the $z$ measurement
+measurements in the $\phi$ direction, while the resolution of the $z$ measurement
 is 130-400 $\mu$m\cite{cms-muon-7tev}.
@@
 sensitive strips placed on these plates in the
-radial direction, to measure the coordinate in the  $r-\phi$ plane
-of the muons. Anode wires in between the cathode planes
+radial direction, to measure the muon coordinate in the  $r-\phi$ plane
+Anode wires in between the cathode planes
 run along the $\phi$ direction and provide a measurement of
@@
 muons is read out using aluminium strips running parallel to the 
-beam axis. The position resolution of the \ac{RPCs} is much poorer than
+beam axis. The position resolution of the \ac{RPCs} is poorer than
 that of the \ac{DT} and \ac{CSCs}, but their time response is very fast. As
@@
 muon stations. The momentum resolution of the muon system
-alone is 9\% for muons with \pT up to 200 GeV, and varies with $\eta$ 
-between 15-40\% for muons with \pT of 1 TeV.
+alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
+between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}.
 
@@
 system is therefore used to select events of interest for study, which reduces the rate
-at which events are written to disk to  $\mathcal{O}(1 \text{ kHz})$.
+at which events are stored to  $\mathcal{O}(1 \text{ kHz})$.
 
@@
 replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides amongst others 
-improved object isolation, hadronic tau identification, muon \pT resolution and
+improved object isolation, hadronic tau identification, muon \pT~resolution and
 jet finding with respect to the system used during Run 1.
@@
 Hits in the muon chambers are read out and passed to the track finder layer 
-of the muon trigger, which combines information from the \ac{CSC}, \ac{DT}
-and \ac{RPC} systems in regions of $\eta-\phi$.
+of the muon trigger, which combines information from the CSC, \ac{DT}
+and RPC systems in regions of $\eta-\phi$.
 In further layers of the muon trigger the information from different
@@
 to make a decision on whether the event should be sent to the \ac{HLT} or whether
-it should be discarded. A decision has to be made within 3.2 $\mu s$, the maximum time during
+it should be discarded. A decision has to be made within 3.2 $\mu$s, the maximum time during
 which data can be stored in the front-end electronics before being lost.
@@
 While the trigger system reduces the rate substantially, several
-petabytes of data are produced by \ac{CMS} each year, in addition to 
-even larger amounts of simulated datasets. To 
-make these large amounts of data easily available for analysis, 
+petabytes of collision data are stored by \ac{CMS} each year, on top
+of large sets of simulated events. 
+To make these large amounts of data easily available for analysis, 
 \ac{CMS} and the other \ac{LHC} experiments make use of the \ac{WLCG} \cite{lhc-wlcg}. 
@@
 laboratories around the world, based on a system of tiers. The Tier 0, at \ac{CERN} and
-thw Wigner Research Centre for Physics in Budapest, performs the full reconstruction
-and saves the data to tape. Datasets are copied to at least one Tier 1 centre, from
+the Wigner Research Centre for Physics in Budapest, performs the full reconstruction
+and saves a copy of the data to tape. Datasets are copied to at least one Tier 1 centre, from
 where data can be distributed to Tier 2 centres. The Tier 2 centres are located

### 2016-11-28 Detector/Detector.tex
Some rephrasing

@@
 using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
-a temperature of 1.9K and generating magnetic fields upwards of 8 T.
+a temperature of 1.9K and generating magnetic fields upwards of 8 Tesla.
 The beams collide at four points
@@
 
-The tracker provides coverage up to $|\eta| < 2.5$ and consists of
-several different components. A schematic of the tracking detector is given
-in figure \ref{fig:CMS_tracker}. The part of the tracking system
-closest to the interaction point is the silicon pixel detector, which 
-consists of 3 layers of pixels in the barrel of the detector, with 
-2 pixel endcap disks. The barrel layers sit at radii of 4.4, 7.3 and 10.2 cm 
-and extend up to $z=\pm 26.5$ cm, with the disks placed at $z=\pm 34.5$ cm and
-$z=\pm 46.5$ cm. The pixel detector consists of 66 million silicon pixels, each
-$100 \mu m \times 150 \mu m$ in size. The choice of this pixel size is driven
-by the achievable spatial resolution, which is $15-20 \mu m$ in the $r$ and $z$ directions.
-This allows for 3D vertex reconstruction. With this layout, the pixel tracker
-provides 3 precise position measurements along each charged particle trajectory.
+The tracker, providing coverage up to $|\eta|<2.5$ consists of 
+several different components. A schematic of the tracking detector, indicating
+the location of these components, is given in figure \ref{fig:CMS_tracker}.
+Nearest the interaction point the tracker is a pixel detector made
+of 66 million silicon pixels, each 100 $\mu$m $\times$ 150 $\mu$m in size.
+The choice of this pixel size is driven by the achievable spatial resolution,
+which is 15-20 $\mu$m in the $r$ and $z$ directions in this case. Such a
+precise resolution allows for 3D vertex reconstruction. The pixel
+detector consists of 3 layers of pixels in the barrel region, with 2 pixel disks 
+placed in the endcap region at either side. The barrel layers sit at radii of
+4.4, 7.3 and 10.2 cm and extend out up to $z=\pm 26.5$ cm. The disks are placed
+at $z=\pm 34.5$ cm and $z=\pm 46.5$ cm. With this layout the pixel tracker can
+provide three precies position measurements along each charged particle trajectory.
 
@@
 strip detector consisting of multiple different subsystems. The first part of the
-silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing 4 layers of
-silicon strip detectors in the barrel plus 3 disks at both ends. These two systems
+silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
+silicon strip detectors in the barrel plus three disks at both ends. These two systems
 extend out towards a radius of 55 cm. The barrel layers and disks each consist
 of silicon strips which are 10 cm long, $80-141~\mu$m wide and $320~\mu$m thick. The \ac{TIB} and \ac{TID}
-provide 4 measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu m$.
-The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of 6 layers of silicon strip sensors extending
+provide four measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu$m.
+The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of six layers of silicon strip sensors extending
 up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500~$\mu$m thick, around 25 cm long and 122-183 $\mu$m 
@@
 of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
-consisting of 9 disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
-This part of the system provides up to 9 $\phi$ measurements.
+consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
+This part of the system provides up to nine $\phi$ measurements.
 
@@
 
-The pixel tracker will be upgraded during the extended year-end technical stop in early 2017 \cite{cms-pixel-upgrade}. %or just replaced?
+The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. This upgrade is needed to
+maintain the performance of the tracker as the pile-up increases \cite{cms-pixel-upgrade}. %or just replaced?
 
@@
 
-Despite being further away from the interaction
-point than the tracker, the materials in other parts of the detector
-still need to be radiation hard. In order to be able to place
-the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
-had to be constructed, and to provide excellent resolution a 
-highly granular system had to be designed. The lead tungstate crystals have a 
-radiation length of 0.89 cm, a Moli\`ere radius of 2.2 cm, and 80\% of the light
-from the crystals is emitted in 25 ns. This short radiation
-length, small Moli\`ere radius and short scintillation decay time combined
-with the radiation hardness of the material motivate the choice of lead tungstate.
+The choice of lead tungstate crystals is motivated by the
+radiation-hardness of the material in combination with its
+short radiation length, small Moli\`ere radius and short scintillation
+decay time. With a radiation length of 0.89 cm and a Moli\`ere radius of 2.2 cm,
+lead tungstate crystals allow for the construction of a compact, highly 
+granular \ac{ECAL}. The compactness of the \ac{ECAL} is required in 
+order to be able to fit the calorimeters inside the bore of the magnet. 
+As 80\% of the light from the crystals is emitted within 25 ns, that is
+within the time between two bunch crossings at design operation of the \ac{LHC},
+the lead tungstate crystals satisfy the requirements imposed by the \ac{LHC} operating
+parameters.
 
@@
 Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
-the geometry. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
+the subsystems it is made up of. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
 covers the pseudorapidity range up to $|\eta|<1.479$, with
@@
 starts at a radius of 2.95 m, space for the \ac{HCAL} inside the magnet
-coil is limited. Therefore the barrel region of the \ac{HCAL} consists
-of the \ac{HB}, which sits inside the magnet coil, and the \ac{HO}, sitting outside it, 
-to complement the \ac{HB}. The \ac{HB} and \ac{HO}  provide coverage up to $|\eta|<1.3$, 
-beyond which they are complemented by the \ac{HE} and the \ac{HF}. The \ac{HE} provides
-coverage between $1.3<|\eta|<3$ with the \ac{HF} extending this coverage up to $|\eta| = 5.2$
-The locations of the different subcomponents of the \ac{HCAL} are shown
+coil is limited. The \ac{HCAL} design takes
+this into account by placing part of the subdetector outside the magnet coil. A schematic of the
+\ac{HCAL}, indicating the different components of the \ac{HCAL} is shown
 in figure \ref{fig:CMS_HCAL}.
@@
 
-The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
+In the barrel region the \ac{HB}, limited in radius by the magnet coil, provides
+coverage up to $|\eta|<1.3$. Beyond this $\eta$ range the \ac{HE} covers
+the region up to $|\eta|<3$. The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
 plates with tiles of plastic scintillator as the active material. The brass used as 
@@
 thickness to at least 11.8 interaction lenghts. 
-Like in the \ac{HB} the active material consists of plastic scintillator tiles which roughly
+Like in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
 map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
@@
 \label{sec:CMSLHC_CMS_muons}
-One of the main physics goals of the \ac{CMS} experiment
-at design was to search for $H\rightarrow ZZ\rightarrow 4\mu$ decays. Muons
-suffer less from radiative losses in the tracker material, which means the most accurate
-4-body mass can be constructed when using the dimuon final state of the $Z$'s.
-Since the discovery of the Higgs boson the ZZ channel has continued to be an important
-final state for Higgs measurements, at the same time many \ac{BSM} searches also make use of 
-signatures with muons in the final state.
-All of this means that good muon identification efficiency and precise muon momentum resolution
-are very important. The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
+Precise muon identification is one of the requirements of the \ac{CMS} 
+experiment. Good muon identification efficiency and precision muon momentum 
+resolution are very important, as muons appear as final states in many
+\ac{BSM} signatures the experiment is used to search for. In addition to
+that, final states with muons are very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays.
+
+The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
 are all necessary to ensure the identification requirements can be met. It is located

### 2016-11-28 Hhh/Hhh.tex
Fixing up some more of Gavins comments on H->hh chapter

@@
 the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
-of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
+of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
 of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.
@@
 which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
-By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
+By requiring $70 < m_{jj} < 150$ GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
 large number of background events can be rejected, while retaining
@@
 compared with the simple 4-body mass reconstruction. It also shifts the mean of the
-distribution closer to the true value. From the right hand side of
-figure \ref{fig:kinfitvsmjj} we can see that the mass distribution for
+distribution closer to the true value. It is also insightful to make such a comparison
+for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
+shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between 4-body mass and
+kinematic fit mass for \ttbar events is shown on the right hand side of figure 
+\ref{fig:kinfitvsmjj}. From this figure we can see that the mass distribution for
 background events is affected less by the kinematic fit, although due to the
@@
 extrapolation factor is determined from the \Wjets \ac{MC} 
-samples. The yield in the signal region is then the other-background-subtracted
-data yield in the high-\mT~region multiplied by this extrapolation factor.
-In the 2jet-2tag, a slightly different high-\mT~sideband of 60-120 GeV is used 
+samples. The yield in the signal region is given by the data yield in the high-\mT sideband, with
+other backgrounds subtracted, multiplied by this extrapolation factor.
+In the 2jet-2tag category, a slightly different high-\mT~sideband of 60-120 GeV is used 
 to give more events for the \Wjets estimate after other backgrounds are
@@
 passing the signal region selection cuts, but with di-\Pgt candidates of
-the same sign, are used for this. The contributions from other backgrounds are 
-subtracted, and the contribution from opposite- and same-sign QCD are
-not exactly the same an OS/SS ratio is applied to the data-other backgrounds in the same--sign region.
+the same sign, are used for this. The contributions from other backgrounds
+in this same--sign region are subtracted from the number of data events obtained.
+As the contribution from opposite- and same-sign QCD are
+not exactly the same an OS/SS ratio is applied to the same--sign region data with other backgrounds subtracted.
 The OS/SS ratio is measured using data with the 
@@
 uncertainties (which affect only the yield of a process), and shape
-uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}
+uncertainties (which affect both the yield of a process and the shape of its kinematic fit mass distribution). Section \ref{sec:hhh_results_extraction}
 describes how these uncertainties are taken into account in the final result.
@@
 \subsubsection*{Luminosity uncertainty}
-The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
+The uncertainty on the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during
 2012. This uncertainty is applied to all processes in which
@@
 \subsubsection*{Identification, isolation and trigger efficiencies}
-A systematic uncertainty due to the uncertainty in efficiency measurements
+A systematic uncertainty due to the uncertainty on the efficiency measurements
 for the leptons is derived by combining the uncertainties on these measurements
@@
 uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
-the \Pgt legs of the triggers. This uncertainty is applied to all processes for which
+the \Pgt legs of the triggers \cite{CMS-HIG-14-034}. The identification, isolation and trigger efficiency measurement uncertainties are applied to all processes for which
 the normalisation is estimated using MC samples.
@@
 The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
-$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$
+$\mu\rightarrow\Pgt$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\mu\rightarrow\Pgt$
 fake rate is close to 1, which is why it is not applied, but the uncertainty is 
@@
 \subsubsection*{B-tag scale factors}
-The b-tag scale factors are varied within their uncertainties to determine the effect
+The b-tag scale factors are varied within their uncertainties, as described in ref. \cite{cms-btag-paper}, to determine the effect
 on the yields of each process. Both a b-tagging uncertainty and a light jet mis-tagging
@@
 the recoil correction parameters within their estimated uncertainties. This 
-leads to a 1-10\% uncertainty, depending on category and process considered.
+leads to a 1-10\% uncertainty, depending on category and process considered \cite{CMS-HIG-14-034}.
 \subsubsection*{Background normalisation}
 \begin{itemize}
-\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived
+\item \Ztautau : the normalisation of the embedded samples has a 3.3\% uncertainty \cite{CMS-HIG-14-034}, which is derived
 from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples.
 In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
-\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
-\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
-\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
-\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
+\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\% \cite{CMS-HIG-14-034}.
+\item \ttbar: the uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
+\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\% \cite{SMHtautauCMS}.
+\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry \cite{CMS-HIG-14-034}.
 \item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio.
-This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.
+This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category \cite{CMS-HIG-14-034}.
 \end{itemize}
@@
 \subsubsection*{Tau energy scale}
-The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty.
+The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty \cite{SMHtautauCMS}.
 As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.
 \subsubsection*{Jet energy scale}
-The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty.
+The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty \cite{cms-jec-2011}.
 Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.
@@
 \label{sec:hhh_azh}
-In this section a summary of the \AtoZhtolltautau analysis, which is combined with the 
+In this section a summary of the \AtoZhtolltautau analysis \cite{CMS-HIG-14-034}, which is combined with the 
 analysis described so far for the purposes of model interpretations, is given.
@@
 First the \PZ candidate is chosen as a pair of isolated electrons or muons, with opposite charge, and 
-invariant mass of the pair between 60-120 GeV. In case there is more than one possible pair, the 
+invariant mass of the pair between 60-120 GeV. If there is more than one possible pair, the 
 pair with invariant mass closest to the \PZ mass is chosen. The \htotautau decay is chosen by selecting
-an oppositely charged pair of isolated leptons in the four channels mentioned earlier. To ensure no overlap
+an oppositely charged pair of isolated particles in the four channels mentioned earlier. To ensure no overlap
 between different final states is possible, events with additional electrons or muons satisfying the
@@
 
-For signal extraction, the mass of the A boson \mA is used. This mass is reconstructed by combining the
+For signal extraction, the mass of the A boson \mA~is used. This mass is reconstructed by combining the
 4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate as obtained by using the 
@@
 luminosity uncertainty and the uncertainties on b-tagging efficiency
-and light jet mistagging rate.
+and light jet mis-tagging rate.
 
@@
 of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
-methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
+statistical methods used were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
 and are used for all Higgs analyses in ATLAS and CMS.
 
-For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
+The likelihood function for data, whether observed or pseudo-data, is constructed as 
 \begin{equation} \label{eqn:hhh_likelihood}
-\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
+\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
 \end{equation}
 
-Where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson}), with $n_i$ the number of 
-data events, whether observed or pseudo-data, in bin i.
+where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given by
 \begin{equation}\label{eqn:hhh_poisson}
-\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
+\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))},
 \end{equation}
 
-The first term of equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
+with $n_i$ the number of 
+data events, whether observed or pseudo-data, in bin i.
+
+The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
 in all channels and categories. $s$ represents the number of expected signal events
 in each bin, and $b$ the number of expected background events. These are functions of 
-$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
-\ref{sec:hhh_uncs} are each represented by a nuisance parameter $\theta_j$. The signal strength
+$\theta$, the full set of nuisance parameters. The signal strength
 modifier $\mu$ can represent different quantities depending on the normalisation of the 
 signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
-to 1 pb, so the signal strenght modifier represents
+to 1 pb, so the signal strength modifier represents
 the cross-section $\times$ branching ratio of a possible signal.
 
-The second term of equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
+The second term in equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
 probability density functions of the uncertainties on the nominal
 values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
-as discussed in section\ref{sec:hhh_uncs}. The functional form of the probability density function
+as discussed in section \ref{sec:hhh_uncs}. The functional form of the probability density function
 depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
@@
 yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
-technique. For each nuisance parameter that affects the shape of the fitted distribution, two additional
+technique \cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
 templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
 parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
-the nominal and $\pm 1\sigma$ templates. Limitations in event statistics for shape templates
+the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
 are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
-shape template are allowed to float within their statistical uncertainty, independent of the other bins. These
+shape template is allowed to float within its statistical uncertainty, independent of the other bins. These
 variations are controlled by log-normal constraints in the likelihood function.
 
-To compare the data with the background only and signal + background hypotheses, a test
+To compare the data with the background-only and signal-plus-background hypotheses, a test
 statistic $q_{\mu}$ can be defined. This is a single 
@@
 statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
-in equation \ref{eqn:hhh_profilelikelihood}.
+by
 \begin{equation}\label{eqn:hhh_profilelikelihood}
-q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
+q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}.
 \end{equation}
@@
 The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
-and assuming the background-only hypothesis, are given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.
+and assuming the background-only hypothesis, are given by
 
 \begin{equation}\label{eqn:hhh_pvaluesig}
-p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
+p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu},
 \end{equation}
 
+and 
 \begin{equation}\label{eqn:hhh_pvaluebkg}
-1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
+1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
 \end{equation}
 
-Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
+where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
 the signal+background and background-only hypotheses.
 
-Using this, $CL_s$ is defined as (equation \ref{eqn:hhh_cls})
+Using this, $CL_s$ is defined as
 \begin{equation}\label{eqn:hhh_cls}
-CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
+CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}.
 \end{equation}
 
-The value of $\mu$ for which $CL_s{\mu}$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
+The value of $\mu$ for which $CL_s$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
 confidence level $1-\alpha$. Upper limits at the LHC are generally
@@
 The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
-using toy MC datasets. These datasets are generated from the signal+background or background-only expectations respectively. 
+using toy MC datasets. These datasets are generated from the signal-plus-background or background-only expectations respectively. 
 For each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to observed data.
-The rates of each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
+The number of events in each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
 systematic uncertainties is taken into account by sampling a set of pseudo measurements $\tilde{\theta}'$ for each toy, based on the 
 pdf $p(\tilde{\theta}|\theta)$.
-The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background-only)
+The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal-plus-background or background-only)
 can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.
@@
 of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
-the properties of the Asimov dataset, a dataset in which the observation in 
+the properties of the Asimov dataset; a dataset in which the observation in 
 each bin exactly matches the predictions of the model. This method is used for the analysis
@@
 
-The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to
+The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to the
 observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
@@
 
-None of these distributions show hints of an excess.
-
-The model-independent 95\% CL expected and observed upper limits are shown in the left-hand side 
+None of these distributions show hints of an excess. The model-independent 95\% CL expected and observed upper limits
+on cross-section times branching ratio are shown in the left-hand side 
 panel of figure \ref{fig:hhh_results_modelindep}, with the right-hand side of the same figure
-showing the expected sensitivity per channel. These figures include the contribution from the 
+showing the expected limit per channel. These figures include the contribution from the 
 \tautau channel not described in this chapter. The expected upper limit
@@
 
-The couplings of the Higgs bosons to quarks and leptons, and of heavy Higgs bosons to other
+The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
 particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.
@@
 centre of the plots in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
-as the couplings of \PHiggslight to pairs of b--quarks and $\Pgt$ leptons are porportional 
+as the coupling of the \PHiggslight to pairs of b--quarks or $\Pgt$ leptons is porportional 
 to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
@@
 the analysis is not yet sensitive enough to actually observe this corridor.
-region.
 %Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
@@
 ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
-(see figure \ref{fig:hhh_results_modelindep} and \ref{fig:AZhUpperLimits}) are excluded.}
+(see figures \ref{fig:AZhUpperLimits} and \ref{fig:hhh_results_modelindep}) are excluded.}
 \label{fig:HhhandAZh2HDMOverlaid}
@@
 to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} we 
-can see that the cross-section times branching ratio in this model is, with exception of a few very small 
-areas, lower than the upper limits set by this analysis. This analysis on its own is
-therefore not sensitive enough to exclude any of the \mA-\tanb~region in this model. Note that
-at low \tanb ~ \mA$\neq$ \mH, and therefore \mH~is not in the studied range of $260-350$ GeV
+can see that the cross-section times branching ratio in this model is, with the exception of a few very small 
+areas, lower than the upper limits set by this analysis. This analysis on its own is,
+therefore, not sensitive enough to exclude any of the \mA-\tanb~region in this model. Note that
+at low \tanb, \mA$\neq$ \mH, and therefore \mH~is not in the studied range of $260-350$ GeV
 throughout the entire \mA-\tanb~plane shown here.
@@
 figure \ref{fig:HhhAZhMSSM2HDM}.
-The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
-very sensitive in this model. Combining the two analyses we do see that a slightly larger amount
+%The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
+%very sensitive in this model. 
+Combining the two analyses we do see that a slightly larger amount
 of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
 described for the plot on the right-hand-side of figure \ref{fig:HhhAndAZhlowtanb} are also visible in this figure. In a small region of phase
-space, at low \mA~and low\tanb, this scenario predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
-This region is therefore excluded, this is indicated by the red band.
+space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
+This region is therefore excluded, as indicated by the red band.
 

### 2016-11-29 Detector/Detector.tex
Fixing up detector chapter

@@
 is also used for proton--lead and lead--lead collisions.
-
-The \ac{LHC} does not operate on its own, a chain of accelerators leads
-the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
-of the \ac{CERN} accelerator complex.
 \begin{figure}[h!]
-\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
+\includegraphics[width=0.6\textwidth]{./Detector/Plots/LHC_default.jpg}
 \caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
@@
 \end{figure}
+The \ac{LHC} does not operate on its own: the protons are lead into
+it via a chain of accelerators. Figure \ref{fig:lhc_schematic} shows a schematic
+of the \ac{CERN} accelerator complex.
+
 Protons originate from hydrogen gas, where electrons are stripped off the 
@@
 using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
-a temperature of 1.9K and generating magnetic fields upwards of 8 Tesla.
+a temperature of 1.9K and generating magnetic fields of up to 8.4 Tesla.
 The beams collide at four points
 around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
-CMS%\cite{cms-jinst} guess we've cited this already
-, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
+\acs{CMS} \cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
 
@@
 standard model Higgs boson is 9-10 orders of magnitude smaller than the total p--p cross section.
-
 \begin{figure}[h!]
@@
 \end{figure}
-
 In order to be able to study these relatively rare processes, 
 the LHC operates at high instantaneous luminosity, defined as
-
 \begin{equation}\label{eqn:CMSLHC_luminosity}
-\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F.
+\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F,
 \end{equation}
-
-In this equation, $N_b$ is the number of protons per bunch, $n_b$ the number of
+where $N_b$ is the number of protons per bunch, $n_b$ the number of
 bunches per beam, $f_{\text{rev}}$ the revolution frequency, $\gamma$ the 
@@
 In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV, and during 
-this year 4.2 fb$^{-1}$ was delivered. The \ac{LHC} operated at a centre-of-mass energy of 13 TeV 
+this year 4.2 fb$^{-1}$ was delivered to \ac{CMS}. The \ac{LHC} operated at a centre-of-mass energy of 13 TeV 
 during 2016 too, when a total of 41.1 fb$^{-1}$ was delivered to \ac{CMS}.
@@
 separated by running year.
-
 \begin{figure}[h!]
@@
 \end{figure}
-
 The data-taking efficiency of CMS is not 100\%, for example the detector might be
@@
 certified as good for use in analyses if it is known that all relevant subdetectors
-were functioning correctly. In 2012 the certification efficiency was 90.4\%
+were functioning correctly. In 2012 the certification efficiency was 90.4\%,
 meaning all subdetectors were working well for a dataset corresponding to 19.7 fb$^{-1}$.
@@
 per bunch crossing was 21 in 2012\cite{cms-lumi-public}. The average number of
-interactions per bunch crossing lowered again at the start of Run 2, with
+interactions per bunch crossing was lower than this at the start of Run 2, with
 an average of 14 interactions per bunch crossing for the data collected
-during 2015. In the data-taking period up to August 2016 the average number of interactions
-per bunch crossing increased to 24\footnote{NoteToBeRemovedBeforeSubmission: Lumi pog letting us down 
-here, no references for what number to quote/no prescriptions for how to calculate it. Use of theoretical
-min bias cross section (80mb) vs min bias cross section tuned for pu reweighting (less than 70 mb both for
-2015 and 2016) can shift the average by 5 evts or more! The 2016 number uses the theoretical
-cross section (only reference to this are various sets of slides presented at conferences), 2015
-number based on the min bias cross section used for pu reweighting (iirc). Assuming the 2012 numer,
-for which there is a public figure, uses the theoretical mb cross section should probably re-calculate the
-number for 2015.}. Additional 
+during 2015 \cite{CMS-PAS-HIG-16-006}. In the data-taking period up to August 2016 the average number of interactions
+per bunch crossing increased to 24 \cite{CMS-PAS-HIG-16-037}. Additional 
 interactions on top of events of interest are referred to as pile-up.
@@
 in figure \ref{fig:cms_detector}.
-
 \begin{figure}[h!]
 \includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
-\caption{A blow-up view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
+\caption{A cutaway view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
 different sub-parts of the detector.}
@@
 
-Surrounding the interaction point is the silicon tracker, a cylinder 5.8 m in length and 2.6 m in 
-diameter. Surrounding the silicon tracker
-the lead-tungstate \ac{ECAL} is found, which in turn is enclosed
-by a brass scintilator \ac{HCAL}.
+The silicon tracker, a cylinder 5.8 m in length and 2.6 m in
+diameter, surrounds the interaction point. The tracker is 
+surrounded by the lead-tungstate \ac{ECAL}, which is enclosed
+by the brass scintillator \ac{HCAL}.
 
 The tracking and calorimeter systems are surrounded by a superconducting
-solenoid, 13 meter long and 6 meter in diameter and operating at 3.8 Tesla.
+solenoid, 13 m long, 6 m in diameter and operating at 3.8 Tesla.
 Charged particles are bent in this magnetic field, allowing for precise 
@@
 for a longer period of time. These requirements motivate the use of a silicon tracking
-system. When a charged particle passes through the silicon, an electron-hole pair
+system.
+
+In a silicon tracking system, the positions of particles are recorded
+due to the creation of drifting electron-hole pairs.
+When a charged particle passes through the silicon, an electron-hole pair
 is created, which drift under an applied electric field and produce a current
@@
 
-The tracker, providing coverage up to $|\eta|<2.5$ consists of 
+The tracker, providing coverage up to $|\eta|<2.5$, consists of 
 several different components. A schematic of the tracking detector, indicating
-the location of these components, is given in figure \ref{fig:CMS_tracker}.
+the locations of these components, is given in figure \ref{fig:CMS_tracker}.
 Nearest the interaction point the tracker is a pixel detector made
@@
 placed in the endcap region at either side. The barrel layers sit at radii of
-4.4, 7.3 and 10.2 cm and extend out up to $z=\pm 26.5$ cm. The disks are placed
+4.4, 7.3 and 10.2 cm and extend out to $z=\pm 26.5$ cm. The disks are placed
 at $z=\pm 34.5$ cm and $z=\pm 46.5$ cm. With this layout the pixel tracker can
@@
 
-Beyond the pixel detector the tracking system is made up of a silicon
-strip detector consisting of multiple different subsystems. The first part of the
+Around the pixel detector the tracking system is made up of a silicon
+strip detector divided into four subsystems. The first part of the
 silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
@@
 of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
-consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
+consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu$m.
 This part of the system provides up to nine $\phi$ measurements.
@@
 The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. This upgrade is needed to
-maintain the performance of the tracker as the pile-up increases \cite{cms-pixel-upgrade}. %or just replaced?
+maintain the performance of the tracker as the pile-up increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?
 
@@
 $\Pe^+\Pe^-$ pair production threshold, and ionisation 
-starts to dominate for electrons. The shower ionises the crystals, 
-which return to their normal state by emitting scintillation light. 
+starts to dominate for electrons. The shower ionises the atoms in the lead-tungstate
+crystals, which then emit scintillation light that is converted to a current by the 
+photodetectors. 
 As the crystals are 25.8 radiation lengths long, most of the shower
@@
 Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
-the subsystems it is made up of. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
+the subsystems it is made up of. The \ac{EB} 
 covers the pseudorapidity range up to $|\eta|<1.479$, with
 crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
-provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
+provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
 Each endcap is divided into two halves. In front of the endcaps 
@@
 calorimeters whose main use is to indentify neutral pions in the endcaps. Additionally
-they help electron identification and improve the resolution
+the preshower detectors aid the identification of electrons and improve the resolution
 of position determination. Each of the two preshower detectors consist
@@
 placed after each layer of radiators to measure the deposited energy. The 
-total thickness of the preshower comprises 3 radiation lenghts.
+total thickness of the preshower is 3 radiation lengths.
 
@@
 as the number of scintillation photons emitted by the crystals,
-and the amplification of the photodetectors are temperature dependent.
+and the amplification of the photodetectors, are temperature dependent.
 The nominal operating temperature, $18^{\circ}$C, is ensured by 
@@
 The energy resolution of the \ac{ECAL} can be parameterised as
-
 \begin{equation}\label{eqn:ecalres}
@@
 \end{equation}
-
 where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
@@
 and additional particles in the event, and the constant term comes
-from calibration errors, and non-uniformity of longitudinal response.
+from calibration errors and the non-uniformity of the longitudinal response.
 
@@
 \label{sec:CMSLHC_CMS_hcal}
-The \ac{ECAL} is surrounded by the \ac{HCAL}, which is important for the
+The \ac{ECAL} is surrounded by the \ac{HCAL} \cite{cms-jinst}, which is needed for the
 measurement of the energies of strongly interacting particles. As
@@
 coil is limited. The \ac{HCAL} design takes
-this into account by placing part of the subdetector outside the magnet coil. A schematic of the
-\ac{HCAL}, indicating the different components of the \ac{HCAL} is shown
+this into account by placing part of the calorimeter outside the magnet coil. An
+illustration of a quadrant of the
+\ac{HCAL}, indicating the positions of the subsystems, is shown
 in figure \ref{fig:CMS_HCAL}.
@@
 \includegraphics[width=0.9\textwidth]{./Detector/Plots/HCAL.png}
-\caption{Illustration of the \ac{HCAL}, indicating the geometry
-of the detector \cite{cms-jinst}.}
+\caption{Illustration of a quadrant of the \ac{HCAL}, showing the different
+subsystems of the detector \cite{cms-jinst}.}
 \label{fig:CMS_HCAL}
@@
 are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
-beyond this range. 
-The light from each tile is collected with a wavelength-shifting fibre, 
-which is read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
-has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
+beyond this range. The light from each tile is collected with a wavelength-shifting fibre, 
+which is read out using hybrid photodiodes.
+
+In the barrel, the \ac{HCAL}
+has a thickness of between 5.82 and 10.6 interaction length, which is not 
 sufficient to identify for example late-starting showers. The \ac{HO}, sitting
 outside of the magnet and using the coil as an additional absorber, extends the 
-thickness to at least 11.8 interaction lenghts. 
+thickness to at least 11.8 interaction lengths. 
 Like in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
 map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
-to a hybrid photodiode via wavelength shifting fibres.
+to a hybrid photodiode via wavelength-shifting fibres.
 %WTF: wavelength-shifting fibres
@@
 subjected to large radiation doses, requiring an extremely
-radiation hard active material. For this reason quartz
+radiation-hard active material. For this reason quartz
 fibres are used as active material. These fibres are embedded
@@
 and can be parameterised as 
-
 \begin{equation}\label{eqn:hcal_res}
@@
 \end{equation}
-
 where $S$ is the stochastic term, found to be 94.3\% %pm 1.2
@@
 Precise muon identification is one of the requirements of the \ac{CMS} 
-experiment. Good muon identification efficiency and precision muon momentum 
-resolution are very important, as muons appear as final states in many
-\ac{BSM} signatures the experiment is used to search for. In addition to
-that, final states with muons are very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays.
+experiment. Good muon identification efficiency and precise muon momentum 
+resolution are key to the success of the experiment, as muons are
+very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays. In addition to that,
+muons appear in the final states of many \ac{BSM} signatures the experiment is used to search for.
 
@@
 the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
-regions as both \ac{DT} and \ac{CSCs}, is used as a dedicated triggering system.
+regions as both \ac{DT} and \ac{CSCs}, are used as a dedicated triggering system.
 
 A cross-section of one quadrant of the detector, indicating
-the positions of the \ac{DT},\ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
-The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1}, providing
+the positions of the \ac{DT}, \ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
+The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1} \cite{cms-muon-upgrade}, providing
 additional layers of \ac{CSCs} and \ac{RPCs}.
@@
 \end{figure}
-
 The \ac{DT} consists of layers of drift cells which have a cross-section of $4.2 \times 1.3$ cm$^2$ and
@@
 measurements in the $\phi$ direction, while the resolution of the $z$ measurement
-is 130-400 $\mu$m\cite{cms-muon-7tev}.
-%Drift lines distorted by magnetic field parallel to the wires
+is 130-400 $\mu$m\cite{cms-muon-7tev}. %Drift lines distorted by magnetic field parallel to the wires
 
@@
 sensitive strips placed on these plates in the
-radial direction, to measure the muon coordinate in the  $r-\phi$ plane
+radial direction, to measure the muon coordinate in the  $r-\phi$ plane.
 Anode wires in between the cathode planes
@@
 \label{sec:CMSLHC_CMS_trigger}
-When the \ac{LHC} is operating under standard conditions, protons are collided at a rate
+When the \ac{LHC} is operating under design conditions, protons are collided at a rate
 of 40 MHz. This rate is too high for the \ac{DAQ} system to read out every event. In
@@
 it should be discarded. A decision has to be made within 3.2 $\mu$s, the maximum time during
-which data can be stored in the front-end electronics before being lost.
+which data can be stored in the \ac{L1} trigger before being lost.
 
@@
 The \ac{WLCG} pools the resources of computer centres at universities and research
-laboratories around the world, based on a system of tiers. The Tier 0, at \ac{CERN} and
+laboratories associated with \ac{LHC} experiments, based on a system of tiers. The Tier 0, at \ac{CERN} and
 the Wigner Research Centre for Physics in Budapest, performs the full reconstruction

### 2016-11-29 Objects/Objects.tex
Adding skeleton of object reco section

\chapter{Object Reconstruction}
\label{chap:objects}

In this chapter the physics objects necessary to be able to perform searches with \Pgt leptons
in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. The 
descriptions correspond to the algorithms as used during Run 2. Where there are differences
between the algorithms used in Run 1 and Run 2 this will be discussed at the end
of the relevant section.

\section{Particle Flow}
\label{sec:objects_pf}

\section{Tracks and vertices}
\label{sec:objects_pv}

\section{Electrons}
\label{sec:objects_ele}

\section{Muons}
\label{sec:objects_muo}

\section{Hadronic taus}
\label{sec:objects_tau}
Taus are unstable particles and they decay before reaching the detector. In 17.4 \% of 
cases they decay to muons and neutrinos, with an additional 17.8 \% decaying to electrons
plus neutrinos. The remaining 64.8 \% decay hadronically. Hadronically decaying
taus are characterised by narrow jets containing either one or three charged
particles ($\pi^{\pm}, K^{\pm}$) and 0,1, or two neutral pions. An overview
of the possible decay modes is given in table \ref{tab:hadronic_tau_decays}

\begin{table}[htp]
\begin{center}
\caption{Summary of hadronic tau decay modes, with the branching fraction, and intermediate resonance where relevant, indicated \cite{pdg-2014}}
\begin{tabular}{@{}lll@{}}
%\toprule
\textbf{Decay mode} & \textbf{Resonance} &\textbf{Branching fraction [\%]}\\
\midrule
\Ptaupm $\rightarrow$ h$^{\pm}$\Pnut & & 11.5\%\\
\Ptaupm $\rightarrow$ h$^{\pm}$\Ppizero\Pnut& $\rho$(770) & 26.0\% \\
\Ptaupm $\rightarrow$ h$^{\pm}$\Ppizero\Ppizero\Pnut & a$_{1}$(1260) & 9.5\% \\
\Ptaupm $\rightarrow$ h$^{\pm}$h$^{\mp}$h$^{\pm}$\Pnut & a$_{1}$(1260) & 9.8\% \\
\Ptaupm $\rightarrow$ h$^{\pm}$h$^{\mp}$h$^{\pm}$\Ppizero\Pnut & & 4.8\%\\
Other modes with hadrons & & 3.2\% \\
\midrule
Total & & 64.8\% \\
%\bottomrule
\end{tabular}
\label{tab:hadronic_tau_decays}
\end{center}
\end{table}

%CP from what I wrote in the HIG-16-006/HIG-16-037 analysis notes:
Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, which uses particle flow candidates to reconstruct and identify hadronic tau decays.
In the reconstruction step, particle-flow charged and neutral particles are grouped into combinations compatible with specific hadronic tau decay modes, and the 4-momentum
of the candidates is computed. In the identification step, discriminators that separate hadronic taus from quark and gluon jets and from electrons and muons are evaluated. \\
Taus in the hadrons plus strips algorithm are seeded by jets clustered with the anti-$k_{\text{T}}$ algorithm with a distance parameter $\Delta R = 0.4$.

To reconstruct the energy deposits $\pi^0$ candidates leave in the ECAL, photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
The e or $\gamma$ with highest $p_{\text{T}}$ that is not yet included in a strip is used to build a new strip.
The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest $p_{\text{T}}$ e or $\gamma$  within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is recomputed as the energy-weighted average of the electron/photon constituents in the strip.
This procedure is repeated until there are no more electrons or photons with $p_{\text{T}} > 0.5$~GeV  within the strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the $p_{\text{T}}$ or $E_{\text{T}}$ to be added to the strip and on the energy the strip already has, as\\

\begin{equation}\label{eqn:dynamicstrip}
\begin{split}
&\Delta \eta  = f(p_{\text{T}}^{e/\gamma}) + f(p_{\text{T}}^{\text{strip}})\\
&\Delta \phi  = g(p_{\text{T}}^{e/\gamma}) + g(p_{\text{T}}^{\text{strip}})\\
\end{split}
\end{equation}

Where $p_{\text{T}}^{e/\gamma}$ is the transverse momentum of the candidate to be added to the strip
and $p_{\text{T}}^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 \Delta\phi < 0.3$.

The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as~\ref{eqn:dynamicstripfg}.

\begin{equation}\label{eqn:dynamicstripfg}
\begin{split}
&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66}\\
&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}\\
\end{split}
\end{equation}

If the $\Sigma p_{\text{T}}$ of the strip is at least 2.5~GeV, it is considered as a $\pi^0$ candidate.\\
 To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
compatible with a certain decay mode if the set of cuts listed below is satisfied. If a candidate satisfies more than one of the hypotheses, the one that maximises the $p_{\text{T}}$ is retained.\\

The decay modes considered for reconstructing taus are:\\
\begin{itemize}
\item \textbf{One prong, 0 $\pi^0$ :} One charged particle, no strips.
\item \textbf{One prong, 1 $\pi^0$ :} One charged particle + one strip with mass $ 0.3 < m_{\tau} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV. The mass window upper limit is constrained to lie between 1.3 and 4.2 GeV.
\item \textbf{One prong, 2 $\pi^0$ :} One charged particle + two strips. The $\tau_{h}$ mass should be $0.4 < m_{\tau} < 1.2\sqrt{p_{\text{T}}/100}$~GeV. The upper limit on the mass window is constrained to lie between 1.2 and 4.0~GeV.
\item \textbf{Three prong, 0 $\pi^0$: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate within $\Delta z<0.4$~cm of the same vertex.
\end{itemize}

% End of C&P

\section{Jets and b-tagging}
\label{sec:objects_jets}

\subsection{Jet energy corrections}
\label{sec:objects_jets_jec}

\section{Missing energy}
\label{sec:objects_met}

\subsection{Recoil corrections}
\label{sec:objects_met_recoilcorr}

### 2016-11-30 Detector/Detector.tex
Adding Gavins comments on Detector chapter (save a few which are indicated)

@@
 Franco-Swiss border near Geneva. It
-is installed in the tunnel that previously hosted the Large Electron Positron accelerator
+is installed in the tunnel that previously hosted the Large Electron Positron accelerator \cite{lep-design}
 that was operated by \acf{CERN} between 1989 and 2000.
@@
 \begin{figure}[h!]
-\includegraphics[width=0.6\textwidth]{./Detector/Plots/LHC_default.jpg}
+\includegraphics[width=\textwidth]{./Detector/Plots/LHC_default.jpg}
 \caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
@@
 \end{figure}
-The \ac{LHC} does not operate on its own: the protons are lead into
+The \ac{LHC} does not operate on its own: the protons are fed into
 it via a chain of accelerators. Figure \ref{fig:lhc_schematic} shows a schematic
@@
 reached the protons are injected into the \ac{LHC} in two counter-rotating
-beams. In the \ac{LHC} ring the beams are further accelerated to the required centre of mass energy
+beams. In the \ac{LHC} ring the beams are further accelerated to the required centre-of-mass energy
 by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
@@
 standard model Higgs boson is 9-10 orders of magnitude smaller than the total p--p cross section.
-\begin{figure}[h!]
-\includegraphics[width=0.5\textwidth]{./Detector/Plots/crosssections2013.jpg}
-\caption{Total proton-proton cross section, and the cross-sections
-for several processes studied at the LHC \cite{stirling-crosssection}.
-The cross sections of these processes
-are often many orders of magnitude smaller than the total p--p cross section.}
-\label{fig:stirling_xs}
-\end{figure}
 In order to be able to study these relatively rare processes, 
@@
 
+\begin{figure}[h!]
+\includegraphics[width=0.5\textwidth]{./Detector/Plots/crosssections2013.jpg}
+\caption{Total proton-proton cross section, and the cross-sections
+for several processes studied at the LHC \cite{stirling-crosssection}.
+The cross sections of these processes
+are often many orders of magnitude smaller than the total p--p cross section.}
+\label{fig:stirling_xs}
+\end{figure}
+
 The \ac{LHC} began its first physics run in May 2010, colliding protons at
-a centre-of-mass energy of 7 TeV. The \ac{CMS} experiment recorded an integrated luminosity of 45 pb$^{-1}$
-during the rest of that year. In 2011 the \ac{LHC} continued operating at a centre-of-mass energy of 7 TeV, delivering
-6.1 fb$^{-1}$ to the \ac{CMS} experiment. The centre-of-mass energy was increased to 8 TeV
-for the 2012 data-taking period, during which the delivered integrated luminosity was 23.3 fb$^{-1}$.
-This completed Run 1 of the \ac{LHC}, after which the 2-year \ac{LS1} was used to 
-upgrade the \ac{LHC} and the detectors for collisions at a centre-of-mass energy of 13-14 TeV.
+a centre-of-mass energy of 7 TeV, and continued operation until the end of 2012. After this the 
+2-year \ac{LS1} was used to upgrade the \ac{LHC} and the detectors for collisions at a centre-of-mass
+energy of 13-14 TeV. In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of
+13 TeV. The integrated luminosity delivered to the \ac{CMS} experiment, separated by running year, is shown in
+figure \ref{fig:CMSLHC_intlumi}.
 
-In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of 13 TeV, and during 
-this year 4.2 fb$^{-1}$ was delivered to \ac{CMS}. The \ac{LHC} operated at a centre-of-mass energy of 13 TeV 
-during 2016 too, when a total of 41.1 fb$^{-1}$ was delivered to \ac{CMS}.
-The integrated luminosity as a function of time is shown in figure \ref{fig:CMSLHC_intlumi},
-separated by running year.
 \begin{figure}[h!]
@@
 \end{figure}
-The data-taking efficiency of CMS is not 100\%, for example the detector might be
+
+The data-taking efficiency of CMS is not 100\%, for example part of the detector might be
 switched off for part of the time collisions are ongoing. In 2012, the data-taking 
@@
 meaning all subdetectors were working well for a dataset corresponding to 19.7 fb$^{-1}$.
-The certification efficiency was 60.4 \% in 2015, leading to 2.3 fb${-1}$ of 
+Due to cryogenic issues the certification efficiency with the magnet operating
+at 3.8 Tesla was 60.4 \% in 2015, leading to 2.3 fb$^{-1}$ of 
 analysable data for which the full detector was operational. An additional 0.6 fb$^{-1}$
@@
 peak luminosity of $10^{32}$cm$^{-2}$s$^{-1}$. In 2012 peak
-luminosities of $7.7*10^{33}$cm$^{-2}$s$^{-1}$ were reached, with the peak luminosity in
-2015 being $5.1*10^{33}$cm$^{-2}$s$^{-1}$. Since July 2016
+luminosities of $7.7\cdot10^{33}$cm$^{-2}$s$^{-1}$ were reached, with the peak luminosity in
+2015 being $5.1\cdot10^{33}$cm$^{-2}$s$^{-1}$. Since July 2016
 the \ac{LHC} has been operating at instantaneous luminosities upwards of the 
-design luminosity, with peak luminosities of $1.5*10^{32}$cm$^{-2}$s$^{-1}$ reached
+design luminosity, with peak luminosities of $1.5\cdot10^{32}$cm$^{-2}$s$^{-1}$ reached
 in October 2016 \cite{cms-lumi-public}.
@@
 Due to the high operating luminosity, multiple proton-proton collisions per 
-bunch crossing are likely to occur. The average number of interactions
+bunch crossing are likely to occur. Additional interactions on top of events of 
+interest are referred to as pile-up. The average number of interactions
 per bunch crossing was 21 in 2012\cite{cms-lumi-public}. The average number of
@@
 during 2015 \cite{CMS-PAS-HIG-16-006}. In the data-taking period up to August 2016 the average number of interactions
-per bunch crossing increased to 24 \cite{CMS-PAS-HIG-16-037}. Additional 
-interactions on top of events of interest are referred to as pile-up.
+per bunch crossing increased to 24 \cite{CMS-PAS-HIG-16-037}.
 
@@
 To meet the demands of the \ac{LHC} physics programme, the
- \ac{CMS} detector was designed to be very perfomant in searches
+ \ac{CMS} detector was designed to perform very well in searches
 for physics at the TeV scale and to be able to 
@@
 
-The silicon tracker, a cylinder 5.8 m in length and 2.6 m in
+The silicon tracker, a cylinder \mbox{5.8 m} in length and \mbox{2.6} m in
 diameter, surrounds the interaction point. The tracker is 
@@
 The tracking and calorimeter systems are surrounded by a superconducting
-solenoid, 13 m long, 6 m in diameter and operating at 3.8 Tesla.
+solenoid, \mbox{13 m} long, \mbox{6 m} in diameter and operating at 3.8 Tesla.
 Charged particles are bent in this magnetic field, allowing for precise 
@@
 points along the beam direction. As such the transverse momentum and energy, 
-\pT~and~\ET are measured from the x- and y- components of the momentum and energy.
+\pT~and \ET~are measured from the x- and y- components of the momentum and energy.
 The azimuthal angle $\phi$ is measured in the x-y plane with respect to the x-axis, 
@@
 is used for accurate reconstruction of charged particle trajectories and 
-the precise reconstruction of secondary vertices, which are important to be
-able to indentify heavy-flavour particles. This means a small impact parameter
+the precise reconstruction of primary and secondary vertices, the latter being important for
+the identification of heavy-flavour particles. This means a small impact parameter
 resolution needs to be achieved, for which a highly granular system is required. 
@@
 each collision, an average of 1000 per bunch crossing (every 25 ns) at LHC design operation, the 
-system also needs to be fast-responding in order to reconstruct trajectories accurately.
+system also needs to be able to respond quickly in order to reconstruct trajectories accurately.
 At the same time, this large particle flux calls for a 
 radiation-hard design that is able to survive in this harsh environment
-for a longer period of time. These requirements motivate the use of a silicon tracking
+for a long period of time. These requirements motivate the use of a silicon tracking
 system.
@@
 the locations of these components, is given in figure \ref{fig:CMS_tracker}.
-Nearest the interaction point the tracker is a pixel detector made
+Nearest the interaction point is the pixel detector, made
 of 66 million silicon pixels, each 100 $\mu$m $\times$ 150 $\mu$m in size.
-The choice of this pixel size is driven by the achievable spatial resolution,
-which is 15-20 $\mu$m in the $r$ and $z$ directions in this case. Such a
+The choice of this pixel size is driven by the ability to achieve the desired spatial resolution,
+which is 15-20 $\mu$m in the $r-\phi$ and $z$ directions in this case. Such a
 precise resolution allows for 3D vertex reconstruction. The pixel
@@
 of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
-consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu$m.
+consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from \mbox{320-500 $\mu$m} and the the strip width ranges from $97-184 \mu$m.
 This part of the system provides up to nine $\phi$ measurements.
@@
 
-The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. This upgrade is needed to
+The pixel tracker will be upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade is needed to
 maintain the performance of the tracker as the pile-up increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?
@@
 made of nearly 76000 lead tungstate (PbWO$_4$) crystals. It has very
-good energy resolution, is highly granular and fast-responding, all qualities 
+good energy resolution, is highly granular and has a fast response, all qualities 
 which are needed to be able to detect $H\rightarrow \gamma\gamma$ decays.
@@
 lead tungstate crystals allow for the construction of a compact, highly 
-granular \ac{ECAL}. The compactness of the \ac{ECAL} is required in 
-order to be able to fit the calorimeters inside the bore of the magnet. 
+granular \ac{ECAL}. The compactness of the \ac{ECAL} is required  
+to fit inside the bore of the magnet. 
 As 80\% of the light from the crystals is emitted within 25 ns, that is
@@
 $\Pe^+\Pe^-$ pair production threshold, and ionisation 
-starts to dominate for electrons. The shower ionises the atoms in the lead-tungstate
+starts to dominate for electrons. The shower ionises [IS THIS WHAT HAPPENS?] the atoms in the lead-tungstate
 crystals, which then emit scintillation light that is converted to a current by the 
-photodetectors. 
+photodetectors. To record the light of the crystals, amplifying photodetectors need
+to be used, with avalanche photodiodes used in the barrel region, and vacuum phototriodes employed
+in the endcaps.
 As the crystals are 25.8 radiation lengths long, most of the shower
@@
 crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
-provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
+provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
 Each endcap is divided into two halves. In front of the endcaps 
 the preshower detectors, covering $1.653<|\eta|<2.6$ are sampling
-calorimeters whose main use is to indentify neutral pions in the endcaps. Additionally
+calorimeters whose main use is to identify neutral pions, decaying to two photons, 
+in the endcaps. Additionally
 the preshower detectors aid the identification of electrons and improve the resolution
@@
 
-To preserve the energy resolution, the \ac{ECAL} crystal and
-photodetector temperatures need to be kept stable within $\pm 0.05^{\circ}$C
+To preserve the energy resolution, the crystals and
+photodetectors need to be kept stable within $\pm 0.05^{\circ}$C
 as the number of scintillation photons emitted by the crystals,
@@
 supplying the detector with water at this temperature.
-
-To record the light yield of the crystals, amplifying photodetectors
-need to be used. In the \ac{EB} avalance photodiodes are employed
-for this, with vacuum phototriodes used in the \ac{EE}.
 
@@
 The stochastic term arises from fluctuations in lateral shower containment and 
-fluctuations in scintillation, the noise term due to noise from the electronics
+fluctuations in the scintillation yield, the noise term due to noise from the electronics
 and additional particles in the event, and the constant term comes
@@
 The \ac{ECAL} is surrounded by the \ac{HCAL} \cite{cms-jinst}, which is needed for the
-measurement of the energies of strongly interacting particles. As
+measurement of the energies of strongly interacting particles and \MET. As
 the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
@@
 In the barrel, the \ac{HCAL}
-has a thickness of between 5.82 and 10.6 interaction length, which is not 
+has a thickness of between 5.82 and 10.6 interaction lengths, which is not 
 sufficient to identify for example late-starting showers. The \ac{HO}, sitting
@@
 radiation-hard active material. For this reason quartz
-fibres are used as active material. These fibres are embedded
-in the steel absorber structure. Charged particles from the
+fibres are used. These fibres are embedded
+in a steel absorber structure. Charged particles from the
 shower initiated in the steel generate Cherenkov light in 
@@
 very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays. In addition to that,
-muons appear in the final states of many \ac{BSM} signatures the experiment is used to search for.
+muons appear in the final states of many of the \ac{BSM} signatures the experiment is searching for.
 
-The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
+The \ac{CMS} muon system \cite{cms-jinst} is designed of three different subsystems which
 are all necessary to ensure the identification requirements can be met. It is located
@@
 are 2.4 m long. The cells are filled with a mixture of %85\% 
-argon and carbon di-oxide gas.
+argon and carbon dioxide gas.
 Muons passing through the chamber ionise the gas, freeing electrons
@@
 There are also layers oriented orthogonal to the beam line, which give a measurement
-of the z-coordinate. Measurements of the spatial resolution were made
+of the z coordinate. Measurements of the spatial resolution were made
 during proton--proton running of the \ac{LHC} in 2010.
@@
 
-In the endcaps, where the muon rate is higher, the \ac{CSCs} provide
+In the endcaps, where both the muon rate and the radiation levels are higher, the \ac{CSCs} provide
 measurements of the muon track. These detectors are radiation-hard,
@@
 alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
-between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}.
+between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. ADD FORMULA
 
@@
 During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
-replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides amongst others 
-improved object isolation, hadronic tau identification, muon \pT~resolution and
+replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides amongst other 
+things improved object isolation, hadronic tau identification, muon \pT~resolution and
 jet finding with respect to the system used during Run 1.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./Detector/Plots/CMSTrigger.png}
+\includegraphics[width=0.7\textwidth]{./Detector/Plots/CMSTrigger.png}
 \caption{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
@@
 The calorimeter trigger starts from \ac{HCAL} and \ac{ECAL} energy deposits, 
-which are fed to the first layer of the trigger. This layer maps onto
-columns of the detector, receiving data from many bunch crossings. These data are passed
+which are fed to the first layer of the trigger, where it makes use of a time-multiplexed system. 
+The first trigger layer maps onto columns of the detector, receiving data from many bunch crossings. These data are passed
 on to the second layer of the trigger in a way that bundles data from a single bunch crossing, but
@@
 deposits, so that a sorted list of the best candidates can be passed to the global trigger.
+The trigger employed during Run 1, and the first year of Run 2, did not use time-multiplexing. Instead, 
+information from different regions of the detector were processed independently.
 Hits in the muon chambers are read out and passed to the track finder layer 
@@
 During the 2012 run of the \ac{LHC} the \ac{HLT} operated with an output
-capacity of around 1 kHz, for Run 2 this has increased. In August 2016, 
+capacity of around 1 kHz, for Run 2 this has been increased. In August 2016, 
 the \ac{HLT} output rate was 1.2 kHz for immediate data processing, with

### 2016-12-01 Detector/Detector.tex
Fixing up another comment on the detector chapter

@@
 $\Pe^+\Pe^-$ pair production threshold, and ionisation 
-starts to dominate for electrons. The shower ionises [IS THIS WHAT HAPPENS?] the atoms in the lead-tungstate
+starts to dominate for electrons. The shower excites the atoms in the lead-tungstate
 crystals, which then emit scintillation light that is converted to a current by the 
@@
 to be used, with avalanche photodiodes used in the barrel region, and vacuum phototriodes employed
-in the endcaps.
+in the endcaps. %Because of the larger radiation levels in the endcaps
 As the crystals are 25.8 radiation lengths long, most of the shower
@@
 absorber fits the constraints imposed by the environment due to its short interaction length
+%Nuclear interaction length is the mean path length required to reduce the numbers of relativistic charged particles by the factor 1/e, or 0.368, as they pass through matter.
+%Nuclear interaction length is the mean distance travelled by a hadronic particle before undergoing an inelastic nuclear interaction.
 of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
@@
 alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
-between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. ADD FORMULA
+between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. %ADD FORMULA
 

### 2016-12-02 Objects/Objects.tex
Adding a little bit about PF

@@
 
-\section{Particle Flow}
+\section{\acl{PF}}
 \label{sec:objects_pf}
+All stable particles are reconstructed and identified using the \ac{PF} algorithm, which
+combines the information from all of the different subdetectors of \ac{CMS}. This makes
+the identification of particles, and determination of position and momentum, as precise
+as possible. All of these particles are then used to build for example jets, \MET and hadronically
+decaying taus.
 

### 2016-12-05 Objects/Objects.tex
Adding section on PF and editing tau reco section

@@
 
+The \ac{PF} algorithm starts from charged particle tracks measured
+by the inner tracker, muon tracks measured in the muon system, and 
+energy deposits in the calorimeters. These energy deposits are combined
+using a clustering algorithm, so that stable neutral particles can be identified,
+separated from charged hadrons, and electrons and all Bremsstrahlung photons
+can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
+\ac{ECAL} endcaps, first and second \ac{PS} layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
+clustering employed in the \ac{HF}.
+%And to aid energy measurement of charged hadrons for which
+%tracks were low quality, or high pT
+The clustering algorithm used for \ac{PF} starts from \textit{cluster seeds},
+calorimeter cells with local energy maxima. Topological clusters are built by 
+merging neighbouring cells into the cluster, provided that the cells
+being merged in contain a certain minimum energy.
+The threshold is 800 MeV in the \ac{HCAL} and two standard deviations above the
+expected noise level in the \ac{ECAL}, meaning 80 MeV in the barrel and up 
+to 300 MeV in the endcaps. Cell energies can be shared between multiple
+\ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.
+
+Any given particle will usually give rise to multiple \ac{PF}
+elements in the different subdetectors. To provide full reconstruction
+of each particle, and avoid double counting,  the next step in the
+\ac{PF} algorithm is to link the different elements. This is
+achieved by defining a distance parameter between any two \ac{PF} elements
+in the event, which quantifies the link quality. Directly and indirectly
+linked elements are considered as input blocks to the reconstruction and
+identification algorithm. Links between charged tracks and calorimeter
+clusters are established by extrapolating the track from its last measured
+tracker hit to the \ac{PS} layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
+%typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
+%length.
+If the extrapolated track position is within the boundaries of the cluster, plus the size
+of one cell in each direction to account for gaps between cells and multiple scattering, the
+track is said to be linked to the calorimeter cluster. The distance is taken as the distance $\Delta R$ 
+between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
+to the ECAL from the track--tracker layer interaction points, and clusters can be 
+linked to the track as a possible Bremsstrahlung photon if the extrapolated tangent
+position is within the boundaries of the cluster.
+Links between calorimeter clusters are made when the cluster position in the
+more granular calorimeter is within the cluster of the less granular calorimeter,
+with the link distance again defined as the $\Delta R$ between two cluster positions.
+To determine links between charged tracks in the inner tracker and a muon track
+in the muon system, a global fit between the two tracks is performed, where the link
+is accepted if requirements on the maximum $\chi^2$ of this fit are met. This
+$\chi^2$ also determines the distance parameter.
+
+For each block, particles are identified following a sequence
+of tests. First, if there is a link between a tracker track and a muon system track,
+a particle flow muon is identified if the combined tracker and muon system
+momentum is compatible with the tracker-only momentum. %within three standard deviations
+The muon track is removed from the block before the next step of the algorithm.
+
+Secondly, tracks are refitted with the \ac{GSF}, the compatibility
+of the track with the already linked \ac{ECAL} clusters is assessed using
+\ac{BDTs} which take several variables into account. If the candidate
+passes, it is identified as a particle flow electron and the track and
+\ac{ECAL} clusters are removed from the block.
+
+Following this, remaining tracks lead to charged hadrons. The track is
+given the momentum from the track fit, assuming the mass of a charged pion. If
+the energy measured in the calorimeters is compatible with the momentum assigned
+to the track, within uncertainties, as charged hadron is identified and the
+momentum redefined by fitting the tracker and calorimeter measurements. If
+the energy of the calorimeter clusters linked to the track is significantly larger than the
+charged particle momentum from the track fit, additional overlapping neutral particles
+are identified. If the difference between tracker momentum and calorimeter
+energies is larger than the total energy registered in associated \ac{ECAL} clusters,
+a particle flow photon with energy equal to the total \ac{ECAL} energy is created.
+Any remaining momentum difference is assigned to a particle flow neutral hadron. If the momentum
+difference is smaller than the energy registered in associated \ac{ECAL} clusters 
+only a particle flow photon is created. %Justified by fact that
+%in jets 25% of the energy is carried by photons while neutral hadrons
+%leave only 3% of the jet energy in the ECAL. This fraction is reduced by one order of magnitued
+%for taus for which decays to final states with neutral hadrons are Cabbibo suppressed to a branching ratio of 
+%about a percent.
+
+Finally, any remaining \ac{ECAL} clusters not linked to a track give
+rise to particle flow photons, with any \ac{HCAL} clusters
+not linked to tracks giving rise to particle flow neutral hadrons.
+
 \section{Tracks and vertices}
@@
 
+\section{Jets and b-tagging}
+\label{sec:objects_jets}
+
+\subsection{Jet energy corrections}
+\label{sec:objects_jets_jec}
+
+\section{Missing energy}
+\label{sec:objects_met}
+
+\subsection{Recoil corrections}
+\label{sec:objects_met_recoilcorr}
+
 \section{Hadronic taus}
@@
 particles ($\pi^{\pm}, K^{\pm}$) and 0,1, or two neutral pions. An overview
-of the possible decay modes is given in table \ref{tab:hadronic_tau_decays}
+of the most common possible decay modes is given in table \ref{tab:hadronic_tau_decays}
 
@@
 \begin{center}
-\caption{Summary of hadronic tau decay modes, with the branching fraction, and intermediate resonance where relevant, indicated \cite{pdg-2014}}
+\caption{Summary of hadronic tau decay modes, indicating the branching fraction, and intermediate resonances where relevant \cite{pdg-2014}.}
 \begin{tabular}{@{}lll@{}}
@@
 
-%CP from what I wrote in the HIG-16-006/HIG-16-037 analysis notes:
-Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, which uses particle flow candidates to reconstruct and identify hadronic tau decays.
-In the reconstruction step, particle-flow charged and neutral particles are grouped into combinations compatible with specific hadronic tau decay modes, and the 4-momentum
-of the candidates is computed. In the identification step, discriminators that separate hadronic taus from quark and gluon jets and from electrons and muons are evaluated. \\
-Taus in the hadrons plus strips algorithm are seeded by jets clustered with the anti-$k_{\text{T}}$ algorithm with a distance parameter $\Delta R = 0.4$.
-
-To reconstruct the energy deposits $\pi^0$ candidates leave in the ECAL, photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
-The e or $\gamma$ with highest $p_{\text{T}}$ that is not yet included in a strip is used to build a new strip.
-The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest $p_{\text{T}}$ e or $\gamma$  within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is recomputed as the energy-weighted average of the electron/photon constituents in the strip.
-This procedure is repeated until there are no more electrons or photons with $p_{\text{T}} > 0.5$~GeV  within the strip window.
-The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the $p_{\text{T}}$ or $E_{\text{T}}$ to be added to the strip and on the energy the strip already has, as\\
+\subsection{Identification}
+\label{sec:objects_tau_id}
+Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
+which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT algorithm with a distance parameter $\Delta R = 0.4$. 
+As table \ref{tab:hadronic_tau_decays}
+shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a high
+probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays convert to
+\APelectron \Pelectron pairs in the tracker volume, which are bent in the magnetic field and 
+therefore cause showers dispersed in the $\phi$ direction in the \ac{ECAL}. Therefore, to 
+reconstruct the energy deposits \Ppizero candidates leave in the ECAL, 
+the photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
+The \Pe or \Pphoton with highest \pT that is not yet included in a strip is used to build a new strip.
+The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT \Pe or \Pphoton  
+within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
+recomputed as the energy-weighted average of the electron/photon constituents in the strip.
+This procedure is repeated until there are no more electrons or photons with \pT $>$ 0.5$~GeV  within the 
+strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the \pT or \ET to 
+be added to the strip and on the energy the strip already has, as
 
@@
 \begin{split}
-&\Delta \eta  = f(p_{\text{T}}^{e/\gamma}) + f(p_{\text{T}}^{\text{strip}})\\
-&\Delta \phi  = g(p_{\text{T}}^{e/\gamma}) + g(p_{\text{T}}^{\text{strip}})\\
+&\Delta \eta  = f(\pT^{\Pe/\Pphoton}) + f(\pT^{\text{strip}}) \notag \\
+&\Delta \phi  = g(\pT^{\Pe/\Pphoton}) + g(\pT^{\text{strip}})\\
 \end{split}
@@
 
-Where $p_{\text{T}}^{e/\gamma}$ is the transverse momentum of the candidate to be added to the strip
-and $p_{\text{T}}^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
-In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 \Delta\phi < 0.3$.
+Where $\pT^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
+and $\pT^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
+In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$.
 
-The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as~\ref{eqn:dynamicstripfg}.
+The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:
 
@@
 \begin{split}
-&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66}\\
-&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}\\
+&f(\pT) = 0.2\cdot \pT^{-0.66} \text{ and } \notag \\
+&g(\pT) = 0.35\cdot \pT^{-0.71}.\\
 \end{split}
@@
 
-If the $\Sigma p_{\text{T}}$ of the strip is at least 2.5~GeV, it is considered as a $\pi^0$ candidate.\\
+If the $\Sigma \pT$ of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
 To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
-compatible with a certain decay mode if the set of cuts listed below is satisfied. If a candidate satisfies more than one of the hypotheses, the one that maximises the $p_{\text{T}}$ is retained.\\
+compatible with a certain decay mode if the selection listed below is satisfied. 
+If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT is retained.\\
 
-The decay modes considered for reconstructing taus are:\\
+The decay modes considered for reconstructing hadronic taus are:\\
 \begin{itemize}
-\item \textbf{One prong, 0 $\pi^0$ :} One charged particle, no strips.
-\item \textbf{One prong, 1 $\pi^0$ :} One charged particle + one strip with mass $ 0.3 < m_{\tau} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV.
-The mass window upper limit is constrained to lie between 1.3 and 4.2 GeV.
-\item \textbf{One prong, 2 $\pi^0$ :} One charged particle + two strips.
-The $\tau_{h}$ mass should be $0.4 < m_{\tau} < 1.2\sqrt{p_{\text{T}}/100}$~GeV.
-The upper limit on the mass window is constrained to lie between 1.2 and 4.0~GeV.
-\item \textbf{Three prong, 0 $\pi^0$: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate within $\Delta z<0.4$~cm of the same vertex.
+\item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
+\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{\pT/100}$~GeV. For momenta
+less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
+\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{\pT/100}$~GeV. For momenta
+less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
+\item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate 
+within $\Delta z<0.4$~cm of the same vertex, and their total charge is required to be $\pm 1$.
 \end{itemize}
 
-% End of C&P
+\subsection{Isolation and discrimination against light leptons}
+\label{sec:objects_tau_iso}
 
-\section{Jets and b-tagging}
-\label{sec:objects_jets}
-
-\subsection{Jet energy corrections}
-\label{sec:objects_jets_jec}
-
-\section{Missing energy}
-\label{sec:objects_met}
-
-\subsection{Recoil corrections}
-\label{sec:objects_met_recoilcorr}
+\subsection{Differences between Run 1 and Run 2}
+\label{sec:objects_taus_diff}
+Broadly speaking the algorithm used for hadronic tau reconstruction during Run 1
+was similar to the Run 2 algorithm described earlier in this section. However, during
+Run 1 strips were reconstructed using a fixed size of $0.05 \times 0.20$ in $\eta \times \phi$.
+The dynamic size used in Run 2 was introduced to mitigate the effects of secondary particles
+with low \pT and multiple \APelectron\Pelectron conversions, resulting in particles ending up outside of 
+the strip window and making the hadronic tau seem less isolated than it actually is.
+SOMETHING ABOUT Jet->Tau FAKE RATES AND e->TAU Misidentification

### 2016-12-05 Objects/Objects.tex
Adding some more on tau iso

@@
 \label{sec:objects_pf}
-All stable particles are reconstructed and identified using the \ac{PF} algorithm, which
+All stable particles are reconstructed and identified using the \ac{PF} algorithm \cite{cms-pf-2009,cms-pf-2010-1,cms-pf-2010-2}, which
 combines the information from all of the different subdetectors of \ac{CMS}. This makes
@@
 recomputed as the energy-weighted average of the electron/photon constituents in the strip.
-This procedure is repeated until there are no more electrons or photons with \pT $>$ 0.5$~GeV  within the 
+This procedure is repeated until there are no more electrons or photons with \pT $> 0.5$~GeV  within the 
 strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the \pT or \ET to 
 be added to the strip and on the energy the strip already has, as
-
 \begin{equation}\label{eqn:dynamicstrip}
 \begin{split}
-&\Delta \eta  = f(\pT^{\Pe/\Pphoton}) + f(\pT^{\text{strip}}) \notag \\
-&\Delta \phi  = g(\pT^{\Pe/\Pphoton}) + g(\pT^{\text{strip}})\\
+&\Delta \eta  = f(p_{\text{T}}^{\Pe/\Pphoton}) + f(p_{\text{T}}^{\text{strip}}) \\
+&\Delta \phi  = g(p_{\text{T}}^{\Pe/\Pphoton}) + g(p_{\text{T}}^{\text{strip}})\\
 \end{split}
 \end{equation}
-
-Where $\pT^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
-and $\pT^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
+Where \pT$^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
+and \pT$^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
 In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$.
@@
 The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:
-
 \begin{equation}\label{eqn:dynamicstripfg}
 \begin{split}
-&f(\pT) = 0.2\cdot \pT^{-0.66} \text{ and } \notag \\
-&g(\pT) = 0.35\cdot \pT^{-0.71}.\\
+&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66} \text{ and } \\
+&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}.\\
 \end{split}
 \end{equation}
-
-If the $\Sigma \pT$ of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
+If the $\Sigma$ \pT of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
 To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
-compatible with a certain decay mode if the selection listed below is satisfied. 
+compatible with a certain decay mode if the selection listed below is satisfied. The charged particles
+and strips are required to be within the signal cone $R_{\text{signal}} = \frac{3.0}{p_{\text{T}}[GeV]}$, always
+required to be $0.05 < R_{\text{sig}} < 0.1$.
 If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT is retained.\\
 
-The decay modes considered for reconstructing hadronic taus are:\\
+The decay modes considered for reconstructing hadronic taus are:
 \begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
 \item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
-\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{\pT/100}$~GeV. For momenta
+\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV. For momenta
 less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
-\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{\pT/100}$~GeV. For momenta
+\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}$~GeV. For momenta
 less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
@@
 \label{sec:objects_tau_iso}
+Requiring the reconstructed $\Pgt_{h}$ to be isolated reduces the jet $\rightarrow\Pgt_{h}$ fake rate. The isolation
+can be defined using a cut--based discriminator using the isolation sum,
+\begin{equation}\label{eqn:cutbased_iso}
+I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm }) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm }) ),
+\end{equation}
+where the first term denotes the sum of the transverse momenta of all charged particles not part
+of the identified hadronic tau,  with \pT $> 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the 
+direction of the hadronic tau, with charged particle tracks required to be compatible with having
+originated from the $\Pgt_{h}$ production vertex within $d_Z < 0.2$ cm. The second term denotes the sum
+of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the direction
+of the hadronic tau. The effect of pile--up on this term is accounted for by subtracting the sum of the momenta of charged
+particles with \pT $ > 0.5$ GeV, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
+tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
+a $\Delta \beta$ factor of 0.2.
+
+In addition to the isolation sum, a selection on the sum of transverse momenta
+of electrons and photons included in strips but which are locaetd outside of the signal cone,
+\begin{equation}\label{eqn:ptouter_iso}
+p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt}.
+\end{equation}
+An  MVA $\tau_{h}$ isolation discriminator combines isolation variables with $\tau$ lifetime information into a BDT to discriminate between $\tau_{h}$ decays and quark and gluon jets.
+The variables used as input are:\\
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item The charged-and neutral-particle isolation sums
+\item The reconstructed $\tau_{h}$ decay mode
+\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
+\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
+\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
+\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
+\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
+\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
+\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
+\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
+\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
+\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
+\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outsie of the signal cone.
+\end{itemize}
+
+Figure \ref{fig:tau_iso_efficiency} compares the \Pgt identification efficiency with the
+jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
+MVA isolation discriminator, as well as the cut--based isolation discriminator based
+on isolation sum and $\p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
+discriminator performs best.
+
+\begin{figure}
+\includegraphics[width=0.7\textwidth]{./Objects/Plots/TauIsolationPlot.png}
+\caption{Something about tau isolation}
+\label{fig:tau_iso_efficiency}
+\end{figure}
 

### 2016-12-07 Objects/Objects.tex
Adding more object stuff

@@
 between the algorithms used in Run 1 and Run 2 this will be discussed at the end
-of the relevant section.
+of the relevant section. Section \ref{sec:objects_pv} discusses the algorithms
+used to reconstruct charged tracks in the inner tracker, with section \ref{sec:objects_ele}
+describing how these tracks are combined with \ac{ECAL} energy deposits to reconstruct electrons.
+In section \ref{sec:objects_muo} the combination of charged tracks in the inner tracker with
+hits in the muon chambers to form reconstructed muons will be discussed. Section \ref{sec:objects_pf}
+describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
+all stable particles, which is of particular importance for the reconstruction of jets, missing transverse
+energy and hadronic taus as discussed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
+respectively.
+
+\section{Tracks and vertices}
+\label{sec:objects_pv}
+To reconstruct the trajectories of charged particles, and therefore
+their momenta and positions, from the hits these particles leave in the 
+inner tracker, dedicated algorithms are required. In \ac{CMS} the
+\ac{CTF} algorithm is used. This algorithm performs four steps:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item Initial estimates of the parameters of the trajectory are given by track seeds, providing track candidates found using hits in 2 or 3 layers of the inner tracker
+\item The track seeds are extrapolated using a Kalman filter \cite{trk-kf}, which extrapolates the seeding trajectories along the expected flight path of a charged particle 
+and adds additional matched hits it finds in the tracker layers to the track.
+\item After the extrapolation has reached the final tracker layers, the Kalman filter is run again, now with the full set of hits that have been found in the previous step.
+This provides the best estimate of the track parameters
+\item Tracks that fail a specified set of quality criteria are rejected
+\end{itemize}
+
+These four steps are repeated six times. After each iteration
+the hits associated with reconstructed tracks are removed, and the settings
+of the algorithm updated, so as to be able to reconstruct as many
+tracks as possible. The tracking efficiency for muons and pions was measured in p--p
+collisions at $\sqrt{s} = 7$ TeV and found to be $ > 98.5\%$ for tracks
+with \pT $ > 500 $ MeV and $ > 99 \%$ for tracks with \pT $ > 2 $ GeV \cite{cms-trk-7tev}.
+
+%The tracking software at CMS is commonly referred to as the Combinatorial Track Finder (CTF), which is an adaptation of the combinatorial Kalman filter [29–31], which in turn is an extension of the Kalman filter [32] to allow pattern recognition and track fitting to occur in the same frame- work.
+The collection of reconstructed tracks is produced by multiple passes (iterations) of the CTF track reconstruction sequence, in a process called iterative tracking.
+%Kalman filter : In its linear form the Kal- ,nan filter is the optimal recursive estimator of the state vector of a (discrete) linear dynamic system.
+In such a system the evolution of the state vector is described by a linear transformation plus a random disturbance w, which is the process noise
+
+The reconstructed tracks are used to determine the positions of all interaction
+vertices in the event. Primary vertices are reconstructed by clustering
+tracks that appear to have originated from the same vertex, then fitting 
+for the position of the vertex using the associated tracks. The tracks 
+are clustered using the \ac{DA} algorithm \cite{vtx-da}, which identifies
+the most probable vertex candidates and assigns tracks to them. Vertex
+candidates with at least two associated tracks are fitted using an adaptive
+vertex fitter \cite{vtx-adaptivefit} to obtain the best estimate
+of the vertex position as well as an indicator for the success of the fit.
+Each track is assigned a weight $w_i$ between 0 and 1 which reflects the probability
+that it belongs to the vertex it is associated with. If the track is consistent
+with the vertex position the weight will be closer to 1, if not the weight 
+will be smaller. Using this the number of degrees of freedom in the fit
+can be defined as
+\begin{equation}\label{eqn:pv_ndof}
+n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
+\end{equation}
+which is strongly correlated with the number of tracks arising from the interaction region
+and can therefore be used to select genuine interactions. For the analysis
+presented in chapter \ref{chap:hhh}, which uses data collected during Run 1, to select the primary vertex, 
+this variable
+was required to be greater than 4, in addition to requirements on the distance between
+the vertex and the nominal interaction point ($\Delta z < 24$ cm and $\Delta x-y < 2$ cm). 
+The primary vertex was then taken as the vertex passing these quality criteria that 
+had the largest scalar sum \pT of associated tracks. For the Run 2 analyses presented
+later the quality requirements were removed and the primary vertex, the vertex
+of the hard scattering process, is simply taken as the reconstructed vertex with
+largest scalar sum \pT of associated tracks.
+The resolution of the z--coordinate of the primary vertex was measured in
+collisions at $\sqrt{s}=7$ TeV and depends strongly on the number of tracks
+associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{./Objects/Plots/PrimaryVertexRes.png}
+\caption{Resolution of the z--coordinate of reconstructed primary vertices
+as a function of the number of tracks associated with the vertex, 
+for minimum--bias events in red and for
+events with many jets in black. The resolution improves
+with larger numbers of tracks \cite{cms-trk-algos}.}
+\label{fig:objects_tracks_pvres}
+\end{figure}
+
+\section{Electrons}
+\label{sec:objects_ele}
+Electrons are reconstructed by combining tracks reconstructed
+in the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
+A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
+described in section \ref{sec:objects_pf}. Because electrons lose on average 33-86\% of
+their energy by radiating photons before the \ac{ECAL} is reached, depending on the thickness of
+the intervening material. To accurately reconstruct the energy of the electron it is
+important to catch the energies of photons, which are spread in the $\phi$ direction
+due to the magnetic field. Therefore \textit{supercluster} algorithms are needed to perform
+the clustering. In this approach the clustering
+is done by defining a seed crystal as the one containg the most energy deposited
+in a region being considered and having a certain minimum transverse energy.
+In the barrel arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
+to the cluster, stepping sideways in both directions in $\phi$, if this
+array contains a minimum energy deposit. These clusters are grouped into 
+superclusters if each distinct cluster has a seed array with a minimum energy deposit.
+In the endcaps the clusters combined into superclusters are arrays of $5\times 5$ crystals,
+merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.
+
+Because the electrons radiate bremsstrahlung photons in the tracker, the
+change in electron track curvature is large. The reconstruction of these
+tracks using the \ac{CTF} is compromised as a result of this, and 
+therefore a dedicated tracking algorithm is used. For high \pT electrons
+the best efficiency is reached by using an \ac{ECAL}-based track seeding
+algorithm which extrapolates the position and energy of the supercluster
+to the first layers of the tracker to determine rough areas to look for
+tracker seeds in. Once the seeds have been determined they are extrapolated
+and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the Kalman Filter, which 
+approximates the non-Gaussian energy loss in each layer by the combination of 
+Gaussian distributions rather than the single Gaussian used in the Kalman filter.
+
+%Once the hits are collected, a GSF fit is performed to estimate the track parameters.
+The energy loss in each layer is approximated by a mixture of Gaussian distributions.
+A weight is at- tributed to each Gaussian distribution that describes the associated probability.
+Two estimates of track properties are usually exploited at each measurement point that correspond either to the weighted mean of all the components, or to their most probable value (mode).
+
+To be identified as an electron, a particle has to be reconstructed as
+an electron by the \ac{PF} algorithm, and must in addition pass
+more advanced identification criteria based on some of the variables used in the
+standalone electron reconstruction, which provide separation power from backgrounds
+such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
+decays. Both cut--based and MVA--based algorithms are available. For the selection of electrons in 
+the analyses presented in later chapters these MVA--based algorithms are usually used, 
+with exceptions for the loose identification criteria required for veto-electrons. 
+The variables used to train the electron identification BDT are:
+
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
+label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
+$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
+respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
+of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
+\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
+\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
+\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
+\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
+\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
+ and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
+\end{itemize}
+
+\subsection{Isolation}
+The identification requirements discussed up to now reduce the backgrounds 
+from misidentified electrons, but do not eliminate them completely. If jets are
+misidentified as electrons, or an electron resulting from a heavy--flavour 
+decay is identified, the electron is not isolated. Therefore requirements
+on the electron isolation can reduce these backgrounds even further.
+Different isolation definitions are used in \ac{CMS}, for the analyses presented
+in later chapters a combined isolation variable is defined as:
+\begin{equation}\label{eqn:electron_reliso
+I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
+\end{equation}
+Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
+of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
+The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
+hadrons associated with the primary vertex and within 
+Where \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} hadrons
+associated with the primary vertex
+
+Where $P_{T}(\text{charged})$ corresponds to the $P_{T}$ of all charged hadronic candidates,
+$E_{T}(\text{photon, neutral})$ to the transverse energy of all photon and neutral hadron candidates, and $\Delta \beta$ is the energy
+esitmate of neutral particles due to pileup, which is taken to be 0.5.
+
+\section{Muons}
+\label{sec:objects_muo}
 
@@
 \label{sec:objects_pf}
-All stable particles are reconstructed and identified using the \ac{PF} algorithm \cite{cms-pf-2009,cms-pf-2010-1,cms-pf-2010-2}, which
+All stable particles are reconstructed and identified using the \ac{PF} algorithm \cite{cms-pf-2009,cms-pf-2010-commfirst,cms-pf-2010-2}, which
 combines the information from all of the different subdetectors of \ac{CMS}. This makes
@@
 
-\section{Tracks and vertices}
-\label{sec:objects_pv}
-
-\section{Electrons}
-\label{sec:objects_ele}
-
-\section{Muons}
-\label{sec:objects_muo}
-
 \section{Jets and b-tagging}
@@
 and \pT$^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
-In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$.
+In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$ \cite{cms-tau-2015}.
 
@@
 In addition to the isolation sum, a selection on the sum of transverse momenta
-of electrons and photons included in strips but which are locaetd outside of the signal cone,
+of electrons and photons included in strips but which are located outside of the signal cone,
 \begin{equation}\label{eqn:ptouter_iso}
@@
 \item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
-\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outsie of the signal cone.
+\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outside of the signal cone.
 \end{itemize}
@@
 MVA isolation discriminator, as well as the cut--based isolation discriminator based
-on isolation sum and $\p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
-discriminator performs best.
+on isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
+discriminator has better performance than the cut-based discriminator alone.
 
@@
 \includegraphics[width=0.7\textwidth]{./Objects/Plots/TauIsolationPlot.png}
-\caption{Something about tau isolation}
+\caption{jet$\rightarrow \Pgt_{h}$ fake rate versus $\Pgt_{h}$ identification efficiency for \htotautau events,
+comparing the MVA-based discriminator in red with the cut-based isolation discriminator in pink. Tighter working points
+give lower hadronic tau identification efficiencies and lower fake rates. The MVA-based discriminator
+has a lower fake rate than the cut-based discrminator for the same $\Pgt_{h}$ identification efficiency \cite{cms-tau-2015}.}
 \label{fig:tau_iso_efficiency}
 \end{figure}
+
+In order to reduce the $Pe\rightarrow\Pgt_h$ and $\Pgm\rightarrow\Pgt_h$ fake rate, 
+anti-electron and anti--muon discriminators are used. 
+The anti--electron discriminator is a BDT-based discriminator with the following input variables:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
+\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
+\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
+\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
+\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
+\item The \pT weighted RMS distances in $\eta$ and $\phi$ between the photons in any strip and the leading 
+charged track (calculated separately for photons inside and outside the $\Pgt$ signal cone)
+\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
+\item $(p_{in} - p_{out})/p_{in}$
+\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
+\item The ratio between the total \ac{ECAL} energy and inner track momentum
+\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
+\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
+\item $\chi^2/Ndof$ of the GSF track fit
+\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
+similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
+\end{itemize}
+
+Five working points are provided, ranging from very loose to very tight.
+
+The anti--muon discriminator is a cut-based discriminant, for which two working points are provided:\\
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item \textbf{Loose:} The $\tau_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or when the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is $<0.2\cdot p_{\text{leading track}}$.
+Otherwise it passes the discriminator
+\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
+\end{itemize}
 
@@
 Broadly speaking the algorithm used for hadronic tau reconstruction during Run 1
-was similar to the Run 2 algorithm described earlier in this section. However, during
+was similar to the Run 2 algorithm described earlier in this section \cite{cms-tau-run1}. However, during
 Run 1 strips were reconstructed using a fixed size of $0.05 \times 0.20$ in $\eta \times \phi$.
@@
 the strip window and making the hadronic tau seem less isolated than it actually is.
-SOMETHING ABOUT Jet->Tau FAKE RATES AND e->TAU Misidentification
+In addition, the anti--electron discriminator MVA was trained with fewer input variables and its performance
+was therefore not as good as the Run 2 version.

### 2016-12-08 Hhh/Hhh.tex
Adding muon reconstruction section

@@
 \chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
-\label{sec:hhh}
+\label{chap:hhh}
 In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 

### 2016-12-08 Objects/Objects.tex
Adding muon reconstruction section

@@
 \subsection{Isolation}
+\label{sec:objects_ele_iso}
 The identification requirements discussed up to now reduce the backgrounds 
@@
 Different isolation definitions are used in \ac{CMS}, for the analyses presented
-in later chapters a combined isolation variable is defined as:
-\begin{equation}\label{eqn:electron_reliso
+in later chapters a combined relative isolation variable is defined as:
+\begin{equation}\label{eqn:electron_reliso}
 I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
@@
 The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
-hadrons associated with the primary vertex and within 
-Where \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} hadrons
-associated with the primary vertex
-
-Where $P_{T}(\text{charged})$ corresponds to the $P_{T}$ of all charged hadronic candidates,
-$E_{T}(\text{photon, neutral})$ to the transverse energy of all photon and neutral hadron candidates, and $\Delta \beta$ is the energy
-esitmate of neutral particles due to pileup, which is taken to be 0.5.
+hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
+the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
+run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
+The contribution from neutral particles due to pile--up needs to be subtracted from
+this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
+with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
+CITE SOMETHING!
 
@@
 \label{sec:objects_muo}
+Muons are reconstructed by combining tracker tracks and tracks
+from the muon system \cite{cms-muon-reco}. Two complementary approaches are used for this,
+\textit{Global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
+tracks reconstructed in the muon system and searches for a matching
+tracker track, then re-applies the Kalman filter on the combination
+of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
+tracks in the inner tracker which pass requirements on momentum to be considered
+a muon candidate track. The trajectory is then extrapolated to the muon systems and
+considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
+Due to the requirement of a single muon segment this method is more efficeint than the global muon
+reconstruction for muons with \pT smaller than 5 GeV \cite{cms-muon-reco}.
+For muons with \pT greater than 200 GeV, the momentum resolution is improved
+by the global muon reconstruction \cite{cms-muon-cosmics-perf}.
+
+The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
+for muons with \pT up to 100 GeV and found to range from 1--6\% depending
+on detector region. For muons with \pT between 100 GeV and 1 TeV the momentum resolution
+was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
+%At values of the transverse momentum pT below about 200 GeV/c, the momentum resolution for a muon track is driven by measurements in the silicon tracker.
+As a particle’s momen- tum increases and the curvature of its corresponding track decreases, however, momentum resolution in the tracker becomes limited by position measurement resolution (including mis- alignment effects).
+One can then benefit from the large lever arm and 3.8 T magnetic field in the region between the tracker and the muon system by including hits in the muon chambers.
+
+For global muon reconstruction non-muon backgrounds are small,
+though there can be small effects from hadronic showers not fully
+contained in the \ac{HCAL}. A larger contribution is expected
+from real muons originating from for example decays of hadrons. These
+backgrounds can be reduced by applying additional identification criteria.
+
+For the analysis presented in chapter CHAPMSSM additional ``Medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
+Apart from having passed either the global or tracker muon reconstruction, the fraction
+of valid tracker hits must be greater than 49\%. Additional requirements are made on the
+$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
+position matching, on the kink finder in the inner tracker, and the segment compatibility. The segment
+compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
+the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
+a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
+The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
+tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
+is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
+The compatibility of the tracker- and standalone-reconstructed position is evaluated
+by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
+compatibility there.
+
+To pass the identification, global- or tracker muons
+with a large enough fraction of tracker hits must  \textbf{either} 
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item The muon is reconstructed by the global muon reconstruction algorithm
+\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
+\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
+\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
+\item The segment compatibility is $>$ 0.303
+\end{itemize}
+\textit{or}:
+\begin{itemize}
+\item The segment compatibility is $>$ 0.451
+\end{itemize}
+
+In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
+was used, muons were required to pass ``Tight'' identification requirements \cite{cms-muon-reco}. 
+The criteria are
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item The muon must be reconstructed by the global muon algorithm
+\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
+\item The global track fit must include hits from at least one chamber in the muon system
+\item The inner tracker track must be matched to muon segments in at least two muon stations (ie the muon must be reconstructed as a tracker muon too)
+\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
+\end{itemize}
+
+\subsection{Isolation}
+\label{sec:objects_muo_iso}
+As described for electrons in section \ref{sec:objects_ele_iso}, placing isolation 
+requirements on muons will also reduce backgrounds from misidentified jets and heavy--flavour
+decays. The isolation variable used for muons is very similar to the one described for
+electrons in equation \ref{eqn:electron_reliso}, however the cone around the direction of the
+muon was chosen as $\Delta R = 0.4$ both during Run 1 and Run 2.
 

### 2016-12-09 Hhh/Hhh.tex
Adding part of jets section

@@
 In this method a demotion or promotion probability is assigned to every
-jet as in equation \ref{eqn:promotedemote}.
+jet as:
 \begin{align}\label{eqn:promotedemote}
 &P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
-&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
+&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1},
 \end{align}
-In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
+Where $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
 the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)

### 2016-12-09 Objects/Objects.tex
Adding part of jets section

@@
 \label{sec:objects_jets}
+Many quarks and gluons are produced in the collisions at the \ac{LHC},
+fragmenting and hadronising immediately and forming collimated
+jets of particles. These particle jets need to be combined
+into single objects so the properties of the original particles can
+be measured.
+
+The particles identified by the \ac{PF} algorithm
+are clustered into jets using the anti-\kT algorithm \cite{antiKT} as implemented
+in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
+define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
+particles) $i$ and 
+object $j$, and $d_{iB}$ denoting the distance between 
+object $i$ and the beam. The smallest of the distances
+is defined and if this is a distance between object i and an object j, objects
+i and j are combined. If $d_{iB}$ is the smallest distance, object i
+is called a jet and removed from the list of objects. In the anti-\kT algorithm
+these distance parameters are defined as:
+\begin{align}\label{eqn:objects_antikt}
+d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\\
+d_{iB} = p_{\text{T}}^{-2},
+\end{align}
+where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
+between the objects i and j in rapidity-azimuthal angle space. The radius
+parameter $R$ was chosen as 0.5 during Run 1 CITATION and as 0.4 during Run 2 \cite{cms-jets-run2}. 
+This algorithm is collinear-- and infrared--safe, which means that the number of jets
+is not affected by the emission of soft collinear gluons or parton splitting. 
+The effects of pile--up particles on the jet energy and substructure can be
+mitigated using several methods. For the analysis presented in CHAPMSSM a
+\ac{CHS} technique is employed \cite{cms-jets-run2}.  In this method
+charged hadronic \ac{PF} candidates not associated with the primary vertex 
+are not considered in the clustering. For the analysis presented in
+chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
+based on vertex- and jet shape information was used to reject jets due to pile--up.
 
@@
 \label{sec:objects_jets_jec}
+
+\subsection{B-tagging}
+\label{sec:objects_jets_btag}
 

### 2016-12-14 Objects/Objects.tex
Finishing text of objects section (pre whittling it all down and adding figures)

@@
 this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
-with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
-CITE SOMETHING!
+with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.
 
@@
 between the objects i and j in rapidity-azimuthal angle space. The radius
-parameter $R$ was chosen as 0.5 during Run 1 CITATION and as 0.4 during Run 2 \cite{cms-jets-run2}. 
+parameter $R$ was chosen as 0.5 during Run 1 \cite{cms-jec-2011} and as 0.4 during Run 2 \cite{cms-jets-run2}. 
 This algorithm is collinear-- and infrared--safe, which means that the number of jets
@@
 \label{sec:objects_jets_jec}
+The energy measured for a jet in the detector is usually different from 
+the true particle jet at hadron level. A correction is applied to both
+jets in data and jets in \ac{MC} to match the measured and true
+energies as
+\begin{equation}\label{eqn:objects_jec}
+p_{\mu}^{\text{corr}} = \mathcal{C}\cdot p_{\mu}^{\text{raw}},
+\end{equation}
+
+where $\mathcal{C}$ is a correction factor broken down into different
+components as \cite{cms-jec-2011}
+\begin{equation}\label{eqn:objects_jec_corrfac}
+\mathcal{C} = \text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
+\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
+\cdot \text{C}_{\text{abs}}(p_{\text{T}}'').
+\end{equation}
+
+Here $\text{C}_{\text{offset}}$ is an offset correction, $\text{C}_{\text{MC}}$ an
+\ac{MC} calibration factor, $\text{C}_{\text{rel}}$ a relative residual correction
+factor and $\text{C}_{\text{abs}}$ an absolute residual correction factor. The corrections
+are applied in sequence with $p_{\text{T}}'$ the transverse momentum 
+of the jet after applying the offset correction and $p_{\text{T}}''$ the \pT of the
+jet after all of the preceding corrections.
+
+The offset correction $\text{C}_{\text{offset}}$ estimates and subtracts the energy
+not associated with the hard scatter. The additional energy this correction
+aims to address includes contributions from electronics noise and pile--up. This is
+estimated on an event--by--event basis based on the average--\pT density
+per unit area $\rho$ and the area of the jet $A$ \cite{jet-area}. The factor $\rho$ includes
+constributions from pile--up, electronics noise and the \ac{UE} of the hard interaction, the 
+latter of which should not be corrected for and therefore the average expected contribution
+from the underlying event $\rho_{<\text{UE}>}$ should be subtracted from $\rho$.
+
+The \ac{MC} calibration factor $\text{C}_{\text{MC}}$ corrects the energy of reconstructed
+jets so that is is on average equal to the energy of jets in \ac{MC} events. This
+factor is measured in simulated multi--jet events, measuring the response $\mathcal{R} = \frac{p_{\text{T}}^{\text{reco}}}{p_{\text{T}}^{\text{gen}}}$
+with $p_{\text{T}}^{\text{gen}}$ the generator--level \pT of the jet. The correction
+factor $\text{C}_{\text{MC}}$ is defined as $\text{C}_{\text{MC}} = \frac{1}{<\mathcal{R}>}$.
+
+A di--jet \pT-balancing technique \cite{cms-jec-2011}
+is used to measure the response of a jet at any $\eta$ relative
+to the jet energy response in the region $|\eta|<1.3$, such that 
+the relative residual correction factor makes the response flat
+as a function of $\eta$. This is achieved by requiring a reference jet
+in the central region of the detector ($|\eta|<1.3$), where
+the response is flat, and a probe jet at any 
+$\eta$ value. The relative response, in bins of $\eta$ and \pT  is determined by
+averaging the balancing function $\frac{p_{\text{T}}^{\text{probe}} - p_{\text{T}}^{\text{reference}}}{p_{\text{T}}^{\text{average}}}$.
+
+%The central region is chosen as a reference because of the uniformity of the detector, the small variation of the jet energy response, and because it provides the highest jet pT-reach.
+
+The absolute energy scale correction factor is designed to
+make the response uniform in \pT. It is measured using the \ac{MPF} method \cite{cms-jec-2011}
+ using samples of \Pphoton+jets and \PZ+jets events. This method relies on the fact that \Pphoton+jets
+and \PZ+jets events have no intrinsic missing energy, and so any measured \MET
+is used to calibrate the \pT response of jets in the event.
+
+Uncertainties on the jet energy scale are propagated through to analyses
+and is driven by uncertainties in the energy density used for pile--up
+subtraction, the photon energy scale, and the extrapolation required in the
+\ac{MPF} method.
+
+%The track-based jet types (JPT and PF) require much smaller correction factors because the charged component of the jet shower is measured accurately in the CMS tracker which extends up to |η| = 2.4.
+The fast rise of the correction factor for JPT jets in the region 2.0 < |η| < 2.5 is explained by the fact that part of the jets lying in this region extends beyond the tracker coverage.
+For PF jets, the transition beyond the tracker acceptance is smoother because the PF candidates, which are input to the clustering of PF jets, are individually calibrated prior to the clustering.
+While both PF jets and JPT jets exploit the tracker measurements, the JPT jets require lower correction in the region |η| < 2.0 because the tracker inefficiency is explicitly corrected for by the JPT algorithm.
+In the forward region (|η| > 3.0) all three jet types converge to simple calorimetric objects and therefore require almost identical corrections.
 
@@
 \label{sec:objects_jets_btag}
+With b--quarks appearing as final states in many of the standard model
+processes being studied at the \ac{LHC}, as well as in final states
+of searches for new physics, correctly identifying jets due to the hadronisation
+of b--quarks is very important. As b--hadrons have a relatively
+large mass of 5--6 GeV and a relatively long lifetime $\tau_B \approx 1.5$ ps \cite{pdg-2014},
+they move for roughl $c\tau_B \approx 450$ $\mu$m before decaying. This means 
+they produce a displaced secondary decay vertex in the inner tracker.
+Algorithms for tagging b--jets usually rely on the information
+from these secondary vertices.
+For the analysis presented in chapter \ref{chap:hhh}
+the \ac{CSV} algorithm \cite{cms-btag-paper} has been used, with the upgraded
+\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter CHAPMSSM. 
+The \ac{CSV} algorithm takes \ac{PF} jets with \pT$ > 20$ GeV and $|\eta|<2.4$ as input and 
+defines a likelihood--based discriminator to determine 
+whether a jet is likely due to a b--quark hadronisation or not.
+For this algorithm, secondary vertices are reconstructed from high-purity tracks
+within a cone of $\Delta R = 0.3$ around the jet axis, with quality cuts applied
+to reduce contamination from decays of long--lived particles or particles due 
+to interactions with the detector material. Information from the resulting
+secondary vertices is combined with information from the tracks associated
+with the jet into a likelihood ratio.
+
+%The presence of a secondary vertex, and kinematic quantities associated with it, 
+%are helpful in distinguishing between b-- and lighter jets. Secondary
+%vertices are reconstructed by selecting high--purity tracks within
+%a cone of $\Delta R = 0.3$ around the jet axis, which are
+%fitted using an adaptive vertex fit as for primary vertex reconstruction (section \ref{sec:objects_tracks}).
+%For the \ac{CSV} algorithm, secondary vertices need to share less than 65\% of associated tracks
+%with the primary vertex, and the significance of the radial distance between the two vertices
+%must exceed $3\sigma$. The flight direction of each candidate has to be within a cone
+%of $\Delta R < 0.5$ around the jet direction. Secondary vertices which are more
+%than 2.5 cm away from the primary vertex and whose mass is either compatible
+%with that of a \PKzero or exceeds $6.5$ GeV are rejected to reduce the contamination
+%from vertices produced due to interactions of particles with the detector
+%material or decays of long--lived particles. The information from the selected
+%secondary vertices is then combined with information about the tracks in the jet,
+%to form two likelihood ratios to discriminate between b- and c- jets and 
+%between b- and light jets. These likelihood ratios are combined into one
+%a single discriminant.
+The \ac{CSV}v2 algorithm as improved for Run 2
+uses an \ac{IVF} algorithm to reconstruct secondary vertices \cite{cms-ivf}. Instead of 
+using only tracks near the jet, in this algorithm all reconstructed
+tracks in the event which are displaced from the primary vertex are used.
+In addition, the algorithm makes use of a multilayer perceptron to combine the variables
+instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
+for the addition of extra variables to discriminate between b- and other jets.
+
+Once the discriminator has been constructed, loose- medium- and tight working points
+can be determined as a minimum requirement on the discriminator such that the
+probability of misidentifying light--flavour jets with \pT $ > 30$ GeV is around
+10\%, 1\% and 0.1 \% respectively \cite{cms-btag-paper}.
+
+Because not all of the input variables to the \ac{CSV} algorithm are perfectly
+modelled in simulation the b--tagging efficiency for different jet
+flavours is different in data and \ac{MC}. Scale factors can be detemined
+as the ratio of tagging efficiencies in data and \ac{MC}, which are applied to the \ac{MC} to align
+the data and \ac{MC} efficiencies. The measurements of the tagging efficiency
+for genuine b--jets makes use of samples containing a muon overlapping with the jet, 
+making use of the $\approx$ 11\% semileptonic branching fraction of b's. For other
+ranges of jet \pT the measurement can be complemented by measurements from samples
+with the kinematic signatures of \ttbar production, making use of 
+the large  $\Ptop \rightarrow \PW \Pbottom$ branching ratio. Measurements
+of mis--tagging efficiencies for light jets are made using negative--tagging
+algorithms to select samples enriched in light jets from multijet events.
+
+Systematic uncertainties in the scale factors arise from, amongst other things,
+pile--up modelling in simulation, gluon splitting into $b\bar{b}$ pairs, track mismeasurement,
+and uncertainties in the fractions of different jet types.
+
+%Some efficiency measurements are performed using samples that include a jet with a muon within ∆R = 0.4 from the jet axis (a “muon jet”).
+Because the semileptonic branching fraction of b hadrons is significantly larger than that for other hadrons (about 11%, or 20% when b → c → l cascade decays are included), these jets are more likely to arise from b quarks than from another flavour.
+
+%The combinatorial complexity of the reconstruction of the decay points (secondary vertices) of b or c hadrons is more challenging in the presence of multiple proton-proton interactions.
+In order to minimize this complexity a different track selection is applied.
+Tracks must be within a cone of ∆R = 0.3 around the jet axis with a maximal distance to this axis of 0.2 cm and pass a “high-purity” criterion [32].
+The “high-purity” criterion uses the normalized χ2 of the track fit, the track length, and impact parameter information to optimize the purity for each of the iterations in track reconstruction.
+The vertex finding procedure begins with tracks defined by this selection and proceeds iteratively.
+A vertex candidate is identified by applying an adaptive vertex fit [31], which is robust in the presence of outliers.
+The fit estimates the vertex position and assigns a weight between 0 and 1 to each track based on its compatibility with the vertex.
+All tracks with weights > 0.5 are then removed from the sample.
+The fit procedure is repeated until no new vertex candidate can be found.
+In the first iteration the interaction region is used as a constraint in order to identify the prompt tracks in the jet.
+The subsequent iterations produce decay vertex candidates.
 
@@
 \label{sec:objects_met}
+The \ac{CMS} detector is able to detect most stable and long--lived particles,
+however, neutrinos and hypothetical neutral weakly interacting particles
+travel straight through the detector without being recorded. These particles
+will give rise to an energy imbalance in the transverse plane, and so their
+presence can be inferred from missing energy \MET in the event.
+
+The \MET is defined as $-\Sigma \vec{p}_{\text{T}}$, where
+the sum runs over all final--state particles and jets in the event. This quantity
+can be mismeasured due to detector inefficiencies, calorimeter energy thresholds,
+the nonlinearity of the calorimeter
+response for hadronic particles.
+
+%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature.
+This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections
+
+The \MET measurement can therefore be corrected by jet energy corrections as
+\begin{equation}\label{eqn:objects_met_corr}
+\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{corr}} - p_{\text{T,jet}})
+\end{equation}
+
+The \MET can also be mismeasured due to pile--up interactions, and improved
+measurement of the \MET at high pile--up can be obtained by using the MVA \MET
+algorithm, used for \MET reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
+CHAPMSSM. This algorithm computes a correction to the hadronic
+recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
+\begin{equation}\label{eqn:objects_met_recoil}
+\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{lep},
+\end{equation}
+
+with $\Sigma \vec{p}_{\text{T}}^{lep}$ corresponds to the vectorial sum of the transverse momenta of the
+candidate constituents selected as signal particles, the di--$\tau$ candidate in the case of \htotautau
+analyses.
+
+Two \ac{BDTs} trained on \Zmm  are used to compute this correction.
+The first one corrects the direction of the hadronic recoil, the second
+one uses a data sample with the corrected recoil direction to compute a correction
+to the magnitued of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
+recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
+different \MET definitions \cite{cms-met-run1} as input. 
+In the process of calculating the corrections to the hadronic recoil using the MVA \MET
+algorithm, the significance of the MVA \MET is also estimated, providing an event--by--event
+estimator of the likelihood that the \MET is due to unseen objects rather than induced
+by mismeasurement of jet energy \cite{cms-met-run1}.
+
+%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
+close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions.
+The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles.
+However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.
 
@@
 \label{sec:objects_met_recoilcorr}
+To correct for the mismodelling of \MET in events without genuine \MET recoil corrections are determined. 
+The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T},\nu/\text{leptons}}$ 
+is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT of the boson producing the leptons
+and neutrinos. For the analyses
+presented in chapters \ref{chap:hhh} and CHAPMSSM it is measured in \Zmm events, where no neutrinos
+are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
+and \ac{MC} events, using convolutions of gaussians. Corrections are then applied to the \ac{MC}
+as
+\begin{equation}\label{eqn:met_recoilcorr}
+u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + u_{\parallel,\perp} - <u_{\parallel,\perp}>_{MC} \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}
+\end{equation}
+
+%Recoil corrections are applied to correct for the mismodelling of $\MET$ in events without genuine $\MET$ \cite{RecoilCorrPresentation}.
+%The hadronic recoil is defined as
+%$\vec{U} = \vec{E}_{\text{T}}^{mis} - \Sigma \vec{p}_{\text{T},\nu/lep}$. This recoil is projected onto the axes parallel ($U_1$) and
+%orthogonal ($U_2$) to the boson $p_{\text{T}}$ and it is measured in $Z\rightarrow\mu\mu$ events, in which the $\nu$ term is 0. Events are selected
+%by requiring the HLT\_IsoMu22\_v trigger in data, and opposite--sign muon pairs are selected by requiring two muons with opposite charge, passing
+%the medium HIP safe muon ID, the same impact parameter cuts as in the muon selection for the analysis, $I_{rel}^{\mu} < 0.15$. The leading
+%muon must have a $p_{\text{T}}$ of at least 23 GeV, with the trailing muon having a $p_{\text{T}}$ of at least 10 GeV. In addition, for data
+%events the leading muon must have fired the HLT\_IsoMu22\_v trigger. The requirements on muon $\eta$ are $|\eta_1| < 2.1$ and $|\eta_2|<2.4$.
+%At pair level, the two muons must be separated by $\Delta R > 0.5$, and the di-muon mass must be at least 20 GeV. Pile--up reweighting,
+%the muon ID, isolation, and trigger scale factors are applied, as are the muon tracking efficiencies. The DY shape reweighting
+%is applied to DY MC and top $p_{T}$ reweighting is applied to the $t\bar{t}$ MC.
+%The projected hadronic recoil $U$
+%is determined for both $Z\rightarrow\mu\mu$ data and MC events. A double gaussian with means symmetrically shifted away from zero is used to fit the $U_2$ component,
+%with a triple  gaussians for fitting the $U_1$ component. These fits are performed in bins of $Z p_{\text{T}}$ (0-10, 10-20, 20-30, 30-50, and $ > 50$ GeV), and
+%bins of number of jets (0, 1 or at least 2). $Z\rightarrow \mu\mu$ events from around the Z peak are used by requiring $70 <m_{\mu\mu} < 110 $ GeV.
+%To apply the corrections, the offset $w = U{1,2} -<U_{1,2}>_{MC} $ and the recoil in MC is corrected as
+%$U_{1,2}' = <U_{1,2}>_{data} + w\frac{\sigma_{data}}{\sigma_{MC}}$.
 

### 2016-12-14 backmatter.tex
Adding some things for H->hh/A->Zh
Updating Hhh section
Adding some more stuff
Adding latest changes to bbtautau chapter
Adding more detector stuff
More HCAL stuff
Bit more on the trigger
Adding more detector bits
Full detector chapter and first part of H->hh corrections
Fixing up detector chapter
Adding section on PF and editing tau reco section
Adding muon reconstruction section
Adding part of jets section
Finishing text of objects section (pre whittling it all down and adding figures)

@@
 %% is derived from the source using the SPIRES Bibtex service.
-%\bibliographystyle{h-physrev}
-%\bibliography{mythesis}
+\bibliographystyle{lucas_unsrt}
+\bibliography{references}
 
@@
 %% front matter seemingly interminable. No-one cares, anyway!
-\listoffigures
-\listoftables
+%\listoffigures
+%\listoftables
+
+\chapter*{List of Acronyms}
+\addcontentsline{toc}{chapter}{List of Acronyms}
+\begin{acronym}[CERN]
+\acro{MC}[MC]{Monte Carlo}
+\acro{CMS}[CMS]{Compact Muon Solenoid}
+\acro{LHC}[LHC]{Large Hadron Colider}
+\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
+\acro{PS}[PS]{Proton Synchrotron}
+\acro{SPS}[SPS]{Super Proton Synchrotron}
+\acro{PSB}[PSB]{Proton Synchrotron Booster}
+\acro{LS1}[LS1]{Long Shutdown 1}
+\acro{MSSM}[MSSM]{Minimal Supersymmetric standard model}
+\acro{SUSY}[SUSY]{Supersymmetry}
+\acro{2HDM}[2HDM]{Two Higgs Doublet Model}
+\acro{ECAL}[ECAL]{Electromagnetic calorimeter}
+\acro{HCAL}[HCAL]{Hadron calorimeter}
+\acro{TIB}[TIB]{Tracker Inner Barrel}
+\acro{TID}[TID]{Tracker Inner Disk}
+\acro{TOB}[TOB]{Tracker Outer Barrel}
+\acro{TEC}[TEC]{Tracker EndCap}
+\acro{EB}[EB]{ECAL Barrel}
+\acro{EE}[EE]{ECAL Endcaps}
+\acro{HB}[HB]{Hadron Barrel Calorimeter}
+\acro{HO}[HO]{Hadron Outer Calorimeter}
+\acro{HE}[HE]{Hadron Endcap Calorimeter}
+\acro{HF}[HF]{Hadron Forward Calorimeter}
+\acro{BSM}[BSM]{Beyond the Standard Model}
+\acro{L1}[L1]{Level-1}
+\acro{HLT}[HLT]{High-level trigger}
+\acro{CSCs}[CSCs]{Cathode Strip Chambers}
+\acro{DT}[DT]{Drift Tube}
+\acro{RPCs}[RPCs]{Resistive Plate Chambers}
+\acro{DAQ}[DAQ]{Data Acquisition}
+\acro{WLCG}[WLCG]{Worldwide LHC Computing Grid}
+\acro{RF}[RF]{radio frequency}
+\acro{PF}[PF]{Particle Flow}
+\acro{BDTs}[BDTs]{Boosted Decision Trees}
+\acro{CTF}[CTF]{Combinatorial Track Finder}
+\acro{GSF}[GSF]{Gaussian Sum Filter}
+%\acro{KF}[KF]{Kalman Filter}
+\acro{DA}[DA]{Deterministic Annealing}
+\acro{CHS}[CHS]{Charged hadron subtraction}
+\acro{CSV}[CSV]{Combined Secondary Vertex}
+\acro{IVF}[IVF]{Inclusive Vertex Finder}
+\acro{UE}[UE]{underlying event}
+\acro{MPF}[MPF]{missing transverse energy projection fraction}
+\end{acronym}
 

### 2016-12-15 Objects/Objects.tex
Adding plots to objects section

@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{./Objects/Plots/PrimaryVertexRes.png}
-\caption{Resolution of the z--coordinate of reconstructed primary vertices
-as a function of the number of tracks associated with the vertex, 
-for minimum--bias events in red and for
-events with many jets in black. The resolution improves
-with larger numbers of tracks \cite{cms-trk-algos}.}
+\begin{center}
+\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
+\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
+\end{center}
+\caption{Resolution of the x-- (a) and z--coordinate  (b)
+of reconstructed primary vertices
+as a function of the scalar sum \pT of the tracks, 
+measured for the 2015 running conditions in blue triangles
+and for 2016 in red squares.
+The resolution improves
+with higher sum \pT (generally corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
 \label{fig:objects_tracks_pvres}
@@
 \end{itemize}
+
+Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
+for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.
+
+\begin{figure}
+\begin{center}
+\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
+\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
+\end{center}
+\caption{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
+misidentified electrons (yellow triangles) in a dataset corresponding to 19.7 fb$^{-1}$
+taken at $\sqrt{s} = 8$ TeV, overlaid on the variables for simulated 
+real electrons in purple \cite{cms-elereco-run1}.}
+\label{fig:ele_id_vars}
+\end{figure}
 
@@
 instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
-for the addition of extra variables to discriminate between b- and other jets.
+for the addition of extra variables to discriminate between b- and other jets. Figure \ref{fig:objects_bjets}a shows
+the distribution of the \ac{CSV}v2 discriminator in multijet events in the 2015 data sample.
 
@@
 and uncertainties in the fractions of different jet types.
+Figure \ref{fig:objects_bjets}b shows the b--tagging scale factors, and associated errors,
+for the medium working point of the \ac{CSV}v2 discriminator in the
+2015 data sample.
+
+\begin{figure}
+\begin{center}
+\subfloat[CSVv2 distribution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}
+\subfloat[CSVv2 scale factors]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVSF.png}}
+\end{center}
+\caption{(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
+collected at $\sqrt{s} = 13$ TeV and (b) the b--scale factors and errors
+as a function of jet \pT for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
+\label{fig:objects_bjets}
+\end{figure}
 
@@
 recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
-different \MET definitions \cite{cms-met-run1} as input. 
+different \MET definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
+the performance of the MVA \MET in data collected at $\sqrt{s}=13$ TeV compared with 
+the \ac{PF} \MET, indicating the lower MVA \MET values for events without genuine
+\MET in figure \ref{fig:objects_mvamet}a and the improved resolution at high pile--up
+in figure \ref{fig:objects_mvamet}b.
+
+\begin{figure}
+\begin{center}
+\subfloat[\MET distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
+\subfloat[\MET resolution]{\includegraphics[width=0.5\texwidth]{./Objects/Plots/transverse_resolution_npv.png}}
+\end{center}
+\caption{(a) \MET distributions comparing MVA \MET (brown circles) to \ac{PF} \MET (black circles) for
+\Zmm events, which contain no genuine \MET, in a sample corresponding to 42 pb${-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET
+values for MVA \MET are lower than for \ac{PF} \MET. (b) the \MET resolution for \ac{PF} \MET in blue and MVA \MET in red/brown
+circles, as a function of number of vertices. The MVA \MET resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
+\label{fig:objects_mvamet}
+\end{figure}
+
 In the process of calculating the corrections to the hadronic recoil using the MVA \MET
@@
 %Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
-close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions.
+%close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions.
 The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles.
@@
 
-Figure \ref{fig:tau_iso_efficiency} compares the \Pgt identification efficiency with the
+Figure \ref{fig:tau_iso_efficiency}a compares the \Pgt identification efficiency with the
 jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
@@
 discriminator has better performance than the cut-based discriminator alone.
-
-\begin{figure}
-\includegraphics[width=0.7\textwidth]{./Objects/Plots/TauIsolationPlot.png}
-\caption{jet$\rightarrow \Pgt_{h}$ fake rate versus $\Pgt_{h}$ identification efficiency for \htotautau events,
-comparing the MVA-based discriminator in red with the cut-based isolation discriminator in pink. Tighter working points
-give lower hadronic tau identification efficiencies and lower fake rates. The MVA-based discriminator
-has a lower fake rate than the cut-based discrminator for the same $\Pgt_{h}$ identification efficiency \cite{cms-tau-2015}.}
-\label{fig:tau_iso_efficiency}
-\end{figure}
 
@@
 
-Five working points are provided, ranging from very loose to very tight.
+Five working points are provided, ranging from very loose to very tight. The real tau efficiency
+and $Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
+figures \ref{fig:tau_efficiency}b and c, respectively.
+
+\begin{figure}
+\begin{center}
+\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyIsol.pdf}}\\
+\subfloat[Anti-e discriminator efficiency]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyEle.pdf}}
+\subfloat[Anti-e discriminator fake rate]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauMisIDEle.pdf}}
+\end{center}
+\caption{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
+efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 
+isolation discriminator in pink. Tighter working points give lower hadronic tau identification
+efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
+from the MVA-based discriminator is lower than from the cut-based discriminator. (b) the real $\Pgt_{h}$ identification
+efficiency for different working points of the anti-electron discriminator, as a function of $\Pgt_{h}$ \pT, and (c)
+the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
+\Pe \pT.}
+\label{fig:tau_efficiency}
+\end{figure}
 

### 2016-12-15 Objects/Objects.tex
Object reco edit round 1

@@
 In this chapter the physics objects necessary to be able to perform searches with \Pgt leptons
-in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. The 
-descriptions correspond to the algorithms as used during Run 2. Where there are differences
-between the algorithms used in Run 1 and Run 2 this will be discussed at the end
-of the relevant section. Section \ref{sec:objects_pv} discusses the algorithms
-used to reconstruct charged tracks in the inner tracker, with section \ref{sec:objects_ele}
+in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. Section \ref{sec:objects_pv} details the algorithms
+used to reconstruct charged particle tracks in the inner tracker, with section \ref{sec:objects_ele}
 describing how these tracks are combined with \ac{ECAL} energy deposits to reconstruct electrons.
@@
 \label{sec:objects_pv}
-To reconstruct the trajectories of charged particles, and therefore
-their momenta and positions, from the hits these particles leave in the 
+To reconstruct the trajectories of charged particles - and therefore
+their momenta and positions - from the hits these particles leave in the 
 inner tracker, dedicated algorithms are required. In \ac{CMS} the
 \ac{CTF} algorithm is used. This algorithm performs four steps:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item Initial estimates of the parameters of the trajectory are given by track seeds, providing track candidates found using hits in 2 or 3 layers of the inner tracker
-\item The track seeds are extrapolated using a Kalman filter \cite{trk-kf}, which extrapolates the seeding trajectories along the expected flight path of a charged particle 
-and adds additional matched hits it finds in the tracker layers to the track.
-\item After the extrapolation has reached the final tracker layers, the Kalman filter is run again, now with the full set of hits that have been found in the previous step.
-This provides the best estimate of the track parameters
-\item Tracks that fail a specified set of quality criteria are rejected
-\end{itemize}
+First, initial estimates of the parameters of the trajectory are given by track seeds, 
+made out of hits found in 2 or 3 layers of the inner tracker. Then, the track seeds
+are extrapolated using a \ac{KF} \cite{trk-kf}, which extrapolates the seeding
+trajectories along the expected flight path of a charged particle and adds 
+additional matched hits it finds in the tracker layers it traverses to the track.
+After the extrapolation has reached the final tracker layers, the \ac{KF} is run again,
+now with the full set of hits that have been found in the previous step. This provides the best
+estimate of the track parameters. Finally, tracks that fail a specified set of quality 
+criteria are rejected.
 
@@
 tracks that appear to have originated from the same vertex, then fitting 
-for the position of the vertex using the associated tracks. The tracks 
-are clustered using the \ac{DA} algorithm \cite{vtx-da}, which identifies
+for the position of the vertex using the associated tracks. The clustering 
+is performed using the \ac{DA} algorithm \cite{vtx-da}, which identifies
 the most probable vertex candidates and assigns tracks to them. Vertex
 candidates with at least two associated tracks are fitted using an adaptive
-vertex fitter \cite{vtx-adaptivefit} to obtain the best estimate
-of the vertex position as well as an indicator for the success of the fit.
-Each track is assigned a weight $w_i$ between 0 and 1 which reflects the probability
-that it belongs to the vertex it is associated with. If the track is consistent
-with the vertex position the weight will be closer to 1, if not the weight 
-will be smaller. Using this the number of degrees of freedom in the fit
-can be defined as
-\begin{equation}\label{eqn:pv_ndof}
-n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
-\end{equation}
-which is strongly correlated with the number of tracks arising from the interaction region
-and can therefore be used to select genuine interactions. For the analysis
-presented in chapter \ref{chap:hhh}, which uses data collected during Run 1, to select the primary vertex, 
-this variable
-was required to be greater than 4, in addition to requirements on the distance between
-the vertex and the nominal interaction point ($\Delta z < 24$ cm and $\Delta x-y < 2$ cm). 
-The primary vertex was then taken as the vertex passing these quality criteria that 
-had the largest scalar sum \pT of associated tracks. For the Run 2 analyses presented
-later the quality requirements were removed and the primary vertex, the vertex
-of the hard scattering process, is simply taken as the reconstructed vertex with
-largest scalar sum \pT of associated tracks.
-The resolution of the z--coordinate of the primary vertex was measured in
-collisions at $\sqrt{s}=7$ TeV and depends strongly on the number of tracks
+vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
+vertex position. The analyses presented in CHAPMSSM take the primary
+vertex of the hard scatter as the reconstructed vertex with largest scalar sum \pT~of
+the associated tracks. This differs from the analysis presented in chapter \ref{chap:hhh},
+where requirements on the quality of the vertex
+fit and the distances between the vertex and the nominal interaction point 
+were made.
+ %By doing this both the best estimate
+%of the vertex position and an indicator for the success of the fit are obtained.
+%Each track is assigned a weight $w_i$ between 0 and 1, where values 
+%closer to 1 indicate more consistency with the vertex position.
+%The number of degrees of freedom in the fit can then be defined as
+%\begin{equation}\label{eqn:pv_ndof}
+%n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
+%\end{equation}
+%which is strongly correlated with the number of tracks arising from the interaction region
+%and can therefore be used to select genuine interactions. During Run 1 this variable was
+%used in many analyses, including the one presented in chapter \ref{chap:hhh}, to define
+%good--quality primary vertices. In addition to requiring $n_{\text{dof}}>4$, the distances
+%between the vertex and the nominal interaction point were required
+%to be $\Delta z< 24$ cm and $\Delta xy < 2$ cm. The primary vertex of the
+%hard scatter was then taken as the vertex with greatest scalar sum \pT~ of associated
+%tracks that passed these requirements. For the analyses with data from Run 2 the
+%quality requirements were removed and the primary vertex of the hard scatter was simply taken
+%as the reconstructed vertex with largest scalar sum \pT~ of tracks.
+
+The resolution of the x-- and z--coordinates of the primary vertex were measured in
+collisions at $\sqrt{s}=13$ TeV and depend strongly on the number of tracks
 associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
@@
 The resolution improves
-with higher sum \pT (generally corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
+with higher sum \pT (corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
 \label{fig:objects_tracks_pvres}
@@
 A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
-described in section \ref{sec:objects_pf}. Because electrons lose on average 33-86\% of
-their energy by radiating photons before the \ac{ECAL} is reached, depending on the thickness of
-the intervening material. To accurately reconstruct the energy of the electron it is
-important to catch the energies of photons, which are spread in the $\phi$ direction
-due to the magnetic field. Therefore \textit{supercluster} algorithms are needed to perform
-the clustering. In this approach the clustering
-is done by defining a seed crystal as the one containg the most energy deposited
-in a region being considered and having a certain minimum transverse energy.
-In the barrel arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
-to the cluster, stepping sideways in both directions in $\phi$, if this
-array contains a minimum energy deposit. These clusters are grouped into 
-superclusters if each distinct cluster has a seed array with a minimum energy deposit.
+described in section \ref{sec:objects_pf}.
+Depending on the thickness of the intervening material, electrons lose up to 86 \% of their energy on
+average by radiating photons before the \ac{ECAL} is reached.
+To accurately reconstruct the energy of the electron it is
+important to catch the energies of bremsstrahlung photons, which are spread in the $\phi$ direction
+due to the magnetic field. Therefore ``supercluster'' algorithms are needed.
+In these algorithms the clustering
+is performed by defining a seed crystal as the crystal containg the most deposited energy
+in a region under consideration, where the transverse energy in this crystal
+passes a minimum threshold.
+In the barrel, arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
+to the cluster, stepping sideways in both directions in $\phi$. The array is
+only added to the cluster if the energy deposited in it passes a threshold.
+These clusters are grouped into superclusters if each distinct cluster has a seed array in 
+which the energy deposit is larger than a pre-defined minimum.
 In the endcaps the clusters combined into superclusters are arrays of $5\times 5$ crystals,
@@
 
-Because the electrons radiate bremsstrahlung photons in the tracker, the
-change in electron track curvature is large. The reconstruction of these
-tracks using the \ac{CTF} is compromised as a result of this, and 
-therefore a dedicated tracking algorithm is used. For high \pT electrons
-the best efficiency is reached by using an \ac{ECAL}-based track seeding
-algorithm which extrapolates the position and energy of the supercluster
-to the first layers of the tracker to determine rough areas to look for
-tracker seeds in. Once the seeds have been determined they are extrapolated
-and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the Kalman Filter, which 
+Due to the radiation of bremsstrahlung photons in the tracker,
+the change in electron track curvature can be large, and so the \ac{CTF} does
+not perform optimally. Therefore a dedicated tracking algorithm is used.
+For high \pT~electrons, the best efficiency is reached
+by the use of an \ac{ECAL}-based track seeding algorithm
+which extrapolates the position and energy of the supercluster to the first
+layers of the tracker to determine the rough area where the tracker seeds should be.
+Once the tracker seeds have been determined they are extrapolated
+and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the \ac{KF}, which 
 approximates the non-Gaussian energy loss in each layer by the combination of 
-Gaussian distributions rather than the single Gaussian used in the Kalman filter.
+Gaussian distributions rather than the single Gaussian used in the \ac{KF}.
 
@@
 
-To be identified as an electron, a particle has to be reconstructed as
-an electron by the \ac{PF} algorithm, and must in addition pass
-more advanced identification criteria based on some of the variables used in the
+For a particle to be identified as an electron, it 
+has to be reconstructed as an electron by the \ac{PF} algorithm, 
+and must in addition pass more advanced identification criteria based on some of the variables used in the
 standalone electron reconstruction, which provide separation power from backgrounds
@@
 with exceptions for the loose identification criteria required for veto-electrons. 
-The variables used to train the electron identification BDT are:
-
+This BDT is trained using variables such as:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
-label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
-$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
-respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
-of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
-\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
-\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
-\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
-\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
-\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
- and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
+\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width in units of $\eta$ crystals. 
+\item Track quality variables
+\item Distances in $\eta$ and $\phi$ betaween the supercluster and the associated track
+\item Ratios between hadronic and electromagnetic energy in the region of the supercluster, between supercluster energy and momentum of the track, and including 
+$1/E_{\text{SC}} - 1/p_{\Pe}$, the inverse of the supercluster energy, with the inverse of electron track momentum subtracted
+%\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
+%label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
+%$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
+%respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
+%of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
+%\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
+%%\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
+%\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
+%\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
+%\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
+% and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
 \end{itemize}
@@
 Different isolation definitions are used in \ac{CMS}, for the analyses presented
-in later chapters a combined relative isolation variable is defined as:
+in later chapters a combined relative isolation variable is defined as \cite{SMHtautauCMS}:
 \begin{equation}\label{eqn:electron_reliso}
-I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
+I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged})} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{P_{T}^{e}},
 \end{equation}
-Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
-of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
-The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
+Where the \pT~and \ET~sums are taken within a cone in $\eta - \phi$ around the direction
+of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
+The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged \ac{PF} 
 hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
@@
 The contribution from neutral particles due to pile--up needs to be subtracted from
-this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
+this term, which is estimated as the sum of charged hadronic \pT~for hadrons not associated
 with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.
@@
 Muons are reconstructed by combining tracker tracks and tracks
-from the muon system \cite{cms-muon-reco}. Two complementary approaches are used for this,
-\textit{Global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
+from the muon system \cite{cms-muon-reco}. Two complementary approaches are used,
+\textit{global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
 tracks reconstructed in the muon system and searches for a matching
-tracker track, then re-applies the Kalman filter on the combination
+tracker track, then re--applies the \ac{KF} on the combination
 of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
@@
 considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
-Due to the requirement of a single muon segment this method is more efficeint than the global muon
-reconstruction for muons with \pT smaller than 5 GeV \cite{cms-muon-reco}.
-For muons with \pT greater than 200 GeV, the momentum resolution is improved
+Due to the requirement of a single muon segment this method is more efficient than the global muon
+reconstruction for muons with \pT~smaller than 5 GeV \cite{cms-muon-reco}.
+For muons with \pT~greater than 200 GeV, the momentum resolution is improved
 by the global muon reconstruction \cite{cms-muon-cosmics-perf}.
@@
 The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
-for muons with \pT up to 100 GeV and found to range from 1--6\% depending
-on detector region. For muons with \pT between 100 GeV and 1 TeV the momentum resolution
+for muons with \pT~up to 100 GeV and found to range from 1--6\% depending
+on detector region. For muons with \pT~between 100 GeV and 1 TeV the momentum resolution
 was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
@@
 
-For the analysis presented in chapter CHAPMSSM additional ``Medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
+For the analysis presented in chapter CHAPMSSM additional ``medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
 Apart from having passed either the global or tracker muon reconstruction, the fraction
@@
 $\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
-position matching, on the kink finder in the inner tracker, and the segment compatibility. The segment
+position matching, on the kink finder in the inner tracker, and the segment compatibility. 
+The compatibility of the tracker- and standalone-reconstructed position is evaluated
+by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
+compatibility there.
+The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
+tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
+is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
+The segment
 compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
@@
 a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
-The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
-tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
-is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
-The compatibility of the tracker- and standalone-reconstructed position is evaluated
-by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
-compatibility there.
 
 To pass the identification, global- or tracker muons
-with a large enough fraction of tracker hits must  \textbf{either} 
+with a large enough fraction of tracker hits must pass \textbf{either} 
 \begin{itemize}
@@
 \begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
 \item The segment compatibility is $>$ 0.451
 \end{itemize}
-
 In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
-was used, muons were required to pass ``Tight'' identification requirements \cite{cms-muon-reco}. 
+was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
 The criteria are
@@
 \item The global track fit must include hits from at least one chamber in the muon system
-\item The inner tracker track must be matched to muon segments in at least two muon stations (ie the muon must be reconstructed as a tracker muon too)
+\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
 \item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
@@
 using a clustering algorithm, so that stable neutral particles can be identified,
-separated from charged hadrons, and electrons and all Bremsstrahlung photons
+separated from charged hadrons, and electrons and all bremsstrahlung photons
 can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
@@
 to the ECAL from the track--tracker layer interaction points, and clusters can be 
-linked to the track as a possible Bremsstrahlung photon if the extrapolated tangent
+linked to the track as a possible bremsstrahlung photon if the extrapolated tangent
 position is within the boundaries of the cluster.
@@
 of tests. First, if there is a link between a tracker track and a muon system track,
-a particle flow muon is identified if the combined tracker and muon system
+a \ac{PF} muon is identified if the combined tracker and muon system
 momentum is compatible with the tracker-only momentum. %within three standard deviations
@@
 
-Secondly, tracks are refitted with the \ac{GSF}, the compatibility
+Secondly, tracks are refitted with the \ac{GSF} and the compatibility
 of the track with the already linked \ac{ECAL} clusters is assessed using
 \ac{BDTs} which take several variables into account. If the candidate
-passes, it is identified as a particle flow electron and the track and
+passes, it is identified as a \ac{PF} electron and the track and
 \ac{ECAL} clusters are removed from the block.
@@
 energies is larger than the total energy registered in associated \ac{ECAL} clusters,
-a particle flow photon with energy equal to the total \ac{ECAL} energy is created.
-Any remaining momentum difference is assigned to a particle flow neutral hadron. If the momentum
+a \ac{PF} photon with energy equal to the total \ac{ECAL} energy is created.
+Any remaining momentum difference is assigned to a \ac{PF} neutral hadron. If the momentum
 difference is smaller than the energy registered in associated \ac{ECAL} clusters 
-only a particle flow photon is created. %Justified by fact that
+only a \ac{PF} photon is created. %Justified by fact that
 %in jets 25% of the energy is carried by photons while neutral hadrons
@@
 Finally, any remaining \ac{ECAL} clusters not linked to a track give
-rise to particle flow photons, with any \ac{HCAL} clusters
-not linked to tracks giving rise to particle flow neutral hadrons.
+rise to \ac{PF} photons, with any \ac{HCAL} clusters
+not linked to tracks giving rise to neutral \ac{PF} hadrons.
 
-\section{Jets and b-tagging}
+\section{Jets and b--tagging}
 \label{sec:objects_jets}
@@
 The particles identified by the \ac{PF} algorithm
-are clustered into jets using the anti-\kT algorithm \cite{antiKT} as implemented
+are clustered into jets using the anti-\kT~algorithm \cite{antiKT} as implemented
 in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
@@
 object $j$, and $d_{iB}$ denoting the distance between 
-object $i$ and the beam. The smallest of the distances
-is defined and if this is a distance between object i and an object j, objects
+object $i$ and the beam. The smallest of these distances
+is determined and if this is a distance between object i and an object j, objects
 i and j are combined. If $d_{iB}$ is the smallest distance, object i
-is called a jet and removed from the list of objects. In the anti-\kT algorithm
+is called a jet and removed from the list of objects. In the anti-\kT~algorithm
 these distance parameters are defined as:
 \begin{align}\label{eqn:objects_antikt}
-d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\\
+d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\notag\\
 d_{iB} = p_{\text{T}}^{-2},
@@
 charged hadronic \ac{PF} candidates not associated with the primary vertex 
-are not considered in the clustering. For the analysis presented in
+are not considered in the jet clustering. For the analysis presented in
 chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
@@
 jets in data and jets in \ac{MC} to match the measured and true
-energies as
+energies as \cite{cms-jec-2011}
 \begin{equation}\label{eqn:objects_jec}
-p_{\mu}^{\text{corr}} = \mathcal{C}\cdot p_{\mu}^{\text{raw}},
+p_{\mu}^{\text{corr}} = 
+ (\text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
+\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
+\cdot \text{C}_{\text{abs}}(p_{\text{T}}''))\cdot p_{\mu}^{\text{raw}}.
 \end{equation}
-
-where $\mathcal{C}$ is a correction factor broken down into different
-components as \cite{cms-jec-2011}
-\begin{equation}\label{eqn:objects_jec_corrfac}
-\mathcal{C} = \text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
-\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
-\cdot \text{C}_{\text{abs}}(p_{\text{T}}'').
-\end{equation}
-
-Here $\text{C}_{\text{offset}}$ is an offset correction, $\text{C}_{\text{MC}}$ an
+%\begin{equation}\label{eqn:objects_jec_corrfac}
+%\mathcal{C} = \text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
+%\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
+%\cdot \text{C}_{\text{abs}}(p_{\text{T}}'').
+%\end{equation}
+In this equation $\text{C}_{\text{offset}}$ is an offset correction, $\text{C}_{\text{MC}}$ an
 \ac{MC} calibration factor, $\text{C}_{\text{rel}}$ a relative residual correction
-factor and $\text{C}_{\text{abs}}$ an absolute residual correction factor. The corrections
+factor and $\text{C}_{\text{abs}}$ an absolute scale correction factor. The corrections
 are applied in sequence with $p_{\text{T}}'$ the transverse momentum 
@@
 aims to address includes contributions from electronics noise and pile--up. This is
-estimated on an event--by--event basis based on the average--\pT density
+estimated on an event--by--event basis based on the average--\pT~density
 per unit area $\rho$ and the area of the jet $A$ \cite{jet-area}. The factor $\rho$ includes
@@
 the response is flat, and a probe jet at any 
-$\eta$ value. The relative response, in bins of $\eta$ and \pT  is determined by
+$\eta$ value. The relative response, in bins of $\eta$ and \pT~ is determined by
 averaging the balancing function $\frac{p_{\text{T}}^{\text{probe}} - p_{\text{T}}^{\text{reference}}}{p_{\text{T}}^{\text{average}}}$.
@@
  using samples of \Pphoton+jets and \PZ+jets events. This method relies on the fact that \Pphoton+jets
-and \PZ+jets events have no intrinsic missing energy, and so any measured \MET
-is used to calibrate the \pT response of jets in the event.
+and \PZ+jets events have no intrinsic missing energy, and so any measured \MET~
+is used to calibrate the \pT~response of jets in the event.
 
-Uncertainties on the jet energy scale are propagated through to analyses
-and is driven by uncertainties in the energy density used for pile--up
+The uncertainty on the jet energy scale is propagated through to analyses.
+It is driven by uncertainties in the energy density used for pile--up
 subtraction, the photon energy scale, and the extrapolation required in the
-\ac{MPF} method.
+\ac{MPF} method \cite{cms-jec-2011}.
 
@@
 
-\subsection{B-tagging}
+\subsection{b--tagging}
 \label{sec:objects_jets_btag}
-With b--quarks appearing as final states in many of the standard model
-processes being studied at the \ac{LHC}, as well as in final states
-of searches for new physics, correctly identifying jets due to the hadronisation
-of b--quarks is very important. As b--hadrons have a relatively
+As b--quarks appear in final states of many of the standard model 
+processes being studied at the \ac{LHC}, as well as in searches for new
+physics, it is important to correctly identify jets which originate
+from the hadronisation of b--quarks.
+As b--hadrons have a relatively
 large mass of 5--6 GeV and a relatively long lifetime $\tau_B \approx 1.5$ ps \cite{pdg-2014},
-they move for roughl $c\tau_B \approx 450$ $\mu$m before decaying. This means 
+they move for roughly $c\tau_B \approx 450$ $\mu$m before decaying. This means 
 they produce a displaced secondary decay vertex in the inner tracker.
@@
 defines a likelihood--based discriminator to determine 
-whether a jet is likely due to a b--quark hadronisation or not.
+whether a jet is likely due to b--quark hadronisation or not.
 For this algorithm, secondary vertices are reconstructed from high-purity tracks
@@
 the sum runs over all final--state particles and jets in the event. This quantity
-can be mismeasured due to detector inefficiencies, calorimeter energy thresholds,
+can be mismeasured due to detector inefficiencies, calorimeter energy thresholds and
 the nonlinearity of the calorimeter
@@
 \begin{equation}\label{eqn:objects_met_corr}
-\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{corr}} - p_{\text{T,jet}})
+\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - p_{\text{T,jet}})
 \end{equation}
@@
 \begin{equation}\label{eqn:objects_met_recoil}
-\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{lep},
+\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{  lep}},
 \end{equation}
 
-with $\Sigma \vec{p}_{\text{T}}^{lep}$ corresponds to the vectorial sum of the transverse momenta of the
+with $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
 candidate constituents selected as signal particles, the di--$\tau$ candidate in the case of \htotautau
@@
 
-Two \ac{BDTs} trained on \Zmm  are used to compute this correction.
+Two \ac{BDTs} trained on \Zmm events are used to compute this correction.
 The first one corrects the direction of the hadronic recoil, the second
 one uses a data sample with the corrected recoil direction to compute a correction
-to the magnitued of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
-recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
-different \MET definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
-the performance of the MVA \MET in data collected at $\sqrt{s}=13$ TeV compared with 
-the \ac{PF} \MET, indicating the lower MVA \MET values for events without genuine
+to the magnitude of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
+recoil, the azimuthal angle and scalar \pT~sum of all \ac{PF} particles for several 
+different \MET~definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
+the performance of the MVA \MET~in data collected at $\sqrt{s}=13$ TeV compared with 
+the \ac{PF} \MET, indicating the lower MVA \MET~values for events without genuine
 \MET in figure \ref{fig:objects_mvamet}a and the improved resolution at high pile--up
@@
 \begin{center}
-\subfloat[\MET distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
-\subfloat[\MET resolution]{\includegraphics[width=0.5\texwidth]{./Objects/Plots/transverse_resolution_npv.png}}
+\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
+\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
 \end{center}
-\caption{(a) \MET distributions comparing MVA \MET (brown circles) to \ac{PF} \MET (black circles) for
-\Zmm events, which contain no genuine \MET, in a sample corresponding to 42 pb${-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET
-values for MVA \MET are lower than for \ac{PF} \MET. (b) the \MET resolution for \ac{PF} \MET in blue and MVA \MET in red/brown
-circles, as a function of number of vertices. The MVA \MET resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
+\caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
+\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb${-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET~
+values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
+circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
 \label{fig:objects_mvamet}
@@
 
-In the process of calculating the corrections to the hadronic recoil using the MVA \MET
-algorithm, the significance of the MVA \MET is also estimated, providing an event--by--event
-estimator of the likelihood that the \MET is due to unseen objects rather than induced
+In the process of calculating the corrections to the hadronic recoil using the MVA \MET~
+algorithm, the significance of the MVA \MET~ is also estimated, providing an event--by--event
+estimator of the likelihood that the \MET~ is due to unseen objects rather than induced
 by mismeasurement of jet energy \cite{cms-met-run1}.
@@
 \label{sec:objects_met_recoilcorr}
-To correct for the mismodelling of \MET in events without genuine \MET recoil corrections are determined. 
+To correct for the mismodelling of \MET~in events without genuine \MET~ in \ac{MC} events, recoil corrections are determined. 
 The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T},\nu/\text{leptons}}$ 
-is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT of the boson producing the leptons
+is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT~of the boson producing the leptons
 and neutrinos. For the analyses
@@
 Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
-which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT algorithm with a distance parameter $\Delta R = 0.4$. 
+which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT~algorithm with a distance parameter $\Delta R = 0.5$ in
+Run 1 and $\Delta R = 0.4$ in Run 2. 
 As table \ref{tab:hadronic_tau_decays}
@@
 the photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
-The \Pe or \Pphoton with highest \pT that is not yet included in a strip is used to build a new strip.
-The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT \Pe or \Pphoton  
+The electron or photon with highest \pT~that is not yet included in a strip is used to build a new strip.
+The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT~ electron or photon
 within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
 recomputed as the energy-weighted average of the electron/photon constituents in the strip.
-This procedure is repeated until there are no more electrons or photons with \pT $> 0.5$~GeV  within the 
-strip window. The $\Delta \eta$ and $\Delta \phi$ of the strip are varied based on the \pT or \ET to 
+This procedure is repeated until there are no more electrons or photons with \pT $ > 0.5$~GeV  within the 
+strip window. During Run 1 the strip window had a fixed size of $0.05 \times 0.2$ in $\eta \times \phi$, 
+while in the algorithm used during Run 2 the strip size is dynamically allocated. The
+width of the strip in $\eta$ and $\phi$ is varied based on the \pT~or \ET~ to 
 be added to the strip and on the energy the strip already has, as
@@
 \end{equation}
-If the $\Sigma$ \pT of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
+If the $\Sigma$ \pT~of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
 To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
@@
 required to be $0.05 < R_{\text{sig}} < 0.1$.
-If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT is retained.\\
-
+If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT~is retained.
 The decay modes considered for reconstructing hadronic taus are:
@@
 \begin{equation}\label{eqn:ptouter_iso}
-p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt}.
+p_{\text{T}}^{\text{strip, outer}} = \Sigma p_{\text{T}}^{\Pe/\Pphoton}(\Delta R > R_{\text{sig}}) < 0.10\cdot p_{\text{T}}^{\Pgt},
 \end{equation}
+can be made.
 An  MVA $\tau_{h}$ isolation discriminator combines isolation variables with $\tau$ lifetime information into a BDT to discriminate between $\tau_{h}$ decays and quark and gluon jets.
-The variables used as input are:\\
+Some of the variables used as input are:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item The charged-and neutral-particle isolation sums
-\item The reconstructed $\tau_{h}$ decay mode
-\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
-\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
-\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
-\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
-\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
-\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
-\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
-\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
-\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
-\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
-\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outside of the signal cone.
+\item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}
+\item Track--related variables such as impact parameters, quality of the track, and information about decay vertices
+\item Information about photons: the momentum weighted $\Delta R$ and/or $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found
+\item $\Pgt_{h}$--related kinematic quantities, plus the reconstructed decay mode  
+%\item The charged-and neutral-particle isolation sums
+%\item The reconstructed $\tau_{h}$ decay mode
+%\item The transverse impact parameter $d_{xy}$ of the leading track of the $\tau_{h}$ candidate with the vertex, and its significance $d_{xy}/\sigma_{d_{xy}}$, and its sign (the projection of the impact parameter vector on the $\tau_h$ direction)
+%\item The 3-dimensional impact parameter $d_{xyz}$ of the leading track, and it significance
+%\item The distance between the $\tau$ production and decay vertices, its significance, and information about whether a decay vertex has successfully been reconstructed for a given candidate.
+%\item $p_{\text{T}}$ and $\eta$ of the $\tau_{h}$ candidate
+%\item $\Delta \beta$ corrected isolation (as equation \ref{eqn:cutbased_iso}
+%\item The sum of transverse momenta of electrons and photons included in strips but located outside of the signal cone (equation \ref{eqn:ptouter_iso})
+%\item The $\chi^2$ value of the fit for the leading track of the $\tau_{h}$ candidate
+%\item The ratio of the total electromagnetic energy to the total energy within the $\tau_h$ signal cone.
+%\item The total number of signal and isolation photons with $p_{\text{T}} > 0.5$~GeV
+%\item The $p_{\text{T}}$ weighted $\Delta R$ of photons within signal cone and the isolation annulus
+%\item The $p_{\text{T}}$ weighted $\Delta \eta$ and $\Delta \phi$ of photons in strips outside of the signal cone.
 \end{itemize}
@@
 
-In order to reduce the $Pe\rightarrow\Pgt_h$ and $\Pgm\rightarrow\Pgt_h$ fake rate, 
+In order to reduce the $\Pe\rightarrow\Pgt_h$ and $\Pgm\rightarrow\Pgt_h$ fake rate, 
 anti-electron and anti--muon discriminators are used. 
-The anti--electron discriminator is a BDT-based discriminator with the following input variables:
+The anti--electron discriminator is a BDT--based discriminator trained using input variables as:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
-\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
-\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
-\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
-\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
-\item The \pT weighted RMS distances in $\eta$ and $\phi$ between the photons in any strip and the leading 
-charged track (calculated separately for photons inside and outside the $\Pgt$ signal cone)
-\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
-\item $(p_{in} - p_{out})/p_{in}$
-\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
-\item The ratio between the total \ac{ECAL} energy and inner track momentum
-\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
-\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
-\item $\chi^2/Ndof$ of the GSF track fit
-\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
-similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
+\item Kinematic variables of the $\Pgt_{h}$ candidate and \ac{GSF} track, including visible mass of the $\Pgt_{h}$
+\item Energy/momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum
+\item Photon--related variables, such as the momentum--weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the $\Pgt_{h}$ energy carried by photons, and the number of photons found in strips
+\item Information on the quality of the track
+%\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
+%\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
+%\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
+%\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
+%\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
+%\item The \pT weighted RMS distances in $\eta$ and $\phi$ between the photons in any strip and the leading 
+%charged track (calculated separately for photons inside and outside the $\Pgt$ signal cone)
+%\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
+%\item $(p_{in} - p_{out})/p_{in}$
+%\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
+%\item The ratio between the total \ac{ECAL} energy and inner track momentum
+%\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
+%\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
+%\item $\chi^2/Ndof$ of the GSF track fit
+%\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
+%similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
 \end{itemize}
@@
 Five working points are provided, ranging from very loose to very tight. The real tau efficiency
-and $Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
+and $\Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
 figures \ref{fig:tau_efficiency}b and c, respectively.
@@
 \begin{center}
-\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyIsol.pdf}}\\
-\subfloat[Anti-e discriminator efficiency]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauEfficiencyEle.pdf}}
-\subfloat[Anti-e discriminator fake rate]{\includegraphics[width=0.5\textwidth]{./Plots/Objects/TauMisIDEle.pdf}}
+\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
+\subfloat[Anti-e discriminator efficiency]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
+\subfloat[Anti-e discriminator fake rate]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
 \end{center}
@@
 \end{figure}
-
-The anti--muon discriminator is a cut-based discriminant, for which two working points are provided:\\
+The anti--muon discriminator is a cut-based discriminant, for which two working points are provided:
 \begin{itemize}
@@
 \end{itemize}
-
-\subsection{Differences between Run 1 and Run 2}
-\label{sec:objects_taus_diff}
-Broadly speaking the algorithm used for hadronic tau reconstruction during Run 1
-was similar to the Run 2 algorithm described earlier in this section \cite{cms-tau-run1}. However, during
-Run 1 strips were reconstructed using a fixed size of $0.05 \times 0.20$ in $\eta \times \phi$.
-The dynamic size used in Run 2 was introduced to mitigate the effects of secondary particles
-with low \pT and multiple \APelectron\Pelectron conversions, resulting in particles ending up outside of 
-the strip window and making the hadronic tau seem less isolated than it actually is.
-In addition, the anti--electron discriminator MVA was trained with fewer input variables and its performance
-was therefore not as good as the Run 2 version.

### 2016-12-19 Objects/Objects.tex
Version of objects chapter before comments

@@
 
-In this chapter the physics objects necessary to be able to perform searches with \Pgt leptons
-in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. Section \ref{sec:objects_pv} details the algorithms
+In this chapter the reconstruction of the physics objects necessary to be able to perform searches with \Pgt leptons
+in the final state in \ac{CMS} will be discussed. Section \ref{sec:objects_pv} details the algorithms
 used to reconstruct charged particle tracks in the inner tracker, with section \ref{sec:objects_ele}
 describing how these tracks are combined with \ac{ECAL} energy deposits to reconstruct electrons.
-In section \ref{sec:objects_muo} the combination of charged tracks in the inner tracker with
-hits in the muon chambers to form reconstructed muons will be discussed. Section \ref{sec:objects_pf}
+The reconstruction of muons by the combination of tracks in the inner tracker with hits in the muon 
+chambers will be discussed in section \ref{sec:objects_muo}.
+Section \ref{sec:objects_pf}
 describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
-all stable particles, which is of particular importance for the reconstruction of jets, missing transverse
-energy and hadronic taus as discussed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
+all stable particles. This is of particular importance for the reconstruction of jets, missing transverse
+energy and hadronic taus as detailed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
 respectively.
@@
 To reconstruct the trajectories of charged particles - and therefore
-their momenta and positions - from the hits these particles leave in the 
-inner tracker, dedicated algorithms are required. In \ac{CMS} the
-\ac{CTF} algorithm is used. This algorithm performs four steps:
+their momenta and positions - from the hits they leave in the 
+inner tracker the
+\ac{CTF} algorithm is used. This algorithm performs four steps.
 First, initial estimates of the parameters of the trajectory are given by track seeds, 
-made out of hits found in 2 or 3 layers of the inner tracker. Then, the track seeds
+made out of the hits found in 2 or 3 layers of the inner tracker. These track seeds
 are extrapolated using a \ac{KF} \cite{trk-kf}, which extrapolates the seeding
-trajectories along the expected flight path of a charged particle and adds 
-additional matched hits it finds in the tracker layers it traverses to the track.
-After the extrapolation has reached the final tracker layers, the \ac{KF} is run again,
+trajectories along the expected flight path of a charged particle. Any additional
+matched hits found along this extrapolated trajectory are added to the track.
+After the extrapolation has reached the final tracker layers the \ac{KF} is run again,
 now with the full set of hits that have been found in the previous step. This provides the best
-estimate of the track parameters. Finally, tracks that fail a specified set of quality 
+estimate of the track parameters. Finally, tracks that fail a set of quality 
 criteria are rejected.
@@
 with \pT $ > 500 $ MeV and $ > 99 \%$ for tracks with \pT $ > 2 $ GeV \cite{cms-trk-7tev}.
-
 %The tracking software at CMS is commonly referred to as the Combinatorial Track Finder (CTF), which is an adaptation of the combinatorial Kalman filter [29–31], which in turn is an extension of the Kalman filter [32] to allow pattern recognition and track fitting to occur in the same frame- work.
@@
 
-The reconstructed tracks are used to determine the positions of all interaction
-vertices in the event. Primary vertices are reconstructed by clustering
+\enlargethispage{\baselineskip}
+Primary vertices are reconstructed by clustering
 tracks that appear to have originated from the same vertex, then fitting 
-for the position of the vertex using the associated tracks. The clustering 
+these tracks for the position of the vertex. The clustering 
 is performed using the \ac{DA} algorithm \cite{vtx-da}, which identifies
@@
 vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
-vertex position. The analyses presented in CHAPMSSM take the primary
-vertex of the hard scatter as the reconstructed vertex with largest scalar sum \pT~of
-the associated tracks. This differs from the analysis presented in chapter \ref{chap:hhh},
+vertex position. The analyses presented in chapter [MSSM] take the primary
+vertex of the hard scatter as the reconstructed vertex for which the scalar sum \pT~of
+the associated tracks is largest. This differs from the analysis presented in chapter \ref{chap:hhh},
 where requirements on the quality of the vertex
 fit and the distances between the vertex and the nominal interaction point 
-were made.
+were additionally made.
  %By doing this both the best estimate
@@
 associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
-
-\begin{figure}
+~\vspace{-1\baselineskip}
+\begin{figure}[h!]
 \begin{center}
@@
 of reconstructed primary vertices
-as a function of the scalar sum \pT of the tracks, 
-measured for the 2015 running conditions in blue triangles
-and for 2016 in red squares.
+as a function of the scalar sum \pT~of the tracks, 
+measured in 2015 (blue triangles) and 2016 (red squares).
 The resolution improves
-with higher sum \pT (corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
+with higher sum \pT~(corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
 \label{fig:objects_tracks_pvres}
@@
 \label{sec:objects_ele}
-Electrons are reconstructed by combining tracks reconstructed
-in the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
+Electrons are reconstructed by combining tracks from 
+the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
 A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
-described in section \ref{sec:objects_pf}.
+that will be described in section \ref{sec:objects_pf}.
 Depending on the thickness of the intervening material, electrons lose up to 86 \% of their energy on
-average by radiating photons before the \ac{ECAL} is reached.
+average due to bremsstrahlung before reaching the \ac{ECAL}.
 To accurately reconstruct the energy of the electron it is
-important to catch the energies of bremsstrahlung photons, which are spread in the $\phi$ direction
-due to the magnetic field. Therefore ``supercluster'' algorithms are needed.
+important to capture the energies of bremsstrahlung photons, which are spread in the $\phi$ direction
+due to the magnetic field. To achieve this, ``supercluster'' algorithms are used.
 In these algorithms the clustering
-is performed by defining a seed crystal as the crystal containg the most deposited energy
-in a region under consideration, where the transverse energy in this crystal
-passes a minimum threshold.
+is performed by defining a seed crystal as the crystal containg a local
+energy maximum above a certain threshold.
 In the barrel, arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
-to the cluster, stepping sideways in both directions in $\phi$. The array is
-only added to the cluster if the energy deposited in it passes a threshold.
-These clusters are grouped into superclusters if each distinct cluster has a seed array in 
-which the energy deposit is larger than a pre-defined minimum.
-In the endcaps the clusters combined into superclusters are arrays of $5\times 5$ crystals,
+to the cluster, stepping sideways in both directions in $\phi$ within a range
+of approximately $\pm 0.3$ rad. Contiguous clusters are merged into
+superclusters if each cluster has a seed array with energy deposit above a minimum.
+In the endcaps arrays of $5\times 5$ crystals are 
 merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.
+%The array is
+%only added to the cluster if the energy deposited in it is larger than a minimum.
+%These clusters are grouped into superclusters if each distinct cluster has a seed array in 
+%which the energy deposit is larger than a pre-defined minimum.
 
 Due to the radiation of bremsstrahlung photons in the tracker,
-the change in electron track curvature can be large, and so the \ac{CTF} does
-not perform optimally. Therefore a dedicated tracking algorithm is used.
-For high \pT~electrons, the best efficiency is reached
+the change in electron track curvature can be large. % and so the \ac{CTF} does
+%not perform optimally. 
+A dedicated tracking algorithm, with better performance than the \ac{CTF} for this 
+particular case, is therefore used.
+For high--\pT~electrons, the best efficiency is reached
 by the use of an \ac{ECAL}-based track seeding algorithm
@@
 layers of the tracker to determine the rough area where the tracker seeds should be.
-Once the tracker seeds have been determined they are extrapolated
+Once the tracker seeds have been found they are extrapolated
 and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the \ac{KF}, which 
-approximates the non-Gaussian energy loss in each layer by the combination of 
+approximates the non--Gaussian energy loss in each layer by a combination of 
 Gaussian distributions rather than the single Gaussian used in the \ac{KF}.
@@
 such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
-decays. Both cut--based and MVA--based algorithms are available. For the selection of electrons in 
-the analyses presented in later chapters these MVA--based algorithms are usually used, 
-with exceptions for the loose identification criteria required for veto-electrons. 
-This BDT is trained using variables such as:
+decays. Both a cut--based and a BDT--based algorithm are available. For the selection of electrons in 
+the analyses presented in later chapters the BDT--based algorithm is used, 
+with exceptions for the loose identification criteria required for vetoing electrons. 
+The variables used to train this BDT include:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width in units of $\eta$ crystals. 
-\item Track quality variables
-\item Distances in $\eta$ and $\phi$ betaween the supercluster and the associated track
-\item Ratios between hadronic and electromagnetic energy in the region of the supercluster, between supercluster energy and momentum of the track, and including 
-$1/E_{\text{SC}} - 1/p_{\Pe}$, the inverse of the supercluster energy, with the inverse of electron track momentum subtracted
+\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy--weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
+\item Track quality variables.
+\item Distances in $\eta$ and $\phi$ between the supercluster and the associated track.
+\item Energy ratios and energy--momentum ratios in the region of the supercluster, including
+$1/E_{\text{SC}} - 1/p_{\Pe}$, where $E_{\text{SC}}$ is the energy in the supercluster and $p_{\Pe}$ the momentum of the electron track (illustrated in figure \ref{fig:ele_id_vars}b).
 %\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
@@
 \end{itemize}
+%Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
+%for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.
 
-Figure \ref{fig:ele_id_vars} shows the distributions of $\sigma_{i\eta,i\eta}$ and $1/E_{sc} - 1/p_e$ 
-for real and misidentified electrons in the full dataset from the 2012 running period of the \ac{LHC}.
-
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 \caption{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
-misidentified electrons (yellow triangles) in a dataset corresponding to 19.7 fb$^{-1}$
-taken at $\sqrt{s} = 8$ TeV, overlaid on the variables for simulated 
+misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
+taken at $\sqrt{s} = 8$ TeV, overlaid on the distributions for simulated 
 real electrons in purple \cite{cms-elereco-run1}.}
@@
 
-\subsection{Isolation}
-\label{sec:objects_ele_iso}
+%\subsection{Isolation}
+%\label{sec:objects_ele_iso}
 The identification requirements discussed up to now reduce the backgrounds 
@@
 \begin{equation}\label{eqn:electron_reliso}
-I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged})} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{P_{T}^{e}},
+I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged}} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{p_{\text{T}}^{e}},
 \end{equation}
@@
 The contribution from neutral particles due to pile--up needs to be subtracted from
-this term, which is estimated as the sum of charged hadronic \pT~for hadrons not associated
-with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.
+this term; it is estimated as the sum of charged hadronic \pT~for hadrons not associated
+with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
 
@@
 \label{sec:objects_muo}
-Muons are reconstructed by combining tracker tracks and tracks
-from the muon system \cite{cms-muon-reco}. Two complementary approaches are used,
-\textit{global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
+Muons are reconstructed by combining tracks in the inner tracker and tracks
+from the muon system \cite{cms-muon-reco}. Two complementary approaches are used:
+``global'' and ``tracker'' muon reconstruction. The former starts from 
 tracks reconstructed in the muon system and searches for a matching
 tracker track, then re--applies the \ac{KF} on the combination
-of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
+of hits in the muon system and inner tracker. Conversely, the tracker muon reconstruction starts from
 tracks in the inner tracker which pass requirements on momentum to be considered
 a muon candidate track. The trajectory is then extrapolated to the muon systems and
-considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
+considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs}, is found.
 Due to the requirement of a single muon segment this method is more efficient than the global muon
@@
 
-For the analysis presented in chapter CHAPMSSM additional ``medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
-Apart from having passed either the global or tracker muon reconstruction, the fraction
-of valid tracker hits must be greater than 49\%. Additional requirements are made on the
-$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
-position matching, on the kink finder in the inner tracker, and the segment compatibility. 
-The compatibility of the tracker- and standalone-reconstructed position is evaluated
-by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
-compatibility there.
-The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
-tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
-is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
-The segment
-compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
-the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
-a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
-
-To pass the identification, global- or tracker muons
-with a large enough fraction of tracker hits must pass \textbf{either} 
+For the analysis presented in chapter chapter [MSSM] ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
+These requirements include:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item The muon is reconstructed by the global muon reconstruction algorithm
-\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
-\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
-\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
-\item The segment compatibility is $>$ 0.303
+\item Reconstruction by either global or tracker muon reconstruction algorithms.
+\item Requirements on track quality, and compatibility between tracker-- and muon system track.
+\item Selection on the segment compatibility, a weight between 0 and 1 which is a measure of the compatibility
+of a track with the muon track segments in muon stations it has crossed.
+\item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in--flight decays.
 \end{itemize}
-\textit{or}:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item The segment compatibility is $>$ 0.451
-\end{itemize}
+%Apart from having passed either the global or tracker muon reconstruction, the selection
+%includes a threshold on the fraction of valid tracker hits, requirements on the
+%$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
+%position matching, on the kink finder in the inner tracker, and the segment compatibility. 
+%The compatibility of the tracker- and standalone-reconstructed position is evaluated
+%by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
+%compatibility there.
+%The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
+%tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
+%is used as a discriminator. If the $\chi^2$ value is large, this could signal an in--flight decay.
+%The segment
+%compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
+%the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
+%a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
+%MEDIUM REQUIREMENTS
+%To pass the identification, global- or tracker muons
+%with a large enough fraction of tracker hits must pass \textbf{either} 
+%\begin{itemize}
+%\setlength{\itemsep}{-\baselineskip}
+%\item The muon is reconstructed by the global muon reconstruction algorithm
+%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
+%\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
+%\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
+%\item The segment compatibility is $>$ 0.303
+%\end{itemize}
+%\textit{or}:
+%\begin{itemize}
+%\setlength{\itemsep}{-\baselineskip}
+%\item The segment compatibility is $>$ 0.451
+%\end{itemize}
+
 In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
 was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
-The criteria are
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item The muon must be reconstructed by the global muon algorithm
-\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
-\item The global track fit must include hits from at least one chamber in the muon system
-\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
-\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
-\end{itemize}
+In addition to having to be reconstructed by the global muon algorithm, selections
+are made on the $\chi^2$/$N_{\text{dof}}$ of the track fit, number of hits of the inner
+track in different tracker layers and number of muon segments the inner track is matched to.
+%TIGHT REQUIREMENTS
+%\begin{itemize}
+%\setlength{\itemsep}{-\baselineskip}
+%\item The muon must be reconstructed by the global muon algorithm
+%\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
+%\item The global track fit must include hits from at least one chamber in the muon system
+%\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
+%\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
+%\end{itemize}
 
-\subsection{Isolation}
-\label{sec:objects_muo_iso}
-As described for electrons in section \ref{sec:objects_ele_iso}, placing isolation 
+%\subsection{Isolation}
+%\label{sec:objects_muo_iso}
+Just as described for electrons in section \ref{sec:objects_ele}, placing isolation 
 requirements on muons will also reduce backgrounds from misidentified jets and heavy--flavour
@@
 energy deposits in the calorimeters. These energy deposits are combined
-using a clustering algorithm, so that stable neutral particles can be identified,
-separated from charged hadrons, and electrons and all bremsstrahlung photons
+using a clustering algorithm, so that stable neutral particles can be identified and
+separated from charged hadrons, and in addition electrons and all bremsstrahlung photons
 can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
@@
 between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
-to the ECAL from the track--tracker layer interaction points, and clusters can be 
+to the ECAL from the interaction points between the track and each tracker layer, and clusters can be 
 linked to the track as a possible bremsstrahlung photon if the extrapolated tangent
@@
 a \ac{PF} muon is identified if the combined tracker and muon system
-momentum is compatible with the tracker-only momentum. %within three standard deviations
+momentum is compatible with the tracker--only momentum. %within three standard deviations
 The muon track is removed from the block before the next step of the algorithm.
@@
 the energy measured in the calorimeters is compatible with the momentum assigned
-to the track, within uncertainties, as charged hadron is identified and the
+to the track, a charged hadron is identified and the
 momentum redefined by fitting the tracker and calorimeter measurements. If
@@
 object $i$ and the beam. The smallest of these distances
-is determined and if this is a distance between object i and an object j, objects
-i and j are combined. If $d_{iB}$ is the smallest distance, object i
+is determined and if this is a distance between an object i and an object j, objects
+i and j are combined. If the smallest distance is a $d_{iB}$, object i
 is called a jet and removed from the list of objects. In the anti-\kT~algorithm
@@
 is not affected by the emission of soft collinear gluons or parton splitting.
-The effects of pile--up particles on the jet energy and substructure can be
-mitigated using several methods. For the analysis presented in CHAPMSSM a
-\ac{CHS} technique is employed \cite{cms-jets-run2}.  In this method
-charged hadronic \ac{PF} candidates not associated with the primary vertex 
+To reject badly reconstructed jets and fake jets due to noise, clustered jets are required to 
+pass loose identification requirements \cite{cms-jet-algos-run1,cms-jets-run2}. These requirements are based on the 
+charged and neutral particle multiplicities in the jet, as well as on the fraction
+of jet energy carried by different \ac{PF} particle types.
+
+Several methods exist for reducing the effects of pile--up particles 
+on the jet energy and substructure.
+For the analysis presented in chapter [MSSM] a
+\ac{CHS} technique \cite{cms-jets-run2} is employed, 
+which means charged hadronic \ac{PF} candidates not associated with the primary vertex 
 are not considered in the jet clustering. For the analysis presented in
@@
 The energy measured for a jet in the detector is usually different from 
-the true particle jet at hadron level. A correction is applied to both
+the true particle jet at hadron level. A correction \cite{cms-jec-2011} is applied to both
 jets in data and jets in \ac{MC} to match the measured and true
-energies as \cite{cms-jec-2011}
+energies as
 \begin{equation}\label{eqn:objects_jec}
@@
  (\text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
-\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
+\text{C}_{\text{rel}}(p_{\text{T}}',\eta)
 \cdot \text{C}_{\text{abs}}(p_{\text{T}}''))\cdot p_{\mu}^{\text{raw}}.
@@
 %\end{equation}
-In this equation $\text{C}_{\text{offset}}$ is an offset correction, $\text{C}_{\text{MC}}$ an
-\ac{MC} calibration factor, $\text{C}_{\text{rel}}$ a relative residual correction
+In this equation $\text{C}_{\text{offset}}$ is an offset correction,
+$\text{C}_{\text{rel}}$ a relative residual correction
 factor and $\text{C}_{\text{abs}}$ an absolute scale correction factor. The corrections
-are applied in sequence with $p_{\text{T}}'$ the transverse momentum 
-of the jet after applying the offset correction and $p_{\text{T}}''$ the \pT of the
+are applied in sequence with $p_{\text{T}}'$ the \pT~of the jet after applying the offset correction and $p_{\text{T}}''$ the \pT~of the
 jet after all of the preceding corrections.
@@
 
-The \ac{MC} calibration factor $\text{C}_{\text{MC}}$ corrects the energy of reconstructed
-jets so that is is on average equal to the energy of jets in \ac{MC} events. This
-factor is measured in simulated multi--jet events, measuring the response $\mathcal{R} = \frac{p_{\text{T}}^{\text{reco}}}{p_{\text{T}}^{\text{gen}}}$
-with $p_{\text{T}}^{\text{gen}}$ the generator--level \pT of the jet. The correction
-factor $\text{C}_{\text{MC}}$ is defined as $\text{C}_{\text{MC}} = \frac{1}{<\mathcal{R}>}$.
-
+%The \ac{MC} calibration factor $\text{C}_{\text{MC}}$ corrects the energy of reconstructed
+%jets so that is is on average equal to the energy of jets in \ac{MC} events. This
+%factor is measured in simulated multi--jet events, measuring the response $\mathcal{R} = \frac{p_{\text{T}}^{\text{reco}}}{p_{\text{T}}^{\text{gen}}}$
+%with $p_{\text{T}}^{\text{gen}}$ the generator--level \pT of the jet. The correction
+%factor $\text{C}_{\text{MC}}$ is defined as $\text{C}_{\text{MC}} = \frac{1}{<\mathcal{R}>}$.
 A di--jet \pT-balancing technique \cite{cms-jec-2011}
@@
 make the response uniform in \pT. It is measured using the \ac{MPF} method \cite{cms-jec-2011}
- using samples of \Pphoton+jets and \PZ+jets events. This method relies on the fact that \Pphoton+jets
-and \PZ+jets events have no intrinsic missing energy, and so any measured \MET~
+ using samples of \Pphoton+ jets and \PZ+ jets events. This method relies on the fact that the
+events used for the measurement have no intrinsic missing energy, and so any measured \MET~
 is used to calibrate the \pT~response of jets in the event.
@@
 \label{sec:objects_jets_btag}
-As b--quarks appear in final states of many of the standard model 
-processes being studied at the \ac{LHC}, as well as in searches for new
-physics, it is important to correctly identify jets which originate
-from the hadronisation of b--quarks.
-As b--hadrons have a relatively
-large mass of 5--6 GeV and a relatively long lifetime $\tau_B \approx 1.5$ ps \cite{pdg-2014},
-they move for roughly $c\tau_B \approx 450$ $\mu$m before decaying. This means 
+As jets due to b--quark hadronisation are an important signature
+for many analylses at the \ac{LHC} it is important to identify such jets correctly.
+Because b--hadrons have a relatively long lifetime $\tau \approx 1.5$ ps \cite{pdg-2014},
+they move for roughly $c\tau \approx 450$ $\mu$m before decaying. This means
+%large mass of 5--6 GeV
 they produce a displaced secondary decay vertex in the inner tracker.
@@
 the \ac{CSV} algorithm \cite{cms-btag-paper} has been used, with the upgraded
-\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter CHAPMSSM. 
+\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter [MSSM]. 
 The \ac{CSV} algorithm takes \ac{PF} jets with \pT$ > 20$ GeV and $|\eta|<2.4$ as input and 
@@
 In addition, the algorithm makes use of a multilayer perceptron to combine the variables
-instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
-for the addition of extra variables to discriminate between b- and other jets. Figure \ref{fig:objects_bjets}a shows
-the distribution of the \ac{CSV}v2 discriminator in multijet events in the 2015 data sample.
-
+instead of constructing a likelihood ratio from the input variables \cite{cms-btag-run2}. This allows
+for the addition of extra variables to discriminate between b- and other jets. %Figure \ref{fig:objects_bjets}a shows
+%the distribution of the \ac{CSV}v2 discriminator in multijet events in the 2015 data sample.
 Once the discriminator has been constructed, loose- medium- and tight working points
@@
 the data and \ac{MC} efficiencies. The measurements of the tagging efficiency
-for genuine b--jets makes use of samples containing a muon overlapping with the jet, 
-making use of the $\approx$ 11\% semileptonic branching fraction of b's. For other
-ranges of jet \pT the measurement can be complemented by measurements from samples
+for genuine b--jets is based on samples containing a muon overlapping with the jet, 
+making use of the $\approx$ 11\% semileptonic branching fraction of b's. This
+measurement can be complemented by measurements from samples
 with the kinematic signatures of \ttbar production, making use of 
-the large  $\Ptop \rightarrow \PW \Pbottom$ branching ratio. Measurements
-of mis--tagging efficiencies for light jets are made using negative--tagging
-algorithms to select samples enriched in light jets from multijet events.
+the large  $\Ptop \rightarrow \PW \Pbottom$ branching ratio. %Measurements
+%of mis--tagging efficiencies for light jets are made using negative--tagging
+%algorithms to select samples enriched in light jets from multijet events.
+
+\begin{figure}[h!]
+%\subfloat[CSVv2 distribution]{\includegraphics[width=0.6\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}\\
+\includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
+\caption{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
+%collected at $\sqrt{s} = 13$ TeV and (b) 
+The b--tagging scale factors and errors for b--jets in the data sample collected during 2015
+as a function of jet \pT~for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
+\label{fig:objects_bjets}
+\end{figure}
 
@@
 and uncertainties in the fractions of different jet types.
-Figure \ref{fig:objects_bjets}b shows the b--tagging scale factors, and associated errors,
+Figure \ref{fig:objects_bjets} shows the b--tagging scale factors, and associated errors,
 for the medium working point of the \ac{CSV}v2 discriminator in the
 2015 data sample.
-
-\begin{figure}
-\begin{center}
-\subfloat[CSVv2 distribution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}
-\subfloat[CSVv2 scale factors]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/CSVSF.png}}
-\end{center}
-\caption{(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
-collected at $\sqrt{s} = 13$ TeV and (b) the b--scale factors and errors
-as a function of jet \pT for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
-\label{fig:objects_bjets}
-\end{figure}
-
 %Some efficiency measurements are performed using samples that include a jet with a muon within ∆R = 0.4 from the jet axis (a “muon jet”).
 Because the semileptonic branching fraction of b hadrons is significantly larger than that for other hadrons (about 11%, or 20% when b → c → l cascade decays are included), these jets are more likely to arise from b quarks than from another flavour.
-
 %The combinatorial complexity of the reconstruction of the decay points (secondary vertices) of b or c hadrons is more challenging in the presence of multiple proton-proton interactions.
@@
 will give rise to an energy imbalance in the transverse plane, and so their
-presence can be inferred from missing energy \MET in the event.
+presence can be inferred from missing energy \MET~in the event.
 
-The \MET is defined as $-\Sigma \vec{p}_{\text{T}}$, where
+The \MET~is defined as $-\Sigma \vec{p}_{\text{T}}$, where
 the sum runs over all final--state particles and jets in the event. This quantity
@@
 response for hadronic particles.
-
-%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature.
-This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections
-
-The \MET measurement can therefore be corrected by jet energy corrections as
+Therefore, the increase the accuracy of the \MET~measurement the jet energy corrections should be propagated as
 \begin{equation}\label{eqn:objects_met_corr}
@@
 
-The \MET can also be mismeasured due to pile--up interactions, and improved
-measurement of the \MET at high pile--up can be obtained by using the MVA \MET
-algorithm, used for \MET reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
-CHAPMSSM. This algorithm computes a correction to the hadronic
+%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature.
+This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections
+The \MET~can also be mismeasured due to pile--up interactions, and an improved
+measurement of the \MET~at high pile--up can be obtained by using the MVA \MET~
+algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
+chapter [MSSM]. This algorithm computes a correction to the hadronic
 recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
@@
 \end{equation}
+where $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
+constituents selected as the di--$\tau$ candidate.
 
-with $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
-candidate constituents selected as signal particles, the di--$\tau$ candidate in the case of \htotautau
-analyses.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
+\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
+\end{center}
+\caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
+\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET~
+values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
+circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
+\label{fig:objects_mvamet}
+\end{figure}
 
@@
 one uses a data sample with the corrected recoil direction to compute a correction
-to the magnitude of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
-recoil, the azimuthal angle and scalar \pT~sum of all \ac{PF} particles for several 
+to the magnitude of the hadronic recoil. This BDT regression uses the magnitude of the hadronic
+recoil, its azimuthal angle and the scalar \pT~sum of all \ac{PF} particles for several 
 different \MET~definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
@@
 
-\begin{figure}
-\begin{center}
-\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
-\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
-\end{center}
-\caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
-\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb${-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET~
-values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
-circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
-\label{fig:objects_mvamet}
-\end{figure}
-
 In the process of calculating the corrections to the hadronic recoil using the MVA \MET~
@@
 by mismeasurement of jet energy \cite{cms-met-run1}.
-
 %Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
@@
 \label{sec:objects_met_recoilcorr}
-To correct for the mismodelling of \MET~in events without genuine \MET~ in \ac{MC} events, recoil corrections are determined. 
-The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T},\nu/\text{leptons}}$ 
+To correct for the mismodelling of \MET~in \ac{MC} events without genuine \MET, recoil corrections are determined. 
+The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{ leptons}/\nu}$ 
 is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT~of the boson producing the leptons
 and neutrinos. For the analyses
-presented in chapters \ref{chap:hhh} and CHAPMSSM it is measured in \Zmm events, where no neutrinos
+presented in chapters \ref{chap:hhh} and [MSSM] it is measured in \Zmm events, where no neutrinos
 are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
@@
 \end{equation}
-
 %Recoil corrections are applied to correct for the mismodelling of $\MET$ in events without genuine $\MET$ \cite{RecoilCorrPresentation}.
@@
 of the most common possible decay modes is given in table \ref{tab:hadronic_tau_decays}
-
 \begin{table}[htp]
@@
 \end{table}
+%\subsection{Identification}
+%\label{sec:objects_tau_id}
 
-\subsection{Identification}
-\label{sec:objects_tau_id}
 Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
@@
 As table \ref{tab:hadronic_tau_decays}
-shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a high
-probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays convert to
-\APelectron \Pelectron pairs in the tracker volume, which are bent in the magnetic field and 
+shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a large
+probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays will convert to
+\APelectron \Pelectron pairs, which are bent in the magnetic field and 
 therefore cause showers dispersed in the $\phi$ direction in the \ac{ECAL}. Therefore, to 
@@
 within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
-recomputed as the energy-weighted average of the electron/photon constituents in the strip.
+recomputed as the energy--weighted average of the electron/photon constituents in the strip.
 This procedure is repeated until there are no more electrons or photons with \pT $ > 0.5$~GeV  within the 
@@
 \begin{split}
-&\Delta \eta  = f(p_{\text{T}}^{\Pe/\Pphoton}) + f(p_{\text{T}}^{\text{strip}}) \\
-&\Delta \phi  = g(p_{\text{T}}^{\Pe/\Pphoton}) + g(p_{\text{T}}^{\text{strip}})\\
+&\Delta \eta  = 0.2\cdot p_{\text{T},\Pe/\Pphoton}^{-0.66} + 0.2\cdot p_{\text{T,strip}}^{-0.66} \\
+&\Delta \phi  = 0.35\cdot p_{\text{T},\Pe/\Pphoton}^{-0.71} + 0.35\cdot p_{\text{T,strip}}^{-0.71}\\
 \end{split}
 \end{equation}
-Where \pT$^{\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
-and \pT$^{\text{strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
+Where $p_{\text{T},\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
+and $p_{\text{T,strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
 In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$ \cite{cms-tau-2015}.
 
-The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:
-\begin{equation}\label{eqn:dynamicstripfg}
-\begin{split}
-&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66} \text{ and } \\
-&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}.\\
-\end{split}
-\end{equation}
+%The functions $f(p_{\text{T}})$ and $g(p_{\text{T}})$ are defined as:
+%\begin{equation}\label{eqn:dynamicstripfg}
+%\begin{split}
+%&f(p_{\text{T}}) = 0.2\cdot p_{\text{T}}^{-0.66} \text{ and } \\
+%&g(p_{\text{T}}) = 0.35\cdot p_{\text{T}}^{-0.71}.\\
+%\end{split}
+%\end{equation}
 If the $\Sigma$ \pT~of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
@@
 \item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
-\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with mass $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV. For momenta
-less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
-\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}$~GeV. For momenta
-less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
+\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with $\Pgt$  mass requirement $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV, with the
+upper limit on the mass at least 1.3 and at most 4.2 GeV.
+%less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
+\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}$~GeV, with the
+upper limit on the mass at least 1.2 and at most 4.0 GeV.
+%less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
 \item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate 
@@
 
-\subsection{Isolation and discrimination against light leptons}
-\label{sec:objects_tau_iso}
-Requiring the reconstructed $\Pgt_{h}$ to be isolated reduces the jet $\rightarrow\Pgt_{h}$ fake rate. The isolation
-can be defined using a cut--based discriminator using the isolation sum,
+%\subsection{Isolation and discrimination against light leptons}
+%\label{sec:objects_tau_iso}
+Requiring the reconstructed $\Pgt_{h}$ to be isolated reduces the jet $\rightarrow\Pgt_{h}$ fake rate. Isolation
+discriminators can be defined using the isolation sum,
 \begin{equation}\label{eqn:cutbased_iso}
@@
 where the first term denotes the sum of the transverse momenta of all charged particles not part
-of the identified hadronic tau,  with \pT $> 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the 
-direction of the hadronic tau, with charged particle tracks required to be compatible with having
+of the identified hadronic tau. Only particles with \pT $> 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the 
+direction of the hadronic tau are taken into account and the charged particle tracks are required to be compatible with having
 originated from the $\Pgt_{h}$ production vertex within $d_Z < 0.2$ cm. The second term denotes the sum
@@
 
-In addition to the isolation sum, a selection on the sum of transverse momenta
+In addition to the isolation sum, requirements on the sum of transverse momenta
 of electrons and photons included in strips but which are located outside of the signal cone,
@@
 \setlength{\itemsep}{-\baselineskip}
-\item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}
-\item Track--related variables such as impact parameters, quality of the track, and information about decay vertices
-\item Information about photons: the momentum weighted $\Delta R$ and/or $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found
-\item $\Pgt_{h}$--related kinematic quantities, plus the reconstructed decay mode  
+\item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
+\item Track--related variables such as impact parameters, quality of the track, and information about decay vertices.
+\item Information about photons: the momentum weighted $\Delta R$ and/or $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
+\item $\Pgt_{h}$--related kinematic quantities, plus the reconstructed decay mode.  
 %\item The charged-and neutral-particle isolation sums
@@
 
-Figure \ref{fig:tau_iso_efficiency}a compares the \Pgt identification efficiency with the
+Figure \ref{fig:tau_efficiency}a compares the $\Pgt_{h}$ identification efficiency with the
 jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
@@
 on isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
-discriminator has better performance than the cut-based discriminator alone.
+discriminator performs better than the cut-based discriminator alone.
 
 In order to reduce the $\Pe\rightarrow\Pgt_h$ and $\Pgm\rightarrow\Pgt_h$ fake rate, 
-anti-electron and anti--muon discriminators are used. 
-The anti--electron discriminator is a BDT--based discriminator trained using input variables as:
+anti--electron and anti--muon discriminators are used. 
+The anti--electron discriminator is a BDT--based discriminator trained using input variables such as:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item Kinematic variables of the $\Pgt_{h}$ candidate and \ac{GSF} track, including visible mass of the $\Pgt_{h}$
-\item Energy/momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum
-\item Photon--related variables, such as the momentum--weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the $\Pgt_{h}$ energy carried by photons, and the number of photons found in strips
-\item Information on the quality of the track
+\item Kinematic variables of the $\Pgt_{h}$ candidate and \ac{GSF} track, including visible mass of the $\Pgt_{h}$.
+\item Energy/momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
+\item Photon--related variables, such as the momentum--weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the $\Pgt_{h}$ energy carried by photons, and the number of photons found in strips.
+\item Information on the quality of the track.
 %\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
@@
 
-Five working points are provided, ranging from very loose to very tight. The real tau efficiency
+Five working points are provided, ranging from very loose to very tight. The $\Pgt_{h}$ efficiency
 and $\Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 \setlength{\itemsep}{-\baselineskip}
-\item \textbf{Loose:} The $\tau_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or when the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is $<0.2\cdot p_{\text{leading track}}$.
-Otherwise it passes the discriminator
+\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
+Otherwise it passes the discriminator.
 \item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.

### 2016-12-19 MSSM/MSSM.tex
Adding skeleton of MSSM chapter

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}

In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on 12.9 fb$^{-1}$ collected
at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the two decay modes (see THEORY) and decay into $\Pgt\Pgt$. In 
addition, the results are interpreted in MSSM benchmark scenarios and 2D likelihood
scans of the two production modes are performed. A very similar analysis
was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
As it is so similar to the analysis performed on the 2016 dataset it
will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.
The results of the 2015 analysis will be shown, in addition to a combination of the 2015 and 2016 datasets.

For the analysis described in this chapter, as well as the 2015 analysis not detailed
here, I was responsible for optimisation of object selection and categorisation,
as well as studies of background methods for the \mutau, \etau and \tautau channels,
evaluation of systematic uncertainties in all four channels, and for producing
the statistical results, including model--dependent interpretations.

\section{Datasets and MC samples}
\label{sec:mssm_datasets}

\section{Optimisation of object selection}
\label{sec:mssm_baseline_opt}

\section{Event selection and categorisation}
\label{sec:mssm_eventsel}

\section{\ac{MC} to data correction factors}
\label{sec:mssm_mccorrs}

\section{Discriminating variable}
\label{sec:mssm_discrvar}

\section{Background estimation}
\label{sec:mssm_bkgs}

\section{Systematic uncertainties}
\label{sec:mssm_uncs}

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}

\section{Signal extraction}
\label{sec:mssm_signalextraction}

\subsection{Inclusion of control regions in the fit}
\label{sec:mssm_sigext_ctrl}

\section{Results}
\label{sec:mssm_results}

\subsection{Model--independent results}
\label{sec:mssm_results_modelindep}

\subsection{Interpretation in MSSM benchmark scenarios}
\label{sec:mssm_results_modeldep}

\section{Combination of 2015 and 2016 datasets}
\label{sec:mssm_combination}

\subsection{Procedure}
\label{sec:mssm_combination_procedure}

\subsection{Results}
\label{sec:mssm_combination_results}

\section{Overview of uncertainties}
\label{sec:mssm_uncs_overview}
The systematics that are applied are summarised in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}.

\begin{table}[!h]
\begin{center}
\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
or background events in the $\mu \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
 {\scriptsize
 \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
    \hline
\textbf{ Process }
    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
    \hline
    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
    All from MC    & 6.2\%  &6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
    All from MC & 0--1\% & 0--2\% & 0--1\% & 0--1\%& 0--12\% & 3--11\% & 0--15\% & 0--14\% & Fully correlated \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{scale} }\\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ, VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ,VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\textbf{Muon identification and trigger} }\\
    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
    \hline
    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
    All from MC & 0--3\% & 0--3\% & 0--3\% & 0--2\% & 1--3\% &  0--3\%& 0--3\% & 0--3\%& Fully correlated\\
    W &  &  &  &  & 4\% & 4\% & 6\% & 6\%& Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
    All from MC & & & & & 1--7\% & & & & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
    \hline
    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt$\textbf{: $Z\to\Pgt\Pgt / Z\to\Pgm\Pgm$ extrapolation } } \\
    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\
    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Corr. between cats, uncorr. between chns        \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns  \\
    \hline
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
    W & 2\% & 2\% & & &11\% &11\% & & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
    W & 2\% & & 2 \% & &14\% & & 14\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
    %W &  & &  & &12\% & 8\%& 22\% & 14\%& Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
    QCD & 4\% & 4\% & & & 60\% & 60\% & & &Fully uncorrelated \\
    \hline
\end{tabular}
}
\label{tab:SystematicUncertainties_mt}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
or background events in the $e \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
 {\scriptsize
 \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
    \hline
\textbf{ Process }
    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
    \hline
    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
    All from MC    & 6.2\%  & 6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
    All from MC & 0--1\% & 0--1\% & 0--2\% & 0--1\%& 1--14\% & 0--12\% & 0--15\% & 0--15\% & Fully correlated \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{scale}}\\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ          \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\textbf{Electron identification and trigger} }\\
    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
    \hline
    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
    All from MC & 0--3\% & 0--3\% & 0--4\% & 0--4\% & 1--4\% & 0--2\% & 0--2\% & 0--2\% & Fully correlated\\
    W &  &  &  &  & 5\% & 2\% & 10\% & 3\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
    All from MC & & & & & 0--3\% & & & & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
    \hline
    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{ extrapolation} } \\
    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\
    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Corr. between cats, uncorr. between chns       \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns       \\
    \hline
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
    W & 2\% & 2\% & & &14\% &14\% & & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
    W & 2\% & & 2 \% & &17\% & & 17\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
    %W &  & &  & &11\% &14\% & 21\% & 16\%& Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
    QCD & 12\% & 12\% & & & 60\% & 60\% & & &Fully uncorrelated \\
    \hline
\end{tabular}
}
\label{tab:SystematicUncertainties_et}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the $\tau_{h} \tau_{h}$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} & \\
    \hline
    Process & No b-tag & B-tag & Correlation                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\%  & Fully correlated                           \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}} \\
    All from MC      & 0--4\%      & 0--9\%  & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
    \hline
    \multicolumn{4}{l}{Tau-lepton identification and trigger} \\
    ZTT,TTT,VVT, signal         & 10\%    & 10\%  & Fully correlated                      \\
    ZTT,TTT,VVT, signal         & 9.2\%     & 9.2\%   & Correlated between categories, uncorrelated between channels \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\
    All from MC   & 0--4\%     & 0--11\%  & Fully correlated                  \\
    \hline
   \multicolumn{4}{l}{\textbf{B-mistag rate}} \\
    All from MC    &  0--1\%    & 0--12\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{Tau-lepton energy scale}} \\
    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels                       \\
    \hline
    \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\
    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels   \\
    \hline
    \multicolumn{4}{l}{\textbf{DY reweighting } } \\
    ZTT       & shape      & shape & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\
    TTT,TTJ & shape & shape & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production}}\\
    ZL,ZJ       & 4\%      & 4\%  & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation}}\\
    ZTT         & 3\%        & 5\%  & Fully uncorrelated                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TTT,TTJ        & 6\%       & 6\%  & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\
    VVT,VVJ &  5\%        & 5\%       & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\
    ZL & 10\%     & 10\%       & Correlated between categories, uncorrelated between channels                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\
    ZJ,W,TTJ & 20\%     & 20\%       & Correlated bewteen categories, uncorrelated between channels     \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (stat) }} \\
    QCD  & 2\% & 20\%  & Fully uncorrelated\\
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (syst) }} \\
    QCD  & 12\% & 14\%  & Fully uncorrelated\\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W & 4\% & 4\% & Fully correlated \\
\end{tabular}}
\label{tab:SystematicUncertainties_tt}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the $e\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \hline
    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \hline
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \hline
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}

### 2016-12-25 Hhh/Hhh.tex
Adding more on MSSM event selection

@@
 In both channels a selection on the transverse mass, \mT,~between the electron/muon
-and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
+and missing transverse energy, defined as,
 \begin{equation}\label{eqn:hhh_selection_mt}
-m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
+m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})},
 \end{equation}
+is applied.
 In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal

### 2016-12-25 MSSM/MSSM.tex
Adding more on MSSM event selection

@@
 \label{sec:mssm_datasets}
+The dataset used for this analysis corresponds to an integrated 
+luminosity of 12.9 fb$^{-1}$ collected at a centre--of--mass
+energy of 13 TeV during the first half of
+the 2016 p--p running period of the \ac{LHC}. Section
+\ref{sec:mssm_combination} includes the combination of this
+dataset with a dataset collected during the 2015 p--p running
+period of the \ac{LHC}. This dataset corresponds to an integrated
+luminosity of 2.3 fb$^{-1}$ collected at $\sqrt{s} = 13$ TeV.
 
-\section{Optimisation of object selection}
-\label{sec:mssm_baseline_opt}
+Signal and background events were generated using
+various \ac{MC} event generators. Signal samples
+for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow b\bar{b}\phi$
+production processes of $\PHiggs/\PHiggsps$ were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
+These samples were produced in a range of masses between 90 GeV and 3.2 TeV.
+This range is slightly wider than the range in which MSSM Higgs sector
+benchmark computations are available, 90 GeV -- 2 TeV, and 
+improves on the mass range, up to 1 TeV, studied during Run 1 in the context of BSM Higgs searches.
+SM Higgs signal samples are used for the interpretation of the analysis results in 
+MSSM benchmark scenarios. These samples are generated using \texttt{Powheg} \cite{powheg1,powheg2,powheg3}.
+
+\ttbar- and single-top background samples are generated using \texttt{Powheg},
+with \texttt{MadGraph5\_aMC\@NLO} \cite{amcnlo} used for the generation of di--boson background
+samples and part of the W+$\gamma$ background included in the \emu channel only.
+\Wjets and \Zll backgrounds are generated with the \ac{MadGraph 5} \cite{madgraph}
+matrix element generator. Both samples containing a mixture
+of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
+are generated. These exclusive samples increase the available number of
+background events with higher jet multiplicities.  Part of the W+$\gamma$ background
+samples are also generated with this event generator.
+%note LO samples used because to get same number of effective
+%events would need to generate more NLO samples
+The `inclusive' and `exclusive' samples are reweighted
+before they are combined so as to preserve the correct
+fractions of events with each jet multiplicity.
+
+Parton showering and hadronisation are modelled using \texttt{PYTHIA 8} for all 
+samples. Minimum--bias events generated with \texttt{PYTHIA 8} are
+added to all \ac{MC} samples to model additional interactions.
+
+%THIS SECTION SHOULD JUST GO INTO THE DETAILED EVENT SELECTION
+%SECTION
+%\section{Optimisation of object selection}
+%\label{sec:mssm_baseline_opt}
+%At the start of Run 2 of the \ac{LHC} an effort was first made to
+%optimise the default, \textit{baseline} di-\Pgt pair selection. This provides
+%a common starting point for all $\PHiggs \rightarrow \Pgt\Pgt$ analyses, on
+%top of which additional selections can be made for specific analyses such
+%as the MSSM \AHtotautau analysis presented in this chapter.
+
+%\subsection{Electrons and muons}
+%\label{sec:mssm_baseline_opt_elemu}
+%For the optimisation of the baseline selection of
+%electrons and muons the main optimisable
+%selection is the choice of isolation discriminator and
+%of
 
@@
 \label{sec:mssm_eventsel}
+In this section an overview of the event selection,
+and how it was optimised, is given. More detailed information
+on how the used objects used are reconstructed, 
+and a more in--depth description of the identification criteria, 
+is given in chapter \ref{chap:objects}.
+
+\subsection{Pair selection and sorting}
+\label{sec:mssm_eventsel_pairs}
+The basis of the event selection is the selection of \mutau, \etau,
+\tautau and \emu pairs following the requirements described
+in the following subsections. After applying trigger
+requirements, identification criteria and kinematic cuts
+more than one possible candidate pair can exist. In this
+case the pair is chosen as follows:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
+electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
+and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
+object with raw MVA isolation value nearest to 1.
+\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
+\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
+candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
+and the $\Pgt_h$ for \etau and \mutau channels).
+\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
+\end{itemize}
+
+To prevent overlap with other channels, events are rejected
+if there are muons and electrons, other than those in the selected pair,
+with \pT $>10$ GeV and passing loose ID and isolation requirements.
+This also reduces backgrounds from \WZ events. 
+In addition to this, \Zee events are 
+reduced in the \etau channel by rejecting events
+where an opposite--sign pair of electrons of \pT $>15$ GeV
+and passing very loose ID and isolation requirements can be formed. 
+In the \mutau channel the contribution from \Zmm events
+is reduced in a similar fashion.
+
+\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
+\label{sec:mssm_eventsel_mt}
+The first selection layer in the \mutau channel is a trigger
+that only requires a muon at \ac{L1}. At the level of the \ac{HLT}, 
+loose identification and isolation criteria are then applied to this muon.
+
+The offline event selection proceeds to require an oppositely charged
+muon and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
+The minimum \pT of the muon is required to be 23 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+Additional ``medium'' identification requirements are placed on the muon, in addition
+to requiring the muon to be consistent with having originated from the primary vertex, such that
+the impact parameters $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm. The muon is also required
+to be isolated, with a selection on its relative isolation variable calculated with a cone size of 0.4 of $< 0.15$.
+
+The hadronic tau needs to have a \pT greater than 30 GeV, $|\eta|<2.3$,
+is required to be reconstructed by the HPS algorithm and to pass the medium
+working point of the MVA isolation discriminator. The hadronic tau also needs
+to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
+required to be less than 0.2 cm.
+
+The selection on the muon's relative isolation is chosen after comparing
+the performance of several isolation variables at different
+relative isolation values. This was based on a simple \mutau channel
+event selection as described above, with varying isolation variables.
+The selection was optimised based on two figures of merit, both of
+which consider \Ztautau as the signal and the other backgrounds
+as background. The first figure of merit used is the number of signal events divided by the
+square root of the number of background events, $S/\sqrt{B}$, after
+the selection. The aim with this figure of merit is to choose
+the isolation selection that maximises it. The second figure of merit
+is the uncertainty interval on the best-fit value for a maximum--likelihood fit
+to the \Ztautau signal strength, which should be minimised by the choice of
+isolation selection.
+
+Different isolation variables were studied over a range of values
+to cut at. In addition to the $\Delta\beta$ corrected isolation variable analogous
+to the one given for electrons in equation \ref{eqn:electron_reliso} with 
+isolation cone sizes in $\Delta R$ of 0.3 and 0.4, a very similar
+variable which does not just consider charged \ac{PF} hadrons, but
+also electrons and muons in the isolation sum is considered. This
+variable is also studied for both cone sizes of 0.3 and 0.4. Finally,
+a relative isolation variable based solely on the \pT of tracks from the primary
+vertex,
+\begin{equation}\label{eqn:reltrkiso}
+I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{tracks from PV within cone of 0.3 of the muon}}}{p_{\text{T}}^{\mu}}, \end{equation} 
+is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
+size of the error interval from the maximum--likelihood fit to the \Ztautau signal strength shown in 
+\ref{fig:mssm_selection_mt_muons}b. From the fact that both figures of merit do not
+vary so much with different isolation cuts and different variables we can see that this analysis
+is not so sensitive to fake,nonisolated muons. The choice of isolation variable is therefore
+driven mostly by simplicity and consistency with other \ac{CMS} analyses.
+
+\begin{figure}[h!]
+\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.pdf}}
+\subfloat[Size of error interval]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_muons_iso_errint.pdf}}
+\caption{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
+the best--fit value of a maximum--likeihood fit to the \Ztautau signal strength,
+for various cut values of the $\Delta\beta$--corrected
+isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
+the $\Delta\beta$--corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
+the $\Delta\beta$--corrected isolation variable including electrons and muons in the isolation
+sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
+the tracker--based relative isolation (solid squares).}
+\label{fig:mssm_selection_mt_muons}
+\end{figure}
+
+A topological selection on the \mT~variable, 
+introduced in section \ref{sec:hhh_selection_categories}, is made on 
+events in the \mutau channel. This selection and the
+cut on hadronic tau isolation working point interfere 
+with each other and therefore they are optimised in a 2D--optimisation. 
+In this method
+
+\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e tau channel}}
+\label{sec:mssm_eventsel_et}
+
+\subsection{\texorpdfstring{Event selection in the \tautau channel}{Event selection in the tau tau channel}}
+\label{sec:mssm_eventsel_tt}
+
+\subsection{\texorpdfstring{Event selection in the \emu channel}{Event selection in the e mu channel}}
+\label{sec:mssm_eventsel_em}
+
+\subsection{Leptonvetos}
+\label{sec:mssm_eventsel_leptonvetos}
+
+\subsection{Categorisation}
+\label{sec:mssm_eventsel_categories}
+
+NEED FIGURE OF NJETS AND NBJETS WITH SIGNAL ON!
 
@@
 \label{sec:mssm_bkgs}
+
+\subsection{\texorpdfstring{\mutau and \etau channels}{mutau and etau channels}}
+\label{sec:mssm_bkgs_mtet}
+
+\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
+\label{sec:mssm_bkgs_mtet_ztt}
+
+\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
+\label{sec:mssm_bkgs_mtet_wjets}
+
+\subsubsection{QCD}
+\label{sec:mssm_bkgs_mtet_qcd}
+
+\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
+\label{sec:mssm_bkgs_mtet_tt}
+
+\subsubsection{Other backgrounds}
+\label{sec:mssm_bkgs_mtet_other}
+
+\subsection{\texorpdfstring{\tautau channel}{tautau channel}}
+\label{sec:mssm_bkgs_tt}
+
+\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
+\label{sec:mssm_bkgs_tt_ztt}
+
+\subsubsection{QCD}
+\label{sec:mssm_bkgs_tt_qcd}
+
+\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
+\label{sec:mssm_bkgs_tt_wjets}
+
+\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
+\label{sec:mssm_bkgs_tt_tt}
+
+\subsubsection{Other backgrounds}
+\label{sec:mssm_bkgs_tt_other}
+
+\subsection{\texorpdfstring{\emu channel}{emu channel}}
+\label{sec:mssm_bkgs_em}
+
+\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
+\label{sec:mssm_bkgs_em_ztt}
+
+\subsubsection{QCD}
+\label{sec:mssm_bkgs_em_qcd}
+
+\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
+\label{sec:mssm_bkgs_em_wjets}
+
+\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
+\label{sec:mssm_bkgs_em_tt}
+
+\subsubsection{Other backgrounds}
+\label{sec:mssm_bkgs_em_other}
 

### 2016-12-25 MSSM/MSSM.tex
More MSSM stuff

@@
 \begin{figure}[h!]
-\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.pdf}}
-\subfloat[Size of error interval]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_muons_iso_errint.pdf}}
+\begin{center}
+\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.pdf}}~\\
+\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.pdf}}
+\end{center}
 \caption{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
@@
 events in the \mutau channel. This selection and the
-cut on hadronic tau isolation working point interfere 
+choice of hadronic tau isolation working point interfere 
 with each other and therefore they are optimised in a 2D--optimisation. 
-In this method
+The pre--fit expected upper limits on $\sigma\times$BR for both gg$\phi$ and bb$\phi$
+production with decay into $\Pgt\Pgt$ at several mass points 
+in the 90 GeV -- 3.2 TeV range are used to do this. 
+Because of the use of such a wide range of signal masses, it
+is not possible to choose a selection that is optimal
+for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
+figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on $\sigma\times$BR for
+the gluon--gluon fusion production process, at a mass $m_{\phi} = 160$ GeV, with
+figures \ref{fig:mssm_selection_mt_taumt}b,c and d showing this upper limit at $m_{\phi} = 900$ GeV,
+$m_{\phi} = 1600$ GeV and $m_{\phi} = 2900$ GeV respectively. From these figures
+we can observe that looser selections are preferred for higher masses. This can be
+explained by considering the function of each of the selections. Tightening the hadronic
+tau isolation working point reduces the selection of fake taus and increases the proportion
+of backgrounds which contain real hadronic taus. The \mT~selection reduces
+the \Wjets background. As the backgrounds are concentrated at the lower
+end of the spectrum of mass--like discriminating variables, such tighter
+selections are preferred where signal and backgrounds overlap. However, at higher
+mass points the signal--sensitive range of the discriminating variable is 
+low in backgrounds and there is more benefit to loosening the selection
+to increase the signal efficiency than to keep the tighter selection
+to reduce an already low background.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160.0_range12.pdf}}
+\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900.0_range12.pdf}}~\\
+\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600.0_range12.pdf}}
+\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900.0_range12.pdf}}
+\end{center}
+\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
+s a function of tau isolation working point (from very loose to very very tight) and
+of \mT~ cut from \mT$<20$ GeV to \mt$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+for $m_{\phi}$ = 160 GeV (a), 900 GeV (b), 1600 GeV (c) and 2900 GeV (d). The most optimal combination of \mT~selection and 
+hadronic tau isolation working point varies by mass point, with looser selections preferred for higher masses.}
+\label{fig:mssm_selection_mt_taumt}.
+\end{figure}
+
+Based on this information, for the analysis on the 2015 dataset the selection was optimised
+for mass points around 700-800 GeV. For the analysis on the 12.9 fb$^{-1}$ collected
+in the first half of 2016, the selection was further loosened by 10 GeV in \mT~cut
+and one step in hadronic tau isolation working point, to obtain the medium isolation working
+point selection combined with a selection on \mT$<40$ GeV.
+
+The choice of the hadronic tau \pT selection is driven by the effect on the low mass region:
+raising the \pT selection by 10 GeV from the minimum of 20 GeV does not affect the sensivity
+of the analysis for high mass points, while recovering some of the loss of loosening 
+tau isolation working point and \mT~cut. This is because when using \pT$>30$ GeV 
+fewer background events are selected.
 
@@
 \label{sec:mssm_combination_results}
-
-\section{Overview of uncertainties}
-\label{sec:mssm_uncs_overview}
-The systematics that are applied are summarised in
-table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
-channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
-in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
-in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
-the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
-in table \ref{tab:SystematicUncertainties_zmm}.
-
-\begin{table}[!h]
-\begin{center}
-\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
-or background events in the $\mu \tau_{h}$ channel. Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
- {\scriptsize
- \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
-     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
-    \hline
-\textbf{ Process }
-    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
-     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
-    All from MC    & 6.2\%  &6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
-    All from MC & 0--1\% & 0--2\% & 0--1\% & 0--1\%& 0--12\% & 3--11\% & 0--15\% & 0--14\% & Fully correlated \\
-    \hline
-    \multicolumn{10}{l}{\MET \textbf{scale} }\\
-    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ, VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
-    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
-    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ,VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Muon identification and trigger} }\\
-    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
-    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
-    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
-    \hline
-    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
-    All from MC & 0--3\% & 0--3\% & 0--3\% & 0--2\% & 1--3\% &  0--3\%& 0--3\% & 0--3\%& Fully correlated\\
-    W &  &  &  &  & 4\% & 4\% & 6\% & 6\%& Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
-    All from MC & & & & & 1--7\% & & & & Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
-    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
-    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
-    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
-    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
-    \hline
-    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
-    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
-    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
-    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
-    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
-   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt$\textbf{: $Z\to\Pgt\Pgt / Z\to\Pgm\Pgm$ extrapolation } } \\
-    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
-    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
-    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
-    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
-   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\
-    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Corr. between cats, uncorr. between chns        \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
-    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns  \\
-    \hline
-    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
-    W & 2\% & 2\% & & &11\% &11\% & & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
-    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
-    W & 2\% & & 2 \% & &14\% & & 14\% & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
-    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
-    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
-    %W &  & &  & &12\% & 8\%& 22\% & 14\%& Fully uncorrelated \\
-    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
-    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
-    QCD & 4\% & 4\% & & & 60\% & 60\% & & &Fully uncorrelated \\
-    \hline
-\end{tabular}
-}
-\label{tab:SystematicUncertainties_mt}
-\end{center}
-\end{table}
-
-\begin{table}[!h]
-\begin{center}
-\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
-or background events in the $e \tau_{h}$ channel. Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
- {\scriptsize
- \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
-     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
-    \hline
-\textbf{ Process }
-    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
-     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
-    All from MC    & 6.2\%  & 6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
-    All from MC & 0--1\% & 0--1\% & 0--2\% & 0--1\%& 1--14\% & 0--12\% & 0--15\% & 0--15\% & Fully correlated \\
-    \hline
-    \multicolumn{10}{l}{\MET \textbf{scale}}\\
-    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
-    \multicolumn{10}{l}{\MET \textbf{resolution}} \\
-    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ          \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Electron identification and trigger} }\\
-    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
-    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
-    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
-    \hline
-    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
-    All from MC & 0--3\% & 0--3\% & 0--4\% & 0--4\% & 1--4\% & 0--2\% & 0--2\% & 0--2\% & Fully correlated\\
-    W &  &  &  &  & 5\% & 2\% & 10\% & 3\% & Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
-    All from MC & & & & & 0--3\% & & & & Fully correlated\\
-    \hline
-    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
-    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
-    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
-    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
-    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
-    \hline
-    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
-    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
-    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
-    \hline
-    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
-    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
-    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
-   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{ extrapolation} } \\
-    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
-    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
-    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
-    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
-   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\
-    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Corr. between cats, uncorr. between chns       \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
-    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns       \\
-    \hline
-    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
-    W & 2\% & 2\% & & &14\% &14\% & & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
-    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
-    W & 2\% & & 2 \% & &17\% & & 17\% & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
-    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
-    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
-    %W &  & &  & &11\% &14\% & 21\% & 16\%& Fully uncorrelated \\
-    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
-    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
-    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
-    QCD & 12\% & 12\% & & & 60\% & 60\% & & &Fully uncorrelated \\
-    \hline
-\end{tabular}
-}
-\label{tab:SystematicUncertainties_et}
-\end{center}
-\end{table}
-
-\begin{table}[!h]
-\begin{center}
-\caption{Systematic uncertainties that affect the estimated number of signal
-or background events in the $\tau_{h} \tau_{h}$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
-{\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
-     & \multicolumn{2}{|c}{Event yield uncertainty by event category} & \\
-    \hline
-    Process & No b-tag & B-tag & Correlation                   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
-    All from MC      & 6.2\%      & 6.2\%  & Fully correlated                           \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Jet energy scale}} \\
-    All from MC      & 0--4\%      & 0--9\%  & Fully correlated                    \\
-    \hline
-    \multicolumn{4}{l}{\MET \textbf{scale}} \\
-    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
-    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
-    \hline
-    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
-    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
-    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
-    \hline
-    \multicolumn{4}{l}{Tau-lepton identification and trigger} \\
-    ZTT,TTT,VVT, signal         & 10\%    & 10\%  & Fully correlated                      \\
-    ZTT,TTT,VVT, signal         & 9.2\%     & 9.2\%   & Correlated between categories, uncorrelated between channels \\
-    \hline
-    \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\
-    All from MC   & 0--4\%     & 0--11\%  & Fully correlated                  \\
-    \hline
-   \multicolumn{4}{l}{\textbf{B-mistag rate}} \\
-    All from MC    &  0--1\%    & 0--12\%  & Fully correlated                  \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Tau-lepton energy scale}} \\
-    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels                       \\
-    \hline
-    \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\
-    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{DY reweighting } } \\
-    ZTT       & shape      & shape & Fully correlated                       \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\
-    TTT,TTJ & shape & shape & Fully correlated                  \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production}}\\
-    ZL,ZJ       & 4\%      & 4\%  & Fully correlated                    \\
-    \hline
-    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation}}\\
-    ZTT         & 3\%        & 5\%  & Fully uncorrelated                   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
-    TTT,TTJ        & 6\%       & 6\%  & Fully correlated                       \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\
-    VVT,VVJ &  5\%        & 5\%       & Fully correlated                        \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\
-    ZL & 10\%     & 10\%       & Correlated between categories, uncorrelated between channels                        \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\
-    ZJ,W,TTJ & 20\%     & 20\%       & Correlated bewteen categories, uncorrelated between channels     \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (stat) }} \\
-    QCD  & 2\% & 20\%  & Fully uncorrelated\\
-    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (syst) }} \\
-    QCD  & 12\% & 14\%  & Fully uncorrelated\\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
-    W & 4\% & 4\% & Fully correlated \\
-\end{tabular}}
-\label{tab:SystematicUncertainties_tt}
-\end{center}
-\end{table}
-
-\begin{table}[!h]
-\begin{center}
-\caption{Systematic uncertainties that affect the estimated number of signal
-or background events in the $e\mu$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
-{\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
-     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
-    \hline
-    \textbf{Process}
-    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
-    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
-    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
-    \hline
-    \multicolumn{4}{l}{\MET \textbf{scale}} \\
-    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
-    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
-    \hline
-   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
-    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
-    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
-    \hline
-    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
-    All from MC       & 2\%        & 2\% & Fully correlated                              \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
-    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
-    \hline
-    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
-    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
-    \hline
-    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
-    All from MC      &     & 0--10\% & Fully correlated                    \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
-    ZTT,signal      & shape      & shape  & Fully correlated                \\
-    \hline
-    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
-     ZTT       & shape      & shape & Fully correlated                       \\
-   \hline
-    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
-    TT & shape & shape  & Fully correlated                 \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
-    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
-    \hline
-    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
-     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
-    TT        & 6\%       & 6\% & Fully correlated                        \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
-    VV        & 5\%       & 5\% & Fully correlated                       \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
-    QCD & 23\% & 34\% & Fully uncorrelated\\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
-    W+jets & 4\% & 4\% & Fully correlated\\
-\end{tabular}}
-\label{tab:SystematicUncertainties_em}
-\end{center}
-\end{table}
-
-\begin{table}[!h]
-\begin{center}
-\caption{Systematic uncertainties that affect the estimated number of
-or background events in the $Z\rightarrow\mu\mu$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
-{\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
-     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
-    \hline
-    \textbf{Process}
-    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
-    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
-    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
-    \hline
-    \multicolumn{4}{l}{\MET \textbf{scale}} \\
-    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
-    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
-    \hline
-   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
-    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
-    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
-    \hline
-    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
-    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
-    \hline
-    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
-    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
-    \hline
-    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
-    All from MC      &     & 0--10\% & Fully correlated                    \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
-    TT        & 6\%       & 6\% & Fully correlated                        \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
-    VV        & 5\%       & 5\% & Fully correlated                       \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
-    W+jets & 4\% & 4\% & Fully correlated\\
-\end{tabular}}
-\label{tab:SystematicUncertainties_zmm}
-\end{center}
-\end{table}

### 2016-12-27 MSSM/MSSM.tex
More selection...

@@
 
-\subsection{Pair selection and sorting}
-\label{sec:mssm_eventsel_pairs}
-The basis of the event selection is the selection of \mutau, \etau,
-\tautau and \emu pairs following the requirements described
-in the following subsections. After applying trigger
-requirements, identification criteria and kinematic cuts
-more than one possible candidate pair can exist. In this
-case the pair is chosen as follows:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
-electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
-and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
-object with raw MVA isolation value nearest to 1.
-\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
-\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
-candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
-and the $\Pgt_h$ for \etau and \mutau channels).
-\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
-\end{itemize}
-
-To prevent overlap with other channels, events are rejected
-if there are muons and electrons, other than those in the selected pair,
-with \pT $>10$ GeV and passing loose ID and isolation requirements.
-This also reduces backgrounds from \WZ events. 
-In addition to this, \Zee events are 
-reduced in the \etau channel by rejecting events
-where an opposite--sign pair of electrons of \pT $>15$ GeV
-and passing very loose ID and isolation requirements can be formed. 
-In the \mutau channel the contribution from \Zmm events
-is reduced in a similar fashion.
-
 \subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
@@
 to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
-required to be less than 0.2 cm.
+required to be less than 0.2 cm. Finally the hadronic tau is required
+to satisfy the very loose working point of the anti--electron discriminator
+and the tight working point of the anti--muon discriminator.
 
@@
 of the analysis for high mass points, while recovering some of the loss of loosening 
-tau isolation working point and \mT~cut. This is because when using \pT$>30$ GeV 
-fewer background events are selected.
+tau isolation working point and \mT~cut. The reason for this is that when using \pT$>30$ GeV 
+fewer background events are selected. The effect of the increased hadronic tau \pT~ cut on the 
+upper limits for the gg$\phi$ production process
+in figure \ref{fig:mssm_tauptcut}a, and on the bb$\phi$ production process
+in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the gg$\phi$ limits
+obtained by increasing the \pT~cut is sizeable, for bb$\phi$ events the effect is much
+less pronounced.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH.png}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH.png}}
+\end{center}
+\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channelfor (a) gg$\phi$ production and (b) bb$\phi$ production. The
+limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
+hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
+circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
+the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
+the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
+\label{fig:mssm_tauptcut}
+\end{figure}
 
@@
 \label{sec:mssm_eventsel_et}
+For selection of events in the \etau channel, the first step is
+a trigger that only requires an electron at \ac{L1}. At the \ac{HLT}
+loose identification and isolation criteria are then required.
+
+The offline event selection proceeds to require an oppositely charged
+electron and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
+The minimum \pT of the electron is required to be 26 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+This electron has to be consistent with having originated from the primary vertex, which
+is achieved by requiring impact parameters $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and it
+is required to pass additional identification criteria. A selection on the MVA identification, which
+selects electrons from \Zee events with 80\% efficiency, is used. In addition the
+electron needs to be isolated. The relative isolation, calculated with a cone size of 0.3, is required to be $< 0.1$.
+
+The hadronic tau is required to have a \pT greater than 30 GeV, $|\eta|<2.3$,
+and is required to be reconstructed by the HPS algorithm and to pass the medium
+working point of the MVA isolation discriminator. It also needs
+to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
+required to be less than 0.2 cm. Finally, the hadronic tau should
+pass the tight working point of the anti--electron discriminator
+and the loose working point of the anti--muon discriminator.
+
+Just like for muons, it was found that the analysis is not highly sensitive
+to the choice of electron isolation variable and selection, yet an effort
+is made not to use a suboptimal selection.
+A topological selection on the \mT~ variable is also made in this channel to reject \Wjets events. 
+The used value of $\mT < 50$ is obtained by performing a 2D optimisation where the \mT~ selection
+and hadronic tau isolation working point are varied at the same time. The same considerations as
+for the \mutau channel apply. The choice of the hadronic tau \pT~ selection to 30 GeV is
+chosen to recover some of the sensitivity lost at low mass by using looser \mT~ and hadronic
+tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH.png}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH.png}}
+\end{center}
+\caption{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
+limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
+hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
+circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
+the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
+the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
+\label{fig:mssm_tauptcut_et}
+\end{figure}
 
@@
 \label{sec:mssm_eventsel_tt}
+Selection of events in the \tautau channel starts with a trigger
+that requires two hadronic taus at \ac{L1}. At the level of the \ac{HLT}, loose identification
+and isolation criteria are applied to these hadronic taus.
+
+The offline event selection continues by requiring both hadronic taus to be oppositely charged, separated
+by $\Delta R > 0.5$, have pT~ of at least 40 GeV and $|\eta|<2.1$. Both taus need
+to pass decay mode finding and have originated from the primary vertex, with the impact parameter $d_{z} < 0.2$ cm. 
+Both taus need to pass the tight working point of the isolation discriminator, the very loose 
+working point of the anti--electron discriminator and the loose working point of the anti--muon discriminator. 
+The tight working point of the isolation discriminator is chosen to optimise the sensitivity
+of this channel for higher masses. INSERT PLOT
 
@@
 \label{sec:mssm_eventsel_em}
+Events in the \emu channel are first selected by a trigger
+that requires an electron and muon at \ac{L1} and applies loose ID and
+isolation requirements to these objects at \ac{HLT}.
 
-\subsection{Leptonvetos}
-\label{sec:mssm_eventsel_leptonvetos}
+\subsection{Pair selection and vetos}
+\label{sec:mssm_eventsel_pairs}
+The basis of the event selection is the selection of \mutau, \etau,
+\tautau and \emu pairs following the requirements described
+in the following subsections. After applying trigger
+requirements, identification criteria and kinematic cuts
+more than one possible candidate pair can exist. In this
+case the pair is chosen as follows:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
+electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
+and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
+object with raw MVA isolation value nearest to 1.
+\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
+\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
+candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
+and the $\Pgt_h$ for \etau and \mutau channels).
+\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
+\end{itemize}
+
+To prevent overlap with other channels, events are rejected
+if there are muons and electrons, other than those in the selected pair,
+with \pT $>10$ GeV and passing loose ID and isolation requirements.
+This also reduces backgrounds from \WZ events. 
+In addition to this, \Zee events are 
+reduced in the \etau channel by rejecting events
+where an opposite--sign pair of electrons of \pT $>15$ GeV
+and passing very loose ID and isolation requirements can be formed. 
+In the \mutau channel the contribution from \Zmm events
+is reduced in a similar fashion.
 
@@
 \label{sec:mssm_eventsel_categories}
+As the analysis targets both the gluon--gluon fusion
+and the b--associated production modes of MSSM Higgs
+bosons, two exclusive categories are defined based on the 
+number of b--tagged jets, where a jet is considered b--tagged
+if it passes the medium working point of the \ac{CSV}v2 discriminator. 
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal
+\item \textbf{b-tag}: At least 1 b--tagged jet and at most 1 
+jet with \pT$>30$ GeV. Due to the different phase space considered for
+b--tagging than for normal jet reconstruction this requirement does not necessarily
+mean there will be only one jet in the event. The requirement reduces the sizeable \ttbar
+background
+\end{itemize}
 
-NEED FIGURE OF NJETS AND NBJETS WITH SIGNAL ON!
+Figure \ref{fig:mssm_cats_tt}a shows the number of jets 
+in the \tautau channel, with \ref{fig:mssm_cats_tt}b showing
+the number of b--tagged jets in that channel. The gluon--gluon fusion
+signal and bb associated signal are overlaid on these distributions,
+thus indicating the signal--sensitive bins, motivating the choice of categories.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Number of jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
+\subfloat[Number of b--tagged jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
+\end{center}
+\caption{(a) Number of jets and (b) number of b--tagged jets in the \tautau channel. The gluon--gluon fusion signal (COLOUR)
+and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
+categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!
+\label{fig:mssm_cats_tt}
+\end{figure}
 

### 2016-12-28 MSSM/MSSM.tex
Adding more MSSM selection

@@
 is given in chapter \ref{chap:objects}.
+
+\subsection{Pair selection and vetos}
+\label{sec:mssm_eventsel_pairs}
+The basis of the event selection is the selection of \mutau, \etau,
+\tautau and \emu pairs following the requirements described
+in the following subsections. After applying trigger
+requirements, identification criteria and kinematic cuts
+more than one possible candidate pair can exist. In this
+case the pair is chosen as follows:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
+electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
+and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
+object with raw MVA isolation value nearest to 1.
+\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
+\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
+candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
+and the $\Pgt_h$ for \etau and \mutau channels).
+\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
+\end{itemize}
+
+To prevent overlap with other channels, events are rejected
+if there are muons and electrons, other than those in the selected pair,
+with \pT $>10$ GeV and passing loose ID and isolation requirements.
+This also reduces backgrounds from \WZ events. 
+In addition to this, \Zee events are 
+reduced in the \etau channel by rejecting events
+where an opposite--sign pair of electrons of \pT $>15$ GeV
+and passing very loose ID and isolation requirements can be formed. 
+In the \mutau channel the contribution from \Zmm events
+is reduced in a similar fashion.
 
@@
 \label{sec:mssm_eventsel_em}
-Events in the \emu channel are first selected by a trigger
-that requires an electron and muon at \ac{L1} and applies loose ID and
-isolation requirements to these objects at \ac{HLT}.
+Events in the \emu channel are first selected by two triggers
+that both require an electron and muon at \ac{L1} and apply loose ID and
+isolation requirements to these objects at \ac{HLT}. The \pT requirements on
+the electron and muon are different in the two triggers, thus using the combination of the two
+improves the analysis performance.
 
-\subsection{Pair selection and vetos}
-\label{sec:mssm_eventsel_pairs}
-The basis of the event selection is the selection of \mutau, \etau,
-\tautau and \emu pairs following the requirements described
-in the following subsections. After applying trigger
-requirements, identification criteria and kinematic cuts
-more than one possible candidate pair can exist. In this
-case the pair is chosen as follows:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
-electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
-and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
-object with raw MVA isolation value nearest to 1.
-\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
-\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
-candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
-and the $\Pgt_h$ for \etau and \mutau channels).
-\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
-\end{itemize}
+The offline requirements to the \emu pair are that the electron 
+and muon are oppositely charged, separated by $\Delta R >$ 0.3. The 
+electron should have a minimum \pT~ of 13 GeV and have $|\eta|< 2.5$. As
+in the \etau channel the electron's impact parameters have to 
+satisfy $d_{xy} < 0.045$ cm and $d_{z}<0.2$ cm. A selection is
+made on the electron identification MVA, using a working point that 
+is 80\% efficient for electrons in \Zee decays. The electron
+also needs to be isolated, with the relative isolation calculated
+with a cone size of 0.3 being less than $<0.15$.
 
-To prevent overlap with other channels, events are rejected
-if there are muons and electrons, other than those in the selected pair,
-with \pT $>10$ GeV and passing loose ID and isolation requirements.
-This also reduces backgrounds from \WZ events. 
-In addition to this, \Zee events are 
-reduced in the \etau channel by rejecting events
-where an opposite--sign pair of electrons of \pT $>15$ GeV
-and passing very loose ID and isolation requirements can be formed. 
-In the \mutau channel the contribution from \Zmm events
-is reduced in a similar fashion.
+The muons need to have a \pT~of at least 10 GeV, $|\eta|<2.4$ and 
+their impact parameters need to be $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm.
+In addition to the kinematic requirements the muon must
+pass the medium identification criteria and be isolated with the relative
+isolation, calculated with a cone size of 0.4, required to be less than 0.15.
+
+Because a combination of triggers is used, the object firing
+the higher \pT~ trigger leg needs to have a transverse momentum
+of at least 24 GeV on top of the requirements already discussed.
+In addition, a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
+\begin{align}\label{eqn:mssm_em_dzeta}
+D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
+\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{vis}} + \vec{p}_{\text{T},2}^{\text{vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
+\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{vis}}+\vec{p}_{\text{T},2}^{\text{vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
+\end{align}
+
+Thus $D_{\zeta}$ is the difference of the projection of the visible tau decay products plus missing energy \pT+\MET,
+and simply the visible tau decay product \pT on the axis $\vec{\zeta}$. This is the axis that bisects 
+the directions $\vec{p}_{\text{T,1}}^{\text{vis}}$ and $\vec{p}_{\text{T,2}}^{\text{vis}}$
+of the visible decay products in the transverse plane. This selection is illustrated in figure
+\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
+for \emu events. The used cut value, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
+events.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Reconstruction of $D_{\zeta}$]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
+\subfloat[$D_{\zeta}$ distribution in \emu channel]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
+\end{center}
+\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
+\emu channel\cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_dzeta}
+\end{figure}
 
@@
 \label{sec:mssm_discrvar}
+The discriminating variable used for signal extraction is the total transverse mass,
+\begin{equation}\label{eqn:mttot}
+m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
+(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}.
+\end{equation}
+
+$m_{\text{T}}(1,2)$ is defined as,
+\begin{equation}\label{eqn:mttot_12}
+m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}.
+\end{equation}
+
+This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
+to the \mT~ defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
+The \mTtot~ variable provides good separation between signal and QCD multi--jet events
+in the \etau, \mutau and \tautau channels, and between
+signal and \ttbar events in the \emu channel.
 
@@
 \label{sec:mssm_bkgs}
+The methods used for background estimation will be described in this
+channel. The background estimation in the \etau and \mutau channels
+is very similar and they are combined
 
@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}
+\end{center}
+\caption{Exclusion in the $m_{h}^{\text{mod}+}$ scenario obtained by the combination
+of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
+solid black line is the observed exclusion, with the dashed black line the
+expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
+expected exclusion. The red shaded area
+is excluded by the lack of a light Higgs boson with mass compatible with 125 GeV \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_mhmodp_2016}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}
+\end{center}
+\caption{Exclusion in the hMSSM scenario obtained by the combination
+of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
+solid black line is the observed exclusion, with the dashed black line the
+expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
+expected exclusion \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_hmssm_2016}
+\end{figure}
+
 \section{Combination of 2015 and 2016 datasets}

### 2016-12-28 MSSM/UncOv.tex
Adding more MSSM selection

\section{Overview of uncertainties}
\label{sec:mssm_uncs_overview}
The systematics that are applied are summarised in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}.

\begin{table}[!h]
\begin{center}
\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
or background events in the $\mu \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
 {\scriptsize
 \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
    \hline
\textbf{ Process }
    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
    \hline
    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
    All from MC    & 6.2\%  &6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
    All from MC & 0--1\% & 0--2\% & 0--1\% & 0--1\%& 0--12\% & 3--11\% & 0--15\% & 0--14\% & Fully correlated \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{scale} }\\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ, VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ,VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\textbf{Muon identification and trigger} }\\
    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
    \hline
    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
    All from MC & 0--3\% & 0--3\% & 0--3\% & 0--2\% & 1--3\% &  0--3\%& 0--3\% & 0--3\%& Fully correlated\\
    W &  &  &  &  & 4\% & 4\% & 6\% & 6\%& Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
    All from MC & & & & & 1--7\% & & & & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
    \hline
    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt$\textbf{: $Z\to\Pgt\Pgt / Z\to\Pgm\Pgm$ extrapolation } } \\
    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\
    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Corr. between cats, uncorr. between chns        \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns  \\
    \hline
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
    W & 2\% & 2\% & & &11\% &11\% & & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
    W & 2\% & & 2 \% & &14\% & & 14\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
    %W &  & &  & &12\% & 8\%& 22\% & 14\%& Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
    QCD & 4\% & 4\% & & & 60\% & 60\% & & &Fully uncorrelated \\
    \hline
\end{tabular}
}
\label{tab:SystematicUncertainties_mt}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
or background events in the $e \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
 {\scriptsize
 \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
     & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
    \hline
\textbf{ Process }
    & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
    \hline
    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
    All from MC    & 6.2\%  & 6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
    All from MC & 0--1\% & 0--1\% & 0--2\% & 0--1\%& 1--14\% & 0--12\% & 0--15\% & 0--15\% & Fully correlated \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{scale}}\\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ                         \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ          \\
    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
    \hline
    \multicolumn{10}{l}{\textbf{Electron identification and trigger} }\\
    All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
    ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
    \hline
    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
    All from MC & 0--3\% & 0--3\% & 0--4\% & 0--4\% & 1--4\% & 0--2\% & 0--2\% & 0--2\% & Fully correlated\\
    W &  &  &  &  & 5\% & 2\% & 10\% & 3\% & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
    All from MC & & & & & 0--3\% & & & & Fully correlated\\
    \hline
    \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline
    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
    TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
    \hline
    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
    ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
    W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
    \hline
    \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZL,ZJ       & 4\% & 4\% & 4\% & 4\% & 4\%  & 4\% & 4\% & 4\% & Fully correlated              \\
    ZTT         &  & 4\% & 4\% & 4\% &  & 4\% & 4\% & 4\% & Fully correlated              \\
   \multicolumn{10}{l}{ $Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{ extrapolation} } \\
    ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
    TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
    VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\
    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Corr. between cats, uncorr. between chns       \\
    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns       \\
    \hline
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
    W & 2\% & 2\% & & &14\% &14\% & & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W OS/SS ratio (syst) } }\\
    W & 8\% & 8\% & & &10\% &10\% & & &Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (stat)}}\\
    W & 2\% & & 2 \% & &17\% & & 17\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{W low/high} $m_{T}$ \textbf{ratio (syst)} }\\
    W & 20\% & &20\% & & 20\% & & 20\% & & Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (stat)}}\\
    %W &  & &  & &11\% &14\% & 21\% & 16\%& Fully uncorrelated \\
    %\multicolumn{10}{l}{\textbf{W b-tag extrap (syst)} }\\
    %W &  & & & & 10\% & & 10\% & & Fully uncorrelated \\
    \multicolumn{10}{l}{\textbf{QCD OS/SS ratio (syst) }}\\
    QCD & 12\% & 12\% & & & 60\% & 60\% & & &Fully uncorrelated \\
    \hline
\end{tabular}
}
\label{tab:SystematicUncertainties_et}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the $\tau_{h} \tau_{h}$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} & \\
    \hline
    Process & No b-tag & B-tag & Correlation                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\%  & Fully correlated                           \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}} \\
    All from MC      & 0--4\%      & 0--9\%  & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
    ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
    \hline
    \multicolumn{4}{l}{Tau-lepton identification and trigger} \\
    ZTT,TTT,VVT, signal         & 10\%    & 10\%  & Fully correlated                      \\
    ZTT,TTT,VVT, signal         & 9.2\%     & 9.2\%   & Correlated between categories, uncorrelated between channels \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\
    All from MC   & 0--4\%     & 0--11\%  & Fully correlated                  \\
    \hline
   \multicolumn{4}{l}{\textbf{B-mistag rate}} \\
    All from MC    &  0--1\%    & 0--12\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{Tau-lepton energy scale}} \\
    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels                       \\
    \hline
    \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\
    ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels   \\
    \hline
    \multicolumn{4}{l}{\textbf{DY reweighting } } \\
    ZTT       & shape      & shape & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\
    TTT,TTJ & shape & shape & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production}}\\
    ZL,ZJ       & 4\%      & 4\%  & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation}}\\
    ZTT         & 3\%        & 5\%  & Fully uncorrelated                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TTT,TTJ        & 6\%       & 6\%  & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\
    VVT,VVJ &  5\%        & 5\%       & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\
    ZL & 10\%     & 10\%       & Correlated between categories, uncorrelated between channels                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\
    ZJ,W,TTJ & 20\%     & 20\%       & Correlated bewteen categories, uncorrelated between channels     \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (stat) }} \\
    QCD  & 2\% & 20\%  & Fully uncorrelated\\
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (syst) }} \\
    QCD  & 12\% & 14\%  & Fully uncorrelated\\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W & 4\% & 4\% & Fully correlated \\
\end{tabular}}
\label{tab:SystematicUncertainties_tt}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the $e\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \hline
    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \hline
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \hline
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}

### 2017-01-08 MSSM/MSSM.tex
Adding more MSSM text

@@
 \begin{center}
-\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160.0_range12.pdf}}
-\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900.0_range12.pdf}}~\\
-\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600.0_range12.pdf}}
-\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900.0_range12.pdf}}
+\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
+\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900_range12.pdf}}~\\
+\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
+\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
 \end{center}
@@
 s a function of tau isolation working point (from very loose to very very tight) and
-of \mT~ cut from \mT$<20$ GeV to \mt$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+of \mT~ cut from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
 for $m_{\phi}$ = 160 GeV (a), 900 GeV (b), 1600 GeV (c) and 2900 GeV (d). The most optimal combination of \mT~selection and 
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH.png}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH.png}}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
 \end{center}
-\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channelfor (a) gg$\phi$ production and (b) bb$\phi$ production. The
-limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
-hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
+\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
+limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
+hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
 circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
 the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
-the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
+the effect on the bb$\phi$ production process is less pronounced.}
 \label{fig:mssm_tauptcut}
@@
 A topological selection on the \mT~ variable is also made in this channel to reject \Wjets events. 
-The used value of $\mT < 50$ is obtained by performing a 2D optimisation where the \mT~ selection
+The used value of \mT $< 50$ is obtained by performing a 2D optimisation where the \mT~ selection
 and hadronic tau isolation working point are varied at the same time. The same considerations as
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH.png}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH.png}}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
 \end{center}
@@
 limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
-hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
+hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
 circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
 the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
-the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
+the effect on the bb$\phi$ production process is less pronounced.}
 \label{fig:mssm_tauptcut_et}
@@
 events. 
+%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
+%as the neutrinos and visible tau decay products travel at small angles from the original tau.
 
@@
 \begin{center}
-\subfloat[Reconstruction of $D_{\zeta}$]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
-\subfloat[$D_{\zeta}$ distribution in \emu channel]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
+\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
+\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
 \end{center}
@@
 \begin{center}
-\subfloat[Number of jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
-\subfloat[Number of b--tagged jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
+\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
+\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
 \end{center}
@@
 and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
-categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!
+categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!}
 \label{fig:mssm_cats_tt}
@@
 \label{sec:mssm_mccorrs}
+\subsubsection*{Tracking efficiency}
+\subsubsection*{Electron, muon and tau ID and isolation}
+\subsubsection*{Trigger efficiency}
+\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
+\subsubsection*{\MET recoil corrections}
+\subsubsection*{Top-quark \pT reweighting}
+\subsubsection*{Drell-Yan shape reweighting}
 
@@
 The methods used for background estimation will be described in this
-channel. The background estimation in the \etau and \mutau channels
-is very similar and they are combined
+section. As the \mutau and \etau channels use very similar
+background methods, they are described in the same subsection.
 
-\subsection{\texorpdfstring{\mutau and \etau channels}{mutau and etau channels}}
-\label{sec:mssm_bkgs_mtet}
+\subsection{Generator matching}
+\label{sec:mssm_bkgs_genmatch}
+For backgrounds estimated from \ac{MC} there are often 
+different sub--processes playing a role that should be
+treated separately by the fit. Taking the \mutau 
+channel as an example, a sample of Drell--Yan events
+will contain \Ztautau events, where one of the taus decays
+hadronically and the other tau decays to a muon, but also
+\Zmm events where one of the muons fakes a tau, or with an 
+additional jet in the event faking a hadronic tau and one of the
+muons not being properly reconstructed. Similarly, \ttbar background
+events can be split into those with genuine taus, and those
+where a jet mimics a hadronic tau.
 
-\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
-\label{sec:mssm_bkgs_mtet_ztt}
+Dividing events from the same production
+process into sub--samples
+based on generator level information allows
+for a more correct treatment of systematic uncertainties.
 
-\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
-\label{sec:mssm_bkgs_mtet_wjets}
+To determine the generator-level particle
+that a reconstructed electron, muon, or hadronic tau
+originates from, reconstructed objects are matched
+to a set of generator level objects within a cone of $\Delta R = 0.2$.
+Five categories of generator-level object are considered for matching:
+prompt electrons and muons,
+that is electrons and muons not originating from a decay; electrons and muons
+from tau decays; and generator-level hadronic taus. These generator-level
+hadronic taus are rebuilt by summing the four--momenta
+of the visible decay products of the generator-level tau.
 
-\subsubsection{QCD}
-\label{sec:mssm_bkgs_mtet_qcd}
+All of these particles are looked for in a cone of $\Delta R = 0.2$ around
+the reconstructed object, and if there are multiple generator-level
+particles within this cone the one nearest the reconstructed particle
+is chosen as the object this particle is matched to. If there are no 
+generator-level particles in the cone at all it is said to 
+have originated from pile--up or a jet at generator level.
 
-\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
-\label{sec:mssm_bkgs_mtet_tt}
+The generator--level object type matched to a 
+reconstructed particle is used to perform the splitting
+of background samples, and is indicated where this is used.
 
-\subsubsection{Other backgrounds}
-\label{sec:mssm_bkgs_mtet_other}
+\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
+\label{sec:mssm_bkgs_ztt}
+For all channels, both shape and normalisation of the \Ztautau background 
+is estimated from the Drell-Yan
+\ac{MC} samples described in section \ref{sec:mssm_datasets}.
+For the \mutau and \etau channels, events from these samples 
+in which the reconstructed hadronic tau is matched to 
+a generator-level hadronic tau are considered part of the \Ztautau
+background. In the \tautau channel both reconstructed
+hadronic taus are required to be matched to a generator-level hadronic tau, and
+in the \emu channel the \Ztautau component of the Drell-Yan background 
+is taken as those events where the reconstructed electron is not matched to
+a prompt electron at generator level and the reconstructed
+muon is not matched to a prompt muon. 
+Events in the Drell-Yan samples selected in the event selection
+but not satisfying the generator matching requirements are considered
+as the, much smaller, \Zll background.
 
-\subsection{\texorpdfstring{\tautau channel}{tautau channel}}
+To correct and constrain the \Ztautau normalisation in the
+b-tag and no b-tag categories of all channels, \Zmm control
+regions are simultaneously fitted. More detail is given in 
+section \ref{sec:mssm_sigext_ctrl}.
+
+\subsection{\texorpdfstring{\Wjets and QCD in the \etau and \mutau channels}{W+jets and QCD in the e tau and mu tau channels}}
+\label{sec:mssm_bkgs_mtet_wjetsqcd}
+A data--driven approach is used for the estimation of
+both the \Wjets and QCD backgrounds in the \etau and \mutau channels. 
+The estimates of the normalisations of the two backgrounds are tied
+together due to the presence of some QCD contamination in the \Wjets--dominated
+control region. The shape of the \Wjets background is taken
+from the \ac{MC} samples, with the QCD shape taken from same--sign
+data with other backgrounds subtracted.
+
+\subsubsection{\texorpdfstring{\Wjets normalisation}{W+jets normalisation}}
+\label{sec:mssm_bkgs_mtet_wjetsnorm}
+The \Wjets normalisation is derived using a high-\mT~ control region, where
+selected events are required to satisfy \mT$>70$ GeV. In the no b-tag
+category the \Wjets
+contribution in this region is enhanced, however there is still
+some contribution from QCD events in this region. Therefore we
+have, for \mT$>70$ GeV:
+
+\begin{equation}\label{eqn:wjets_ss_norm}
+\begin{split}
+N_{\text{data}}^{SS, \text{high } m_{\text{T}}} - N_{\text{other}}^{SS,
+\text{high } m_{\text{T}}} & =
+N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} + N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
+N_{\text{data}}^{OS, \text{high } m_{\text{T}}} - N_{\text{other}}^{OS,
+\text{high } m_{\text{T}}} & = N_{\text{QCD}}^{OS, \text{high } m_{\text{T}}} +
+N_{W}^{OS, \text{high } m_{\text{T}}} \\
+& = R_{\text{QCD}}^{OS/SS}\cdot N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} +
+R_{W}^{OS/SS} \cdot N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
+\Rightarrow N_{W}^{SS, \text{high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{OS,
+\text{high } m_{\text{T}}}  - N_{\text{other}}^{OS, \text{high } m_{\text{T}}}  -
+R_{\text{QCD}}^{OS/SS}\cdot(N_{\text{data}}^{SS, \text{high } m_{\text{T}}}  -
+N_{\text{other}}^{SS, \text{high } m_{\text{T}}} )}{R_{W}^{OS/SS} -
+R_{\text{QCD}}^{OS/SS}} ,
+\end{split}
+\end{equation}
+
+where $R_{W}^{OS/SS}$ is the ratio between opposite-sign and same-sign \Wjets events
+and $R_{QCD}^{OS/SS}$ the ratio between opposite-sign and same-sign QCD events. Using 
+equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
+opposite-sign, high \mT~region is given by $R_{W}^{OS/SS}\cdot N_{W}^{SS,\text{high} m_{T}}$. 
+This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:
+
+\begin{equation}\label{eqn:wjets_os_norm}
+N_{W}^{OS,\text{low} m_{T}} = \frac{N_{W,MC}^{OS,\text{low} m_{T}}}{N_{W,MC}^{OS,\text{high} m_{T}}}\cdot R_{W}^{OS/SS} \cdot N_W^{SS,\text{high }m_{T}},
+\end{equation}
+
+which is the estimate of the number of \Wjets events in the opposite-sign, high \mT, region
+multiplied by the ratio of the number of \ac{MC} events in the opposite-sign, low \mT~ region to the number of \ac{MC} events in the opposite-sign, high \mT~region. This means that
+the \ac{MC} samples are used to derive a high \mT-to-low \mT extrapolation factor.
+
+The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
+$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
+The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
+control region in data; this is described in section ADD REF. $R_{W}^{OS/SS}$ is 
+taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
+is close to 1.
+
+The method described so far works well in the no b-tag categories, but in the b-tag category
+the \ttbar background dominates. For this reason the estimate of the number
+of \Wjets events in this category is made with a relaxed category selection where the b-tagging
+requirement itself is removed, but the jet requirements still stand. Events with at least one 
+jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
+region is determined by the estimate given by the number of \Wjets events
+estimated in the 1-jet selection, multiplied by an extrapolation factor 
+$\frac{N_{W,MC}^{OS,\text{low } m_{T},\text{b-tag category}}}{N_{W,MC}^{OS,\text{low }m_{\text{T}},\text{1-jet selection}}}$ ADD FIGURES
+
+\subsubsection{QCD OS/SS ratio}
+\label{sec:mssm_bkgs_etmt_qcdosss}
+Studies of QCD OS/SS ratio go here
+
+\subsubsection{QCD normalisation}
+\label{sec:mssm_bkgs_etmt_qcdnorm}
+The QCD normalisation is estimated by inverting the opposite-sign requirement
+of the di-tau pair in the signal region. The yield is taken from the same--sign
+region with otherwise identical cuts to the opposite--sign region. The contributions
+from other backgrounds in this region are subtracted to give an estimate of the number
+of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
+yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
+expected in this region is given by
+\begin{equation}\label{eqn:wjets_qcdsub}
+N_{W,SS SR} = \frac{N_{MC,SS SR}}{N_{MC,SS high mT}}N_{W,SS high mT}
+\end{equation}
+
+Because opposite--sign and same--sign QCD events do not
+necessarily appear in equal amounts the number of QCD
+events obtained by subtracting other backgrounds from the
+observed number of events in the same--sign region is multiplied
+by $R_{QCD}^{OS/SS}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
+to obtain an estimate of the number of QCD events in the signal region.
+
+\subsubsection{Control regions in the fit}
+\label{sec:mssm_bkgs_etmt_ctrl}
+Several control regions in data are used for the estimation
+of the QCD and \Wjets backgrounds: the same--sign and 
+opposite--sign high \mT~ regions, as well as the same--sign
+low \mT~region. This leads to three control regions used 
+in each category of both the \mutau and \etau channels to determine
+the initial estimate of the background normalisations.
+These control regions are included in a simultaneous fit
+with the signal regions to obtain the final results.
+
+\subsection{QCD}
+\label{sec:mssm_bkgs_qcd}
+This section describes the QCD background
+estimation in the \tautau and \emu channels.
+
+\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
+\label{sec:mssm_bkgs_qcd_tt}
+In the \tautau channel the QCD background is by far the 
+dominant background. The normalisation and shape 
+of this background are estimated from a sideband with loosened 
+isolation requirements with respect to the signal region. 
+In the no b-tag category the sideband used is determined
+by having the tau with highest \pT~ pass the tight working
+point of the tau ID discriminator, as in the nominal selection.
+The other hadronic tau in the pair does not pass the tight working point,
+but does pass the medium working point. This sideband is 
+chosen as it is as close to the signal region as possible, and 
+this should minimise biases in the shape of the total transverse mass
+distribution. Other backgrounds
+in this sideband are subtracted from the observation to give
+the QCD estimate. Differences in normalisation due to
+the use of a loosened sideband are corrected for by loose-to-tight isolation
+scale factor. This correction factor is measured as
+\begin{equation}\label{eqn:tautau_qcd}
+R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{obs}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{obs}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
+\end{equation}
+
+So this takes the ratio between the observed data with other
+backgrounds subtracted in the region equivalent to the signal region, but with the
+charge requirement of the pair inverted, and the region equivalent to the sideband
+with loosened isolation but with the charge requirement on the pair inverted.
+
+An analogous method is used for this estimate in the 
+b-tag category, however, the sideband as used for the 
+no b-tag category does not contain enough events to 
+provide a background estimate. Therefore a sideband where
+the highest \pT~tau passes the tight working point of the
+tau ID discriminator, and the other tau passes the loose working
+point of the discriminator, but not the tight working point, is used.
+This sideband is slightly further away from the signal region than the
+'tight--medium' sideband INSERT FIGURE. The bias from using this looser
+sideband has been assessed and has a less than 1$\sigma$ effect.
+FIXME THIS ISN'T VERY USEFUL INFO!
+
+\subsubsection{\texorpdfstring{\emu channel}{e mu channel}}
+\label{sec:mssm_bkgs_qcd_em}
+In the \emu channel the QCD multijet background
+is estimated by inverting the charge requirement
+of the pair, considering the same--sign region
+with otherwise identical cuts to the signal region.
+Other backgrounds present in this region are subtracted.
+As for the \etau and \mutau channels, the number of
+QCD events with opposite--sign \emu pairs is not
+necessarily equal to the number of QCD events
+with same--sign \emu pairs and therefore the ratio
+of opposite--sign to same--sign pairs is measured by inverting
+the isolation requirements on the electron or muon. Both
+leptons need to satisfy $I_{\text{rel}} < 0.4$ and at 
+least one of them needs to fail the nominal isolation requirement.
+The opposite--sign to same--sign ratio is parameterised in terms
+of lepton kinematics and the separation in $\Delta R$ between the
+two leptons. These ratios are then applied to the same--sign region
+QCD estimate to give a QCD estimate in the signal region. 
+Because the opposite--sign to same--sign ratios are measured
+before applying the categorisation, and \ac{MC} studies suggest
+that the opposite--sign to same--sign ratio is different in the b-tag
+category than in the no b-tag category, an extra scale factor of 
+1.45/2.20 is applied to the QCD estimate in this category.
+
+\subsection{\texorpdfstring{\ttbar}{ttbar}}
 \label{sec:mssm_bkgs_tt}
+The \ttbar shape and normalisation are estimated from \ac{MC} 
+samples and are checked against data in a control
+region with a \ttbar purity of 91\%. This control region
+is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
+the \emu channel. INSERT PLOT
+In the \mutau, \etau and \tautau channels
+the \ttbar contribution is split into
+two components, one with real taus and 
+one without. The component with real taus is composed
+of \ttbar events in which the hadronic tau is matched
+to a generator level tau. In the fully hadronic channel
+both taus need to be generator matched to a hadronically
+decaying tau.
 
-\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
-\label{sec:mssm_bkgs_tt_ztt}
-
-\subsubsection{QCD}
-\label{sec:mssm_bkgs_tt_qcd}
-
-\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
-\label{sec:mssm_bkgs_tt_wjets}
-
-\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
-\label{sec:mssm_bkgs_tt_tt}
-
-\subsubsection{Other backgrounds}
-\label{sec:mssm_bkgs_tt_other}
-
-\subsection{\texorpdfstring{\emu channel}{emu channel}}
-\label{sec:mssm_bkgs_em}
-
-\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
-\label{sec:mssm_bkgs_em_ztt}
-
-\subsubsection{QCD}
-\label{sec:mssm_bkgs_em_qcd}
-
-\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
-\label{sec:mssm_bkgs_em_wjets}
-
-\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
-\label{sec:mssm_bkgs_em_tt}
-
-\subsubsection{Other backgrounds}
-\label{sec:mssm_bkgs_em_other}
+\subsection{Other backgrounds}
+\label{sec:mssm_bkgs_other}
+For all channels the di--boson plus 
+single--top background is small.
+Both normalisation and shape are estimated from \ac{MC}
+samples. For the \etau, \mutau and \tautau channels
+this background contribution is split into a component
+where the hadronically decaying tau originates from a real
+tau, and one where it does not. This is done in a similar
+way as for the \ttbar background
+In the \tautau and \emu channels the \Wjets background
+is less important than in the \etau and \mutau channels, and both
+its shape and normalisation are estimated from the
+\ac{MC} samples.
 
@@
 \label{sec:mssm_uncs}
+Just like for the analysis presented in chapter \ref{chap:hhh}
+two types of systematic uncertainty are considered. Normalisation
+uncertainties only affect the yield of a process while shape
+uncertainties affect both the process normalisation, as well as the shape
+of the \mTtot~ distribution. The uncertainties are taken into account 
+in the final result as described in section \ref{sec:hhh_results_extraction}.
 
@@
 \label{sec:mssm_uncs_norm}
+\subsubsection*{Luminosity uncertainty}
+The uncertainty on the luminosity measurement amounts to 6.2\% for
+data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
+applied to all processes for which the normalisation was estimated 
+using \ac{MC} samples.
+\subsubsection*{Identification, isolation and trigger efficiencies}
+\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
+\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
+\subsubsection*{Jet energy scale uncertainty}
+\subsubsection*{B-tag scale factors}
+\subsubsection*{\MET resolution and response}
+\subsubsection*{Background normalisation}
+\subsubsection*{Theory uncertainties}
 
@@
 \label{sec:mssm_uncs_shape}
+\subsubsection*{$\Pgt_{h}$ energy scale}
+\subsubsection*{Electron energy scale}
+\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
+\subsubsection*{Top quark \pT~ reweighting}
+\subsubsection*{Drell-Yan shape reweighting}
+\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
 

### 2017-01-08 MSSM/MSSM.tex
Adding more figs + some words on systematic uncertainties

@@
 data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
-applied to all processes for which the normalisation was estimated 
+applied to all processes for which the normalisation is estimated 
 using \ac{MC} samples.
 \subsubsection*{Identification, isolation and trigger efficiencies}
+The uncertainty on electron and muon identification, isolation, and
+trigger efficiency amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
+isolation uncertainty amounts to 6\% in the \etau and \mutau channels
+and 12\% in the \tautau channel, with an additional 7\% uncertainty
+on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
+uncertainty is split between a part that is correlated between the channels, 
+a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
+part amounts to 3\% (9.2\%) for the \etau and \mutau (\tautau) channels.
+The uncertainties on lepton/hadronic tau identificiation, isolation and 
+trigger efficiency are applied to all processes for which the normalisation
+is estimated using \ac{MC} samples.
 \subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
+The uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate
+is 20\% \cite{cms-tau-2015}. This uncertainty is applied
+to those backgrounds where the normalisation is estimated from \ac{MC} and
+where the hadronic taus are mimicked by jets, that is the \Zellell background
+with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
+channel, and the \ttbar background with a jet faking a hadronic tau. 
 \subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
+The $\Pe\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 10-30\%,
+depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
+applied to the \Zellell background with the hadronic tau faked by an electron.
+The $\Pgm\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 20-30\%, depending
+on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
+background with the hadronic tau faked by a muon.
 \subsubsection*{Jet energy scale uncertainty}
+The uncertainties on the jet-energy corrections are applied
+by shifting the jet energy up and down by the \pT~ and $\eta$ dependendent
+uncertainty, and evaluating the the change in process normalisation in
+each category. Where the change in normalisation is non-negligible the
+uncertainty is applied. It ranges from 1--10\% depending on process and category.
 \subsubsection*{B-tag scale factors}
+Uncertainties on the b-tagging efficiency and light jet mis-tagging
+rates are given as a function of jet \pT~ and $\eta$ for the 
+medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
+The b-tagging scale factors are are varied within these uncertainties
+and the overall change in normalisation for each process in each category is
+evaluated. If the change in normalisation is non-negligible this
+uncertainty is applied. The uncertainty varies from 1--5\%.
 \subsubsection*{\MET resolution and response}
@@
 \label{sec:mssm_results_modelindep}
+The \mTtot~ distributions in the no b-tag and b-tag
+categories of all channels, after the fit to the observed
+data has been performed, are shown in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em}.
+The signal of the 3 neutral Higgs bosons at \mA=1 TeV and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid 
+on the total transverse mass distributions. The signal peaks twice due to the presence of a light Higgs boson
+with mass compatible with 125 GeV in this model, which is necessary to incorporate the Higgs boson
+observed at 125 GeV into the model.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
+\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
+\end{center}
+\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+of the \mutau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
+and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid. Note that, to incorporate
+the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_mt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
+\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
+\end{center}
+\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+of the \etau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
+and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_et}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
+\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
+\end{center}
+\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
+and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_tt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
+\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
+\end{center}
+\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
+and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_em}
+\end{figure}
+
+None of these distributions show hints of a significant excess. The
+95\% upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
+for gluon--gluon fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
+production. All channels and categories are combined. 
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
+\end{center}
+\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+process and (b) the b--associated production process. All four final states and 
+all categories are combined for these limits \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_limits}
+\end{figure}
+
+A comparison of the expected limits
+per channel is shown in figure \ref{fig:mssm_results_limits_breakdown}a for gg$\phi$ production
+and in figure \ref{fig:mssm_results_limits_breakdown}b for bb$\phi$ production.
+These figures show that the \mutau channel is the most sensitive at masses up to 
+200 GeV, beyond which the \tautau channel becomes more sensitive. The \etau
+channel is always slightly less sensitivie than the \mutau channel. The \emu channel
+is the least sensitive over a large part of the parameter space, until it overtakes the 
+\etau channel in sensitivity at 1.6 TeV and is slightly more sensitive than the
+\mutau channel at 3.2 TeV. The \emu channel becomes more sensitive at higher masses as
+a narrower binning of the \mTtot~ distribution is possible than for the other channels.
+The \mTtot~ distribution for the high mass signals is therefore wide enough not to
+fall entirely into the last bin used for the fit. This means at high mass this channel
+benefits more from the shape discrimination between signal and backgrounds than
+the other channels.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-a.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-b.pdf}}
+\end{center}
+\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
+comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
+and \emu (gold) channels \cite{CMS-PAS-HIG-16-037}. For masses below 200 GeV the \mutau channel is the most sensitive,
+while the \tautau channel dominates for higher masses. The \etau channel is always
+slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
+until at around 1.6 TeV it starts to overtake the \etau channel, with the sensitivity at 3.2 TeV 
+being similar or slightly better than the \mutau channel. FIXME REMAKE PLOT?}
+\label{fig:mssm_results_limits_breakdown}
+\end{figure}
+
+\subsection{2D likelihood scans}
+\label{sec:mssm_results_2D}
 
@@
 \label{sec:mssm_results_modeldep}
+The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
+scenario and the hMSSM scenario. Both scenarios are described in chapter THEORY.
+
+Figure \ref{fig:mssm_mhmodp_2016} shows the expected (dashed line and grey bands) and
+observed (blue shaded area bounded by solid line) exclusion of the search presented in this chapter
+in the \mA-\tanb~ plane of the $m_{\text{h}}^{\text{mod+}}$ scenario. The red shaded band
+indicates the area that is excluded due to the lack of a light Higgs boson with a mass compatible
+with 125 GeV. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
+limits at high \tanb~ have improved by around 300 GeV.
 
@@
 \end{figure}
+
+Figure \ref{fig:mssm_hmssm_2016} shows the expected (dashed line and grey bands)
+and observed (blue shaded area bounded by solid line) exclusion of the search
+presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
+MENTION FEATURE
 

### 2017-01-08 MSSM/MSSM.tex
Some more uncertainty work

@@
 \subsubsection*{\MET resolution and response}
+Uncertainties on \MET resolution and response are estimated
+by varying the recoil correction paramters within their
+uncertainty and evaluating the effect on process
+normalisations. The uncertainty amounts to around 2\%
 \subsubsection*{Background normalisation}
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item \Ztautau: As the \Zmm control region is included in the simultaneous
+fit with the signal region to correct the \Ztautau normalisation
+the Drell-Yan cross section is not applied as an uncertainty. A 3\% (5\%)
+extrapolation uncertainty from \Zmm $\rightarrow$ \Ztautau is applied in 
+the no b-tag (b-tag) category \cite{CMS-PAS-HIG-16-037}.
+\item \Zellell: The uncertainty on the Drell-Yan cross-section
+amounts to 4\% \cite{CMS-PAS-HIG-16-037}.
+\item \ttbar: The uncertainty on the \ttbar cross-section amounts
+to 6\% \cite{CMS-PAS-HIG-16-037}.
+\item di-boson and single-top: The uncertainty on the di-boson and
+single-top production cross-sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
+\item \Wjets:
+\item QCD:
+\end{itemize}
 \subsubsection*{Theory uncertainties}
@@
 \subsubsection*{$\Pgt_{h}$ energy scale}
+The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}. As the 
+shape of the total transverse mass distribution depends on the energy of the $\Pgt_{h}$
+it is applied as a shape uncertainty. It is applied to the signal samples and to
+backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
+\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
+hadronic taus.
 \subsubsection*{Electron energy scale}
+The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This affects
+the shape of the total transverse mass distribution, and this uncertainty is applied to the
+signals and to the \Ztautau background.
 \subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
+An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
+is applied to account for the extrapolation from the tau ID efficiency
+measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s. This
+uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels
 \subsubsection*{Top quark \pT~ reweighting}
+To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape
+uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
+of the correction, ie the difference between applying the correction twice and not applying the correction at all.
 \subsubsection*{Drell-Yan shape reweighting}
+An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
+is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
 \subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
+On the \Wjets background in the \etau and \mutau channels a shape 
+uncertainty of $\frac{-20\% \times p_{\text{T}}}{\text{GeV}}$ is 
+applied. This uncertainty is derived from variations in the data/MC ratio
+for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~ in 
+\Wjets events \cite{CMS-PAS-HIG-16-037}.
 
@@
 \label{sec:mssm_signalextraction}
+The total transverse mass \mTtot~ is used as discriminating variable in this analysis.
+All bins of the distribution are used to perform a shape analysis. The statistical
+methods, including the incorporation of nuisance parameters in the fit, were already
+described in section \ref{sec:hhh_results_extraction}. Some additional
+methods are used for this analysis, and they will be discussed in this section.
 
@@
 \label{sec:mssm_sigext_ctrl}
+
+\subsection{MSSMvsSM hypothesis testing}
+\label{sec:mssm_sigext_mssmvssm}
 

### 2017-01-10 MSSM/MSSM.tex
Adding some more on categorisation to MSSM chapter

@@
 samples. Minimum--bias events generated with \texttt{PYTHIA 8} are
-added to all \ac{MC} samples to model additional interactions.
+added to all \ac{MC} samples to model additional interactions. A reweighting
+is then applied to the \ac{MC} samples to make the pile--up distribution match
+that observed in data.
 
@@
 b--tagging than for normal jet reconstruction this requirement does not necessarily
-mean there will be only one jet in the event. The requirement reduces the sizeable \ttbar
+mean there will be only one b--tagged jet in the event. The requirement reduces the sizeable \ttbar
 background
@@
 
-Figure \ref{fig:mssm_cats_tt}a shows the number of jets 
-in the \tautau channel, with \ref{fig:mssm_cats_tt}b showing
+Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
+in the \mutau channel, with \ref{fig:mssm_cats_mt}b showing
 the number of b--tagged jets in that channel. The gluon--gluon fusion
-signal and bb associated signal are overlaid on these distributions,
-thus indicating the signal--sensitive bins, motivating the choice of categories.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
-\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
-\end{center}
-\caption{(a) Number of jets and (b) number of b--tagged jets in the \tautau channel. The gluon--gluon fusion signal (COLOUR)
-and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
-categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!}
-\label{fig:mssm_cats_tt}
+signal and bb associated signal are overlaid on these distributions, normalised
+to 100 times their cross--section times branching ratio at \mA=1 TeV and 
+\tanb=50 in the $m_{\text{h}}^{\text{mod+}}$ scenario. From the distribution of the
+gluon--gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
+see that the vast majority of these signal events do not have any b-tagged jets, which
+motivates the choice of the no b-tag category to target this signal. From
+the bb associated signal in the same figure we also see that the majority of bb associated
+signal events do not have any b-tagged jets either: either the b-jets in these events 
+are too soft, or they do not pass the b-tagging requirements. This means the no b-tag 
+category is also sensitive to some of the bb$\phi$ signal. The other observation we 
+can make from the bb$\phi$ signal in figure \ref{fig:mssm_cats_mt}b is that there is not
+such a large proportion of events with more than 1 b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
+we see that the \ttbar background starts to become more sizeable for events with more than
+one jet. The definition of the b-tag category is therefore chosen with the inclusion
+of the jet veto, such that the region where the \ttbar background becomes larger is excluded, 
+while retaining a large proportion of the bb$\phi$ signal.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
+\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
+\end{center}
+\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon--gluon fusion signal (dashed
+blue line) and bb--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
+are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
+scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
+\label{fig:mssm_cats_mt}
 \end{figure}
@@
 \label{sec:mssm_mccorrs}
+Because \ac{MC} samples are used for the signal predication, and 
+to estimate some of the backgrounds, it is important to correct for possible 
+mis-modelling with respect to the data. Dedicated control regions in
+data are used to derive the \ac{MC} to data correction factors
+that are applied to the \ac{MC} samples.
 \subsubsection*{Tracking efficiency}
+A discrepancy between the track reconstruction efficiency
+in data and \ac{MC} for electrons and muons was found. $\eta$--dependent
+scale factors are applied to mitigate the issue \cite{CMS-PAS-HIG-16-037}.
 \subsubsection*{Electron, muon and tau ID and isolation}
+Identification and isolation efficiencies in data and \ac{MC} are measured
+for electrons, muons and hadronic taus. A tag--and--probe
+method using \Zeenog (\Zmmnog) events is used to measure
+the efficiencies for electrons (muons). The hadronic tau identification
+and isolation efficiency is measured using a tag--and--probe method
+making use of $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+The measured efficiencies are used to construct scale factors to be
+applied to the \ac{MC} samples as $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
 \subsubsection*{Trigger efficiency}
+The electron, muon and hadronic tau trigger efficiencies are also measured
+using tag--and--probe methods with the types of events as described for the identification
+and isolation efficiencies. Because no trigger simulation is applied to
+the \ac{MC} samples, the efficiency $\epsilon_{\text{Data}}$ is simply applied
+to the \ac{MC} events. Because two electron/muon cross--triggers are 
+used to select events in the \emu channel, the efficiencies of the different
+cross trigger legs need to be combined. With one of the cross triggers having a
+\pT~cut of 23 GeV on the muon leg and 12 GeV on the electron leg, and the
+other having a minimum \pT~ of 23 GeV on the electron leg and 8 GeV on the muon
+leg, the combined efficiency of the two triggers becomes:
+\begin{equation}\label{eqn:mssm_em_trigeff}
+\epsilon_{\text{data}} = \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele12}) + \epsilon_{\text{data}}(\text{Mu8})\cdot\epsilon_{\text{data}}(\text{Ele23}) - \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele23}).
+\end{equation}
 \subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
+The $\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rates
+after applying the anti--electron and anti--muon discriminators are measured
+using a tag--and--probe method with \Zeenog and \Zmmnog events. A scale
+factor, to be applied to \ac{MC} events where the tau is faked by an electron or muon,
+is derived as the ratio between the fake rate in data and the fake rate in \ac{MC} events.
 \subsubsection*{\MET recoil corrections}
+Differences in \MET~ resolution and response between data and \ac{MC} 
+are accounted for by the application of recoil corrections
+to signal, \Wjets and \Ztautau events. These corrections
+are detailed in section \ref{sec:objects_met_recoilcorr}.
+\subsubsection*{B-tag scale factors}
+To correct for the difference in b--tagging efficiency
+and light jet mis--tagging rates between data and \ac{MC}
+\pT~ and $\eta$ dependent scale factors are derived as 
+described in reference \cite{cms-btag-run2}. They 
+are applied using the promote--demote method
+as outlined in equation \ref{eqn:promotedemote}.
 \subsubsection*{Top-quark \pT reweighting}
+A reweighting which was derived during \ac{LHC} Run-1
+to better match the top quark \pT~distribution in \ac{MC}
+to that observed in data is applied to \ttbar events. Despite
+the fact that the correction was derived during Run-1, it still
+improves the data/\ac{MC} agreement in a \ttbar enriched
+control region, as shown in figure \ref{fig:mssm_corrs_toppt}.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Without top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notopptrwt.png}}
+\subfloat[With top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
+\end{center}
+\label{fig:mssm_corrs_toppt}
+\caption{\mTtot~ distribution in the \ttbar enriched control region
+ (a) without and (b) with top quark \pT~ reweighting. The uncertainty band includes
+the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty. We can see
+that the data/\ac{MC} agreement in this control region improves when applying the top quark \pT~
+reweighting, particularly in the high \mTtot~ tail.}
+\end{figure}
 \subsubsection*{Drell-Yan shape reweighting}
+As the \ac{MC} samples used for the \Ztautau estimate
+do not model the data well for events with high di-lepton
+mass and high Z \pT~, a reweighting is applied to correct for this.
+These weights are derived in bins of $\PZ/Pphoton*$ mass and \pT~
+using \Zmm events in data, in such a way that they do not
+change the overall Drell-Yan normalisation. The weights
+are then applied to the \Ztautau and \Zellell background processes.
 
@@
 The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
-control region in data; this is described in section ADD REF. $R_{W}^{OS/SS}$ is 
+control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{W}^{OS/SS}$ is 
 taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
@@
 single-top production cross-sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
-\item \Wjets:
-\item QCD:
+\item \Wjets: FIXME
+\item QCD: FIXME
 \end{itemize}
 \subsubsection*{Theory uncertainties}
+FIXME
 
@@
 presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
-MENTION FEATURE
+We should note again that this model, although defined for \tanb~ values
+upwards of 10, is only strictly valid for \tanb~ below 10.
+The small excluded area around \mA=200 GeV is genuine. It is caused by the 
+production cross-section times branching ratio in the model, which is driven by
+two effects \cite{CMS-PAS-HIG-16-007}. On the one hand the branching ratio into taus decreases with decreasing
+\tanb~, while on the other hand a negative top--bottom interference effect increases the
+gluon--gluon fusion cross-section with decreasing \tanb~. Therefore the
+combined cross--section times branching ratio decreases with decreasing \tanb, until it
+increases again from a low value of \tanb~ down to \tanb=1. The feature is 
+thus expected to grow with more data.
 

### 2017-01-11 MSSM/MSSM.tex
Adding a lot more of MSSM chapter _ stuff on combination

@@
 \begin{equation}\label{eqn:mssm_em_trigeff}
-\epsilon_{\text{data}} = \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele12}) + \epsilon_{\text{data}}(\text{Mu8})\cdot\epsilon_{\text{data}}(\text{Ele23}) - \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele23}).
+\begin{split}
+\epsilon_{\text{data}}  = \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele12}) + \epsilon_{\text{data}}(\text{Mu8})\cdot\epsilon_{\text{data}}(\text{Ele23})~\\ - \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele23}).
+\end{split}
 \end{equation}
@@
 is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
-the \emu channel. INSERT PLOT
+the \emu channel, and it is shown in
+figure \ref{fig:mssm_corrs_toppt}b. Because the 6\%
+\ttbar normalisation uncertainty covers the observed
+discrepancy between data and \ac{MC}, no scale factor is applied.
 In the \mutau, \etau and \tautau channels
@@
 single-top production cross-sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
-\item \Wjets: FIXME
-\item QCD: FIXME
+\item \Wjets: In the \mutau and \etau channels the statistical uncertainties
+on the observed data and subtracted backgrounds are taken into account by
+the inclusion of these control regions in the fit. The statistical and 
+uncertainties on $R_{W}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag
+category in both the \etau and \mutau channels, and 11\% (14\%) in the b-tag
+category of the \mutau (\etau) channel. The systematic unsertainty on
+this ratio amounts to 8\% (10\%) in the no b-tag (b-tag) category of both channels.
+The statistical uncertainty on the low \mT/high \mT ratio is 2\% in the no b-tag
+category of both channels and 14\% (17\%) in the b-tag category of the \mutau (\etau) channel.
+The systematic uncertainty on this ratio amounts to 20\%. As the \Wjets background
+in the \tautau and \emu channels is estimated from \ac{MC} a 4\% theoretical
+normalisation uncertainty is applied.
+\item QCD: In the \emu channel the uncertainty on the QCD estimate
+is taken as the uncertainty on the measured opposite--sign to same--sign
+ratio, which is 23\% in the no b-tag category and 34 \% in the b-tag category. In the
+\tautau channel the statistical uncertainty on the QCD estimate is derived from
+the uncertainties on the observations and subtracted backgrounds in the
+sidebands used to derive the estimate. This uncertainty amounts to 3\% in the no b-tag
+category and 20\% in the b-tag category. An additional systematic uncertainty on the
+extrapolation factor from the anti-isolated sideband into the signal region is found
+to be 12\% in the no b-tag category and 14 \% in the b-tag category. For the \etau and
+\mutau channels the statistical
+uncertainties on the observation and subtracted \ac{MC} backgrounds in the control
+region used to derive the QCD estimate from is accounted for by the inclusion of control
+regions in the fit. The uncertainty on the opposite--sign to same--sign ratio, based on
+the studies described in section QCD OSSS is found to be 4\% (60\%) in the 
+no b-tag (b-tag) category of the \mutau channel, and 12\% (60\%) in the no b-tag (b-tag) category
+of the \etau channel. 
 \end{itemize}
-\subsubsection*{Theory uncertainties}
-FIXME
+\subsubsection*{Signal theory uncertainties}
+For interpretations of the results in MSSM benchmark scenarios, theory
+uncertainties on the SM and MSSM Higgs cross section predictions are included. 
+The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
+Uncertainties due to different renormalisation scales. 
+amount to 3.9\% for gluon fusion production,
+0.4\% for vector boson fusion, 2.8\% for ZH and 0.5\% for WH. The uncertainties
+due to different choice of pdf and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for vector boson fusion,
+1.6\% for ZH and 1.9\% for WH.
+For the MSSM Higgs cross sections used in the models, the uncertainties
+due to different choices of factorisation and renormalisation scale
+are computed, separately for each \mA-\tanb~ point, following the description in refs\cite{pdf-lhc,alphas-uncs}.
 
@@
 \label{sec:mssm_sigext_ctrl}
+The control regions used for estimation of the 
+\Wjets and QCD background contributions in the signal regions, discussed
+in section \ref{sec:mssm_bkgs_etmt_ctrl}, are included in the fit. They
+are added to the likelihood as single-bin counting experiments. In a given
+category of one of the channels, the \Wjets
+normalisation is fully correlated between the three control 
+regions and the signal region. One common, freely floating, nuisance parameter
+controls the \Wjets normalisation in all four regions. The QCD normalisation
+is fully correlated between the opposite--sign high and low \mT~ regions. The
+same is true for the same--sign high and low \mT regions. This means there are
+two freely floating nuisance parameters that govern the QCD normalisation: one
+that controls the QCD normalisation in the two opposite--sign regions, and one
+that controls it in the two same--sign regions.
+
+The \Zmm control regions mentioned in section \ref{sec:mssm_bkgs_ztt}
+are also included in the likelihood as single-bin counting experiments.
+The \Zmm control region in the no b-tag category is tied
+to the \Ztautau normalisation in the no b-tag categories of all four
+channels, again being controlled by a freely floating nuisance parameter. 
+The same is true for the \Zmm control region in the b-tag category
+and the \Ztautau normalisation in the b-tag categories of all four channels.
+
+\subsection{Signal process profiling and 2D likelihood scans}
+\label{sec:mssm_sigext_profile}
+Because the analysis targets the two main MSSM production modes, gluon fusion and
+b-associated production, limits are set on these two signal processes.
+However, in the upper limits on cross--section times branching ratio for the $gg\phi$
+process we should not make any assumptions about the presence or lack of the $bb\phi$
+process and vice versa. Therefore when calculating the upper limits on the $gg\phi$
+process, the contribution of the $bb\phi$ process is added to the fit as a freely floating nuisance
+parameter, and vice versa, in a process referred to as signal process profiling.
 
@@
 \label{sec:mssm_sigext_mssmvssm}
+The results of the search are interpreted in MSSM benchmark
+scenarios, with the interpretation made in the \mA-\tanb~ plane.
+At each point in the \mA-\tanb~ plane each MSSM scenario
+predicts a production cross section, and corresponding branching
+ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
+masses of the light h and the scalar H are also given as a function of \mA~ and \tanb.
+To interpret the results of this search in a particular scenario, the predicted
+signal from the three neutral Higgs bosons is combined into a single signal template.
+Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
+which give the \mTtot~ distributions for all channels and categories with an example three-Higgs signal overlaid.
+The compatibility of the data with all three Higgs bosons, not just a single one, is thus tested.
+
+Simply comparing a three-Higgs-signal-plus-background hypothesis with a background-only 
+hypothesis to determine the exclusion power of the search in a particular
+model can be problematic. Due to the existence of a Higgs boson with a 
+mass of 125 GeV, all MSSM benchmark scenarios must include a light Higgs boson
+with very similar properties to the boson discovered during Run 1 of the \ac{LHC}.
+This means that we should do a test that distinguishes between three-Higgs-signal-plus-background, and
+standard model Higgs-signal-plus-background.
+
+This means the likelihood function defined in equation \ref{eqn:hhh_likelihood}
+must be modified. Instead of testing for the compatibility of the data with
+a signal + background expectation modified by the signal strenght modifier $\mu$ as
+$\mu \cdot s(\theta) + b(\theta)$, a likelihood must be constructed as:
+\begin{equation}\label{mssm_likelihood}
+\mathcal{L}(\text{data}|\mu, \theta) = \mathcal{L}(\text{data}|\mu \cdot s_{\text{MSSM}}(\theta) + (1-\mu)\cdot s_{\text{SM}}(\theta) + b(\theta)),
+\end{equation}
+where $s_{\text{MSSM}}(\theta)$ corresponds to the MSSM signal expectation, ie the three-Higgs-signal, and $s_{\text{SM}}(\theta)$ 
+corresponds to the SM signal expectation.
+The signal strength modifier $\mu$ takes the role of distinguishing between
+the two hypothesis in this case. The model cannot allow for the coexistence 
+of the SM and MSSM hypotheses; the MSSM hypothesis ($\mu=1$) is tested
+against the SM hypothesis ($\mu=0$).
+
+The modification of the likelihood function means it is no longer possible
+to use the profile likelihood ratio of equation \ref{eqn:hhh_profilelikelihood}:
+we are forced to test $\mu=1$ against $\mu=0$ and 
+$\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
+general not 0. A solution to this problem can be found in test statistic used at the Tevatron \cite{LHCHComb2011},
+\begin{equation}\label{eqn:mssm_tevatron_teststat}
+q_{\mu} = -2\text{ln}\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0}} \text{ with } 0\leq\mu.
+\end{equation}
+In this test statistic we test a positive value of $\mu$ against 0, thus we are able to define
+the desired `MSSMvsSM' test statistic as
+\begin{equation}\label{eqn:mssm_mssmvssm_stat}
+q_{\text{MSSMvsSM}} = -2\text{ln}\frac{\mathcal{L}(\text{data}|s_{\text{MSSM}}(\theta) + b(\theta)}{\mathcal{L}(\text{data}|s_{\text{SM}}(\theta)+b(\theta)}.
+\end{equation}
+
+The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, can not be applied
+to the Tevatron test statistic, and therefore the probability density functions need to be generated 
+with toy datasets. Using these pdfs we can then calculate $CL_s{\mu=1}$ as defined in equation \ref{eqn:hhh_cls}.
+If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95 \% CL. This generation of toy datasets and 
+calculation of corresponding $CL_s$ value is performed for many points in a grid in the \mA-\tanb~ plane,
+with interpolation between grid points performed to obtain a smooth exclusion contour.
+The distribution of toy datasets for the SM and MSSM hypothesis, as well as the resulting $CL_s$ values,
+are given for three \mA-\tanb~ points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
+there is no separation between the MSSM and SM toy distributions, and so we cannot exclude this point. The separation
+between the distributions in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
+with the SM hypothesis. This point is on the edge of being excluded. Finally the distributions in figure \ref{fig:mssm_mssmvssm_toys}c
+are very well separated, and the observation is compatible with the SM hypothesis, meaning this point of the parameter space is excluded.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\mA=1.2 TeV, \tanb=16]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_16.png}}
+\subfloat[\mA=1.2 TeV, \tanb=50]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_50.png}}~\\
+\subfloat[\mA=700 GeV, \tanb=60]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_700_tanb_60.png}}
+\end{center}
+\caption{Distribution of toys for the SM and MSSM hypothesis at three different points in the $m_{\text{h}}^{\text{mod+}}$
+scenario, each with different levels of separation between the MSSM and SM toy distributions.}
+\label{fig:mssm_mssmvssm_toys}
+\end{figure}
 
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-a.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-b.pdf}}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_ggh.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_bbh.pdf}}
 \end{center}
@@
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
-and \emu (gold) channels \cite{CMS-PAS-HIG-16-037}. For masses below 200 GeV the \mutau channel is the most sensitive,
+and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
 while the \tautau channel dominates for higher masses. The \etau channel is always
@@
 until at around 1.6 TeV it starts to overtake the \etau channel, with the sensitivity at 3.2 TeV 
-being similar or slightly better than the \mutau channel. FIXME REMAKE PLOT?}
+being similar or slightly better than the \mutau channel.}
 \label{fig:mssm_results_limits_breakdown}
@@
 \label{sec:mssm_combination}
-
-\subsection{Procedure}
+The results outlined in the previous section, for the analysis
+on a dataset corresponding to an integrated luminosity of 12.9 fb$^{-1}$
+at a centre-of-mass energy of 13 TeV, collected during the 2016 running period
+of the \ac{LHC}, can be combined with the results from a very similar analysis
+performed on 2.3 fb$^{-1}$ collected at 13 TeV during 2015, detailed
+in reference \cite{CMS-PAS-HIG-16-006}. This combination should be able
+to improve slighty on the limits set by the 2016 analysis. Because the 
+analysis on the 2015 dataset is very similar to the 2016 analysis it 
+is not described in detail, however, the results will
+be presented, and key differences with the more recent result highlighted
+where needed.
+
+\subsection{Results from 2015 analysis}
+\label{sec:mssm_combination_2015}
+The results from the search for \AHtotautau on a
+dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
+collected at a centre-of-mass energy of 13 TeV during 2015 are presented
+in this section. As for the analysis discussed earlier
+in the chapter a shape analysis is performed, however a different
+discriminating variable, the transverse component of the di-$\Pgt$ mass
+as reconstructed using the SVFit algorithm, was used. This variable
+is denoted $m_{\text{T,\Pgt\Pgt}}$. The transverse di-$\Pgt$ mass 
+distributions for the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
+The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
+in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
+and once at higher mass, for the heavy H and A.}
+\label{fig:mssm_hig16006_mtsv_mt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+observed events in the (a) no b-tag and (b) b-tag categories of the \etau channel.}
+%The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
+%in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
+%and once at higher mass, for the heavy H and A.}
+\label{fig:mssm_hig16006_mtsv_et}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+observed events in the (a) no b-tag and (b) b-tag categories of the \tautau channel.}
+%The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
+%in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
+%and once at higher mass, for the heavy H and A.}
+\label{fig:mssm_hig16006_mtsv_tt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
+%The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
+%in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
+%and once at higher mass, for the heavy H and A.}
+\label{fig:mssm_hig16006_mtsv_em}
+\end{figure}
+
+These distributions do not show any significant excesses. The upper limits
+on cross--section times branching ratio for the gluon-fusion and b-associated
+process are shown in figure \ref{fig:mssm_results_hig16006_limits}a
+and b, respectively. All channels and categories are combined. A comparison of
+the expected limits per channel is given in figure \ref{fig:mssm_results_limits_breakdown_hig16006}.
+These follow a similar pattern to those given in figure \ref{gi:mssm_results_limits_breakdown}, notice
+however the \emu channel remains the least sensitive even at very high mass, as the
+transverse component of the di-$\Pgt$ mass exhibits a sizeable \ttbar tail in the \emu channel. The total
+transverse mass collapses events from the tail into lower regions of the distribution.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-a.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-b.pdf}}
+\end{center}
+\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+process and (b) the b--associated production process. All four final states and 
+all categories are combined for these limits \cite{CMS-PAS-HIG-16-006}.}
+\label{fig:mssm_results_hig16006_limits}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_ggH.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_bbH.pdf}}
+\end{center}
+\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
+comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
+and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
+while the \tautau channel dominates for higher masses. The \etau channel is always
+slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive.}
+\label{fig:mssm_results_limits_breakdown_hig16006}
+\end{figure}
+
+\subsection{Combination procedure}
 \label{sec:mssm_combination_procedure}
+The idea of combining the two analyses is to combine the 
+individual likelihoods to improve the analysis sensitivity and
+physics reach. To do this correctly the correlations between
+nuisance parameters in 2015 and 2016 need to be taken into account.
+%Strictly, studies into the underlying correlations between
+%nuisance parameters should be performed. This is however not always
+%feasible and in some cases
+The correlation scheme between nuisance parameters relating to the 2015 and 2016
+analyses, as used for this combination, is given in table ADD TABLE.
 
@@
 \label{sec:mssm_combination_results}
+The expected and observed upper limits on cross--section times branching ratio,
+for the combination of the 2015 and 2016 analyses, are shown in figure
+\ref{fig:mssm_results_combination_limits}. The limits behave as expected
+from the individual 2015 and 2016 limits.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_ggH_cmb.png}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_bbH_cmb.png}}
+\end{center}
+\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+process and (b) the b--associated production process. These results
+combine all categories and all four final states from both the 2015
+and the 2016 analysis.}
+\label{fig:mssm_results_combination_limits}
+\end{figure}
+
+To get a better idea of which analysis
+is driving the sensitivity of the combination, we should consider the comparison
+of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
+gluon-fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
+higher masses the analysis sensitivity is only very slightly improved with respect to the 
+analysis of the 12.9 fb$^{-1}$ dataset. However, for masses between 200 and 800 GeV
+there is a larger improvement in analysis sensitivity from combining the two analyses.
+This is expected since the analysis on the 2016 dataset used a slightly different
+selection that made the analysis more optimal at masses above 800 GeV,
+and slightly less optimal below this mass, than the analysis on the 2015 dataset. This
+effect is less visible on the b--associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_limitcomp_ggH.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_limitcomp_bbH.pdf}}
+\end{center}
+\caption{Comparison of the expected Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+process and (b) the b--associated production process. The green curve shows the results
+from combining the 2015 and 2016 analyses (integrated luminosity of 15.2 fb$^{-1}$),
+with the red line indicating the limits from the 2016 analysis only (integrated luminosity of 12.9 fb$^{-1}$)
+and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of 2.3 fb$^{-1}$).}
+\label{fig:mssm_results_combination_limits_comp}
+\end{figure}

### 2017-01-12 MSSM/MSSM.tex
Adding more MSSM stuff

@@
 control region, as shown in figure \ref{fig:mssm_corrs_toppt}.
-\begin{figure}[h!]
-\begin{center}
-\subfloat[Without top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notopptrwt.png}}
-\subfloat[With top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
-\end{center}
-\label{fig:mssm_corrs_toppt}
-\caption{\mTtot~ distribution in the \ttbar enriched control region
- (a) without and (b) with top quark \pT~ reweighting. The uncertainty band includes
-the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty. We can see
-that the data/\ac{MC} agreement in this control region improves when applying the top quark \pT~
-reweighting, particularly in the high \mTtot~ tail.}
-\end{figure}
 \subsubsection*{Drell-Yan shape reweighting}
@@
 contribution in this region is enhanced, however there is still
-some contribution from QCD events in this region. Therefore we
+some contribution from QCD events in this region. This is visible in 
+figure \ref{fig:mssm_bkgs_wjets_mutau_mt} which shows the \mT~ distribution in the
+\mutau channel, indicating the signal region and the high-\mT~ control region.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_002.pdf}
+\end{center}
+\caption{Distribution of the transverse mass \mT~ in the \mutau channel, indicating
+the signal region and the high \mT~ control region \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_bkgs_wjets_mutau_mt}
+\end{figure}
+
+Because of this contribution from QCD events in the high \mT~ region we
 have, for \mT$>70$ GeV:
@@
 \label{sec:mssm_bkgs_etmt_qcdosss}
-Studies of QCD OS/SS ratio go here
+The ratio of opposite--sign to same--sign QCD events, $R_{QCD}^{OS/SS}$ is measured
+in two anti-isolated sidebands by performing a fit to the distribution of the
+visible mass of the di-tau pair in 
+opposite-sign events. The QCD template, which is taken from same--sign events 
+assuming $R_{QCD}^{OS/SS} = 1$ is treated as the signal, and a binned maximum
+likelihood fit to the QCD signal strength is performed while allowing the other
+backgrounds to float within reasonable normalisation uncertainties. The
+resulting best fit value of the signal strengh parameter is taken as $R_{QCD}^{OS/SS}$.
+Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\mu}<0.25$ and $0.1<I_{\text{rel}}^{e}<0.2$)
+and one further away ($0.25<I_{\text{rel}}^{\mu}<0.5$ and $0.2<I_{\text{rel}}^{e}<0.5$). The results of the fits,
+performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_far}
+for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
+$R_{QCD}^{OS/SS}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
+Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
+an overall uncertainty of 12\% in the \etau channel and 4\% in the \mutau channel.
+When performing the same fits in the no b-tag and b-tag categories to determine differences between
+this pre-categorisation opposite--sign to same--sign ratio, and the ratio as measured in categories it is found that 
+the fit is not stable in the b-tag category due to the number of events in this region being too small.
+The uncertainty on the ratio is increased for the b-tag category to cover the differences.
+The uncertainties are already large enough to cover differences between the pre-categorisation $R_{QCD}^{OS/SS}$ and the
+fits as performed in the no b-tag category. So $R_{QCD}^{OS/SS}$ in the \mutau channel is taken to be
+1.18 in both the b-tag and the no b-tag category, with a 60\% uncertainty in the b-tag category and a 4\% uncertainty in the no b-tag category.
+In the \etau channel $R_{QCD}^{OS/SS}$ is taken to be 1.02 with a 60\% uncertainty in the b-tag category and a 12\% uncertainty
+in the no b-tag category.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_prefit.png}}
+\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_postfit.png}}
+\end{center}
+\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+is 1.180$\pm$0.044.}
+\label{fig:mssm_qcdossss_mtnear}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_prefit.png}}
+\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_postfit.png}}
+\end{center}
+\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
+the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+is 1.184$\pm$0.035.}
+\label{fig:mssm_qcdossss_mtfar}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_prefit.png}}
+\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_et_1_postfit.png}}
+\end{center}
+\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+is 1.015$\pm$0.059.}
+\label{fig:mssm_qcdossss_etnear}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_prefit.png}}
+\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_postfit.png}}
+\end{center}
+\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
+the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+is 1.127$\pm$0.045.}
+\label{fig:mssm_qcdossss_etfar}
+\end{figure}
 
@@
 is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
-the \emu channel, and it is shown in
-figure \ref{fig:mssm_corrs_toppt}b. Because the 6\%
+the \emu channel, and it is shown in \ref{fig:mssm_corrs_toppt}.
+Because the 6\%
 \ttbar normalisation uncertainty covers the observed
@@
 
-\subsection{Other backgrounds}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
+\end{center}
+\caption{\mTtot~ distribution in the \ttbar enriched control region.
+The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
+\label{fig:mssm_corrs_toppt}
+\end{figure}
+
+\subsection{Di--boson plus single--top}
 \label{sec:mssm_bkgs_other}
@@
 Because the analysis targets the two main MSSM production modes, gluon fusion and
-b-associated production, limits are set on these two signal processes.
+b-associated production, limits are set on these two signal processes. As we
+have seen in section WHATEVER we cannot fully separate the two signals by means
+of the categorisation used. 
 However, in the upper limits on cross--section times branching ratio for the $gg\phi$
@@
 parameter, and vice versa, in a process referred to as signal process profiling.
+
+Because these two signal processes are targeted by this analysis, it is possible
+to re-define the likelihood as a function of both the gg$\phi$ and bb$\phi$ signals:
+\begin{equation}\label{mssm_2D_likelihood}
+\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi}, \theta) = \mathcal{L}(\text{data}|\mu_{gg\phi} \cdot s_{gg\phi}(\theta) + \mu_{bb\phi}\cdot s_{bb\phi}(\theta) + b(\theta)),
+\end{equation}
+where $s_{gg\phi}$ and $s_{bb\phi}$ are the signal expectations of the two
+production processes and the signal strength modifiers $\mu_{gg\phi}$ and $\mu_{bb\phi}$ now represent the cross--section times branching ratio of the
+processes. Using this definition we can now perform a likelihood scan in two dimensions by 
+constructing a two-dimensional grid in $\mu_{gg\phi}$ and $\mu_{bb\phi}$, both required to be greater than or equal to 0. 
+The negative log-likelihood,
+\begin{equation}\label{eqn:nll}
+\text{NLL} = -\text{ln}\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta)
+\end{equation}
+is then evaluated at each point. The point in the 2D grid where the NLL reaches
+its lowest value gives the best fit value for $\mu_{gg\phi}$ and $\mu_{bb\phi}$.
+68\% and 95\% confidence intervals are constructed as the values
+$\mu_{gg\phi}^{N\%}$ and $\mu_{bb\phi}^{N\%}$ for which:
+\begin{equation}\label{eqn:mssm_2D_deltaNLL}
+\begin{split}
+\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{68\%},\mu_{bb\phi}^{68\%}) = 0.5, ~\\
+\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{95\%},\mu_{bb\phi}^{95\%}) = 1.92,
+\end{split}
+\end{equation}
 
@@
 
+\subsection{Sensitivity to the Standard Model Higgs boson}
+\label{sec:mssm_results_125GeV}
+As we set limits on MSSM Higgs boson production 
+down to masses of 90 GeV it is important to consider possible sensitivity
+to the 125 GeV Higgs boson. As the cross--section times branching ratio for gluon-fusion
+production of the 125 GeV Higgs boson in the standard model, with decay into $\Pgt\Pgt$
+is 3.05 pb \cite{YR4} and the expected limit on cross--section times
+branching ratio for MSSM gg$\phi$ production at around 125 GeV is around 20 pb
+the analysis is not yet sensitive to the SM Higgs boson. The
+limits shown in figure \ref{fig:mssm_results_greenband},
+which include the standard model Higgs boson as part of the backgrounds,
+are almost exactly the same as those shown in figure \ref{fig:mssm_results_limits}. This
+also indicates the current lack of sensitivity to the standard model Higgs boson.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-a.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-b.pdf}}
+\end{center}
+\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+process and (b) the b--associated production process. The SM, 125 GeV Higgs boson
+is included as one of the backgrounds. All four final states and 
+all categories are combined for these limits \cite{CMS-PAS-HIG-16-037-addit}.}
+\label{fig:mssm_results_greenband}
+\end{figure}
+
 \subsection{2D likelihood scans}
 \label{sec:mssm_results_2D}
+The 2D likelihood scans, as described in section \ref{sec:mssm_sigext_profile}, for
+a few mass points are shown in figure \ref{fig:mssm_results_2D_scans},
+for four mass points ranging from 100 GeV to 3.2 TeV. From the shape of the contours
+we can see the correlation between the gg$\phi$ and bb$\phi$ processes, in a show of
+the fact that we cannot fully disentangle the two processes.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\phi} = 100$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-a.pdf}}
+\subfloat[$m_{\phi} = 700$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-g.pdf}}~\\
+\subfloat[$m_{\phi} = 1.6$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-i.pdf}}
+\subfloat[$m_{\phi} = 3.2$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-l.pdf}}
+\end{center}
+\caption{2D likelihood scans showing the best-fit value (black cross) for cross--section times branching ratio 
+of both the gluon fusion (x-axis) and b- associated production (y-axis) processes. The red diamond indicates the
+expected best fit point for the presence of a 125 GeV SM Higgs boson, and the purple bands indicate the 68\% and
+95\% confidence interval contours \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_2D_scans}
+\end{figure}
 
@@
 
+\begin{table}[htp]
+\begin{center}
+\caption{Correlations between nuisance parameters in 2015 and 2016 analysis}
+\begin{tabular}{@{}lll@{}}
+%\toprule
+\textbf{Nuisance} & \textbf{Correlation} & \textbf{Motivation}\\
+\midrule
+Luminosity & Partially correlated & As studied by the relevant people in the experiment\\
+Jet energy scale & Fully correlated & Found to be so by those responsible for it in the experiment\\
+b-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods\\
+mis-tagging & Part correlated & As recommended by those measuring b-tagging scale factors\\
+Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016\\
+Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016\\
+Tau ID/isolation/trigger& Uncorrelated & On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis\\
+High \pT tau ID efficiency & Correlated & This should not be affected by the lack of tau ID scale factor and covers teh same underlying issue in both analyses\\
+Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
+Drell-Yan shape & Correlated & The same \ac{MC} samples, exhibiting the observed discrepancies, is used.
+In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar\\
+W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
+The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point\\
+MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016\\
+Top quark \pT reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses\\
+Drell-Yan cross section & Correlated & Theoretical uncertainty so should be correlated\\
+Di--boson cross section & Correlated & Theoretical uncertainty so should be correlated\\
+\ttbar cross section & Correlated & Theoretical uncertainty so should be correlated\\
+\Wjets cross section & Correlated & Theoretical uncertainty so should be correlated\\
+SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated\\
+\Ztautau acceptance & - & Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet\\
+\Ztautau extrapolation& - & Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance\\
+e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
+$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
+jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
+
+\end{tabular}
+\label{tab:mssm_combination_correlations}
+\end{center}
+\end{table}
+
 \subsection{Results}

### 2017-01-12 MSSM/MSSM.tex
Fixing tables in MSSM section

@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
+\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
 \end{center}
@@
 
+\subsection{Summary of uncertainties and correlations}
+\label{sec:mssm_uncs_summary}
+The systematics that are applied are summarised in
+table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
+channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
+in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
+in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
+the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
+in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
+Some of the uncertainties
+are different for different processes, where this is the case ranges are given.
+Uncertainties marked "Fully correlated" are correlated between the different
+decay channels and event categories, those marked "Fully uncorrelated" are
+uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
+indicates that the uncertainty is correlated between categories but uncorrelated between
+the different decay channels.
+\input{MSSM/UncOv}
+\clearpage
+
 \section{Signal extraction}
@@
 \end{figure}
+\clearpage
 
@@
 The correlation scheme between nuisance parameters relating to the 2015 and 2016
-analyses, as used for this combination, is given in table ADD TABLE.
+analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}.
 
@@
 \caption{Correlations between nuisance parameters in 2015 and 2016 analysis}
-\begin{tabular}{@{}lll@{}}
-%\toprule
+{\footnotesize
+\begin{tabular}{p{3cm}p{2cm}p{10cm}}
+\toprule
 \textbf{Nuisance} & \textbf{Correlation} & \textbf{Motivation}\\
 \midrule
-Luminosity & Partially correlated & As studied by the relevant people in the experiment\\
-Jet energy scale & Fully correlated & Found to be so by those responsible for it in the experiment\\
+Luminosity & Partially \mbox{correlated} & As studied by the relevant people in the experiment\\
+\midrule
+Jet energy scale & Fully \mbox{correlated} & Found to be so by those responsible for it in the experiment\\
+\midrule
 b-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods\\
-mis-tagging & Part correlated & As recommended by those measuring b-tagging scale factors\\
+\midrule
+mis-tagging & Partially \mbox{correlated} & As recommended by those measuring b-tagging scale factors\\
+\midrule
 Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016\\
+\midrule
 Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016\\
-Tau ID/isolation/trigger& Uncorrelated & On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis\\
+\midrule
+Tau ID/isolation/trigger& Uncorrelated & \scriptsize{On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis}\\
+\midrule
 High \pT tau ID efficiency & Correlated & This should not be affected by the lack of tau ID scale factor and covers teh same underlying issue in both analyses\\
+\midrule
 Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
-Drell-Yan shape & Correlated & The same \ac{MC} samples, exhibiting the observed discrepancies, is used.
-In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar\\
-W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
-The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point\\
+\midrule
+Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, exhibiting the observed discrepancies, are used.
+In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar}\\
+\midrule
+W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & \scriptsize{Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
+The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point}\\
+\midrule
 MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016\\
+\midrule
 Top quark \pT reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses\\
-Drell-Yan cross section & Correlated & Theoretical uncertainty so should be correlated\\
-Di--boson cross section & Correlated & Theoretical uncertainty so should be correlated\\
-\ttbar cross section & Correlated & Theoretical uncertainty so should be correlated\\
-\Wjets cross section & Correlated & Theoretical uncertainty so should be correlated\\
+\midrule
+Drell-Yan $\sigma$& Correlated & Theoretical uncertainty so should be correlated\\
+\midrule
+Di--boson $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
+\midrule
+\ttbar $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
+\midrule
+\Wjets $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
+\midrule
 SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated\\
-\Ztautau acceptance & - & Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet\\
-\Ztautau extrapolation& - & Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance\\
+\midrule
+\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet.}\\
+\midrule
+\Ztautau \mbox{extrapolation}& N/A & \scriptsize{Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance.}\\
+\midrule
+%e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
+%$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
+%jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
+%QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-iso sideband in 2015 and 2016 analyses\\
+%QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
+%Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
+%Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
+%Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
+In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that\\
+%Statistical uncertainty on W low/high\mT~ ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
+%Systematic uncertainty on W low/high\mT~ ratio (\etau and \mutau) & Uncorrelated & This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately\\
+%QCD OS/SS ratio statistical uncertainty (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated\\
+%QCD OS/SS ratio systematic uncertainty (\etau and \mutau) & Uncorrelated & The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
+Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.\\
+%bin--by--bin uncertainties for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible to achieve\\
+\end{tabular}}
+\label{tab:mssm_combination_correlations}
+\end{center}
+\clearpage
+\end{table}
+\begin{table}[pt!]
+\begin{center}
+{\footnotesize
+\begin{tabular}{p{3cm}p{2cm}p{10cm}}
+\midrule
 e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
+\midrule
 $\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
+\midrule
 jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
-
-\end{tabular}
-\label{tab:mssm_combination_correlations}
+\midrule
+QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-iso sideband in 2015 and 2016 analyses\\
+\midrule
+QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
+\midrule
+Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
+\midrule
+Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
+\midrule
+Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
+In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
+\midrule
+Statistical uncertainty on W low/high\mT~ ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
+\midrule
+Systematic uncertainty on W low/high\mT~ ratio (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately}\\
+\midrule
+QCD OS/SS ratio statistical uncertainty (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated\\
+\midrule
+QCD OS/SS ratio systematic uncertainty (\etau and \mutau) & Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
+Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.}\\
+\midrule
+bin--by--bin uncertainties for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible to achieve\\
+\bottomrule
+\end{tabular}}
 \end{center}
 \end{table}
+\clearpage
 

### 2017-01-12 MSSM/UncOv.tex
Fixing tables in MSSM section

@@
-\section{Overview of uncertainties}
-\label{sec:mssm_uncs_overview}
-The systematics that are applied are summarised in
-table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
-channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
-in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
-in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
-the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
-in table \ref{tab:SystematicUncertainties_zmm}.
-
 \begin{table}[!h]
@@
 \caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
-or background events in the $\mu \tau_{h}$ channel. Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
- {\scriptsize
+or background events in the $\mu \tau_{h}$ channel.} 
+ {\tiny
  \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
+\toprule
      & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
-    \hline
+    \midrule
 \textbf{ Process }
@@
      & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
     All from MC    & 6.2\%  &6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
     All from MC & 0--1\% & 0--2\% & 0--1\% & 0--1\%& 0--12\% & 3--11\% & 0--15\% & 0--14\% & Fully correlated \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\MET \textbf{scale} }\\
@@
     TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\MET \textbf{resolution}} \\
@@
     TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Muon identification and trigger} }\\
     All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
     ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
-    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
-    \hline
+    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Cats:C,chns:U    \\
+    \midrule
     \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
@@
     W &  &  &  &  & 4\% & 4\% & 6\% & 6\%& Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
     All from MC & & & & & 1--7\% & & & & Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
-    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
+    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
+    \midrule
     \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
-    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
+    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
+    \midrule
     \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
     TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{DY reweighting } }\\
     ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
     W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
@@
     ZTT         & 3\% & 3\% & 3\% & 3\% & 5\% & 5\% & 5\% & 5\% & Fully uncorrelated           \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\
+    \multicolumn{10}{l}{\textbf{Normalisation,} \ttbar}\\
     TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
@@
    \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\
-    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Corr. between cats, uncorr. between chns        \\
+    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Cats:C,chns:U        \\
     \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
-    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns  \\
-    \hline
+    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Cats:C,chns:U  \\
+    \midrule
     \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
@@
     QCD & 4\% & 4\% & & & 60\% & 60\% & & &Fully uncorrelated \\
-    \hline
+\bottomrule
 \end{tabular}
@@
 \caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
-or background events in the $e \tau_{h}$ channel. Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
- {\scriptsize
+or background events in the \etau channel.}
+ {\tiny
  \begin{tabular}{p{2cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1cm}p{1cm}|p{3cm}}
+\toprule
      & \multicolumn{8}{|c}{Event yield uncertainty by event category} &  \\
-    \hline
+    \midrule
 \textbf{ Process }
@@
      & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
     All from MC    & 6.2\%  & 6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Jet energy scale }}\\
     All from MC & 0--1\% & 0--1\% & 0--2\% & 0--1\%& 1--14\% & 0--12\% & 0--15\% & 0--15\% & Fully correlated \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\MET \textbf{scale}}\\
@@
     TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\MET \textbf{resolution}} \\
@@
     TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Electron identification and trigger} }\\
     All from MC & 2\% & 2\% &2\% &2\%  & 2\%  & 2\% & 2\% & 2\% & Fully correlated      \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Tau-lepton identification}}\\
     ZTT,TTT,VVT, signal     & 5\% & 5\% & 5\% & 5\%   & 5\%  & 5\% & 5\% & 5\% & Fully correlated \\
-    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
-    \hline
+    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Cats:C,chns:U    \\
+    \midrule
     \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
@@
     W &  &  &  &  & 5\% & 2\% & 10\% & 3\% & Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
     All from MC & & & & & 0--3\% & & & & Fully correlated\\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Tau-lepton energy scale}}\\
-    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
+    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
+    \midrule
     \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
-    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
-    \hline
+    ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
+    \midrule
     \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
     TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{DY reweighting } }\\
     ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
     W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
-    \hline
+    \midrule
     \multicolumn{10}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
@@
    \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\
-    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Corr. between cats, uncorr. between chns       \\
+    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Cats:C,chns:U       \\
     \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
-    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns       \\
-    \hline
+    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Cats:C,chns:U       \\
+    \midrule
     \multicolumn{10}{l}{\textbf{W OS/SS ratio (stat) } } \\
@@
     QCD & 12\% & 12\% & & & 60\% & 60\% & & &Fully uncorrelated \\
-    \hline
+    \bottomrule
 \end{tabular}
@@
 \caption{Systematic uncertainties that affect the estimated number of signal
-or background events in the $\tau_{h} \tau_{h}$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
+or background events in the \tautau channel.}
 {\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
+\begin{tabular}{l|cc|p{5cm}}
+\toprule
      & \multicolumn{2}{|c}{Event yield uncertainty by event category} & \\
-    \hline
+    \midrule
     Process & No b-tag & B-tag & Correlation                   \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
     All from MC      & 6.2\%      & 6.2\%  & Fully correlated                           \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Jet energy scale}} \\
     All from MC      & 0--4\%      & 0--9\%  & Fully correlated                    \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\MET \textbf{scale}} \\
@@
     TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\MET \textbf{resolution}} \\
@@
     TTT,TTJ,VVT,VVJ     & 2\%     & 2\% & ZTT/W uncorrelated from TTT,TTJ,VVT,VVJ                          \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{Tau-lepton identification and trigger} \\
@@
     ZTT,TTT,VVT, signal         & 9.2\%     & 9.2\%   & Correlated between categories, uncorrelated between channels \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\
     All from MC   & 0--4\%     & 0--11\%  & Fully correlated                  \\
-    \hline
+    \midrule
    \multicolumn{4}{l}{\textbf{B-mistag rate}} \\
     All from MC    &  0--1\%    & 0--12\%  & Fully correlated                  \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Tau-lepton energy scale}} \\
     ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels                       \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\
     ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels   \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{DY reweighting } } \\
     ZTT       & shape      & shape & Fully correlated                       \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\
     TTT,TTJ & shape & shape & Fully correlated                  \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production}}\\
     ZL,ZJ       & 4\%      & 4\%  & Fully correlated                    \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation}}\\
     ZTT         & 3\%        & 5\%  & Fully uncorrelated                   \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
+    \midrule
+    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
     TTT,TTJ        & 6\%       & 6\%  & Fully correlated                       \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\
     VVT,VVJ &  5\%        & 5\%       & Fully correlated                        \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\
     ZL & 10\%     & 10\%       & Correlated between categories, uncorrelated between channels                        \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\
     ZJ,W,TTJ & 20\%     & 20\%       & Correlated bewteen categories, uncorrelated between channels     \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet (stat) }} \\
@@
     QCD  & 12\% & 14\%  & Fully uncorrelated\\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
     W & 4\% & 4\% & Fully correlated \\
+\bottomrule
 \end{tabular}}
@@
 \caption{Systematic uncertainties that affect the estimated number of signal
-or background events in the $e\mu$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
+or background events in the \emu channel.}
 {\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
+\begin{tabular}{l|cc|p{5cm}}
+   \toprule
      & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
-    \hline
+    \midrule
     \textbf{Process}
     &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
     All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
     All from MC   & 0--1\% & 1--69\% &Fully correlated \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\MET \textbf{scale}} \\
@@
     TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
-    \hline
+    \midrule
    \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
@@
     TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
     All from MC       & 2\%        & 2\% & Fully correlated                              \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
     All from MC      & 2\%     & 2\%  & Fully correlated                      \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
     All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
     All from MC      &     & 0--10\% & Fully correlated                    \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
     ZTT,signal      & shape      & shape  & Fully correlated                \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{DY reweighting }}\\
      ZTT       & shape      & shape & Fully correlated                       \\
-   \hline
+   \midrule
     \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
     TT & shape & shape  & Fully correlated                 \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
     ZLL      & 4\%      & 4\%  & Fully correlated                   \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
      ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
+    \midrule
+    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
     TT        & 6\%       & 6\% & Fully correlated                        \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
     VV        & 5\%       & 5\% & Fully correlated                       \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
     QCD & 23\% & 34\% & Fully uncorrelated\\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
     W+jets & 4\% & 4\% & Fully correlated\\
+\bottomrule
 \end{tabular}}
@@
 \caption{Systematic uncertainties that affect the estimated number of
-or background events in the $Z\rightarrow\mu\mu$ channel.Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories.}
+or background events in the $Z\rightarrow\mu\mu$ channel.}
 {\scriptsize
-\begin{tabular}{l|cc|p{3cm}}
+\begin{tabular}{l|cc|p{5cm}}
+   \toprule
      & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
-    \hline
+    \midrule
     \textbf{Process}
     &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
     All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
     All from MC   & 0--1\% & 1--69\% &Fully correlated \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\MET \textbf{scale}} \\
@@
     TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
     All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
     All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
     All from MC      &     & 0--10\% & Fully correlated                    \\
-    \hline
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
+    \midrule
+    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
     TT        & 6\%       & 6\% & Fully correlated                        \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
     VV        & 5\%       & 5\% & Fully correlated                       \\
-    \hline
+    \midrule
     \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
     W+jets & 4\% & 4\% & Fully correlated\\
+    \bottomrule
 \end{tabular}}

### 2017-01-13 MSSM/MSSM.tex
Adding something on tau iso for tt

@@
 model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
-production in the two decay modes (see THEORY) and decay into $\Pgt\Pgt$. In 
-addition, the results are interpreted in MSSM benchmark scenarios and 2D likelihood
+production in the two modes (see THEORY) and decay into $\Pgt\Pgt$. The gluon fusion
+production mode will also be referred to as gg$\phi$, and the b-associated production
+mode will be referred to as bb$\phi$. In 
+addition to the upper limits on cross--section times branching ratio of these two processes, 
+the results are interpreted in MSSM benchmark scenarios and 2D likelihood
 scans of the two production modes are performed. A very similar analysis
@@
 will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.
-The results of the 2015 analysis will be shown, in addition to a combination of the 2015 and 2016 datasets.
 
 For the analysis described in this chapter, as well as the 2015 analysis not detailed
-here, I was responsible for optimisation of object selection and categorisation,
+here, I was responsible for all stages of the analysis. This includes optimisation of object selection and categorisation,
 as well as studies of background methods for the \mutau, \etau and \tautau channels,
@@
 samples and part of the W+$\gamma$ background included in the \emu channel only.
-\Wjets and \Zll backgrounds are generated with the \ac{MadGraph 5} \cite{madgraph}
+\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
 matrix element generator. Both samples containing a mixture
@@
 are generated. These exclusive samples increase the available number of
-background events with higher jet multiplicities.  Part of the W+$\gamma$ background
-samples are also generated with this event generator.
-%note LO samples used because to get same number of effective
+background events with higher jet multiplicities. %note LO samples used because to get same number of effective
 %events would need to generate more NLO samples
@@
 fractions of events with each jet multiplicity.
+\texttt{MadGraph 5} 
+is also used to generate part of the W+$\gamma$ background
+samples.
 
@@
 
-Based on this information, for the analysis on the 2015 dataset the selection was optimised
-for mass points around 700-800 GeV. For the analysis on the 12.9 fb$^{-1}$ collected
-in the first half of 2016, the selection was further loosened by 10 GeV in \mT~cut
-and one step in hadronic tau isolation working point, to obtain the medium isolation working
-point selection combined with a selection on \mT$<40$ GeV.
+The selection was then optimised for mass points of around 1 TeV to obtain a combination
+of the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
 
@@
 The tight working point of the isolation discriminator is chosen to optimise the sensitivity
-of this channel for higher masses. INSERT PLOT
+of this channel for higher masses, while retaining the second best senstivity in the intermediate
+mass range, as seen in figure \ref{fig:mssm_tauid_tt}.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./MSSM/Figures/ggh_tt_isolation.png}
+\end{center}
+\caption{Expected upper limits for gg$\phi$ process in the \tautau channel, using the 
+loose (green), medium (red), tight (blue, very tight (black) and very very tight (gold)
+working point. REMAKE?}
+\label{fig:mssm_tauid_tt}
+\end{figure}
 
@@
 
-\section{Combination of 2015 and 2016 datasets}
+\chapter{Combination of MSSM analyses}
 \label{sec:mssm_combination}
-The results outlined in the previous section, for the analysis
-on a dataset corresponding to an integrated luminosity of 12.9 fb$^{-1}$
-at a centre-of-mass energy of 13 TeV, collected during the 2016 running period
-of the \ac{LHC}, can be combined with the results from a very similar analysis
-performed on 2.3 fb$^{-1}$ collected at 13 TeV during 2015, detailed
-in reference \cite{CMS-PAS-HIG-16-006}. This combination should be able
-to improve slighty on the limits set by the 2016 analysis. Because the 
-analysis on the 2015 dataset is very similar to the 2016 analysis it 
+The results of the search for MSSM \AHtotautau on a dataset
+corresponding to an integrated luminosity of 12.9 fb$^{-1}$, collected during the
+first half of 2016 and thus referred to as `2016 analysis', can be combined 
+with a previous search. This previous analysis, very similar to the 2016 analysis,
+was performed on a dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
+collected during 2015 (`2015 analysis'), detailed in reference \cite{CMS-PAS-HIG-16-006}.
+By combining the two analyses we should be able to set the most stringent
+limits on the two MSSM production modes, and in the \mA-\tanb~ plane of 
+MSSM benchmark scenarios, available at the time of writing. It is also
+a first step on the way to combining the \AHtotautau analysis with
+searches for charged Higgs bosons or heavy neutral Higgs bosons in 
+other final states.
+
+Because the 2015 analysis is very similar to the 2016 analysis it 
 is not described in detail, however, the results will
@@
 
-\subsection{Results from 2015 analysis}
+\section{Results from 2015 analysis}
 \label{sec:mssm_combination_2015}
@@
 
-\subsection{Combination procedure}
+\section{Combination procedure}
 \label{sec:mssm_combination_procedure}
@@
 physics reach. To do this correctly the correlations between
-nuisance parameters in 2015 and 2016 need to be taken into account.
+nuisance parameters in the 2015 and 2016 analyses need to be taken into account.
+The only truly correct way to establish the correlations is to perform
+dedicated studies into them. In many cases such studies would be 
+unfeasible to perform, or it would not be clear how to approach the 
+problem in the first place.
+
+Even without performing such studies, a good estimate of what the correlation
+should be can usually be based on reasoning. With a small number of 
+exceptions this is what has been done for this combination.
 %Strictly, studies into the underlying correlations between
@@
 analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
+The third column gives the motivation for the chosen correlation.
 
@@
 
-To get a better idea of which analysis
-is driving the sensitivity of the combination, we should consider the comparison
+To get a better picture of how the sensitivity of the individual analyses compares
+with the combination, we should consider the comparison
 of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
@@
 there is a larger improvement in analysis sensitivity from combining the two analyses.
-This is expected since the analysis on the 2016 dataset used a slightly different
+This behaviour is expected since the analysis on the 2016 dataset used a slightly different
 selection that made the analysis more optimal at masses above 800 GeV,

### 2017-01-16 Objects/Objects.tex
Adding more MSSM text
Addressing Gavins comments on object reconstruction chapter

@@
 describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
-all stable particles. This is of particular importance for the reconstruction of jets, missing transverse
+all stable particles. \ac{PF} is of particular importance for the reconstruction of jets, missing transverse
 energy and hadronic taus as detailed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
@@
 inner tracker the
-\ac{CTF} algorithm is used. This algorithm performs four steps.
+\ac{CTF} algorithm is used \cite{cms-trk-algos}. This algorithm performs four steps.
 First, initial estimates of the parameters of the trajectory are given by track seeds, 
@@
 vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
-vertex position. The analyses presented in chapter [MSSM] take the primary
-vertex of the hard scatter as the reconstructed vertex for which the scalar sum \pT~of
+vertex position. The analyses presented in chapter \ref{chap:mssm} take the primary
+vertex of the hard scatter as the reconstructed vertex for which the scalar sum of the \pT s of
 the associated tracks is largest. This differs from the analysis presented in chapter \ref{chap:hhh},
 where requirements on the quality of the vertex
-fit and the distances between the vertex and the nominal interaction point 
+fit and the distance between the vertex and the nominal interaction point 
 were additionally made.
@@
 of reconstructed primary vertices
-as a function of the scalar sum \pT~of the tracks, 
+as a function of the scalar sum of the \pT s of the associated tracks, 
 measured in 2015 (blue triangles) and 2016 (red squares).
 The resolution improves
-with higher sum \pT~(corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
+with higher scalar sum of the \pT s of the associated tracks, which corresponds to larger numbers of tracks \cite{cms-trk-dp}.}
 \label{fig:objects_tracks_pvres}
@@
 Electrons are reconstructed by combining tracks from 
-the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
+the inner tracker with energy deposits in the \ac{ECAL}.
 A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
@@
 To accurately reconstruct the energy of the electron it is
-important to capture the energies of bremsstrahlung photons, which are spread in the $\phi$ direction
+important to capture the energy of the bremsstrahlung photons, which are spread in the $\phi$ direction
 due to the magnetic field. To achieve this, ``supercluster'' algorithms are used.
 In these algorithms the clustering
-is performed by defining a seed crystal as the crystal containg a local
+is performed by defining a seed crystal as the crystal containing a local
 energy maximum above a certain threshold.
@@
 of approximately $\pm 0.3$ rad. Contiguous clusters are merged into
-superclusters if each cluster has a seed array with energy deposit above a minimum.
+superclusters as long as each cluster satisfies a minimum energy deposit.
 In the endcaps arrays of $5\times 5$ crystals are 
@@
 Due to the radiation of bremsstrahlung photons in the tracker,
-the change in electron track curvature can be large. % and so the \ac{CTF} does
+the change in curvature of the electron track can be large. % and so the \ac{CTF} does
 %not perform optimally. 
@@
 For high--\pT~electrons, the best efficiency is reached
-by the use of an \ac{ECAL}-based track seeding algorithm
+by the use of an \ac{ECAL}-based track seeding algorithm \cite{cms-elereco-run1}
 which extrapolates the position and energy of the supercluster to the first
@@
 on the electron isolation can reduce these backgrounds even further.
-Different isolation definitions are used in \ac{CMS}, for the analyses presented
-in later chapters a combined relative isolation variable is defined as \cite{SMHtautauCMS}:
+Different isolation definitions are used in \ac{CMS}. The default, which is
+used for the analyses presented in later chapters, is a combined relative isolation variable
+defined as \cite{SMHtautauCMS}:
 \begin{equation}\label{eqn:electron_reliso}
@@
 \end{equation}
-Where the \pT~and \ET~sums are taken within a cone in $\eta - \phi$ around the direction
+where the \pT~and \ET~sums are taken within a cone in $\eta - \phi$ around the direction
 of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
@@
 
-For the analysis presented in chapter chapter [MSSM] ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
+For the analysis presented in chapter \ref{chap:mssm} ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
 These requirements include:
@@
 \item Reconstruction by either global or tracker muon reconstruction algorithms.
-\item Requirements on track quality, and compatibility between tracker-- and muon system track.
+\item Requirements on track quality, and compatibility between the tracker-- and muon system track.
 \item Selection on the segment compatibility, a weight between 0 and 1 which is a measure of the compatibility
-of a track with the muon track segments in muon stations it has crossed.
+of a track with the muon track segments in the muon stations it has crossed.
 \item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in--flight decays.
@@
 the identification of particles, and determination of position and momentum, as precise
-as possible. All of these particles are then used to build for example jets, \MET and hadronically
-decaying taus.
+as possible. All of these particles are then used to build for example jets, hadronically decaying taus and missing transverse
+energy \MET, defined in equation \ref{eqn:objects_met_corr}.
 
@@
 of one cell in each direction to account for gaps between cells and multiple scattering, the
-track is said to be linked to the calorimeter cluster. The distance is taken as the distance $\Delta R$ 
+track is said to be linked to the calorimeter cluster. The link distance parameter 
+is taken as the distance $\Delta R$ 
 between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
@@
 more granular calorimeter is within the cluster of the less granular calorimeter,
-with the link distance again defined as the $\Delta R$ between two cluster positions.
+with the link distance again defined as the $\Delta R$ between the positions of the two clusters.
 To determine links between charged tracks in the inner tracker and a muon track
@@
 charged particle momentum from the track fit, additional overlapping neutral particles
-are identified. If the difference between tracker momentum and calorimeter
-energies is larger than the total energy registered in associated \ac{ECAL} clusters,
+are identified. If the difference between the tracker momentum and the calorimeter
+energy is larger than the total energy registered in associated \ac{ECAL} clusters,
 a \ac{PF} photon with energy equal to the total \ac{ECAL} energy is created.
@@
 Many quarks and gluons are produced in the collisions at the \ac{LHC},
-fragmenting and hadronising immediately and forming collimated
+fragmenting and hadronising and forming collimated
 jets of particles. These particle jets need to be combined
@@
 on the jet energy and substructure.
-For the analysis presented in chapter [MSSM] a
+For the analysis presented in chapter \ref{chap:mssm} a
 \ac{CHS} technique \cite{cms-jets-run2} is employed, 
@@
 
-The offset correction $\text{C}_{\text{offset}}$ estimates and subtracts the energy
-not associated with the hard scatter. The additional energy this correction
-aims to address includes contributions from electronics noise and pile--up. This is
+The offset correction $\text{C}_{\text{offset}}$ estimates and subtracts the additional energy
+not associated with the hard scatter,
+including contributions from electronics noise and pile--up. This is
 estimated on an event--by--event basis based on the average--\pT~density
 per unit area $\rho$ and the area of the jet $A$ \cite{jet-area}. The factor $\rho$ includes
-constributions from pile--up, electronics noise and the \ac{UE} of the hard interaction, the 
-latter of which should not be corrected for and therefore the average expected contribution
-from the underlying event $\rho_{<\text{UE}>}$ should be subtracted from $\rho$.
+contributions from pile--up, electronics noise and the \ac{UE} of the hard interaction. The 
+last of these should not be corrected for and therefore the average expected contribution
+from the underlying event $\rho_{<\text{UE}>}$ is subtracted from $\rho$.
 
@@
 As jets due to b--quark hadronisation are an important signature
-for many analylses at the \ac{LHC} it is important to identify such jets correctly.
+for many analyses at the \ac{LHC} it is important to identify such jets correctly.
 Because b--hadrons have a relatively long lifetime $\tau \approx 1.5$ ps \cite{pdg-2014},
@@
 the \ac{CSV} algorithm \cite{cms-btag-paper} has been used, with the upgraded
-\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter [MSSM]. 
+\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter \ref{chap:mssm}. 
 The \ac{CSV} algorithm takes \ac{PF} jets with \pT$ > 20$ GeV and $|\eta|<2.4$ as input and 
-defines a likelihood--based discriminator to determine 
+uses a likelihood--based discriminator to determine 
 whether a jet is likely due to b--quark hadronisation or not.
@@
 probability of misidentifying light--flavour jets with \pT $ > 30$ GeV is around
-10\%, 1\% and 0.1 \% respectively \cite{cms-btag-paper}.
+10\%, 1\% and 0.1 \% respectively \cite{cms-btag-paper,cms-btag-run2}.
 
@@
 response for hadronic particles.
-Therefore, the increase the accuracy of the \MET~measurement the jet energy corrections should be propagated as
+Therefore, to increase the accuracy of the \MET~measurement the jet energy corrections should be propagated as
 \begin{equation}\label{eqn:objects_met_corr}
@@
 algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
-chapter [MSSM]. This algorithm computes a correction to the hadronic
+chapter \ref{chap:mssm}. This algorithm computes a correction to the hadronic
 recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
@@
 \caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
-\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV. The \MET~
+\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=$\mbox{13 TeV}. The \MET~
 values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
@@
 In the process of calculating the corrections to the hadronic recoil using the MVA \MET~
-algorithm, the significance of the MVA \MET~ is also estimated, providing an event--by--event
+algorithm, an event--by--event
 estimator of the likelihood that the \MET~ is due to unseen objects rather than induced
-by mismeasurement of jet energy \cite{cms-met-run1}.
+by mismeasurement of jet energy is also estimated \cite{cms-met-run1}.
 %Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
@@
 and neutrinos. For the analyses
-presented in chapters \ref{chap:hhh} and [MSSM] it is measured in \Zmm events, where no neutrinos
+presented in chapters \ref{chap:hhh} and \ref{chap:mssm} it is measured in \Zmm events, where no neutrinos
 are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
@@
 As table \ref{tab:hadronic_tau_decays}
-shows, 60\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a large
+shows, 62\% of hadronic tau decays contain at least one \Ppizero in the final state. There is a large
 probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays will convert to
@@
 &\Delta \eta  = 0.2\cdot p_{\text{T},\Pe/\Pphoton}^{-0.66} + 0.2\cdot p_{\text{T,strip}}^{-0.66} \\
-&\Delta \phi  = 0.35\cdot p_{\text{T},\Pe/\Pphoton}^{-0.71} + 0.35\cdot p_{\text{T,strip}}^{-0.71}\\
+&\Delta \phi  = 0.35\cdot p_{\text{T},\Pe/\Pphoton}^{-0.71} + 0.35\cdot p_{\text{T,strip}}^{-0.71},\\
 \end{split}
 \end{equation}
-Where $p_{\text{T},\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
+where $p_{\text{T},\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
 and $p_{\text{T,strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
@@
 compatible with a certain decay mode if the selection listed below is satisfied. The charged particles
-and strips are required to be within the signal cone $R_{\text{signal}} = \frac{3.0}{p_{\text{T}}[GeV]}$, always
+and strips are required to be within the signal cone $R_{\text{sig}} = \frac{3.0}{p_{\text{T}}[GeV]}$, always
 required to be $0.05 < R_{\text{sig}} < 0.1$.
@@
 where the first term denotes the sum of the transverse momenta of all charged particles not part
-of the identified hadronic tau. Only particles with \pT $> 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the 
+of the identified hadronic tau. Only particles with \pT $> 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the 
 direction of the hadronic tau are taken into account and the charged particle tracks are required to be compatible with having
 originated from the $\Pgt_{h}$ production vertex within $d_Z < 0.2$ cm. The second term denotes the sum
-of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone $\Delta R = 0.5$ centred around the direction
+of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
 of the hadronic tau. The effect of pile--up on this term is accounted for by subtracting the sum of the momenta of charged
@@
 \subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
-\subfloat[Anti-e discriminator efficiency]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
-\subfloat[Anti-e discriminator fake rate]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
+\subfloat[Real $\Pgt_{h}$ efficiency for anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
+\subfloat[$\Pe\rightarrow\Pgt_{h}$ fake rate for the anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
 \end{center}
@@
 efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
-from the MVA-based discriminator is lower than from the cut-based discriminator. (b) the real $\Pgt_{h}$ identification
-efficiency for different working points of the anti-electron discriminator, as a function of $\Pgt_{h}$ \pT, and (c)
+from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real $\Pgt_{h}$ identification
+efficiency for different working points of the anti-electron discriminator, as a function of the \pT~of the $\Pgt_{h}$, and (c)
 the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
-\Pe \pT.}
+the \pT~of the \Pe.}
 \label{fig:tau_efficiency}
 \end{figure}
-The anti--muon discriminator is a cut-based discriminant, for which two working points are provided:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
-Otherwise it passes the discriminator.
-\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
-\end{itemize}
+The anti--muon discriminator is a cut-based discriminant, for which a loose and a tight working
+point are provided. It is based on variables such as the number of track segments found in various
+parts of the muon system around the direction of the $\Pgt_{h}$, and comparisons of calorimeter energy
+with the momentum of the leading $\Pgt_{h}$ track.
+%\begin{itemize}
+%\setlength{\itemsep}{-\baselineskip}
+%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
+%Otherwise it passes the discriminator.
+%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
+%\end{itemize}

### 2017-01-16 MSSM/MSSM.tex
Adding a few more figs to MSSM chapter

@@
 decaying to a pair of \Pgt leptons will be discussed. The results presented
-here correspond to those from an analysis peformed on 12.9 fb$^{-1}$ collected
+here correspond to those from an analysis peformed on a dataset corresponding to
+an integrated luminosity of 12.9 fb$^{-1}$ collected
 at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
@@
 \begin{split}
-N_{\text{data}}^{SS, \text{high } m_{\text{T}}} - N_{\text{other}}^{SS,
-\text{high } m_{\text{T}}} & =
-N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} + N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
-N_{\text{data}}^{OS, \text{high } m_{\text{T}}} - N_{\text{other}}^{OS,
-\text{high } m_{\text{T}}} & = N_{\text{QCD}}^{OS, \text{high } m_{\text{T}}} +
-N_{W}^{OS, \text{high } m_{\text{T}}} \\
-& = R_{\text{QCD}}^{OS/SS}\cdot N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} +
-R_{W}^{OS/SS} \cdot N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
-\Rightarrow N_{W}^{SS, \text{high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{OS,
-\text{high } m_{\text{T}}}  - N_{\text{other}}^{OS, \text{high } m_{\text{T}}}  -
-R_{\text{QCD}}^{OS/SS}\cdot(N_{\text{data}}^{SS, \text{high } m_{\text{T}}}  -
-N_{\text{other}}^{SS, \text{high } m_{\text{T}}} )}{R_{W}^{OS/SS} -
-R_{\text{QCD}}^{OS/SS}} ,
+N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
+ high } m_{\text{T}}} & =
+N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} + N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
+N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
+ high } m_{\text{T}}} & = N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
+N_{\text{W}}^{\text{OS, high } m_{\text{T}}} \\
+& = R_{\text{QCD}}^{\text{OS/SS}}\cdot N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} +
+R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
+\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{\text{OS,
+ high } m_{\text{T}}}  - N_{\text{other}}^{\text{OS, high } m_{\text{T}}}  -
+R_{\text{QCD}}^{\text{OS/SS}}\cdot(N_{\text{data}}^{\text{SS, high } m_{\text{T}}}  -
+N_{\text{other}}^{\text{SS, high } m_{\text{T}}} )}{R_{\text{W}}^{\text{OS/SS}} -
+R_{\text{QCD}}^{\text{OS/SS}}} ,
 \end{split}
@@
 
-where $R_{W}^{OS/SS}$ is the ratio between opposite-sign and same-sign \Wjets events
-and $R_{QCD}^{OS/SS}$ the ratio between opposite-sign and same-sign QCD events. Using 
+where $R_{\text{W}}^{\text{OS/SS}}$ is the ratio between opposite-sign and same-sign \Wjets events
+and $R_{\text{QCD}}^{\text{OS/SS}}$ the ratio between opposite-sign and same-sign QCD events. Using 
 equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
-opposite-sign, high \mT~region is given by $R_{W}^{OS/SS}\cdot N_{W}^{SS,\text{high} m_{T}}$. 
+opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS,high} m_{T}}$. 
 This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:
@@
 \begin{equation}\label{eqn:wjets_os_norm}
-N_{W}^{OS,\text{low} m_{T}} = \frac{N_{W,MC}^{OS,\text{low} m_{T}}}{N_{W,MC}^{OS,\text{high} m_{T}}}\cdot R_{W}^{OS/SS} \cdot N_W^{SS,\text{high }m_{T}},
+N_{\text{W}}^{\text{OS, low} m_{T}} = \frac{N_{\text{W,MC}}^{\text{OS, low} m_{T}}}{N_{\text{W,MC}}^{\text{OS, high} m_{T}}}\cdot R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high }m_{T}},
 \end{equation}
@@
 
-The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
-$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
-The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
-control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{W}^{OS/SS}$ is 
-taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
+The use of the method presented relies on knowledge of $R_{\text{W}}^{\text{OS/SS}}$,
+$R_{\text{QCD}}^{\text{OS/SS}}$, and on these two ratios not being too similar to each other. 
+The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti--isolated
+control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
+taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
 is close to 1.
@@
 estimated in the 1-jet selection, multiplied by an extrapolation factor 
-$\frac{N_{W,MC}^{OS,\text{low } m_{T},\text{b-tag category}}}{N_{W,MC}^{OS,\text{low }m_{\text{T}},\text{1-jet selection}}}$ ADD FIGURES
+$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$
 
@@
 \label{sec:mssm_bkgs_etmt_qcdosss}
-The ratio of opposite--sign to same--sign QCD events, $R_{QCD}^{OS/SS}$ is measured
+The ratio of opposite--sign to same--sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$ is measured
 in two anti-isolated sidebands by performing a fit to the distribution of the
@@
 opposite-sign events. The QCD template, which is taken from same--sign events 
-assuming $R_{QCD}^{OS/SS} = 1$ is treated as the signal, and a binned maximum
+assuming $R_{\text{QCD}}^{\text{OS/SS}} = 1$ is treated as the signal, and a binned maximum
 likelihood fit to the QCD signal strength is performed while allowing the other
 backgrounds to float within reasonable normalisation uncertainties. The
-resulting best fit value of the signal strengh parameter is taken as $R_{QCD}^{OS/SS}$.
+resulting best fit value of the signal strengh parameter is taken as $R_{\text{QCD}}^{\text{OS/SS}}$.
 Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\mu}<0.25$ and $0.1<I_{\text{rel}}^{e}<0.2$)
 and one further away ($0.25<I_{\text{rel}}^{\mu}<0.5$ and $0.2<I_{\text{rel}}^{e}<0.5$). The results of the fits,
-performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_far}
+performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_mtfar}
 for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
-$R_{QCD}^{OS/SS}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
+$R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
 Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
@@
 The uncertainty on the ratio is increased for the b-tag category to cover the differences.
-The uncertainties are already large enough to cover differences between the pre-categorisation $R_{QCD}^{OS/SS}$ and the
-fits as performed in the no b-tag category. So $R_{QCD}^{OS/SS}$ in the \mutau channel is taken to be
+The uncertainties are already large enough to cover differences between the pre-categorisation $R_{\text{QCD}}^{\text{OS/SS}}$ and the
+fits as performed in the no b-tag category. So $R_{\text{QCD}}^{\text{OS/SS}}$ in the \mutau channel is taken to be
 1.18 in both the b-tag and the no b-tag category, with a 60\% uncertainty in the b-tag category and a 4\% uncertainty in the no b-tag category.
-In the \etau channel $R_{QCD}^{OS/SS}$ is taken to be 1.02 with a 60\% uncertainty in the b-tag category and a 12\% uncertainty
+In the \etau channel $R_{\text{QCD}}^{\text{OS/SS}}$ is taken to be 1.02 with a 60\% uncertainty in the b-tag category and a 12\% uncertainty
 in the no b-tag category.
@@
 is 1.180$\pm$0.044.}
-\label{fig:mssm_qcdossss_mtnear}
+\label{fig:mssm_qcdosss_mtnear}
 \end{figure}
@@
 is 1.184$\pm$0.035.}
-\label{fig:mssm_qcdossss_mtfar}
+\label{fig:mssm_qcdosss_mtfar}
 \end{figure}
@@
 is 1.015$\pm$0.059.}
-\label{fig:mssm_qcdossss_etnear}
+\label{fig:mssm_qcdosss_etnear}
 \end{figure}
@@
 is 1.127$\pm$0.045.}
-\label{fig:mssm_qcdossss_etfar}
+\label{fig:mssm_qcdosss_etfar}
 \end{figure}
@@
 \begin{equation}\label{eqn:wjets_qcdsub}
-N_{W,SS SR} = \frac{N_{MC,SS SR}}{N_{MC,SS high mT}}N_{W,SS high mT}
+N_{\text{W,SS SR}} = \frac{N_{\text{MC,SS SR}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}
 \end{equation}
@@
 \begin{equation}\label{eqn:tautau_qcd}
-R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{obs}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{obs}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
+R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{\text{obs}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{obs}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
 \end{equation}
-
 So this takes the ratio between the observed data with other
@@
 This sideband is slightly further away from the signal region than the
-'tight--medium' sideband INSERT FIGURE. The bias from using this looser
-sideband has been assessed and has a less than 1$\sigma$ effect.
-FIXME THIS ISN'T VERY USEFUL INFO!
+`tight--medium' sideband. %The bias from using this looser
+%sideband has been assessed and has a less than 1$\sigma$ effect.
+%FIXME THIS ISN'T VERY USEFUL INFO!
 
@@
 signals and to the \Ztautau background.
-\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
+\subsubsection*{High-\pT~$\Pgt_{h}$ ID efficiency}
 An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
 is applied to account for the extrapolation from the tau ID efficiency
-measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s. This
-uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels
-\subsubsection*{Top quark \pT~ reweighting}
+measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s \cite{CMS-PAS-HIG-16-037}. This
+uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
+The shape difference between the nominal, up- and down- shapes for this uncertainty in the no b-tag category
+of the \tautau channel can be seen for a high-mass signal sample in figure \ref{fig:mssm_highpttauid_shapes}a and
+for the \Ztautau background in figure \ref{fig:mssm_highpttauid_shapes}b. Because the \Ztautau background
+has much softer hadronic taus than the high-mass signal sample, the shape-altering effect of this uncertainty
+is much smaller.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$ signal at $m_{\phi} = 3.2$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
+\subfloat[\Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ZTT.pdf}}
+\end{center}
+\caption{Shape-altering effect of the high \pT~tau ID uncertainty in the no b-tag category of the
+\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect is much
+larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
+\pT~than the \Ztautau sample.}
+\label{fig:mssm_highpttauid_shapes}
+\end{figure}
+\subsubsection*{Top quark \pT~reweighting}
 To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape

### 2017-01-17 MSSM/MSSM.tex
Adding most of own comments on MSSM chapter

@@
 decaying to a pair of \Pgt leptons will be discussed. The results presented
-here correspond to those from an analysis peformed on a dataset corresponding to
-an integrated luminosity of 12.9 fb$^{-1}$ collected
-at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
+here correspond to those from an analysis peformed on a dataset collected
+during the first half of the 2016 p--p running period of the \ac{LHC}. This dataset
+corresponds to an integrated luminosity of 12.9 fb$^{-1}$, and the analysis is
 detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
@@
 model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
-production in the two modes (see THEORY) and decay into $\Pgt\Pgt$. The gluon fusion
-production mode will also be referred to as gg$\phi$, and the b-associated production
-mode will be referred to as bb$\phi$. In 
-addition to the upper limits on cross--section times branching ratio of these two processes, 
-the results are interpreted in MSSM benchmark scenarios and 2D likelihood
-scans of the two production modes are performed. A very similar analysis
-was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
-As it is so similar to the analysis performed on the 2016 dataset it
-will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.
+production in the gluon-fusion (gg$\phi$) and b-associated (bb$\phi$) production 
+modes (see THEORY) and decay into $\Pgt\Pgt$. 
+In addition to the upper limits on cross--section times branching ratio of these two processes, 
+the results are interpreted in MSSM benchmark scenarios.
+A very similar analysis, not described in detail here,
+was performed on a dataset corresponding to 2.3 fb$^{-1}$ collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period.  
+More information can be found in reference \cite{CMS-PAS-HIG-16-006}.
 
 For the analysis described in this chapter, as well as the 2015 analysis not detailed
-here, I was responsible for all stages of the analysis. This includes optimisation of object selection and categorisation,
+here, I was responsible for all stages of the analysis. This included optimisation 
+of object selection and categorisation,
 as well as studies of background methods for the \mutau, \etau and \tautau channels,
-evaluation of systematic uncertainties in all four channels, and for producing
+evaluation of systematic uncertainties in all four channels, and production of
 the statistical results, including model--dependent interpretations.
@@
 energy of 13 TeV during the first half of
-the 2016 p--p running period of the \ac{LHC}. Section
-\ref{sec:mssm_combination} includes the combination of this
-dataset with a dataset collected during the 2015 p--p running
-period of the \ac{LHC}. This dataset corresponds to an integrated
-luminosity of 2.3 fb$^{-1}$ collected at $\sqrt{s} = 13$ TeV.
+the 2016 p--p running period of the \ac{LHC}. %Section
+%\ref{sec:mssm_combination} includes the combination of this
+%dataset with a dataset collected during the 2015 p--p running
+%period of the \ac{LHC}. This dataset corresponds to an integrated
+%luminosity of 2.3 fb$^{-1}$ collected at $\sqrt{s} = 13$ TeV.
 
@@
 production processes of $\PHiggs/\PHiggsps$ were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
-These samples were produced in a range of masses between 90 GeV and 3.2 TeV.
+These samples were produced for a range of masses between 90 GeV and 3.2 TeV.
 This range is slightly wider than the range in which MSSM Higgs sector
 benchmark computations are available, 90 GeV -- 2 TeV, and 
-improves on the mass range, up to 1 TeV, studied during Run 1 in the context of BSM Higgs searches.
+improves on the mass range of 90 GeV to 1 TeV that was studied during Run 1 in the context of BSM Higgs searches.
 SM Higgs signal samples are used for the interpretation of the analysis results in 
@@
 
-\ttbar- and single-top background samples are generated using \texttt{Powheg},
+single-top and \ttbar background samples are generated using \texttt{Powheg},
 with \texttt{MadGraph5\_aMC\@NLO} \cite{amcnlo} used for the generation of di--boson background
-samples and part of the W+$\gamma$ background included in the \emu channel only.
+samples and part of the W+$\gamma$ background, which is included in the \emu channel only.
 \Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
@@
 
-Parton showering and hadronisation are modelled using \texttt{PYTHIA 8} for all 
-samples. Minimum--bias events generated with \texttt{PYTHIA 8} are
+Parton showering and hadronisation are modelled using \texttt{PYTHIA 8.1} for all 
+samples, and  minimum--bias events generated with \texttt{PYTHIA 8.1} are
 added to all \ac{MC} samples to model additional interactions. A reweighting
 is then applied to the \ac{MC} samples to make the pile--up distribution match
-that observed in data.
-
-%THIS SECTION SHOULD JUST GO INTO THE DETAILED EVENT SELECTION
-%SECTION
-%\section{Optimisation of object selection}
-%\label{sec:mssm_baseline_opt}
-%At the start of Run 2 of the \ac{LHC} an effort was first made to
-%optimise the default, \textit{baseline} di-\Pgt pair selection. This provides
-%a common starting point for all $\PHiggs \rightarrow \Pgt\Pgt$ analyses, on
-%top of which additional selections can be made for specific analyses such
-%as the MSSM \AHtotautau analysis presented in this chapter.
-
-%\subsection{Electrons and muons}
-%\label{sec:mssm_baseline_opt_elemu}
-%For the optimisation of the baseline selection of
-%electrons and muons the main optimisable
-%selection is the choice of isolation discriminator and
-%of
+the pile--up distribution observed in data.
 
@@
 and how it was optimised, is given. More detailed information
-on how the used objects used are reconstructed, 
+on how the objects used are reconstructed, 
 and a more in--depth description of the identification criteria, 
@@
 The basis of the event selection is the selection of \mutau, \etau,
-\tautau and \emu pairs following the requirements described
+\tautau and \emu pairs by the requirements described
 in the following subsections. After applying trigger
 requirements, identification criteria and kinematic cuts
-more than one possible candidate pair can exist. In this
-case the pair is chosen as follows:
+more than one possible candidate pair can exist. If this
+is the case for an event, the pair is chosen as follows:
 \begin{itemize}
@@
 if there are muons and electrons, other than those in the selected pair,
-with \pT $>10$ GeV and passing loose ID and isolation requirements.
+with \pT~$>10$ GeV and passing loose ID and isolation requirements.
 This also reduces backgrounds from \WZ events. 
@@
 reduced in the \etau channel by rejecting events
-where an opposite--sign pair of electrons of \pT $>15$ GeV
+where an opposite--sign pair of electrons of \pT~$>15$ GeV
 and passing very loose ID and isolation requirements can be formed. 
@@
 muon and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
-The minimum \pT of the muon is required to be 23 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+The minimum \pT~of the muon is required to be 23 GeV, with $|\eta| < 2.1$. %due to trigger conditions
 Additional ``medium'' identification requirements are placed on the muon, in addition
@@
 the impact parameters $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm. The muon is also required
-to be isolated, with a selection on its relative isolation variable calculated with a cone size of 0.4 of $< 0.15$.
-
-The hadronic tau needs to have a \pT greater than 30 GeV, $|\eta|<2.3$,
+to be isolated, with $I_{\text{rel}}^{\mu} < 0.15$, where the isolation variable is calculated using
+a cone size of $\Delta R = 0.4$.
+
+The hadronic tau needs to have a \pT~greater than 30 GeV, $|\eta|<2.3$,
 is required to be reconstructed by the HPS algorithm and to pass the medium
@@
 The selection on the muon's relative isolation is chosen after comparing
-the performance of several isolation variables at different
+the performance of several isolation variables, using different selections.
 relative isolation values. This was based on a simple \mutau channel
-event selection as described above, with varying isolation variables.
+event selection as described above, only varying the isolation requirements.
 The selection was optimised based on two figures of merit, both of
@@
 
-Different isolation variables were studied over a range of values
-to cut at. In addition to the $\Delta\beta$ corrected isolation variable analogous
+Different isolation variables were studied over a range of maximum
+values. The $\Delta\beta$ corrected isolation variable analogous
 to the one given for electrons in equation \ref{eqn:electron_reliso} with 
-isolation cone sizes in $\Delta R$ of 0.3 and 0.4, a very similar
-variable which does not just consider charged \ac{PF} hadrons, but
-also electrons and muons in the isolation sum is considered. This
+isolation cone sizes in $\Delta R$ of 0.3 and 0.4 was studied. In addition
+to this a very similar
+variable, which does not just consider charged \ac{PF} hadrons but
+also electrons and muons in the isolation sum, is considered. This
 variable is also studied for both cone sizes of 0.3 and 0.4. Finally,
-a relative isolation variable based solely on the \pT of tracks from the primary
+a relative isolation variable based solely on the \pT~of tracks from the primary
 vertex,
@@
 \ref{fig:mssm_selection_mt_muons}b. From the fact that both figures of merit do not
-vary so much with different isolation cuts and different variables we can see that this analysis
-is not so sensitive to fake,nonisolated muons. The choice of isolation variable is therefore
+change so much with varying isolation requirements we can see that this analysis
+is not so sensitive to fake, nonisolated muons. The choice of isolation variable is therefore
 driven mostly by simplicity and consistency with other \ac{CMS} analyses.
@@
 the best--fit value of a maximum--likeihood fit to the \Ztautau signal strength,
-for various cut values of the $\Delta\beta$--corrected
+for various selections of the $\Delta\beta$--corrected
 isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
@@
 the gluon--gluon fusion production process, at a mass $m_{\phi} = 160$ GeV, with
-figures \ref{fig:mssm_selection_mt_taumt}b,c and d showing this upper limit at $m_{\phi} = 900$ GeV,
-$m_{\phi} = 1600$ GeV and $m_{\phi} = 2900$ GeV respectively. From these figures
-we can observe that looser selections are preferred for higher masses. This can be
+figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit at $m_{\phi} = 2.9$ TeV.
+Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
+tau isolation working point selection on both the gg$\phi$ and bb$\phi$ production processes. From these figures
+we can observe that looser selections are preferred for higher masses. This behaviour can be
 explained by considering the function of each of the selections. Tightening the hadronic
@@
 to reduce an already low background.
-
 \begin{figure}[h!]
@@
 \subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
-\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900_range12.pdf}}~\\
-\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
-\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
+%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
 \end{center}
@@
 of \mT~ cut from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
-for $m_{\phi}$ = 160 GeV (a), 900 GeV (b), 1600 GeV (c) and 2900 GeV (d). The most optimal combination of \mT~selection and 
-hadronic tau isolation working point varies by mass point, with looser selections preferred for higher masses.}
+for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
+hadronic tau isolation working point varies, with looser selections preferred for higher mass.}
 \label{fig:mssm_selection_mt_taumt}.
 \end{figure}
-
-The selection was then optimised for mass points of around 1 TeV to obtain a combination
-of the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
-
-The choice of the hadronic tau \pT selection is driven by the effect on the low mass region:
-raising the \pT selection by 10 GeV from the minimum of 20 GeV does not affect the sensivity
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
+\end{center}
+\caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
+(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
+at tight working point and \mT$<30$ GeV in green, medium working point and \mT$<40$ GeV in red,
+loose working point and \mT$<50$ GeV in blue and very loose working point and \mT$<60$ GeV in black. Loosening
+the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
+degrades them at low mass.}
+\label{fig:mssm_gradcuts_mt}
+\end{figure}
+The selection was then optimised for mass points of around 1 TeV, which leads to 
+the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
+
+The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
+raising the \pT~selection by 10 GeV from the minimum of 20 GeV does not affect the sensivity
 of the analysis for high mass points, while recovering some of the loss of loosening 
 tau isolation working point and \mT~cut. The reason for this is that when using \pT$>30$ GeV 
-fewer background events are selected. The effect of the increased hadronic tau \pT~ cut on the 
-upper limits for the gg$\phi$ production process
+fewer background events are selected. The effect of the increased hadronic tau \pT~selection on the 
+upper limits for the gg$\phi$ production process is shown
 in figure \ref{fig:mssm_tauptcut}a, and on the bb$\phi$ production process
 in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the gg$\phi$ limits
-obtained by increasing the \pT~cut is sizeable, for bb$\phi$ events the effect is much
+obtained by increasing the \pT~selection is sizeable, for bb$\phi$ events the effect is much
 less pronounced.
@@
 limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
-hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
+hadronic tau \pT~selection of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
 circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
-the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
+the gg$\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
 the effect on the bb$\phi$ production process is less pronounced.}
@@
 For selection of events in the \etau channel, the first step is
-a trigger that only requires an electron at \ac{L1}. At the \ac{HLT}
-loose identification and isolation criteria are then required.
+a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
+criteria are made on the electron at the \ac{HLT}.
 
@@
 electron and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
-The minimum \pT of the electron is required to be 26 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+The minimum \pT~of the electron is required to be 26 GeV, with $|\eta| < 2.1$. %due to trigger conditions
 This electron has to be consistent with having originated from the primary vertex, which
-is achieved by requiring impact parameters $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and it
+is achieved by requiring the impact parameters to satisfy $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and it
 is required to pass additional identification criteria. A selection on the MVA identification, which
 selects electrons from \Zee events with 80\% efficiency, is used. In addition the
-electron needs to be isolated. The relative isolation, calculated with a cone size of 0.3, is required to be $< 0.1$.
-
-The hadronic tau is required to have a \pT greater than 30 GeV, $|\eta|<2.3$,
+electron needs to be isolated, $I_{\text{rel}}^{\Pe} < 0.1$, with the relative isolation variable calculated with a cone size of 0.3.
+
+The hadronic tau is required to have a \pT~greater than 30 GeV, $|\eta|<2.3$,
 and is required to be reconstructed by the HPS algorithm and to pass the medium
@@
 
-Just like for muons, it was found that the analysis is not highly sensitive
-to the choice of electron isolation variable and selection, yet an effort
-is made not to use a suboptimal selection.
-A topological selection on the \mT~ variable is also made in this channel to reject \Wjets events. 
-The used value of \mT $< 50$ is obtained by performing a 2D optimisation where the \mT~ selection
+Analogously to the muons, it was found that the analysis is not highly sensitive
+to the choice of electron isolation variable and selection.
+A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
+The used value of \mT~$< 50$ is obtained by performing a 2D optimisation where the \mT~selection
 and hadronic tau isolation working point are varied at the same time. The same considerations as
-for the \mutau channel apply. The choice of the hadronic tau \pT~ selection to 30 GeV is
-chosen to recover some of the sensitivity lost at low mass by using looser \mT~ and hadronic
+for the \mutau channel apply, as illustrated in figure \ref{fig:mssm_gradcuts_et}.
+The choice of the hadronic tau \pT~selection of 30 GeV is
+made to recover some of the sensitivity lost at low mass by using looser \mT~and hadronic
 tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.
-
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
+\end{center}
+\caption{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
+(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
+at tight working point and \mT$<40$ GeV in green, medium working point and \mT$<50$ GeV in red,
+loose working point and \mT$<60$ GeV in blue and very loose working point and \mT$<70$ GeV in black. Loosening
+the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
+degrades them at low mass.}
+\label{fig:mssm_gradcuts_et}
+\end{figure}
 \begin{figure}[h!]
@@
 The offline event selection continues by requiring both hadronic taus to be oppositely charged, separated
-by $\Delta R > 0.5$, have pT~ of at least 40 GeV and $|\eta|<2.1$. Both taus need
+by $\Delta R > 0.5$, have \pT~of at least 40 GeV and satisfy $|\eta|<2.1$. Both taus need
 to pass decay mode finding and have originated from the primary vertex, with the impact parameter $d_{z} < 0.2$ cm. 
@@
 of this channel for higher masses, while retaining the second best senstivity in the intermediate
-mass range, as seen in figure \ref{fig:mssm_tauid_tt}.
+mass range, as seen in figure \ref{fig:mssm_tauid_tt} for the gg$\phi$ process.
 \begin{figure}[h!]
@@
 loose (green), medium (red), tight (blue, very tight (black) and very very tight (gold)
-working point. REMAKE?}
+working point.}
 \label{fig:mssm_tauid_tt}
@@
 that both require an electron and muon at \ac{L1} and apply loose ID and
-isolation requirements to these objects at \ac{HLT}. The \pT requirements on
+isolation requirements to these objects at \ac{HLT}. The \pT~requirements on
 the electron and muon are different in the two triggers, thus using the combination of the two
-improves the analysis performance.
-
-The offline requirements to the \emu pair are that the electron 
-and muon are oppositely charged, separated by $\Delta R >$ 0.3. The 
-electron should have a minimum \pT~ of 13 GeV and have $|\eta|< 2.5$. As
+improves the signal efficiency.
+
+The offline requirements on the \emu pair are that the electron 
+and muon are oppositely charged and separated by $\Delta R >$ 0.3. The 
+electron should have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
 in the \etau channel the electron's impact parameters have to 
@@
 is 80\% efficient for electrons in \Zee decays. The electron
-also needs to be isolated, with the relative isolation calculated
-with a cone size of 0.3 being less than $<0.15$.
+also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
+with a cone size of 0.3.
 
@@
 In addition to the kinematic requirements the muon must
-pass the medium identification criteria and be isolated with the relative
-isolation, calculated with a cone size of 0.4, required to be less than 0.15.
-
-Because a combination of triggers is used, the object firing
-the higher \pT~ trigger leg needs to have a transverse momentum
+pass the medium identification criteria and be isolated with $I_{\text{rel}}^{\Pgm} < 0.2$,
+where the relative isolation variable is calculated using a cone size of 0.4.
+
+Because a combination of triggers is used, one with electron \pT~$>$ 23 GeV and muon \pT~$>8$ GeV
+and one with muon \pT~$>$ 23 GeV and electron \pT~$>$ 13 GeV, the object firing
+the higher \pT~trigger leg needs to have a transverse momentum
 of at least 24 GeV on top of the requirements already discussed.
-In addition, a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
+
+In addition to the selection described so far,
+ a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
 \begin{align}\label{eqn:mssm_em_dzeta}
 D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
-\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{vis}} + \vec{p}_{\text{T},2}^{\text{vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
-\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{vis}}+\vec{p}_{\text{T},2}^{\text{vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
+\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
+\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
 \end{align}
 
-Thus $D_{\zeta}$ is the difference of the projection of the visible tau decay products plus missing energy \pT+\MET,
-and simply the visible tau decay product \pT on the axis $\vec{\zeta}$. This is the axis that bisects 
-the directions $\vec{p}_{\text{T,1}}^{\text{vis}}$ and $\vec{p}_{\text{T,2}}^{\text{vis}}$
-of the visible decay products in the transverse plane. This selection is illustrated in figure
+Thus $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy \pT+\MET on to 
+the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products on to this axis.
+The axis $\vec{\zeta}$ is the axis that bisects
+the directions $\vec{p}_{\text{T,1}}^{\text{  vis}}$ and $\vec{p}_{\text{T,2}}^{\text{  vis}}$
+of the visible decay products in the transverse plane. This definition is illustrated in figure
 \ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
-for \emu events. The used cut value, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
+for \emu events. The used selection, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
 events. 
@@
 \label{sec:mssm_eventsel_categories}
-As the analysis targets both the gluon--gluon fusion
+As the analysis targets both the gluon--fusion
 and the b--associated production modes of MSSM Higgs
 bosons, two exclusive categories are defined based on the 
-number of b--tagged jets, where a jet is considered b--tagged
+number of b--tagged jets. A jet is considered b--tagged
 if it passes the medium working point of the \ac{CSV}v2 discriminator. 
+The categories are defined as:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal
+\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal.
 \item \textbf{b-tag}: At least 1 b--tagged jet and at most 1 
@@
 mean there will be only one b--tagged jet in the event. The requirement reduces the sizeable \ttbar
-background
+background.
 \end{itemize}
@@
 Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
-in the \mutau channel, with \ref{fig:mssm_cats_mt}b showing
-the number of b--tagged jets in that channel. The gluon--gluon fusion
-signal and bb associated signal are overlaid on these distributions, normalised
+in the \mutau channel, with figure \ref{fig:mssm_cats_mt}b showing
+the number of b--tagged jets in that channel. The gluon--fusion
+and b--associated signals are overlaid on these distributions, normalised
 to 100 times their cross--section times branching ratio at \mA=1 TeV and 
 \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$ scenario. From the distribution of the
-gluon--gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
+gluon--fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
 see that the vast majority of these signal events do not have any b-tagged jets, which
-motivates the choice of the no b-tag category to target this signal. From
-the bb associated signal in the same figure we also see that the majority of bb associated
+motivates the choice of the no b-tag category to target this production mode. From
+the b--associated signal in the same figure we also see that the majority of bb$\phi$
 signal events do not have any b-tagged jets either: either the b-jets in these events 
@@
 \end{center}
-\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon--gluon fusion signal (dashed
-blue line) and bb--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
+\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon--fusion signal (dashed
+blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
 are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
@@
 \label{sec:mssm_mccorrs}
-Because \ac{MC} samples are used for the signal predication, and 
+Because \ac{MC} samples are used for the signal prediction, and 
 to estimate some of the backgrounds, it is important to correct for possible 
@@
 A discrepancy between the track reconstruction efficiency
-in data and \ac{MC} for electrons and muons was found. $\eta$--dependent
-scale factors are applied to mitigate the issue \cite{CMS-PAS-HIG-16-037}.
+in data and \ac{MC} for electrons and muons was found. It is corrected for using $\eta$--dependent
+scale factors \cite{CMS-PAS-HIG-16-037}.
 \subsubsection*{Electron, muon and tau ID and isolation}
@@
 cross trigger legs need to be combined. With one of the cross triggers having a
-\pT~cut of 23 GeV on the muon leg and 12 GeV on the electron leg, and the
-other having a minimum \pT~ of 23 GeV on the electron leg and 8 GeV on the muon
+minimum \pT~ of
+23 GeV on the muon leg and 12 GeV on the electron leg, and the
+other having a minimum \pT~of 23 GeV on the electron leg and 8 GeV on the muon
 leg, the combined efficiency of the two triggers becomes:
@@
 \subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
-The $\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rates
-after applying the anti--electron and anti--muon discriminators are measured
-using a tag--and--probe method with \Zeenog and \Zmmnog events. A scale
-factor, to be applied to \ac{MC} events where the tau is faked by an electron or muon,
-is derived as the ratio between the fake rate in data and the fake rate in \ac{MC} events.
-\subsubsection*{\MET recoil corrections}
-Differences in \MET~ resolution and response between data and \ac{MC} 
+The $\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rates,
+after applying the anti--electron and anti--muon discriminators, are measured
+using a tag--and--probe method with \Zeenog and \Zmmnog events. Scale
+factors, applied to \ac{MC} events where the tau is faked by an electron or muon,
+are derived as the ratio between the fake rate in data and the fake rate in \ac{MC} events.
+\subsubsection*{\MET~recoil corrections}
+Differences in \MET~resolution and response between data and \ac{MC} 
 are accounted for by the application of recoil corrections
-to signal, \Wjets and \Ztautau events. These corrections
-are detailed in section \ref{sec:objects_met_recoilcorr}.
+to signal, \Wjets and \Ztautau events. More detail
+about these corrections is given in section \ref{sec:objects_met_recoilcorr}.
 \subsubsection*{B-tag scale factors}
 To correct for the difference in b--tagging efficiency
-and light jet mis--tagging rates between data and \ac{MC}
-\pT~ and $\eta$ dependent scale factors are derived as 
+and light jet mis--tagging rates between data and \ac{MC} events,
+\pT- and $\eta$-dependent scale factors are derived as 
 described in reference \cite{cms-btag-run2}. They 
@@
 as outlined in equation \ref{eqn:promotedemote}.
-\subsubsection*{Top-quark \pT reweighting}
+\subsubsection*{Top-quark \pT~reweighting}
 A reweighting which was derived during \ac{LHC} Run-1
@@
 improves the data/\ac{MC} agreement in a \ttbar enriched
-control region, as shown in figure \ref{fig:mssm_corrs_toppt}.
+control region.
 \subsubsection*{Drell-Yan shape reweighting}
@@
 do not model the data well for events with high di-lepton
-mass and high Z \pT~, a reweighting is applied to correct for this.
-These weights are derived in bins of $\PZ/Pphoton*$ mass and \pT~
+mass and high Z \pT, a reweighting is applied to correct for this.
+These weights are derived in bins of $\PZ/Pphotonx$ mass and \pT~
 using \Zmm events in data, in such a way that they do not
@@
 This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
-to the \mT~ defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
-The \mTtot~ variable provides good separation between signal and QCD multi--jet events
+to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
+The \mTtot~variable provides good separation between signal and QCD multi--jet events
 in the \etau, \mutau and \tautau channels, and between
@@
 The methods used for background estimation will be described in this
-section. As the \mutau and \etau channels use very similar
-background methods, they are described in the same subsection.
+section.
 
@@
 \label{sec:mssm_bkgs_genmatch}
-For backgrounds estimated from \ac{MC} there are often 
-different sub--processes playing a role that should be
-treated separately by the fit. Taking the \mutau 
+For backgrounds estimated from \ac{MC}, it is possible
+that it is more correct to split a background process
+into different sub--processes that should be treated separately in the fit to data.
+Taking the \mutau 
 channel as an example, a sample of Drell--Yan events
@@
 events can be split into those with genuine taus, and those
-where a jet mimics a hadronic tau.
-
-Dividing events from the same production
-process into sub--samples
-based on generator level information allows
-for a more correct treatment of systematic uncertainties.
-
-To determine the generator-level particle
+where a jet mimics a hadronic tau. In such cases dividing
+events from the same production process into sub--samples
+based on generator information allows for a more correct
+treatment of systematic uncertainties.
+
+To determine the generator--level particle
 that a reconstructed electron, muon, or hadronic tau
@@
 prompt electrons and muons,
-that is electrons and muons not originating from a decay; electrons and muons
+that is electrons and muons not originating from a hadron, tau or muon decay; electrons and muons
 from tau decays; and generator-level hadronic taus. These generator-level
@@
 
-All of these particles are looked for in a cone of $\Delta R = 0.2$ around
-the reconstructed object, and if there are multiple generator-level
-particles within this cone the one nearest the reconstructed particle
-is chosen as the object this particle is matched to. If there are no 
+If there is at least one generator-level object
+within a cone of $\Delta R = 0.2$ around the direction of the reconstructed
+object, the generator-level object nearest the reconstructed particle is chosen
+as the one the reconstructed particle is matched to. 
+If there are no 
 generator-level particles in the cone at all it is said to 
@@
 reconstructed particle is used to perform the splitting
-of background samples, and is indicated where this is used.
+of background samples, where this is used it is indicated.
 
@@
 For all channels, both shape and normalisation of the \Ztautau background 
-is estimated from the Drell-Yan
+are estimated from the Drell-Yan
 \ac{MC} samples described in section \ref{sec:mssm_datasets}.
@@
 b-tag and no b-tag categories of all channels, \Zmm control
-regions are simultaneously fitted. More detail is given in 
+regions are considered in a simultaneous fit with the signal region. More detail is given in 
 section \ref{sec:mssm_sigext_ctrl}.
@@
 control region. The shape of the \Wjets background is taken
-from the \ac{MC} samples, with the QCD shape taken from same--sign
-data with other backgrounds subtracted.
+from the \ac{MC} samples. The QCD shape taken from same--sign
+data, that is events selected in observed data with the opposite charge requirement
+on the di-$\Pgt$ pair inverted but otherwise identical cuts to the signal region. Contributions
+from other backgrounds in this region are subtracted.
 
@@
 some contribution from QCD events in this region. This is visible in 
-figure \ref{fig:mssm_bkgs_wjets_mutau_mt} which shows the \mT~ distribution in the
-\mutau channel, indicating the signal region and the high-\mT~ control region.
+figure \ref{fig:mssm_bkgs_wjets_mutau_mt} which shows the \mT~distribution in the
+\mutau channel, indicating the signal region and the high-\mT~control region.
 
@@
 \end{center}
-\caption{Distribution of the transverse mass \mT~ in the \mutau channel, indicating
-the signal region and the high \mT~ control region \cite{CMS-PAS-HIG-16-037}.}
+\caption{Distribution of the transverse mass \mT~in the \mutau channel, indicating
+the signal region and the high \mT~control region \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_bkgs_wjets_mutau_mt}
@@
 
-Because of this contribution from QCD events in the high \mT~ region we
+Because of this contribution from QCD events in the high \mT~region we
 have, for \mT$>70$ GeV:
@@
 equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
-opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS,high} m_{T}}$. 
-This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:
-
+opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS, high } m_{T}}$. 
+This is extrapolated to the number of \Wjets events in the signal region at low \mT~as:
 \begin{equation}\label{eqn:wjets_os_norm}
@@
 \end{equation}
-
-which is the estimate of the number of \Wjets events in the opposite-sign, high \mT, region
-multiplied by the ratio of the number of \ac{MC} events in the opposite-sign, low \mT~ region to the number of \ac{MC} events in the opposite-sign, high \mT~region. This means that
-the \ac{MC} samples are used to derive a high \mT-to-low \mT extrapolation factor.
+which means the estimate of the number of \Wjets events in the opposite-sign, high \mT, region
+is multiplied by a high \mT-to-low \mT~extrapolation factor determined from the \ac{MC} samples.
 
@@
 resulting best fit value of the signal strengh parameter is taken as $R_{\text{QCD}}^{\text{OS/SS}}$.
-Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\mu}<0.25$ and $0.1<I_{\text{rel}}^{e}<0.2$)
-and one further away ($0.25<I_{\text{rel}}^{\mu}<0.5$ and $0.2<I_{\text{rel}}^{e}<0.5$). The results of the fits,
+Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\Pgm}<0.25$ for the \mutau channel and $0.1<I_{\text{rel}}^{\Pe}<0.2$ for the \etau channel)
+and one further away ($0.25<I_{\text{rel}}^{\Pgm}<0.5$ for the \mutau channel and $0.2<I_{\text{rel}}^{\Pe}<0.5$ for the \etau channel). The results of the fits,
 performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_mtfar}
 for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
-$R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent within 10\% (1\%) in the \etau (\mutau) channel between the two sidebands.
+$R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent between the two sidebands within 10\% (1\%) in the \etau (\mutau) channel.
 Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
@@
 \begin{equation}\label{eqn:wjets_qcdsub}
-N_{\text{W,SS SR}} = \frac{N_{\text{MC,SS SR}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}
+N_{\text{W,SS low }m_{\text{T}}} = \frac{N_{\text{MC,SS low }m_{\text{T}}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}
 \end{equation}
@@
 observed number of events in the same--sign region is multiplied
-by $R_{QCD}^{OS/SS}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
+by $R_{\text{QCD}}^{\text{OS/SS}}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
 to obtain an estimate of the number of QCD events in the signal region.
@@
 of the QCD and \Wjets backgrounds: the same--sign and 
-opposite--sign high \mT~ regions, as well as the same--sign
+opposite--sign high \mT~regions, as well as the same--sign
 low \mT~region. This leads to three control regions used 
@@
 These control regions are included in a simultaneous fit
-with the signal regions to obtain the final results.
-
-\subsection{QCD}
+with the signal regions to obtain the final results. More detail
+can be found in section \ref{sec:mssm_sigext_ctrl}.
+
+\subsection{\texorpdfstring{QCD in the \tautau and \emu channels}{QCD in the tautau and emu channels}}
 \label{sec:mssm_bkgs_qcd}
 This section describes the QCD background
-estimation in the \tautau and \emu channels.
+estimation in the \tautau and \emu channels, which takes a slightly
+different form than in the \mutau and \etau channels.
 
@@
 \label{sec:mssm_bkgs_qcd_tt}
-In the \tautau channel the QCD background is by far the 
-dominant background. The normalisation and shape 
+In the \tautau channel QCD events constitute by far the dominant background.
+The normalisation and shape 
 of this background are estimated from a sideband with loosened 
@@
 In the no b-tag category the sideband used is determined
-by having the tau with highest \pT~ pass the tight working
+by having the tau with highest \pT~pass the tight working
 point of the tau ID discriminator, as in the nominal selection.
-The other hadronic tau in the pair does not pass the tight working point,
-but does pass the medium working point. This sideband is 
+The other hadronic tau in the pair should not pass the tight working point,
+but should pass the medium working point. This sideband is 
 chosen as it is as close to the signal region as possible, and 
@@
 
-An analogous method is used for this estimate in the 
-b-tag category, however, the sideband as used for the 
+The QCD estimate in the b-tag category is derived using an analogous method, 
+ however, the sideband as used for the 
 no b-tag category does not contain enough events to 
@@
 Other backgrounds present in this region are subtracted.
-As for the \etau and \mutau channels, the number of
+Like for the \etau and \mutau channels, the number of
 QCD events with opposite--sign \emu pairs is not
@@
 category than in the no b-tag category, an extra scale factor of 
-1.45/2.20 is applied to the QCD estimate in this category.
+1.45/2.20 is applied to the QCD estimate in the b-tag category.
 
@@
 is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
-the \emu channel, and it is shown in \ref{fig:mssm_corrs_toppt}.
+the \emu channel, and it is shown in figure \ref{fig:mssm_corrs_toppt}.
 Because the 6\%
@@
 two components, one with real taus and 
-one without. The component with real taus is composed
+one without for fitting purposes. The component with real taus is composed
 of \ttbar events in which the hadronic tau is matched
@@
 \end{center}
-\caption{\mTtot~ distribution in the \ttbar enriched control region.
+\caption{\mTtot~distribution in the \ttbar enriched control region.
 The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
@@
 
-\subsection{Di--boson plus single--top}
+\subsection{Other backgrounds}
 \label{sec:mssm_bkgs_other}
@@
 where the hadronically decaying tau originates from a real
-tau, and one where it does not. This is done in a similar
-way as for the \ttbar background
+tau, and one where it does not, for purposes of the fit. This is done in a similar
+way as for the \ttbar background.
 In the \tautau and \emu channels the \Wjets background
@@
 its shape and normalisation are estimated from the
-\ac{MC} samples.
+\ac{MC} samples. In the \emu channel the \PW\Pphoton background
+is also added to the \Wjets background component. For plotting purposes the single-top plus
+di-boson and \Wjets backgrounds are drawn together as the `electroweak' contribution for all channels, even though
+they are considered as separate components in the fit.
 
@@
 uncertainties only affect the yield of a process while shape
-uncertainties affect both the process normalisation, as well as the shape
-of the \mTtot~ distribution. The uncertainties are taken into account 
+uncertainties affect both the process normalisation and the shape
+of the \mTtot~distribution. The uncertainties are taken into account 
 in the final result as described in section \ref{sec:hhh_results_extraction}.
@@
 with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
-channel, and the \ttbar background with a jet faking a hadronic tau. 
+channel, and the \ttbar background without real hadronic taus.
 \subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
@@
 The uncertainties on the jet-energy corrections are applied
-by shifting the jet energy up and down by the \pT~ and $\eta$ dependendent
+by shifting the jet energy up and down by the \pT-and $\eta$-dependendent
 uncertainty, and evaluating the the change in process normalisation in
@@
 Uncertainties on \MET resolution and response are estimated
-by varying the recoil correction paramters within their
+by varying the recoil correction parameters within their
 uncertainty and evaluating the effect on process
-normalisations. The uncertainty amounts to around 2\%
+normalisations. The uncertainty amounts to around 2\%.
 \subsubsection*{Background normalisation}
@@
 fit with the signal region to correct the \Ztautau normalisation
-the Drell-Yan cross section is not applied as an uncertainty. A 3\% (5\%)
-extrapolation uncertainty from \Zmm $\rightarrow$ \Ztautau is applied in 
-the no b-tag (b-tag) category \cite{CMS-PAS-HIG-16-037}.
+the Drell-Yan cross section is not applied as an uncertainty. In the no b-tag (b-tag) category a 3\% (5\%)
+extrapolation uncertainty from \Zmm to \Ztautau is applied \cite{CMS-PAS-HIG-16-037}.
 \item \Zellell: The uncertainty on the Drell-Yan cross-section
 amounts to 4\% \cite{CMS-PAS-HIG-16-037}.
-\item \ttbar: The uncertainty on the \ttbar cross-section amounts
+\item \ttbar: The uncertainty on the \ttbar production cross-section amounts
 to 6\% \cite{CMS-PAS-HIG-16-037}.
@@
 on the observed data and subtracted backgrounds are taken into account by
-the inclusion of these control regions in the fit. The statistical and 
-uncertainties on $R_{W}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag
+the inclusion of these control regions in the fit. The statistical
+uncertainty on $R_{W}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag
 category in both the \etau and \mutau channels, and 11\% (14\%) in the b-tag
-category of the \mutau (\etau) channel. The systematic unsertainty on
+category of the \mutau (\etau) channel. The systematic uncertainty on
 this ratio amounts to 8\% (10\%) in the no b-tag (b-tag) category of both channels.
-The statistical uncertainty on the low \mT/high \mT ratio is 2\% in the no b-tag
+The statistical uncertainty on the low \mT/high \mT~ratio is 2\% in the no b-tag
 category of both channels and 14\% (17\%) in the b-tag category of the \mutau (\etau) channel.
@@
 in the \tautau and \emu channels is estimated from \ac{MC} a 4\% theoretical
-normalisation uncertainty is applied.
+production cross-section uncertainty is applied.
 \item QCD: In the \emu channel the uncertainty on the QCD estimate
@@
 regions in the fit. The uncertainty on the opposite--sign to same--sign ratio, based on
-the studies described in section QCD OSSS is found to be 4\% (60\%) in the 
+the studies described in section \ref{sec:mssm_bkgs_etmt_qcdosss} is found to be 4\% (60\%) in the 
 no b-tag (b-tag) category of the \mutau channel, and 12\% (60\%) in the no b-tag (b-tag) category
@@
 Uncertainties due to different renormalisation scales. 
-amount to 3.9\% for gluon fusion production,
-0.4\% for vector boson fusion, 2.8\% for ZH and 0.5\% for WH. The uncertainties
+amount to 3.9\% for gluon-fusion,
+0.4\% for VBF, 2.8\% for ZH and 0.5\% for WH. The uncertainties
 due to different choice of pdf and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for vector boson fusion,
@@
 due to different choices of factorisation and renormalisation scale
-are computed, separately for each \mA-\tanb~ point, following the description in refs\cite{pdf-lhc,alphas-uncs}.
+are computed, separately for each \mA-\tanb~point, following the prescription in refs\cite{pdf-lhc,alphas-uncs}.
 
@@
 \subsubsection*{$\Pgt_{h}$ energy scale}
-The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}. As the 
-shape of the total transverse mass distribution depends on the energy of the $\Pgt_{h}$
-it is applied as a shape uncertainty. It is applied to the signal samples and to
+The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}, affecting
+the shape of the total transverse mass distribution.
+The uncertainty is applied to the signal samples and to
 backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
@@
 \subsubsection*{Electron energy scale}
-The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This affects
-the shape of the total transverse mass distribution, and this uncertainty is applied to the
-signals and to the \Ztautau background.
+The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This 
+uncertainty is applied to the
+signals and to the \Ztautau background in the \emu channel.
 \subsubsection*{High-\pT~$\Pgt_{h}$ ID efficiency}
@@
 is applied to account for the extrapolation from the tau ID efficiency
-measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s \cite{CMS-PAS-HIG-16-037}. This
+measurement, which uses mostly taus close to the Z peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
 uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
@@
 \end{center}
-\caption{Shape-altering effect of the high \pT~tau ID uncertainty in the no b-tag category of the
+\caption{Shape-altering effect of the high-\pT~tau ID uncertainty in the no b-tag category of the
 \tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect is much
@@
 \subsubsection*{Top quark \pT~reweighting}
-To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape
+To account for the uncertainty in the derivation of the top-quark \pT~reweighting, a shape
 uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
-of the correction, ie the difference between applying the correction twice and not applying the correction at all.
+of the correction, that is the difference between applying the correction twice and not applying the correction at all.
 \subsubsection*{Drell-Yan shape reweighting}
@@
 applied. This uncertainty is derived from variations in the data/MC ratio
-for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~ in 
+for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~in 
 \Wjets events \cite{CMS-PAS-HIG-16-037}.
 
-\subsection{Summary of uncertainties and correlations}
-\label{sec:mssm_uncs_summary}
-The systematics that are applied are summarised in
-table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
-channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
-in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
-in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
-the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
-in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
-Some of the uncertainties
-are different for different processes, where this is the case ranges are given.
-Uncertainties marked "Fully correlated" are correlated between the different
-decay channels and event categories, those marked "Fully uncorrelated" are
-uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
-indicates that the uncertainty is correlated between categories but uncorrelated between
-the different decay channels.
-\input{MSSM/UncOv}
-\clearpage
+Overview tables of the systematic uncertainties per category of each
+channel can be found in appendix \ref{appendix:uncerts}. The correlations
+between the different channels and categories for these uncertainties
+is also indicated.
 
@@
 \label{sec:mssm_signalextraction}
-The total transverse mass \mTtot~ is used as discriminating variable in this analysis.
+The total transverse mass \mTtot~is used as discriminating variable in this analysis.
 All bins of the distribution are used to perform a shape analysis. The statistical
@@
 controls the \Wjets normalisation in all four regions. The QCD normalisation
-is fully correlated between the opposite--sign high and low \mT~ regions. The
-same is true for the same--sign high and low \mT regions. This means there are
+is fully correlated between the opposite--sign high and low \mT~regions. The
+same is true for the same--sign high and low \mT~regions. This means there are
 two freely floating nuisance parameters that govern the QCD normalisation: one
@@
 b-associated production, limits are set on these two signal processes. As we
-have seen in section WHATEVER we cannot fully separate the two signals by means
+have seen in section \ref{sec:mssm_eventsel_categories}  we cannot fully separate the two signals by means
 of the categorisation used. 
@@
 production processes and the signal strength modifiers $\mu_{gg\phi}$ and $\mu_{bb\phi}$ now represent the cross--section times branching ratio of the
-processes. Using this definition we can now perform a likelihood scan in two dimensions by 
+two processes. Using this definition we can now perform a likelihood scan in two dimensions by 
 constructing a two-dimensional grid in $\mu_{gg\phi}$ and $\mu_{bb\phi}$, both required to be greater than or equal to 0. 
@@
 \begin{equation}\label{eqn:nll}
-\text{NLL} = -\text{ln}\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta)
+\text{NLL} = -\text{ln }\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta)
 \end{equation}
@@
 ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
-masses of the light h and the scalar H are also given as a function of \mA~ and \tanb.
+masses of the light h and the scalar H are also given as a function of \mA~and \tanb.
 To interpret the results of this search in a particular scenario, the predicted
@@
 Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
-which give the \mTtot~ distributions for all channels and categories with an example three-Higgs signal overlaid.
+which give the \mTtot~distributions for all channels and categories with an example three-Higgs signal overlaid.
 The compatibility of the data with all three Higgs bosons, not just a single one, is thus tested.
@@
 hypothesis to determine the exclusion power of the search in a particular
-model can be problematic. Due to the existence of a Higgs boson with a 
+model is not strictly correct. Due to the existence of a Higgs boson with a 
 mass of 125 GeV, all MSSM benchmark scenarios must include a light Higgs boson
 with very similar properties to the boson discovered during Run 1 of the \ac{LHC}.
-This means that we should do a test that distinguishes between three-Higgs-signal-plus-background, and
+Therefore we should perform a test that distinguishes between three-Higgs-signal-plus-background, and
 standard model Higgs-signal-plus-background.
@@
 a signal + background expectation modified by the signal strenght modifier $\mu$ as
-$\mu \cdot s(\theta) + b(\theta)$, a likelihood must be constructed as:
+$\mu \cdot s(\theta) + b(\theta)$, a likelihood should be constructed as:
 \begin{equation}\label{mssm_likelihood}
@@
 The signal strength modifier $\mu$ takes the role of distinguishing between
-the two hypothesis in this case. The model cannot allow for the coexistence 
-of the SM and MSSM hypotheses; the MSSM hypothesis ($\mu=1$) is tested
+the two hypotheses in this case. The model must not allow for the coexistence 
+of the SM and MSSM hypotheses; the MSSM hypothesis ($\mu=1$) has to be tested
 against the SM hypothesis ($\mu=0$).
@@
 to use the profile likelihood ratio of equation \ref{eqn:hhh_profilelikelihood}:
-we are forced to test $\mu=1$ against $\mu=0$ and 
+we need to test $\mu=1$ against $\mu=0$, and 
 $\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
@@
 \begin{equation}\label{eqn:mssm_tevatron_teststat}
-q_{\mu} = -2\text{ln}\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0}} \text{ with } 0\leq\mu.
+q_{\mu} = -2\text{ln }\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0}} \text{ with } 0\leq\mu.
 \end{equation}
 In this test statistic we test a positive value of $\mu$ against 0, thus we are able to define
-the desired `MSSMvsSM' test statistic as
+the desired `MSSMvsSM' test statistic, using $\mu=1$, as,
 \begin{equation}\label{eqn:mssm_mssmvssm_stat}
-q_{\text{MSSMvsSM}} = -2\text{ln}\frac{\mathcal{L}(\text{data}|s_{\text{MSSM}}(\theta) + b(\theta)}{\mathcal{L}(\text{data}|s_{\text{SM}}(\theta)+b(\theta)}.
+q_{\text{MSSMvsSM}} = -2\text{ln }\frac{\mathcal{L}(\text{data}|s_{\text{MSSM}}(\theta) + b(\theta))}{\mathcal{L}(\text{data}|s_{\text{SM}}(\theta)+b(\theta))}.
 \end{equation}
@@
 to the Tevatron test statistic, and therefore the probability density functions need to be generated 
-with toy datasets. Using these pdfs we can then calculate $CL_s{\mu=1}$ as defined in equation \ref{eqn:hhh_cls}.
-If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95 \% CL. This generation of toy datasets and 
-calculation of corresponding $CL_s$ value is performed for many points in a grid in the \mA-\tanb~ plane,
+with toy datasets. Using these pdfs we can then calculate $CL_s(\mu=1)$ as defined in equation \ref{eqn:hhh_cls}.
+If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95 \% CL. The generation of toy datasets and 
+calculation of corresponding $CL_s$ value is performed for many points in a grid in the \mA-\tanb~plane,
 with interpolation between grid points performed to obtain a smooth exclusion contour.
-The distribution of toy datasets for the SM and MSSM hypothesis, as well as the resulting $CL_s$ values,
-are given for three \mA-\tanb~ points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
-there is no separation between the MSSM and SM toy distributions, and so we cannot exclude this point. The separation
-between the distributions in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
-with the SM hypothesis. This point is on the edge of being excluded. Finally the distributions in figure \ref{fig:mssm_mssmvssm_toys}c
+The pdfs for the SM and MSSM hypotheses, as well as the resulting $CL_s$ values,
+are given for three \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
+there is no separation between the MSSM and SM pdfs, and so we cannot exclude this point. The separation
+between the pdfs in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
+with the SM hypothesis. This point is on the edge of being excluded. Finally the pdfs in figure \ref{fig:mssm_mssmvssm_toys}c
 are very well separated, and the observation is compatible with the SM hypothesis, meaning this point of the parameter space is excluded.
@@
 \end{center}
-\caption{Distribution of toys for the SM and MSSM hypothesis at three different points in the $m_{\text{h}}^{\text{mod+}}$
-scenario, each with different levels of separation between the MSSM and SM toy distributions.}
+\caption{Pdfs, obtained by generating a large number of toy datasets, for the SM and MSSM hypothesis at three different points in the $m_{\text{h}}^{\text{mod+}}$
+scenario, each with different levels of separation between the MSSM and SM pdfs.}
 \label{fig:mssm_mssmvssm_toys}
@@
 \label{sec:mssm_results_modelindep}
-The \mTtot~ distributions in the no b-tag and b-tag
+The \mTtot~distributions in the no b-tag and b-tag
 categories of all channels, after the fit to the observed
@@
 with mass compatible with 125 GeV in this model, which is necessary to incorporate the Higgs boson
-observed at 125 GeV into the model.
+observed at 125 GeV.
 
@@
 \end{center}
-\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \mutau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 \end{center}
-\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \etau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 \end{center}
-\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
+\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 95\% upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
-for gluon--gluon fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
+for gluon--fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
 production. All channels and categories are combined. 
@@
 \mutau channel at 3.2 TeV. The \emu channel becomes more sensitive at higher masses as
-a narrower binning of the \mTtot~ distribution is possible than for the other channels.
-The \mTtot~ distribution for the high mass signals is therefore wide enough not to
+a narrower binning of the \mTtot~distribution is possible than for the other channels.
+The \mTtot~distribution for the high mass signals is therefore wide enough not to
 fall entirely into the last bin used for the fit. This means at high mass this channel
@@
 
-\subsection{Sensitivity to the Standard Model Higgs boson}
+\subsection{Sensitivity to the standard model Higgs boson}
 \label{sec:mssm_results_125GeV}
@@
 down to masses of 90 GeV it is important to consider possible sensitivity
-to the 125 GeV Higgs boson. As the cross--section times branching ratio for gluon-fusion
+to the 125 GeV SM Higgs boson. As the cross--section times branching ratio for gluon-fusion
 production of the 125 GeV Higgs boson in the standard model, with decay into $\Pgt\Pgt$
@@
 which include the standard model Higgs boson as part of the backgrounds,
-are almost exactly the same as those shown in figure \ref{fig:mssm_results_limits}. This
+are almost exactly the same as those shown in figure \ref{fig:mssm_results_limits}, which
 also indicates the current lack of sensitivity to the standard model Higgs boson.
@@
 \label{sec:mssm_results_2D}
-The 2D likelihood scans, as described in section \ref{sec:mssm_sigext_profile}, for
-a few mass points are shown in figure \ref{fig:mssm_results_2D_scans},
+The 2D likelihood scans, as described in section \ref{sec:mssm_sigext_profile},
+are shown in figure \ref{fig:mssm_results_2D_scans}
 for four mass points ranging from 100 GeV to 3.2 TeV. From the shape of the contours
@@
 
-Figure \ref{fig:mssm_mhmodp_2016} shows the expected (dashed line and grey bands) and
+Figure \ref{fig:mssm_mhmodp_2016}a shows the expected (dashed line and grey bands) and
 observed (blue shaded area bounded by solid line) exclusion of the search presented in this chapter
@@
 with 125 GeV. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
-limits at high \tanb~ have improved by around 300 GeV.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}
-\end{center}
-\caption{Exclusion in the $m_{h}^{\text{mod}+}$ scenario obtained by the combination
+limits at high \tanb~have been significantly improved, by around 300 GeV.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
+\subfloat[hMSSM scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
+\end{center}
+\caption{Exclusion in (a) the $m_{h}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+obtained by the combination
 of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
@@
 expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
-expected exclusion. The red shaded area
+expected exclusion. The red shaded area in the $m_{h}^{\text{mod}+}$ figure
 is excluded by the lack of a light Higgs boson with mass compatible with 125 GeV \cite{CMS-PAS-HIG-16-037}.}
@@
 
-Figure \ref{fig:mssm_hmssm_2016} shows the expected (dashed line and grey bands)
+Figure \ref{fig:mssm_mhmodp_2016}b shows the expected (dashed line and grey bands)
 and observed (blue shaded area bounded by solid line) exclusion of the search
@@
 two effects \cite{CMS-PAS-HIG-16-007}. On the one hand the branching ratio into taus decreases with decreasing
-\tanb~, while on the other hand a negative top--bottom interference effect increases the
-gluon--gluon fusion cross-section with decreasing \tanb~. Therefore the
+\tanb, while on the other hand a negative top--bottom interference effect increases the
+gluon--gluon fusion cross-section with decreasing \tanb. Therefore the
 combined cross--section times branching ratio decreases with decreasing \tanb, until it
@@
 thus expected to grow with more data.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}
-\end{center}
-\caption{Exclusion in the hMSSM scenario obtained by the combination
-of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
-solid black line is the observed exclusion, with the dashed black line the
-expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
-expected exclusion \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_hmssm_2016}
-\end{figure}
 
@@
 collected at a centre-of-mass energy of 13 TeV during 2015 are presented
-in this section. As for the analysis discussed earlier
-in the chapter a shape analysis is performed, however a different
-discriminating variable, the transverse component of the di-$\Pgt$ mass
-as reconstructed using the SVFit algorithm, was used. This variable
-is denoted $m_{\text{T,\Pgt\Pgt}}$. The transverse di-$\Pgt$ mass 
-distributions for the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
+in this section. Like for the analysis presented in 
+chapter \ref{chap:mssm} a shape analysis is performed, however a different
+discriminating variable is used. The variable used is the transverse component of the di-$\Pgt$ mass
+as reconstructed using the \texttt{SVFit} algorithm, 
+denoted $m_{\text{T},\tau\tau}$. The transverse di-$\Pgt$ mass 
+distributions for the signal region categories of the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
 \begin{figure}[h!]
@@
 These distributions do not show any significant excesses. The upper limits
-on cross--section times branching ratio for the gluon-fusion and b-associated
-process are shown in figure \ref{fig:mssm_results_hig16006_limits}a
+on cross--section times branching ratio for the gluon-fusion and b-associated production
+processes are shown in figure \ref{fig:mssm_results_hig16006_limits}a
 and b, respectively. All channels and categories are combined. A comparison of
 the expected limits per channel is given in figure \ref{fig:mssm_results_limits_breakdown_hig16006}.
-These follow a similar pattern to those given in figure \ref{gi:mssm_results_limits_breakdown}, notice
+These follow a similar pattern to those given in figure \ref{fig:mssm_results_limits_breakdown}, notice
 however the \emu channel remains the least sensitive even at very high mass, as the
 transverse component of the di-$\Pgt$ mass exhibits a sizeable \ttbar tail in the \emu channel. The total
-transverse mass collapses events from the tail into lower regions of the distribution.
+transverse mass collapses events from the tail into lower regions of the distribution, thus reducing the backgrounds
+at higher mass.
 
@@
 nuisance parameters in the 2015 and 2016 analyses need to be taken into account.
-The only truly correct way to establish the correlations is to perform
+The correct way to establish the correlations is to perform
 dedicated studies into them. In many cases such studies would be 
@@
 
-Even without performing such studies, a good estimate of what the correlation
-should be can usually be based on reasoning. With a small number of 
-exceptions this is what has been done for this combination.
+Even without performing these studies, a choice of correlation scheme can be motivated
+by carefully considering the differences between the two analyses and the conditions
+under which they were performed.
+This is what has been done for this combination.
 %Strictly, studies into the underlying correlations between
@@
 analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
-The third column gives the motivation for the chosen correlation.
+The third column of this table gives the motivation for the chosen correlation.
 
@@
 Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
+\midrule
+Electron energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
 \midrule

### 2017-01-17 backmatter.tex
Object reco edit round 1
Adding most of own comments on MSSM chapter

@@
 \acro{BDTs}[BDTs]{Boosted Decision Trees}
+\acro{KF}[KF]{Kalman Filter}
 \acro{CTF}[CTF]{Combinatorial Track Finder}
@@
 \acro{DA}[DA]{Deterministic Annealing}
-\acro{CHS}[CHS]{Charged hadron subtraction}
+\acro{CHS}[CHS]{charged hadron subtraction}
 \acro{CSV}[CSV]{Combined Secondary Vertex}
+
 \acro{IVF}[IVF]{Inclusive Vertex Finder}
@@
 
+\appendix
+\chapter{\texorpdfstring{Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
+\label{appendix:uncerts}
+An overview of the systematic uncertainties that are applied in the MSSM \AHtotautau analysis (chapter \ref{chap:mssm})
+are summarised in this appendix. The uncertainties are given in
+table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
+channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
+in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
+in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
+the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
+in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
+Some of the uncertainties
+are different for different processes, where this is the case ranges are given.
+Uncertainties marked "Fully correlated" are correlated between the different
+decay channels and event categories, those marked "Fully uncorrelated" are
+uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
+indicates that the uncertainty is correlated between categories but uncorrelated between
+the different decay channels.
+\input{MSSM/UncOv}
+
 %% If you have time and interest to generate a (decent) index,

### 2017-01-17 MSSM/MSSM.tex
Adding the high mT ctrl plots to thesis

@@
 The method described so far works well in the no b-tag categories, but in the b-tag category
-the \ttbar background dominates. For this reason the estimate of the number
+the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
+the high-\mT~region in the no b-tag category (figure \ref{fig:bkgs_highmtctrl}a) is compared with the high-\mT~region in the 
+b-tag category (figure \ref{fig:bkgs_highmtctrl}b) of the \etau channel. It is clear that the \ttbar 
+background is much larger than the \Wjets background in the b-tag high-\mT~control region.
+For this reason the estimate of the number
 of \Wjets events in this category is made with a relaxed category selection where the b-tagging
@@
 estimated in the 1-jet selection, multiplied by an extrapolation factor 
-$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$
+$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
+\end{center}
+\caption{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
+channel. In the no b-tag category the \Wjets background, drawn together with the small
+ di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
+category the \ttbar background is larger than the \Wjets background.}
+\label{fig:bkgs_highmtctrl}
+\end{figure}
 

### 2017-01-17 MSSM/MSSM.tex
One more change...

@@
 \label{sec:mssm_bkgs}
-The methods used for background estimation will be described in this
-section.
+To estimate the backgrounds to the analysis a mixture of data--driven
+methods and \ac{MC} samples is employed. The methods used for background 
+estimation will be described in this section.
 

### 2017-01-19 MSSM/MSSM.tex
Adding a few missing figures

@@
 \label{chap:mssm}
-
 In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
@@
 model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
-production in the gluon-fusion (gg$\phi$) and b-associated (bb$\phi$) production 
-modes (see THEORY) and decay into $\Pgt\Pgt$. 
+production in the gluon fusion (gg$\phi$) and b-associated (bb$\phi$) production 
+modes (see chapter [THEORY]) and decay into $\Pgt\Pgt$. 
 In addition to the upper limits on cross--section times branching ratio of these two processes, 
@@
 evaluation of systematic uncertainties in all four channels, and production of
-the statistical results, including model--dependent interpretations.
+the statistical results, including model interpretations.
 
@@
 
-single-top and \ttbar background samples are generated using \texttt{Powheg},
-with \texttt{MadGraph5\_aMC\@NLO} \cite{amcnlo} used for the generation of di--boson background
+Single-top and \ttbar background samples are generated using \texttt{Powheg},
+with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di--boson background
 samples and part of the W+$\gamma$ background, which is included in the \emu channel only.
@@
 \item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
-\item If the \pT of candidate 1 is the same in both pairs, prefer the pair with most isolated
+\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
 candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
@@
 The selection on the muon's relative isolation is chosen after comparing
-the performance of several isolation variables, using different selections.
-relative isolation values. This was based on a simple \mutau channel
+the performance of several isolation variables, using different relative isolation selections.
+This was based on a simple \mutau channel
 event selection as described above, only varying the isolation requirements.
@@
 
-Different isolation variables were studied over a range of maximum
-values. The $\Delta\beta$ corrected isolation variable analogous
+The isolation variables studied include
+the $\Delta\beta$ corrected isolation variable analogous
 to the one given for electrons in equation \ref{eqn:electron_reliso} with 
-isolation cone sizes in $\Delta R$ of 0.3 and 0.4 was studied. In addition
+isolation cone sizes in $\Delta R$ of 0.3 and 0.4. In addition
 to this a very similar
@@
 events in the \mutau channel. This selection and the
-choice of hadronic tau isolation working point interfere 
-with each other and therefore they are optimised in a 2D--optimisation. 
+choice of hadronic tau isolation working point provide two competing
+effects and therefore they are optimised in a 2D--optimisation. 
 The pre--fit expected upper limits on $\sigma\times$BR for both gg$\phi$ and bb$\phi$
 production with decay into $\Pgt\Pgt$ at several mass points 
-in the 90 GeV -- 3.2 TeV range are used to do this. 
+in the 90 GeV -- 3.2 TeV range are used as a figure of merit.
 Because of the use of such a wide range of signal masses, it
@@
 figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on $\sigma\times$BR for
-the gluon--gluon fusion production process, at a mass $m_{\phi} = 160$ GeV, with
+the gluon fusion production process, at a mass $m_{\phi} = 160$ GeV, with
 figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit at $m_{\phi} = 2.9$ TeV.
 Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
-tau isolation working point selection on both the gg$\phi$ and bb$\phi$ production processes. From these figures
+tau isolation working point selection on both the gg$\phi$ and bb$\phi$ production processes.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
+\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
+%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+\end{center}
+\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
+as a function of tau isolation working point (from very loose to very very tight) and
+of \mT~selection from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
+hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
+\label{fig:mssm_selection_mt_taumt}
+\end{figure}
+~
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
+\end{center}
+\caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
+(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
+at tight working point and \mT$<30$ GeV in green, medium working point and \mT$<40$ GeV in red,
+loose working point and \mT$<50$ GeV in blue and very loose working point and \mT$<60$ GeV in black. Loosening
+the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
+degrades them at low mass.}
+\label{fig:mssm_gradcuts_mt}
+\end{figure}
+
+From these figures
 we can observe that looser selections are preferred for higher masses. This behaviour can be
@@
 to reduce an already low background.
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
-\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
-%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
-%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
-\end{center}
-\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
-s a function of tau isolation working point (from very loose to very very tight) and
-of \mT~ cut from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
-for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
-hadronic tau isolation working point varies, with looser selections preferred for higher mass.}
-\label{fig:mssm_selection_mt_taumt}.
-\end{figure}
-\begin{figure}[h!]
-\begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
-\end{center}
-\caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
-(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
-at tight working point and \mT$<30$ GeV in green, medium working point and \mT$<40$ GeV in red,
-loose working point and \mT$<50$ GeV in blue and very loose working point and \mT$<60$ GeV in black. Loosening
-the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
-degrades them at low mass.}
-\label{fig:mssm_gradcuts_mt}
-\end{figure}
-The selection was then optimised for mass points of around 1 TeV, which leads to 
+Using this, the selection was optimised for mass points of around 1 TeV, which leads to 
 the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
@@
 to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
-required to be less than 0.2 cm. Finally, the hadronic tau should
+required to be less than 0.2 cm. Finally, the hadronic tau must 
 pass the tight working point of the anti--electron discriminator
@@
 tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.
+
 \begin{figure}[h!]
@@
 mass range, as seen in figure \ref{fig:mssm_tauid_tt} for the gg$\phi$ process.
+
 \begin{figure}[h!]
@@
 and muon are oppositely charged and separated by $\Delta R >$ 0.3. The 
-electron should have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
+electron needs to have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
 in the \etau channel the electron's impact parameters have to 
@@
 
-The muons need to have a \pT~of at least 10 GeV, $|\eta|<2.4$ and 
-their impact parameters need to be $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm.
+The muon needs to have a \pT~of at least 10 GeV, $|\eta|<2.4$ and 
+its impact parameters need to be $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm.
 In addition to the kinematic requirements the muon must
@@
 the higher \pT~trigger leg needs to have a transverse momentum
-of at least 24 GeV on top of the requirements already discussed.
+of at least 24 GeV on top of the requirements already discussed. This avoids
+events in the lower part of the trigger turn-on curve being selected.
 
@@
 \end{align}
-
-Thus $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy \pT+\MET on to 
-the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products on to this axis.
+This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy \pT+\MET~onto 
+the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
 The axis $\vec{\zeta}$ is the axis that bisects
@@
 \label{sec:mssm_eventsel_categories}
-As the analysis targets both the gluon--fusion
+As the analysis targets both the gluon fusion
 and the b--associated production modes of MSSM Higgs
@@
 \item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal.
-\item \textbf{b-tag}: At least 1 b--tagged jet and at most 1 
+\item \textbf{B-tag}: At least 1 b--tagged jet, at most 1 
 jet with \pT$>30$ GeV. Due to the different phase space considered for
-b--tagging than for normal jet reconstruction this requirement does not necessarily
+b--tagging than for default jet reconstruction this requirement does not necessarily
 mean there will be only one b--tagged jet in the event. The requirement reduces the sizeable \ttbar
@@
 
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
+\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
+\end{center}
+\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
+blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
+are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
+scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
+\label{fig:mssm_cats_mt}
+\end{figure}
+
 Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
 in the \mutau channel, with figure \ref{fig:mssm_cats_mt}b showing
-the number of b--tagged jets in that channel. The gluon--fusion
+the number of b--tagged jets in that channel. The gluon fusion
 and b--associated signals are overlaid on these distributions, normalised
@@
 \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$ scenario. From the distribution of the
-gluon--fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
+gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
 see that the vast majority of these signal events do not have any b-tagged jets, which
@@
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
-\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
-\end{center}
-\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon--fusion signal (dashed
-blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
-are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
-scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
-\label{fig:mssm_cats_mt}
-\end{figure}
-
 \section{\ac{MC} to data correction factors}
@@
 in data and \ac{MC} for electrons and muons was found. It is corrected for using $\eta$--dependent
-scale factors \cite{CMS-PAS-HIG-16-037}.
+scale factors.% \cite{CMS-PAS-HIG-16-037}.
 \subsubsection*{Electron, muon and tau ID and isolation}
@@
 cross trigger legs need to be combined. With one of the cross triggers having a
-minimum \pT~ of
+minimum \pT~of
 23 GeV on the muon leg and 12 GeV on the electron leg, and the
@@
 mass and high Z \pT, a reweighting is applied to correct for this.
-These weights are derived in bins of $\PZ/Pphotonx$ mass and \pT~
+These weights are derived in bins of $\PZ/\Pphotonx$ mass and \pT~
 using \Zmm events in data, in such a way that they do not
@@
 The \Wjets normalisation is derived using a high-\mT~ control region, where
-selected events are required to satisfy \mT$>70$ GeV. In the no b-tag
-category the \Wjets
+selected events are required to satisfy \mT$>70$ GeV. The 
+\Wjets
 contribution in this region is enhanced, however there is still
@@
 \caption{Distribution of the transverse mass \mT~in the \mutau channel, indicating
-the signal region and the high \mT~control region \cite{CMS-PAS-HIG-16-037}.}
+the signal region and the high \mT~control region. This distribution is plotted
+before dividing the events into categories \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_bkgs_wjets_mutau_mt}
@@
 have, for \mT$>70$ GeV:
-
 \begin{equation}\label{eqn:wjets_ss_norm}
@@
 \end{equation}
-
 where $R_{\text{W}}^{\text{OS/SS}}$ is the ratio between opposite-sign and same-sign \Wjets events
@@
 The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti--isolated
-control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
+control region in data; this measurement is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
 taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
@@
 
-The method described so far works well in the no b-tag categories, but in the b-tag category
+The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
 the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
@@
 The uncertainties are already large enough to cover differences between the pre-categorisation $R_{\text{QCD}}^{\text{OS/SS}}$ and the
-fits as performed in the no b-tag category. So $R_{\text{QCD}}^{\text{OS/SS}}$ in the \mutau channel is taken to be
+fits as performed in the no b-tag category. Therefore $R_{\text{QCD}}^{\text{OS/SS}}$ in the \mutau channel is taken to be
 1.18 in both the b-tag and the no b-tag category, with a 60\% uncertainty in the b-tag category and a 4\% uncertainty in the no b-tag category.
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
 is 1.180$\pm$0.044.}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
 is 1.184$\pm$0.035.}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
 is 1.015$\pm$0.059.}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit tot the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
 is 1.127$\pm$0.045.}
@@
 \begin{equation}\label{eqn:wjets_qcdsub}
-N_{\text{W,SS low }m_{\text{T}}} = \frac{N_{\text{MC,SS low }m_{\text{T}}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}
+N_{\text{W,SS low }m_{\text{T}}} = \frac{N_{\text{MC,SS low }m_{\text{T}}}}{N_{\text{MC,SS high }m_{\text{T}}}}N_{\text{W,SS high }m_{\text{T}}}.
 \end{equation}
-
 Because opposite--sign and same--sign QCD events do not
@@
 \end{equation}
-So this takes the ratio between the observed data with other
+This correction factor takes the ratio between the observed data with other
 backgrounds subtracted in the region equivalent to the signal region, but with the
@@
 \label{sec:mssm_bkgs_qcd_em}
-In the \emu channel the QCD multijet background
+In the \emu channel the QCD background
 is estimated by inverting the charge requirement
@@
 two components, one with real taus and 
-one without for fitting purposes. The component with real taus is composed
+one without, for fitting purposes. The component with real taus is composed
 of \ttbar events in which the hadronic tau is matched
@@
 Uncertainties on the b-tagging efficiency and light jet mis-tagging
-rates are given as a function of jet \pT~ and $\eta$ for the 
+rates are given as a function of jet \pT-and $\eta$-for the 
 medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
@@
 uncertainty is applied. The uncertainty varies from 1--5\%.
-\subsubsection*{\MET resolution and response}
-Uncertainties on \MET resolution and response are estimated
+\subsubsection*{\MET~resolution and response}
+Uncertainties on \MET~resolution and response are estimated
 by varying the recoil correction parameters within their
@@
 \item \Ztautau: As the \Zmm control region is included in the simultaneous
-fit with the signal region to correct the \Ztautau normalisation
+fit with the signal region to correct the \Ztautau normalisation,
 the Drell-Yan cross section is not applied as an uncertainty. In the no b-tag (b-tag) category a 3\% (5\%)
@@
 \item \Wjets: In the \mutau and \etau channels the statistical uncertainties
-on the observed data and subtracted backgrounds are taken into account by
+on the observed data and subtracted backgrounds in the control regions are taken into account by
 the inclusion of these control regions in the fit. The statistical
@@
 uncertainties on the observation and subtracted \ac{MC} backgrounds in the control
-region used to derive the QCD estimate from is accounted for by the inclusion of control
+region used to derive the QCD estimate is accounted for by the inclusion of these control
 regions in the fit. The uncertainty on the opposite--sign to same--sign ratio, based on
@@
 For interpretations of the results in MSSM benchmark scenarios, theory
-uncertainties on the SM and MSSM Higgs cross section predictions are included. 
+uncertainties on the SM and MSSM Higgs cross section predictions are taken into account.
 The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
-Uncertainties due to different renormalisation scales. 
-amount to 3.9\% for gluon-fusion,
+Uncertainties due to different renormalisation scales
+amount to 3.9\% for gluon fusion,
 0.4\% for VBF, 2.8\% for ZH and 0.5\% for WH. The uncertainties
@@
 controls the \Wjets normalisation in all four regions. The QCD normalisation
-is fully correlated between the opposite--sign high and low \mT~regions. The
-same is true for the same--sign high and low \mT~regions. This means there are
+is fully correlated between the opposite--sign and same--sign low-\mT~regions. The
+same is true for the opposite--sign and same--sign high-\mT~regions. This means there are
 two freely floating nuisance parameters that govern the QCD normalisation: one
-that controls the QCD normalisation in the two opposite--sign regions, and one
-that controls it in the two same--sign regions.
+that controls the QCD normalisation in the two low-\mT~regions, and one
+that controls it in the two high-\mT~regions.
 
@@
 of the categorisation used. 
-However, in the upper limits on cross--section times branching ratio for the $gg\phi$
-process we should not make any assumptions about the presence or lack of the $bb\phi$
-process and vice versa. Therefore when calculating the upper limits on the $gg\phi$
-process, the contribution of the $bb\phi$ process is added to the fit as a freely floating nuisance
-parameter, and vice versa, in a process referred to as signal process profiling.
-
-Because these two signal processes are targeted by this analysis, it is possible
+However, in the upper limits on cross--section times branching ratio for the gg$\phi$
+process we should not make any assumptions about the presence or lack of the bb$\phi$
+process and vice versa. Therefore when calculating the upper limits on the gg$\phi$ (bb$\phi$)
+process, the contribution of the bb$\phi$ (gg$\phi$) process is profiled. This means it is floated
+in the fit like a nuisance parameter.
+
+Because the analysis targets these two signal processes, it is possible
 to re-define the likelihood as a function of both the gg$\phi$ and bb$\phi$ signals:
@@
 \begin{equation}\label{eqn:nll}
-\text{NLL} = -\text{ln }\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta)
+\text{NLL} = -\text{ln }\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi},\theta),
 \end{equation}
@@
 \Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{68\%},\mu_{bb\phi}^{68\%}) = 0.5, ~\\
-\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{95\%},\mu_{bb\phi}^{95\%}) = 1.92,
+\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{95\%},\mu_{bb\phi}^{95\%}) = 1.92.
 \end{split}
@@
 The results of the search are interpreted in MSSM benchmark
-scenarios, with the interpretation made in the \mA-\tanb~ plane.
-At each point in the \mA-\tanb~ plane each MSSM scenario
-predicts a production cross section, and corresponding branching
+scenarios, with the interpretation made in the \mA-\tanb~plane.
+At each point in the \mA-\tanb~plane each MSSM scenario
+predicts a production cross--section, and corresponding branching
 ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
@@
 which give the \mTtot~distributions for all channels and categories with an example three-Higgs signal overlaid.
-The compatibility of the data with all three Higgs bosons, not just a single one, is thus tested.
+In this way the compatibility of the data with all three Higgs bosons, not just a single one, is tested.
 
@@
 \end{equation}
-where $s_{\text{MSSM}}(\theta)$ corresponds to the MSSM signal expectation, ie the three-Higgs-signal, and $s_{\text{SM}}(\theta)$ 
+where $s_{\text{MSSM}}(\theta)$ corresponds to the MSSM signal expectation, that is the three-Higgs-signal, and $s_{\text{SM}}(\theta)$ 
 corresponds to the SM signal expectation.
@@
 \begin{equation}\label{eqn:mssm_tevatron_teststat}
-q_{\mu} = -2\text{ln }\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0}} \text{ with } 0\leq\mu.
+q_{\mu} = -2\text{ln }\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0})} \text{ with } 0\leq\mu.
 \end{equation}
-In this test statistic we test a positive value of $\mu$ against 0, thus we are able to define
+In this test statistic we test a positive value of $\mu$ against $\mu=0$, thus we are able to define
 the desired `MSSMvsSM' test statistic, using $\mu=1$, as,
@@
 \label{sec:mssm_results}
-
 \subsection{Model--independent results}
@@
 None of these distributions show hints of a significant excess. The
-95\% upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
-for gluon--fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
+95\% CL upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
+for gluon fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
 production. All channels and categories are combined. 
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+\caption{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. All four final states and 
@@
 \end{center}
-\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
+\caption{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
@@
 
+\clearpage
+
 \subsection{Sensitivity to the standard model Higgs boson}
@@
 down to masses of 90 GeV it is important to consider possible sensitivity
-to the 125 GeV SM Higgs boson. As the cross--section times branching ratio for gluon-fusion
-production of the 125 GeV Higgs boson in the standard model, with decay into $\Pgt\Pgt$
+to the 125 GeV SM Higgs boson. As the cross--section times branching ratio for gluon fusion
+production of the 125 GeV Higgs boson in the standard model, with decay into $\Pgt\Pgt$,
 is 3.05 pb \cite{YR4} and the expected limit on cross--section times
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+\caption{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. The SM, 125 GeV Higgs boson
@@
 are shown in figure \ref{fig:mssm_results_2D_scans}
-for four mass points ranging from 100 GeV to 3.2 TeV. From the shape of the contours
-we can see the correlation between the gg$\phi$ and bb$\phi$ processes, in a show of
+for four mass points ranging from 100 GeV to 3.2 TeV. The black cross indicates the best-fit value, with the red diamond showing the expected
+best-fit value in the presence of the 125 GeV SM Higgs boson. The dark and light purple contours
+indicate the 68\% and 95\% confidence interval, respectively.  From the shape of the contours
+we can see the correlation between the gg$\phi$ and bb$\phi$ processes, illustrating
 the fact that we cannot fully disentangle the two processes.
@@
 The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
-scenario and the hMSSM scenario. Both scenarios are described in chapter THEORY.
+scenario and the hMSSM scenario. Both scenarios are described in chapter [THEORY].
 
@@
 and observed (blue shaded area bounded by solid line) exclusion of the search
-presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
+presented in this chapter in the \mA-\tanb~plane of the hMSSM scenario. 
 We should note again that this model, although defined for \tanb~ values
-upwards of 10, is only strictly valid for \tanb~ below 10.
+upwards of 10, is only strictly valid for \tanb~below 10.
 The small excluded area around \mA=200 GeV is genuine. It is caused by the 
@@
 \tanb, while on the other hand a negative top--bottom interference effect increases the
-gluon--gluon fusion cross-section with decreasing \tanb. Therefore the
+gluon fusion cross--section with decreasing \tanb. Therefore the
 combined cross--section times branching ratio decreases with decreasing \tanb, until it
-increases again from a low value of \tanb~ down to \tanb=1. The feature is 
+increases again from a low value of \tanb~down to \tanb=1. The feature is 
 thus expected to grow with more data.
@@
 By combining the two analyses we should be able to set the most stringent
-limits on the two MSSM production modes, and in the \mA-\tanb~ plane of 
+limits on the two MSSM production modes, and in the \mA-\tanb~plane of 
 MSSM benchmark scenarios, available at the time of writing. It is also
@@
 These distributions do not show any significant excesses. The upper limits
-on cross--section times branching ratio for the gluon-fusion and b-associated production
+on cross--section times branching ratio for the gluon fusion and b-associated production
 processes are shown in figure \ref{fig:mssm_results_hig16006_limits}a
@@
 \midrule
-Luminosity & Partially \mbox{correlated} & As studied by the relevant people in the experiment\\
-\midrule
-Jet energy scale & Fully \mbox{correlated} & Found to be so by those responsible for it in the experiment\\
-\midrule
-b-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods\\
-\midrule
-mis-tagging & Partially \mbox{correlated} & As recommended by those measuring b-tagging scale factors\\
-\midrule
-Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016\\
-\midrule
-Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016\\
-\midrule
-Tau ID/isolation/trigger& Uncorrelated & \scriptsize{On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis}\\
-\midrule
-High \pT tau ID efficiency & Correlated & This should not be affected by the lack of tau ID scale factor and covers teh same underlying issue in both analyses\\
-\midrule
-Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
-\midrule
-Electron energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
+Luminosity & Partially \mbox{correlated} & Recommended by the CMS collaborators who perform the luminosity measurement, after dedicated studies.\\
+\midrule
+Jet energy scale & Fully \mbox{correlated} & Recommended by the CMS collaborators who derive jet energy corrections, after dedicated studies.\\
+\midrule
+B-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods.\\
+\midrule
+Mis-tagging & Partially \mbox{correlated} & Recommended by the CMS collaborators responsible for deriving b-tagging scale factors, after dedicated studies.\\
+\midrule
+Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016.\\
+\midrule
+Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016.\\
+\midrule
+Tau ID/isolation/trigger& Uncorrelated & \scriptsize{On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite an observed downward correction of 8\% on the yield of backgrounds with real hadronic taus.}\\
+\midrule
+High-\pT~tau ID \mbox{efficiency} & Correlated & This should not be affected by the lack of tau ID scale factor and covers the same underlying issue in both analyses.\\
+\midrule
+Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016.\\
+\midrule
+Electron energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016.\\
 \midrule
 Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, exhibiting the observed discrepancies, are used.
-In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar}\\
+In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar.}\\
 \midrule
 W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & \scriptsize{Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
-The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point}\\
-\midrule
-MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016\\
-\midrule
-Top quark \pT reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses\\
-\midrule
-Drell-Yan $\sigma$& Correlated & Theoretical uncertainty so should be correlated\\
-\midrule
-Di--boson $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
-\midrule
-\ttbar $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
-\midrule
-\Wjets $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
-\midrule
-SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated\\
+The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point.}\\
+\midrule
+MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016.\\
+\midrule
+\mbox{Top quark} \pT~reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses.\\
+\midrule
+Drell-Yan $\sigma$& Correlated & Theoretical uncertainty so should be correlated.\\
+\midrule
+Di--boson $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
+\midrule
+\ttbar $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
+\midrule
+\Wjets $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
+\midrule
+SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated.\\
 \midrule
@@
 \midrule
-%e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
+%e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets.\\
 %$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
@@
 \midrule
-e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
-\midrule
-$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
-\midrule
-jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
-\midrule
-QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-iso sideband in 2015 and 2016 analyses\\
-\midrule
-QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
-\midrule
-Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
-\midrule
-Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
-\midrule
-Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
+e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets.\\
+\midrule
+$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet, while this had changed for the 2016 analysis.\\
+\midrule
+jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & Uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate should not be affected by changes in hadronic tau isolation working point.\\
+\midrule
+QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-isolated sideband in 2015 and 2016 analyses.\\
+\midrule
+QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband.\\
+\midrule
+Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa.\\
+\midrule
+Statistical \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+Systematic \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
 In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
 \midrule
-Statistical uncertainty on W low/high\mT~ ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
-\midrule
-Systematic uncertainty on W low/high\mT~ ratio (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately}\\
-\midrule
-QCD OS/SS ratio statistical uncertainty (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated\\
-\midrule
-QCD OS/SS ratio systematic uncertainty (\etau and \mutau) & Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
+Statistical \mbox{uncertainty} on W low/high-\mT~\mbox{ratio} (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+Systematic \mbox{uncertainty} on W low/high-\mT~\mbox{ratio} (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately.}\\
+\midrule
+QCD OS/SS \mbox{ratio} statistical \mbox{uncertainty} (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+QCD OS/SS \mbox{ratio} systematic \mbox{uncertainty} (\etau and \mutau) & Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
 Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.}\\
 \midrule
-bin--by--bin uncertainties for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible to achieve\\
+bin--by--bin \mbox{uncertainties} for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible.\\
 \bottomrule
@@
 
-\subsection{Results}
+\section{Results}
 \label{sec:mssm_combination_results}
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+\caption{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. These results
@@
 of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
-gluon-fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
-higher masses the analysis sensitivity is only very slightly improved with respect to the 
+gluon fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
+higher masses the sensitivity is only very slightly improved with respect to the 
 analysis of the 12.9 fb$^{-1}$ dataset. However, for masses between 200 and 800 GeV
-there is a larger improvement in analysis sensitivity from combining the two analyses.
+there is a larger improvement in sensitivity from combining the two analyses.
 This behaviour is expected since the analysis on the 2016 dataset used a slightly different
@@
 \end{center}
-\caption{Comparison of the expected Upper limits at 95\% CL for (a) the gluon--gluon fusion production
+\caption{Comparison of the expected upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. The green curve shows the results
@@
 \end{figure}
+
+Interpretations in MSSM benchmark scenarios to be added.

### 2017-01-19 backmatter.tex
Adding a few missing figures

@@
 \appendix
-\chapter{\texorpdfstring{Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
+\chapter*{\texorpdfstring{Appendix A: Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
+\addcontentsline{toc}{chapter}{A: Overview of systematic uncertainties in the MSSM \AHtotautau analysis}
 \label{appendix:uncerts}

### 2017-01-21 Theory/Theory.tex
Helps to actually add theory chappter doesn't it

\chapter{Introduction and theory}
\label{chap:theory}

\section{The standard model of particle physics}
\label{sec:theory_sm}

\section{Standard model Higgs boson measurements}
\label{sec:theory_smH}

\section{Beyond the standard model}
\label{sec:theory_BSM}

\subsection{The Higgs sector of the MSSM}
\label{sec:theory_MSSM_H}

\subsection{\acl{2HDM}s}
\label{sec:theory_2HDM}

\section{MSSM benchmark scenarios}
\label{sec:theory_BSM_models}

\subsection{The $m_{h}^{\text{mod+}}$ scenario}
\label{sec:theory_BSM_models_mhmodp}

\subsection{MSSM scenarios at low \tanb}
A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 
scenario contains a light Higgs boson with a mass compatible with
125 GeV. However, at low values of \tanb this is not the case, with
values of \mh~dropping below 122 GeV. The low \tanb~regime can be re-opened
if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
MORE ABOUT FINE-TUNING
%But not too large, see ref above!
Figure \ref{fig:tanb_accessibility} shows contours of constant
light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./Theory/Figures/tanb_accessibility.png}
\end{center}
\caption{Contours of constant light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
High values of $M_{\text{SUSY}}$ allow for light Higgs boson masses compatible with
125 GeV down to low values of \tanb~\cite{hMSSM-2}.}
\label{fig:tanb_accessibility}
\end{figure}

%where the ±3 GeV variation corresponds to a rough estimate of the theoretical uncertainty of the MSSM prediction for mh, due to the unknown effect of higher-order correction

Gluon fusion dominance? Show decays? Or do it in the relevant subsecs?

Two approches for the definition of an MSSM scenario that gives
access to the low-\tanb~region have been developed, they will be
discussed in the next sections.

\subsubsection{The low-\tanb-scenario}
\label{sec:theory_BSM_model_lowtb}
In the low-\tanb-scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
the radiative corrections are tuned to obtain light 
Higgs boson masses of around 125 GeV in most of the \mA-\tanb~plane considered.
Figure \ref{fig:lowtbhigh_mh} shows that, apart from in a corner of \tanb~1-4 and 
\mA~150-250 GeV, \mh~is compatible with 125 GeV.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
\end{center}
\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
\label{fig:lowtbhigh_mh}
\end{figure}

To obtain \mh$\approx$125 GeV over a large part of the parameter
space, the SUSY parameters are chosen such that SUSY BREAKING MASSES ETC?
and $M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
varying the parameter $X_t$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25\\
8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to 2 TeV, with $\mu$ set to 1.5 TeV and $M_2$ to 2 TeV.

The branching fractions of \Htohh and \AtoZh in the low-\tanb~scenario are shown in
figure \ref{fig:lowtbhigh_br}. For both decay channels there are areas in the \mA-\tanb~plane
where the branching ratio is enhanced, indicating how analyses targeting such processes 
can be sensitive in this scenario. %REPHRASE
The analysis presented in chapter \ref{chap:hhh} is interpreted
in the low-\tanb~scenario.

\begin{figure}[h!]
\begin{center}
\subfloat[\Htohh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_hhbr.png}}
\subfloat[\AtoZh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_azhbr.png}}
\end{center}
\caption{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
areas where both are significantly enhanced \cite{MSSM-lowtanb}.}
\label{fig:lowtbhigh_br}.
\end{figure}

\subsubsection{The hMSSM scenario}
\label{sec:theory_BSM_models_hMSSM}
The hMSSM scenario \cite{hMSSM-1,hMSSM-2} uses a different approach by starting from 
the REPHRASE tree-level expressions for masses and mixing and
the mass of the light Higgs boson \mh=125 GeV.

One of the assumptions of the hMSSM is that the
the mass matrix for the neutral CP-even states can
be decomposed as,
\begin{equation}
\label{eqn:hmssm_massmatrix}
\mathcal{M}^2_{\phi} = \mathcal{M}^2_{\text{tree}} + \begin{pmatrix}
\Delta\mathcal{M}^2_{11} & \Delta\mathcal{M}^2_{12} \\
\Delta\mathcal{M}^2_{12} & \Delta\mathcal{M}^2_{22} \end{pmatrix},
\end{equation}
where the $\Delta\mathcal{M}^2_{ij}$ are the radiative corrections.
The second assumption is that only $\Delta\mathcal{M}^2_{22}$ needs to be
taken into account, as this is the element that involves the stop-top correction
and so $\Delta\mathcal{M}^2_{22} >> \Delta\mathcal{M}^2_{12},\Delta\mathcal{M}^2_{11}$. 
Finally, all SUSY particles are assumed to be heavy enough not to be
detected at the \acs{LHC} and apart from effects on the mass matrix, 
the effects on the Higgs sector can be neglected.
%all SUSY particles are heavy enough to escape detection at the LHC, and their effects on the Higgs sector other than those on the mass matrix, e.g. via direct loop corrections to the Higgs-boson couplings or via modifications of the total decay widths, can be neglected.

Using these assumptions we can invert the lightest eigenvalue
of the mass matrix to get: 
\begin{equation}
\label{eqn:hmssm_deltam22}
\Delta\mathcal{M}^2_{22} = \frac{m_h^2(m_A^2+m_Z^2 - m_h^2) - m_A^2m_Z^2\text{cos}^22\beta}{m_Z^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_h^2},
\end{equation}

This means we can write,
\begin{equation}
\label{eqn:hmssm_mHalpha}
\begin{split}
&m^2_H = \frac{(m_A^2+m_Z^2-m_h^2)(m_z^2\cos{\beta}^2+m_A^2\sin{\beta}^2 - m_A^2m_Z^2\cos{2\beta}^2}{m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2-m_h^2},\\
&\tan{\alpha} = -\frac{(m_Z^2+m_A^2)\cos{\beta}\sin{\beta}}{m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2-m_h^2}.
\end{split}
\end{equation}
Combining this with the Hhh coupling,
\begin{equation}
\label{eqn:hmssm_Hhh}
\lambda_{Hhh} = \lambda_{Hhh,tree} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_Z^2\sin{\beta}}\cos{\alpha}^2,
\end{equation}
gives enough information to determine the cross sections and branching
ratios of all the five Higgs bosons as a function of \mA~and \tanb. The scenario
is only well defined in regions where the denominator in equations
\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2 - m_h^2$, is nonzero. 
This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
a minimum accessible \mA~of around 151 GeV for \tanb=1. In addition, the scenario
can be formulated, but is not strictly valid, for values of \tanb upwards of 10 \cite{CMS-PAS-HIG-16-007}.
The reason for this is that direct higher order SUSY corrections to down-type
fermion couplings and corrections due to SUSY particles in loops become relevant
above \tanb=10, but these are omitted in the hMSSM approach.

%to the couplings to the h, as expected from the SM, as will be further discussed in Section 3. This scenario is strictly valid for mA > 130 GeV and tanβ < 10. It can still be formulated for values up to tanβ < 60 though the omission of direct higher order SUSY corrections to down-type fermion couplings (also referred to as ∆β corrections) and corrections due to SUSY particles in loops, which be- come relevant for tan β > 10 question the consistency of the predictions with SUSY. A detailed

The production cross--sections at $\sqrt{s}=14$ TeV for gluon fusion production of the
H and A bosons, as well as for b-associated production, are shown in figure \ref{fig:hmssm_xs}.
As expected, gluon fusion production is dominant at low \tanb,with b-associated
production being more important at high \tanb. The cross sections increase for increasing \tanb,
apart from the gluon fusion cross section at low \tanb, where it decreases as \tanb~increases
due to a negative top-bottom intereference effect.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_xsAH.png}
\caption{Cross-sections at $\sqrt{s}=14$ TeV as a function of
\mA~and \tanb~ in 
the hMSSM scenario for b-associated production of \PHiggsps (top left), b-associated
production of \PHiggs (top right), gluon fusion production of \PHiggsps (bottom left) and
gluon fusion production of \PHiggs (bottom right). The white areas indicate cross-sections
smaller than the minimum value on the z-axis. We can generally see the cross-sections increase
with growing \tanb, apart from the gluon fusion cross sections which decrease with increasing
\tanb~for low \tanb~\cite{hMSSM-2}.}
\label{fig:hmssm_xs}
\end{figure}

Figure \ref{fig:hmssm_brtautau} shows the branching ratios of \PHiggsps and \PHiggs into \Pgt\Pgt.
The branching ratios are large over a large part of the mA-\tanb~plane, but mostly so
at high \tanb.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_brtautau.png}
\caption{Branching ratios of \PHiggsps (left) and \PHiggs (right) into \tautau. The
branching ratio is enhanced at high \tanb~\cite{hMSSM-2}.} 
\label{fig:hmssm_brtautau}
\end{figure}

\section{Status of BSM Higgs boson searches}
\label{sec:theory_BSMH_status}
With the data collected during 
Run 1 of the \ac{LHC} many searches for BSM Higgs
bosons were already performed. The state of play with the full
Run-1 dataset collected by \ac{CMS} can be seen in figure \ref{fig:bsm_summary},
which shows the interpretations of different searches in the $m_{h}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
and hMSSM scenarios (figure \ref{fig:bsm_summary}b). The direct search for heavier Higgs bosons decaying into pairs
of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb,with searches for 
heavy Higgs bosons decaying to $b\bar{b}$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
Searches for heavy Higgs bosons decaying to WW and ZZ are able to exclude part of the low-\tanb-region. In the 
hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA=250-350 GeV.
The red exclusion contour in figure \ref{fig:bsm_summary}b is the re-interpretation of the analysis presented in
chapter \ref{chap:hhh}.

In Run-2 of the \ac{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. Other searches
for heavy Higgs bosons with decays to other final states are also in progress as the Run-2 data keep
amassing.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{h}^{\text{mod+}}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-a.pdf}}
\subfloat[hMSSM scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-b.pdf}}
\end{center}
\caption{Summary of the interpretations of Run 1 BSM Higgs searches at \ac{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
scenarios. The results from MSSM Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
space than any of the other searches. The MSSM Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
of the high-\tanb region, with Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low-mass region for all values of \tanb. Masses below around 300 GeV in the 
hMSSM scenario are excluded instead by constraints from standard model Higgs boson measurements (magenta). In this scenario small
areas of the low-\tanb~region are also excluded by the search for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
and the search for $H\rightarrow hh \rightarrow bb\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}
\label{fig:bsm_summary}
\end{figure}

### 2017-01-22 Theory/Theory.tex
More theory

@@
 \label{sec:theory_MSSM_H}
+At least two Higgs doublets are required in the
+Higgs sector of the MSSM due to the supersymmetric
+background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
+\begin{equation}\label{eqn:mssm_higgsdoublets}
+\phi_d = \begin{pmatrix} \phi_d^0 \\
+\phi_d^- \end{pmatrix} \text{ and } \phi_u = \begin{pmatrix} \phi_u^+ \\
+\phi_u^0 \end{pmatrix}
+\end{equation}
+Note that $\phi_d^0$ couples exclusively to down-type fermions, and $\phi_u^0$ couples
+exclusively to up-type fermions.
+This leads to potential terms in the MSSM Lagrangian of the form:
+\begin{equation}\label{eqn:mssm_lagrangian_potential}
+V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
+\end{equation}
+with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
+This provides electroweak symmetry breaking as in the \ac{SM} case and
+minimising this potential gives,
+\begin{equation}\label{eqn:mssm_minimpot}
+\langle 0|\phi_d| 0 \rangle = \begin{pmatrix}v_d\\
+0 \end{pmatrix} \text{ and} \langle 0 |\phi_d|\rangle 0 = \begin{pmatrix} 0\\
+v_u \end{pmatrix}
+\end{equation}
+Using this we define
+\begin{equation}\label{eqn:tanb_def}
+\tan{\beta} \equiv \frac{v_u}{v_d}
+\end{equation}
+Of the eight degrees of freedom due to the introduction of two complex
+doublets, three become longitudinal states of the $\PW^{\pm}$ and \PZ bosons.
+The remaining 5 degrees of freedom lead to five physical Higgs bosons, a charged
+Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
+and the neutral scalars h and H. These are defined in terms
+of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
+the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}. The five bosons become:
+\begin{align}\label{eqn:MSSMHiggsMixing}
+&\PHiggs^+ = \phi_u^+\cos{\beta} + \phi_d^{-\dagger}\sin{\beta},\\
+&\PHiggs^- = \phi_u^{+\dagger}\cos{\beta} + \phi_d^{-}\sin{\beta},\\
+&\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
+&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi+u^0 -v_u)\cos{\alpha}\\
+&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
+\end{align}
+As the self-interactions of the Higgs fields are not independent parameters
+but are functions of the electroweak gauge coupling constants, at tree
+level the MSSM Higgs sector parameters are determined by two free parameters, \tanb~and
+one of the Higgs boson masses, conventionally chosen as \mA.
+Using this the masses of the five Higgs states are found as:
+\begin{equation}\label{mssm_chargedhigss_mass}
+m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2,
+\end{equation}
+while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the tree-level
+squared-mass matrix:
+\begin{equation}\label{eqn:treelevel_mass}
+\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
+m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
+-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
+\end{equation}
+This leads to the masses of \PHiggslight and \PHiggs as eigenvalue of $\mathcal{M}_{\text{tree}}^2$,
+\begin{equation}\label{eqn:scalarmass}
+m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
+\end{equation}
+A consequence of this is a tree-level upper bound to the mass of the light Higgs
+boson,
+\begin{equation}\label{eqn:mh_upper}
+m_{h} \leq m_{Z},
+\end{equation}
+and a constraing on $\alpha$,
+\begin{equation}\label{eqn:alpha_constraint}
+\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.
+\end{equation}
+
+The constraint on $m_h$ being less than the mass of the Z boson, 91.2 GeV, seems 
+problematic at first, as we know there is a Higgs state with a mass of 125 GeV. However,
+the tree-level masses and couplings of the Higgs bosons in the MSSM can be
+significantly altered by radiative corrections. The dominat effect is from
+incomplete cancellation of the stop- and top-loop corrections, which
+do not completely cancel as SUSY is a broken symmetry. FIND REFERENCE FOR THIS
+
+The couplings of the neutral Higgs bosons to bosons and fermions 
+are modified with respect to the \ac{SM} couplings, by factors
+described in table \ref{tab:mssm_couplings} \cite{YR4}.
+
+\begin{table}[htp]
+\label{tab:mssm_couplings}
+\begin{center}
+\caption{Couplings in the MSSM, as multiplicative factors with
+respect to the \ac{SM} couplings}
+\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
+\toprule
+Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
+\midrule
+\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
+\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
+\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
+\bottomrule
+\end{tabular}
+\label{tab:mssm_couplings}
+\end{center}
+\end{table}
+
+In the \textit{decoupling limit}, when \mA$>>m_{Z}$, the mixing
+angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
+\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
+with negligible couplings to bosons for the two remaining neutral
+Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
+and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$.
+%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
+%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
+%such that -sinalpha/cosbeta = 1
+%cos alpha/sin beta = sin beta/sin beta = 1
+%sin beta-alpha = sin pi/2 = 1
+%cos beta-alpha = cos pi/2 = 0
+%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)
 
@@
 \label{sec:theory_BSM_models}
+Because the MSSM contains a large number of
+SUSY-breaking parameters that affect the Higgs
+sector, it us usual to define benchmark scenarios 
+in which the only free parameters are \mA~and \tanb.
+In these scenarios the SUSY parameters entering in 
+the radiative corrections are fixed to define the scenario.
+
+The parameters that need to be fixed in the benchmark scenarios are:
+\begin{itemize}
+\item The mass of the third generation squarks, given by $M_{\text{SUSY}}$.
+\item The higgsino mass parameter, $\mu$.
+\item The mass of the stau, the third generation sleptons, $M_{\tilde{\ell_3}}$.
+\item The mass of the gluino, $M_{\tilde{g}}$.
+\item The U(1) gaugino mass parameter, $M_1$.
+\item The SU(2) gaugino mass parameter, $M_2$.
+\item The trilinear couplings of the stops, sbottoms and staus to the Higgs: $A_t$, $A_b$ and $A_{\Pgt}$.
+\item The stop, sbottom and stau mixing parameters, $X_t$, $X_b$ and $X_{\Pgt}$.
+\end{itemize}
+
+Some of these parameters can be expressed in terms of relations to other parameters. 
+$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as,
+\begin{equation}\label{eqn:trilinear_couplings}
+\begin{split}
+&X_t = A_t-\mu\cot{\beta},\\
+&X_b = A_b-\mu\tan{\beta},\\
+&X_{\Pgt} = A_{\Pgt} - \mu\tan{\beta}.
+\end{split}
+\end{equation}
+In addition, $M_1$ is fixed via the unification
+relation,
+\begin{equation}
+M_1 = \frac{5}{3}M_s\tan{\theta_w}^2,
+\end{equation}
+where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
+
+Some additional parameters which have only a
+small effect on the MSSM Higgs boson sector are alos considered.
+Because their effect is so small they are
+fixed in all benchmark scenarios at values compatible with 
+exclusion limits from direct searches:
+\begin{itemize}
+\item Masses of the first and second generation squarks, $M_{\tilde{q}_{1,2}} = 1.5$ TeV.
+\item Masses of the first and second generation sleptons, $M_{\tilde{\ell}_{1,2}} = 500$ GeV.
+\item Trilinear couplings of first and second generation squarks and sleptons, $A_f=0$.
+\end{itemize}
+
+After the discovery of the 125 GeV Higgs boson the MSSM benchmark
+scenarios need to accommodate this particle, which means only the 
+scenarios which contain a light Higgs boson with a mass of around 125 GeV
+are still accessible.
+
+% in the mmax scenario the benchmark values have been chosen h
+%such that the mass of the light CP-even Higgs boson is maximized for fixed tanβ and large
+%MA (the scale of the soft SUSY-breaking masses in the stop and sbottom sectors, which
+%sets the mass scale for the corresponding supersymmetric particles, has been fixed to 1 TeV
+%in this scenario). This scenario is useful to obtain conservative bounds on tanβ for fixed
+%values of the top-quark mass
 
@@
 \label{sec:theory_BSM_models_mhmodp}
+The $m_{h}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
+is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. This scenario, which
+was used for interpretations of MSSM Higgs boson searches at LEP, allows
+the mass of the light Higgs boson to reach the highest a-priori expected 
+value of around 135 GeV for high \mA. There is only a small area of the \mA-\tanb~plane
+in this scenario where the mass of the light Higgs boson is compatible with the
+observed 125 GeV state. The modifications to the parameters of the $m_{h}^{\text{max}}$ 
+scenario address this issue. In the $m_{h}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
+to be 1 TeV. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
+%This gives better agreement with muon g-2 results while the mhmod- scenario
+%negative stop mixing (-1.9 M_SUSY) results in better agreements with B(b->sgamma) 
+%meausrements 
+The remaining parameters are set as $\mu=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
+$m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. Figure \ref{fig:mhmodp_mh}
+shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
+that its mass is compatible with 125 GeV over a large part of the parameter space.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}
+\end{center}
+\caption{The mass of the light Higgs boson, \mh, as a function 
+of \mA~and \tanb~in the $m_{h}^{\text{mod+}}$ scenario. The white areas
+indicate masses lower than 122 GeV. The figure shows that
+the mass of the light Higgs boson is compatible with 125 GeV over a large
+part of the \mA-\tanb~plane.}
+\label{fig:mhmodp_mh}
+\end{figure}
+
+Figure \ref{fig:mhmodp_xs} shows the cross--sections of
+gluon fusion production of the \PHiggs boson and (four--flavour scheme) b-associated
+production of the \PHiggsps boson in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
+production dominates at low \tanb, while b-associated production has a larger cross--section
+at high \tanb.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
+\subfloat[$\sigma(gg\rightarrow bb\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_bbA4FS_mhmodp.pdf}}
+\end{center}
+\caption{Production cross--section of (a) gluon fusion production of the \PHiggs boson and
+(b) b--associated production (four--flavour scheme) of the \PHiggsps boson in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
+the b-associated production cross-section is larger at high \tanb.}
+\label{fig:mhmodp_xs}
+\end{figure}
+
+Figure \ref{fig:mhmodp_br} shows the branching ratio of the \PHiggs and \PHiggsps 
+into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
+high \tanb, showing how this decay channel is useful for MSSM Higgs boson searches.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[BR($\PHiggs \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
+\subfloat[BR($\PHiggsps \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
+\end{center}
+\caption{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
+ratios into $\tau\tau$ are enhanced at high \tanb.}
+\label{fig:mhmodp_br}
+\end{figure}
 
@@
 %where the ±3 GeV variation corresponds to a rough estimate of the theoretical uncertainty of the MSSM prediction for mh, due to the unknown effect of higher-order correction
-
-Gluon fusion dominance? Show decays? Or do it in the relevant subsecs?
 
@@
 \begin{figure}[h!]
-\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_xsAH.png}
-\caption{Cross-sections at $\sqrt{s}=14$ TeV as a function of
+\begin{center}
+\subfloat[$\sigma(gg\rightarrow\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsggA_hmssm.pdf}}
+\subfloat[$\sigma(bb\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_hmssm.pdf}}
+\end{center}
+\caption{Cross-sections at $\sqrt{s}=13$ TeV as a function of
 \mA~and \tanb~ in 
-the hMSSM scenario for b-associated production of \PHiggsps (top left), b-associated
-production of \PHiggs (top right), gluon fusion production of \PHiggsps (bottom left) and
-gluon fusion production of \PHiggs (bottom right). The white areas indicate cross-sections
-smaller than the minimum value on the z-axis. We can generally see the cross-sections increase
-with growing \tanb, apart from the gluon fusion cross sections which decrease with increasing
-\tanb~for low \tanb~\cite{hMSSM-2}.}
+the hMSSM scenario for (a) gluon fusion production of the \PHiggsps boson and (b)
+b-associated production (four--flavour scheme) of the \PHiggs boson. We can generally see the cross-sections increase
+with growing \tanb, apart from the gluon fusion cross section which decrease with increasing
+\tanb~for low \tanb.}
 \label{fig:hmssm_xs}
@@
 \begin{figure}[h!]
-\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_brtautau.png}
-\caption{Branching ratios of \PHiggsps (left) and \PHiggs (right) into \tautau. The
-branching ratio is enhanced at high \tanb~\cite{hMSSM-2}.} 
+\begin{center}
+\subfloat[BR$(\PHiggs\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_hmssm.pdf}}
+\subfloat[BR$(\PHiggsps\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_hmssm.pdf}}
+\end{center}
+\caption{Branching ratios of (a) the \PHiggs boson and (b) the \PHiggsps boson into \tautau. The
+branching ratio is enhanced at high \tanb.} 
 \label{fig:hmssm_brtautau}

### 2017-01-23 Theory/Theory.tex
Adding a little bit about 2HDMs

@@
 Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
-and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$.
+and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
+the choice of decay into $\Pgt\Pgt$ as search channel for the neutral Higgs bosons in the MSSM.
+Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
+in the $m_{h}^{\text{mod+}}$ scenario
+which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
+The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
+into $\Pgt\Pgt$ of \PHiggsps are of similar size.
 %Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
@@
 
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\tanb=5]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta5_FeynHiggs_HDecay.pdf}}
+\subfloat[\tanb=30]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta30_FeynHiggs_HDecay.pdf}}
+\end{center}
+\caption{Branching ratios of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario,
+at (a) \tanb=5~and (b) \tanb=30. The branching ratio into \Pgt\Pgt (blue), $b\bar{b}$ (red) 
+and \Pgm\Pgm (yellow) is enhanced at high \tanb, while the branching ratio into 
+WW (grey) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
+\label{fig:mssm_brtautau}
+\end{figure}
+
+The dominant neutral MSSM Higgs boson production processes at hadron colliders
+are slightly different from the \ac{SM} Higgs boson production processes. 
+Because the pseudoscalar A does not couple to the
+vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
+bosons is suppressed with respect to the \ac{SM} expectation, VBF and PW/PZ associated
+production do not constitute dominant production processes. Gluon fusion production is 
+the dominant production mode at low \tanb, like in the \ac{SM}. An example tree-level Feynman diagram is given in figure \ref{fig:production_mssm}a. In gluon fusion production the Higgs boson
+is produced via a quark loop. At low \tanb~values this loop is dominated by top quarks, while at 
+high \tanb~the b-quark loop dominates.
+This is a result of the enhanced coupling to down-type fermions at high \tanb.
+Another consequence of these enhanced couplings to down-type fermions at high \tanb~is the dominance of b-associated production, where the Higgs boson is produced through
+bottom quark fusion. The tree-level Feynman diagram for this process is shown in figure \ref{fig:production_mssm}b.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.pdf}}
+\subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
+\end{center}
+\caption{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
+production of neutral Higgs boson in the MSSM \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:production_mssm}
+\end{figure}
+
 \subsection{\acl{2HDM}s}
 \label{sec:theory_2HDM}
+A different approach, also leading to an extended Higgs sector with
+respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I}.
+As the name suggests \ac{2HDM}s are a generic class of models in which
+there is not one, but two Higgs doublets. The addition of a second
+Higgs doublet can also motivated by \ac{SUSY}, but also by axion models.
+An important point to note is that despite the presence of a second 
+Higgs doublet, there are no explicit \ac{SUSY} particles in the \ac{2HDM}.
+There are many different types of \ac{2HDM}, all distinguished by the couplings
+of the different Higgs bosons to bosons and fermions. The most studied of the
+\ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
+the MSSM Higgs sector. The couplings of the neutral Higgs bosons to 
+vector bosons and fermions are the same as the \ac{MSSM} couplings from table \ref{tab:mssm_couplings}.
+
+The differences between the type II \ac{2HDM} and the \ac{MSSM}
+are that $\alpha$ is a free parameter in the \ac{2HDM}, while
+in the \ac{MSSM} it is not. In addition the masses of the Higgs bosons
+are free parameters. In the \textit{alignment} limit, where $\cos{(\beta-\alpha)}$
+approaches 0, the couplings are exactly \ac{SM}-like.
 

### 2017-01-25 Hhh/Hhh.tex
Fixing up pileup reweighting comments in Hhh chapter
Fixing tables in MSSM section
Adding more on 2HDMs and SM H measurements

@@
 The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
-new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
+new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
 generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
@@
 Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
-interactions.
+interactions. The \ac{MC} samples are then reweighted so that the pile--up distribtuion matches the
+pile--up distribution in data.
 
@@
 correction factors used for this are estimated in dedicated control regions.
-
-A reweighting is applied to make the pile--up distribution in \ac{MC}
-match the distribution observed in data, as described in chapter OBJECTS.
 
@@
 The results of the analysis are interpreted in two scenarios, the low \tanb~MSSM
-scenario, and a type II two--Higgs doublet model (2HDM), both discussed in section THEORY
+scenario, and a type II two--Higgs doublet model (2HDM), both discussed in chapter \ref{chap:theory}.
 
@@
 \label{sec:hhh_results_modeldep_2HDM}
-NOTE: move description of 2HDM to theory section + expand
-A 2HDM of type II has more free parameters than specific MSSM benchmark scenarios: the physical masses of the Higgs bosons (\mh, \mH,
-\mA, \mHplus), the ratio of the vacuum expectation values of the two Higgs doublets (\tanb),
-the CP-even Higgs mixing angle ($\alpha$) and $m_{12}^{2} = m_{\PHiggsps}^{2}[\tan{\beta}/(1+\tan{\beta}^2)]$.
-To leave two free parameters, it is enough to fix the masses of the physical Higgs bosons. For this
-interpretation the assumption that \mA = \mH = \mHplus = $300$~GeV, and \mh = $125$~GeV, is made.
+As we have seen in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
+free parameters than a particular \ac{MSSM} benchmark scenario. To leave
+just two free parameters, it is enough to fix the masses of the five Higgs bosons
+and take the quartic couplings to be 0.
+For the interpretation shown here the assumption that \mA=\mH=\mHplus=$300$ GeV is made.
 
@@
 \begin{tabular}{@{}ll@{}}
-%\toprule
+\toprule
 \textbf{Decay} & \textbf{Coupling}\\
@@
 $\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
-%\bottomrule
+\bottomrule
 \end{tabular}
@@
 \label{sec:hhh_results_modeldep_lowtb}
-The low \tanb~MSSM scenario, as discussed in section THEORY
+The low \tanb~MSSM scenario, as discussed in section \ref{sec:mssm_theory_lowtb}
 is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb~values

### 2017-01-25 MSSM/MSSM.tex
Adding more on 2HDMs and SM H measurements

@@
 production in the gluon fusion (gg$\phi$) and b-associated (bb$\phi$) production 
-modes (see chapter [THEORY]) and decay into $\Pgt\Pgt$. 
+modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
 In addition to the upper limits on cross--section times branching ratio of these two processes, 
@@
 The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
-scenario and the hMSSM scenario. Both scenarios are described in chapter [THEORY].
+scenario and the hMSSM scenario. Both scenarios are described in chapter \ref{chap:theory}.
 

### 2017-01-25 Theory/Theory.tex
Adding more on 2HDMs and SM H measurements

@@
 \label{sec:theory_smH}
+The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
+searches for the boson had to be conducted over a large range of
+masses. Searches for the Higgs boson at \ac{LEP} did not lead
+to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
+providing a lower search limit. Subsequent studies at the 
+Tevatron did also not lead to discovery of the Higgs boson, but did provide
+an additional excluded masses range of 140-186 GeV at 95\% \ac{CL} \cite{TEV-Higgs}.
+
+On the fourth of July 2012 the ATLAS and CMS collaborations
+announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
+The observations were based on excesses in the search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$.
+More data were collected and analysed during the remainder of 2012, and subsequent studies 
+grew the confidence in this boson being compatible with the standard model Higgs boson. The ATLAS and CMS combined
+mass measurement using the full dataset of Run 1 of the \ac{LHC} 
+found \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
+The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
+shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. Some discrepancies
+with the \ac{SM} predicition do remain, and so the measurements of \ac{SM} Higgs boson
+properties are certainly not finished yet.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Gluon fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ggH.pdf}}
+\subfloat[Vector boson fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_qqH.pdf}}~\\
+\subfloat[W/Z associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_VH.pdf}}
+\subfloat[\ttbar associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ttH.pdf}}
+\end{center}
+\caption{Feynman diagrams at tree level for the dominant Higgs boson production modes at
+the \ac{LHC}.}
+\label{fig:theory_smhprod}
+\end{figure}
+
+Figure \ref{fig:theory_smhprod} shows the dominant Higgs boson production modes
+at the \ac{LHC}. From the production cross sections for each mode in figure
+\ref{fig:theory_smhxsbr} we see that gluon fusion is by far dominant. The other modes
+shown have smaller cross sections, but are of importance due to their topologies, with
+additional leptons or jets in the final state. Tagging such topologies can reduce the size
+of the \ac{SM} background.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\ac{SM} H production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
+\subfloat[\ac{SM} H branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
+\end{center}
+\caption{(a) standard model Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) standard model
+Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
+\label{fig:theory_smhxsbr}
+\end{figure}
+
+It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}
+that the two discovery channels $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow \PZ
+PZ$ have smaller branching ratios than many other channels. These two channels are very sensitive
+due to the small backgrounds and the excellent photon and lepton energy resolution the detectors provide.
+
+During Run 2
 
@@
 \label{sec:theory_BSM}
+The \ac{SM} has been successfully tested to high accuraccy. However,
+some issues remain that cannot be addressed by the \ac{SM} alone.
+For example BLAH BLAH
+
+Therefore \acf{BSM} theories have been developed
+that aim to cover some of these issues. One of the most
+popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
+that there is a symmetry between bosons and fermions. Every fermionic
+\ac{SM} particle has a bosonic superpartner (named `s'+name of fermion, e.g.
+sbottom, selectron,...), and every bosonic \ac{SM} particle
+has a fermionic superpartner (named boson name + `ino', e.g. higgsino, Wino,...).
+
+If this symmetry were unbroken the \ac{SUSY} particles must
+have the same mass as their \ac{SM} partners. However, we know that
+this is not the case as such particles would have been detected a long time ago. The 
+only possibility is then that \ac{SUSY} is a broken symmetry and the superpartners
+are heavier than their \ac{SM} equivalents.
 
@@
 the tree-level masses and couplings of the Higgs bosons in the MSSM can be
-significantly altered by radiative corrections. The dominat effect is from
+significantly altered by radiative corrections. The dominant effect is from
 incomplete cancellation of the stop- and top-loop corrections, which
-do not completely cancel as SUSY is a broken symmetry. FIND REFERENCE FOR THIS
+do not completely cancel as SUSY is a broken symmetry.
 
-The couplings of the neutral Higgs bosons to bosons and fermions 
+The tree-level couplings of the neutral Higgs bosons to bosons and fermions 
 are modified with respect to the \ac{SM} couplings, by factors
@@
 \begin{center}
-\caption{Couplings in the MSSM, as multiplicative factors with
+\caption{Tree-level couplings in the MSSM, as multiplicative factors with
 respect to the \ac{SM} couplings}
@@
 
-In the \textit{decoupling limit}, when \mA$>>m_{Z}$, the mixing
+In the \textit{decoupling limit}, when \mA$>>m_{Z}$ and $\cos{(\beta-\alpha)}$ tends
+to 0, the mixing
 angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
@@
 A different approach, also leading to an extended Higgs sector with
-respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I}.
+respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I,2HDM-II}.
 As the name suggests \ac{2HDM}s are a generic class of models in which
@@
 There are many different types of \ac{2HDM}, all distinguished by the couplings
-of the different Higgs bosons to bosons and fermions. The most studied of the
+of the different Higgs bosons to bosons and fermions. The 
+most general potential for a CP-conserving 2HDM has 9 free parameters,
+taken as \tanb, the mixing angle $\alpha$, already discussed in 
+the context of the \ac{MSSM}, the masses of the five Higgs bosons,
+and quartic couplings appearing in the potential. The most studied of the
 \ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
-the MSSM Higgs sector. The couplings of the neutral Higgs bosons to 
-vector bosons and fermions are the same as the \ac{MSSM} couplings from table \ref{tab:mssm_couplings}.
+the MSSM Higgs sector. The tree-level couplings of the neutral Higgs bosons to 
+vector bosons and fermions are the same as the tree-level \ac{MSSM} couplings 
+from table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
+%the \AtoZh~coupling is proportional to $\cos{(\beta-\alpha)}, like the \Htohh~coupling.
 
-The differences between the type II \ac{2HDM} and the \ac{MSSM}
-are that $\alpha$ is a free parameter in the \ac{2HDM}, while
-in the \ac{MSSM} it is not. In addition the masses of the Higgs bosons
-are free parameters. In the \textit{alignment} limit, where $\cos{(\beta-\alpha)}$
-approaches 0, the couplings are exactly \ac{SM}-like.
+The behaviour of the \ac{2HDM} couplings in the \textit{alignment} limit,
+where $\cos{(\beta-\alpha)} = 0$, differs from that of the \ac{MSSM} couplings.
+In particular, in the alignment limit the decays \AtoZh~and \Htohh vanish
+in the \ac{2HDM}. This is due to the fact that the coupling is 
+proportional to $\cos{(\beta-\alpha)}$ and there are no radiative corrections
+to make the branching ratio nonzero.
+
+The inclusive $\sigma\times$branching ratios for production of a \PHiggs boson 
+and decays into various states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
+example of a type-II \ac{2HDM}, at two \tanb points. Figure \ref{fig:2hdm_Hxsbr}b 
+shows the inclusive $\sigma\times$branching ratios for production and decay
+of a \PHiggsps boson in the same type-II \ac{2HDM} example, at two \tanb~points. At
+low \tanb~the $\sigma\times$branching ratio for \Htohh production and decay and \AtoZh production
+and decay are enhanced for $250\leq m_{\PHiggs}\leq 350$ GeV and $220 \leq m_{\PHiggsps} \leq 350$ GeV, respectively.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
+\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
+\end{center}
+\caption{Inclusive production cross--section times branching ratio for an example
+of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
+top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
+figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
+\AtoZh decays are enhanced for masses up to 350 GeV \cite{2HDM-II}.}
+\label{fig:2hdm_Hxsbr}
+\end{figure}
 
@@
 \subsection{MSSM scenarios at low \tanb}
+\label{sec:mssm_theory_lowtb}
 A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 

### 2017-01-30 Hhh/Hhh.tex
Adding some more stuff

@@
 
-The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
+The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
 new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more

### 2017-01-30 Theory/Theory.tex
Adding some more stuff

@@
-\chapter{Introduction and theory}
+\chapter{Theory and motivation}
 \label{chap:theory}
+To understand and motivate the searches presented in chapters 
+\ref{chap:hhh} and \ref{chap:mssm} it is important
+to understand the theory and phenomenology behind them. 
+This chapter describes the \acl{SM} of particle physics, the
+motivations for \acl{SUSY} and the phenomenology of Higgs
+sectors beyond the \acl{SM}.
 
-\section{The standard model of particle physics}
+\section{The \acl{SM} of particle physics}
 \label{sec:theory_sm}
+The \ac{SM} of particle physics is a theory that describes the weak and strong
+nuclear forces, plus the \ac{EM} force, and the interaction of those forces
+with particles. The \ac{SM} is a \ac{QFT} in which matter particles
+are represented by spin-$\frac{1}{2}$ fermions, with the forces represented
+by spin-1 bosons.
+
+\subsection{Fundamental particles and forces}
+\label{sec:theory_sm_particles}
+In the \ac{SM} there are twelve fundamental fermions, six quarks and
+six leptons. The quarks interact via both strong nuclear force and the 
+electroweak force, while
+the leptons only interact via the electoweak force.
+Each of the fermions has a corresponding antiparticle
+with opposite quantum numbers. The quarks and leptons
+are divided into three generations. The particles from different
+generations have similar properties, apart from the mass which increases
+for each generation. The quarks and leptons are summarised in 
+table \ref{tab:theory_fermions}.
+
+\begin{table}[htp]
+\begin{center}
+\caption{The fundamental fermions}
+\begin{tabular}{@{}llll@{}}
+\toprule
+ & \textbf{1st generation} & \textbf{2nd generation} & \textbf{3d generation}\\
+\midrule
+\textbf{Quarks} & & & \\
+\midrule
+Charge: +$\frac{2}{3}$& up (\Pup)  & charm (\Pcharm) & top (\Ptop) \\
+Charge: -$\frac{1}{3}$& down (\Pdown) & strange (\Pstrange) & bottom (\Pbottom) \\
+\midrule
+\textbf{Leptons} & & & \\
+\midrule
+Charge: -1 & electron (\Pe) & muon (\Pgm) & tau (\Pgt) \\
+Charge: 0  & electron neutrino ($\Pgn_{\Pe}$) & muon neutrino ($\Pgn_{\Pgm}$) & tau neutrino ($\Pgn_{\Pgt}$)\\
+\bottomrule
+\end{tabular}
+\label{tab:theory_fermions}
+\end{center}
+\end{table}
+
+The forces in the \ac{SM} are mediated by spin-1 bosons: The gluon (\Pgluon),
+which carries the strong force, the photon (\Pphoton) as the
+electromagnetic force carrier, and the $\PW^{\pm}$ and \PZ bosons, the
+force carriers of the weak nuclear force.
+
+The particles that interact via the strong force carry colour charge (red, green, or blue),
+as do their mediators, the gluons. The interactions in the \ac{QFT} of the
+strong force, called \ac{QCD}, are governed by an SU(3) (colour) symmetry.
+%There are 8 gluons due to the SU(3) symmetry, colour octet and a colour singlet, but
+%if there was a colour singlet it should occur as a free particle while it does not.
+%See chapter 285 of griffiths
+The quarks are never observed in isolation but always in bound
+hadron states, which is referred to as confinement. Due to asymptotic
+freedom \cite{asympt-I,asympt-II}, the strong coupling strength decreases at 
+high energy (short distances). More detailed introductions to \ac{QCD} can 
+be found in ref. \cite{griffiths}.
+
+Particles that carry electric charge interact via the 
+electromagnetic force, summarised in by the rules of \ac{QED}. 
+The weak interaction, governed by weak isospin transformations,
+only couples to the left-handed part of the fermion states. In 
+general a fermion state can be decomposed into its left- and right-handed parts
+\begin{equation}\label{eqn:leftright}
+\chi=\psi_R+\psi_L,
+\end{equation}
+and only $\psi_L$ will interact via the weak force. Handedness and
+helicity have the same eigenstates for massless particles, and as
+such neutrinos, which are massless in the \ac{SM}, must all be left-handed.
+The observation of neutrino flavour oscillations since the formulation of
+the \ac{SM} implies that neutrinos do have a small but finite mass
+and so there must be right-handed neutrinos in the \ac{SM}. This is
+not discussed further here ADD REFERENCE.
+The weak isospin acts on doublets of left-handed lepton pairs, while
+the right-handed leptons transform as singlet states. This works similarly
+for the quarks, with weak isospin acting three left-handed doublets and
+six right-handed singlets. Note that the weak eigenstates of the quarks
+differ from the physical states, which mix via the \ac{CKM}-matrix CITATION
+in charged current interactions as
+\begin{equation}\label{eqn:ckm_matrix}
+\begin{pmatrix} d' \\
+s' \\
+b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
+V_{cd} & V_{cs} & V_{cb} \\
+V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
+s\\
+b \end{pmatrix}.
+\end{equation}
+
+\subsection{The electroweak force}
+\label{sec:theory_sm_ewk}
+The unification of the weak and electromagnetic forces, introduced
+in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk},
+is a key component of the \ac{SM}. The unification of these forces,
+governed by an SU(2)$\times$U(1) symmetry, implies the presence of a charged
+current. A quantum number, weak hypercharge $Y$, is introduced. Weak
+hypercharge is related to weak isospin $I_{1,2,3}$ and electric charge as
+\begin{equation}\label{eqn:hypercharge}
+Q=I_3 + \frac{1}{2}Y.
+\end{equation}
+We then have the three weak isospin fields, $W_{\mu}^{i}$, and the
+weak hypercharge field $Y_{\mu}$, which mix to form the physical \Pphoton,
+\PZ and $\PW^{\pm}$ states as
+\begin{align}\label{eqn:ewk_propagators}
+\PW^{\pm} &= \frac{1}{\sqrt{2}}(W_{\mu}^1 \mp i W_{\mu}^2),\\
+A_{\mu} &= W_{\mu}^3\sin{\theta_W} + Y_{\mu}\cos{\theta_W},\\
+Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - Y_{\mu}\sin{\theta_W}.
+\end{align}
+In these equations $A_{\mu}$ is the photon field and $Z_{\mu}$ the \PZ field.
+The weak mixing angle $\theta_W$ is related to the weak (g) and electromagnetic (g')
+coupling constants as
+\begin{equation}\label{eqn:thetaw}
+g\sin{\theta_W} = g'\cos{\theta_W}
+\end{equation}
+
+The gauge invariance of the Lagrangian would be broken
+by the addition of mass terms. For the photon this is fine, as we know it
+is massless, but it is known that the \PW and \PZ bosons, as well as fermions, 
+are massive. This means electroweak symmetry must be broken. In the \ac{SM}
+this is achieved via the Higgs mechanism.
+
+\subsection{The Higgs mechanism}
+\label{sec:theory_sm_higgsmech}
+The masses of the vector bosons are generated via the
+Higgs mechanism, proposed in the 1960s by Englert and Brout \cite{englertbrout}
 
@@
 The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
-shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. Some discrepancies
-with the \ac{SM} predicition do remain, and so the measurements of \ac{SM} Higgs boson
+shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, through
+this combination the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$, while
+the individual experiments did not reach a significance upwards of 5$\sigma$ in this channel during Run 1.
+Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
+and so the measurements of \ac{SM} Higgs boson
 properties are certainly not finished yet.
@@
 
-During Run 2
+During Run 2 of the LHC, standard model Higgs boson measurements, and searches for the 
+standard model Higgs boson in decay channels not previously established, have 
+already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
+as has the decay in to $ZZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}. In addition, measurements
+of $H\rightarrow WW$ are under way \cite{CMSHWW2016,ATLASHWW2016}. Establishment of the decay of 
+$H\rightarrow b\bar{b}$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $H\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
+is still to be achieved.
+Finally, searches for ttH production, important to establish the top-Higgs coupling, have also been carried 
+out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
+keeps growing, more such measurements will be made to shed more light on the standard model Higgs boson.
 
@@
 \label{sec:theory_BSM}
-The \ac{SM} has been successfully tested to high accuraccy. However,
-some issues remain that cannot be addressed by the \ac{SM} alone.
-For example BLAH BLAH
+The \ac{SM} has been successfully tested to high accuraccy \cite{pdg-2014}. However,
+some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
+For example, it does not provide a candidate for dark matter. 
+Additionally, the energy dependence of the running coupling constants
+do not converge the GUT scale, and the force of gravity does not
+appear in the \ac{SM}, no quantum theory can be formulated for it.
 
-Therefore \acf{BSM} theories have been developed
-that aim to cover some of these issues. One of the most
+These issues aside, one of the most pressing issues regarding
+the Higgs sector of the \ac{SM} is the hierarcy problem.
+The \ac{SM}
+is accepted to be an effective field theory that describes
+the elementary particles and their interactions well up to an energy scale $\Lambda$.
+This is the energy scale at which new physics must enter.
+We know that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
+gravitational effects start to become important in that region. $\Lambda$ enters
+the corrections due to fermion and boson loops to the Higgs boson mass quadratically \cite{MSSM-carena-haber}:
+\begin{equation}\label{eqn:mh_hierarchy}
+m_{h_{\text{SM}}}^2  = (m_h^2)_0 + \mathcal{O}(\Lambda^2).
+\end{equation}
+Thus assuming that there is no new physics all the way up to
+the Planck scale the observation \mh=125 GeV would only be compatible with $\Lambda$ of order $10^{19}$ GeV
+if there was extreme fine-tuning of the bare Higgs boson mass $(m_h^2)_0$.
+
+Many \acf{BSM} theories have been developed
+that can to address the hierarchy problem and some of the other issues 
+discussed. One of the most
 popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
@@
 If this symmetry were unbroken the \ac{SUSY} particles must
-have the same mass as their \ac{SM} partners. However, we know that
-this is not the case as such particles would have been detected a long time ago. The 
+have the same mass as their \ac{SM} partners. However, if that had 
+been the case such particles would have been detected a long time ago. The 
 only possibility is then that \ac{SUSY} is a broken symmetry and the superpartners
-are heavier than their \ac{SM} equivalents.
+are heavier than their \ac{SM} equivalents. It is important to note
+that the fermion and boson loops contribute to the Higgs boson
+mass corrections with opposite sign, and so, if \ac{SUSY}
+was an exact symmetry their contributions to the Higgs boson mass
+would cancel. Due to 
+symmetry breaking the contributions of \ac{SM} particles 
+and their supersymmetric partners do not completely cancel. If
+the \ac{SUSY} breaking scale, where new particles should
+be found, is much larger than a few TeV further fine-tuning of 
+the bare Higgs boson mass would be required \cite{MSSM-carena-haber,SUSY-primer}.
+Apart from solving the hierarchy problem, \ac{SUSY} addresses some
+of the other aforementioned issues. The lightest \ac{SUSY} particle
+would be a candidate for dark matter if it were stable \cite{SUSY-primer}. On top of that
+assuming \ac{SUSY} means the electroweak and strong coupling
+constants intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.
 
-\subsection{The Higgs sector of the MSSM}
+The simplest supersymmetric extension of the \ac{SM}, the \ac{MSSM} \cite{SUSY-primer}, only adds the minimum
+number of particles and fields required to formulate a supersymmetric theory.
+%And conserves R-parity, see section 6.2 of the SUSY primer
+
+\subsection{The Higgs sector of the \ac{MSSM}}
 \label{sec:theory_MSSM_H}
 At least two Higgs doublets are required in the
-Higgs sector of the MSSM due to the supersymmetric
+Higgs sector of the \ac{MSSM} due to the supersymmetric
 background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
@@
 In Run-2 of the \ac{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
-have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. Other searches
-for heavy Higgs bosons with decays to other final states are also in progress as the Run-2 data keep
-amassing.
+have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
+Similar searches have been performed by \acs{ATLAS} \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
+are being searched for in other channels too, with some results for decays into \ttbar \cite{ATLASHttbar}, 
+ZZ \cite{CMSHZZ2016,ATLASHZZ2016}, and WW \cite{ATLASHeavyHWW} already public.
+In addition, searches for charged
+Higgs bosons \cite{ATLASHplustaunu,ATLASHplustb,CMSHplustaunu} and
+di-Higgs searches \cite{ATLASHbbgamgam,ATLASHgamgamWW,ATLASHhhbbbb,CMSbbgamgam,CMSHbbtautau,CMSHbbWW}, both in 
+various final states, have been performed. The interest in these searches will remain, and so
+as more data are collected during Run 2 more of such searches will be performed.
 

### 2017-01-31 Theory/Theory.tex
Fixing up theory :-)

@@
 
-\subsection{Fundamental particles and forces}
+\subsection{Fundamental particles}
 \label{sec:theory_sm_particles}
@@
 
+\subsection{Fundamental forces}
+\label{sec:theory_sm_forces}
+%Symmetries of the Lagrangian describing a physical system lead
+%to conserved quantities, as shown by Noether's theorem \cite{noethersthm}.
+%This is and important concept for the description of particle interactions
+%under different forces: invariance (symmetry) under a certain 
+%transformation group is imposed on 
+%the Lagrangians describing the fundamental forces. This is brought
+%about as local gauge invariance, where the Lagrangians 
+%are required to be invariant under a local phase transformation
+%plus a gauge transformation. The local phase transformation
+%might introduce additional derivatives of potentials, taken care of by gauge transf.
 The forces in the \ac{SM} are mediated by spin-1 bosons: The gluon (\Pgluon),
@@
 
-Particles that carry electric charge interact via the 
-electromagnetic force, summarised in by the rules of \ac{QED}. 
-The weak interaction, governed by weak isospin transformations,
-only couples to the left-handed part of the fermion states. In 
-general a fermion state can be decomposed into its left- and right-handed parts
+The weak and electromagnetic forces were unified into the
+electroweak force. The unification of these forces was introduced 
+in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk},
+is a key component of the \ac{SM}. Electroweak theory,
+governed by an SU(2)$\times$U(1) symmetry, implies the presence of weak
+neutral currents.
+
+%Particles that carry electric charge interact via the
+%electromagnetic force, while the weak force works
+%between particles carrying weak isospin.
+The weak interaction, working on all fermions,
+only couples to the left-handed part of fermion states. In 
+general a fermion state $\chi$ can be decomposed into its left- and right-handed parts
 \begin{equation}\label{eqn:leftright}
@@
 \end{equation}
-and only $\psi_L$ will interact via the weak force. Handedness and
-helicity have the same eigenstates for massless particles, and as
-such neutrinos, which are massless in the \ac{SM}, must all be left-handed.
+and only $\psi_L$ will interact via the weak force. For massless particles
+the general state $\chi$ is not a mixture of left-handed and right-handed parts,
+but is either completely left-handed or right-handed. As such neutrinos, which are
+massless in the \ac{SM}, must all be left-handed. %CAREFUL: handedness =/= helicity
 The observation of neutrino flavour oscillations since the formulation of
 the \ac{SM} implies that neutrinos do have a small but finite mass
-and so there must be right-handed neutrinos in the \ac{SM}. This is
-not discussed further here ADD REFERENCE.
-The weak isospin acts on doublets of left-handed lepton pairs, while
-the right-handed leptons transform as singlet states. This works similarly
-for the quarks, with weak isospin acting three left-handed doublets and
-six right-handed singlets. Note that the weak eigenstates of the quarks
-differ from the physical states, which mix via the \ac{CKM}-matrix CITATION
+and so there must be right-handed neutrinos in the \ac{SM}. This will
+not be discussed here, for a more detailed account see reference \cite{pdg-2014}.
+%The weak isospin acts on doublets of left-handed lepton pairs, while
+%the right-handed leptons transform as singlet states. This works similarly
+%for the quarks, with weak isospin acting three left-handed doublets and
+Another feature of the weak force is that the weak eigenstates of the quarks
+differ from the physical states, which mix via the \ac{CKM}-matrix \cite{ckm-matrix-cabibbo,ckm-matrix-KM}
 in charged current interactions as
@@
 
-\subsection{The electroweak force}
-\label{sec:theory_sm_ewk}
-The unification of the weak and electromagnetic forces, introduced
-in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk},
-is a key component of the \ac{SM}. The unification of these forces,
-governed by an SU(2)$\times$U(1) symmetry, implies the presence of a charged
-current. A quantum number, weak hypercharge $Y$, is introduced. Weak
-hypercharge is related to weak isospin $I_{1,2,3}$ and electric charge as
-\begin{equation}\label{eqn:hypercharge}
-Q=I_3 + \frac{1}{2}Y.
+Going back to the symmetry of the unified electroweak forces,
+The SU(2) part of the symmetry is built from the weak
+isospin generators $I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$,
+where $\sigma_i$ are the Pauli spin matrices. The U(1)
+symmetry comes from the weak hypercharge generator $Y$, which
+is related to weak isospin and electric charge as $Q = I_3 + \frac{1}{2}Y$.
+
+Associated gauge fields are the three weak fields $W_{\mu}^{i}$ and the
+weak hypercharge field $B_{\mu}$. These four fields mix to form the physical \Pphoton,
+\PZ and $\PW^{\pm}$ states as
+\begin{equation}\label{eqn:ewk_propagators_W}
+\PW^{\pm} &= \frac{1}{\sqrt{2}}(W_{\mu}^1 \mp i W_{\mu}^2),
 \end{equation}
-We then have the three weak isospin fields, $W_{\mu}^{i}$, and the
-weak hypercharge field $Y_{\mu}$, which mix to form the physical \Pphoton,
-\PZ and $\PW^{\pm}$ states as
-\begin{align}\label{eqn:ewk_propagators}
-\PW^{\pm} &= \frac{1}{\sqrt{2}}(W_{\mu}^1 \mp i W_{\mu}^2),\\
-A_{\mu} &= W_{\mu}^3\sin{\theta_W} + Y_{\mu}\cos{\theta_W},\\
+\begin{equation}\label{eqn:ewk_propagators_phot}
+A_{\mu} &= W_{\mu}^3\sin{\theta_W} + Y_{\mu}\cos{\theta_W},
+\end{equation}
+\begin{equation}\label{eqn:ewk_propagators_Z}
 Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - Y_{\mu}\sin{\theta_W}.
-\end{align}
+\end{equation}
 In these equations $A_{\mu}$ is the photon field and $Z_{\mu}$ the \PZ field.
@@
 \begin{equation}\label{eqn:thetaw}
-g\sin{\theta_W} = g'\cos{\theta_W}
+\begin{split}
+&g\sin{\theta_W} = g'\cos{\theta_W} \Rightarrow \\
+&\sin{\theta_W} = \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}
+\end{split}
 \end{equation}
 
-The gauge invariance of the Lagrangian would be broken
-by the addition of mass terms. For the photon this is fine, as we know it
-is massless, but it is known that the \PW and \PZ bosons, as well as fermions, 
-are massive. This means electroweak symmetry must be broken. In the \ac{SM}
+Neutral weak-current interactions were discovered in 1973 at the Gargamelle
+bubble chamber experiment at \acs{CERN} \cite{gargamelle}. This discovery was 
+followed 10 years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
+and UA2 collaborations at \acs{CERN}.
+
+An issue with electroweak theory is that the gauge invariance of the Lagrangian would be
+broken by the addition of mass terms for the gauge bosons. However, the \PW and \PZ bosons are known to be massive. 
+Furthermore fermion mass terms would also not be gauge invariant, and it is also known
+that the fermions are massive.
+This means electroweak symmetry must be broken. In the \ac{SM}
 this is achieved via the Higgs mechanism.
@@
 The masses of the vector bosons are generated via the
-Higgs mechanism, proposed in the 1960s by Englert and Brout \cite{englertbrout}
+Higgs mechanism, proposed in the 1960s by Englert and Brout \cite{englertbrout},
+Higgs \cite{higgs-I,higgs-II,higgs-III} and Guralnik, Hagen and Kibble \cite{GHK}.
+The idea is to add a field that is symmetric under gauge transformations, but
+has a nonzero vacuum expectation value and thus breaks the symmetry spontaneously.
+According to Goldstone's theorem \cite{goldstone-theorem,goldstone-theorem-2} a 
+consequence of spontaneous symmetry breaking is the appearance of a 
+massless scalar (Goldstone boson) for each broken generator.
+
+The simplest addition to achieve this is a complex doublet,
+\begin{equation}\label{eqn:phi_hfield}
+\Phi = \begin{pmatrix} \phi^{+} \\
+\phi^{0} \end{pmatrix}.
+\end{equation}
+This field has an associated Lagrangian
+\begin{equation}\label{eqn:higgs_gen_lag}
+\begin{split}
+\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, where we choose, }\\
+V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda})^2,
+\end{split}
+\end{equation}
+Where $\lambda$ and $\mu^2$ are two real parameters, and $\lambda>0$ is needed for stability
+of the vacuum. To get spontaneous symmetry breaking we require $\mu^2>0$.
+
+Under a local $SU(2)\times U(1)$ transformation, with hypercharge Y=$\frac{1}{2}$
+the resulting transformation of the field is,
+\begin{equation}\label{eqn:hfield_trsf}
+\begin{pmatrix} \phi^+ \\
+\phi^0 \end{pmatrix} = \exp{\frac{i}{2}(\vec{\theta(x)}\cdot\vec{\sigma} + \rho(x))}
+\begin{pmatrix} \phi^+ \\
+\phi^0 \end{pmatrix}, 
+\end{equation}
+where $\vec{\sigma}$ are the Pauli spin matrices and $\vec{\theta(x)}$ and $\rho(x)$
+are functions of the space-time coordinates. From such a transformation
+the covariant derivative is required to be
+\begin{equation}\label{eqn:H_cov_deriv}
+D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'Y_{\mu}
+\end{equation}
+In the vacuum state we must have $V(\Phi^{\dagger}\Phi) =0$, which happens for nonzero values of $\Phi$,
+and we can choose $\phi^+$ = 0 and $\phi^0$ real to get:
+%\begin{equation}\label{eqn:vacuum_expt}
+%\begin{split}
+%&\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda} = 0 \Rightarrow \\
+%&\Phi^{\dagger}\Phi = \frac{\mu^2}{2\lambda} \Rightarrow\\
+%&\phi^{+*}\phi^+ + \phi^{0*}\phi^0 = \frac{\mu^2}{2\lambda} \text{ and choosing } \phi^+ \text{ = 0 and } \phi^0 \text{ to be real,}\\
+%&\phi^0 = \frac{v}{\sqrt{2}} \text{ where } v \text{ is real and} v^2=\frac{\mu^2}{\lambda}.
+%\end{split}
+%\end{equation}
+\begin{equation}\label{eqn:field_vev}
+\langle 0 | \Phi | 0 \rangle = \begin{pmatrix} 0 \\
+\frac{v}{\sqrt{2}} \end{pmatrix},
+\end{equation}
+where $v$ is real and $v^2 = \frac{\mu^2}{\lambda}$.
+
+Looking at fluctuations around the vacuum state,
+\begin{equation}\label{eqn:fluctvac}
+\begin{split}
+&\delta\Phi = \frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)\Phi\\
+&=\frac{i}{2}\begin{pmatrix} \theta_3 + \rho & \theta_1 - i\theta_2 \\
+\theta_1+i\theta_2 & \rho - \theta_3 \end{pmatrix} \begin{pmatrix} 0\\
+\frac{v}{\sqrt{2}} \end{pmatrix}.
+\end{split}
+\end{equation}
+Requiring $\delta\Phi=0$, we have $\theta_1=\theta_2=0$ and $\rho=\theta_3$, 
+and the only remaining generator that leaves the field 
+invariant is $\frac{i}{2}\theta_3 + Y = I_3 +Y$ is the U(1) group. Denoting the 
+remaining generators as $\vec{b}$, and parameterising the field as an expansion around the
+vacuum state gives:
+\begin{equation}\label{eqn:vev_expansion}
+\Phi = \exp{\frac{i}{\sqrt{2}v}\vec{\theta}\cdot\vec{b}}\begin{pmatrix} 0 \\
+\frac{1}{\sqrt{2}} (v+H) \end{pmatrix}.
+\end{equation}
+By choosing the appropriate gauge the Goldstone bosons $\vec{\theta}$
+can be eliminated. They become the longitudinal degrees of freedom of the \PW and \PZ 
+bosons. This leaves us with
+\begin{equation}\label{eqn:vev_expansion_satisfied}
+\Phi = \begin{pmatrix} 0 \\
+\frac{1}{\sqrt{2}}(v+H) \end{pmatrix}
+\end{equation}
+Substituting this into the Lagrangian of equation \ref{eqn:higgs_gen_lag}, 
+and using the definitions of $\PW_{\mu}^{\pm}$ and $\PZ_{\mu}$ from 
+equations \ref{eqn:ewk_propagators}, we get
+\begin{equation}\label{eqn:completed_lagrangian}
+\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}H\partial^{\mu}H -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu^2H^2  + \text{terms of order 3 and up in the fields}.
+\end{equation}
+This gives us masses for the \PW bosons as $m_{\PW} = \frac{gv}{2}$ and a mass
+for the \PZ boson as $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. The photon remains massles. 
+The remaining mass term is for the field $H$, the
+Higgs field, which has a mass $m_{H} = \sqrt{2\mu^2}$.
+%Mass term : -1/2m_X^2. However for m_W note W_mu+Wmu- = 1/2(W_mu^1+iW_mu^2)(W_mu^1-iW_mu^2) = 
+%1/2*(W_mu^1W_mu^1+W_mu^2W_mu^2). But also W+^2+W^-2 = W1^2+W2^2 so masses end up the same
+
+Using the developments so far we can also add fermion masses
+through Yukawa couplings between the fermion- and Higgs fields
+\begin{equation}\label{eqn:yukawa_coupl}
+\lambda_f(\bar{\psi_L}\Phi\psi_R + \bar{\psi_R}\Phi\psi_L),
+\end{equation}
+where $\lambda_f$ are coupling constants specific to each fermion, $\lambda_f \propto m_f$.
+This means that heavier fermions have stronger couplings to the Higgs boson.
 

### 2017-01-31 Theory/Theory.tex
Some of my own editing...

@@
 \label{sec:theory_sm_particles}
-In the \ac{SM} there are twelve fundamental fermions, six quarks and
-six leptons. The quarks interact via both strong nuclear force and the 
-electroweak force, while
-the leptons only interact via the electoweak force.
+In the \ac{SM} there are twelve fundamental fermions, six which
+interact via the strong nuclear force (quarks) and six that do not (leptons).
 Each of the fermions has a corresponding antiparticle
 with opposite quantum numbers. The quarks and leptons
-are divided into three generations. The particles from different
-generations have similar properties, apart from the mass which increases
-for each generation. The quarks and leptons are summarised in 
+are divided into three generations, with corresponding particles from different
+generations sharing the same properties apart from their mass.
+The quarks and leptons are summarised in 
 table \ref{tab:theory_fermions}.
@@
 %might introduce additional derivatives of potentials, taken care of by gauge transf.
-The forces in the \ac{SM} are mediated by spin-1 bosons: The gluon (\Pgluon),
-which carries the strong force, the photon (\Pphoton) as the
-electromagnetic force carrier, and the $\PW^{\pm}$ and \PZ bosons, the
+The forces in the \ac{SM} are mediated by spin-1 bosons: the gluon (\Pgluon),
+which carries the strong force, the photon (\Pphoton) 
+mediating the electromagnetic force, and the $\PW^{\pm}$ and \PZ bosons, the
 force carriers of the weak nuclear force.
 
-The particles that interact via the strong force carry colour charge (red, green, or blue),
-as do their mediators, the gluons. The interactions in the \ac{QFT} of the
+The quantum number associated with the strong force is colour, which
+is carried both by quarks and gluons.
+The interactions in the \ac{QFT} of the
 strong force, called \ac{QCD}, are governed by an SU(3) (colour) symmetry.
@@
 %See chapter 285 of griffiths
-The quarks are never observed in isolation but always in bound
-hadron states, which is referred to as confinement. Due to asymptotic
-freedom \cite{asympt-I,asympt-II}, the strong coupling strength decreases at 
-high energy (short distances). More detailed introductions to \ac{QCD} can 
-be found in ref. \cite{griffiths}.
+Characteristics of \ac{QCD} include confinement, meaning quarks are always observed in bound
+hadron states, and asymptotic
+freedom \cite{asympt-I,asympt-II}. Due to asymptotic freedom the 
+strong coupling strength decreases at 
+high energy (or short distances), making the force weaker. 
+A more detailed introduction to \ac{QCD} can 
+be found in Ref. \cite{griffiths}.
 
-The weak and electromagnetic forces were unified into the
-electroweak force. The unification of these forces was introduced 
-in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk},
-is a key component of the \ac{SM}. Electroweak theory,
-governed by an SU(2)$\times$U(1) symmetry, implies the presence of weak
+The unification of the weak nuclear and electromagnetic forces was introduced 
+in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk}.
+The electroweak theory is a key component of the \ac{SM}. It 
+is governed by an SU(2)$\times$U(1) symmetry and implies the presence of weak
 neutral currents.
@@
 %between particles carrying weak isospin.
-The weak interaction, working on all fermions,
-only couples to the left-handed part of fermion states. In 
-general a fermion state $\chi$ can be decomposed into its left- and right-handed parts
+%The weak force, which interacts with all fermions,
+%only couples to the left-handed part of fermion states. In 
+A general fermion state $\chi$ can be decomposed into its left- and right-handed parts
 \begin{equation}\label{eqn:leftright}
-\chi=\psi_R+\psi_L,
+\chi=\psi_R+\psi_L.
 \end{equation}
-and only $\psi_L$ will interact via the weak force. For massless particles
-the general state $\chi$ is not a mixture of left-handed and right-handed parts,
-but is either completely left-handed or right-handed. As such neutrinos, which are
-massless in the \ac{SM}, must all be left-handed. %CAREFUL: handedness =/= helicity
-The observation of neutrino flavour oscillations since the formulation of
-the \ac{SM} implies that neutrinos do have a small but finite mass
-and so there must be right-handed neutrinos in the \ac{SM}. This will
-not be discussed here, for a more detailed account see reference \cite{pdg-2014}.
+The weak force only couples to $\psi_L$, and is thus violates parity maximally.
+%where only $\psi_L$ will interact via the weak force. %For massless particles
+%the general state $\chi$ is not a mixture of left-handed and right-handed parts,
+%but is either completely left-handed or right-handed. As such neutrinos, which are
+%massless in the \ac{SM}, must all be left-handed. %CAREFUL: handedness =/= helicity
+%The observation of neutrino flavour oscillations since the formulation of
+%the \ac{SM} implies that neutrinos do have a small but finite mass
+%and so there must be right-handed neutrinos in the \ac{SM}. This will
+%not be discussed here, for a more detailed account see reference \cite{pdg-2014}.
 %The weak isospin acts on doublets of left-handed lepton pairs, while
@@
 %for the quarks, with weak isospin acting three left-handed doublets and
+
 Another feature of the weak force is that the weak eigenstates of the quarks
@@
 \begin{equation}\label{eqn:ewk_propagators_phot}
-A_{\mu} &= W_{\mu}^3\sin{\theta_W} + Y_{\mu}\cos{\theta_W},
+A_{\mu} &= W_{\mu}^3\sin{\theta_W} + B_{\mu}\cos{\theta_W},
 \end{equation}
 \begin{equation}\label{eqn:ewk_propagators_Z}
-Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - Y_{\mu}\sin{\theta_W}.
+Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - B_{\mu}\sin{\theta_W}.
 \end{equation}
@@
 broken by the addition of mass terms for the gauge bosons. However, the \PW and \PZ bosons are known to be massive. 
-Furthermore fermion mass terms would also not be gauge invariant, and it is also known
-that the fermions are massive.
+A similar problem exists for fermions, as they are known to have mass but the introduction
+of mass terms would break gauge invariance of the Lagrangian. 
 This means electroweak symmetry must be broken. In the \ac{SM}
@@
 \begin{split}
-\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, where we choose, }\\
-V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda})^2,
+&\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, where we choose, }\\
+&V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda})^2,
 \end{split}
@@
 
-Under a local $SU(2)\times U(1)$ transformation, with hypercharge Y=$\frac{1}{2}$
-the resulting transformation of the field is,
+Under a local $SU(2)\times U(1)$ transformation, the field transforms as,
 \begin{equation}\label{eqn:hfield_trsf}
 \begin{pmatrix} \phi^+ \\
-\phi^0 \end{pmatrix} = \exp{\frac{i}{2}(\vec{\theta(x)}\cdot\vec{\sigma} + \rho(x))}
+\phi^0 \end{pmatrix} = \exp{\frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)}
 \begin{pmatrix} \phi^+ \\
@@
 \end{equation}
-where $\vec{\sigma}$ are the Pauli spin matrices and $\vec{\theta(x)}$ and $\rho(x)$
+where $\vec{\sigma}$ are the Pauli spin matrices and $\vec{\theta}$ and $\rho$
 are functions of the space-time coordinates. From such a transformation
@@
 \begin{equation}\label{eqn:H_cov_deriv}
-D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'Y_{\mu}
+D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'B_{\mu}
 \end{equation}
@@
 
-Looking at fluctuations around the vacuum state,
-\begin{equation}\label{eqn:fluctvac}
-\begin{split}
-&\delta\Phi = \frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)\Phi\\
-&=\frac{i}{2}\begin{pmatrix} \theta_3 + \rho & \theta_1 - i\theta_2 \\
-\theta_1+i\theta_2 & \rho - \theta_3 \end{pmatrix} \begin{pmatrix} 0\\
-\frac{v}{\sqrt{2}} \end{pmatrix}.
-\end{split}
-\end{equation}
-Requiring $\delta\Phi=0$, we have $\theta_1=\theta_2=0$ and $\rho=\theta_3$, 
-and the only remaining generator that leaves the field 
-invariant is $\frac{i}{2}\theta_3 + Y = I_3 +Y$ is the U(1) group. Denoting the 
+Considering infinitesimal fluctuations around the vacuum state, it can be shown that the
+only remaining generator that leaves the field invariant is $I_3+Y$, the generator
+of the U(1) group.
+%\begin{equation}\label{eqn:fluctvac}
+%\begin{split}
+%&\delta\Phi = \frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)\Phi\\
+%&=\frac{i}{2}\begin{pmatrix} \theta_3 + \rho & \theta_1 - i\theta_2 \\
+%\theta_1+i\theta_2 & \rho - \theta_3 \end{pmatrix} \begin{pmatrix} 0\\
+%\frac{v}{\sqrt{2}} \end{pmatrix}.
+%\end{split}
+%\end{equation}
+%Requiring $\delta\Phi=0$, we have $\theta_1=\theta_2=0$ and $\rho=\theta_3$, 
+%and the only generator that leaves the field invariant is $I_3+Y$, the generator of the U(1) group.
+Denoting the 
 remaining generators as $\vec{b}$, and parameterising the field as an expansion around the
@@
 \Phi = \exp{\frac{i}{\sqrt{2}v}\vec{\theta}\cdot\vec{b}}\begin{pmatrix} 0 \\
-\frac{1}{\sqrt{2}} (v+H) \end{pmatrix}.
+\frac{1}{\sqrt{2}} (v+h) \end{pmatrix}.
 \end{equation}
-By choosing the appropriate gauge the Goldstone bosons $\vec{\theta}$
+By choosing an appropriate gauge the Goldstone bosons $\vec{\theta}$
 can be eliminated. They become the longitudinal degrees of freedom of the \PW and \PZ 
@@
 \Phi = \begin{pmatrix} 0 \\
-\frac{1}{\sqrt{2}}(v+H) \end{pmatrix}
+\frac{1}{\sqrt{2}}(v+h) \end{pmatrix}
 \end{equation}
@@
 and using the definitions of $\PW_{\mu}^{\pm}$ and $\PZ_{\mu}$ from 
-equations \ref{eqn:ewk_propagators}, we get
+equations \ref{eqn:ewk_propagators_W}-\ref{eqn:ewk_propagators_Z}, we get
 \begin{equation}\label{eqn:completed_lagrangian}
-\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}H\partial^{\mu}H -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu^2H^2  + \text{terms of order 3 and up in the fields}.
+\begin{split}
+&\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}h\partial^{\mu}h -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu^2h^2  + \\ 
+&\text{terms of at least order 3 in the fields}.
+\end{split}
 \end{equation}
-This gives us masses for the \PW bosons as $m_{\PW} = \frac{gv}{2}$ and a mass
-for the \PZ boson as $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. The photon remains massles. 
-The remaining mass term is for the field $H$, the
-Higgs field, which has a mass $m_{H} = \sqrt{2\mu^2}$.
+This leads to the \PW mass as $m_{\PW} = \frac{gv}{2}$ and a mass
+for the \PZ boson as $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. Note that these
+masses are related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The photon remains massles. 
+The remaining mass term is for the field $h$, the
+Higgs field, which has a mass $m_{h} = \sqrt{2\mu^2}$.
 %Mass term : -1/2m_X^2. However for m_W note W_mu+Wmu- = 1/2(W_mu^1+iW_mu^2)(W_mu^1-iW_mu^2) = 
@@
 The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
-searches for the boson had to be conducted over a large range of
-masses. Searches for the Higgs boson at \ac{LEP} did not lead
+a large range of possible masses had to be covered in searches. 
+Searches for the Higgs boson at \ac{LEP} did not lead
 to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
@@
 More data were collected and analysed during the remainder of 2012, and subsequent studies 
-grew the confidence in this boson being compatible with the standard model Higgs boson. The ATLAS and CMS combined
+grew the confidence in the compatibility of this boson being the standard model Higgs boson. The ATLAS and CMS combined
 mass measurement using the full dataset of Run 1 of the \ac{LHC} 
-found \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
+found its mass as \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
 The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
@@
 the individual experiments did not reach a significance upwards of 5$\sigma$ in this channel during Run 1.
-Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
-and so the measurements of \ac{SM} Higgs boson
+%Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
+%and so the measurements of \ac{SM} Higgs boson
 properties are certainly not finished yet.
@@
 It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}
-that the two discovery channels $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow \PZ
-PZ$ have smaller branching ratios than many other channels. These two channels are very sensitive
+that the two discovery channels $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow ZZ$
+have smaller branching ratios than many other channels. These two channels are very sensitive
 due to the small backgrounds and the excellent photon and lepton energy resolution the detectors provide.
@@
 already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
-as has the decay in to $ZZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}. In addition, measurements
-of $H\rightarrow WW$ are under way \cite{CMSHWW2016,ATLASHWW2016}. Establishment of the decay of 
-$H\rightarrow b\bar{b}$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $H\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
+as has the decay in to $ZZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
+of $h\rightarrow WW$ are being performed \cite{CMSHWW2016,ATLASHWW2016}. Establishment of the decay of 
+$h\rightarrow b\bar{b}$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $h\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
 is still to be achieved.
@@
 out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
-keeps growing, more such measurements will be made to shed more light on the standard model Higgs boson.
+keeps growing it will be possible to shed more light on the standard model Higgs boson.
 
@@
 For example, it does not provide a candidate for dark matter.
-Additionally, the energy dependence of the running coupling constants
+In addition, the energy dependence of the running coupling constants
 do not converge the GUT scale, and the force of gravity does not
-appear in the \ac{SM}, no quantum theory can be formulated for it.
+appear in the \ac{SM}.
 
-These issues aside, one of the most pressing issues regarding
-the Higgs sector of the \ac{SM} is the hierarcy problem.
+These points aside, the most important issue concerning
+the Higgs sector of the \ac{SM} is the hierarchy problem.
 The \ac{SM}
@@
 
-Many \acf{BSM} theories have been developed
-that can to address the hierarchy problem and some of the other issues 
-discussed. One of the most
-popular of such theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
+Many \acf{BSM} theories that can address the hierarchy problem, and some of
+the other issues that were mentioned, have been developed.
+One of the most
+popular of these theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
 that there is a symmetry between bosons and fermions. Every fermionic
-\ac{SM} particle has a bosonic superpartner (named `s'+name of fermion, e.g.
-sbottom, selectron,...), and every bosonic \ac{SM} particle
-has a fermionic superpartner (named boson name + `ino', e.g. higgsino, Wino,...).
+\ac{SM} particle has a bosonic superpartner (sfermion, for scalar fermion)
+and every bosonic \ac{SM} particle
+has a fermionic superpartner (boson name + `ino', e.g. higgsino, Wino).
 
@@
 of the other aforementioned issues. The lightest \ac{SUSY} particle
-would be a candidate for dark matter if it were stable \cite{SUSY-primer}. On top of that
-assuming \ac{SUSY} means the electroweak and strong coupling
+would be a candidate for dark matter if it were stable \cite{SUSY-primer}. On top of that,
+\ac{SUSY} allows the electroweak and strong coupling
 constants intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.
@@
 \begin{equation}\label{eqn:mssm_higgsdoublets}
-\phi_d = \begin{pmatrix} \phi_d^0 \\
-\phi_d^- \end{pmatrix} \text{ and } \phi_u = \begin{pmatrix} \phi_u^+ \\
+\Phi_d = \begin{pmatrix} \phi_d^0 \\
+\phi_d^- \end{pmatrix} \text{ and } \Phi_u = \begin{pmatrix} \phi_u^+ \\
 \phi_u^0 \end{pmatrix}
@@
 with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
-This provides electroweak symmetry breaking as in the \ac{SM} case and
+Electroweak symmetry is broken as in the \ac{SM} case and
 minimising this potential gives,
 \begin{equation}\label{eqn:mssm_minimpot}
-\langle 0|\phi_d| 0 \rangle = \begin{pmatrix}v_d\\
-0 \end{pmatrix} \text{ and} \langle 0 |\phi_d|\rangle 0 = \begin{pmatrix} 0\\
+\langle 0|\Phi_d| 0 \rangle = \begin{pmatrix}v_d\\
+0 \end{pmatrix} \text{ and} \langle 0 |\Phi_u|\rangle 0 = \begin{pmatrix} 0\\
 v_u \end{pmatrix}
@@
 Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
-and the neutral scalars h and H. These are defined in terms
+and the neutral scalars \PHiggslight and \PHiggs. These are defined in terms
 of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
@@
 &\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
-&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi+u^0 -v_u)\cos{\alpha}\\
+&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi_u^0 -v_u)\cos{\alpha}\\
 &\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
 \end{align}
-As the self-interactions of the Higgs fields are not independent parameters
-but are functions of the electroweak gauge coupling constants, at tree
-level the MSSM Higgs sector parameters are determined by two free parameters, \tanb~and
+As the self-interactions of the Higgs fields are not independent parameters,
+%they are functions of the electroweak gauge coupling constants 
+at tree
+level the MSSM Higgs sector is determined by two free parameters, \tanb~and
 one of the Higgs boson masses, conventionally chosen as \mA.
-Using this the masses of the five Higgs states are found as:
+Using this the masses of the five Higgs states are:
 \begin{equation}\label{mssm_chargedhigss_mass}
@@
 \end{equation}
-and a constraing on $\alpha$,
+and a constraint on $\alpha$,
 \begin{equation}\label{eqn:alpha_constraint}
@@
 
-The constraint on $m_h$ being less than the mass of the Z boson, 91.2 GeV, seems 
-problematic at first, as we know there is a Higgs state with a mass of 125 GeV. However,
+The requirement that $m_h$ be less than the mass of the Z boson, 91.2 GeV, seems 
+problematic at first, as it is known that there is a Higgs state with a mass of 125 GeV. However,
 the tree-level masses and couplings of the Higgs bosons in the MSSM can be
@@
 The tree-level couplings of the neutral Higgs bosons to bosons and fermions 
-are modified with respect to the \ac{SM} couplings, by factors
+are modified with respect to the \ac{SM} couplings, by the multiplicative factors
 described in table \ref{tab:mssm_couplings} \cite{YR4}.
@@
 \caption{Branching ratios of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario,
-at (a) \tanb=5~and (b) \tanb=30. The branching ratio into \Pgt\Pgt (blue), $b\bar{b}$ (red) 
-and \Pgm\Pgm (yellow) is enhanced at high \tanb, while the branching ratio into 
+at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $b\bar{b}$ (red) 
+and $\mu\mu$ (yellow) is enhanced at high \tanb, while the branching ratio into 
 WW (grey) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
@@
 vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
-bosons is suppressed with respect to the \ac{SM} expectation, VBF and PW/PZ associated
-production do not constitute dominant production processes. Gluon fusion production is 
-the dominant production mode at low \tanb, like in the \ac{SM}. An example tree-level Feynman diagram is given in figure \ref{fig:production_mssm}a. In gluon fusion production the Higgs boson
+bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
+production are not part of the important production processes. Gluon fusion production is 
+the dominant production mode at low \tanb, like in the \ac{SM}. 
+An example tree-level Feynman diagram is given in figure \ref{fig:production_mssm}a. In gluon fusion production the Higgs boson
 is produced via a quark loop. At low \tanb~values this loop is dominated by top quarks, while at 
-high \tanb~the b-quark loop dominates.
-This is a result of the enhanced coupling to down-type fermions at high \tanb.
+high \tanb~the b-quark loop dominates. This is a result of the enhanced coupling to down-type fermions at high \tanb. 
 Another consequence of these enhanced couplings to down-type fermions at high \tanb~is the dominance of b-associated production, where the Higgs boson is produced through
@@
 there is not one, but two Higgs doublets. The addition of a second
-Higgs doublet can also motivated by \ac{SUSY}, but also by axion models.
+Higgs doublet can of course be motivated by \ac{SUSY}, but also by other models.
 An important point to note is that despite the presence of a second 
 Higgs doublet, there are no explicit \ac{SUSY} particles in the \ac{2HDM}.
-There are many different types of \ac{2HDM}, all distinguished by the couplings
-of the different Higgs bosons to bosons and fermions. The 
-most general potential for a CP-conserving 2HDM has 9 free parameters,
-taken as \tanb, the mixing angle $\alpha$, already discussed in 
+
+There are several different types of \ac{2HDM}, all distinguished by the couplings
+of the different Higgs bosons to bosons and fermions. In its most general
+form, there are 9 free parameters in the potential of a CP-conserving 2HDM. 
+These are taken as \tanb, the mixing angle $\alpha$, already discussed in 
 the context of the \ac{MSSM}, the masses of the five Higgs bosons,
@@
 
-The inclusive $\sigma\times$branching ratios for production of a \PHiggs boson 
+The inclusive cross-section times branching ratios for production of a \PHiggs boson 
 and decays into various states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
@@
 
-The parameters that need to be fixed in the benchmark scenarios are:
-\begin{itemize}
-\item The mass of the third generation squarks, given by $M_{\text{SUSY}}$.
-\item The higgsino mass parameter, $\mu$.
-\item The mass of the stau, the third generation sleptons, $M_{\tilde{\ell_3}}$.
-\item The mass of the gluino, $M_{\tilde{g}}$.
-\item The U(1) gaugino mass parameter, $M_1$.
-\item The SU(2) gaugino mass parameter, $M_2$.
-\item The trilinear couplings of the stops, sbottoms and staus to the Higgs: $A_t$, $A_b$ and $A_{\Pgt}$.
-\item The stop, sbottom and stau mixing parameters, $X_t$, $X_b$ and $X_{\Pgt}$.
-\end{itemize}
+The parameters that need to be fixed in the benchmark scenarios are the 
+\ac{SUSY} breaking scale, the mass scale of the third generation squarks ($M_{\text{SUSY}}$). 
+In addition, the higgsino mass parameter $\mu$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
+The masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also need to be determined, plus to the
+trilinear couplings of the stops, sbottoms and staus to the Higgs field: $A_t$, $A_b$ and $A_{\tau}$. The 
+stop, sbottom and stau mixing parameters $X_t$, $X_b$ and $X_{\tau}$ are also fixed.
 
@@
 \end{equation}
-where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
+%where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
 
 Some additional parameters which have only a
-small effect on the MSSM Higgs boson sector are alos considered.
+small effect on the MSSM Higgs boson sector are considered.
 Because their effect is so small they are
 fixed in all benchmark scenarios at values compatible with 
-exclusion limits from direct searches:
-\begin{itemize}
-\item Masses of the first and second generation squarks, $M_{\tilde{q}_{1,2}} = 1.5$ TeV.
-\item Masses of the first and second generation sleptons, $M_{\tilde{\ell}_{1,2}} = 500$ GeV.
-\item Trilinear couplings of first and second generation squarks and sleptons, $A_f=0$.
-\end{itemize}
+exclusion limits from direct searches. The masses
+of the first and second generation squarks are set to 1.5 TeV, 
+and the masses of the first and second generation sleptons to 500 GeV. The trilinear
+couplings of the first and second generation squarks and sleptons are taken to be 0.
 
-After the discovery of the 125 GeV Higgs boson the MSSM benchmark
-scenarios need to accommodate this particle, which means only the 
-scenarios which contain a light Higgs boson with a mass of around 125 GeV
+Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
+scenarios 
+which contain a light Higgs boson with a mass of around 125 GeV
 are still accessible.
@@
 Figure \ref{fig:mhmodp_xs} shows the cross--sections of
-gluon fusion production of the \PHiggs boson and (four--flavour scheme) b-associated
+gluon fusion production of the \PHiggs boson and b-associated
 production of the \PHiggsps boson in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
@@
 scenario contains a light Higgs boson with a mass compatible with
-125 GeV. However, at low values of \tanb this is not the case, with
+125 GeV. However, at low values of \tanb~this is not the case, with
 values of \mh~dropping below 122 GeV. The low \tanb~regime can be re-opened
 if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
-MORE ABOUT FINE-TUNING
 %But not too large, see ref above!
@@
 To obtain \mh$\approx$125 GeV over a large part of the parameter
-space, the SUSY parameters are chosen such that SUSY BREAKING MASSES ETC?
-and $M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
+space, 
+$M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
 varying the parameter $X_t$ as:
@@
 \label{sec:theory_BSM_models_hMSSM}
-The hMSSM scenario \cite{hMSSM-1,hMSSM-2} uses a different approach by starting from 
-the REPHRASE tree-level expressions for masses and mixing and
-the mass of the light Higgs boson \mh=125 GeV.
+The hMSSM scenario \cite{hMSSM-1,hMSSM-2} uses a different approach, in
+which \mh=125 GeV by construction.
 
@@
 a minimum accessible \mA~of around 151 GeV for \tanb=1. In addition, the scenario
-can be formulated, but is not strictly valid, for values of \tanb upwards of 10 \cite{CMS-PAS-HIG-16-007}.
+can be formulated, but is not strictly valid, for values of \tanb~upwards of 10 \cite{CMS-PAS-HIG-16-007}.
 The reason for this is that direct higher order SUSY corrections to down-type
@@
 
-The production cross--sections at $\sqrt{s}=14$ TeV for gluon fusion production of the
-H and A bosons, as well as for b-associated production, are shown in figure \ref{fig:hmssm_xs}.
-As expected, gluon fusion production is dominant at low \tanb,with b-associated
-production being more important at high \tanb. The cross sections increase for increasing \tanb,
-apart from the gluon fusion cross section at low \tanb, where it decreases as \tanb~increases
-due to a negative top-bottom intereference effect.
+The production cross--sections of the \PHiggs and \PHiggsps bosons are
+qualitatively similar to those in other MSSM scenarios. Gluon fusion is dominant
+at low \tanb, with b-associated production being more important at high \tanb. The
+negative top-bottom loop interference effect again means the cross sections decrease with increasing 
+\tanb~up to around \tanb=3, when the cross sections start increasing with increasing \tanb again.
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$\sigma(gg\rightarrow\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsggA_hmssm.pdf}}
-\subfloat[$\sigma(bb\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_hmssm.pdf}}
-\end{center}
-\caption{Cross-sections at $\sqrt{s}=13$ TeV as a function of
-\mA~and \tanb~ in 
-the hMSSM scenario for (a) gluon fusion production of the \PHiggsps boson and (b)
-b-associated production (four--flavour scheme) of the \PHiggs boson. We can generally see the cross-sections increase
-with growing \tanb, apart from the gluon fusion cross section which decrease with increasing
-\tanb~for low \tanb.}
-\label{fig:hmssm_xs}
-\end{figure}
+The branching ratios of \PHiggs and \PHiggsps into $\tau\tau$ follow a similar
+pattern as in other MSSM scenarios again, with large branching ratios at high \tanb.
 
-Figure \ref{fig:hmssm_brtautau} shows the branching ratios of \PHiggsps and \PHiggs into \Pgt\Pgt.
-The branching ratios are large over a large part of the mA-\tanb~plane, but mostly so
-at high \tanb.
+%\begin{figure}[h!]
+%\begin{center}
+%\subfloat[$\sigma(gg\rightarrow\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsggA_hmssm.pdf}}
+%\subfloat[$\sigma(bb\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_hmssm.pdf}}
+%\end{center}
+%\caption{Cross-sections at $\sqrt{s}=13$ TeV as a function of
+%\mA~and \tanb~ in 
+%the hMSSM scenario for (a) gluon fusion production of the \PHiggsps boson and (b)
+%b-associated production (four--flavour scheme) of the \PHiggs boson. We can generally see the cross-sections increase
+%with growing \tanb, apart from the gluon fusion cross section which decrease with increasing
+%\tanb~for low \tanb.}
+%\label{fig:hmssm_xs}
+%\end{figure}
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[BR$(\PHiggs\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_hmssm.pdf}}
-\subfloat[BR$(\PHiggsps\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_hmssm.pdf}}
-\end{center}
-\caption{Branching ratios of (a) the \PHiggs boson and (b) the \PHiggsps boson into \tautau. The
-branching ratio is enhanced at high \tanb.} 
-\label{fig:hmssm_brtautau}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\subfloat[BR$(\PHiggs\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_hmssm.pdf}}
+%\subfloat[BR$(\PHiggsps\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_hmssm.pdf}}
+%\end{center}
+%\caption{Branching ratios of (a) the \PHiggs boson and (b) the \PHiggsps boson into \tautau. The
+%branching ratio is enhanced at high \tanb.} 
+%\label{fig:hmssm_brtautau}
+%\end{figure}
 
@@
 Run 1 of the \ac{LHC} many searches for BSM Higgs
-bosons were already performed. The state of play with the full
+bosons were already performed. The status of MSSM benchmark model exclusion with the full
 Run-1 dataset collected by \ac{CMS} can be seen in figure \ref{fig:bsm_summary},
@@
 and hMSSM scenarios (figure \ref{fig:bsm_summary}b). The direct search for heavier Higgs bosons decaying into pairs
-of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb,with searches for 
+of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb, with searches for 
 heavy Higgs bosons decaying to $b\bar{b}$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
@@
 
-In Run-2 of the \ac{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
-have been performed in \ac{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
-Similar searches have been performed by \acs{ATLAS} \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
+In Run-2 of the \acs{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
+have been performed in \acs{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
+Similar searches have been performed by ATLAS \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
 are being searched for in other channels too, with some results for decays into \ttbar \cite{ATLASHttbar}, 
@@
 di-Higgs searches \cite{ATLASHbbgamgam,ATLASHgamgamWW,ATLASHhhbbbb,CMSbbgamgam,CMSHbbtautau,CMSHbbWW}, both in 
-various final states, have been performed. The interest in these searches will remain, and so
-as more data are collected during Run 2 more of such searches will be performed.
+various final states, have been performed. As more data are collected during Run 2 and beyond, the \ac{BSM}
+Higgs sector will continue to be probed.
 

### 2017-02-01 Theory/Theory.tex
Own theory chapter edits

@@
 
-\subsection{Fundamental particles}
+\subsection{Fundamental particles and forces}
 \label{sec:theory_sm_particles}
-In the \ac{SM} there are twelve fundamental fermions, six which
+In the \ac{SM} there are twelve fundamental fermions, six that 
 interact via the strong nuclear force (quarks) and six that do not (leptons).
@@
 table \ref{tab:theory_fermions}.
-
 \begin{table}[htp]
@@
 \midrule
-\textbf{Quarks} & & & \\
+\multicolumn{4}{c}{\textbf{Quarks}}\\
 \midrule
@@
 \midrule
-\textbf{Leptons} & & & \\
+\multicolumn{4}{c}{\textbf{Leptons}} \\
 \midrule
@@
 \end{table}
-
-\subsection{Fundamental forces}
-\label{sec:theory_sm_forces}
 %Symmetries of the Lagrangian describing a physical system lead
@@
 %might introduce additional derivatives of potentials, taken care of by gauge transf.
-The forces in the \ac{SM} are mediated by spin-1 bosons: the gluon (\Pgluon),
-which carries the strong force, the photon (\Pphoton) 
-mediating the electromagnetic force, and the $\PW^{\pm}$ and \PZ bosons, the
-force carriers of the weak nuclear force.
+
+The symmetries governing the forces in the \ac{SM} imply the presence
+of spin-1 bosons which carry the forces. The gluon (\Pgluon) mediates 
+the strong nuclear force, while the \ac{EM} force is mediated
+by the photon (\Pphoton), and the $\PW^{\pm}$ and \PZ bosons carry the weak nuclear force.
 
 The quantum number associated with the strong force is colour, which
-is carried both by quarks and gluons.
+both the quarks and the gluons carry.
 The interactions in the \ac{QFT} of the
@@
 
-The unification of the weak nuclear and electromagnetic forces was introduced 
-in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk}.
-The electroweak theory is a key component of the \ac{SM}. It 
+The unification of the weak nuclear and \ac{EM} forces, introduced 
+in the 1960s by Glashow \cite{glashow-ewk}, Weinberg \cite{weinberg-ewk} and Salam \cite{salam-ewk}, 
+is a key component of the \ac{SM}. The electroweak force 
 is governed by an SU(2)$\times$U(1) symmetry and implies the presence of weak
@@
 %only couples to the left-handed part of fermion states. In 
-A general fermion state $\chi$ can be decomposed into its left- and right-handed parts
-\begin{equation}\label{eqn:leftright}
-\chi=\psi_R+\psi_L.
-\end{equation}
-The weak force only couples to $\psi_L$, and is thus violates parity maximally.
+%A general fermion state $\chi$ can be decomposed into its left- and right-handed parts
+%\begin{equation}\label{eqn:leftright}
+%\chi=\psi_R+\psi_L.
+%\end{equation}
+%The weak force only couples to $\psi_L$, and is thus violates parity maximally.
 %where only $\psi_L$ will interact via the weak force. %For massless particles
@@
 %for the quarks, with weak isospin acting three left-handed doublets and
+%Another feature of the weak force is that the weak eigenstates of the quarks
+%differ from the physical states, which mix via the \ac{CKM}-matrix \cite{ckm-matrix-cabibbo,ckm-matrix-KM}
+%in charged current interactions as
+%\begin{equation}\label{eqn:ckm_matrix}
+%\begin{pmatrix} d' \\
+%s' \\
+%b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
+%V_{cd} & V_{cs} & V_{cb} \\
+%V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
+%s\\
+%b \end{pmatrix}.
+%\end{equation}
 
-Another feature of the weak force is that the weak eigenstates of the quarks
-differ from the physical states, which mix via the \ac{CKM}-matrix \cite{ckm-matrix-cabibbo,ckm-matrix-KM}
-in charged current interactions as
-\begin{equation}\label{eqn:ckm_matrix}
-\begin{pmatrix} d' \\
-s' \\
-b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
-V_{cd} & V_{cs} & V_{cb} \\
-V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
-s\\
-b \end{pmatrix}.
-\end{equation}
-
-Going back to the symmetry of the unified electroweak forces,
 The SU(2) part of the symmetry is built from the weak
@@
 
-Associated gauge fields are the three weak fields $W_{\mu}^{i}$ and the
+The associated gauge fields are the three weak isospin fields $W_{\mu}^{i}$ and the
 weak hypercharge field $B_{\mu}$. These four fields mix to form the physical \Pphoton,
@@
 and UA2 collaborations at \acs{CERN}.
+It should be noted that the weak force only couples to the left-handed parts
+of fermion states, and so is maximally parity violating.
 
 An issue with electroweak theory is that the gauge invariance of the Lagrangian would be
-broken by the addition of mass terms for the gauge bosons. However, the \PW and \PZ bosons are known to be massive. 
-A similar problem exists for fermions, as they are known to have mass but the introduction
+broken by the addition of mass terms of the form $-\frac{1}{2}m^2\PZ_{\mu}\PZ^{\mu}$ 
+for the gauge bosons. However, the \PW and \PZ bosons are known to be massive. 
+A similar problem exists for fermions, as they are known to have mass but again the introduction
 of mass terms would break gauge invariance of the Lagrangian. 
-This means electroweak symmetry must be broken. In the \ac{SM}
-this is achieved via the Higgs mechanism.
+To be able to introduce mass terms electroweak symmetry must be broken. In the 
+\ac{SM} this happens via the Higgs mechanism.
 
@@
 
-The simplest addition to achieve this is a complex doublet,
+The simplest field that needs to be added to break electroweak symmetry is a complex doublet,
 \begin{equation}\label{eqn:phi_hfield}
@@
 \end{equation}
-This field has an associated Lagrangian
+The Lagrangian of this field is of the form
 \begin{equation}\label{eqn:higgs_gen_lag}
 \begin{split}
-&\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, where we choose, }\\
+&\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, with }\\
 &V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda})^2,
@@
 \end{equation}
-Where $\lambda$ and $\mu^2$ are two real parameters, and $\lambda>0$ is needed for stability
-of the vacuum. To get spontaneous symmetry breaking we require $\mu^2>0$.
+where $\lambda$ and $\mu^2$ are two real parameters. The parameter $\lambda$ 
+is a quartic coupling strength modifier, and it will later be shown 
+that $\mu$ is a mass parameter.
+For the vacuum to be stable $\lambda$ must be positive,
+and for spontaneous symmetry breaking $\mu^2$ is also required to be positive.
 
@@
 \begin{pmatrix} \phi^+ \\
-\phi^0 \end{pmatrix} = \exp{\frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)}
+\phi^0 \end{pmatrix} = \exp{\{\frac{i}{2}(\vec{\theta}\cdot\vec{\sigma} + \rho)\}}
 \begin{pmatrix} \phi^+ \\
@@
 \end{equation}
-where $\vec{\sigma}$ are the Pauli spin matrices and $\vec{\theta}$ and $\rho$
-are functions of the space-time coordinates. From such a transformation
-the covariant derivative is required to be
+where $\vec{\theta}$ and $\rho$
+are phase transformations which are functions of the space-time coordinates. The covariant
+derivative associated with such a transformation is
 \begin{equation}\label{eqn:H_cov_deriv}
-D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'B_{\mu}
+D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'B_{\mu}.
 \end{equation}
-In the vacuum state we must have $V(\Phi^{\dagger}\Phi) =0$, which happens for nonzero values of $\Phi$,
-and we can choose $\phi^+$ = 0 and $\phi^0$ real to get:
+In the vacuum state, $V(\Phi^{\dagger}\Phi) =0$, $\Phi^{\dagger}\Phi=\frac{\mu^2}{2\lambda}$ and so
+$\Phi$ has to be nonzero.
+Now choosing $\phi^+$ = 0 and taking $\phi^0$ to be real, this means:
 %\begin{equation}\label{eqn:vacuum_expt}
@@
 \end{equation}
-where $v$ is real and $v^2 = \frac{\mu^2}{\lambda}$.
+where $v$ is a real parameter, $v^2 \equiv \frac{\mu^2}{\lambda}$.
 
 Considering infinitesimal fluctuations around the vacuum state, it can be shown that the
-only remaining generator that leaves the field invariant is $I_3+Y$, the generator
+only remaining generator that leaves the field invariant is $I_3+\frac{Y}{2}$, the generator
 of the U(1) group.
@@
 Denoting the 
-remaining generators as $\vec{b}$, and parameterising the field as an expansion around the
+remaining, broken, generators as $\vec{b}$, and parameterising the field as an expansion around the
 vacuum state gives:
 \begin{equation}\label{eqn:vev_expansion}
-\Phi = \exp{\frac{i}{\sqrt{2}v}\vec{\theta}\cdot\vec{b}}\begin{pmatrix} 0 \\
+\Phi = \exp{\{\frac{i}{\sqrt{2}v}\vec{\theta}\cdot\vec{b}\}}\begin{pmatrix} 0 \\
 \frac{1}{\sqrt{2}} (v+h) \end{pmatrix}.
@@
 By choosing an appropriate gauge the Goldstone bosons $\vec{\theta}$
-can be eliminated. They become the longitudinal degrees of freedom of the \PW and \PZ 
-bosons. This leaves us with
+can be eliminated. They become the longitudinal degrees of freedom of the $\PW^{\pm}$ and \PZ 
+bosons. This then leaves
 \begin{equation}\label{eqn:vev_expansion_satisfied}
 \Phi = \begin{pmatrix} 0 \\
-\frac{1}{\sqrt{2}}(v+h) \end{pmatrix}
+\frac{1}{\sqrt{2}}(v+h) \end{pmatrix}.
 \end{equation}
@@
 and using the definitions of $\PW_{\mu}^{\pm}$ and $\PZ_{\mu}$ from 
-equations \ref{eqn:ewk_propagators_W}-\ref{eqn:ewk_propagators_Z}, we get
+equations \ref{eqn:ewk_propagators_W}-\ref{eqn:ewk_propagators_Z}, the Lagrangian becomes
 \begin{equation}\label{eqn:completed_lagrangian}
@@
 &\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}h\partial^{\mu}h -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu^2h^2  + \\ 
-&\text{terms of at least order 3 in the fields}.
+&\text{terms of at least }\mathcal{O}(3)\text{ in the fields}.
 \end{split}
 \end{equation}
-This leads to the \PW mass as $m_{\PW} = \frac{gv}{2}$ and a mass
-for the \PZ boson as $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. Note that these
-masses are related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The photon remains massles. 
-The remaining mass term is for the field $h$, the
-Higgs field, which has a mass $m_{h} = \sqrt{2\mu^2}$.
+This Lagrangian contains mass terms for the $\PW^{\pm}$ and \PZ bosons, with 
+$m_{\PW} = \frac{gv}{2}$ and $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. Using equation \ref{eqn:thetaw} 
+we can see that these two masses are
+related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The remaining mass term is for the Higgs field $h$, 
+which leads to a mass $m_{h} = \sqrt{2\mu^2}$.
+Note that the photon does not acquire a mass.
 %Mass term : -1/2m_X^2. However for m_W note W_mu+Wmu- = 1/2(W_mu^1+iW_mu^2)(W_mu^1-iW_mu^2) = 
@@
 
-Using the developments so far we can also add fermion masses
-through Yukawa couplings between the fermion- and Higgs fields
+Using these developments it is also possible to add mass terms for the fermions
+through Yukawa couplings between the fermion- and Higgs fields, which are of the form
 \begin{equation}\label{eqn:yukawa_coupl}
-\lambda_f(\bar{\psi_L}\Phi\psi_R + \bar{\psi_R}\Phi\psi_L),
+\lambda_f(\bar{\psi_L}\Phi\psi_R + \bar{\psi_R}\Phi\psi_L).
 \end{equation}
-where $\lambda_f$ are coupling constants specific to each fermion, $\lambda_f \propto m_f$.
-This means that heavier fermions have stronger couplings to the Higgs boson.
+The parameter $\lambda_f$ is a coupling constant specific to each fermion, $\lambda_f \propto m_f$.
+This means that heavier fermions couple more strongly to the Higgs field.
 
@@
 The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
-a large range of possible masses had to be covered in searches. 
-Searches for the Higgs boson at \ac{LEP} did not lead
+a large range of possible masses needed to be covered in Higgs boson searches. 
+Searches for the Higgs boson at the \ac{LEP} did not lead
 to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
-providing a lower search limit. Subsequent studies at the 
-Tevatron did also not lead to discovery of the Higgs boson, but did provide
-an additional excluded masses range of 140-186 GeV at 95\% \ac{CL} \cite{TEV-Higgs}.
+providing a lower search limit. Higgs boson searches at the 
+Tevatron also did not lead to discovery of the Higgs boson, but did exclude 
+an additional mass range of 140-186 GeV at 95\% \ac{CL} \cite{TEV-Higgs}.
 
@@
 announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
-The observations were based on excesses in the search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$.
+The discovery was based on the observation of excesses in the 
+search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$, with a significance 
+above 5$\sigma$.
 More data were collected and analysed during the remainder of 2012, and subsequent studies 
-grew the confidence in the compatibility of this boson being the standard model Higgs boson. The ATLAS and CMS combined
-mass measurement using the full dataset of Run 1 of the \ac{LHC} 
-found its mass as \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV \cite{MassComb}.
-The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \ac{LHC} Run 1,
+increased the confidence in the compatibility of this new state with being the \ac{SM} Higgs boson. 
+The most precise measurement of the mass of the Higgs boson, \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV, 
+comes from the ATLAS and CMS combined
+mass measurement using the full dataset of Run 1 of the \acs{LHC} \cite{MassComb}.
+The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \acs{LHC} Run 1,
 shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, through
@@
 %and so the measurements of \ac{SM} Higgs boson
-properties are certainly not finished yet.
 
@@
 \end{center}
-\caption{Feynman diagrams at tree level for the dominant Higgs boson production modes at
+\caption{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
 the \ac{LHC}.}
@@
 
-Figure \ref{fig:theory_smhprod} shows the dominant Higgs boson production modes
+Figure \ref{fig:theory_smhprod} shows Feynman diagrams of the dominant Higgs boson production modes
 at the \ac{LHC}. From the production cross sections for each mode in figure
-\ref{fig:theory_smhxsbr} we see that gluon fusion is by far dominant. The other modes
-shown have smaller cross sections, but are of importance due to their topologies, with
-additional leptons or jets in the final state. Tagging such topologies can reduce the size
+\ref{fig:theory_smhxsbr}a we see that gluon fusion is by far dominant. The other modes
+shown have cross sections at least an order of magnitude smaller, but are of importance due to their topologies.
+Tagging the additional leptons or jets in the final states of
+these production modes can reduce the size
 of the \ac{SM} background.
@@
 \end{center}
-\caption{(a) standard model Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) standard model
+\caption{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
 Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
@@
 
-It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}
-that the two discovery channels $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow ZZ$
-have smaller branching ratios than many other channels. These two channels are very sensitive
-due to the small backgrounds and the excellent photon and lepton energy resolution the detectors provide.
+It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b that
+the branching ratios into
+$\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow ZZ$, the two discovery
+channels, are smaller than the branching ratios into many other final states.
+These two channels are thus not sensitive as a result of their branching ratio, but
+rather due to the small backgrounds in these analysis as well as the excellent photon and lepton energy resolution the detectors provide.
 
-During Run 2 of the LHC, standard model Higgs boson measurements, and searches for the 
-standard model Higgs boson in decay channels not previously established, have 
+During Run 2 of the LHC, \ac{SM} Higgs boson measurements, and searches for the 
+\ac{SM} Higgs boson in decay channels not previously established, have 
 already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
@@
 is still to be achieved.
-Finally, searches for ttH production, important to establish the top-Higgs coupling, have also been carried 
+Finally, searches for ttH production, which are important to probe the top-Higgs coupling, have also been carried 
 out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
@@
 some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
-For example, it does not provide a candidate for dark matter.
-In addition, the energy dependence of the running coupling constants
-do not converge the GUT scale, and the force of gravity does not
-appear in the \ac{SM}.
+For example, it does not provide a candidate for dark matter, which is estimated
+to make up 25\% of the matter in the universe.
+In addition, the running coupling constants of the electroweak and
+strong forces do not converge at the GUT scale. Another problem is that the force
+of gravity does not appear in the \ac{SM}.
 
@@
 is accepted to be an effective field theory that describes
-the elementary particles and their interactions well up to an energy scale $\Lambda$.
+the elementary particles and their interactions well, up to an energy scale $\Lambda$ beyond which it breaks down.
 This is the energy scale at which new physics must enter.
 We know that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
-gravitational effects start to become important in that region. $\Lambda$ enters
+gravitational effects start to become important in that region. The energy scale $\Lambda$ enters
 the corrections due to fermion and boson loops to the Higgs boson mass quadratically \cite{MSSM-carena-haber}:
 \begin{equation}\label{eqn:mh_hierarchy}
-m_{h_{\text{SM}}}^2  = (m_h^2)_0 + \mathcal{O}(\Lambda^2).
+\begin{split}
+&m_{h_{\text{SM}}}^2  = (m_h^2)_0 + \Delta m_h^2,\\
+&\Delta m_h^2 \sim \mathcal{O}(\Lambda^2).
+\end{split}
 \end{equation}
@@
 popular of these theories is \acf{SUSY} \cite{SUSY-primer}, which postulates
-that there is a symmetry between bosons and fermions. Every fermionic
+that there is a symmetry between bosons and fermions. This means every fermionic
 \ac{SM} particle has a bosonic superpartner (sfermion, for scalar fermion)
@@
 
-If this symmetry were unbroken the \ac{SUSY} particles must
+If this symmetry is unbroken the \ac{SUSY} particles must
 have the same mass as their \ac{SM} partners. However, if that had 
@@
 that the fermion and boson loops contribute to the Higgs boson
-mass corrections with opposite sign, and so, if \ac{SUSY}
-was an exact symmetry their contributions to the Higgs boson mass
-would cancel. Due to 
-symmetry breaking the contributions of \ac{SM} particles 
-and their supersymmetric partners do not completely cancel. If
-the \ac{SUSY} breaking scale, where new particles should
-be found, is much larger than a few TeV further fine-tuning of 
+mass corrections with opposite sign, and so the symmetry between bosons and fermions 
+allows for the cancellation of $\Delta m_h^2$ terms. The cancellation
+would be exact if \ac{SUSY} was unbroken, but because this is not the case the
+cancellation is not complete. Therefore if the \ac{SUSY} breaking scale, where
+new particles should be found, is much larger than a few TeV further fine-tuning of
 the bare Higgs boson mass would be required \cite{MSSM-carena-haber,SUSY-primer}.
@@
 \ac{SUSY} allows the electroweak and strong coupling
-constants intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.
+constants to intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.
 
@@
 At least two Higgs doublets are required in the
-Higgs sector of the \ac{MSSM} due to the supersymmetric
-background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
+Higgs sector of the \ac{MSSM}, and so in its simplest form two complex Higgs doublets are added \cite{MSSM-carena-haber},
 \begin{equation}\label{eqn:mssm_higgsdoublets}
@@
 \phi_d^- \end{pmatrix} \text{ and } \Phi_u = \begin{pmatrix} \phi_u^+ \\
-\phi_u^0 \end{pmatrix}
+\phi_u^0 \end{pmatrix}.
 \end{equation}
@@
 exclusively to up-type fermions.
-This leads to potential terms in the MSSM Lagrangian of the form:
-\begin{equation}\label{eqn:mssm_lagrangian_potential}
-V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
-\end{equation}
-with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
+%This leads to potential terms in the MSSM Lagrangian of the form:
+%\begin{equation}\label{eqn:mssm_lagrangian_potential}
+%V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
+%\end{equation}
+%with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
 Electroweak symmetry is broken as in the \ac{SM} case and
-minimising this potential gives,
+minimising the potential associated with the two Higgs doublets gives,
 \begin{equation}\label{eqn:mssm_minimpot}
 \langle 0|\Phi_d| 0 \rangle = \begin{pmatrix}v_d\\
-0 \end{pmatrix} \text{ and} \langle 0 |\Phi_u|\rangle 0 = \begin{pmatrix} 0\\
-v_u \end{pmatrix}
+0 \end{pmatrix} \text{ and } \langle 0 |\Phi_u|0\rangle  = \begin{pmatrix} 0\\
+v_u \end{pmatrix}.
 \end{equation}
-Using this we define
+Using this we can define
 \begin{equation}\label{eqn:tanb_def}
-\tan{\beta} \equiv \frac{v_u}{v_d}
+\tan{\beta} \equiv \frac{v_u}{v_d}.
 \end{equation}
@@
 Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
-and the neutral scalars \PHiggslight and \PHiggs. These are defined in terms
-of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
-the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}. The five bosons become:
+and the neutral scalars \PHiggslight and \PHiggs. These arise from mixing of the
+fields as:
 \begin{align}\label{eqn:MSSMHiggsMixing}
@@
 &\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
-&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi_u^0 -v_u)\cos{\alpha}\\
-&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
+&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi_u^0 -v_u)\cos{\alpha},\\
+&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}.
 \end{align}
+These mixtures depend on \tanb~and the mixing angle $\alpha$ which arises
+from diagonalising
+the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}.
 As the self-interactions of the Higgs fields are not independent parameters,
 %they are functions of the electroweak gauge coupling constants 
-at tree
-level the MSSM Higgs sector is determined by two free parameters, \tanb~and
+at tree level the MSSM Higgs sector is determined by two free parameters, \tanb~and
 one of the Higgs boson masses, conventionally chosen as \mA.
-Using this the masses of the five Higgs states are:
+The masses of the five Higgs states are then:
 \begin{equation}\label{mssm_chargedhigss_mass}
@@
 \end{equation}
-while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the tree-level
-squared-mass matrix:
+while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the
+squared-mass matrix at tree level:
 \begin{equation}\label{eqn:treelevel_mass}
@@
 \end{equation}
-This leads to the masses of \PHiggslight and \PHiggs as eigenvalue of $\mathcal{M}_{\text{tree}}^2$,
+Such that $m_{\PHiggs,\PHiggslight}$ are eigenvalues of $\mathcal{M}_{\text{tree}}^2$,
 \begin{equation}\label{eqn:scalarmass}
@@
 significantly altered by radiative corrections. The dominant effect is from
-incomplete cancellation of the stop- and top-loop corrections, which
-do not completely cancel as SUSY is a broken symmetry.
+incomplete cancellation of the stop- and top-loop corrections.
 
@@
 are modified with respect to the \ac{SM} couplings, by the multiplicative factors
-described in table \ref{tab:mssm_couplings} \cite{YR4}.
+given in table \ref{tab:mssm_couplings} \cite{YR4}.
 
@@
 bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
-production are not part of the important production processes. Gluon fusion production is 
-the dominant production mode at low \tanb, like in the \ac{SM}. 
-An example tree-level Feynman diagram is given in figure \ref{fig:production_mssm}a. In gluon fusion production the Higgs boson
-is produced via a quark loop. At low \tanb~values this loop is dominated by top quarks, while at 
+production are not as important as for the production of the \ac{SM} Higgs boson. Gluon fusion production is 
+the dominant production mode at low \tanb, as in the \ac{SM}. 
+An example tree-level Feynman diagram for gluon fusion production, which proceeds via
+a quark loop, is given in figure \ref{fig:production_mssm}a.
+At low \tanb~values this loop is dominated by top quarks, while at 
 high \tanb~the b-quark loop dominates. This is a result of the enhanced coupling to down-type fermions at high \tanb. 
@@
 A different approach, also leading to an extended Higgs sector with
-respect to the \ac{SM} case, is found in the \ac{2HDM} \cite{2HDM-I,2HDM-II}.
+respect to the \ac{SM}, is found in the \ac{2HDM} \cite{2HDM-I,2HDM-II}.
 As the name suggests \ac{2HDM}s are a generic class of models in which
@@
 where $\cos{(\beta-\alpha)} = 0$, differs from that of the \ac{MSSM} couplings.
-In particular, in the alignment limit the decays \AtoZh~and \Htohh vanish
-in the \ac{2HDM}. This is due to the fact that the coupling is 
-proportional to $\cos{(\beta-\alpha)}$ and there are no radiative corrections
-to make the branching ratio nonzero.
+In particular, in the alignment limit of the \ac{2HDM} the decays \AtoZh~and \Htohh~vanish.
+This is due to the fact that these couplings are
+proportional to $\cos{(\beta-\alpha)}$ and there are no corrections
+from \ac{SUSY} particles to make the branching ratios nonzero.
 
@@
 and decays into various states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
-example of a type-II \ac{2HDM}, at two \tanb points. Figure \ref{fig:2hdm_Hxsbr}b 
-shows the inclusive $\sigma\times$branching ratios for production and decay
+example of a type-II \ac{2HDM}, at two \tanb~points. Figure \ref{fig:2hdm_Hxsbr}b 
+shows the inclusive cross-section times branching ratios for production and decay
 of a \PHiggsps boson in the same type-II \ac{2HDM} example, at two \tanb~points. At
-low \tanb~the $\sigma\times$branching ratio for \Htohh production and decay and \AtoZh production
+low \tanb~the cross-section times branching ratios for \Htohh production and decay and \AtoZh production
 and decay are enhanced for $250\leq m_{\PHiggs}\leq 350$ GeV and $220 \leq m_{\PHiggsps} \leq 350$ GeV, respectively.
@@
 The parameters that need to be fixed in the benchmark scenarios are the 
-\ac{SUSY} breaking scale, the mass scale of the third generation squarks ($M_{\text{SUSY}}$). 
+\ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks.
 In addition, the higgsino mass parameter $\mu$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
-The masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also need to be determined, plus to the
-trilinear couplings of the stops, sbottoms and staus to the Higgs field: $A_t$, $A_b$ and $A_{\tau}$. The 
-stop, sbottom and stau mixing parameters $X_t$, $X_b$ and $X_{\tau}$ are also fixed.
+A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
+trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_t$, $A_b$ and $A_{\Pgt}$) and the 
+stop, sbottom and stau mixing parameters ($X_t$, $X_b$ and $X_{\tau}$) are also fixed.
 
-Some of these parameters can be expressed in terms of relations to other parameters. 
-$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as,
+Some of these parameters can be related to each other. For example,
+$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as:
 \begin{equation}\label{eqn:trilinear_couplings}
@@
 \begin{equation}
-M_1 = \frac{5}{3}M_s\tan{\theta_w}^2,
+M_1 = \frac{5}{3}M_2\tan{\theta_w}^2.
 \end{equation}
 %where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
-
-Some additional parameters which have only a
-small effect on the MSSM Higgs boson sector are considered.
-Because their effect is so small they are
-fixed in all benchmark scenarios at values compatible with 
-exclusion limits from direct searches. The masses
+Some additional parameters which only have a
+small effect on the MSSM Higgs boson sector are 
+fixed to values compatible with 
+exclusion limits from direct searches in all benchmark scenarios. The masses
 of the first and second generation squarks are set to 1.5 TeV, 
@@
 couplings of the first and second generation squarks and sleptons are taken to be 0.
-
-Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
-scenarios 
-which contain a light Higgs boson with a mass of around 125 GeV
-are still accessible.
-
+%Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
+%scenarios 
+%which contain a light Higgs boson with a mass of around 125 GeV
+%are still accessible.
 % in the mmax scenario the benchmark values have been chosen h
@@
 The $m_{h}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
-is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. This scenario, which
+is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
 was used for interpretations of MSSM Higgs boson searches at LEP, allows
@@
 The remaining parameters are set as $\mu=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
-$m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. Figure \ref{fig:mhmodp_mh}
-shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
-that its mass is compatible with 125 GeV over a large part of the parameter space.
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}
-\end{center}
-\caption{The mass of the light Higgs boson, \mh, as a function 
-of \mA~and \tanb~in the $m_{h}^{\text{mod+}}$ scenario. The white areas
-indicate masses lower than 122 GeV. The figure shows that
-the mass of the light Higgs boson is compatible with 125 GeV over a large
-part of the \mA-\tanb~plane.}
-\label{fig:mhmodp_mh}
-\end{figure}
+$m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. 
+%Figure \ref{fig:mhmodp_mh}a
+%shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
+%that its mass is compatible with 125 GeV over a large part of the parameter space. Masses within 
+%a window $\pm 3$ GeV around 125 GeV are considered compatible with 125 GeV, where the 3 GeV
+%variation corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
 
 Figure \ref{fig:mhmodp_xs} shows the cross--sections of
-gluon fusion production of the \PHiggs boson and b-associated
-production of the \PHiggsps boson in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
+gluon fusion and b-associated production of the \PHiggs boson 
+in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
 production dominates at low \tanb, while b-associated production has a larger cross--section
-at high \tanb.
+at high \tanb. The behaviour of the production cross-sections of the \PHiggsps boson
+is similar.
 
@@
 \subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
-\subfloat[$\sigma(gg\rightarrow bb\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_bbA4FS_mhmodp.pdf}}
+\subfloat[$\sigma(gg\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
 \end{center}
-\caption{Production cross--section of (a) gluon fusion production of the \PHiggs boson and
-(b) b--associated production (four--flavour scheme) of the \PHiggsps boson in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
+\caption{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
+in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
 the b-associated production cross-section is larger at high \tanb.}
@@
 scenario contains a light Higgs boson with a mass compatible with
-125 GeV. However, at low values of \tanb~this is not the case, with
-values of \mh~dropping below 122 GeV. The low \tanb~regime can be re-opened
+125 GeV. However, at low values of \tanb~this is not the case.
+The mass of the light Higgs
+boson in the $m_{h}^{\text{mod}+}$ scenario is shown in 
+figure \ref{fig:mhmodp_mh}a, illustrating that the mass 
+is not within $\pm 3$ GeV of 125 GeV at low \tanb. Masses within
+a window of $\pm3$ GeV around 125 GeV are considered compatible with 125
+GeV, as the 3 GeV variation corresponds to the theoretical uncertainty on the 
+\ac{MSSM} prediction for \mh.
+The low \tanb~regime can be re-opened
 if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
 %But not too large, see ref above!
-Figure \ref{fig:tanb_accessibility} shows contours of constant
-light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
-It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
-for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
-\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./Theory/Figures/tanb_accessibility.png}
-\end{center}
-\caption{Contours of constant light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
-High values of $M_{\text{SUSY}}$ allow for light Higgs boson masses compatible with
-125 GeV down to low values of \tanb~\cite{hMSSM-2}.}
-\label{fig:tanb_accessibility}
-\end{figure}
+%Figure \ref{fig:tanb_accessibility} shows contours of constant
+%light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
+%It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
+%for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
+%\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.
+%
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.5\textwidth]{./Theory/Figures/tanb_accessibility.png}
+%\end{center}
+%\caption{Contours of constant light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
+%High values of $M_{\text{SUSY}}$ allow for light Higgs boson masses compatible with
+%125 GeV down to low values of \tanb~\cite{hMSSM-2}.}
+%\label{fig:tanb_accessibility}
+%\end{figure}
 
@@
 Higgs boson masses of around 125 GeV in most of the \mA-\tanb~plane considered.
-Figure \ref{fig:lowtbhigh_mh} shows that, apart from in a corner of \tanb~1-4 and 
+Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1-4 and 
 \mA~150-250 GeV, \mh~is compatible with 125 GeV.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
+\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
+\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
 \end{center}
-\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
-The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
-\label{fig:lowtbhigh_mh}
+\caption{The mass of the light Higgs boson, \mh, as a function 
+of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
+indicate masses lower than 122 GeV. The figures shows that
+the mass of the light Higgs boson is compatible with 125 GeV over a large
+part of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
+the mass of the light Higgs boson is compatible with 125 GeV nearly everywhere.}
+\label{fig:mhmodp_mh}
 \end{figure}
-
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
+%\end{center}
+%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
+%The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
+%\label{fig:lowtbhigh_mh}
+%\end{figure}
 To obtain \mh$\approx$125 GeV over a large part of the parameter
@@
 \begin{split}
-\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2\\
-2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25\\
+\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2,\\
+2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
 8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
@@
 
-Using these assumptions we can invert the lightest eigenvalue
-of the mass matrix to get: 
+Using these assumptions the lightest eigenvalue
+of the mass matrix can be inverted to get: 
 \begin{equation}
@@
 gives enough information to determine the cross sections and branching
-ratios of all the five Higgs bosons as a function of \mA~and \tanb. The scenario
+ratios of all of the five Higgs bosons as a function of \mA~and \tanb. The scenario
 is only well defined in regions where the denominator in equations
@@
 negative top-bottom loop interference effect again means the cross sections decrease with increasing 
-\tanb~up to around \tanb=3, when the cross sections start increasing with increasing \tanb again.
+\tanb~up to around \tanb=3, when the cross sections start increasing with increasing \tanb~again.
 
@@
 pattern as in other MSSM scenarios again, with large branching ratios at high \tanb.
-
 %\begin{figure}[h!]
@@
 %\end{figure}
-
 %\begin{figure}[h!]
@@
 Run 1 of the \ac{LHC} many searches for BSM Higgs
-bosons were already performed. The status of MSSM benchmark model exclusion with the full
-Run-1 dataset collected by \ac{CMS} can be seen in figure \ref{fig:bsm_summary},
-which shows the interpretations of different searches in the $m_{h}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
+bosons were already performed. Figure \ref{fig:bsm_summary} shows the interpetations
+of different searches performed within \acs{CMS} during Run 1 of the \acs{LHC}
+in the $m_{h}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
 and hMSSM scenarios (figure \ref{fig:bsm_summary}b). The direct search for heavier Higgs bosons decaying into pairs
@@
 
-In Run-2 of the \acs{LHC} searches for \AHtotautau, setting more stringent limits than those shown in \ref{fig:bsm_summary},
+In Run 2 of the \acs{LHC} searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
 have been performed in \acs{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
@@
 di-Higgs searches \cite{ATLASHbbgamgam,ATLASHgamgamWW,ATLASHhhbbbb,CMSbbgamgam,CMSHbbtautau,CMSHbbWW}, both in 
-various final states, have been performed. As more data are collected during Run 2 and beyond, the \ac{BSM}
-Higgs sector will continue to be probed.
+various final states, have been performed. %As more data are collected during Run 2 and beyond, the \ac{BSM}
+%Higgs sector will continue to be probed.
 
@@
 \end{center}
-\caption{Summary of the interpretations of Run 1 BSM Higgs searches at \ac{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
+\caption{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
 hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
-scenarios. The results from MSSM Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
-space than any of the other searches. The MSSM Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
-of the high-\tanb region, with Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
-scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low-mass region for all values of \tanb. Masses below around 300 GeV in the 
-hMSSM scenario are excluded instead by constraints from standard model Higgs boson measurements (magenta). In this scenario small
-areas of the low-\tanb~region are also excluded by the search for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
+scenarios. The results from \ac{MSSM} Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
+space than any of the other searches. The \ac{MSSM} Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
+of the high-\tanb~region, with searches for Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
+scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around 300 GeV in the 
+hMSSM scenario are excluded instead by constraints from \ac{SM} Higgs boson measurements (magenta). In this scenario small
+areas of the low-\tanb~region are also excluded by the searches for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
 and the search for $H\rightarrow hh \rightarrow bb\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}

### 2017-02-02 MSSM/MSSM.tex
Adding some MSSM chapter stuff

@@
 corresponds to an integrated luminosity of 12.9 fb$^{-1}$, and the analysis is
-detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
+detailed in Ref. \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
 states of the di-\Pgt pair were studied. The results of this search are 
@@
 
-For the analysis described in this chapter, as well as the 2015 analysis not detailed
-here, I was responsible for all stages of the analysis. This included optimisation 
+For the analysis described in this chapter, as well as the 2015 analysis,
+I was responsible for all stages of the analysis. This included optimisation 
 of object selection and categorisation,
@@
 with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di--boson background
-samples and part of the W+$\gamma$ background, which is included in the \emu channel only.
+samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
 \Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
-matrix element generator. Both samples containing a mixture
+matrix element generator. Samples containing both a mixture
 of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
@@
 before they are combined so as to preserve the correct
-fractions of events with each jet multiplicity.
-\texttt{MadGraph 5} 
-is also used to generate part of the W+$\gamma$ background
-samples.
+fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
+only included in the \emu channel, is generated in part with \texttt{MadGraph 5} and in
+part with \texttt{MadGraph5\_aMC@NLO}.
 
@@
 
+The basis of the event selection is to select \mutau, \etau,
+\tautau and \emu pairs. Events are selected first by using a trigger,
+followed by additional selection criteria. For the \etau
+and \mutau channels we only trigger on the electron or muon. 
+While the lepton + hadronic tau cross triggers that are also available
+allow for a 3 (6) GeV lower \pT~threshold on the
+muon (electron), the benefit of using such a trigger is small as 
+most of the signal samples at high-mass, the region of interest in this
+analysis, have higher \pT~electrons and muons. This is illustrated
+in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
+\mutau channel, with the signal normalised to 4000 times its cross--section
+times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod}+}$ scenario overlaid.
+In the \emu channel two dedicated electron-muon cross triggers
+are used. These have significantly lower online \pT~cuts 
+on the two leptons than the single lepton triggers. For the 
+\tautau channel a di-tau cross-trigger is used.
+
+Because the triggers involving electrons or muons reach 
+their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
+on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
+hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
+on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
+In addition, a requirement is made on the $\eta$ of the electrons, muons and
+hadronic taus. Such a selection is driven by the $\eta$ range covered by the tracker and the $\eta$
+range that is used in the reconstruction of the particles,
+although in some cases the used trigger is restricted in $\eta$ and the cut is chosen to
+align with that. As an illustration figure \ref{fig:mt_muonpt}b shows
+the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
+The signal peaks in the central $\eta$ region.
+
+Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
+ensure that the particle is compatible with having
+originated from the primary vertex. This reduces the selection of particles
+coming from pile--up events. Additional identification and isolation criteria
+are also applied. These will be discussed in the following sections.
+The optimisation of some of the selections will also be discussed there. Note that 
+the optimisations were all based on the dataset collected during 2015, which
+corresponds to an integrated luminosity of 2.3 fb$^{-1}$.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_1_inclusive_mt_2016.pdf}}
+\subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/eta_1_inclusive_et_2016.pdf}}
+\end{center}
+\caption{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
+The gluon fusion (dashed blue line)
+and b-associated (dashed purple line) signals are overlaid. The signals are normalised to 4000 times their
+cross-section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod+}}$ scenario.}
+\label{fig:mt_muonpt}
+\end{figure}
+
 \subsection{Pair selection and vetos}
@@
 requirements, identification criteria and kinematic cuts
-more than one possible candidate pair can exist. If this
-is the case for an event, the pair is chosen as follows:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
-electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
-and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
-object with raw MVA isolation value nearest to 1.
-\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
-\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
-candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
-and the $\Pgt_h$ for \etau and \mutau channels).
-\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
-\end{itemize}
+more than one possible candidate pair can exist. If
+this is the case the pair with the two most isolated candidates
+ is chosen, as isolated candidates are less likely 
+to be jets misreconstructed
+as leptons or hadronic taus.
+%If this
+%is the case for an event, the pair is chosen as follows:
+%\begin{itemize}
+%\setlength{\itemsep}{-\baselineskip}
+%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
+%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
+%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
+%object with raw MVA isolation value nearest to 1.
+%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
+%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
+%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
+%and the $\Pgt_h$ for \etau and \mutau channels).
+%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
+%\end{itemize}
 
@@
 with \pT~$>10$ GeV and passing loose ID and isolation requirements.
-This also reduces backgrounds from \WZ events. 
-In addition to this, \Zee events are 
+This also reduces backgrounds from \WZ events. The application
+of these vetos means that the selection of the pair with the
+two most isolated candidates is only important where hadronic
+taus are concerned, for if there were additional electrons
+or muons the event would not pass the electron or muon veto.
+In addition to these extra electron and muon vetos, \Zee events are 
 reduced in the \etau channel by rejecting events
@@
 \label{sec:mssm_eventsel_mt}
-The first selection layer in the \mutau channel is a trigger
-that only requires a muon at \ac{L1}. At the level of the \ac{HLT}, 
-loose identification and isolation criteria are then applied to this muon.
-
-The offline event selection proceeds to require an oppositely charged
+The trigger only requires a muon at \ac{L1}, while at the level of the \ac{HLT}
+loose identification and isolation criteria are applied to this muon.
+
+The offline event selection requires an oppositely charged
 muon and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
 The minimum \pT~of the muon is required to be 23 GeV, with $|\eta| < 2.1$. %due to trigger conditions
-Additional ``medium'' identification requirements are placed on the muon, in addition
-to requiring the muon to be consistent with having originated from the primary vertex, such that
-the impact parameters $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm. The muon is also required
-to be isolated, with $I_{\text{rel}}^{\mu} < 0.15$, where the isolation variable is calculated using
-a cone size of $\Delta R = 0.4$.
+Additional ``medium'' identification requirements are placed on the muon, and the impact
+parameters of the muon must satisfy $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm. The muon is also
+required to be isolated, with $I_{\text{rel}}^{\mu}<0.15$, where the isolation variable
+is calculated using a cone size of $\Delta R = 0.4$.
 
@@
 is required to be reconstructed by the HPS algorithm and to pass the medium
-working point of the MVA isolation discriminator. The hadronic tau also needs
-to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
+working point of the MVA isolation discriminator. The impact parameter $d_{z}$ is
 required to be less than 0.2 cm. Finally the hadronic tau is required
@@
 to the one given for electrons in equation \ref{eqn:electron_reliso} with 
-isolation cone sizes in $\Delta R$ of 0.3 and 0.4. In addition
+isolation cone sizes of $\Delta R$  0.3 and 0.4. In addition
 to this a very similar
@@
 also electrons and muons in the isolation sum, is considered. This
-variable is also studied for both cone sizes of 0.3 and 0.4. Finally,
+variable is also studied for cone sizes of 0.3 and 0.4. Finally,
 a relative isolation variable based solely on the \pT~of tracks from the primary
@@
 size of the error interval from the maximum--likelihood fit to the \Ztautau signal strength shown in 
-\ref{fig:mssm_selection_mt_muons}b. From the fact that both figures of merit do not
+\ref{fig:mssm_selection_mt_muons}b. As both figures of merit do not
 change so much with varying isolation requirements we can see that this analysis
@@
 figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on $\sigma\times$BR for
-the gluon fusion production process, at a mass $m_{\phi} = 160$ GeV, with
-figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit at $m_{\phi} = 2.9$ TeV.
+the gluon fusion production process, for a mass $m_{\phi} = 160$ GeV, with
+figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9$ TeV.
 Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
@@
 \caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
-(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
-at tight working point and \mT$<30$ GeV in green, medium working point and \mT$<40$ GeV in red,
-loose working point and \mT$<50$ GeV in blue and very loose working point and \mT$<60$ GeV in black. Loosening
+(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
+at the tight working point and \mT$<30$ GeV in green, the medium working point and \mT$<40$ GeV in red,
+the loose working point and \mT$<50$ GeV in blue and the very loose working point and \mT$<60$ GeV in black. Loosening
 the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
@@
 From these figures
-we can observe that looser selections are preferred for higher masses. This behaviour can be
+we observe that looser selections are preferred for higher masses. This behaviour can be
 explained by considering the function of each of the selections. Tightening the hadronic
@@
 end of the spectrum of mass--like discriminating variables, such tighter
-selections are preferred where signal and backgrounds overlap. However, at higher
-mass points the signal--sensitive range of the discriminating variable is 
-low in backgrounds and there is more benefit to loosening the selection
+selections are preferred where signal and backgrounds overlap. For higher masses the
+backgrounds are lower in the region where the signal peaks,
+and there is more benefit to loosening the selection
 to increase the signal efficiency than to keep the tighter selection
 to reduce an already low background.
-Using this, the selection was optimised for mass points of around 1 TeV, which leads to 
-the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
+The selection was optimised for masses around 800 GeV - 1 TeV, by
+using the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
 
@@
 a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
-criteria are made on the electron at the \ac{HLT}.
-
-The offline event selection proceeds to require an oppositely charged
+criteria are made on the electron with the \ac{HLT}.
+
+The offline event selection requires an oppositely charged
 electron and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
 The minimum \pT~of the electron is required to be 26 GeV, with $|\eta| < 2.1$. %due to trigger conditions
-This electron has to be consistent with having originated from the primary vertex, which
-is achieved by requiring the impact parameters to satisfy $d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and it
-is required to pass additional identification criteria. A selection on the MVA identification, which
-selects electrons from \Zee events with 80\% efficiency, is used. In addition the
+The impact parameters of the electron are required to satisfy
+$d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and the electron
+must pass additional identification criteria. The working point of the
+MVA identification discriminator that is used corresponds to a cut on the discriminator
+which selects electrons from \Zee events with 80\% efficiency. In addition the
 electron needs to be isolated, $I_{\text{rel}}^{\Pe} < 0.1$, with the relative isolation variable calculated with a cone size of 0.3.
@@
 and is required to be reconstructed by the HPS algorithm and to pass the medium
-working point of the MVA isolation discriminator. It also needs
-to have originiated from the primary vertex and so the impact paramter $d_{z}$ is 
-required to be less than 0.2 cm. Finally, the hadronic tau must 
+working point of the MVA isolation discriminator. The impact parameter $d_{z}$ of the
+hadronic tau must be less than 0.2 cm.
+Finally, the hadronic tau must 
 pass the tight working point of the anti--electron discriminator
@@
 Analogously to the muons, it was found that the analysis is not highly sensitive
-to the choice of electron isolation variable and selection.
+to the choice of electron isolation variable and cut value.
 A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
-The used value of \mT~$< 50$ is obtained by performing a 2D optimisation where the \mT~selection
+The value of \mT~$< 50$ GeV that is used is obtained by performing a 2D optimisation where the \mT~selection
 and hadronic tau isolation working point are varied at the same time. The same considerations as
@@
 made to recover some of the sensitivity lost at low mass by using looser \mT~and hadronic
-tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.
+tau isolation criteria. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.
 
@@
 \caption{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
-(b) bb$\phi$ production, for increasingly looser \mT~selection and tau isolation working point, starting
-at tight working point and \mT$<40$ GeV in green, medium working point and \mT$<50$ GeV in red,
-loose working point and \mT$<60$ GeV in blue and very loose working point and \mT$<70$ GeV in black. Loosening
+(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
+at the tight working point and \mT$<40$ GeV in green, the medium working point and \mT$<50$ GeV in red,
+the loose working point and \mT$<60$ GeV in blue and the very loose working point and \mT$<70$ GeV in black. Loosening
 the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
@@
 \label{sec:mssm_eventsel_tt}
-Selection of events in the \tautau channel starts with a trigger
-that requires two hadronic taus at \ac{L1}. At the level of the \ac{HLT}, loose identification
-and isolation criteria are applied to these hadronic taus.
-
-The offline event selection continues by requiring both hadronic taus to be oppositely charged, separated
+The trigger in the \tautau channel requires two hadronic taus at \ac{L1} and the \ac{HLT}
+applies loose identification and isolation criteria to these hadronic taus.
+
+The offline event selection requires both hadronic taus to be oppositely charged, separated
 by $\Delta R > 0.5$, have \pT~of at least 40 GeV and satisfy $|\eta|<2.1$. Both taus need
-to pass decay mode finding and have originated from the primary vertex, with the impact parameter $d_{z} < 0.2$ cm. 
+to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than 0.2 cm.
 Both taus need to pass the tight working point of the isolation discriminator, the very loose 
@@
 
-The offline requirements on the \emu pair are that the electron 
-and muon are oppositely charged and separated by $\Delta R >$ 0.3. The 
-electron needs to have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
+Offline, the electron and muon are required to be oppositely charged
+and separated by $\Delta R >$0.3.
+The electron needs to have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
 in the \etau channel the electron's impact parameters have to 
-satisfy $d_{xy} < 0.045$ cm and $d_{z}<0.2$ cm. A selection is
-made on the electron identification MVA, using a working point that 
-is 80\% efficient for electrons in \Zee decays. The electron
-also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
+satisfy $d_{xy} < 0.045$ cm and $d_{z}<0.2$ cm. The additional
+identification requirement is identical to the criterium applied to electrons in the \etau channel.
+The electron also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
 with a cone size of 0.3.
@@
 \ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
-for \emu events. The used selection, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
+for \emu events. The selection used, $D_{\zeta} > -20$ GeV, rejects $\ttbar$, \Wjets and diboson
 events. 
@@
 \end{figure}
-
+~\clearpage
 \subsection{Categorisation}
@@
 As the analysis targets both the gluon fusion
-and the b--associated production modes of MSSM Higgs
-bosons, two exclusive categories are defined based on the 
-number of b--tagged jets. A jet is considered b--tagged
-if it passes the medium working point of the \ac{CSV}v2 discriminator. 
-The categories are defined as:
-\begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
-\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal.
-\item \textbf{B-tag}: At least 1 b--tagged jet, at most 1 
-jet with \pT$>30$ GeV. Due to the different phase space considered for
-b--tagging than for default jet reconstruction this requirement does not necessarily
-mean there will be only one b--tagged jet in the event. The requirement reduces the sizeable \ttbar
-background.
-\end{itemize}
+and the b--associated production modes, 
+the sensitivity to the signal can be increased by categorising
+based on the number of b--tagged jets in the event.
 
@@
 gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
-see that the vast majority of these signal events do not have any b-tagged jets, which
-motivates the choice of the no b-tag category to target this production mode. From
-the b--associated signal in the same figure we also see that the majority of bb$\phi$
+see that the vast majority of these signal events do not have any b-tagged jets. To
+target this production mode we can use a category which requires 0 b-tagged jets.
+From the b--associated signal in the same figure we also see that the majority of bb$\phi$
 signal events do not have any b-tagged jets either: either the b-jets in these events 
-are too soft, or they do not pass the b-tagging requirements. This means the no b-tag 
-category is also sensitive to some of the bb$\phi$ signal. The other observation we 
-can make from the bb$\phi$ signal in figure \ref{fig:mssm_cats_mt}b is that there is not
+are too soft, or they do not pass the b-tagging requirements. This means that the category
+which requires 0 b-tagged jets
+is also sensitive to some of the bb$\phi$ signal. To target
+the bb$\phi$ signal, we then define another category with at least one b-tagged jet. 
+From the bb$\phi$ signal in figure \ref{fig:mssm_cats_mt}b we can also see that there is not
 such a large proportion of events with more than 1 b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
 we see that the \ttbar background starts to become more sizeable for events with more than
-one jet. The definition of the b-tag category is therefore chosen with the inclusion
+one jet. The definition of the category that targets the bb$\phi$ signal is therefore chosen with the inclusion
 of the jet veto, such that the region where the \ttbar background becomes larger is excluded, 
 while retaining a large proportion of the bb$\phi$ signal.
+
+In summary, the two categories are defined as:
+\begin{itemize}
+\setlength{\itemsep}{-\baselineskip}
+\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal.
+\item \textbf{B-tag}: At least 1 b--tagged jet, at most 1 
+jet with \pT$>30$ GeV. This second requirement, the jet veto, reduces the \ttbar background. 
+Due to the different phase space considered for
+b--tagging than for default jet reconstruction this requirement does not necessarily
+mean there will be only one b--tagged jet in the event.
+\end{itemize}
 
@@
 data are used to derive the \ac{MC} to data correction factors
-that are applied to the \ac{MC} samples.
+that are applied to the \ac{MC} samples. Where efficiencies
+are involved this scale factor is derived by measuring the efficiency
+in data and in \ac{MC} and constructing the scale factor as $\text{SF}=\frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
 \subsubsection*{Tracking efficiency}
@@
 making use of $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
-The measured efficiencies are used to construct scale factors to be
-applied to the \ac{MC} samples as $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
 \subsubsection*{Trigger efficiency}
@@
 improves the data/\ac{MC} agreement in a \ttbar enriched
-control region.
+control region in the \emu channel, defined as 
+\MET>80 GeV and $D_{\zeta}<-20$ GeV. The improvement in data/\ac{MC} agreement
+by applying the top quark \pT~reweighting is illustrated in figure \ref{fig:mssm_corrs_toppt}.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Without top-quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notoppt.png}}
+\subfloat[With top-quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
+\end{center}
+\caption{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,
+(a) without applying top quark \pT~reweighting and (b) with top quark \pT~reweighting.
+The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
+\label{fig:mssm_corrs_toppt}
+\end{figure}
+
 \subsubsection*{Drell-Yan shape reweighting}
@@
 are then applied to the \Ztautau and \Zellell background processes.
+The mismodelling can be seen in figure \ref{fig:dyrwt}a, which
+shows the observed data and expected background distribution of the \PZ \pT~in
+\Zmm events. The overall effect of the reweighting, which is derived
+based on the events shown in figure \ref{fig:dyrwt}a, on the \Ztautau background
+shape in the no b-tag category of the \etau channel is shown in figure \ref{fig:dyrwt}b.
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\Zmm events]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_tt_inclusive_zmm_2016_log_noweight.png}}
+\subfloat[Effect of Drell-Yan shape reweighting on \Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_zttweight_et_nobtag.pdf}}
+\end{center}
+\caption{(a) The mismodelling in the \PZ \pT~distribution as observed
+in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
+reweighting on the total transverse
+mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.}
+\label{fig:dyrwt}
+\end{figure}
 
@@
 in the \etau, \mutau and \tautau channels, and between
-signal and \ttbar events in the \emu channel.
+signal and \ttbar events in the \emu channel. These are some of the 
+major backgrounds and thus good separation between these processes and 
+the signal is important for the sensitivity of the analysis.
+The separation between signal and backgrounds is illustrated in figure
+\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps} shows the total transverse mass
+distribution of the QCD
+background in the no b-tag category of the \tautau channel with the gluon fusion
+signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
+shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
+the b-associated production signal at the same three masses overlaid.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[QCD and signal in \tautau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_tt_nobtag.pdf}}
+\subfloat[\ttbar and signal in \emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_em_btag.pdf}}
+\end{center}
+\caption{Total transverse mass distributions in (a) the no b-tag category of the \tautau
+channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
+category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
+The total transverse mass variable separates the signal and these backgrounds well.}
+\label{fig:mttot_sigseps}
+\end{figure}
 
@@
 \label{sec:mssm_bkgs}
-To estimate the backgrounds to the analysis a mixture of data--driven
-methods and \ac{MC} samples is employed. The methods used for background 
-estimation will be described in this section.
+There are several backgrounds in this analysis, and the different final
+states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
+which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
+of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
+region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
+is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
+it has two real taus in the final state, like the signal that we are searching for. The only aspect
+that distinguishes the \Ztautau background from the gluon fusion signal is the mass of the particle. Smaller backgrounds
+from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
+might pass the selection for example if a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
+Production of QCD multijet events, labelled QCD on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
+two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
+As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
+This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$. and so such events 
+always contain real b-jets. One or both of the \PW bosons, and additional jets in the event, can 
+then form \etau, \mutau, \tautau and \emu pairs.
+The \Wjets background arises in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
+as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
+decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
+reconstructed as hadronic taus.
+In the \emu channel an additional lepton would have to originate from one of the jets, and so here this
+background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
+figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
+background as the `Electroweak' component.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\mutau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_001-a.pdf}}
+\subfloat[\emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_003-b.pdf}}
+\end{center}
+\caption{The low $m_{\text{T}}^{\text{tot}}$ region in (a) the 
+no b-tag category of the \mutau channel and (b) the b-tag category of the \emu channel.
+This low $m_{\text{T}}^{\text{tot}}$ region is where the backgrounds
+are concentrated \cite{CMS-PAS-HIG-16-037-addit}.}
+\label{fig:mssm_bkgs_overview}
+\end{figure}
+
+To estimate these backgrounds a mixture of data-driven 
+methods and \ac{MC} samples is employed. The QCD background
+is estimated using data-driven techniques in all four channels.
+In the \mutau and \etau channels the \Wjets background is also
+estimated using data-driven techniques. The control regions used
+in the estimation of QCD and \Wjets in the \etau and \mutau channels
+are included in a simultaneous fit with the signal region to obtain
+the final results. More detail on this is given in section ADD SECTION.
+In the \emu and \tautau channels the \Wjets background is estimated using
+\ac{MC} samples. The \Ztautau and \Zellell backgrounds are also estimated
+using \ac{MC} samples, and a \Zmm control region
+is considered in a simultaneous fit with the signal region to correct and
+constrain the \Ztautau normalisation.
+The \ttbar, di-boson and single-top backgrounds are estimated
+using \ac{MC} samples, with cross-checks in control regions in data.
+The rest of this section describes the background estimation methods
+in more detail.
 
@@
 \begin{split}
-N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
- high } m_{\text{T}}} & =
+&N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
+ high } m_{\text{T}}}  =
 N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} + N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
-N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
- high } m_{\text{T}}} & = N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
+&N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
+ high } m_{\text{T}}}  = N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
 N_{\text{W}}^{\text{OS, high } m_{\text{T}}} \\
@@
 R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
-\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{\text{OS,
+&\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}}  = \frac{N_{\text{data}}^{\text{OS,
  high } m_{\text{T}}}  - N_{\text{other}}^{\text{OS, high } m_{\text{T}}}  -
@@
 and $R_{\text{QCD}}^{\text{OS/SS}}$ the ratio between opposite-sign and same-sign QCD events. Using 
-equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
+equation \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
 opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS, high } m_{T}}$. 
@@
 \label{sec:mssm_bkgs_etmt_qcdosss}
-The ratio of opposite--sign to same--sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$ is measured
+The ratio of opposite--sign to same--sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$, is measured
 in two anti-isolated sidebands by performing a fit to the distribution of the
@@
 and one further away ($0.25<I_{\text{rel}}^{\Pgm}<0.5$ for the \mutau channel and $0.2<I_{\text{rel}}^{\Pe}<0.5$ for the \etau channel). The results of the fits,
-performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear}--\ref{fig:mssm_qcdosss_mtfar}
-for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear}--\ref{fig:mssm_qcdosss_etfar} for the \etau channel.
-$R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent between the two sidebands within 10\% (1\%) in the \etau (\mutau) channel.
-Adding this in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
+performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear} and \ref{fig:mssm_qcdosss_mtfar}
+for the \mutau channel and in figures \ref{fig:mssm_qcdosss_etnear} and \ref{fig:mssm_qcdosss_etfar} for the \etau channel.
+The value of $R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent between the two sidebands within 10\% (1\%) in the \etau (\mutau) channel.
+Adding this uncertainty in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
 an overall uncertainty of 12\% in the \etau channel and 4\% in the \mutau channel.
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
 is 1.180$\pm$0.044.}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
 is 1.184$\pm$0.035.}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
-is 1.015$\pm$0.059.}
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength is 1.015$\pm$0.059.}
 \label{fig:mssm_qcdosss_etnear}
@@
 \caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength parameter
+the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength
 is 1.127$\pm$0.045.}
@@
 point of the tau ID discriminator, as in the nominal selection.
-The other hadronic tau in the pair should not pass the tight working point,
-but should pass the medium working point. This sideband is 
+The other hadronic tau in the pair is required to fail the tight working point,
+but pass the medium working point. This sideband is 
 chosen as it is as close to the signal region as possible, and 
@@
 the QCD estimate. Differences in normalisation due to
-the use of a loosened sideband are corrected for by loose-to-tight isolation
+the use of a loosened sideband are corrected for by the medium-to-tight isolation
 scale factor. This correction factor is measured as
 \begin{equation}\label{eqn:tautau_qcd}
-R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{\text{obs}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{obs}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
+R_{QCD}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
 \end{equation}
@@
 of lepton kinematics and the separation in $\Delta R$ between the
-two leptons. These ratios are then applied to the same--sign region
-QCD estimate to give a QCD estimate in the signal region. 
-Because the opposite--sign to same--sign ratios are measured
-before applying the categorisation, and \ac{MC} studies suggest
+two leptons. These ratios are then applied to the estimate in the same--sign region
+to give an estimate in the signal region. The statistical uncertainty
+on the measurement is 13\%. Cross-checking the measurement 
+using QCD \ac{MC} samples, it is observed that there is a 19\% difference
+between the OS/SS ratio in the signal region and the sideband, the two
+uncertainties are added in quadrature. 
+The opposite--sign to same--sign ratios are measured
+before applying the categorisation, and because \ac{MC} studies suggest
 that the opposite--sign to same--sign ratio is different in the b-tag
 category than in the no b-tag category, an extra scale factor of 
-1.45/2.20 is applied to the QCD estimate in the b-tag category.
+1.45/2.20 $\pm$ 0.16 is applied to the QCD estimate in the b-tag category. This is 
+the ratio between the OS/SS ratio as measured in the b-tag category and 
+the measurement made before categorisation. The uncertainty is added in
+quadrature to the statistical and systematic uncertainties already described.
 
@@
 is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
-the \emu channel, and it is shown in figure \ref{fig:mssm_corrs_toppt}.
+the \emu channel, and it is shown in figure \ref{fig:mssm_corrs_toppt}b.
 Because the 6\%
@@
 decaying tau.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
-\end{center}
-\caption{\mTtot~distribution in the \ttbar enriched control region.
-The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
-\label{fig:mssm_corrs_toppt}
-\end{figure}
 
@@
 its shape and normalisation are estimated from the
-\ac{MC} samples. In the \emu channel the \PW\Pphoton background
+\ac{MC} samples. In the \emu channel the $\PW\Pphoton$ background
 is also added to the \Wjets background component. For plotting purposes the single-top plus
@@
 \label{sec:mssm_uncs}
-Just like for the analysis presented in chapter \ref{chap:hhh}
+As for the analysis presented in chapter \ref{chap:hhh}
 two types of systematic uncertainty are considered. Normalisation
@@
 \subsubsection*{Identification, isolation and trigger efficiencies}
-The uncertainty on electron and muon identification, isolation, and
-trigger efficiency amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
+The combined uncertainty on the electron and muon identification, isolation, and
+trigger efficiencies amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
 isolation uncertainty amounts to 6\% in the \etau and \mutau channels
@@
 by shifting the jet energy up and down by the \pT-and $\eta$-dependendent
-uncertainty, and evaluating the the change in process normalisation in
+uncertainty, and evaluating the change in the process normalisation in
 each category. Where the change in normalisation is non-negligible the
@@
 \subsubsection*{\MET~resolution and response}
-Uncertainties on \MET~resolution and response are estimated
+Uncertainties on the \MET~resolution and response are estimated
 by varying the recoil correction parameters within their
@@
 normalisations. The uncertainty amounts to around 2\%.
-\subsubsection*{Background normalisation}
+\subsubsection*{Background normalisation uncertainties}
 \begin{itemize}
@@
 \item \Zellell: The uncertainty on the Drell-Yan cross-section
-amounts to 4\% \cite{CMS-PAS-HIG-16-037}.
+is to 4\% \cite{CMS-PAS-HIG-16-037}.
 \item \ttbar: The uncertainty on the \ttbar production cross-section amounts
@@
 For interpretations of the results in MSSM benchmark scenarios, theory
-uncertainties on the SM and MSSM Higgs cross section predictions are taken into account.
+uncertainties on the SM and MSSM Higgs cross--section predictions are taken into account.
 The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
@@
 0.4\% for VBF, 2.8\% for ZH and 0.5\% for WH. The uncertainties
-due to different choice of pdf and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for vector boson fusion,
+due to different choices of pdf set and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for vector boson fusion,
 1.6\% for ZH and 1.9\% for WH.
-For the MSSM Higgs cross sections used in the models, the uncertainties
+For the MSSM Higgs cross--sections used in the models, the uncertainties
 due to different choices of factorisation and renormalisation scale
-are computed, separately for each \mA-\tanb~point, following the prescription in refs\cite{pdf-lhc,alphas-uncs}.
+are computed, separately for each \mA-\tanb~point, following the prescription in Refs. \cite{pdf-lhc,alphas-uncs}.
 
@@
 The uncertainty is applied to the signal samples and to
-backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
+backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels, namely
 \Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
@@
 for the \Ztautau background in figure \ref{fig:mssm_highpttauid_shapes}b. Because the \Ztautau background
-has much softer hadronic taus than the high-mass signal sample, the shape-altering effect of this uncertainty
+has much softer hadronic taus than the high-mass signal sample, the impact of this uncertainty on the shape
 is much smaller.
@@
 \end{center}
-\caption{Shape-altering effect of the high-\pT~tau ID uncertainty in the no b-tag category of the
-\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect is much
+\caption{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
+\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is much
 larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
@@
 The total transverse mass \mTtot~is used as discriminating variable in this analysis.
-All bins of the distribution are used to perform a shape analysis. The statistical
-methods, including the incorporation of nuisance parameters in the fit, were already
+All bins of the distribution are used to perform a shape analysis. The general statistical
+methods, including the incorporation of nuisance parameters in the fit, were 
 described in section \ref{sec:hhh_results_extraction}. Some additional
@@
 To interpret the results of this search in a particular scenario, the predicted
-signal from the three neutral Higgs bosons is combined into a single signal template.
-Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
-which give the \mTtot~distributions for all channels and categories with an example three-Higgs signal overlaid.
+signal from the three neutral Higgs bosons is combined into a single signal template\footnote{Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
+which give the \mTtot~distributions for all channels and categories with an example three-Higgs signal overlaid.}.
 In this way the compatibility of the data with all three Higgs bosons, not just a single one, is tested.
@@
 with very similar properties to the boson discovered during Run 1 of the \ac{LHC}.
-Therefore we should perform a test that distinguishes between three-Higgs-signal-plus-background, and
-standard model Higgs-signal-plus-background.
+Therefore we should perform a test that distinguishes between a three-Higgs-signal-plus-background hypothesis, and
+a standard model Higgs-signal-plus-background hypothesis.
 
@@
 must be modified. Instead of testing for the compatibility of the data with
-a signal + background expectation modified by the signal strenght modifier $\mu$ as
+a signal + background expectation modified by the signal strength modifier $\mu$ as
 $\mu \cdot s(\theta) + b(\theta)$, a likelihood should be constructed as:
@@
 $\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
-general not 0. A solution to this problem can be found in test statistic used at the Tevatron \cite{LHCHComb2011},
+general not 0. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011},
 \begin{equation}\label{eqn:mssm_tevatron_teststat}
@@
 to the Tevatron test statistic, and therefore the probability density functions need to be generated 
-with toy datasets. Using these pdfs we can then calculate $CL_s(\mu=1)$ as defined in equation \ref{eqn:hhh_cls}.
-If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95 \% CL. The generation of toy datasets and 
-calculation of corresponding $CL_s$ value is performed for many points in a grid in the \mA-\tanb~plane,
+with toy datasets. Using these probability density functions  we can then calculate $CL_s(\mu=1)$ as defined in equation \ref{eqn:hhh_cls}.
+If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95\% CL. The generation of toy datasets and 
+calculation of corresponding $CL_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
 with interpolation between grid points performed to obtain a smooth exclusion contour.
 The pdfs for the SM and MSSM hypotheses, as well as the resulting $CL_s$ values,
-are given for three \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
+are given for three illustrative \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
 there is no separation between the MSSM and SM pdfs, and so we cannot exclude this point. The separation
@@
 \end{center}
-\caption{Pdfs, obtained by generating a large number of toy datasets, for the SM and MSSM hypothesis at three different points in the $m_{\text{h}}^{\text{mod+}}$
-scenario, each with different levels of separation between the MSSM and SM pdfs.}
+\caption{Probability density functions, obtained by generating a large number of toy datasets, for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$
+scenario, each with different levels of separation between the MSSM and SM distributions.}
 \label{fig:mssm_mssmvssm_toys}
@@
 
-None of these distributions show hints of a significant excess. The
+None of these distributions show a significant excess. The
 95\% CL upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
@@
 process and (b) the b--associated production process. All four final states and 
-all categories are combined for these limits \cite{CMS-PAS-HIG-16-037}.}
+all categories are combined for these limits. The green and yellow bands indicate
+the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_results_limits}
@@
 is included as one of the backgrounds. All four final states and 
-all categories are combined for these limits \cite{CMS-PAS-HIG-16-037-addit}.}
+all categories are combined for these limits. The light and dark green bands indicate
+the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
 \label{fig:mssm_results_greenband}
@@
 solid black line is the observed exclusion, with the dashed black line the
-expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
-expected exclusion. The red shaded area in the $m_{h}^{\text{mod}+}$ figure
+expected exclusion. The light and dark grey bands indicate
+the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit.
+The red shaded area in the $m_{h}^{\text{mod}+}$ figure
 is excluded by the lack of a light Higgs boson with mass compatible with 125 GeV \cite{CMS-PAS-HIG-16-037}.}
@@
 \label{sec:mssm_combination}
-The results of the search for MSSM \AHtotautau on a dataset
+The results of the search for neutral Higgs bosons in the  MSSM using the di-tau
+final state, using a dataset
 corresponding to an integrated luminosity of 12.9 fb$^{-1}$, collected during the
@@
 
-Because the 2015 analysis is very similar to the 2016 analysis it 
-is not described in detail, however, the results will
+The 2015 analysis uses the same channels, categories, and very
+similar background estimation methods as the 2016 analysis and so
+it is not described in detail. The results of the analysis will 
 be presented, and key differences with the more recent result highlighted
@@
 
-\section{Results from 2015 analysis}
+\section{Results from the 2015 analysis}
 \label{sec:mssm_combination_2015}
-The results from the search for \AHtotautau on a
-dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
-collected at a centre-of-mass energy of 13 TeV during 2015 are presented
-in this section. Like for the analysis presented in 
+As for the analysis presented in 
 chapter \ref{chap:mssm} a shape analysis is performed, however a different

### 2017-02-03 Conclusion/Conclusion.tex
And adding conclusion and outlook :-)

\chapter{Conclusions and outlook}
\label{chap:conclusions}
In this thesis analyses of proton-proton collisions recorded by the \ac{CMS} detector during
Run 1 and Run 2 of the \ac{LHC} have been presented.
The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ collected at a
centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350$ GeV. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario.

Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
using 2.3 fb$^{-1}$ of proton-proton collision data recorded during the 2015
data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of proton-proton collision
data recorded during the first half of the 2016 data-taking period.
No significant excess is observed, and so these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on this process to date.

As more data are collected during the rest of Run 2, and in the 
future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
MSSM benchmark scenarios. A projection of the results of the 2015 \ac{MSSM}
analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
3000 fb$^{-1}$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
is very low in the bottom right corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover the still
available phase space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons - or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/MSSMProjection.png}
\end{center}
\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
 at 95\% CL of the 2015 MSSM analysis (pink)
projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
under several assumptions of how the systematic uncertainties scale. Even with 3000 fb$^{-1}$
not the entire \mA-\tanb~plane in this MSSM benchmark model \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

### 2017-02-06 MSSM/MSSM.tex
Adding some more corrections

@@
 \begin{center}
-\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.pdf}}~\\
-\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.pdf}}
+\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.png}}~\\
+\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.png}}
 \end{center}
@@
 \begin{center}
-\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
-\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
+\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
 %\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
@@
 working point of the anti--electron discriminator and the loose working point of the anti--muon discriminator. 
-The tight working point of the isolation discriminator is chosen to optimise the sensitivity
-of this channel for higher masses, while retaining the second best senstivity in the intermediate
-mass range, as seen in figure \ref{fig:mssm_tauid_tt} for the gg$\phi$ process.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./MSSM/Figures/ggh_tt_isolation.png}
-\end{center}
-\caption{Expected upper limits for gg$\phi$ process in the \tautau channel, using the 
-loose (green), medium (red), tight (blue, very tight (black) and very very tight (gold)
-working point.}
+The tight working point of the isolation discriminator is chosen such that
+the channel is near-optimal at high mass, while not losing too much sensitivity in the low-intermediate mass range.
+This is illustrated in figure \ref{fig:mssm_tauid_tt} for the gg$\phi$ process.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
+\end{center}
+\caption{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
+in the \tautau channel, using the 
+medium (green), tight (red) and very tight working point of the tau isolation discriminator.
+The pattern is roughly the same as in the \etau and \mutau channels, with looser selections preferred at high
+mass.}
 \label{fig:mssm_tauid_tt}
@@
 first half of 2016 and thus referred to as `2016 analysis', can be combined 
-with a previous search. This previous analysis, very similar to the 2016 analysis,
+with a previous search. This previous analysis
 was performed on a dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
-collected during 2015 (`2015 analysis'), detailed in reference \cite{CMS-PAS-HIG-16-006}.
+collected during 2015 (`2015 analysis'), and is detailed in Ref. \cite{CMS-PAS-HIG-16-006}.
 By combining the two analyses we should be able to set the most stringent
@@
 process and (b) the b--associated production process. All four final states and 
-all categories are combined for these limits \cite{CMS-PAS-HIG-16-006}.}
+all categories are combined for these limits. The green and yellow bands indicate
+the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit  \cite{CMS-PAS-HIG-16-006}.}
 \label{fig:mssm_results_hig16006_limits}
@@
 \begin{center}
-\caption{Correlations between nuisance parameters in 2015 and 2016 analysis}
+\caption{Correlations between nuisance parameters in the 2015 and 2016 analysis}
 {\footnotesize
@@
 \midrule
-B-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods.\\
+B-tagging & Uncorrelated & Scale factors used in the 2015 and 2016 analysis measured via different methods.\\
 \midrule
@@
 \midrule
-Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, exhibiting the observed discrepancies, are used.
-In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar.}\\
+Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, are used in 2014 and 2016 to derive the correction.
+The weights derived for the 2015 analysis and the 2016 analysis are very similar.}\\
 \midrule
@@
 \midrule
-Drell-Yan $\sigma$& Correlated & Theoretical uncertainty so should be correlated.\\
-\midrule
-Di--boson $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
-\midrule
-\ttbar $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
-\midrule
-\Wjets $\sigma$ & Correlated & Theoretical uncertainty so should be correlated.\\
-\midrule
-SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated.\\
-\midrule
-\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet.}\\
+Drell-Yan $\sigma$& Correlated & The same recommended cross sections were used in 2015 and 2016.\\
+\midrule
+Di--boson $\sigma$ & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
+\midrule
+\ttbar $\sigma$ & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
+\midrule
+\Wjets $\sigma$ & Correlated & The same recommended cross section was used in 2015 and 2016..\\
+\midrule
+SM signal theory uncertainties & Correlated & The same recommende cross sections were used in 2015 and 2016..\\
+\midrule
+\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in the 2015 analysis as no fits to the \Zmm control region were included.}\\
 \midrule
@@
 %e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets.\\
-%$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
+%$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied.\\
 %jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
@@
 %QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
-%Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
+%Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 signal region and vice versa\\
 %Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
-%Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
+%Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
 In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that\\
@@
 \midrule
-Systematic \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region.
+Systematic \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
 In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
@@
 combine all categories and all four final states from both the 2015
-and the 2016 analysis.}
+and the 2016 analyses. The green and yellow bands indicate
+the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit.}
 \label{fig:mssm_results_combination_limits}
@@
 there is a larger improvement in sensitivity from combining the two analyses.
-This behaviour is expected since the analysis on the 2016 dataset used a slightly different
+This behaviour is expected since the 2016 analysis used a slightly different
 selection that made the analysis more optimal at masses above 800 GeV,
-and slightly less optimal below this mass, than the analysis on the 2015 dataset. This
+and slightly less optimal below this mass. This
 effect is less visible on the b--associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_limitcomp_ggH.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_limitcomp_bbH.pdf}}
+\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_ggH_with_ratio.pdf}}
+\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_bbH_with_ratio.pdf}}
 \end{center}
@@
 with the red line indicating the limits from the 2016 analysis only (integrated luminosity of 12.9 fb$^{-1}$)
-and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of 2.3 fb$^{-1}$).}
+and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of 2.3 fb$^{-1}$).
+The plotted relative difference is with respect to the limits from the 2016 analysis, showing how the combination
+improves on those limits by between a few per cent at high mass up to 40\% at low mass.}
 \label{fig:mssm_results_combination_limits_comp}

### 2017-02-06 Theory/Theory.tex
Adding some more corrections

@@
 \label{sec:theory_sm}
-The \ac{SM} of particle physics is a theory that describes the weak and strong
-nuclear forces, plus the \ac{EM} force, and the interaction of those forces
+The \ac{SM} of particle physics is a theory that describes the \ac{EM}, weak nuclear and strong
+nuclear forces, and the interaction of those forces
 with particles. The \ac{SM} is a \ac{QFT} in which matter particles
@@
 interact via the strong nuclear force (quarks) and six that do not (leptons).
-Each of the fermions has a corresponding antiparticle
+Each of the fermions has an antiparticle
 with opposite quantum numbers. The quarks and leptons
@@
 followed 10 years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
-and UA2 collaborations at \acs{CERN}.
+and UA2 collaborations at \acs{CERN}a, confirming the predicitions from electroweak unification.
 It should be noted that the weak force only couples to the left-handed parts
@@
 \label{sec:theory_sm_higgsmech}
-The masses of the vector bosons are generated via the
-Higgs mechanism, proposed in the 1960s by Englert and Brout \cite{englertbrout},
+The mechanism of electroweak symmetry breaking, the
+Higgs mechanism, was proposed in the 1960s by Englert and Brout \cite{englertbrout},
 Higgs \cite{higgs-I,higgs-II,higgs-III} and Guralnik, Hagen and Kibble \cite{GHK}.
@@
 \end{equation}
-The Lagrangian of this field is of the form
+The corresponding Lagrangian is of the form
 \begin{equation}\label{eqn:higgs_gen_lag}
@@
 &\mathcal{L}_{\text{Higgs}} = -(D_{\mu}\Phi)^{\dagger}(D^{\mu}\Phi) - V(\Phi^{\dagger}\Phi) \text{, with }\\
-&V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu^2}{2\lambda})^2,
+&V = \lambda(\Phi^{\dagger}\Phi - \frac{\mu_{\text{SM}}^2}{2\lambda})^2,
 \end{split}
 \end{equation}
-where $\lambda$ and $\mu^2$ are two real parameters. The parameter $\lambda$ 
+where $\lambda$ and $\mu_{\text{SM}}^2$ are two real parameters. The parameter $\lambda$ 
 is a quartic coupling strength modifier, and it will later be shown 
-that $\mu$ is a mass parameter.
+that $\mu_{\text{SM}}$ is a mass parameter.
 For the vacuum to be stable $\lambda$ must be positive,
-and for spontaneous symmetry breaking $\mu^2$ is also required to be positive.
+and for spontaneous symmetry breaking $\mu_{\text{SM}}^2$ is also required to be positive.
 
@@
 \end{equation}
-In the vacuum state, $V(\Phi^{\dagger}\Phi) =0$, $\Phi^{\dagger}\Phi=\frac{\mu^2}{2\lambda}$ and so
+In the vacuum state, $V(\Phi^{\dagger}\Phi) =0$, $\Phi^{\dagger}\Phi=\frac{\mu_{\text{SM}}^2}{2\lambda}$ and so
 $\Phi$ has to be nonzero.
@@
 %&\Phi^{\dagger}\Phi = \frac{\mu^2}{2\lambda} \Rightarrow\\
-%&\phi^{+*}\phi^+ + \phi^{0*}\phi^0 = \frac{\mu^2}{2\lambda} \text{ and choosing } \phi^+ \text{ = 0 and } \phi^0 \text{ to be real,}\\
+%&\phi^{+*}\phi^+ + \phi^{0*}\phi^0 = \frac{\mu_^2}{2\lambda} \text{ and choosing } \phi^+ \text{ = 0 and } \phi^0 \text{ to be real,}\\
 %&\phi^0 = \frac{v}{\sqrt{2}} \text{ where } v \text{ is real and} v^2=\frac{\mu^2}{\lambda}.
@@
 \end{equation}
-where $v$ is a real parameter, $v^2 \equiv \frac{\mu^2}{\lambda}$.
+where $v$ is a real parameter, $v^2 \equiv \frac{\mu_{\text{SM}}^2}{\lambda}$.
 
@@
 remaining, broken, generators as $\vec{b}$, and parameterising the field as an expansion around the
-vacuum state gives:
+vacuum state gives
 \begin{equation}\label{eqn:vev_expansion}
@@
 can be eliminated. They become the longitudinal degrees of freedom of the $\PW^{\pm}$ and \PZ 
+%longitudinal polarisation: ms=0
 bosons. This then leaves
@@
 \begin{split}
-&\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}h\partial^{\mu}h -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu^2h^2  + \\ 
+&\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}h\partial^{\mu}h -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu_{\text{SM}}^2h^2  + \\ 
 &\text{terms of at least }\mathcal{O}(3)\text{ in the fields}.
@@
 related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The remaining mass term is for the Higgs field $h$, 
-which leads to a mass $m_{h} = \sqrt{2\mu^2}$.
+$m_{h} = \sqrt{2\mu_{\text{SM}}^2}$.
 Note that the photon does not acquire a mass.
@@
 to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
-providing a lower search limit. Higgs boson searches at the 
+providing a lower search limit. Subsequent searches at the 
 Tevatron also did not lead to discovery of the Higgs boson, but did exclude 
@@
 More data were collected and analysed during the remainder of 2012, and subsequent studies 
-increased the confidence in the compatibility of this new state with being the \ac{SM} Higgs boson. 
+increased the confidence in the compatibility of this new state with the \ac{SM} Higgs boson. 
 The most precise measurement of the mass of the Higgs boson, \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV, 
@@
 The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \acs{LHC} Run 1,
-shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, through
-this combination the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$, while
+shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
+the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination, while
 the individual experiments did not reach a significance upwards of 5$\sigma$ in this channel during Run 1.
@@
 Figure \ref{fig:theory_smhprod} shows Feynman diagrams of the dominant Higgs boson production modes
-at the \ac{LHC}. From the production cross sections for each mode in figure
-\ref{fig:theory_smhxsbr}a we see that gluon fusion is by far dominant. The other modes
+at the \ac{LHC}. From the production cross sections for each mode, shown in figure
+\ref{fig:theory_smhxsbr}a, we see that gluon fusion production is by far dominant. The other modes
 shown have cross sections at least an order of magnitude smaller, but are of importance due to their topologies.
@@
 
-It is clear from the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b that
-the branching ratios into
+Considering the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b, we observe that
+the branching ratios of
 $\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow ZZ$, the two discovery
 channels, are smaller than the branching ratios into many other final states.
-These two channels are thus not sensitive as a result of their branching ratio, but
-rather due to the small backgrounds in these analysis as well as the excellent photon and lepton energy resolution the detectors provide.
+These two channels are thus not sensitive as a result of the size of their branching ratio, but
+rather due to the small backgrounds in these analyses as well as the excellent photon and lepton energy resolution the detectors provide.
 
@@
 out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
-keeps growing it will be possible to shed more light on the standard model Higgs boson.
+keeps growing studies at the \acs{LHC} will continue to test the compatibility of the Higgs boson with the \ac{SM}.
 
@@
 \end{align}
-These mixtures depend on \tanb~and the mixing angle $\alpha$ which arises
-from diagonalising
-the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}.
+These mixtures depend on \tanb~and the mixing angle $\alpha$ which is found
+by diagonalising
+the neutral scalar Higgs squared-mass matrix,
+\begin{equation}\label{eqn:treelevel_mass}
+\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
+m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
+-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix},
+\end{equation}
+of which \PHiggs and \PHiggslight are the eigenstates.
 As the self-interactions of the Higgs fields are not independent parameters,
@@
 one of the Higgs boson masses, conventionally chosen as \mA.
-The masses of the five Higgs states are then:
+The masses of the neutral scalars \PHiggs and \PHiggslight are the eigenvalues of 
+of $\mathcal{M}_{\text{tree}}^2$,
+\begin{equation}\label{eqn:scalarmass}
+m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}].
+\end{equation}
+The masses of the charged Higgs bosons are
 \begin{equation}\label{mssm_chargedhigss_mass}
@@
 \end{equation}
-while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the
-squared-mass matrix at tree level:
-\begin{equation}\label{eqn:treelevel_mass}
-\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
-m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
--(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
-\end{equation}
-Such that $m_{\PHiggs,\PHiggslight}$ are eigenvalues of $\mathcal{M}_{\text{tree}}^2$,
-\begin{equation}\label{eqn:scalarmass}
-m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
-\end{equation}
-A consequence of this is a tree-level upper bound to the mass of the light Higgs
+%while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the
+%squared-mass matrix at tree level:
+%\begin{equation}\label{eqn:treelevel_mass}
+%\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
+%m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
+%-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
+%\end{equation}
+%Such that $m_{\PHiggs,\PHiggslight}$ are eigenvalues of $\mathcal{M}_{\text{tree}}^2$,
+%\begin{equation}\label{eqn:scalarmass}
+%m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
+%\end{equation}
+A consequence of equation \ref{eqn:scalarmass} is a tree-level upper bound to the mass of the light Higgs
 boson,
@@
 The tree-level couplings of the neutral Higgs bosons to bosons and fermions 
-are modified with respect to the \ac{SM} couplings, by the multiplicative factors
+are modified with respect to the couplings of the Higgs boson in the \ac{SM}, by the multiplicative factors
 given in table \ref{tab:mssm_couplings} \cite{YR4}.
@@
 \caption{Tree-level couplings in the MSSM, as multiplicative factors with
-respect to the \ac{SM} couplings}
+respect to the couplings of the Higgs boson in the \ac{SM}.}
 \begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
@@
 The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
-into $\Pgt\Pgt$ of \PHiggsps are of similar size.
+ of the \PHiggsps boson follow a similar pattern.
 %Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
@@
 bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
-production are not as important as for the production of the \ac{SM} Higgs boson. Gluon fusion production is 
-the dominant production mode at low \tanb, as in the \ac{SM}. 
+production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, Gluon fusion production is 
+the dominant production mode at low \tanb.
 An example tree-level Feynman diagram for gluon fusion production, which proceeds via
@@
 high \tanb~the b-quark loop dominates. This is a result of the enhanced coupling to down-type fermions at high \tanb. 
-Another consequence of these enhanced couplings to down-type fermions at high \tanb~is the dominance of b-associated production, where the Higgs boson is produced through
+Due to the negative top-bottom loop interference effect the gluon fusion cross section decreases with increasing \tanb~up
+to around \tanb=3, when the cross section starts to increase with increasing \tanb~again.
+
+Another consequence of the enhanced couplings to down-type fermions at high \tanb~is the dominance of b-associated production, where the Higgs boson is produced through
 bottom quark fusion. The tree-level Feynman diagram for this process is shown in figure \ref{fig:production_mssm}b.
@@
 \begin{center}
-\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.pdf}}
+\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.png}}
 \subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
@@
 there is not one, but two Higgs doublets. The addition of a second
-Higgs doublet can of course be motivated by \ac{SUSY}, but also by other models.
-An important point to note is that despite the presence of a second 
+Higgs doublet can not just be motivated by \ac{SUSY}, but also by other models.
+An important point is that despite the presence of a second 
 Higgs doublet, there are no explicit \ac{SUSY} particles in the \ac{2HDM}.
@@
 There are several different types of \ac{2HDM}, all distinguished by the couplings
-of the different Higgs bosons to bosons and fermions. In its most general
+of the different Higgs states to bosons and fermions. In its most general
 form, there are 9 free parameters in the potential of a CP-conserving 2HDM. 
@@
 The inclusive cross-section times branching ratios for production of a \PHiggs boson 
-and decays into various states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
+and decays into various final states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
 example of a type-II \ac{2HDM}, at two \tanb~points. Figure \ref{fig:2hdm_Hxsbr}b 
@@
 In these scenarios the SUSY parameters entering in 
-the radiative corrections are fixed to define the scenario.
+the radiative corrections are fixed.
 
@@
 \ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks.
-In addition, the higgsino mass parameter $\mu$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
+In addition, the higgsino mass parameter $\mu_{\text{MSSM}}$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
 A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
@@
 \begin{split}
-&X_t = A_t-\mu\cot{\beta},\\
-&X_b = A_b-\mu\tan{\beta},\\
-&X_{\Pgt} = A_{\Pgt} - \mu\tan{\beta}.
+&X_t = A_t-\mu_{\text{MSSM}}\cot{\beta},\\
+&X_b = A_b-\mu_{\text{MSSM}}\tan{\beta},\\
+&X_{\Pgt} = A_{\Pgt} - \mu_{\text{MSSM}}\tan{\beta}.
 \end{split}
@@
 %meausrements 
-The remaining parameters are set as $\mu=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
+The remaining parameters are set as $\mu_{\text{MSSM}}=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
 $m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. 
@@
 \label{sec:mssm_theory_lowtb}
+The mass of the light Higgs boson in the \ac{MSSM} is said to
+be compatible with 125 GeV, if the light Higgs boson mass lies within a 
+mass window of $\pm 3$ GeV mass window around 125 GeV. This mass window
+corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
 A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 
@@
 figure \ref{fig:mhmodp_mh}a, illustrating that the mass 
-is not within $\pm 3$ GeV of 125 GeV at low \tanb. Masses within
-a window of $\pm3$ GeV around 125 GeV are considered compatible with 125
-GeV, as the 3 GeV variation corresponds to the theoretical uncertainty on the 
-\ac{MSSM} prediction for \mh.
-The low \tanb~regime can be re-opened
+is not within $\pm 3$ GeV of 125 GeV at low \tanb. The low \tanb~regime can be re-opened
 if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
@@
 \end{equation}
-The other trilinear couplings are set to 2 TeV, with $\mu$ set to 1.5 TeV and $M_2$ to 2 TeV.
+The other trilinear couplings are set to 2 TeV, with $\mu_{\text{MSSM}}$ set to 1.5 TeV and $M_2$ to 2 TeV.
 
@@
 can be sensitive in this scenario. %REPHRASE
-The analysis presented in chapter \ref{chap:hhh} is interpreted
-in the low-\tanb~scenario.
+%The analysis presented in chapter \ref{chap:hhh} is interpreted
+%in the low-\tanb~scenario.
 
@@
 qualitatively similar to those in other MSSM scenarios. Gluon fusion is dominant
-at low \tanb, with b-associated production being more important at high \tanb. The
-negative top-bottom loop interference effect again means the cross sections decrease with increasing 
-\tanb~up to around \tanb=3, when the cross sections start increasing with increasing \tanb~again.
+at low \tanb, with b-associated production being more important at high \tanb.
 
 The branching ratios of \PHiggs and \PHiggsps into $\tau\tau$ follow a similar
-pattern as in other MSSM scenarios again, with large branching ratios at high \tanb.
+pattern as in other MSSM scenarios, with large branching ratios at high \tanb.
 %\begin{figure}[h!]
@@
 Run 1 of the \ac{LHC} many searches for BSM Higgs
-bosons were already performed. Figure \ref{fig:bsm_summary} shows the interpetations
-of different searches performed within \acs{CMS} during Run 1 of the \acs{LHC}
+bosons were performed. Figure \ref{fig:bsm_summary} shows the interpetations
+of different searches performed with the \acs{CMS} detector during Run 1 of the \acs{LHC}
 in the $m_{h}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
@@
 In Run 2 of the \acs{LHC} searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
-have been performed in \acs{CMS}. The results of these searches will be presented in chapter \ref{chap:mssm}. 
+have been performed with the \acs{CMS} detector. The results of these searches will be presented in chapter \ref{chap:mssm}. 
 Similar searches have been performed by ATLAS \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons

### 2017-02-08 Conclusion/Conclusion.tex
Some more updates

@@
 In this thesis analyses of proton-proton collisions recorded by the \ac{CMS} detector during
-Run 1 and Run 2 of the \ac{LHC} have been presented.
+Run 1 and Run 2 of the \ac{LHC} have been presented. The focus of these analyses
+is the search for \ac{BSM} Higgs bosons with tau leptons in the final state.
+
 The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
-125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ collected at a
+125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ of data collected at a
 centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
 state can access areas of the MSSM phase space not easily accessible via other channels.
+To separate more signal-like and more background-like events, a categorisation based on the number of 
+b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
+mass in a window around 125 GeV are used in combination with a kinematic fitting technique for
+the reconstruction of the 4-body mass.
+The resulting mass variable provides good separation between the signal and the dominant
+\ttbar background, and is thus used as the variable for signal extraction. 
 The results of this search are upper limits on production cross section times branching 
@@
 Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
-using 2.3 fb$^{-1}$ of proton-proton collision data recorded during the 2015
-data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of proton-proton collision
-data recorded during the first half of the 2016 data-taking period.
-No significant excess is observed, and so these analyses set limits on the production cross section times branching ratio of both the
+using 2.3 fb$^{-1}$ of data recorded during the 2015
+data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of 
+data recorded during the first half of the 2016 data-taking period. The 
+branching ratio of heavy neutral Higgs bosons into di-\Pgt pairs is enhanced at high \tanb~in the \ac{MSSM},
+making this one of the most sensitive search channels for such particles. The analysis uses a categorisation 
+based on the presence of b-tagged jets to separate
+the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
+The hadronic tau isolation working point, as well as the topological selection on 
+the \mT~variable, are chosen to optimise the search sensitivity for signal
+masses of around 1 TeV.
+The sensitivity is maximised by using the \mTtot~variable for signal extraction.
+This variable separates the dominant backgrounds
+and the high-mass signal well.
+No significant excess is observed in these searches, and so 
+these analyses set limits on the production cross section times branching ratio of both the
 gluon fusion and b-associated production processes. The results are also
@@
 
-As more data are collected during the rest of Run 2, and in the 
+As more data are collected during the remainder of Run 2, and in the 
 future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
@@
 will be able to exclude even more of the \mA-\tanb~plane in specific
-MSSM benchmark scenarios. A projection of the results of the 2015 \ac{MSSM}
+MSSM benchmark scenarios, although not all of the \mA-\tanb~plane
+will become accessible. A projection of the results of the 2015 \ac{MSSM}
 analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
@@
 as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
-is very low in the bottom right corner. This region can be accessed 
+is very low in the high \mA-low \tanb~corner. This region can be accessed 
 via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/MSSMProjection.png}
+\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
 \end{center}
@@
 projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
-under several assumptions of how the systematic uncertainties scale. Even with 3000 fb$^{-1}$
-not the entire \mA-\tanb~plane in this MSSM benchmark model \cite{HTT-projection}.}
+under several assumptions of how the systematic uncertainties scale. Even with an integrated 
+luminosity of 3000 fb$^{-1}$ it is not possible to exclude the entire \mA-\tanb~plane
+in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
 \label{fig:mssm_projection_fig}

### 2017-02-08 MSSM/MSSM.tex
Some more updates

@@
 
-The basis of the event selection is to select \mutau, \etau,
+The basis of the event selection is to identify \mutau, \etau,
 \tautau and \emu pairs. Events are selected first by using a trigger,
@@
 muon (electron), the benefit of using such a trigger is small as 
-most of the signal samples at high-mass, the region of interest in this
+most of the signals at high-mass, the region of interest in this
 analysis, have higher \pT~electrons and muons. This is illustrated
@@
 In addition, a requirement is made on the $\eta$ of the electrons, muons and
-hadronic taus. Such a selection is driven by the $\eta$ range covered by the tracker and the $\eta$
-range that is used in the reconstruction of the particles,
-although in some cases the used trigger is restricted in $\eta$ and the cut is chosen to
-align with that. As an illustration figure \ref{fig:mt_muonpt}b shows
+hadronic taus. This election is driven by the $\eta$ range covered by the tracker and
+that is thus used for the reconstruction of the particles. For some of the
+channels the used trigger is restricted in $\eta$. If that is the case
+then the cut is chosen to align with the trigger restrictions.
+As an illustration figure \ref{fig:mt_muonpt}b shows
 the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
@@
 Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
-ensure that the particle is compatible with having
-originated from the primary vertex. This reduces the selection of particles
-coming from pile--up events. Additional identification and isolation criteria
-are also applied. These will be discussed in the following sections.
+ensure that the particle is likely to have
+originated from the primary vertex. This reduces the number of selected particles
+which come from pile--up interactions.
+Additional identification and isolation criteria
+are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
 The optimisation of some of the selections will also be discussed there. Note that 
-the optimisations were all based on the dataset collected during 2015, which
+the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
 corresponds to an integrated luminosity of 2.3 fb$^{-1}$.
@@
 \label{sec:mssm_eventsel_pairs}
-The basis of the event selection is the selection of \mutau, \etau,
-\tautau and \emu pairs by the requirements described
-in the following subsections. After applying trigger
+After applying trigger
 requirements, identification criteria and kinematic cuts
@@
 two most isolated candidates is only important where hadronic
-taus are concerned, for if there were additional electrons
-or muons the event would not pass the electron or muon veto.
+taus are concerned, for if there were additional electrons (muons)
+the event would not pass the electron (muon) veto.
 In addition to these extra electron and muon vetos, \Zee events are 
@@
 \end{itemize}
+
+\section{Discriminating variable}
+\label{sec:mssm_discrvar}
+The discriminating variable used for signal extraction is the total transverse mass,
+\begin{equation}\label{eqn:mttot}
+m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
+(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}.
+\end{equation}
+
+$m_{\text{T}}(1,2)$ is defined as,
+\begin{equation}\label{eqn:mttot_12}
+m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}.
+\end{equation}
+
+This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
+to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
+The \mTtot~variable provides good separation between signal and QCD multi--jet events
+in the \etau, \mutau and \tautau channels, and between
+signal and \ttbar events in the \emu channel. These are some of the 
+major backgrounds and thus good separation between these processes and 
+the signal is important for the sensitivity of the analysis.
+The separation between signal and backgrounds is illustrated in figure
+\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps}a shows the total transverse mass
+distribution of the QCD
+background in the no b-tag category of the \tautau channel with the gluon fusion
+signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
+shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
+the b-associated production signal at the same three masses overlaid.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[QCD and signal in \tautau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_tt_nobtag.pdf}}
+\subfloat[\ttbar and signal in \emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_em_btag.pdf}}
+\end{center}
+\caption{Total transverse mass distributions in (a) the no b-tag category of the \tautau
+channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
+category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
+The total transverse mass variable separates the signal and these backgrounds well.}
+\label{fig:mttot_sigseps}
+\end{figure}
 
@@
 
-\section{Discriminating variable}
-\label{sec:mssm_discrvar}
-The discriminating variable used for signal extraction is the total transverse mass,
-\begin{equation}\label{eqn:mttot}
-m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
-(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}.
-\end{equation}
-
-$m_{\text{T}}(1,2)$ is defined as,
-\begin{equation}\label{eqn:mttot_12}
-m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}.
-\end{equation}
-
-This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
-to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
-The \mTtot~variable provides good separation between signal and QCD multi--jet events
-in the \etau, \mutau and \tautau channels, and between
-signal and \ttbar events in the \emu channel. These are some of the 
-major backgrounds and thus good separation between these processes and 
-the signal is important for the sensitivity of the analysis.
-The separation between signal and backgrounds is illustrated in figure
-\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps} shows the total transverse mass
-distribution of the QCD
-background in the no b-tag category of the \tautau channel with the gluon fusion
-signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
-shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
-the b-associated production signal at the same three masses overlaid.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[QCD and signal in \tautau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_tt_nobtag.pdf}}
-\subfloat[\ttbar and signal in \emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_em_btag.pdf}}
-\end{center}
-\caption{Total transverse mass distributions in (a) the no b-tag category of the \tautau
-channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
-category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
-The total transverse mass variable separates the signal and these backgrounds well.}
-\label{fig:mttot_sigseps}
-\end{figure}
-
 \section{Background estimation}
@@
 is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
-it has two real taus in the final state, like the signal that we are searching for. The only aspect
-that distinguishes the \Ztautau background from the gluon fusion signal is the mass of the particle. Smaller backgrounds
+it has two real taus in the final state, like the signal that we are searching for. 
+Smaller backgrounds 
 from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
-might pass the selection for example if a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
-Production of QCD multijet events, labelled QCD on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
+might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
+Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
 two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
 As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
-This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$. and so such events 
-always contain real b-jets. One or both of the \PW bosons, and additional jets in the event, can 
-then form \etau, \mutau, \tautau and \emu pairs.
-The \Wjets background arises in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
+This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
+always contain real b-jets. The decay products  of one or both of the \PW bosons, and additional jets in the event, can 
+then form \etau, \mutau, \tautau and \emu pairs.\\
+The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
 as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
@@
 reconstructed as hadronic taus.
-In the \emu channel an additional lepton would have to originate from one of the jets, and so here this
-background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
+In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
+channel this background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
 figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
@@
 estimated using data-driven techniques. The control regions used
-in the estimation of QCD and \Wjets in the \etau and \mutau channels
+for the estimation of QCD and \Wjets in the \etau and \mutau channels
 are included in a simultaneous fit with the signal region to obtain
-the final results. More detail on this is given in section ADD SECTION.
+the final results. More detail on this is given in section \ref{sec:mssm_sigext_ctrl}.
 In the \emu and \tautau channels the \Wjets background is estimated using
-\ac{MC} samples. The \Ztautau and \Zellell backgrounds are also estimated
-using \ac{MC} samples, and a \Zmm control region
+\ac{MC} samples. The \Ztautau and \Zellell backgrounds are estimated
+using \ac{MC} samples for all four channels. A \Zmm control region
 is considered in a simultaneous fit with the signal region to correct and
@@
 to obtain an estimate of the number of QCD events in the signal region.
-
-\subsubsection{Control regions in the fit}
-\label{sec:mssm_bkgs_etmt_ctrl}
-Several control regions in data are used for the estimation
-of the QCD and \Wjets backgrounds: the same--sign and 
-opposite--sign high \mT~regions, as well as the same--sign
-low \mT~region. This leads to three control regions used 
-in each category of both the \mutau and \etau channels to determine
-the initial estimate of the background normalisations.
-These control regions are included in a simultaneous fit
-with the signal regions to obtain the final results. More detail
-can be found in section \ref{sec:mssm_sigext_ctrl}.
+%\subsubsection{Control regions in the fit}
+%\label{sec:mssm_bkgs_etmt_ctrl}
+%Several control regions in data are used for the estimation
+%of the QCD and \Wjets backgrounds: the same--sign and 
+%opposite--sign high \mT~regions, as well as the same--sign
+%low \mT~region. This leads to three control regions used 
+%in each category of both the \mutau and \etau channels to determine
+%the initial estimate of the background normalisations.
+%These control regions are included in a simultaneous fit
+%with the signal regions to obtain the final results. More detail
+%can be found in section \ref{sec:mssm_sigext_ctrl}.
 
@@
 nuisance parameters in the 2015 and 2016 analyses need to be taken into account.
-The correct way to establish the correlations is to perform
-dedicated studies into them. In many cases such studies would be 
-unfeasible to perform, or it would not be clear how to approach the 
-problem in the first place.
-
-Even without performing these studies, a choice of correlation scheme can be motivated
-by carefully considering the differences between the two analyses and the conditions
-under which they were performed.
-This is what has been done for this combination.
+
+The choice of correlation scheme is decided on
+based on the procedure used for the ATLAS and \ac{CMS}
+Higgs combinations \cite{MassComb,CouplComb}. This means
+uncertainties are either considered 100\% correlated or fully uncorrelated. Partial
+correlations are not taken into account, with a small number of exceptions. The
+correlations used for this combination are given in table \ref{tab:mssm_combination_correlations},
+with the motivation for the chosen correlation given in the third column of the table.
+The chosen correlation scheme is motivated
+by carefully considering the differences between the two analyses
+and the conditions under which they were perofrmed.
+
+%The correct way to establish the correlations is to perform
+%dedicated studies into them. In many cases such studies would be 
+%unfeasible to perform, or it would not be clear how to approach the 
+%problem in the first place.
+%Even without performing these studies, a choice of correlation scheme can be motivated
+%by carefully considering the differences between the two analyses and the conditions
+%under which they were performed.
+%This is what has been done for this combination.
 %Strictly, studies into the underlying correlations between
@@
 %feasible and in some cases
-The correlation scheme between nuisance parameters relating to the 2015 and 2016
-analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
-The third column of this table gives the motivation for the chosen correlation.
+%The correlation scheme between nuisance parameters relating to the 2015 and 2016
+%analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
+%The third column of this table gives the motivation for the chosen correlation.
 
@@
 \midrule
-e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets.\\
+e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expected to behave the same in 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.\\
 \midrule

### 2017-02-09 Conclusion/Conclusion.tex
Some boring caption stuff

@@
 \end{center}
-\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
+\caption[The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
+at 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of 300-3000 fb$^{-1}$.]{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
  at 95\% CL of the 2015 MSSM analysis (pink)

### 2017-02-09 Detector/Detector.tex
Some boring caption stuff

@@
 \includegraphics[width=\textwidth]{./Detector/Plots/LHC_default.jpg}
-\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
+\caption[Schematic of the CERN accelerator complex.]{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
 \label{fig:lhc_schematic}
@@
 \includegraphics[width=0.5\textwidth]{./Detector/Plots/crosssections2013.jpg}
-\caption{Total proton-proton cross section, and the cross-sections
+\caption[Total proton-proton cross section, and the cross-sections for
+several processes studied at the LHC.]{Total proton-proton cross section, and the cross-sections
 for several processes studied at the LHC \cite{stirling-crosssection}.
@@
 \includegraphics[width=0.85\textwidth]{./Detector/Plots/int_lumi_cumulative_pp_2.pdf}
-\caption{Cumulative integrated luminosity delivered to \ac{CMS} for p--p collisions at the \ac{LHC}, separated
+\caption[Cumulative integrated luminosity delivered to CMS
+for p--p collisions at the LHC, separated by running year.]{Cumulative integrated luminosity delivered to \ac{CMS} for p--p collisions at the \ac{LHC}, separated
 by running year \cite{cms-lumi-public}.}
@@
 \includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
-\caption{A cutaway view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
+\caption[A cutaway view of the CMS detector, indicating the different sub-parts of the detector.]{A cutaway view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
 different sub-parts of the detector.}
@@
 \includegraphics[width=0.9\textwidth]{./Detector/Plots/Tracker.png}
-\caption{Schematic of the CMS tracker in the r-z plane, indicating the
+\caption[Schematic of the CMS tracker in the 
+r-z plane, indicating the positions of the pixel and
+strip detectors.]{Schematic of the CMS tracker in the r-z plane, indicating the
 positions of the pixel and strip detectors \cite{cms-jinst}. Each line 
-on the plot represents a detector module}
+on the plot represents a detector module.}
 \label{fig:CMS_tracker}
@@
 \includegraphics[width=0.9\textwidth]{./Detector/Plots/ECAL.png}
-\caption{Layout of the \ac{ECAL}, indicating the position of the
+\caption[Layout of the ECAL, indicating the positions
+of the different components.]{Layout of the \ac{ECAL}, indicating the position of the
 different components \cite{cms-jinst}.}
@@
 \includegraphics[width=0.9\textwidth]{./Detector/Plots/HCAL.png}
-\caption{Illustration of a quadrant of the \ac{HCAL}, showing the different
+\caption[Illustration of a quadrant of the HCAL, showing the different
+subsystems of the detector.]{Illustration of a quadrant of the \ac{HCAL}, showing the different
 subsystems of the detector \cite{cms-jinst}.}
@@
 \includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystemUpgrade.png}
-\caption{Cross-section of one quadrant of the CMS detector, indicating
+\caption[Cross-section of one quadrant of the CMS detector,
+indicating the positions of the different muon system components.]{Cross-section of one quadrant of the CMS detector, indicating
 the positions of the different muon system components \cite{cms-muon-upgrade}. The 
@@
 \includegraphics[width=0.7\textwidth]{./Detector/Plots/CMSTrigger.png}
-\caption{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
+\caption[Schematic of the different components of the L1 trigger.]{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
 \label{fig:CMS_Trigger}

### 2017-02-09 Hhh/Hhh.tex
Some boring caption stuff

@@
 This section gives an overview of the event selection, a detailed description of the physics
-objecs used in this analysis is given in chapter OBJECTS.
+objecs used in this analysis is given in chapter \ref{chap:objects}.
 
@@
 than 0.045 and 0.2 cm respectively. Tight muon identification
-criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
-in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
+criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$
+ are applied. The hadronic tau must have a \pT~of at least
 20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
@@
 \end{center}
-\caption{\mT~distributions in the \mutau (left) and \etau (right) channels}
+\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the \mutau (left) and \etau (right) channels.}
 \label{fig:Hhh_selection_mt}
@@
 \end{center}
-\caption{Number of b-tagged jets in the 2-jet selection of the \mutau (left) and \etau (right) channels. The signal
+\caption[Number of b-tagged jets in the 2-jet selection of the \mutau and \etau channels.]{Number of b-tagged jets in the 2-jet selection of the \mutau (left) and \etau (right) channels. The signal
 at \mH~=$300$~GeV and \tanb~=2, multiplied by a factor of 10, is overlaid on the figures.}
@@
 \end{center}
-\caption{Reconstructed di-\Pgt invariant mass (left) and di-jet invariant mass (right) in the 2jet-2tag category of the \mutau
+\caption[Reconstruced di-\Pgt invariant mass and di-jet invariant mass in
+the 2jet-2tag category of the \mutau channel.]{Reconstructed di-\Pgt invariant mass (left) and di-jet invariant mass (right) in the 2jet-2tag category of the \mutau
 channel. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in the low \tanb~ MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
@@
 Differences in \MET resolution and response between data and \ac{MC} are accounted for by
-applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter OBJECTS
+applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter \ref{chap:objects} 
 gives more details on how these corrections are derived.
@@
 where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
-the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET as discussed in the
-OBJECTS section,
+the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
 while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
@@
 \end{center}
-\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
+\caption[Comparison of the reconstructed heavy Higgs mass
+using the kinematic fit in signal events with $m_{H}=300$ GeV and \ttbar 
+background events in the 2jet-1tag category of the \mutau channel.]{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
 4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $~GeV (left) and \ttbar background events (right) in 
@@
 \includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
-\caption{The 95\% confidence level expected (dashed) and observed (solid)
+\caption[The 95\% confidence level expected and observed upper limits on the 
+$\sigma \times$ BR for the \AtoZhtolltautau process.]{The 95\% confidence level expected (dashed) and observed (solid)
 upper limits on the $\sigma \times BR$ for the \AtoZhtolltautau process.
@@
 \end{center}
-\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+\caption[Distributions of $m_{h}^{\text{kinfit}}$ in the 2jet-0tag,
+2jet-1tag and 2jet-2tag categories of the \mutau channel.]{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
 of the \mutau channel. The \Htohhtobbtautau signal for \mA $= 300 $~GeV at \tanb=2 in the low \tanb~MSSM
@@
 \end{center}
-\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
+\caption[Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag,
+2jet-1tag and 2jet-2tag categories of the \etau channel.]{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
 of the \etau channel. The \Htohhtobbtautau signal for \mA $ = 300 $~GeV at \tanb=2 in the low \tanb~ MSSM
@@
 \subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
-\caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
+\caption[Expected and observed 95\% CL upper limits on cross--section
+times branching ratio for the \Htohhtobbtautau process.]{Expected and observed 95\% CL upper limits on cross-section times branching ratio
 for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034} (left).
@@
 \subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZh2HDM.pdf}}
-\caption{Search for \Htohhtobbtautau (left) and \AtoZhtolltautau (right) interpreted in a type II 
+\caption[Search for \Htohhtobbtautau and search for \AtoZhtolltautau
+interpreted in a type II 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV.]{Search for \Htohhtobbtautau (left) and \AtoZhtolltautau (right) interpreted in a type II 
 2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
@@
 \subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}}
-\caption{Cross-section times branching ratio of the \Htohhtobbtautau process (left) and of the
+\caption[Cross-section times branching ratio of the \Htohhtobbtautau
+process and the \AtoZhtolltautau process in the low-\tanb ~MSSM scenario. The
+expected and observed 95\% CL exclusion limits for the \AtoZhtolltautau analysis
+in the low \tanb~MSSM scenario have been overlaid.]{Cross-section times branching ratio of the \Htohhtobbtautau process (left) and of the
 \AtoZhtolltautau process (right) in the low-\tanb ~MSSM scenario. On the right-hand side
@@
 \subfloat[low \tanb ~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
-\caption{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
+\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
+interpreted in a type II 2HDM and in the low \tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
 interpreted in a type II 2HDM assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV (left) and interpreted

### 2017-02-09 MSSM/MSSM.tex
Some boring caption stuff

@@
 \end{center}
-\caption{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
+\caption[The \pT~of the muon in the \mutau channel
+and $\eta$ of the electron in the \etau channel, with the signal
+overlaid.]{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
 The gluon fusion (dashed blue line)
@@
 \end{center}
-\caption{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
-the best--fit value of a maximum--likeihood fit to the \Ztautau signal strength,
+\caption[The $S/\sqrt{B}$ for \Ztautau signal and
+the size of the error interval on the best--fit value of a
+maximum--likelihood fit to the \Ztautau signal strength, for various 
+isolation selections.]{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
+the best--fit value of a maximum--likelihood fit to the \Ztautau signal strength,
 for various selections of the $\Delta\beta$--corrected
@@
 \end{center}
-\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
+\caption[Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$
+production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
+working point and \mT~selection, for two mass points.]{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
 as a function of tau isolation working point (from very loose to very very tight) and
@@
 \end{center}
-\caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
+\caption[Pre-fit expected limits on $\sigma \times$ BR for the gg$\phi$ and bb$\phi$
+processes
+in the
+\mutau channel for an increasingly looser \mT~selection and tau isolation
+working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
 (b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
@@
 \end{center}
-\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
+\caption[Pre-fit expected limits on $\sigma\times$BR in the
+\mutau channel for gg$\phi$ and bb$\phi$ prouduction, comparing
+different hadronic tau \pT~cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
 limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
@@
 \end{center}
-\caption{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
+\caption[Pre-fit expected limits on $\sigma\times$ BR in the \etau
+channel for gg$\phi$ and bb$\phi$ production for an increasingly
+looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
 (b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
@@
 \end{center}
-\caption{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
+\caption[Pre-fit expected limits on $\sigma\times$BR in the \etau
+channel for gg$\phi$ and bb$\phi$ production comparing different
+hadronic tau isolation cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
 limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
@@
 \end{center}
-\caption{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
+\caption[Expected upper limits for the gg$\phi$ and bb$\phi$ process
+in the \tautau channel, comparing different hadronic tau isolation working
+points.]{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
 in the \tautau channel, using the 
@@
 \end{center}
-\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
+\caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
+in the \emu channel.]{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
 \emu channel\cite{CMS-PAS-HIG-16-037}.}
@@
 \end{center}
-\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
+\caption[Number of jets and number of b-tagged jets in the \mutau channel, 
+with the signal overlaid.]{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
 blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
@@
 \end{center}
-\caption{Total transverse mass distributions in (a) the no b-tag category of the \tautau
+\caption[Total transverse mass distributions in the no b-tag category of the
+\tautau channel for QCD and gluon fusion signal, and in the b-tag category
+of the \emu channel, for \ttbar and b-associated signal.]{Total transverse mass distributions in (a) the no b-tag category of the \tautau
 channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
@@
 \end{center}
-\caption{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,
+\caption[\mTtot~distribution in the \ttbar
+enriched control region, with and without applying top quark \pT~reweighting.]{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,
 (a) without applying top quark \pT~reweighting and (b) with top quark \pT~reweighting.
@@
 \end{center}
-\caption{(a) The mismodelling in the \PZ \pT~distribution as observed
+\caption[The mismodelling in the \PZ \pT~distribution as observed
+in \Zmm events, and the impact of applying the Drell-Yan shape reweighting
+on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mismodelling in the \PZ \pT~distribution as observed
 in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
@@
 \end{center}
-\caption{The low $m_{\text{T}}^{\text{tot}}$ region in (a) the 
+\caption[The low \mTtot~region in the no b-tag category of the \mutau channel 
+and in the b-tag category of the \emu channel.]{The low $m_{\text{T}}^{\text{tot}}$ region in (a) the 
 no b-tag category of the \mutau channel and (b) the b-tag category of the \emu channel.
@@
 \end{center}
-\caption{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
+\caption[High-\mT~control region in the no b-tag and b-tag
+categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
 channel. In the no b-tag category the \Wjets background, drawn together with the small
@@
 \end{center}
-\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
+\caption[The visible mass distribution of the di-$\tau$ pair
+in the \mutau channel for the sideband near the signal region, before
+and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
 the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
@@
 \end{center}
-\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
+\caption[The visible mass distribution of the di-$\tau$ pair in the
+\mutau channel for the sideband further away from the signal region,
+before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
+the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength 
 is 1.184$\pm$0.035.}
@@
 \end{center}
-\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength is 1.015$\pm$0.059.}
+\caption[The visible mass distribution of the di-$\tau$ pair in
+the \etau channel for the sideband near the signal region,
+before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength is 1.015$\pm$0.059.}
 \label{fig:mssm_qcdosss_etnear}
@@
 \end{center}
-\caption{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
+\caption[The visible mass distribution of the di-$\tau$ pair
+in the \etau channel for the sideband further away from the signal
+region, before and after the maximum likelihood fit to the QCD signal 
+strength.]{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
 the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength
@@
 \end{center}
-\caption{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
+\caption[Impact of the high-\pT~tau ID uncertainty in the no b-tag category
+of the \tautau channel for a high-mass signal sample and the \Ztautau
+background.]{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
 \tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is much
@@
 \end{center}
-\caption{Probability density functions, obtained by generating a large number of toy datasets, for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$
+\caption[Probability density functions for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$ scenario.]{Probability density functions, obtained by generating a large number of toy datasets, for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$
 scenario, each with different levels of separation between the MSSM and SM distributions.}
@@
 \end{center}
-\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
+of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \mutau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 \end{center}
-\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+\caption[Distributions of \mTtot~inthe no b-tag and b-tag 
+categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \etau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 \end{center}
-\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
+of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
 of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
@@
 \end{center}
-\caption{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories of 
+the \emu channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+of the \emu channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
 and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at 95\% CL for the gluon fusion production process and the
+b-associated production process, combining all final states and categories.]{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. All four final states and 
@@
 \end{center}
-\caption{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
+\caption[Comparison of expected upper limits at 95\% CL for gluon fusion and 
+b-associated production per channel.]{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production processes, with the 125 GeV Higgs boson included as one of the backgrounds.]{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. The SM, 125 GeV Higgs boson
@@
 \end{center}
-\caption{2D likelihood scans showing the best-fit value (black cross) for cross--section times branching ratio 
+\caption[2D likelihood scans showing the best-fit value for cross--section 
+times branching ratio of both the gluon fusion and b-associated production 
+processes.]{2D likelihood scans showing the best-fit value (black cross) for cross--section times branching ratio 
 of both the gluon fusion (x-axis) and b- associated production (y-axis) processes. The red diamond indicates the
@@
 \end{center}
-\caption{Exclusion in (a) the $m_{h}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+\caption[Exclusion in the $m_{h}^{\text{mod+}}$ scenario and the hMSSM
+scenario of the \AHtotautau analysis.]{Exclusion in (a) the $m_{h}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
 obtained by the combination
@@
 \end{center}
-\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\caption[Transverse component of the di-\Pgt mass for expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \mutau channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
@@
 \end{center}
-\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\caption[Transverse component of the di-\Pgt mass for expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \etau channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \etau channel.}
@@
 \end{center}
-\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\caption[Transverse component of the di-\Pgt mass for expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \tautau
+channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \tautau channel.}
@@
 \end{center}
-\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\caption[Transverse component of the di-\Pgt mass for expected backgrounds
+and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production process.]{Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. All four final states and 
@@
 \end{center}
-\caption{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
+\caption[Expected upper limits at 95\% CL for the gluon fusion and b-associated
+production, comparing the combination of all channels with the per-channel limits.]{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
@@
 \end{center}
-\caption{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production
+process, obtained by combining all channels and categories of the 2015 nd the 2016 analyses.] {Upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. These results
@@
 \end{center}
-\caption{Comparison of the expected upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Comparison of the expected upper limits at 95\% CL for the 
+gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at 95\% CL for (a) the gluon fusion production
 process and (b) the b--associated production process. The green curve shows the results

### 2017-02-09 Objects/Objects.tex
Some boring caption stuff

@@
 \end{center}
-\caption{Resolution of the x-- (a) and z--coordinate  (b)
+\caption[Resolution of the x- and z- coordinates of reconstructed
+primary vertices as a function of the scalar sum of the \pT s of the associated
+tracks.]{Resolution of the x-- (a) and z--coordinate  (b)
 of reconstructed primary vertices
@@
 \end{center}
-\caption{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
+\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
+and misidentified electrons at 8 TeV, for data and MC]{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
 misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
@@
 \includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
-\caption{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
+\caption[The b--tagging scale factors and errors for b--jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$
 %collected at $\sqrt{s} = 13$ TeV and (b) 
@@
 \end{center}
-\caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
+\caption[\MET~distributions comparing MVA \MET~to PF \MET~for
+\Zmm events, in a sample corresponding to 42 pb$^{-1}$ of data collected
+at $\sqrt{s}=13$ TeV.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
 \Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=$\mbox{13 TeV}. The \MET~
@@
 \end{center}
-\caption{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
+\caption[Figures of the jet$\rightarrow\Pgt_{h}$ fake rate in QCD MC events
+versus $\Pgt_{h}$ identification efficiency for \htotautau MC events, the real
+$\Pgt_{h}$ identification efficiecny for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
+working points of the anti-electron discriminator.]{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
 efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 

### 2017-02-09 Theory/Theory.tex
Some boring caption stuff

@@
 \end{center}
-\caption{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
+\caption[Tree-level Feynman diagrams for the dominant Higgs production modes at the LHC]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
 the \ac{LHC}.}
@@
 \end{center}
-\caption{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
+\caption[SM Higgs boson production cross sections at $\sqrt{s}=13$ TeV and SM Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
 Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
@@
 \begin{center}
-\caption{Tree-level couplings in the MSSM, as multiplicative factors with
+\caption[Tree-level couplings in the MSSM, as multiplicative factors with respect to the couplings of the Higgs boson in the SM]{Tree-level couplings in the MSSM, as multiplicative factors with
 respect to the couplings of the Higgs boson in the \ac{SM}.}
@@
 \end{center}
-\caption{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
-production of neutral Higgs boson in the MSSM \cite{CMS-PAS-HIG-16-037}.}
+\caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
+production of neutral Higgs bosons in the MSSM \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:production_mssm}
@@
 \end{center}
-\caption{Inclusive production cross--section times branching ratio for an example
+\caption[Inclusive production cross--section times branching ratio for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production cross--section times branching ratio for an example
 of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
@@
 \end{center}
-\caption{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
+\caption[Production cross--sections of  gluon fusion and b--associated
+production of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario.]{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
 in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
@@
 \end{center}
-\caption{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
+\caption[Branching ratio of \PHiggs and \PHiggsps into $\tau\tau$.]{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
 ratios into $\tau\tau$ are enhanced at high \tanb.}
@@
 \end{center}
-\caption{The mass of the light Higgs boson, \mh, as a function 
+\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
+\tanb~in the $m_{h}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
 of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
@@
 \end{center}
-\caption{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
+\caption[Branching fractions of \Htohh and \AtoZh in the low-\tanb~scenario.]{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
 areas where both are significantly enhanced \cite{MSSM-lowtanb}.}
@@
 \end{center}
-\caption{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
+\caption[Summary of the interpretations of Run 1 BSM Higgs searches at CMS in the $m_{h}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
 hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these

### 2017-02-09 frontmatter.tex
Updating Hhh section
Adding some more stuff
First round of own comments on detector chapter
Some more updates
Some boring caption stuff

@@
 %% Title
-\titlepage[Imperial College London]{%
+\titlepage[Imperial College London\\ Department of Physics]{
   A dissertation submitted to Imperial College London\\ for the degree of Doctor of Philosophy}
 
+\begin{abstract}[]
+The copyright of this thesis rests with the author and is made available under a
+Creative Commons Attribution Non-Commercial No Derivatives licence. Researchers
+are free to copy, distribute or transmit the thesis on the condition that they
+attribute it, that they do not use it for commercial purposes and that they do
+not alter, transform or build upon it. For any reuse or redistribution,
+researchers must make clear to others the licence terms of this work.
+\end{abstract}
 %% Abstract
-%\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
+\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
+The BLAH BLAH
   %\thispagestyle{empty}
-%\end{abstract}
+\end{abstract}
 
@@
 %\end{preface}
-
 %% ToC
 \tableofcontents
+%\listoffigures
+%\listoftables
 

### 2017-02-12 Hhh/Hhh.tex
Committing some updates before edit round 1

@@
 Differences in \MET resolution and response between data and \ac{MC} are accounted for by
-applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter \ref{chap:objects} 
+applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
 gives more details on how these corrections are derived.
@@
 extrapolation factor is determined from the \Wjets \ac{MC} 
-samples. The yield in the signal region is given by the data yield in the high-\mT sideband, with
+samples. The yield in the signal region is given by the data yield in the high-\mT~sideband, with
 other backgrounds subtracted, multiplied by this extrapolation factor.

### 2017-02-12 Detector/Detector.tex
Detailed edit of detector chapter

@@
 
-The \acf{LHC} \cite{lhc-machine}  is a 26.7 km long synchrotron hadron accelerator and collider below the surface of the 
+The \acf{LHC} \cite{lhc-machine}  is a $26.7\,\kilo\metre$ long synchrotron hadron accelerator and collider below the surface of the 
 Franco-Swiss border near Geneva. It
@@
 
-The \ac{LHC} was designed to collide beams of protons with each other at centre-of-mass
-energies of up to 14 TeV. It therefore consists of two rings in which the two beams
+The \ac{LHC} was designed to collide two beams of protons %with each other 
+at centre-of-mass
+energies ($\sqrt{s}$) of up to $14\,\TeV$. It therefore consists of two rings in which the beams
 of protons are individually accelerated. In addition to colliding beams of protons, the \ac{LHC}
-is also used for proton--lead and lead--lead collisions.
+is also used for proton-lead and lead-lead collisions.
 \begin{figure}[h!]
@@
 \end{figure}
+
 The \ac{LHC} does not operate on its own: the protons are fed into
@@
 of the \ac{CERN} accelerator complex.
-
 Protons originate from hydrogen gas, where electrons are stripped off the 
@@
 chain which increases the energy of the protons in several steps. After the protons
-are created from the hydrogen gas, they are accelerated to an energy of
-50 MeV in the Linac2 linear accelerator. They are then passed on to the
-\acf{PSB} which accelerates the protons until they reach an energy of 1.4 GeV.
-The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
-with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
+are created from the hydrogen gas they are accelerated to an energy of
+$50\,\MeV$ in the Linac~2 linear accelerator. They are then passed on to the
+\acf{PSB} which accelerates the protons until they reach an energy of $1.4\,\GeV$.
+The next accelerator in the chain, the \acf{PS}, further accelerates the protons to $25\,\GeV$,
+with the \acf{SPS} bringing the energy up to $450\,\GeV$. When this energy has been 
 reached the protons are injected into the \ac{LHC} in two counter-rotating
@@
 by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
-of $\mathcal{O}(10^{11})$ protons, spaced 25ns apart. The beams are kept in circulation
+of $\mathcal{O}(10^{11})$ protons, spaced $25\,\ns$ apart. The beams are kept in circulation
 using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
-a temperature of 1.9K and generating magnetic fields of up to 8.4 Tesla.
+a temperature of $1.9\,\kelvin$ and generating magnetic fields of up to $8.4\,\tesla$.
 The beams collide at four points
 around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
-\acs{CMS} \cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
+\acs{CMS}\cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.
 
-The processes the \ac{LHC} was built to study have a small cross-section
-compared with the total proton-proton inelastic cross-section, as seen from figure
-\ref{fig:stirling_xs}. For example, the production cross-section of the
-standard model Higgs boson is 9-10 orders of magnitude smaller than the total p--p cross section.
-In order to be able to study these relatively rare processes, 
-the LHC operates at high instantaneous luminosity, defined as
+The processes the \ac{LHC} was built to study have a small cross section
+compared with the total proton-proton (p-p) inelastic cross section, as seen from figure
+\ref{fig:stirling_xs}. For example, the production cross section of the
+\ac{SM} Higgs boson is 9--10 orders of magnitude smaller than the total p-p cross section.
+In order to be able to study these relatively rare processes  
+the \ac{LHC} operates at high instantaneous luminosity, defined as
 \begin{equation}\label{eqn:CMSLHC_luminosity}
@@
 \includegraphics[width=0.5\textwidth]{./Detector/Plots/crosssections2013.jpg}
-\caption[Total proton-proton cross section, and the cross-sections for
-several processes studied at the LHC.]{Total proton-proton cross section, and the cross-sections
-for several processes studied at the LHC \cite{stirling-crosssection}.
+\caption[Total p-p cross section, and the cross sections for
+several processes studied at the LHC.]{Total p-p cross section, $\sigma^{\text{tot}}$, and the cross sections
+for several processes studied at the LHC as a function of $\sqrt{s}$ \cite{stirling-crosssection}.
 The cross sections of these processes
-are often many orders of magnitude smaller than the total p--p cross section.}
+are often many orders of magnitude smaller than the total p-p cross section.}
 \label{fig:stirling_xs}
@@
 The \ac{LHC} began its first physics run in May 2010, colliding protons at
-a centre-of-mass energy of 7 TeV, and continued operation until the end of 2012. After this the 
-2-year \ac{LS1} was used to upgrade the \ac{LHC} and the detectors for collisions at a centre-of-mass
-energy of 13-14 TeV. In April 2015 the \ac{LHC} restarted with collisions at a centre-of-mass energy of
-13 TeV. The integrated luminosity delivered to the \ac{CMS} experiment, separated by running year, is shown in
+$\sqrt{s}=7\,\TeV$, and continued operation until the end of 2012. This period is known
+collectively as \ac{LHC} Run 1. After this the 
+two-year \ac{LS1} was used to upgrade the \ac{LHC} and the detectors for collisions at a
+$\sqrt{s}$ of $13\text{--}14\,\TeV$. In April 2015 the \ac{LHC} restarted with collisions at 
+$\sqrt{s}=13\,\TeV$, marking the start of Run 2. The integrated luminosity delivered to the \ac{CMS} experiment, separated by running year, is shown in
 figure \ref{fig:CMSLHC_intlumi}.
@@
 \caption[Cumulative integrated luminosity delivered to CMS
-for p--p collisions at the LHC, separated by running year.]{Cumulative integrated luminosity delivered to \ac{CMS} for p--p collisions at the \ac{LHC}, separated
+for p-p collisions at the LHC, separated by running year.]{Cumulative integrated luminosity delivered to \ac{CMS} for p-p collisions at the \ac{LHC}, separated
 by running year \cite{cms-lumi-public}.}
@@
 
-The data-taking efficiency of CMS is not 100\%, for example part of the detector might be
-switched off for part of the time collisions are ongoing. In 2012, the data-taking 
-efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.4 \%
-
-From all of the data that is recorded, only a subset is used for analysis. Data is 
-certified as good for use in analyses if it is known that all relevant subdetectors
+The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
+switched off while collisions are ongoing. In 2012 the data-taking 
+efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.4\%
+From all of the data that is recorded only a subset is used for analysis. Data is 
+certified as good for use in analyses if it is known that all relevant sub-detectors
 were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
-meaning all subdetectors were working well for a dataset corresponding to 19.7 fb$^{-1}$.
+meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
 Due to cryogenic issues the certification efficiency with the magnet operating
-at 3.8 Tesla was 60.4 \% in 2015, leading to 2.3 fb$^{-1}$ of 
-analysable data for which the full detector was operational. An additional 0.6 fb$^{-1}$
-was taken with the \ac{CMS} magnet switched off. For the full 2016 p--p running period
-the certification efficiency was 95.4\%, resulting in 36.26 fb$^{-1}$ of data marked good
+at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
+analysable data for which the full detector was operational. An additional $0.6\,\invfb$
+was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
+the certification efficiency was 95.4\%, resulting in $36.3\,\invfb$ of data marked good %FIXME: certification efficiency
 for use in analyses.
 
-The \ac{LHC} was designed for proton-proton collisions with a nominal
-peak luminosity of $10^{32}$cm$^{-2}$s$^{-1}$. In 2012 peak
-luminosities of $7.7\cdot10^{33}$cm$^{-2}$s$^{-1}$ were reached, with the peak luminosity in
-2015 being $5.1\cdot10^{33}$cm$^{-2}$s$^{-1}$. Since July 2016
+The \ac{LHC} was designed for p-p collisions with a nominal
+peak luminosity of $10^{34}\,\lumiunits$. In 2012 peak
+luminosities of $7.7\times 10^{33}\,\lumiunits$ were reached, with the peak luminosity in
+2015 being $5.1\times 10^{33}\,\lumiunits$. Since July 2016
 the \ac{LHC} has been operating at instantaneous luminosities upwards of the 
-design luminosity, with peak luminosities of $1.5\cdot10^{32}$cm$^{-2}$s$^{-1}$ reached
+design luminosity, with peak luminosities of $1.5\times10^{34}\,\lumiunits$ reached
 in October 2016 \cite{cms-lumi-public}.
 
-Due to the high operating luminosity, multiple proton-proton collisions per 
-bunch crossing are likely to occur. Additional interactions on top of events of 
-interest are referred to as pile-up. The average number of interactions
+Multiple p-p collisions per bunch crossing are likely to occur due to the high
+operating luminosity. 
+Additional interactions on top of events of 
+interest are referred to as pileup. The average number of interactions %FIXME: make clear that they are unintersting?
 per bunch crossing was 21 in 2012\cite{cms-lumi-public}. The average number of
@@
 To meet the demands of the \ac{LHC} physics programme, the
- \ac{CMS} detector was designed to perform very well in searches
-for physics at the TeV scale and to be able to 
+ \ac{CMS} detector was designed to have a high sensitivity in searches 
+for new physics at the $\TeV$ scale and to be able to 
 function in the challenging high-luminosity environment.
-The detector is 21.6 m long, 14.6 m in diameter, and weighs
-12500 tonnes \cite{cms-jinst}. It consists of several subdetectors, as illustrated
+The detector is $21.6\,\metre$ long, $14.6\,\metre$ in diameter, and weighs
+$12\,500$ tonnes \cite{cms-jinst}. It consists of several sub-detectors, arranged parallel
+to the beam axis in the barrel region and perpendicular to it in the endcaps, as illustrated
 in figure \ref{fig:cms_detector}.
@@
 \includegraphics[width=0.8\textwidth]{./Detector/Plots/cms.png}
-\caption[A cutaway view of the CMS detector, indicating the different sub-parts of the detector.]{A cutaway view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
-different sub-parts of the detector.}
+\caption[A cutaway view of the CMS detector, indicating the different sub-components of the detector.]{A cutaway view of the \ac{CMS} detector \cite{cms-jinst}, indicating the
+different sub-components of the detector.}
 \label{fig:cms_detector}
@@
 
-The silicon tracker, a cylinder \mbox{5.8 m} in length and \mbox{2.6} m in
+The silicon tracker, a cylinder $5.8\,\metre$ in length and $2.6\,\metre$ in
 diameter, surrounds the interaction point. The tracker is 
@@
 by the brass scintillator \ac{HCAL}.
-
 The tracking and calorimeter systems are surrounded by a superconducting
-solenoid, \mbox{13 m} long, \mbox{6 m} in diameter and operating at 3.8 Tesla.
+solenoid, $13\,\metre$ long, $6\,\metre$ in diameter and operating at $3.8\,\tesla$.
 Charged particles are bent in this magnetic field, allowing for precise 
@@
 
-For the measurement of physical quantities, \ac{CMS} uses a coordinate
+For the measurement of physical quantities \ac{CMS} uses a coordinate
 system with the origin centred at the nominal collision point
-inside the experiment. The y-axis points vertically upward, the x-axis
-points radially inward toward the centre of the \ac{LHC} ring. The z-axis
+inside the experiment. The $y$ axis points vertically upward, the $x$ axis
+points radially inward toward the centre of the \ac{LHC} ring. The $z$ axis
 points along the beam direction. As such the transverse momentum and energy, 
-\pT~and \ET~are measured from the x- and y- components of the momentum and energy.
-The azimuthal angle $\phi$ is measured in the x-y plane with respect to the x-axis, 
-the polar angle $\theta$ measured with respect to the z-axis. A coordinate
-more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$.
-Distances in the $\eta-\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.
+\pT~and \ET, are defined by the $x$- and $y$-components of the momentum and energy.
+The azimuthal angle $\phi$ is measured in the $x$-$y$ plane with respect to the $x$ axis  
+and the polar angle $\theta$ is measured with respect to the $z$ axis. A coordinate
+more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$.%Look up: differences in eta are lorentz-invariant
+Distances in the $\eta$-$\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.
 
@@
 \label{sec:CMSLHC_CMS_tracker}
-The tracker \cite{cms-jinst} is the subdetector closest to the interaction point. It
+The tracker \cite{cms-jinst} is the sub-detector closest to the interaction point. It
 is used for accurate reconstruction of charged particle trajectories and 
-the precise reconstruction of primary and secondary vertices, the latter being important for
-the identification of heavy-flavour particles. This means a small impact parameter
+the precise reconstruction of primary (collision) and secondary vertices, the latter being important for
+the identification of the in-flight decays of heavy-flavour particles. This means a small impact parameter
 resolution needs to be achieved, for which a highly granular system is required. 
 Due to the large number of particles emerging from 
-each collision, an average of 1000 per bunch crossing (every 25 ns) at LHC design operation, the 
+each collision, on average 1000 per bunch crossing at design operation, the 
 system also needs to be able to respond quickly in order to reconstruct trajectories accurately.
@@
 
-In a silicon tracking system, the positions of particles are recorded
-due to the creation of drifting electron-hole pairs.
-When a charged particle passes through the silicon, an electron-hole pair
+In a silicon tracking system the positions of particles are recorded
+via the creation of drifting electron-hole pairs.
+When a charged particle passes through the silicon an electron-hole pair
 is created, which drift under an applied electric field and produce a current
@@
 the locations of these components, is given in figure \ref{fig:CMS_tracker}.
-Nearest the interaction point is the pixel detector, made
-of 66 million silicon pixels, each 100 $\mu$m $\times$ 150 $\mu$m in size.
-The choice of this pixel size is driven by the ability to achieve the desired spatial resolution,
-which is 15-20 $\mu$m in the $r-\phi$ and $z$ directions in this case. Such a
+The pixel detector is the closest to the interaction point.
+It is composed
+of 66 million silicon pixels, each $100\,\micron\,\times\,150\,\micron$ in size.
+The choice of this pixel size is driven by the desired spatial resolution,
+which is $15$--$20\,\micron$ in the $r$-$\phi$ and $z$~directions. Such a
 precise resolution allows for 3D vertex reconstruction. The pixel
-detector consists of 3 layers of pixels in the barrel region, with 2 pixel disks 
+detector consists of three layers of pixels in the barrel region, with two pixel disks 
 placed in the endcap region at either side. The barrel layers sit at radii of
-4.4, 7.3 and 10.2 cm and extend out to $z=\pm 26.5$ cm. The disks are placed
-at $z=\pm 34.5$ cm and $z=\pm 46.5$ cm. With this layout the pixel tracker can
-provide three precies position measurements along each charged particle trajectory.
+$4.4$, $7.3$ and $10.2\,\cm$ and extend out to $z=\pm\,26.5\,\cm$. The disks are placed
+at $z=\pm\,34.5\,\cm$ and $z=\pm\,46.5\cm$. With this layout the pixel tracker can
+provide three precise position measurements along each charged particle trajectory.
 
@@
 \caption[Schematic of the CMS tracker in the 
-r-z plane, indicating the positions of the pixel and
-strip detectors.]{Schematic of the CMS tracker in the r-z plane, indicating the
+$r$-$z$ plane, indicating the positions of the pixel and
+strip detectors.]{Schematic of the CMS tracker in the $r$-$z$ plane, indicating the
 positions of the pixel and strip detectors \cite{cms-jinst}. Each line 
-on the plot represents a detector module.}
+on the figure represents a detector module.}
 \label{fig:CMS_tracker}
@@
 Around the pixel detector the tracking system is made up of a silicon
-strip detector divided into four subsystems. The first part of the
+strip detector divided into four sub-systems. The first part of the
 silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
 silicon strip detectors in the barrel plus three disks at both ends. These two systems
-extend out towards a radius of 55 cm. The barrel layers and disks each consist
-of silicon strips which are 10 cm long, $80-141~\mu$m wide and $320~\mu$m thick. The \ac{TIB} and \ac{TID}
-provide four measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu$m.
+extend out up to a radius of $55\,\cm$. The barrel layers and disks each consist
+of silicon strips which are $10\,\cm$ long, $80$--$141\,\micron$ wide and $320\,\micron$ thick. The \ac{TIB} and \ac{TID}
+provide four measurements of the $r$-$\phi$ position with a resolution of $23$--$35\,\micron$. 
 The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of six layers of silicon strip sensors extending
-up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500~$\mu$m thick, around 25 cm long and 122-183 $\mu$m 
-wide and this subdetector provides 6 measurements of $r$ and $\phi$, with a resolution
-of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
-consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from \mbox{320-500 $\mu$m} and the the strip width ranges from $97-184 \mu$m.
+up to an outer radius of $116\,\cm$ and up to $z=\pm\,118\,\cm$. The strips in the \ac{TOB} are $500\,\micron$ thick, 
+around $25\,\cm$ long and $122$--$183\,\micron$ 
+wide providing 6 measurements of $r$ and $\phi$, with a resolution
+of $35$--$53\,\micron$. Beyond the $z$ range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
+consisting of nine disks of strips. In the \ac{TEC} the strip thickness ranges from $320$--$500\,\micron$ and 
+the the strip width ranges from $97$--$184\,\micron$. %FIXME: look up why
 This part of the system provides up to nine $\phi$ measurements.
@@
 Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
-of 100 mrad, in order to provide measurements of the $z-$ coordinate in the barrel. This is achieved with a resolution of 230-530 $\mu$m.
+of $100\,$mrad, in order to provide measurements of the $z$ coordinate in the barrel. This is achieved with a resolution of $230$--$530\,\micron$.
 
 The pixel tracker will be upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade is needed to
-maintain the performance of the tracker as the pile-up increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?
+maintain the performance of the tracker as the pileup increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?
 
@@
 The \ac{ECAL} \cite{cms-jinst} is a hermetic homogeneous calorimeter
-made of nearly 76000 lead tungstate (PbWO$_4$) crystals. It has very
+made of nearly $76\,000$ lead tungstate (PbWO$_4$) crystals. It has very
 good energy resolution, is highly granular and has a fast response, all qualities 
-which are needed to be able to detect $H\rightarrow \gamma\gamma$ decays.
+which are needed to be able to detect $\PHiggslight\rightarrow \Pphoton\Pphoton$ decays.
 
@@
 short radiation length, small Moli\`ere radius and short scintillation
-decay time. With a radiation length of 0.89 cm and a Moli\`ere radius of 2.2 cm,
+decay time. With a radiation length of $0.89\,\cm$ and a Moli\`ere radius of $2.2\,\cm$,
 lead tungstate crystals allow for the construction of a compact, highly 
-granular \ac{ECAL}. The compactness of the \ac{ECAL} is required  
-to fit inside the bore of the magnet. 
-As 80\% of the light from the crystals is emitted within 25 ns, that is
-within the time between two bunch crossings at design operation of the \ac{LHC},
-the lead tungstate crystals satisfy the requirements imposed by the \ac{LHC} operating
-parameters.
-
+granular \ac{ECAL}. The \ac{ECAL} is required to be compact 
+for it to fit inside the bore of the magnet. 
+The lead tungstate crystals satisfy the requirements imposed by the \ac{LHC} 
+operating parameters as 80\% of the light from the crystals is emitted within $25\,\ns$,
+which is the time between two bunch crossings at design operation.
 %Moliere radius: characteristic constant of a material giving scale of transverse dimenstion
@@
 
-When a high energy electron or photon enters a crystal, it starts a
+When a high energy electron or photon enters a crystal it starts a
 shower producing a cascade of lower energy particles. Electrons lose
@@
 crystals, which then emit scintillation light that is converted to a current by the 
-photodetectors. To record the light of the crystals, amplifying photodetectors need
+photodetectors. To record the light of the crystals amplifying photodetectors need
 to be used, with avalanche photodiodes used in the barrel region, and vacuum phototriodes employed
@@
 Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
-the subsystems it is made up of. The \ac{EB} 
+the sub-systems it is made up of. The \ac{EB} 
 covers the pseudorapidity range up to $|\eta|<1.479$, with
-crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
+crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \ac{EE}
 provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
-Each endcap is divided into two halves. In front of the endcaps 
-the preshower detectors, covering $1.653<|\eta|<2.6$ are sampling
-calorimeters whose main use is to identify neutral pions, decaying to two photons, 
-in the endcaps. Additionally
-the preshower detectors aid the identification of electrons and improve the resolution
-of position determination. Each of the two preshower detectors consist
+Each endcap is divided into two halves. The preshower detectors, 
+which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
+The main use of the preshower detectors is to identifiy neutral pions decaying to two photons in the 
+endcaps. Additionally,
+they aid in the identification of electrons and improve the resolution
+of the position determination. Each of the two preshower detectors consists
 of two layers of lead radiators to initiate the shower, with silicon sensors
 placed after each layer of radiators to measure the deposited energy. The 
-total thickness of the preshower is 3 radiation lengths.
+total thickness of the preshower is three radiation lengths.
 
@@
 
-To preserve the energy resolution, the crystals and
-photodetectors need to be kept stable within $\pm 0.05^{\circ}$C
+To preserve the energy resolution the crystals and
+photodetectors need to be kept stable within $18\pm 0.05^{\circ}$C
 as the number of scintillation photons emitted by the crystals,
 and the amplification of the photodetectors, are temperature dependent.
-The nominal operating temperature, $18^{\circ}$C, is ensured by 
-supplying the detector with water at this temperature.
+This nominal operating temperature, is ensured by 
+supplying the detector with water at the same temperature.
 
@@
 The stochastic term arises from fluctuations in lateral shower containment and 
-fluctuations in the scintillation yield, the noise term due to noise from the electronics
+fluctuations in the scintillation yield, the noise term is due to noise from the electronics
 and additional particles in the event, and the constant term comes
@@
 test-beam, without a magnetic field or material in front of the \ac{ECAL}, as 
-$S = 0.028$ GeV$^{\frac{1}{2}}$, $N = 0.12$ GeV and $C= 0.003$.
+$S = 0.028\,\GeV^{\frac{1}{2}}$, $N = 0.12\,\GeV$ and $C= 0.003$.
 %S = 2.83 %pm 0.03%, C = 0.26% pm 0.04%
@@
 The \ac{ECAL} is surrounded by the \ac{HCAL} \cite{cms-jinst}, which is needed for the
-measurement of the energies of strongly interacting particles and \MET. As
-the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
-starts at a radius of 2.95 m, space for the \ac{HCAL} inside the magnet
+measurement of the energies of strongly interacting particles. As
+the \ac{ECAL} extends out to a radius of $1.77\,\metre$ and the magnet coil
+starts at a radius of $2.95\,\metre$, space for the \ac{HCAL} inside the magnet
 coil is limited. The \ac{HCAL} design takes
@@
 illustration of a quadrant of the
-\ac{HCAL}, indicating the positions of the subsystems, is shown
+\ac{HCAL}, indicating the positions of the sub-systems, is shown
 in figure \ref{fig:CMS_HCAL}.
@@
 \caption[Illustration of a quadrant of the HCAL, showing the different
-subsystems of the detector.]{Illustration of a quadrant of the \ac{HCAL}, showing the different
-subsystems of the detector \cite{cms-jinst}.}
+sub-systems of the detector.]{Illustration of a quadrant of the \ac{HCAL}, showing the different
+sub-systems of the detector \cite{cms-jinst}.}
 \label{fig:CMS_HCAL}
@@
 
-In the barrel region the \ac{HB}, limited in radius by the magnet coil, provides
+In the barrel region the \ac{HB} provides
 coverage up to $|\eta|<1.3$. Beyond this $\eta$ range the \ac{HE} covers
@@
 %Nuclear interaction length is the mean distance travelled by a hadronic particle before undergoing an inelastic nuclear interaction.
-of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
-are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
+of $16.42\,\cm$ and the fact that it is non-magnetic. The tiles of scintillator 
+are $0.087 \times 0.087$ in $\eta$-$\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta$-$\phi$
 beyond this range. The light from each tile is collected with a wavelength-shifting fibre, 
@@
 
-In the barrel, the \ac{HCAL}
+In the barrel the \ac{HCAL}
 has a thickness of between 5.82 and 10.6 interaction lengths, which is not 
-sufficient to identify for example late-starting showers. The \ac{HO}, sitting
+sufficient to identify, for example, late-starting showers. The \ac{HO}, sitting
 outside of the magnet and using the coil as an additional absorber, extends the 
 thickness to at least 11.8 interaction lengths. 
-Like in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
-map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
-to a hybrid photodiode via wavelength-shifting fibres.
+As in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
+map on the granularity of the tiles in the \ac{HB}, and are read out via the same mechanism. %by feeding the light
+%to a hybrid photodiode via wavelength-shifting fibres.
 %WTF: wavelength-shifting fibres
@@
 The \ac{HF}, providing coverage in the very forward region, is 
-subjected to large radiation doses, requiring an extremely
-radiation-hard active material. For this reason quartz
+subjected to large radiation doses. This means an extremely radiation-hard
+active material is needed. 
+For this reason quartz
 fibres are used. These fibres are embedded
@@
 where $S$ is the stochastic term, found to be 94.3\% %pm 1.2
-and $C$ is the constant term, measured to be 8.4\% %pm 1.0
+and $C$ is the constant term, measured to be 8.4\%. %pm 1.0
 
 %UPGRADE
-During \ac{LS1}, the photomultiplier tubes of the \ac{HF} were upgraded. The photomultiplier- and
+During \ac{LS1} the photomultiplier tubes of the \ac{HF} were upgraded. The photomultiplier tubes and
 read-out systems of other parts of the \ac{HCAL} will be upgraded in stages over the
@@
 \label{sec:CMSLHC_CMS_muons}
-Precise muon identification is one of the requirements of the \ac{CMS} 
-experiment. Good muon identification efficiency and precise muon momentum 
+Accurate muon identification is one of the requirements of the \ac{CMS} 
+experiment. High muon identification efficiency and precise muon momentum 
 resolution are key to the success of the experiment, as muons are
-very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays. In addition to that,
+very important for the detection of $\PHiggslight\rightarrow \PZ\PZ \rightarrow 4\ell$ decays. In addition to that,
 muons appear in the final states of many of the \ac{BSM} signatures the experiment is searching for.
 
-The \ac{CMS} muon system \cite{cms-jinst} is designed of three different subsystems which
-are all necessary to ensure the identification requirements can be met. It is located
+The \ac{CMS} muon system \cite{cms-jinst} is composed of three sub-systems which
+are all necessary to ensure the identification requirements can be met. The muon system is located
 outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
-In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
+In the barrel of the detector the \ac{DTs} provide coverage for $|\eta|<1.2$, with
 the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
-regions as both \ac{DT} and \ac{CSCs}, are used as a dedicated triggering system.
+regions as both the \ac{DTs} and \ac{CSCs}, are used as a dedicated triggering system.
 
-A cross-section of one quadrant of the detector, indicating
-the positions of the \ac{DT}, \ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
+A cross section of one quadrant of the detector, indicating
+the positions of the \ac{DTs}, \ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
 The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1} \cite{cms-muon-upgrade}, providing
@@
 \includegraphics[width=0.8\textwidth]{./Detector/Plots/MuonSystemUpgrade.png}
-\caption[Cross-section of one quadrant of the CMS detector,
-indicating the positions of the different muon system components.]{Cross-section of one quadrant of the CMS detector, indicating
+\caption[Cross section of one quadrant of the CMS detector,
+indicating the positions of the different muon system components.]{Cross section of one quadrant of the CMS detector, indicating
 the positions of the different muon system components \cite{cms-muon-upgrade}. The 
-fourth muon endcap stations were extended during \ac{LS1}, in Run 1 only the lower
+fourth muon endcap stations were extended during \ac{LS1}; in Run 1 only the lower
 part existed.}
@@
 \end{figure}
-The \ac{DT} consists of layers of drift cells which have a cross-section of $4.2 \times 1.3$ cm$^2$ and
-are 2.4 m long. The cells are filled with a mixture of %85\% 
-argon and carbon dioxide gas.
+
+The \ac{DTs} consists of layers of drift cells which have a cross section of $4.2\,\cm \times 1.3\,\cm$ and
+are $2.4\,\metre$ long. The cells are filled with a mixture of %85\% 
+argon gas and carbon dioxide gas.
 Muons passing through the chamber ionise the gas, freeing electrons
 which drift towards the anode wire running along the centre of the tube-shaped cell. 
-This gives rise to an electric signal. There are 4 \ac{DT} stations in each wedge of 
+This gives rise to an electric signal. There are four drift tube stations in each wedge of 
 the detector, each in turn consisting of 8 to 12 layers of drift tubes. Some of
@@
 There are also layers oriented orthogonal to the beam line, which give a measurement
-of the z coordinate. Measurements of the spatial resolution were made
-during proton--proton running of the \ac{LHC} in 2010.
-The spatial resolution of the \ac{DT} is 80-120 $\mu$m per chamber for
+of the $z$ coordinate. Measurements of the spatial resolution were made
+during p-p running in 2010.
+The spatial resolution of the \ac{DTs} is $80$--$120\,\micron$ per chamber for
 measurements in the $\phi$ direction, while the resolution of the $z$ measurement
-is 130-400 $\mu$m\cite{cms-muon-7tev}. %Drift lines distorted by magnetic field parallel to the wires
+is $130$--$400\,\micron$ \cite{cms-muon-7tev}. %Drift lines distorted by magnetic field parallel to the wires
 
 In the endcaps, where both the muon rate and the radiation levels are higher, the \ac{CSCs} provide
-measurements of the muon track. These detectors are radiation-hard,
+measurements of the muon track. These detectors are radiation hard,
 and have a fast response and fine segmentation.
@@
 multi-wire proportional chamber %WTF
-with 6 gaseous chambers bounded by cathode planes, with
-sensitive strips placed on these plates in the
-radial direction, to measure the muon coordinate in the  $r-\phi$ plane.
-Anode wires in between the cathode planes
+with six gaseous chambers bounded by cathode plates. Sensitive
+strips are placed on these plates in the 
+radial direction, to measure the muon coordinate in the  $r$--$\phi$ plane.
+Anode wires between the cathode planes
 run along the $\phi$ direction and provide a measurement of
-$\eta$. The resolution of the $r-\phi$ measurement is 40-120 $\mu$m \cite{cms-muon-7tev}.
+$\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.
 
-In addition to the \ac{DT} and \ac{CSCs}, the \ac{RPCs} provide coverage
+In addition to the \ac{DTs} and \ac{CSCs}, the \ac{RPCs} provide coverage
 for $|\eta|<1.6$. These are made up of parallel plates, forming the anode and cathode,
@@
 beam axis. The position resolution of the \ac{RPCs} is poorer than
-that of the \ac{DT} and \ac{CSCs}, but their time response is very fast. As
-a result of this the \ac{RPCs} can be used as an independent muon trigger
+that of the \ac{DTs} and \ac{CSCs}, but their time response is very fast. As
+a result of this the \ac{RPCs} are used as an independent muon trigger
 which can correctly identify the beam crossing from which the muon
@@
 
-To obtain precise muon momentum resolution, information from 
+To obtain precise muon momentum resolution information from 
 the tracker hits has to be combined with measurements in the
 muon stations. The momentum resolution of the muon system
-alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
-between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. %ADD FORMULA
+alone is 9\% for muons with \pT~up to $200\,\GeV$, and varies with $\eta$ 
+between $15$--$40\%$ for muons with \pT~of $1\,\TeV$ \cite{cms-jinst}. %ADD FORMULA
 
@@
 When the \ac{LHC} is operating under design conditions, protons are collided at a rate
-of 40 MHz. This rate is too high for the \ac{DAQ} system to read out every event. In
+of $40\,$MHz. This rate is too high for the \ac{DAQ} system to read out every event. In
 addition this high collision rate produces such a large number of events that it would
-not be feasible to write every single event, with sizes of around 1 MB, to tape. A trigger
-system is therefore used to select events of interest for study, which reduces the rate
+not be feasible to write every single event, with a size of around 1 MB, to tape. Therefore, a trigger
+system is used to select events of interest, which reduces the rate
 at which events are stored to  $\mathcal{O}(1 \text{ kHz})$.
 
-The trigger system consists of two stages: the \ac{L1} trigger, which only makes use of
-front-end electronics 
-and reduces the event rate from 40 MHz to around 100 kHz, and the
-\ac{HLT}, which runs on a computer farm with around 13000 CPU cores \cite{cms-trigger}.
+The trigger system consists of two stages: the \ac{L1} trigger and the \ac{HLT}. which only makes use of
+The \ac{L1} trigger only makes use of front-end electronics and reduces the event rate 
+from $40\,$MHz to around $100\,$kHz. The \ac{HLT} 
+runs on a computer farm with around $13\,000$ CPU cores \cite{cms-trigger}.
 During \ac{LS1} and the year-end technical stop at the end of 2015 the \ac{L1} trigger was
-replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides amongst other 
-things improved object isolation, hadronic tau identification, muon \pT~resolution and
+replaced by a completely upgraded system \cite{cms-trigger-tdr}, which provides, amongst other 
+things, improved object isolation, hadronic tau identification, muon \pT~resolution and
 jet finding with respect to the system used during Run 1.
@@
 which are fed to the first layer of the trigger, where it makes use of a time-multiplexed system. 
-The first trigger layer maps onto columns of the detector, receiving data from many bunch crossings. These data are passed
+The first trigger layer maps onto slices of the detector, receiving data from many bunch crossings. These data are passed
 on to the second layer of the trigger in a way that bundles data from a single bunch crossing, but
-different columns of the detector, to be processed on one node in the second layer of the
+different slices of the detector, to be processed on one node in the second layer of the
 trigger. In this step basic object identification is performed based on the energy
@@
 The trigger employed during Run 1, and the first year of Run 2, did not use time-multiplexing. Instead, 
-information from different regions of the detector were processed independently.
+information from different regions of the detector was processed independently.
+
 Hits in the muon chambers are read out and passed to the track finder layer 
-of the muon trigger, which combines information from the CSC, \ac{DT}
-and RPC systems in regions of $\eta-\phi$.
+of the muon trigger, which combines information from the CSC, DT
+and RPC systems in regions of $\eta$-$\phi$.
 In further layers of the muon trigger the information from different
@@
 to make a decision on whether the event should be sent to the \ac{HLT} or whether
-it should be discarded. A decision has to be made within 3.2 $\mu$s, the maximum time during
+it should be discarded. A decision has to be made within $3.2\,\micro\second$, the maximum time during
 which data can be stored in the \ac{L1} trigger before being lost.
@@
 During the 2012 run of the \ac{LHC} the \ac{HLT} operated with an output
-capacity of around 1 kHz, for Run 2 this has been increased. In August 2016, 
-the \ac{HLT} output rate was 1.2 kHz for immediate data processing, with
-an additional 0.6 kHz parked to be reconstructed and analysed when 
-more processing power is available\cite{CMS-PAS-HIG-16-037}. %ie at the end of run 2
+capacity of around $1\,$kHz. For Run 2 this has been increased. In August 2016 
+the \ac{HLT} output rate was $1.2\,$kHz for immediate data processing, with
+an additional $0.6\,$kHz saved as raw data to be reconstructed and analysed when 
+more processing power is available \cite{CMS-PAS-HIG-16-037}. %ie at the end of run 2
 
@@
 of large sets of simulated events. 
-To make these large amounts of data easily available for analysis, 
+To make these large amounts of data easily accessible for analysis, 
 \ac{CMS} and the other \ac{LHC} experiments make use of the \ac{WLCG} \cite{lhc-wlcg}. 

### 2017-02-12 Objects/Objects.tex
Edit of first section of object reconstruction chapter

@@
-\chapter{Object Reconstruction}
+\chapter{Object reconstruction}
 \label{chap:objects}
 
-In this chapter the reconstruction of the physics objects necessary to be able to perform searches with \Pgt leptons
-in the final state in \ac{CMS} will be discussed. Section \ref{sec:objects_pv} details the algorithms
+In this chapter the reconstruction of the physics objects necessary for performing searches with taus 
+in the final state with \ac{CMS} will be discussed. Section \ref{sec:objects_pv} details the algorithms
 used to reconstruct charged particle tracks in the inner tracker, with section \ref{sec:objects_ele}
@@
 Section \ref{sec:objects_pf}
-describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
+describes the \ac{PF} algorithm, which uses information from all sub-detectors in \ac{CMS} to reconstruct
 all stable particles. \ac{PF} is of particular importance for the reconstruction of jets, missing transverse
-energy and hadronic taus as detailed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
+energy and hadronically decaying taus as detailed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
 respectively.
@@
 \label{sec:objects_pv}
-To reconstruct the trajectories of charged particles - and therefore
-their momenta and positions - from the hits they leave in the 
+To reconstruct the trajectories of charged particles, and therefore
+their momenta and positions, from the hits they leave in the 
 inner tracker the
@@
 First, initial estimates of the parameters of the trajectory are given by track seeds, 
-made out of the hits found in 2 or 3 layers of the inner tracker. These track seeds
+made out of the hits found in two or three layers of the inner tracker. These track seeds
 are extrapolated using a \ac{KF} \cite{trk-kf}, which extrapolates the seeding
@@
 These four steps are repeated six times. After each iteration
-the hits associated with reconstructed tracks are removed, and the settings
-of the algorithm updated, so as to be able to reconstruct as many
-tracks as possible. The tracking efficiency for muons and pions was measured in p--p
-collisions at $\sqrt{s} = 7$ TeV and found to be $ > 98.5\%$ for tracks
-with \pT $ > 500 $ MeV and $ > 99 \%$ for tracks with \pT $ > 2 $ GeV \cite{cms-trk-7tev}.
+the hits associated with reconstructed tracks are removed and the settings
+of the algorithm updated, in order to reconstruct as many
+tracks as possible. The tracking efficiency for muons and pions was measured in p-p
+collisions at $\sqrt{s} = 7\,\TeV$ and found to be $ > 98.5\%$ for tracks
+with \pT $ > 500\,\MeV$ and $ > 99 \%$ for tracks with \pT $ > 2\,\GeV$ \cite{cms-trk-7tev}.
 %The tracking software at CMS is commonly referred to as the Combinatorial Track Finder (CTF), which is an adaptation of the combinatorial Kalman filter [29–31], which in turn is an extension of the Kalman filter [32] to allow pattern recognition and track fitting to occur in the same frame- work.
@@
 Primary vertices are reconstructed by clustering
-tracks that appear to have originated from the same vertex, then fitting 
+tracks that are compatible with have originated from the same vertex, then fitting 
 these tracks for the position of the vertex. The clustering 
@@
 vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
-vertex position. The analyses presented in chapter \ref{chap:mssm} take the primary
-vertex of the hard scatter as the reconstructed vertex for which the scalar sum of the \pT s of
-the associated tracks is largest. This differs from the analysis presented in chapter \ref{chap:hhh},
-where requirements on the quality of the vertex
-fit and the distance between the vertex and the nominal interaction point 
-were additionally made.
+vertex position. The analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} take the primary
+vertex of the hard scatter to be the reconstructed vertex with the largest scalar \pT~sum of the associated
+tracks. %which the scalar sum of the \pT s of
+%the associated tracks is largest. %This differs from the analysis presented in chapter \ref{chap:hhh},
+%where requirements on the quality of the vertex
+%fit and the distance between the vertex and the nominal interaction point 
+%were additionally made.
  %By doing this both the best estimate
@@
 
-The resolution of the x-- and z--coordinates of the primary vertex were measured in
-collisions at $\sqrt{s}=13$ TeV and depend strongly on the number of tracks
+The resolutions of the $x$ and $z$ coordinates of the primary vertex were measured in
+collisions at $\sqrt{s}=13\,\TeV$ and depend strongly on the number of tracks
 associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
@@
 \end{center}
-\caption[Resolution of the x- and z- coordinates of reconstructed
-primary vertices as a function of the scalar sum of the \pT s of the associated
-tracks.]{Resolution of the x-- (a) and z--coordinate  (b)
+\caption[Resolution of the $x$ and $z$ coordinates of reconstructed
+primary vertices as a function of the scalar \pT~sum of the associated
+tracks.]{Resolution of (a) the $x$ coordinate and (b) the $z$ coordinate 
 of reconstructed primary vertices
-as a function of the scalar sum of the \pT s of the associated tracks, 
+as a function of the scalar \pT~sum of the associated tracks, 
 measured in 2015 (blue triangles) and 2016 (red squares).
 The resolution improves
-with higher scalar sum of the \pT s of the associated tracks, which corresponds to larger numbers of tracks \cite{cms-trk-dp}.}
+with higher scalar \pT~sum of the associated tracks, which corresponds to larger numbers of tracks \cite{cms-trk-dp}.}
 \label{fig:objects_tracks_pvres}

### 2017-02-16 MSSM/MSSM.tex
Committing a few changes before continuing edit

@@
 by carefully considering the differences between the two analyses
-and the conditions under which they were perofrmed.
+and the conditions under which they were performed.
 

### 2017-02-16 Objects/Objects.tex
Committing a few changes before continuing edit
Edit of objects section

@@
 A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
-that will be described in section \ref{sec:objects_pf}.
-Depending on the thickness of the intervening material, electrons lose up to 86 \% of their energy on
-average due to bremsstrahlung before reaching the \ac{ECAL}.
+that will be described in section \ref{sec:objects_pf}.%FIXME don't say this, they're more similar now
+Depending on the thickness of the intervening material, electrons lose up to an average of 86\% of their energy 
+due to bremsstrahlung before reaching the \ac{ECAL}.
 To accurately reconstruct the energy of the electron it is
@@
 %not perform optimally. 
-A dedicated tracking algorithm, with better performance than the \ac{CTF} for this 
-particular case, is therefore used.
-For high--\pT~electrons, the best efficiency is reached
-by the use of an \ac{ECAL}-based track seeding algorithm \cite{cms-elereco-run1}
-which extrapolates the position and energy of the supercluster to the first
-layers of the tracker to determine the rough area where the tracker seeds should be.
+Therefore a dedicated tracking algorithm is used, with better performance than the \ac{CTF} for this 
+particular case.
+For high-\pT~electrons the best efficiency is reached
+by the use of an \ac{ECAL}-based track seeding algorithm \cite{cms-elereco-run1}.
+This algorithm extrapolates the position and energy of the supercluster to the first
+layers of the tracker to determine the approximate area where the tracker seeds should be.
 Once the tracker seeds have been found they are extrapolated
 and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the \ac{KF}, which 
-approximates the non--Gaussian energy loss in each layer by a combination of 
+approximates the non-Gaussian energy loss in each layer by a combination of 
 Gaussian distributions rather than the single Gaussian used in the \ac{KF}.
@@
 
-For a particle to be identified as an electron, it 
-has to be reconstructed as an electron by the \ac{PF} algorithm, 
+For a particle to be identified as an electron it 
+must also be reconstructed as an electron by the \ac{PF} algorithm, 
 and must in addition pass more advanced identification criteria based on some of the variables used in the
-standalone electron reconstruction, which provide separation power from backgrounds
+standalone electron reconstruction. This provides separation power from backgrounds
 such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
-decays. Both a cut--based and a BDT--based algorithm are available. For the selection of electrons in 
-the analyses presented in later chapters the BDT--based algorithm is used, 
+decays. Both a cut-based and a BDT-based algorithm are available. %FIXME define BDT
+For the selection of electrons in 
+the analyses presented in later chapters the BDT-based algorithm is used, 
 with exceptions for the loose identification criteria required for vetoing electrons. 
-The variables used to train this BDT include:
+The variables used in this BDT include:%FIXME full stop usage?!
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy--weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
+\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
 \item Track quality variables.
 \item Distances in $\eta$ and $\phi$ between the supercluster and the associated track.
-\item Energy ratios and energy--momentum ratios in the region of the supercluster, including
+\item Energy ratios and energy-momentum ratios in the region of the supercluster, including
 $1/E_{\text{SC}} - 1/p_{\Pe}$, where $E_{\text{SC}}$ is the energy in the supercluster and $p_{\Pe}$ the momentum of the electron track (illustrated in figure \ref{fig:ele_id_vars}b).
@@
 \caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
-and misidentified electrons at 8 TeV, for data and MC]{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
+and misidentified electrons at 8 TeV, for data and MC]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
 misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
@@
 from misidentified electrons, but do not eliminate them completely. If jets are
-misidentified as electrons, or an electron resulting from a heavy--flavour 
+misidentified as electrons, or an electron resulting from a heavy-flavour 
 decay is identified, the electron is not isolated. Therefore requirements
@@
 \end{equation}
-where the \pT~and \ET~sums are taken within a cone in $\eta - \phi$ around the direction
-of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
-The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged \ac{PF} 
-hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
-the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
-run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
-The contribution from neutral particles due to pile--up needs to be subtracted from
-this term; it is estimated as the sum of charged hadronic \pT~for hadrons not associated
+where the \pT~and \ET~sums are taken within a cone in $\eta$-$\phi$ around the direction
+of the electron of size $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
+The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged %\ac{PF} 
+hadrons associated with the primary vertex. %and within the cone of radius $\Delta R$ around
+%the electron's axis. 
+The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
+run over all neutral hadronic energy and photon energy. %within the cone of radius $\Delta R$.
+The contribution from neutral particles due to pileup needs to be subtracted from
+the sum of these two terms. It is estimated as the sum of charged hadronic \pT~for hadrons not associated
 with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
@@
 \label{sec:objects_muo}
-Muons are reconstructed by combining tracks in the inner tracker and tracks
+Muons are reconstructed by combining tracks in the inner tracker with tracks
 from the muon system \cite{cms-muon-reco}. Two complementary approaches are used:
@@
 tracks reconstructed in the muon system and searches for a matching
-tracker track, then re--applies the \ac{KF} on the combination
+tracker track, then reapplies the \ac{KF} to the combination
 of hits in the muon system and inner tracker. Conversely, the tracker muon reconstruction starts from
-tracks in the inner tracker which pass requirements on momentum to be considered
+tracks in the inner tracker which pass requirements on \pT~to be considered
 a muon candidate track. The trajectory is then extrapolated to the muon systems and
-considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs}, is found.
+considered a muon if at least one muon segment, a track stub in the \ac{DTs} or \ac{CSCs}, is found.
 Due to the requirement of a single muon segment this method is more efficient than the global muon
-reconstruction for muons with \pT~smaller than 5 GeV \cite{cms-muon-reco}.
-For muons with \pT~greater than 200 GeV, the momentum resolution is improved
+reconstruction for muons with \pT~smaller than $5\,\GeV$ \cite{cms-muon-reco}.
+For muons with \pT~greater than $200\,\GeV$, the momentum resolution is improved
 by the global muon reconstruction \cite{cms-muon-cosmics-perf}.
 
-The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
-for muons with \pT~up to 100 GeV and found to range from 1--6\% depending
-on detector region. For muons with \pT~between 100 GeV and 1 TeV the momentum resolution
+The muon momentum resolution was measured in p-p collisions at $\sqrt{s}=7\,\TeV$ 
+for muons with \pT~up to $100\,\GeV$ and found to range from 1--6\% depending
+on detector region. For muons with \pT~between $100\,\GeV$ and $1\,\TeV$ the momentum resolution
 was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
@@
 
-For global muon reconstruction non-muon backgrounds are small,
-though there can be small effects from hadronic showers not fully
+For global muon reconstruction the non-muon backgrounds are small,
+though there can be a small contamination from hadronic showers not fully
 contained in the \ac{HCAL}. A larger contribution is expected
-from real muons originating from for example decays of hadrons. These
+from real muons originating from, for example, decays of hadrons. These
 backgrounds can be reduced by applying additional identification criteria.
 
-For the analysis presented in chapter \ref{chap:mssm} ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
+For the analysis presented in chapter \ref{chap:mssm}, ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
 These requirements include:
@@
 \setlength{\itemsep}{-\baselineskip}
-\item Reconstruction by either global or tracker muon reconstruction algorithms.
-\item Requirements on track quality, and compatibility between the tracker-- and muon system track.
+\item Reconstruction by either the global or tracker muon reconstruction algorithms.
+\item Requirements on track quality, and compatibility between the tracker track and the muon system track.
 \item Selection on the segment compatibility, a weight between 0 and 1 which is a measure of the compatibility
 of a track with the muon track segments in the muon stations it has crossed.
-\item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in--flight decays.
+\item Requirements on the maximum kink in the tracker track in any of the layers of the tracker, to suppress in-flight decays.
 \end{itemize}
@@
 In addition to having to be reconstructed by the global muon algorithm, selections
-are made on the $\chi^2$/$N_{\text{dof}}$ of the track fit, number of hits of the inner
+are made on the $\chi^2$ per degrees of freedom of the track fit, number of hits of the inner
 track in different tracker layers and number of muon segments the inner track is matched to.
@@
 %\label{sec:objects_muo_iso}
-Just as described for electrons in section \ref{sec:objects_ele}, placing isolation 
-requirements on muons will also reduce backgrounds from misidentified jets and heavy--flavour
+As described for electrons in section \ref{sec:objects_ele}, placing isolation 
+requirements on muons will also reduce backgrounds from misidentified jets and heavy-flavour
 decays. The isolation variable used for muons is very similar to the one described for
 electrons in equation \ref{eqn:electron_reliso}, however the cone around the direction of the
-muon was chosen as $\Delta R = 0.4$ both during Run 1 and Run 2.
+muon was chosen as $\Delta R = 0.4$ during both Run 1 and Run 2.
 
@@
 combines the information from all of the different subdetectors of \ac{CMS}. This makes
-the identification of particles, and determination of position and momentum, as precise
-as possible. All of these particles are then used to build for example jets, hadronically decaying taus and missing transverse
-energy \MET, defined in equation \ref{eqn:objects_met_corr}.
+the identification of particles, and determination of their position and momentum, as precise
+as possible. All of these particles are then used to build, for example, jets, hadronically decaying taus and missing transverse
+energy \MET, which will be discussed in subsequent sections.
 
@@
 %tracks were low quality, or high pT
-The clustering algorithm used for \ac{PF} starts from \textit{cluster seeds},
+The clustering algorithm used for \ac{PF} starts from cluster seeds,
 calorimeter cells with local energy maxima. Topological clusters are built by 
@@
 being merged in contain a certain minimum energy.
-The threshold is 800 MeV in the \ac{HCAL} and two standard deviations above the
-expected noise level in the \ac{ECAL}, meaning 80 MeV in the barrel and up 
-to 300 MeV in the endcaps. Cell energies can be shared between multiple
+The threshold is $800\,\MeV$ in the \ac{HCAL} and two standard deviations above the
+expected noise level in the \ac{ECAL}, meaning $80\,\MeV$ in the barrel and up 
+to $300\,\MeV$ in the endcaps. Cell energies can be shared between multiple
 \ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.
@@
 For each block, particles are identified following a sequence
-of tests. First, if there is a link between a tracker track and a muon system track,
+of tests. Firstly, if there is a link between a tracker track and a muon system track,
 a \ac{PF} muon is identified if the combined tracker and muon system
-momentum is compatible with the tracker--only momentum. %within three standard deviations
+momentum is compatible with the tracker-only momentum. %within three standard deviations
 The muon track is removed from the block before the next step of the algorithm.
@@
 difference is smaller than the energy registered in associated \ac{ECAL} clusters 
-only a \ac{PF} photon is created. %Justified by fact that
+the energy difference is only associated with a \ac{PF} photon. %Justified by fact that
 %in jets 25% of the energy is carried by photons while neutral hadrons
@@
 %about a percent.
-
 Finally, any remaining \ac{ECAL} clusters not linked to a track give
@@
 
-\section{Jets and b--tagging}
+\section{Jets and b-tagging}
 \label{sec:objects_jets}
@@
 between the objects i and j in rapidity-azimuthal angle space. The radius
-parameter $R$ was chosen as 0.5 during Run 1 \cite{cms-jec-2011} and as 0.4 during Run 2 \cite{cms-jets-run2}. 
-This algorithm is collinear-- and infrared--safe, which means that the number of jets
+parameter $R$ was chosen as 0.5 during Run~1 \cite{cms-jec-2011} and as 0.4 during Run~2 \cite{cms-jets-run2}. 
+This algorithm is collinear- and infrared-safe, which means that the number of jets
 is not affected by the emission of soft collinear gluons or parton splitting.
@@
 
-Several methods exist for reducing the effects of pile--up particles 
+Several methods exist for reducing the effects of pileup particles 
 on the jet energy and substructure.
@@
 chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
-based on vertex- and jet shape information was used to reject jets due to pile--up.
+based on vertex information and jet shape information was used to reject jets due to pileup.
 
@@
 the true particle jet at hadron level. A correction \cite{cms-jec-2011} is applied to both
-jets in data and jets in \ac{MC} to match the measured and true
+jets in data and jets in \ac{MC} simulation to match the measured and true
 energies as
@@
 not associated with the hard scatter,
-including contributions from electronics noise and pile--up. This is
-estimated on an event--by--event basis based on the average--\pT~density
+including contributions from electronics noise and pileup. This is
+estimated on an event-by-event basis based on the average \pT~density
 per unit area $\rho$ and the area of the jet $A$ \cite{jet-area}. The factor $\rho$ includes
-contributions from pile--up, electronics noise and the \ac{UE} of the hard interaction. The 
+contributions from pileup, electronics noise and the \ac{UE} of the hard interaction. The 
 last of these should not be corrected for and therefore the average expected contribution
@@
 %factor $\text{C}_{\text{MC}}$ is defined as $\text{C}_{\text{MC}} = \frac{1}{<\mathcal{R}>}$.
-A di--jet \pT-balancing technique \cite{cms-jec-2011}
+A di-jet \pT-balancing technique \cite{cms-jec-2011}
 is used to measure the response of a jet at any $\eta$ relative
@@
 the response is flat, and a probe jet at any 
-$\eta$ value. The relative response, in bins of $\eta$ and \pT~ is determined by
+$\eta$ value. The relative response, in bins of $\eta$ and \pT, is determined by
 averaging the balancing function $\frac{p_{\text{T}}^{\text{probe}} - p_{\text{T}}^{\text{reference}}}{p_{\text{T}}^{\text{average}}}$.
@@
 make the response uniform in \pT. It is measured using the \ac{MPF} method \cite{cms-jec-2011}
- using samples of \Pphoton+ jets and \PZ+ jets events. This method relies on the fact that the
+ using samples of $\Pphoton+$jets and $\PZ+$jets events. This method relies on the fact that the
 events used for the measurement have no intrinsic missing energy, and so any measured \MET~
@@
 The uncertainty on the jet energy scale is propagated through to analyses.
-It is driven by uncertainties in the energy density used for pile--up
+It is driven by uncertainties in the energy density used for pileup
 subtraction, the photon energy scale, and the extrapolation required in the
@@
 
-\subsection{b--tagging}
+\subsection{b-Tagging}
 \label{sec:objects_jets_btag}
-As jets due to b--quark hadronisation are an important signature
+As jets due to b-quark hadronisation are an important signature
 for many analyses at the \ac{LHC} it is important to identify such jets correctly.
-Because b--hadrons have a relatively long lifetime $\tau \approx 1.5$ ps \cite{pdg-2014},
-they move for roughly $c\tau \approx 450$ $\mu$m before decaying. This means
+Because b-hadrons have a relatively long lifetime, $\tau \approx 1.5$ ps \cite{pdg-2014},
+they travel for around $c\tau \approx 450\,\micron$ before decaying. This means
 %large mass of 5--6 GeV
 they produce a displaced secondary decay vertex in the inner tracker.
-Algorithms for tagging b--jets usually rely on the information
+Algorithms for tagging b-jets usually rely on the information
 from these secondary vertices.
@@
 \ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter \ref{chap:mssm}. 
-The \ac{CSV} algorithm takes \ac{PF} jets with \pT$ > 20$ GeV and $|\eta|<2.4$ as input and 
-uses a likelihood--based discriminator to determine 
-whether a jet is likely due to b--quark hadronisation or not.
+The \ac{CSV} algorithm takes \ac{PF} jets with \pT~$> 20\,\GeV$ and $|\eta|<2.4$ as input and 
+uses a likelihood-based discriminator to determine 
+whether a jet is likely due to b-quark hadronisation or not.
 For this algorithm, secondary vertices are reconstructed from high-purity tracks
 within a cone of $\Delta R = 0.3$ around the jet axis, with quality cuts applied
-to reduce contamination from decays of long--lived particles or particles due 
+to reduce contamination from decays of long-lived particles or particles due 
 to interactions with the detector material. Information from the resulting
@@
 %a single discriminant.
-The \ac{CSV}v2 algorithm as improved for Run 2
+The \ac{CSV}v2 algorithm as improved for Run~2
 uses an \ac{IVF} algorithm to reconstruct secondary vertices \cite{cms-ivf}. Instead of 
@@
 instead of constructing a likelihood ratio from the input variables \cite{cms-btag-run2}. This allows
-for the addition of extra variables to discriminate between b- and other jets. %Figure \ref{fig:objects_bjets}a shows
+for the addition of extra variables to discriminate between b-jets and other jets. %Figure \ref{fig:objects_bjets}a shows
 %the distribution of the \ac{CSV}v2 discriminator in multijet events in the 2015 data sample.
-Once the discriminator has been constructed, loose- medium- and tight working points
+Once the discriminator has been constructed, loose, medium and tight working points
 can be determined as a minimum requirement on the discriminator such that the
-probability of misidentifying light--flavour jets with \pT $ > 30$ GeV is around
-10\%, 1\% and 0.1 \% respectively \cite{cms-btag-paper,cms-btag-run2}.
+probability of misidentifying light-flavour jets with \pT~$> 30\,\GeV$ is around
+10\%, 1\% and 0.1\% respectively \cite{cms-btag-paper,cms-btag-run2}.
 
 Because not all of the input variables to the \ac{CSV} algorithm are perfectly
-modelled in simulation the b--tagging efficiency for different jet
-flavours is different in data and \ac{MC}. Scale factors can be detemined
-as the ratio of tagging efficiencies in data and \ac{MC}, which are applied to the \ac{MC} to align
-the data and \ac{MC} efficiencies. The measurements of the tagging efficiency
-for genuine b--jets is based on samples containing a muon overlapping with the jet, 
-making use of the $\approx$ 11\% semileptonic branching fraction of b's. This
+modelled in simulation, the b-tagging efficiency for different jet
+flavours is different in data and \ac{MC} simulation. Scale factors can be detemined
+as the ratio of tagging efficiencies between the two, which are applied to the simulated events in order to match the data.
+The measurement of the tagging efficiency
+for genuine b-jets is based on samples containing a muon overlapping with the jet, 
+making use of the $\approx$ 11\% semileptonic branching fraction of b-hadrons. This
 measurement can be complemented by measurements from samples
@@
 \includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
-\caption[The b--tagging scale factors and errors for b--jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$
+\caption[The b-tagging scale factors and uncertainties for b-jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$
 %collected at $\sqrt{s} = 13$ TeV and (b) 
-The b--tagging scale factors and errors for b--jets in the data sample collected during 2015
+The b-tagging scale factors and uncertainties for b-jets in the data sample collected during 2015
 as a function of jet \pT~for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
@@
 Systematic uncertainties in the scale factors arise from, amongst other things,
-pile--up modelling in simulation, gluon splitting into $b\bar{b}$ pairs, track mismeasurement,
+pileup modelling in simulation, gluon splitting into $\Pbottom\APbottom$ pairs, track mismeasurement,
 and uncertainties in the fractions of different jet types.
-Figure \ref{fig:objects_bjets} shows the b--tagging scale factors, and associated errors,
+Figure \ref{fig:objects_bjets} shows the b-tagging scale factors, and associated uncertainties,
 for the medium working point of the \ac{CSV}v2 discriminator in the
@@
 \label{sec:objects_met}
-The \ac{CMS} detector is able to detect most stable and long--lived particles,
+The \ac{CMS} detector is able to detect most stable and long-lived particles,
 however, neutrinos and hypothetical neutral weakly interacting particles
@@
 will give rise to an energy imbalance in the transverse plane, and so their
-presence can be inferred from missing energy \MET~in the event.
+presence can be inferred from missing energy,\MET, in the event.
 
 The \MET~is defined as $-\Sigma \vec{p}_{\text{T}}$, where
-the sum runs over all final--state particles and jets in the event. This quantity
+the sum runs over all final-state particles and jets in the event. This quantity
 can be mismeasured due to detector inefficiencies, calorimeter energy thresholds and
@@
 response for hadronic particles.
-Therefore, to increase the accuracy of the \MET~measurement the jet energy corrections should be propagated as
+Therefore, to increase the accuracy of the \MET~measurement the jet energy corrections are propagated as
 \begin{equation}\label{eqn:objects_met_corr}
-\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - p_{\text{T,jet}})
+\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - p_{\text{T,jet}}).
 \end{equation}
@@
 This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections
-The \MET~can also be mismeasured due to pile--up interactions, and an improved
-measurement of the \MET~at high pile--up can be obtained by using the MVA \MET~
+The \MET~can also be mismeasured due to pileup interactions, and an improved
+measurement of the \MET~at high pileup can be obtained by using the MVA \MET~
 algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
-chapter \ref{chap:mssm}. This algorithm computes a correction to the hadronic
+\ref{chap:mssm}. This algorithm computes a correction to the hadronic
 recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
@@
 where $\Sigma \vec{p}_{\text{T}}^{\text{  lep}}$ corresponds to the vectorial sum of the transverse momenta of the
-constituents selected as the di--$\tau$ candidate.
+constituents selected as the di-tau candidate.
 
@@
 \Zmm events, in a sample corresponding to 42 pb$^{-1}$ of data collected
-at $\sqrt{s}=13$ TeV.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
-\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=$\mbox{13 TeV}. The \MET~
-values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
-circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
+at $\sqrt{s}=13\,\TeV$.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
+\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=13\,\TeV$. The 
+\MET~values for MVA \MET~are lower than for \ac{PF} \MET. (b) The \MET~resolution for \ac{PF} \MET~in blue and MVA \MET~in red/brown
+circles, as a function of number of vertices. The MVA \MET~resolution is more stable with increased pileup \cite{cms-dp-mvamet}.}
 \label{fig:objects_mvamet}
@@
 different \MET~definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
-the performance of the MVA \MET~in data collected at $\sqrt{s}=13$ TeV compared with 
-the \ac{PF} \MET, indicating the lower MVA \MET~values for events without genuine
-\MET in figure \ref{fig:objects_mvamet}a and the improved resolution at high pile--up
-in figure \ref{fig:objects_mvamet}b.
+the performance of the MVA \MET~in data collected at $\sqrt{s}=13\,\TeV$ compared with 
+the \ac{PF} \MET. Figure \ref{fig:objects_mvamet}a indicates the lower MVA \MET~values for events without genuine
+\MET and figure \ref{fig:objects_mvamet}b shows the improved resolution at high pileup.
 
-In the process of calculating the corrections to the hadronic recoil using the MVA \MET~
-algorithm, an event--by--event
-estimator of the likelihood that the \MET~ is due to unseen objects rather than induced
-by mismeasurement of jet energy is also estimated \cite{cms-met-run1}.
+In the process of calculating the corrections to the hadronic recoil using the MVA \MET~algorithm, an event-by-event
+estimator of the likelihood that the \MET~is due to unseen objects rather than induced
+by mismeasurement of jet energy is also determined \cite{cms-met-run1}.
 %Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
@@
 \label{sec:objects_met_recoilcorr}
-To correct for the mismodelling of \MET~in \ac{MC} events without genuine \MET, recoil corrections are determined. 
+To correct for the mismodelling of \MET~in simulated events, recoil corrections are determined. 
 The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{ leptons}/\nu}$ 
-is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT~of the boson producing the leptons
+is projected onto the axes parallel, $u_{\parallel}$, and perpendicular, $u_{\perp}$, to the \pT~of the boson producing the leptons
 and neutrinos. For the analyses
@@
 are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
-and \ac{MC} events, using convolutions of gaussians. Corrections are then applied to the \ac{MC}
+and simulated events, using convolutions of gaussians. Corrections are then applied to the \ac{MC}
 as
 \begin{equation}\label{eqn:met_recoilcorr}
-u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + u_{\parallel,\perp} - <u_{\parallel,\perp}>_{MC} \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}
+u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + (u_{\parallel,\perp} - <u_{\parallel,\perp}>_{\text{MC}}) \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}.
 \end{equation}
@@
 \label{sec:objects_tau}
-Taus are unstable particles and they decay before reaching the detector. In 17.4 \% of 
-cases they decay to muons and neutrinos, with an additional 17.8 \% decaying to electrons
-plus neutrinos. The remaining 64.8 \% decay hadronically. Hadronically decaying
-taus are characterised by narrow jets containing either one or three charged
-particles ($\pi^{\pm}, K^{\pm}$) and 0,1, or two neutral pions. An overview
-of the most common possible decay modes is given in table \ref{tab:hadronic_tau_decays}
+Taus are unstable particles and they decay before reaching the detector. In 17.4\% of 
+cases they decay to muons and neutrinos, with an additional 17.8\% decaying to electrons
+plus neutrinos. The remaining 64.8\% decay hadronically. Hadronically decaying
+taus, \Pgth, are characterised by narrow jets containing either one or three charged
+particles ($\pi^{\pm}, K^{\pm}$) and zero, one, or two neutral pions. An overview
+of the most common decay modes is given in table \ref{tab:hadronic_tau_decays}.
 \begin{table}[htp]
@@
 
-Hadronic tau decays are reconstructed using the \texttt{hadrons plus strips} (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
+Hadronic tau decays are reconstructed using the ``hadrons plus strips'' (HPS) algorithm~\cite{cms-tau-run1,cms-tau-2015}, 
 which is seeded by jets clustered from \ac{PF} candidates, using the anti-\kT~algorithm with a distance parameter $\Delta R = 0.5$ in
-Run 1 and $\Delta R = 0.4$ in Run 2. 
+Run~1 and $\Delta R = 0.4$ in Run~2. 
 As table \ref{tab:hadronic_tau_decays}
@@
 probability that photons from $\Ppizero \rightarrow \Pphoton \Pphoton$ decays will convert to
-\APelectron \Pelectron pairs, which are bent in the magnetic field and 
+$\APelectron \Pelectron$ pairs, which are bent in the magnetic field and 
 therefore cause showers dispersed in the $\phi$ direction in the \ac{ECAL}. Therefore, to 
 reconstruct the energy deposits \Ppizero candidates leave in the ECAL, 
-the photon and electron constituents of the jet that seeds the $\tau_{h}$ reconstruction are clustered into strips.
-The electron or photon with highest \pT~that is not yet included in a strip is used to build a new strip.
-The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT~ electron or photon
+the photon and electron constituents of the jet that seeds the \Pgth reconstruction are clustered into strips.
+The electron or photon with the highest \pT~that is not yet included in a strip is used to build a new strip.
+The $\eta$ and $\phi$ of this candidate determine the initial position of the strip, the next highest \pT~electron or photon
 within an $\eta \times \phi$ window centered on the strip location is added to the strip and the position is 
-recomputed as the energy--weighted average of the electron/photon constituents in the strip.
-This procedure is repeated until there are no more electrons or photons with \pT $ > 0.5$~GeV  within the 
-strip window. During Run 1 the strip window had a fixed size of $0.05 \times 0.2$ in $\eta \times \phi$, 
-while in the algorithm used during Run 2 the strip size is dynamically allocated. The
-width of the strip in $\eta$ and $\phi$ is varied based on the \pT~or \ET~ to 
+recomputed as the energy-weighted average of the electron and photon constituents in the strip.
+This procedure is repeated until there are no more electrons or photons with \pT~$ > 0.5\,\GeV$ within the 
+strip window. During Run~1 the strip window had a fixed size of $0.05 \times 0.2$ in $\eta \times \phi$, 
+while in the algorithm used during Run~2 the strip size is dynamically allocated. The
+width of the strip in $\eta$ and $\phi$ is varied based on the \pT~or \ET~to 
 be added to the strip and on the energy the strip already has, as
@@
 where $p_{\text{T},\Pe/\Pphoton}$ is the transverse momentum of the candidate to be added to the strip
-and $p_{\text{T,strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\
-In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$, $0.05 < \Delta\phi < 0.3$ \cite{cms-tau-2015}.
+and $p_{\text{T,strip}}$ is the transverse momentum of the strip before merging a new candidate in.\\%FIXME EXPLAIN WHERE THIS COMES FROM SEE AN ETC
+In addition, the strip size is bounded as $0.05 < \Delta\eta < 0.15$ and $0.05 < \Delta\phi < 0.3$ \cite{cms-tau-2015}.
 
@@
 %\end{equation}
-If the $\Sigma$ \pT~of the strip is at least 2.5~GeV, it is considered as a \Ppizero candidate.
+If the $\Sigma$ \pT~of the strip is at least $2.5\,\GeV$ it is considered as a \Ppizero candidate.
 To reconstruct hadronic taus, charged particles and strips are combined into different signatures which are said to be
 compatible with a certain decay mode if the selection listed below is satisfied. The charged particles
-and strips are required to be within the signal cone $R_{\text{sig}} = \frac{3.0}{p_{\text{T}}[GeV]}$, always
-required to be $0.05 < R_{\text{sig}} < 0.1$.
-If a candidate satisfies more than one of the hypotheses, the one that maximises the \pT~is retained.
+and strips are required to be within the signal cone $R_{\text{sig}} = \frac{3.0}{p_{\text{T}}[\GeV]}$, bounded 
+by $0.05 < R_{\text{sig}} < 0.1$.
+If a candidate satisfies more than one of the hypotheses the one that maximises the \pT~is retained.
 The decay modes considered for reconstructing hadronic taus are:
@@
 \item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
-\item \textbf{One prong + 1 \Ppizero :} One charged particle + one strip with $\Pgt$  mass requirement $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}$~GeV, with the
-upper limit on the mass at least 1.3 and at most 4.2 GeV.
+\item \textbf{One prong + 1 \Ppizero :} One charged particle and one strip with tau mass requirement $ 0.3 < m_{\Pgt} < 1.3 \sqrt{p_{\text{T}}/100}\,\GeV$, with this
+upper limit on the mass at least $1.3\,\GeV$ and at most $4.2\,\GeV$.
 %less than 100 GeV, the upper limit is fixed to 1.3 GeV, and for momenta larger than 1044 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.2 GeV.
-\item \textbf{One prong + 2 \Ppizero :} One charged particle + two strips. The $\Pgt$ mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}$~GeV, with the
-upper limit on the mass at least 1.2 and at most 4.0 GeV.
+\item \textbf{One prong + 2 \Ppizero :} One charged particle and two strips. The tau mass should be $0.4 < m_{\Pgt} < 1.2\sqrt{p_{\text{T}}/100}\,\GeV$, with the
+upper limit on the mass at least $1.2\,\GeV$ and at most $4.0\,\GeV$.
 %less than 100 GeV, the upper limit is fixed to 1.2 GeV and for momenta larger than 1111 GeV the upper limit on $m_{\Pgt}$ is fixed to 4.0 GeV.
-\item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5$~GeV. The tracks are required to originate 
+\item \textbf{Three prong + 0 \Ppizero: } Three charged particles with mass $0.8 < m_{\tau} < 1.5\,\GeV$. The tracks are required to originate 
 within $\Delta z<0.4$~cm of the same vertex, and their total charge is required to be $\pm 1$.
@@
 %\label{sec:objects_tau_iso}
-Requiring the reconstructed $\Pgt_{h}$ to be isolated reduces the jet $\rightarrow\Pgt_{h}$ fake rate. Isolation
+Requiring the reconstructed \Pgth to be isolated reduces the jet $\rightarrow$\Pgth fake rate. Isolation
 discriminators can be defined using the isolation sum,
 \begin{equation}\label{eqn:cutbased_iso}
-I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm }) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm }) ),
+I_{\Pgt} = \Sigma p_{\text{T}}^{\text{charged}}(d_Z < 0.2\text{ cm}) + \text{max}(0,\Sigma p_{\text{T}}^{\Pphoton} - \Delta \beta \Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm}) ),
 \end{equation}
 where the first term denotes the sum of the transverse momenta of all charged particles not part
-of the identified hadronic tau. Only particles with \pT $> 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the 
-direction of the hadronic tau are taken into account and the charged particle tracks are required to be compatible with having
-originated from the $\Pgt_{h}$ production vertex within $d_Z < 0.2$ cm. The second term denotes the sum
+of the identified \Pgth. Only particles with \pT~$> 0.5\,\GeV$ within a cone of $\Delta R = 0.5$ centred around the 
+direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
+originated from the \Pgth production vertex within $d_Z < 0.2\,\cm$. The second term denotes the sum
 of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
-of the hadronic tau. The effect of pile--up on this term is accounted for by subtracting the sum of the momenta of charged
-particles with \pT $ > 0.5$ GeV, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
+of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
+particles with \pT~$> 0.5\,\GeV$, within a cone of $\Delta R = 0.8$ around the direction of the hadronic tau and
 tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
-a $\Delta \beta$ factor of 0.2.
+a $\Delta \beta$ factor of 0.2.%FIXME rephrase
 
-In addition to the isolation sum, requirements on the sum of transverse momenta
+In addition to the isolation sum, a requirement on the sum of transverse momenta
 of electrons and photons included in strips but which are located outside of the signal cone,
@@
 can be made.
-An MVA $\tau_{h}$ isolation discriminator combines isolation variables with $\tau$ lifetime information into a BDT to discriminate between $\tau_{h}$ decays and quark and gluon jets.
+An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a BDT to discriminate between \Pgth decays and quark and gluon jets.
 Some of the variables used as input are:
@@
 \item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
-\item Track--related variables such as impact parameters, quality of the track, and information about decay vertices.
-\item Information about photons: the momentum weighted $\Delta R$ and/or $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
-\item $\Pgt_{h}$--related kinematic quantities, plus the reconstructed decay mode.  
+\item Track-related variables such as impact parameters, quality of the track, and information about decay vertices.
+\item Information about photons: the momentum weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
+\item \Pgth-related kinematic quantities, plus the reconstructed decay mode.  
 %\item The charged-and neutral-particle isolation sums
@@
 
-Figure \ref{fig:tau_efficiency}a compares the $\Pgt_{h}$ identification efficiency with the
-jet$\rightarrow \Pgt_{h}$ fake rate for different working points of the
-MVA isolation discriminator, as well as the cut--based isolation discriminator based
-on isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA--based 
+Figure \ref{fig:tau_efficiency}a compares the \Pgth identification efficiency with the
+jet$\rightarrow$\Pgth fake rate for different working points of the
+MVA isolation discriminator, as well as the cut-based isolation discriminator based
+on the isolation sum and $p_{\text{T}}^{\text{strip,outer}}$. The MVA-based 
 discriminator performs better than the cut-based discriminator alone.
 
-In order to reduce the $\Pe\rightarrow\Pgt_h$ and $\Pgm\rightarrow\Pgt_h$ fake rate, 
-anti--electron and anti--muon discriminators are used. 
-The anti--electron discriminator is a BDT--based discriminator trained using input variables such as:
+In order to reduce the $\Pe\rightarrow$\Pgth and $\Pgm\rightarrow$\Pgth fake rates, 
+anti-electron and anti-muon discriminators are used. 
+The anti-electron discriminator is a BDT-based discriminator trained using input variables such as:
 \begin{itemize}
 \setlength{\itemsep}{-\baselineskip}
-\item Kinematic variables of the $\Pgt_{h}$ candidate and \ac{GSF} track, including visible mass of the $\Pgt_{h}$.
-\item Energy/momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
-\item Photon--related variables, such as the momentum--weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the $\Pgt_{h}$ energy carried by photons, and the number of photons found in strips.
+\item Kinematic variables of the \Pgth candidate and \ac{GSF} track, including visible mass of the \Pgth.
+\item Energy and momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
+\item Photon-related variables, such as the momentum-weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the \Pgth energy carried by photons, and the number of photons found in strips.
 \item Information on the quality of the track.
@@
 
-Five working points are provided, ranging from very loose to very tight. The $\Pgt_{h}$ efficiency
-and $\Pe\rightarrow\Pgt_h$ fake rate for the various working points are shown in
-figures \ref{fig:tau_efficiency}b and c, respectively.
+Five working points are provided, ranging from very loose to very tight. The \Pgth efficiency
+and $\Pe\rightarrow$\Pgth fake rate for the various working points are shown in
+figures \ref{fig:tau_efficiency}b and \ref{fig:tau_efficiency}c, respectively.
 
@@
 \subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
-\subfloat[Real $\Pgt_{h}$ efficiency for anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
-\subfloat[$\Pe\rightarrow\Pgt_{h}$ fake rate for the anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
+\subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
+\subfloat[$\Pe\rightarrow$\Pgth fake rate for the anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
 \end{center}
-\caption[Figures of the jet$\rightarrow\Pgt_{h}$ fake rate in QCD MC events
+\caption[Figures of the jet$\rightarrow$\Pgth fake rate in QCD MC events
 versus $\Pgt_{h}$ identification efficiency for \htotautau MC events, the real
 $\Pgt_{h}$ identification efficiecny for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
-working points of the anti-electron discriminator.]{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
-efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 
+working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
+efficiency for simulated \htotautau events, comparing the MVA-based isolation discriminator in red with the cut-based 
 isolation discriminator in pink. Tighter working points give lower hadronic tau identification
-efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
-from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real $\Pgt_{h}$ identification
-efficiency for different working points of the anti-electron discriminator, as a function of the \pT~of the $\Pgt_{h}$, and (c)
-the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
+efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
+from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real \Pgth identification
+efficiency for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
+the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
 the \pT~of the \Pe.}
@@
 \end{figure}
-The anti--muon discriminator is a cut-based discriminant, for which a loose and a tight working
+The anti-muon discriminator is a cut-based discriminant, for which a loose and a tight working
 point are provided. It is based on variables such as the number of track segments found in various
-parts of the muon system around the direction of the $\Pgt_{h}$, and comparisons of calorimeter energy
-with the momentum of the leading $\Pgt_{h}$ track.
+parts of the muon system around the direction of the \Pgth, and comparisons of calorimeter energy
+with the momentum of the leading \Pgth track.
 %\begin{itemize}

### 2017-02-17 Conclusion/Conclusion.tex
Adding some more of the crap at the beginning, plus editing

--- 2017-02-08 Conclusion/Conclusion.tex
@@
 The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
-125 GeV Higgs bosons was performed using 19.7 fb$^{-1}$ of data collected at a
-centre of mass energy of 8 TeV during the 2012 \ac{LHC} data-taking period. Such a final
+$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
+centre of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
 state can access areas of the MSSM phase space not easily accessible via other channels.
@@
 b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
-mass in a window around 125 GeV are used in combination with a kinematic fitting technique for
+mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
 the reconstruction of the 4-body mass.
@@
 The results of this search are upper limits on production cross section times branching 
-ratio, in a mass range $260<m_H<350$ GeV. A combination with a search for \AtoZhtolltautau
-yields exclusion in the lowest \tanb~region of the low-tanb~MSSM scenario, as well
-as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario.
+ratio, in a mass range $260<m_H<350\,\GeV$. A combination with a search for \AtoZhtolltautau
+yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well
+as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.
 
 Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
-using 2.3 fb$^{-1}$ of data recorded during the 2015
-data-taking period of the \ac{LHC}, and using 12.9 fb$^{-1}$ of 
+using $2.3\,\invfb$ of data recorded during the 2015
+data-taking period of the \ac{LHC}, and using $12.9\,\invfb$ of 
 data recorded during the first half of the 2016 data-taking period. The 
-branching ratio of heavy neutral Higgs bosons into di-\Pgt pairs is enhanced at high \tanb~in the \ac{MSSM},
-making this one of the most sensitive search channels for such particles. The analysis uses a categorisation 
+branching ratio of heavy neutral Higgs bosons into di-tau pairs is enhanced at high \tanb~in the \ac{MSSM},
+making this one of the most sensitive search channels for such particles. Both analyses use a categorisation 
 based on the presence of b-tagged jets to separate
@@
 the \mT~variable, are chosen to optimise the search sensitivity for signal
-masses of around 1 TeV.
+masses of around $1\,\TeV$.
 The sensitivity is maximised by using the \mTtot~variable for signal extraction.
@@
 of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
-results obtained in Run 1. A combination of the 2015 and 2016 analyses is also
+results obtained in Run 1 \cite{CMS-PAS-HIG-16-006,CMS-PAS-HIG-16-037}. A combination of the 2015 and 2016 analyses is also
 performed. This combination improves on the results of the 2016 analysis alone, thus
@@
 As more data are collected during the remainder of Run 2, and in the 
-future, searches for MSSM Higgs bosons in the di-$\Pgt$ final
+future, searches for MSSM Higgs bosons in the di-tau final
 state will continue. If no such Higgs bosons are found, these searches
@@
 will become accessible. A projection of the results of the 2015 \ac{MSSM}
-analysis to an integrated luminosity of 300 fb$^{-1}$ and 3000 fb$^{-1}$ is
+analysis to an integrated luminosity of $300\,\invfb$ and $3000\,\invfb$, presented at ECFA \cite{HTT-projection}, is
 shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
-3000 fb$^{-1}$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
-as the branching ratio of $\PHiggsps/\PHiggs$ into di-$\Pgt$ pairs 
+$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
+as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
 is very low in the high \mA-low \tanb~corner. This region can be accessed 
@@
 \end{center}
-\caption{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
+\caption[The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
+at 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
  at 95\% CL of the 2015 MSSM analysis (pink)
-projected to an integrated luminosity of 300 fb$^{-1}$ (blue) and 3000 fb$^{-1}$ (red)
+projected to an integrated luminosity of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
 under several assumptions of how the systematic uncertainties scale. Even with an integrated 
-luminosity of 3000 fb$^{-1}$ it is not possible to exclude the entire \mA-\tanb~plane
+luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
 in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}

### 2017-02-17 Detector/Detector.tex
Adding some more of the crap at the beginning, plus editing

@@
 
-\subsection{\acl{ECAL}}
+\subsection{Electromagnetic calorimeter}
 \label{sec:CMSLHC_CMS_ecal}
@@
 covers the pseudorapidity range up to $|\eta|<1.479$, with
-crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \ac{EE}
+crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \acp{EE}
 provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
@@
 
-\subsection{\acl{HCAL}}
+\subsection{Hadron calorimeter}
 \label{sec:CMSLHC_CMS_hcal}
@@
 outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
-In the barrel of the detector the \ac{DTs} provide coverage for $|\eta|<1.2$, with
-the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
-regions as both the \ac{DTs} and \ac{CSCs}, are used as a dedicated triggering system.
+In the barrel of the detector the \acp{DT} provide coverage for $|\eta|<1.2$, with
+the \acp{CSC} covering the $0.9<|\eta|<2.4$ region. The \acp{RPC}, covering the same
+regions as both the \acp{DT} and \acp{CSC}, are used as a dedicated triggering system.
 
 A cross section of one quadrant of the detector, indicating
-the positions of the \ac{DTs}, \ac{CSCs} and \ac{RPCs}, is shown in figure \ref{fig:CMS_MuonSystem}.
+the positions of the \acp{DT}, \acp{CSC} and \acp{RPC}, is shown in figure \ref{fig:CMS_MuonSystem}.
 The top of the fourth muon endcap station as shown in this figure was added during \ac{LS1} \cite{cms-muon-upgrade}, providing
-additional layers of \ac{CSCs} and \ac{RPCs}.
+additional layers of \acp{CSC} and \acp{RPC}.
 \begin{figure}[h!]
@@
 
-The \ac{DTs} consists of layers of drift cells which have a cross section of $4.2\,\cm \times 1.3\,\cm$ and
+The \acp{DT} consist of layers of drift cells which have a cross section of $4.2\,\cm \times 1.3\,\cm$ and
 are $2.4\,\metre$ long. The cells are filled with a mixture of %85\% 
@@
 during p-p running in 2010.
-The spatial resolution of the \ac{DTs} is $80$--$120\,\micron$ per chamber for
+The spatial resolution of the \acp{DT} is $80$--$120\,\micron$ per chamber for
 measurements in the $\phi$ direction, while the resolution of the $z$ measurement
@@
 
-In the endcaps, where both the muon rate and the radiation levels are higher, the \ac{CSCs} provide
+In the endcaps, where both the muon rate and the radiation levels are higher, the \acp{CSC} provide
 measurements of the muon track. These detectors are radiation hard,
 and have a fast response and fine segmentation.
-Each of the CSC modules is a wedge-shaped
+Each of the \ac{CSC} modules is a wedge-shaped
 multi-wire proportional chamber %WTF
@@
 
-In addition to the \ac{DTs} and \ac{CSCs}, the \ac{RPCs} provide coverage
+In addition to the \acp{DT} and \acp{CSC}, the \acp{RPC} provide coverage
 for $|\eta|<1.6$. These are made up of parallel plates, forming the anode and cathode,
@@
 muons is read out using aluminium strips running parallel to the 
-beam axis. The position resolution of the \ac{RPCs} is poorer than
-that of the \ac{DTs} and \ac{CSCs}, but their time response is very fast. As
-a result of this the \ac{RPCs} are used as an independent muon trigger
+beam axis. The position resolution of the \acp{RPC} is poorer than
+that of the \acp{DT} and \acp{CSC}, but their time response is very fast. As
+a result of this the \acp{RPC} are used as an independent muon trigger
 which can correctly identify the beam crossing from which the muon
@@
 Hits in the muon chambers are read out and passed to the track finder layer 
-of the muon trigger, which combines information from the CSC, DT
-and RPC systems in regions of $\eta$-$\phi$.
+of the muon trigger, which combines information from the \ac{CSC}, \ac{DT}
+and \ac{RPC} systems in regions of $\eta$-$\phi$.
 In further layers of the muon trigger the information from different

### 2017-02-17 MSSM/MSSM.tex
Edit of objects section
Adding some more of the crap at the beginning, plus editing

@@
 
-\section{Datasets and MC samples}
+\section{Datasets and \acs{MC} samples}
 \label{sec:mssm_datasets}
@@
 In addition, a requirement is made on the $\eta$ of the electrons, muons and
-hadronic taus. This election is driven by the $\eta$ range covered by the tracker and
+hadronic taus. This selection is driven by the $\eta$ range covered by the tracker and
 that is thus used for the reconstruction of the particles. For some of the
@@
 
-Other selections include cuts on the impact parameters $d_{xy}$ and $d_{z}$, which
+Other selections include cuts on the transverse and longitudinal impact parameters $d_{xy}$ and $d_{z}$, which
 ensure that the particle is likely to have
@@
 
-\section{\ac{MC} to data correction factors}
+\section{\acs{MC} to data correction factors}
 \label{sec:mssm_mccorrs}
@@
 Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
-two jets are misreconstructed as the two particles of the candidate pair. %Relatively likely to happen in tautau channel
-As visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
+two jets are misreconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
+As is visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
 This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
@@
 figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
-background as the `Electroweak' component.
+background and is referred to as the `Electroweak' component.
 

### 2017-02-17 Objects/Objects.tex
Adding some more of the crap at the beginning, plus editing

@@
 such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
-decays. Both a cut-based and a BDT-based algorithm are available. %FIXME define BDT
+decays. Both a cut-based algorithm and an algorithm based on \acp{BDT} are available. %FIXME define BDT
 For the selection of electrons in 
-the analyses presented in later chapters the BDT-based algorithm is used, 
+the analyses presented in later chapters the \ac{BDT}-based algorithm is used, 
 with exceptions for the loose identification criteria required for vetoing electrons. 
-The variables used in this BDT include:%FIXME full stop usage?!
+The variables used in this \ac{BDT} include:%FIXME full stop usage?!
 \begin{itemize}
@@
 \caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
-and misidentified electrons at 8 TeV, for data and MC]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
-misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
-taken at $\sqrt{s} = 8$ TeV, overlaid on the distributions for simulated 
+and misidentified electrons at $8\,\TeV$, for data and MC]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
+misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
+taken at $\sqrt{s} = 8\,\TeV$, overlaid on the distributions for simulated 
 real electrons in purple \cite{cms-elereco-run1}.}
@@
 of the track with the already linked \ac{ECAL} clusters is assessed using
-\ac{BDTs} which take several variables into account. If the candidate
+\acp{BDT} which take several variables into account. If the candidate
 passes, it is identified as a \ac{PF} electron and the track and
@@
 \includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
-\caption[The b-tagging scale factors and uncertainties for b-jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$
+\caption[The b-tagging scale factors and uncertainties for b-jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in $2.6\,\invfb$
 %collected at $\sqrt{s} = 13$ TeV and (b) 
@@
 \caption[\MET~distributions comparing MVA \MET~to PF \MET~for
-\Zmm events, in a sample corresponding to 42 pb$^{-1}$ of data collected
+\Zmm events, in a sample corresponding to $42\,\invpb$ of data collected
 at $\sqrt{s}=13\,\TeV$.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
-\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=13\,\TeV$. The 
+\Zmm events, which contain no genuine \MET~, in a sample corresponding to $42\,\invpb$ of data collected at $\sqrt{s}=13\,\TeV$. The 
 \MET~values for MVA \MET~are lower than for \ac{PF} \MET. (b) The \MET~resolution for \ac{PF} \MET~in blue and MVA \MET~in red/brown
@@
 
-Two \ac{BDTs} trained on \Zmm events are used to compute this correction.
+Two \acp{BDT} trained on \Zmm events are used to compute this correction.
 The first one corrects the direction of the hadronic recoil, the second
 one uses a data sample with the corrected recoil direction to compute a correction
-to the magnitude of the hadronic recoil. This BDT regression uses the magnitude of the hadronic
+to the magnitude of the hadronic recoil. This \ac{BDT} regression uses the magnitude of the hadronic
 recoil, its azimuthal angle and the scalar \pT~sum of all \ac{PF} particles for several 
@@
 can be made.
-An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a BDT to discriminate between \Pgth decays and quark and gluon jets.
+An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a \ac{BDT} to discriminate between \Pgth decays and quark and gluon jets.
 Some of the variables used as input are:
@@
 anti-electron and anti-muon discriminators are used. 
-The anti-electron discriminator is a BDT-based discriminator trained using input variables such as:
+The anti-electron discriminator is a \ac{BDT}-based discriminator trained using input variables such as:
 \begin{itemize}

### 2017-02-17 Theory/Theory.tex
Adding some more of the crap at the beginning, plus editing

@@
 \toprule
- & \textbf{1st generation} & \textbf{2nd generation} & \textbf{3d generation}\\
+ & \textbf{$1^{\text{st}}$ generation} & \textbf{$2^{\text{nd}}$ generation} & \textbf{$3^{\text{d}}$ generation}\\
 \midrule
@@
 the strong nuclear force, while the \ac{EM} force is mediated
-by the photon (\Pphoton), and the $\PW^{\pm}$ and \PZ bosons carry the weak nuclear force.
+by the photon (\Pphoton), and the weak force by the $\PW^{\pm}$ and \PZ bosons.
 
@@
 both the quarks and the gluons carry.
-The interactions in the \ac{QFT} of the
-strong force, called \ac{QCD}, are governed by an SU(3) (colour) symmetry.
+Within the framework of \ac{QFT}, the
+strong force is described by \ac{QCD}, governed by an SU(3) (colour) symmetry.
 %There are 8 gluons due to the SU(3) symmetry, colour octet and a colour singlet, but
@@
 Characteristics of \ac{QCD} include confinement, meaning quarks are always observed in bound
-hadron states, and asymptotic
+states called hadrons, and asymptotic
 freedom \cite{asympt-I,asympt-II}. Due to asymptotic freedom the 
@@
 is a key component of the \ac{SM}. The electroweak force 
-is governed by an SU(2)$\times$U(1) symmetry and implies the presence of weak
+is governed by an SU(2)$_{\text{L}}\times$U(1)$_{\text{Y}}$ symmetry and implies the presence of weak
 neutral currents.
@@
 symmetry comes from the weak hypercharge generator $Y$, which
-is related to weak isospin and electric charge as $Q = I_3 + \frac{1}{2}Y$.
+is related to weak isospin and electric charge as
+\begin{equation}\label{eqn:hypercharge}
+Q = I_3 + \frac{1}{2}Y.
+\end{equation}
 
@@
 \begin{split}
-&g\sin{\theta_W} = g'\cos{\theta_W} \Rightarrow \\
-&\sin{\theta_W} = \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}
+&g\sin{\theta_W} = g'\cos{\theta_W}\\
+&\Rightarrow \sin{\theta_W} = \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}
 \end{split}
@@
 followed 10 years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
-and UA2 collaborations at \acs{CERN}a, confirming the predicitions from electroweak unification.
+and UA2 Collaborations at \acs{CERN}, confirming the predicitions from electroweak unification.
 It should be noted that the weak force only couples to the left-handed parts
@@
 Searches for the Higgs boson at the \ac{LEP} did not lead
-to its observation. However, masses below 114.4 GeV were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
+to its observation. However, masses below $114.4\,\GeV$ were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
 providing a lower search limit. Subsequent searches at the 
 Tevatron also did not lead to discovery of the Higgs boson, but did exclude 
-an additional mass range of 140-186 GeV at 95\% \ac{CL} \cite{TEV-Higgs}.
+an additional mass range of $140$--$186\,\GeV$ at 95\% \ac{CL} \cite{TEV-Higgs}.
 
-On the fourth of July 2012 the ATLAS and CMS collaborations
-announced the discovery of a boson with a mass of around 125 GeV \cite{HDiscoveryATLAS,HDiscoveryCMS}.
+On the fourth of July 2012 the ATLAS and CMS Collaborations
+announced the discovery of a boson with a mass of around $125\,\GeV$ \cite{HDiscoveryATLAS,HDiscoveryCMS}.
 The discovery was based on the observation of excesses in the 
-search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ$, with a significance 
+search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ\rightarrow 4\ell$, with a significance 
 above 5$\sigma$.
@@
 increased the confidence in the compatibility of this new state with the \ac{SM} Higgs boson. 
-The most precise measurement of the mass of the Higgs boson, \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst) }$ GeV, 
+The most precise measurement of the mass of the Higgs boson, \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst)}\,\GeV$, 
 comes from the ATLAS and CMS combined
-mass measurement using the full dataset of Run 1 of the \acs{LHC} \cite{MassComb}.
-The combined ATLAS and CMS production- and decay rate measurement, also using the full dataset of \acs{LHC} Run 1,
-shows very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
+mass measurement using the full Run 1 dataset \cite{MassComb}.
+The combined ATLAS and CMS production- and decay rate measurements, also using the full Run 1 dataset,
+show very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
 the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination, while
@@
 \end{center}
-\caption[SM Higgs boson production cross sections at $\sqrt{s}=13$ TeV and SM Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
-Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
+\caption[SM Higgs boson production cross sections at $\sqrt{s}=13\,\TeV$ and SM Higgs boson branching ratios, for Higgs boson masses between $120$ and $130\,\GeV$]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13\,\TeV$ and (b) \ac{SM}
+Higgs boson branching ratios, for Higgs boson masses between $120$ and $130\,\GeV$ \cite{YR4}.}
 \label{fig:theory_smhxsbr}
@@
 is still to be achieved.
-Finally, searches for ttH production, which are important to probe the top-Higgs coupling, have also been carried 
+Finally, searches for ttH production, which are important to probe directly the top-Higgs coupling, have also been carried 
 out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
@@
 For example, it does not provide a candidate for dark matter, which is estimated
-to make up 25\% of the matter in the universe.
+to make up 25\% of the matter energy density in the universe.
 In addition, the running coupling constants of the electroweak and
@@
 \ac{SUSY} allows the electroweak and strong coupling
-constants to intersect at a common energy scale of $\mathcal{O}(10^{16} \text{ GeV })$ \cite{GUT-LEP}.
+constants to intersect at a common energy scale of $\mathcal{O}(10^{16}\,\GeV)$ \cite{GUT-LEP}.
 
@@
 one of the Higgs boson masses, conventionally chosen as \mA.
-The masses of the neutral scalars \PHiggs and \PHiggslight are the eigenvalues of 
+The masses of the neutral scalars \PHiggs and \PHiggslight are the eigenvalues  
 of $\mathcal{M}_{\text{tree}}^2$,
@@
 %\end{equation}
-A consequence of equation \ref{eqn:scalarmass} is a tree-level upper bound to the mass of the light Higgs
+A consequence of equation \ref{eqn:scalarmass} is a tree-level upper bound on the mass of the light Higgs
 boson,
@@
 
-The requirement that $m_h$ be less than the mass of the Z boson, 91.2 GeV, seems 
-problematic at first, as it is known that there is a Higgs state with a mass of 125 GeV. However,
+The requirement that $m_h$ be less than the mass of the Z boson, $91.2\,\GeV$, seems 
+problematic at first, as it is known that there is a Higgs state with a mass of $125\,\GeV$. However,
 the tree-level masses and couplings of the Higgs bosons in the MSSM can be
@@
 and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
-the choice of decay into $\Pgt\Pgt$ as search channel for the neutral Higgs bosons in the MSSM.
+the choice of decay into $\Pgt\Pgt$ as a search channel for the neutral Higgs bosons in the \ac{MSSM}.
 Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
@@
 bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
-production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, Gluon fusion production is 
+production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
 the dominant production mode at low \tanb.
@@
 A different approach, also leading to an extended Higgs sector with
-respect to the \ac{SM}, is found in the \ac{2HDM} \cite{2HDM-I,2HDM-II}.
-As the name suggests \ac{2HDM}s are a generic class of models in which
+respect to the \ac{SM}, is found in \acp{2HDM} \cite{2HDM-I,2HDM-II}.
+As the name suggests \acp{2HDM} are a generic class of models in which
 there is not one, but two Higgs doublets. The addition of a second
@@
 vector bosons and fermions are the same as the tree-level \ac{MSSM} couplings 
-from table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
+in table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
 %the \AtoZh~coupling is proportional to $\cos{(\beta-\alpha)}, like the \Htohh~coupling.
@@
 and decays into various final states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
-example of a type-II \ac{2HDM}, at two \tanb~points. Figure \ref{fig:2hdm_Hxsbr}b 
+example of a type-II \ac{2HDM}, for two values of \tanb. Figure \ref{fig:2hdm_Hxsbr}b 
 shows the inclusive cross-section times branching ratios for production and decay
@@
 low \tanb~the cross-section times branching ratios for \Htohh production and decay and \AtoZh production
-and decay are enhanced for $250\leq m_{\PHiggs}\leq 350$ GeV and $220 \leq m_{\PHiggsps} \leq 350$ GeV, respectively.
+and decay are enhanced for $250\leq m_{\PHiggs}\leq 350\,\GeV$ and $220 \leq m_{\PHiggsps} \leq 350\,\GeV$, respectively.
 
@@
 figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
-\AtoZh decays are enhanced for masses up to 350 GeV \cite{2HDM-II}.}
+\AtoZh decays are enhanced for masses up to $350\,\GeV$ \cite{2HDM-II}.}
 \label{fig:2hdm_Hxsbr}
@@
 exclusion limits from direct searches in all benchmark scenarios. The masses
-of the first and second generation squarks are set to 1.5 TeV, 
-and the masses of the first and second generation sleptons to 500 GeV. The trilinear
+of the first and second generation squarks are set to $1.5\,\TeV$, 
+and the masses of the first and second generation sleptons to $500\,\GeV$. The trilinear
 couplings of the first and second generation squarks and sleptons are taken to be 0.
@@
 is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
-was used for interpretations of MSSM Higgs boson searches at LEP, allows
+was used for interpretations of MSSM Higgs boson searches at LEP and the Tevatron, allows
 the mass of the light Higgs boson to reach the highest a-priori expected 
-value of around 135 GeV for high \mA. There is only a small area of the \mA-\tanb~plane
+value of around $135\,\GeV$ for high \mA. There is only a small area of the \mA-\tanb~plane
 in this scenario where the mass of the light Higgs boson is compatible with the
-observed 125 GeV state.  The modifications to the parameters of the $m_{h}^{\text{max}}$ 
+observed $125\,\GeV$ state. The modifications to the parameters of the $m_{h}^{\text{max}}$ 
 scenario address this issue. In the $m_{h}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
@@
 %meausrements 
-The remaining parameters are set as $\mu_{\text{MSSM}}=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
-$m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. 
+The remaining parameters are set as $\mu_{\text{MSSM}}=200\,\GeV$, $m_{\tilde{g}} = 1.5\,\TeV$,
+$m_{\tilde{\ell}_3} = 1\,\TeV$, and $A_b=A_t=A_{\Pgt}$. 
 %Figure \ref{fig:mhmodp_mh}a
@@
 The mass of the light Higgs boson in the \ac{MSSM} is said to
-be compatible with 125 GeV, if the light Higgs boson mass lies within a 
-mass window of $\pm 3$ GeV mass window around 125 GeV. This mass window
+be compatible with $125\,\GeV$, if the light Higgs boson mass lies within a 
+mass window of $\pm 3\,\GeV$ mass window around $125\,\GeV$. This mass window
 corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
@@
 scenario contains a light Higgs boson with a mass compatible with
-125 GeV. However, at low values of \tanb~this is not the case.
+$125\,\GeV$. However, at low values of \tanb~this is not the case.
 The mass of the light Higgs
@@
 figure \ref{fig:mhmodp_mh}a, illustrating that the mass 
-is not within $\pm 3$ GeV of 125 GeV at low \tanb. The low \tanb~regime can be re-opened
-if $M_{\text{SUSY}}$ is allowed to be greater than 3 TeV \cite{MSSM-reopen}. 
+is not within $\pm 3\,\GeV$ of $125\,\GeV$ at low \tanb. The low \tanb~regime can be re-opened
+if $M_{\text{SUSY}}$ is allowed to be greater than $3\,\TeV$ \cite{MSSM-reopen}. 
 %But not too large, see ref above!
@@
 the radiative corrections are tuned to obtain light 
-Higgs boson masses of around 125 GeV in most of the \mA-\tanb~plane considered.
+Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
 Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1-4 and 
-\mA~150-250 GeV, \mh~is compatible with 125 GeV.
+\mA~$150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
 
@@
 of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
-indicate masses lower than 122 GeV. The figures shows that
-the mass of the light Higgs boson is compatible with 125 GeV over a large
+indicate masses lower than $122\,\GeV$. The figures shows that
+the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
 part of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
-the mass of the light Higgs boson is compatible with 125 GeV nearly everywhere.}
+the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere.}
 \label{fig:mhmodp_mh}
@@
 %\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
-%The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
+%The mass is compatible with $125\,\GeV$ nearly everywhere \cite{MSSM-lowtanb}.}
 %\label{fig:lowtbhigh_mh}
 %\end{figure}
-To obtain \mh$\approx$125 GeV over a large part of the parameter
+To obtain \mh$\approx125\,\GeV$ over a large part of the parameter
 space, 
@@
 The hMSSM scenario \cite{hMSSM-1,hMSSM-2} uses a different approach, in
-which \mh=125 GeV by construction.
+which \mh$=125\,\GeV$ by construction.
 
-One of the assumptions of the hMSSM is that the
+One of the assumptions of the hMSSM is that 
 the mass matrix for the neutral CP-even states can
@@
 This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
-a minimum accessible \mA~of around 151 GeV for \tanb=1. In addition, the scenario
+a minimum accessible \mA~of around $151\,\GeV$ for \tanb=1. In addition, the scenario
 can be formulated, but is not strictly valid, for values of \tanb~upwards of 10 \cite{CMS-PAS-HIG-16-007}.
@@
 Searches for heavy Higgs bosons decaying to WW and ZZ are able to exclude part of the low-\tanb-region. In the 
-hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA=250-350 GeV.
+hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA=$250--350\,\GeV$.
 The red exclusion contour in figure \ref{fig:bsm_summary}b is the re-interpretation of the analysis presented in
@@
 of the high-\tanb~region, with searches for Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
-scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around 300 GeV in the 
+scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around $300\,\GeV$ in the 
 hMSSM scenario are excluded instead by constraints from \ac{SM} Higgs boson measurements (magenta). In this scenario small

### 2017-02-17 frontmatter.tex
Committing some updates before edit round 1
Adding some more of the crap at the beginning, plus editing

@@
 \end{abstract}
-%% Abstract
+
+% Abstract
 \begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
-The BLAH BLAH
   %\thispagestyle{empty}
+The \ac{CMS} detector is a general-purpose detector located at the Large Hadron
+Collider at CERN. It was designed to test the predictions of the standard model 
+and to search for the Higgs boson in addition to searches for new physics beyond
+the standard model.
+The analyses presented in this thesis are searches for neutral
+Higgs bosons with tau leptons in the final state, and use proton-proton collision data recorded
+by \acs{CMS} during 2012, 2015 and 2016. The searches are performed in the
+context of the \ac{MSSM}. One of the analyses, using $19.7\,\invfb$ collected
+during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
+decaying into two $125\,\GeV$ \ac{MSSM} Higgs bosons with \ac{SM}-like properties,
+with two b-quarks and two tau leptons in the final state. The other analyses use 
+$2.3\,\invfb$ collected during 2015 and $12.9\,\invfb$ collected during 2016, both
+at $\sqrt{s}=13\,\TeV$. These are searches for neutral \ac{MSSM}
+Higgs bosons in the mass range of $90\,\GeV$--$3.2\,\TeV$ directly decaying
+into pairs of tau leptons. 
+No significant excess is observed in any of the searches. Upper limits at 95\% confidence 
+level are set on the cross section times branching ratio for the Higgs production process
+in consideration. In addition, limits are set in the \mA-\tanb~parameter space of 
+several \ac{MSSM} benchmark scenarios, and in the \cosba-\tanb~parameter space of an example
+of a two Higgs doublet model.
+
 \end{abstract}
 
-%% Declaration
-%\begin{declaration}
-%  \vspace*{1cm}
-%  \begin{flushright}
-%  \end{flushright}
-%\end{declaration}
+% Declaration
+\begin{declaration}
+  \vspace*{1cm}
+  I declare that the work in this thesis is mine. Figures and results taken from other sources
+include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
+directly from CMS publications. The `CMS Preliminary' label indicates figures which
+have been made public via a preliminary public document or a public website, but are not
+included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
+including those made by myself, include the relevant reference in the figure caption.
+The work for the analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} was 
+carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
+For the results presented in chapter \ref{chap:hhh} I 
+was responsible for the statistical inference. This included
+the interpretation of the results in MSSM and two Higgs doublet model benchmark scenarios. The 
+work is included in Ref. \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
+I was responsible for all stages of the analysis, including the optimisation
+of object selection and event categorisation, as well as studies of background
+methods for three out of four channels presented in the final version of the analysis,
+evaluation of systematic uncertainties in all four channels, and production of the statistical
+results, including model interpretations. This work is included in the most recent
+preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
+result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
+The work presented in chapter \ref{sec:mssm_combination} has
+not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
+
+  \begin{flushright}
+  Adinda de Wit
+  \end{flushright}
+\end{declaration}
 

### 2017-02-20 Hhh/Hhh.tex
Hhh edit

--- 2017-01-30 Hhh/Hhh.tex
@@
 \label{chap:hhh}
-In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
-uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
+In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
+a pair of b-jets and the other decaying to a pair of tau leptons is discussed. In this analysis, which 
+uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
 period of the \ac{LHC}, the \etau, \mutau and \tautau final states
-of the \Pgt-pair are studied; these final states are referred to as channels. 
+of the di-tau pair are studied; these final states are referred to as channels. 
 The results of this search are model-independent
-upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
-which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
+upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
+which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
 be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
-In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
-these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
-My work focussed on checks for the \mutau and \etau channels, as well as being
-responsible for limit setting for the \Htohh analysis, and performing the model interpretations
+In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
+These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
+For these results I contributed to the analysis of the \etau and \mutau channels,
+and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
 of the \Htohh and \AtoZh analyses, plus their combination.
-Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.
+Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.
 
-The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
-new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
-generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
-of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
+The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
+new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
+generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
+of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
 the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
-of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
-of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.
+of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
+of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner \htotautau final state.
 
@@
 \label{sec:hhh_datasets}
-The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
+The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
 running period of the LHC. 
 Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
-\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
+\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
 events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
@@
 
-Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
-were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
-\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
+Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
+were generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
+ mass is $350\,\GeV$ because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
 starts to dominate beyond this mass. In all of the samples
-\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
+\texttt{TAUOLA} \cite{tauola} is used to decay the tau leptons, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
 Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
-interactions. The \ac{MC} samples are then reweighted so that the pile--up distribtuion matches the
-pile--up distribution in data.
+interactions. The \ac{MC} samples are then reweighted so that the pileup distribution matches the
+pileup distribution in data. The detector response to the final simulated particles is modelled using a \texttt{GEANT4}-based \cite{Geant4} detector simulation.
 
-To better model the \Ztautau background, an embedding technique is used. In this method, 
-\Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
-to decay the taus and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
-response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
-tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
+To better model the \Ztautau background an embedding technique is used. In this method, 
+\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
+to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
+Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
 due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
-of the two muons originiating from the \PZ have been removed. This technique is also applied to 
-a \ttbar background sample to estimate the \ttbar contamination in the embedded sample. This contribution
-needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
-avoid double counting with the \ttbar \ac{MC}.
+of the two muons originiating from the \PZ boson have been removed. This technique is also applied to 
+a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
+%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
+%avoid double counting with the \ttbar \ac{MC}.
 
@@
 \label{sec:hhh_selection}
-This section gives an overview of the event selection, a detailed description of the physics
-objecs used in this analysis is given in chapter OBJECTS.
+This section gives an overview of the event selection; a detailed description of the physics
+objecs used in this analysis is given in chapter \ref{chap:objects}.
 
@@
 The muon is required to have a \pT~of at 
-least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
-primary vertex. This means the impact parameters $d_{xy}$ and $d_{z}$ must be smaller
-than 0.045 and 0.2 cm respectively. Tight muon identification
-criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
-in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
-20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
+least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
+primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
+than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
+criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
+ are applied. The hadronic tau must have a \pT~of at least
+$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
 the decay mode finding identification
-from the HPS algorithm. Additionally
-the raw combined isolation is required to be
-at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
+from the HPS algorithm. Additionally,
+the combined isolation is required to be
+at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
 reduce the contribution of \Zmm background events, the hadronic tau is 
 also required to pass the tight working point of the anti-$\Pgm$ discriminator
-and the loose working point of the cut--based anti-$\Pe$ discriminator.
+and the loose working point of the cut-based anti-$\Pe$ discriminator.
 
-After this selection there is still a chance more than one possible 
+After this selection there is still a chance that more than one possible 
 \mutau pair exists
-in the event. If this is the case, the combination with largest 
-\pT$^{\Pgm}$ + \pT$^{\Pgt_{h}}$ is chosen. In order to reduce \Zmm 
-backgrounds further, for cases where the reconstructed hadronic tau originates
-from a misidentified jet, the event is rejected if an opposite--charge pair 
-of lower \pT (at least 15 GeV) muons, passing looser ID and isolation requirements
-than the signal muon, can be formed. Additional vetos, requiring exactly one muon and 
-exactly zero electrons to pass \pT $>10$ GeV and loose ID and isolation requirements, 
-are applied to reduce the \WZ background.
+in the event. If this is the case the combination with largest 
+\pT$^{\Pgm}$ + \pT$^{\Pgth}$ is chosen. In order to reduce the \Zmm 
+background further, in cases where the reconstructed hadronic tau originates
+from a misidentified jet, the event is rejected if an opposite-charge pair 
+of lower \pT~(at least $15\,\GeV$) muons, passing looser ID and isolation requirements
+than the signal muon, can be formed. Additional vetoes, requiring exactly one muon and 
+exactly zero electrons to pass \pT~$>10\,\GeV$ and loose ID and isolation requirements, 
+are applied to prevent overlap with other channels and to reduce the di-boson background.
 
-In addition to the requirements on the di--tau pair, at least 2 jets with \pT$ >20$ GeV are 
-required. No b--tagging requirements are applied at this stage, these will be discussed 
+In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
+required. No b-tagging requirements are applied at this stage, these will be discussed 
 in more detail in section \ref{sec:hhh_selection_categories}.
@@
 \label{sec:hhh_selection_etau}
-Events in the \etau channel are selected using a trigger which requires an electron at L1, and both an electron
-and a hadronic tau at HLT.
+Events in the \etau channel are selected using a trigger which requires an electron at \ac{L1}, and both an electron
+and a hadronic tau in the \ac{HLT}.
 The hadronic
@@
 After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
-The electron should have a \pT~of at least 24 GeV, $|\eta| < 2.1$, and should
-satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
+The electron should have a \pT~of at least $24\,\GeV$, $|\eta| < 2.1$, and should
+satisfy $d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$. The electron must pass the tight
 working point of the electron MVA ID discriminator, and the
-relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
+relative isolation is required to be $I_{\text{rel}}^{\Pe} < 0.1$. The requirements placed on the
 hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
-where the loose working point is required, and the anti--$\Pe$ discriminator, where the medium
+where the loose working point is required, and the anti-$\Pe$ discriminator, where the medium
 working point of the MVA discriminator is required.
 
-If there is more than one possible \etau pair, The pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
-is taken. Similar additional vetos as in the \mutau channel are applied.
-the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
-isolation requirements than the signal electron requirements, can be formed. To reduce the \WZ
-background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
+If there is more than one possible \etau pair, the pair with the largest \pT$^{\Pe}$+\pT$^{\Pgth}$
+is taken. Similar additional vetoes as in the \mutau channel are applied.
+The event is rejected if an opposite-charge pair of electrons with \pT~ $> 15\,\GeV$, passing looser ID and
+isolation requirements than the signal electron requirements, can be formed. To prevent overlap with other channels and to reduce the di-boson
+background, events that have more than one electron or at least one muon passing \pT~$>10\,\GeV$ and loose ID and isolation
 requirements are rejected.
 
-In addition to the requirements on the di--tau pair, at least 2 jets with \pT $>20$ GeV are 
+In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
 required.
@@
 \label{sec:hhh_selection_categories}
-In both channels a selection on the transverse mass, \mT,~between the electron/muon
+In both channels a selection on the transverse mass, \mT, between the electron or muon
 and missing transverse energy, defined as,
 \begin{equation}\label{eqn:hhh_selection_mt}
-m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})},
+m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}\,,
 \end{equation}
@@
 In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
-angle between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
+angle between this light lepton and the missing transverse energy. The \mT~distributions for the \etau
 and \mutau channels, using the selections as
@@
 \end{center}
-\caption{\mT~distributions in the \mutau (left) and \etau (right) channels}
+\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels.}
 \label{fig:Hhh_selection_mt}
@@
 
-This quantity is required to be smaller than 30 GeV in both channels. In events
-where the missing energy and the light lepton are oriented back--to--back, \mT~is
+This quantity is required to be smaller than $30\,\GeV$ in both channels. In events
+where the missing energy and the light lepton are oriented back-to-back, \mT~is
 large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
-events, as the W is very heavy, the lepton and neutrino are more likely to be emitted back--to--back,
-therefore \mT~will be large. For \Ztautau and \htotautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
-the neutrinos are more likely to travel in the same direction as the visible decay products of 
-the tau, due to the smaller mass of the \Pgt compared with the \PW. Therefore requiring the
-transverse mass to be less than 30 GeV reduces the \Wjets background. This effect
+events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back,
+therefore \mT~will be large. For \Ztautau and \htotautau events, the neutrinos in the $\tau\rightarrow\ell\nu\nu$ decay 
+ are more likely to travel in the same direction as the visible decay products of 
+the tau, due to the smaller mass of the \Pgt compared with the \PW boson. Therefore requiring the
+transverse mass to be less than $30\,\GeV$ reduces the \Wjets background. This effect
 is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
-smaller diboson and single-top backgrounds are combined into the `electroweak' background contribution, drawn in red.
+smaller di-boson and single-top backgrounds are combined into the ``electroweak'' background contribution, drawn in red.
 %In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
@@
 After applying the \mT~selection, events are divided into three categories to maximise
-sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
-(at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
+sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), 2jet-1tag 
+(at least two jets, exactly one of which is b-tagged), 2jet-2tag (at least two jets, at least two of which are b-tagged).
 Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
@@
 backgrounds, the 2jet-2tag category is the most sensitive to signal. 
-Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
+Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
 channels, illustrates this.
@@
 \end{center}
-\caption{Number of b-tagged jets in the 2-jet selection of the \mutau (left) and \etau (right) channels. The signal
-at \mH~=$300$~GeV and \tanb~=2, multiplied by a factor of 10, is overlaid on the figures.}
+\caption[Number of b-tagged jets in the two-jet selection of the \mutau and \etau channels.]{Number of b-tagged jets in the two-jet selection of the (a) \mutau and (b) \etau channels. The signal
+at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 10, is overlaid.}
 \label{fig:Hhh_selection_bjets}
@@
 
-In signal events, the di--tau pair and di--jet pair 
-are the decay products of a 125 GeV Higgs boson, therefore their invariant
-masses should be close to 125 GeV. To reduce background contributions
-from events where the di--tau or di--jet mass is not compatible with
-125 GeV, requirements are made on the di--jet invariant mass and the di--tau
+In signal events the di-tau pair and di-jet pair 
+are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
+masses should be close to $125\,\GeV$. To reduce background contributions
+from events where the di-tau or di-jet mass is not compatible with
+$125\,\GeV$, requirements are made on the di-jet invariant mass, and the di-tau
 invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
@@
 of the taus and the reconstructed \MET. The use of this algorithm greatly
-improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
-which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
-By requiring $70 < m_{jj} < 150$ GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
+improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
+which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
+By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
 large number of background events can be rejected, while retaining
@@
 \end{center}
-\caption{Reconstructed di-\Pgt invariant mass (left) and di-jet invariant mass (right) in the 2jet-2tag category of the \mutau
-channel. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in the low \tanb~ MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
-In both variables the signal peaks at around 125 GeV.}
+\caption[Reconstruced di-tau invariant mass and di-jet invariant mass in
+the 2jet-2tag category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the 2jet-2tag category of the \mutau
+channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
+The signal peaks at around $125\,\GeV$ in both variables.}
 \label{fig:Hhh_selection_masscuts}
@@
 
-\section{\acl{MC} to data correction factors}
+\section{\acl{MC} simulation to data correction factors}
 \label{sec:hhh_datamc}
 \ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
-and it is therefore important to correct for any mismodelling. The \ac{MC} to data 
+and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
 correction factors used for this are estimated in dedicated control regions.
 
-Data and \ac{MC} identification, isolation, and trigger efficiencies
-are measured for electrons, muons and hadronic taus. The difference between
-the efficiencies in data and \ac{MC} are applied to \ac{MC} events as a
-scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
+Identification, isolation, and trigger efficiencies are measured for electrons, muons
+and hadronic taus in data and simulated events.
+The difference between
+the efficiencies in data and simulated events are applied to \ac{MC} events as a
+scale factor $\text{SF} = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
 
-For electrons and muons, these efficiencies are measured using a 
-tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
+For electrons and muons these efficiencies are measured using a 
+tag-and-probe method using \Zeenog and \Zmmnog events, respectively.
 The hadronic tau identification, isolation and trigger efficiencies
 are measured via a similar method that makes use of
-$Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+$\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
 
 The energy scale for hadronic taus is determined by fitting the mass of the 
-hadronic tau candidate in $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+hadronic tau candidate in $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
 This fit is performed separately for each hadronic tau decay mode to obtain
 an energy scaling that is applied to reconstructed hadronic taus matched
-to generator-level hadronic tau decays in MC events.
+to simulated hadronic tau decays in \ac{MC} events.
 
-In the \etau channel a \ac{MC} to data scale factor is applied
-to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
-fake rate between data and \ac{MC}. This scale factor is derived separately
-for the 1-prong + 0$\pi^0$ hadronic tau decay mode, and 1-prong + at least one
-$\pi^0$ decay modes by fitting the visible mass of the \Pe+$\Pgt_{h}$ pair
+In the \etau channel a scale factor is applied
+to the \Zee background to correct for differences in the $\Pe\rightarrow\Pgth$
+fake rate between data and simulation. This scale factor is derived separately
+for the 1-prong + 0$\pi^0$ and 1-prong + at least one
+$\pi^0$ decay modes by fitting the visible mass of the \etau pair
 in events passing the selection of the \etau channel as described in section
-\ref{sec:hhh_selection_etau}, with the 2-jet requirement lifted.
+\ref{sec:hhh_selection_etau}, but with the two-jet requirement removed.
 
-Differences in \MET resolution and response between data and \ac{MC} are accounted for by
-applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter OBJECTS
+Differences in \MET~resolution and response between data and simulation are accounted for by
+applying recoil corrections to \Zellell, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
 gives more details on how these corrections are derived.
 
-To correct for the difference in b--tagging efficiency and light jet mis--tagging
-rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
-derived using the method described in ref. \cite{BTV8TeV}. There are separate scale factors for 
-b-/c- jets and light jets. Multiple possible ways to apply these scale factors
-exist, for this analysis this is done through a promote/demote method.
+To correct for the differences in b-tagging efficiency and light jet mis-tagging
+rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
+derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
+b-/c-jets and light jets. In this analysis the ``promote/demote'' method
+is used to apply these.
 
@@
 \begin{align}\label{eqn:promotedemote}
-&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
-&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1},
+&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
+&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
 \end{align}
-Where $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
-the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
+Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
+the b-tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
 under consideration.
@@
 \label{sec:hhh_discr}
-The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
-reconstructed as the 4--body mass of the two jets and the two taus; however
-a more accurate result can be obtained by using a kinematic fitting 
-procedure that makes use of the 125 GeV mass constraint on the di--tau and
-di--jet candidates.
+The variable of interest in this analysis is the mass of the heavy Higgs boson \PHiggs. This can be
+reconstructed as the four-body mass of the two jets and the two taus. 
+A more accurate result can be obtained by using a kinematic fitting 
+procedure that makes use of the $125\,\GeV$ mass constraint on the di-tau and
+di-jet candidates.
 
@@
 case of this analysis these constraints are
-$m(\Pgt_{1},\Pgt_{2}) = m_{h} = 125 $~GeV and
-$m(b_{1},b_{2}) = m_{h} = 125 $ GeV.
+$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
+$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
 The kinematic observables related to the hadronic taus and jets
@@
 
-Before the fit, from the mass constraint we have:
+Before the fit, the mass constraint gives:
 ~\vspace{-0.5\baselineskip}
 \begin{align}\label{eqn:kinfit_prefit}
-m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
-& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
-& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
-&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}.
+m_{\PHiggslight}^2 &= E_{\PHiggslight}^2 - \vec{p_{\PHiggslight}}^2 = (E_{\Pbottom 1}+E_{\Pbottom 2})^2 - (\vec{p_{\Pbottom 1}} + \vec{p_{\Pbottom 2}})^2 \notag\\
+& = 2E_{\Pbottom 1}E_{\Pbottom 2} + m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2\vec{p_{\Pbottom 1}}\vec{p_{\Pbottom 2}} \notag\\
+& = m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
+&\Rightarrow (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}}) = \frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2 - m_{\Pbottom 2}^2}{2E_{\Pbottom 1}E_{\Pbottom 2}}.
 \end{align}
 When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
-rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
+rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})$ 
 and
@@
 \begin{equation}\label{eqn:gamma_def}
-\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}.
+\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2},
 \end{equation}
-We get:
+we get:
 ~\vspace{-0.5\baselineskip}
 \begin{align}\label{eqn:kinfit_variation}
-m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}})\notag\\
-&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
-\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
-&= - E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
-&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}})
+m_{\PHiggslight}^2 &= m_{\Pbottom 1}^2 + m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
+&= m_{\Pbottom 1}^2 +\frac{E_{\Pbottom 2,\text{fit}}^2}{\gamma_{\Pbottom 2}^2} +2\mathcal{A}E_{\Pbottom 1}E_{\Pbottom 2,\text{fit}}\notag\\
+\Rightarrow E_{\Pbottom 2}^{\text{fit}}& = \frac{(-2E_{\Pbottom 1}\mathcal{A} + \sqrt{4E_{\Pbottom 1}^2\mathcal{A} - 4(m_{\Pbottom 1}^2-m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^{-2}})\gamma_{\Pbottom 2}^2}{2}\notag\\
+&= - E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2+\sqrt{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^4 - (m_{\Pbottom 1}^2 - m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^2}\notag\\
+&\Rightarrow E_{\Pbottom 2}^{\text{fit}} = E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2(-1 + \sqrt{1+\frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2}{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^2}}).
 \end{align}
@@
 \begin{equation}\label{eqn:kinfit_bjetmass}
-m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}.
+m_{\Pbottom_{1,2}}^{\text{fit}} = m_{\Pbottom{1,2}}\frac{E_{\Pbottom{1,2}}^{\text{fit}}}{E_{\Pbottom{1,2}}}.
 \end{equation}
-The $\chi^2$ term for each b-jet is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.
+The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$.
 
-For taus only the visible decay products are measured. Assuming the visible decay products of the \Pgt point in 
-the same direction as the original \Pgt, a similar procedure as for the b-jets can be employed to constrain the mass of the second tau
-when varying the mass of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.
+For taus only the visible decay products are measured. Assuming these point in 
+the same direction as the original tau, a similar procedure as for the b-jets can be employed to constrain the energy of the second tau
+when varying the energy of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.
 
-Due to the missing energy associated with the \Pgt decays, additional constraints
+Due to the missing energy associated with the tau decays, additional constraints
 on the fit have to be used to reconstruct the correct tau energies. This is done by 
@@
 \begin{equation}\label{eqn:kinfit_recoilmeas}
-\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
+\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 1}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilfit}
-\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}.
+\vec{p_{\text{T,recoil}}}^{\text{fit}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{fit}} = - \vec{p_{\text{T},\Pbottom 1}}^{\text{fit}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_1}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_2}}^{\text{fit}}.
 \end{equation}
-A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
+A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_recoilchi2}
-\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
+\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}}),
 \end{equation}
-where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
-the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET as discussed in the
-OBJECTS section,
+where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as 
+\begin{equation}\label{eqn:kinfit_recoilcov}
+V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
+\end{equation}
+ from the covariance matrices of the b-jets and
+the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
 while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
-~\vspace{-0.5\baselineskip}
-\begin{equation}\label{eqn:kinfit_recoilcov}
-V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
-\end{equation}
 The total $\chi^2$ term that needs to be minimised in the fit can then be written as
@@
 \begin{equation}\label{eqn:kinfit_chitot}
-\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}.
+\chi^2 = \chi^2_{\Pbottom 1} + \chi^2_{\Pbottom 2} + \chi^2_{\text{recoil}}.
 \end{equation}
-The results of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
+The results of the kinematic fit are the tau and b-jet four-vectors with their energies and momenta
 set to the best fit values found for them in the fit. These can then be added together to find
@@
 
-As illustrated in figure \ref{fig:kinfitvsmjj} the use of the kinematic fit greatly
-improves the resolution of the reconstructed heavy Higgs mass in signal events, when 
-compared with the simple 4-body mass reconstruction. It also shifts the mean of the
+As illustrated in figure \ref{fig:kinfitvsmjj}a the use of the kinematic fit greatly
+improves the resolution of the reconstructed heavy Higgs boson mass in signal events, when 
+compared with the simple four-body mass reconstruction. It also shifts the mean of the
 distribution closer to the true value. It is also insightful to make such a comparison
 for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
-shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between 4-body mass and
-kinematic fit mass for \ttbar events is shown on the right hand side of figure 
-\ref{fig:kinfitvsmjj}. From this figure we can see that the mass distribution for
-background events is affected less by the kinematic fit, although due to the
+shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between four-body mass and
+kinematic fit mass for \ttbar events is shown in figure 
+\ref{fig:kinfitvsmjj}b. From this figure we can see that the mass distribution for
+background events is less affected by the kinematic fit, although due to the
 invariant mass constraint the minimum of the reconstructed mass distribution
-is forced to 250 GeV.
+is forced to $250\,\GeV$.
 
@@
 \end{center}
-\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
-4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $~GeV (left) and \ttbar background events (right) in 
+\caption[Comparison of the reconstructed heavy Higgs boson mass
+using the kinematic fit in signal events with $m_{\PHiggs}=300\,\GeV$ and \ttbar 
+background events in the 2jet-1tag category of the \mutau channel.]{Comparison of the reconstructed heavy Higgs boson mass using the kinematic fit (blue) and
+four-body mass without use of the kinematic fit (black) in (a) signal events with $m_{\PHiggs} = 300\,\GeV$ and (b) \ttbar background events in 
 the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
@@
 \label{sec:hhh_backgrounds}
-To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
+To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
 used where possible. 
@@
 described in section \ref{sec:hhh_datasets}. To estimate the 
-yield of \Ztautau in each category, the total
-yield after the initial event selection (before subdividing into categories) as
-estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
+yield of \Ztautau in each category the total
+yield after the initial event selection, before subdividing into categories, as
+estimated in the \Ztautau \ac{MC} sample is scaled by the efficiency with which 
 such events pass the category selection in the embedded sample. The shape of
 the \Ztautau background is taken from the embedded sample after applying the full
-category selection. The contamination from \ttbar backgrounds in the embedded
-sample is accounted for by subtracting this contamination, as evaluated using
-the dedicated \ttbar embedded samples, from the \Ztautau background.
+category selection. The contamination from the \ttbar background in the embedded
+sample is evaluated using the dedicated \ttbar embedded sample. This contribution
+is subtracted from the \Ztautau background.
 \subsection{\texorpdfstring{\ttbar}{ttbar}}
 Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
-These are checked against data in dedicated control regions, one such control
-region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
-this control region and applied to the yield estimate from \ac{MC} in the signal region. 
+These are checked against data in dedicated control regions. One such control
+region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
+this control region and applied to the yield estimate from simulation in the signal region. 
+%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
 \subsection{\texorpdfstring{\Wjets}{W + jets}}
@@
 The \Wjets background is greatly reduced by requiring \mT~to
-be less than 30 GeV. To estimate the remaining contribution
-from \Wjets in the signal region a sideband with \mT~greater
-than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
+be less than $30\,\GeV$. To estimate the remaining contribution
+in the signal region a sideband with \mT~greater
+than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
 Contributions from other backgrounds are subtracted 
-from the data in this region, and a high-\mT~to low- \mT~
-extrapolation factor is determined from the \Wjets \ac{MC} 
-samples. The yield in the signal region is given by the data yield in the high-\mT sideband, with
+from the data in this region, and a high-\mT~to low-\mT~extrapolation
+ factor is determined from the \Wjets \ac{MC} 
+sample. The yield in the signal region is given by the data yield in the high-\mT~sideband, with
 other backgrounds subtracted, multiplied by this extrapolation factor.
-In the 2jet-2tag category, a slightly different high-\mT~sideband of 60-120 GeV is used 
-to give more events for the \Wjets estimate after other backgrounds are
-subtracted. The method of extrapolating this yied estimate into
+In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
+as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
+The method of extrapolating this yield estimate into
 the signal region is otherwise analogous.
 
-The shape of the \Wjets distribution is taken from the \ac{MC} samples. To 
+The shape of the \Wjets distribution is taken from the simulation. To 
 increase the number of events for this estimate, the b-tagging definition
-in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
+in the 2jet-1tag and 2jet-2tag categories is relaxed from the medium to the loose 
 working point for the purposes of shape estimation.
-\subsection{QCD}
+\subsection{QCD multijet}
 \label{sec:hhh_backgrounds_qcd}
-A fully data-driven method is used to estimate the QCD background. Data events
-passing the signal region selection cuts, but with di-\Pgt candidates of
-the same sign, are used for this. The contributions from other backgrounds
-in this same--sign region are subtracted from the number of data events obtained.
-As the contribution from opposite- and same-sign QCD are
-not exactly the same an OS/SS ratio is applied to the same--sign region data with other backgrounds subtracted.
-The OS/SS ratio is measured using data with the 
-the electron/muon isolation requirements inverted.
+A fully data-driven method is used to estimate the QCD background. Here, di-tau candidates
+of the same sign, which otherwise pass the signal region selection, are used. 
+The contributions from other backgrounds
+in this same-sign (SS) region are subtracted from the number of data events obtained.
+As the contributions from opposite-sign (OS) and same-sign QCD are
+not exactly the same an OS/SS ratio is applied to the same-sign region data yield with other backgrounds subtracted.
+The OS/SS ratio is measured using data with 
+the electron or muon isolation requirements inverted.
 
@@
 category the number of available events is too low for this, so another sideband is defined
-in which the electron/muon isolation requirement is inverted. This 
+in which the electron or muon isolation requirement is inverted. This 
 sideband is then used to determine an extrapolation factor from events
-with 2 jets to events passing the 2jet-2tag category selection. This extrapolation
-factor is then applied to a QCD estimate as described above, but using the 2-jet 
+with two jets to events passing the 2jet-2tag category selection. This extrapolation
+factor is then applied to a QCD estimate as described above, but using the two-jet 
 selection only, to obtain the yield in the 2jet-2tag category.
 
-The shapes in all categories are taken from same-sign data with the electron/muon
+The shapes in all categories are taken from same-sign data with the electron or muon
 isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
 inverting the light lepton isolation requirements, the category definition
-is loosened to obtain the shapes. For the purposes of QCD shape
-estimation, jets are considered b-tagged if they pass a looser b-tagging
-working point than the working point used elsewhere in the analysis.
+is relaxed to obtain the shapes. For the purposes of QCD shape
+estimation, jets are considered b-tagged if they pass the loose b-tagging
+working point.
 \subsection{Other backgrounds}
@@
 The remaining backgrounds of \Zellell, di-boson and single-top
-events are small. Both shape and normalisation are
+events are small. Both shapes and normalisations are
 estimated using \ac{MC} samples.
@@
 Two types of systematic uncertainties are considered: normalisation
-uncertainties (which affect only the yield of a process), and shape
-uncertainties (which affect both the yield of a process and the shape of its kinematic fit mass distribution). Section \ref{sec:hhh_results_extraction}
+uncertainties and shape uncertainties. Normalisation uncertainties affect only
+the yield of a process, while shape uncertainties affect both the yield of a process and the 
+shape of its kinematic fit mass distribution. 
+Section \ref{sec:hhh_results_extraction}
 describes how these uncertainties are taken into account in the final result.
@@
 2012. This uncertainty is applied to all processes in which
-the normalisation is estimated using MC samples.
+the normalisation is estimated using simulation.
 \subsubsection*{Identification, isolation and trigger efficiencies}
-A systematic uncertainty due to the uncertainty on the efficiency measurements
-for the leptons is derived by combining the uncertainties on these measurements
-in quadrature. For electrons and muons this leads to a 2\% uncertainty, for hadronic taus a 6\% 
-uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
-the \Pgt legs of the triggers \cite{CMS-HIG-14-034}. The identification, isolation and trigger efficiency measurement uncertainties are applied to all processes for which
-the normalisation is estimated using MC samples.
-\subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
-The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
-$\mu\rightarrow\Pgt$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\mu\rightarrow\Pgt$
-fake rate is close to 1, which is why it is not applied, but the uncertainty is 
+A systematic uncertainty on the efficiency measurements
+for the leptons is derived by combining the separate uncertainties on these measurements
+in quadrature. For electrons and muons this leads to a 2\% uncertainty. For hadronic taus a 6\% 
+uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3\% for
+the tau legs of the triggers \cite{CMS-HIG-14-034}. The identification, isolation and trigger efficiency measurement uncertainties are applied to all processes for which
+the normalisation is estimated using simulation.
+\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates}
+The uncertainty on both the $\Pe\rightarrow\Pgth$ fake rate measurement and the
+$\Pgm\rightarrow\Pgth$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\Pgm\rightarrow\Pgth$
+fake rate correction is close to 1, which is why it is not applied, but the uncertainty is 
 taken into account.
-\subsubsection*{B-tag scale factors}
-The b-tag scale factors are varied within their uncertainties, as described in ref. \cite{cms-btag-paper}, to determine the effect
+\subsubsection*{b-Tag scale factors}
+The b-tag scale factors are varied within their uncertainties, as described in reference \cite{cms-btag-paper}, to determine the effect
 on the yields of each process. Both a b-tagging uncertainty and a light jet mis-tagging
@@
 change when the scale factors are varied within their uncertainty. The b-tagging
-efficiency uncertainty amounts to 1-10\% for most processes in most categories, except for the 2jet-2tag
-category where a 70\% uncertainty applies to the W background. Due to the nature
-of the estimation method, where other backgrounds are subtracted from the data to 
-obtain a W estimate, and the presence of large amounts of \ttbar, a 10\% change in the \ttbar
-yield can vary the W yield by such large amounts.
-The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.
-\subsubsection*{\MET resolution and response}
-Uncertainties on the \MET resolution and response are estimated by varying
+efficiency uncertainty amounts to $1$--$10$\% for most processes in most categories, except for the 2jet-2tag
+category where a 70\% uncertainty applies to the \Wjets background. 
+This uncertainty is large because in this category there is a significant amount of \ttbar in the 
+control region used for the \Wjets estimate. A 10\% change in the \ttbar yield causes the \Wjets
+yield to vary by this amount.
+The light jet mis-tagging rate uncertainty varies between $1$--$5$\% for all processes in all channels.
+\subsubsection*{\MET~resolution and response}
+Uncertainties on the \MET~resolution and response are estimated by varying
 the recoil correction parameters within their estimated uncertainties. This 
-leads to a 1-10\% uncertainty, depending on category and process considered \cite{CMS-HIG-14-034}.
+leads to a $1$--$10$\% uncertainty, depending on the category and process considered.
 \subsubsection*{Background normalisation}
 \begin{itemize}
-\item \Ztautau : the normalisation of the embedded samples has a 3.3\% uncertainty \cite{CMS-HIG-14-034}, which is derived
+\item \Ztautau : The inclusive normalisation of the embedded samples has a 3.3\% uncertainty, which is derived
 from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples.
-In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
-\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\% \cite{CMS-HIG-14-034}.
-\item \ttbar: the uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
-\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\% \cite{SMHtautauCMS}.
-\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry \cite{CMS-HIG-14-034}.
+In addition, an uncertainty of $5$--$6$\% for extrapolation from the inclusive selection to the category selection is applied.
+\item \Zellell: As this is a very small background after requiring two jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between $20$--$90$\%.
+\item \ttbar: The uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
+\item Di-boson and single top: The combined uncertainty on the di-boson and single-top cross sections is 15\% \cite{SMHtautauCMS}.
+\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region.
+The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.
 \item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio.
-This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category \cite{CMS-HIG-14-034}.
+This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a $60$--$100$\% uncertainty in the 2jet-2tag category.
 \end{itemize}
@@
 \subsubsection*{Tau energy scale}
-The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty \cite{SMHtautauCMS}.
+The energy of hadronically decaying taus is varied up and down by a 3\% uncertainty \cite{SMHtautauCMS}.
 As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.
 \subsubsection*{Jet energy scale}
-The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty \cite{cms-jec-2011}.
+The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT-and $\eta$-dependent uncertainty \cite{cms-jec-2011}.
 Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.
@@
 In this section a summary of the \AtoZhtolltautau analysis \cite{CMS-HIG-14-034}, which is combined with the 
-analysis described so far for the purposes of model interpretations, is given.
+analysis described so far for the purpose of model interpretations, is given.
 
 The search for \AtoZhtolltautau also uses the full dataset collected by the CMS experiment during
-the 2012 $p-p$ running period of the LHC. In this search the \mumu and \ee final states of the \PZ boson
+the 2012 p-p running period of the \ac{LHC}. In this search the \mumu and \ee final states of the \PZ boson
 and the \emu, \etau, \mutau and \tautau channels of the \htotautau decay are considered, leading to a total of
@@
 First the \PZ candidate is chosen as a pair of isolated electrons or muons, with opposite charge, and 
-invariant mass of the pair between 60-120 GeV. If there is more than one possible pair, the 
-pair with invariant mass closest to the \PZ mass is chosen. The \htotautau decay is chosen by selecting
-an oppositely charged pair of isolated particles in the four channels mentioned earlier. To ensure no overlap
+invariant mass between $60$--$120\,\GeV$. If there is more than one possible pair, the 
+pair with invariant mass closest to the \PZ boson mass is chosen. The \htotautau decay is chosen by selecting
+an oppositely charged pair of isolated particles in the four channels mentioned above. To ensure no overlap
 between different final states is possible, events with additional electrons or muons satisfying the
@@
 To reject some of the backgrounds from misidentified leptons and \ZZ production, a requirement is made
-on the scalar sum of the visible transverse momenta of the two $\tau$ candidates from the \htotautau decay.
+on the scalar sum of the visible transverse momenta of the two tau candidates from the \htotautau decay.
 This selection changes by final state and has been chosen to optimise the analysis sensitivity to an 
-\AtoZh signal with \mA $= 220 - 350 $ GeV. Furthermore \ttbar events are discarded by rejecting
+\AtoZh signal with \mA~$= 220$--$350\,\GeV$. Furthermore, \ttbar events are discarded by rejecting
 events with at least one b-tagged jet.
 
-Remaining backgrounds from \ZZ, triboson and \ttbar\PZ production are estimated using
-\ac{MC} samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
-and \WZ+jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
+Remaining backgrounds from \ZZ, tri-boson and \ttbar+\PZ production are estimated using
+simulation. Backgrounds from $\PZ+$jets %($\ell\ell\tautau$ channel) 
+and $\WZ+$jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
 events, with at least one misidentified lepton, are estimated from control regions in data.
 
-For signal extraction, the mass of the A boson \mA~is used. This mass is reconstructed by combining the
-4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate as obtained by using the 
-\texttt{SVFit} algorithm. The expected and observed 95\% confidence level upper limits, for
-all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}
+For signal extraction the mass of the \PHiggsps boson, \mA, is used. This mass is reconstructed by combining the
+four-vector of the \PZ boson candidate with the four-vector of the \PHiggslight candidate as obtained by using the 
+\texttt{SVFit} algorithm. The expected and observed 95\% \ac{CL} upper limits, for
+all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}.
 
@@
 \includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
-\caption{The 95\% confidence level expected (dashed) and observed (solid)
-upper limits on the $\sigma \times BR$ for the \AtoZhtolltautau process.
-The green and yellow bands indicate the $\pm 1 \sigma $ and $2\sigma$
+\caption[The 95\% confidence level expected and observed upper limits on the 
+\xsbr for the \AtoZhtolltautau process.]{The 95\% confidence level expected (dashed) and observed (solid)
+upper limits on the \xsbr for the \AtoZhtolltautau process.
+The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$
 expectations \cite{CMS-HIG-14-034}.}
@@
 Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
-For the purposes of combining the results with the \Htohhtobbtautau search,
+For the purpose of combining the results with the \Htohhtobbtautau search,
 some of these are correlated between the two analyses.
@@
 \label{sec:hhh_results_extraction}
-The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable in this analysis.
-For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
+The kinematic fit mass $m_{\PHiggs}^{\text{kinfit}}$ is used as the discriminating variable in the \Htohh analysis.
+For each channel and category the compatibility of the $m_{\PHiggs}^{\text{kinfit}}$ distribution
 of the observed data with the expected background distribution can be assessed. All bins
-of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
-statistical methods used were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
+of the $m_{\PHiggs}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
+statistical methods used are recommended by the LHC Higgs Combination Group \cite{LHCHComb2011} 
 and are used for all Higgs analyses in ATLAS and CMS.
@@
 \end{equation}
-
 where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given by
@@
 \end{equation}
+with $n_i$ the number of 
+data events in bin $i$.
 
-with $n_i$ the number of 
-data events, whether observed or pseudo-data, in bin i.
-
-The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
-in all channels and categories. $s$ represents the number of expected signal events
+The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
+in all channels and categories. The parameter $s$ represents the number of expected signal events
 in each bin, and $b$ the number of expected background events. These are functions of 
@@
 signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
-to 1 pb, so the signal strength modifier represents
-the cross-section $\times$ branching ratio of a possible signal.
+to $1\,\picobarn$, so the signal strength modifier represents
+the \xsbr of a possible signal.
 
-The second term in equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
+The second term in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
 probability density functions of the uncertainties on the nominal
@@
 as discussed in section \ref{sec:hhh_uncs}. The functional form of the probability density function
-depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
-For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
-uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
-an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
-yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
+depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
+ensures that the process yields can never become negative, and therefore unphysical, in the fit. 
+%For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
+%uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
+%an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
+%yields do not become negative. 
+Shape uncertainties are accounted for using a vertical template morphing
 technique \cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
 templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
-parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
+parameter is added to the likelihood model with a gaussian constraint to smoothly interpolate between
 the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
 are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
-shape template is allowed to float within its statistical uncertainty, independent of the other bins. These
-variations are controlled by log-normal constraints in the likelihood function.
+shape template is allowed to vary within its statistical uncertainty, independent of the other bins. %These
+%variations are controlled by log-normal constraints in the likelihood function.
 
@@
 \begin{equation}\label{eqn:hhh_profilelikelihood}
-q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}.
+q_{\mu} = -2\text{ln}\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})},
 \end{equation}
 
-Where we require $0 \leq \hat{\mu} \leq \mu$.
+where $0 \leq \hat{\mu} \leq \mu$ is required for setting upper limits.
 
-In this equation $\mu$ is the signal strenght modifier being tested, $\hat{\theta_{\mu}}$ denotes the values of the
+In this equation $\mu$ is the signal strength modifier being tested, $\hat{\theta_{\mu}}$ denotes the values of the
 nuisance parameters which maximise the likelihood for that particular $\mu$, while $\hat{\mu}$ and $\hat{\theta}$ are
-the values of signal strength modifier and nuisance parameters which give the global maximum of the likelihood.
-The requirements on $\mu$ ensure that the signal strength is non-negative ($ 0 \leq \hat{\mu}$) and that
+the values of the signal strength modifier and the nuisance parameters which give the global maximum of the likelihood.
+The requirements on $\mu$ ensure that the signal strength is non-negative and that
 a one-sided confidence interval is constructed so as not to allow the observation of  a 
-signal with strength $\hat{\mu} > \mu$ to cause rejection of the signal hypothesis ($ \hat{\mu} \leq \mu$).
+signal with strength $\hat{\mu} > \mu$ to cause rejection of the signal hypothesis.
 
-The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
+The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal-plus-background hypothesis
 and assuming the background-only hypothesis, are given by
@@
 where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
-the signal+background and background-only hypotheses.
+the signal-plus-background and background-only hypotheses.
 
-Using this, $CL_s$ is defined as
+Using this, $\text{CL}_s$ is defined as
 \begin{equation}\label{eqn:hhh_cls}
-CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}.
+\text{CL}_s(\mu) = \frac{\text{CL}_{s+b}}{\text{CL}_b} = \frac{p_{\mu}}{1-p_b}.
 \end{equation}
 
-The value of $\mu$ for which $CL_s$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
-confidence level $1-\alpha$. Upper limits at the LHC are generally
-quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
+The value of $\mu$ for which $\text{CL}_s$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
+\acf{CL} $1-\alpha$. Upper limits at the LHC are generally
+quoted at 95\% \ac{CL}. %, therefore the upper limit on cross-section times branching ratio
 %for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
 %equals 0.05. The use of $CL_s$ to set
-The use of $CL_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.
+The use of $\text{CL}_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.
 
@@
 using toy MC datasets. These datasets are generated from the signal-plus-background or background-only expectations respectively. 
-For each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to observed data.
-The number of events in each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
+To generate each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to the observed data.
+The number of events in each bin in the toy dataset is set using poisson fluctuations around the expectation in that bin, and the effect of
 systematic uncertainties is taken into account by sampling a set of pseudo measurements $\tilde{\theta}'$ for each toy, based on the 
-pdf $p(\tilde{\theta}|\theta)$.
-The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal-plus-background or background-only)
+probability density function $p(\tilde{\theta}|\theta)$.
+The probability density function of $q_{\mu}$ under the relevant hypothesis (signal-plus-background or background-only)
 can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.
 
-This method of generating toy MC datasets is computationally intensive.
-In the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
+This method of generating toy MC datasets can be computationally intensive.
+In the limit of a large number of events $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
 This formula, known as the asymptotic approximation, allows for the calculation
-of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
-the properties of the Asimov dataset; a dataset in which the observation in 
+of the observed limit as well as the median and $\pm 1\sigma$ and $\pm 2\sigma$ expected limits using
+the properties of the Asimov dataset: a dataset in which the observation in 
 each bin exactly matches the predictions of the model. This method is used for the analysis
@@
 
-The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to the
+The $m_{\PHiggs}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to the
 observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
@@
 \end{center}
-\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \mutau channel. The \Htohhtobbtautau signal for \mA $= 300 $~GeV at \tanb=2 in the low \tanb~MSSM
-scenario, multiplied by 10, is also overlaid. Note that at low \tanb \mA$\neq$\mH, ~\mH~ at the point
-in the MSSM scenario considered is around 316 GeV.}
+\caption[Distributions of $m_{\PHiggs}^{\text{kinfit}}$ in the 2jet-0tag,
+2jet-1tag and 2jet-2tag categories of the \mutau channel.]{Distributions of $m_{\PHiggs}^{\text{kinfit}}$ in the (a) 2jet-0tag, (b) 2jet-1tag and (c) 2jet-2tag categories 
+of the \mutau channel. The \Htohhtobbtautau signal for \mA~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM
+scenario, multiplied by 10, is also overlaid. Note that at low \tanb~\mA$\neq$\mH, at the point in the MSSM scenario
+that is considered \mH~is around 
+around $316\,\GeV$.}
 \label{fig:hhh_results_mhkinfit_mutau}
@@
 \end{center}
-\caption{Distributions of $m_{H}^{\text{kinfit}}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
-of the \etau channel. The \Htohhtobbtautau signal for \mA $ = 300 $~GeV at \tanb=2 in the low \tanb~ MSSM
-scenario, multiplied by 10, is also overlaid. Note that at this low value of \tanb \mA$\neq$ \mH, in 
-this case \mH is around 316 GeV.}
+\caption[Distributions of $m_{\PHiggs}^{\text{kinfit}}$ in the 2jet-0tag,
+2jet-1tag and 2jet-2tag categories of the \etau channel.]{Distributions of $m_{\PHiggs}^{\text{kinfit}}$ in the (a) 2jet-0tag, (b) 2jet-1tag and (c) 2jet-2tag categories 
+of the \etau channel. The \Htohhtobbtautau signal for \mA~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM
+scenario, multiplied by 10, is also overlaid. Note that at this low value of \tanb~\mA$\neq$ \mH, in 
+this case \mH~is around $316\,\GeV$.}
 \label{fig:hhh_results_mhkinfit_etau}
@@
 
-None of these distributions show hints of an excess. The model-independent 95\% CL expected and observed upper limits
-on cross-section times branching ratio are shown in the left-hand side 
-panel of figure \ref{fig:hhh_results_modelindep}, with the right-hand side of the same figure
+None of these distributions show hints of an excess of observed events above the background expectation. 
+The model-independent 95\% \ac{CL} expected and observed upper limits
+on \xsbr are shown in 
+figure \ref{fig:hhh_results_modelindep}a, with figure \ref{fig:hhh_results_modelindep}b 
 showing the expected limit per channel. These figures include the contribution from the 
 \tautau channel not described in this chapter. The expected upper limit
-on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
-from 0.2 pb at low mass to 0.4 pb at high mass. We can
-see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
+on the \Htohhtobbtautau process is around $0.3\,\picobarn$, the observed ranges
+from $0.2\,\picobarn$ at low mass to $0.4\,\picobarn$ at high mass. 
+The \mutau channel is the most sensitive at masses lower than $320\,\GeV$, with 
 the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
@@
 \subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
-\caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
-for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034} (left).
-The right hand side panel shows the expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau
+\caption[Expected and observed 95\% CL upper limits on 
+\xsbr for the \Htohhtobbtautau process.]{Expected and observed 95\% \ac{CL} upper limits on \xsbr  
+for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.
+(b) Shows the expected 95\% \ac{CL} upper limits on \xsbr for the \Htohhtobbtautau
 process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
-for the \etau channel and the black line the limit for all three channels combined. Up to around \mH$= 320$~GeV the \mutau channel is the most
+for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
 sensitive, with the \tautau channel being more sensitive at higher masses.}
@@
 \label{sec:hhh_results_modeldep}
-The results of the analysis are interpreted in two scenarios, the low \tanb~MSSM
-scenario, and a type II two--Higgs doublet model (2HDM), both discussed in chapter \ref{chap:theory}.
+The results of the analysis are interpreted in two scenarios, a type-II \ac{2HDM} and the low-\tanb~MSSM
+scenario, both discussed in chapter \ref{chap:theory}.
 
-\subsubsection{Interpretation in a type II 2HDM}
+\subsubsection{Interpretation in a type-II 2HDM}
 \label{sec:hhh_results_modeldep_2HDM}
-As we have seen in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
+As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
 free parameters than a particular \ac{MSSM} benchmark scenario. To leave
 just two free parameters, it is enough to fix the masses of the five Higgs bosons
-and take the quartic couplings to be 0.
-For the interpretation shown here the assumption that \mA=\mH=\mHplus=$300$ GeV is made.
+and take the quartic couplings to be zero.
+For the interpretation shown here the assumption that \mA=\mH=\mHplus~$=300\,\GeV$ is made.
 
@@
 \begin{center}
-\caption{Couplings in the type II 2HDM}
+\caption{Couplings in the type-II 2HDM}
 \begin{tabular}{@{}ll@{}}
@@
 \midrule
-$\PHiggslight \rightarrow$ up--type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
-$\PHiggslight \rightarrow$ down--type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
+$\PHiggslight \rightarrow$ up-type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
+$\PHiggslight \rightarrow$ down-type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
 $\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
@@
 
-The interpretations are made in the \cosba--\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
-shows the observed and expected exclusion at 95\% confidence level for the \Htohh
-and \AtoZh analyses, overlaid on the production cross--section times branching ratio.
+The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
+shows the observed and expected exclusion at 95\% \ac{CL} for the \Htohh
+and \AtoZh analyses, overlaid on the \xsbr.
 The exclusion contours have some interesting features, most of which can be explained by the couplings
-from table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
-of all particles are exactly standard model--like. This is reflected in the \Htohh and \AtoZh branching ratios, 
-which both vanish as \cosba~approaches 0. This leads to the corridor of non--exclusion down the 
-centre of the plots in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
-as the coupling of the \PHiggslight to pairs of b--quarks or $\Pgt$ leptons is porportional 
+in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
+of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
+which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
+centre of the graphs in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
+as the coupling of the \PHiggslight to pairs of b-quarks or tau leptons is proportional 
 to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
-and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non--exclusion
+and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non-exclusion
 at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
-to become visible in the $\sigma \times BR$ structure of the \Htohh interpretation, but
-the analysis is not yet sensitive enough to actually observe this corridor.
+to become visible in the \xsbr structure of the \Htohh interpretation, but
+the analysis is not yet sensitive enough to actually observe it.
 %Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
@@
 \subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZh2HDM.pdf}}
-\caption{Search for \Htohhtobbtautau (left) and \AtoZhtolltautau (right) interpreted in a type II 
-2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
-and observed (solid line) exclusion contours at 95\% confidence level are overlaid
-on the cross--section times branching ratio of the searched-for process.
-Regions of the \cosba-\tanb~plane where the cross--section times branching
-ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
+\caption[Search for \Htohhtobbtautau and search for \AtoZhtolltautau
+interpreted in a type-II 2HDM, assuming \mA=\mH=\mHplus~$=300\,\GeV$.]{Search for (a) \Htohhtobbtautau and (b) \AtoZhtolltautau interpreted in a type-II 
+\ac{2HDM}, assuming \mA=\mH=\mHplus~$= 300\,\GeV$. The expected (dashed line)
+and observed (solid line) exclusion contours at 95\% \ac{CL} are overlaid
+on the \xsbr of the searched-for process.
+Regions of the \cosba-\tanb~plane where the 
+\xsbr is larger than the model-independent upper limit set for $m_{\PHiggs} = 300\,\GeV$ 
 (see figures \ref{fig:AZhUpperLimits} and \ref{fig:hhh_results_modelindep}) are excluded.}
@@
 A combined interpretation of both analyses in this model is presented
-in the left-hand side panel of figure \ref{fig:HhhAZhMSSM2HDM}. Some of the features discussed earlier
+in figure \ref{fig:HhhAZhMSSM2HDM}a. Some of the features discussed earlier
 in this section are also visible in this combined interpretation.
 
-\subsubsection{Interpretation in the low \tanb~MSSM scenario}
+\subsubsection{Interpretation in the low-\tanb~MSSM scenario}
 \label{sec:hhh_results_modeldep_lowtb}
-The low \tanb~MSSM scenario, as discussed in section \ref{sec:mssm_theory_lowtb}
-is an MSSM scenario that has been adapted to allow \mh $=125 \pm 3$~GeV for \tanb~values
+The low-\tanb~MSSM scenario, as discussed in section \ref{sec:mssm_theory_lowtb},
+is an \ac{MSSM} scenario that has been adapted to allow \mh~$=125 \pm 3\,\GeV$ for \tanb~values
 as low as 1.
 
-The left-hand side panel of figure \ref{fig:HhhAndAZhlowtanb} shows the cross-section times branching ratio
-of the \Htohhtobbtautau process in the low \tanb~ MSSM scenario. Comparing these values 
+Figure \ref{fig:HhhAndAZhlowtanb}a shows the \xsbr 
+of the \Htohhtobbtautau process in the low-\tanb~MSSM scenario. Comparing these values 
 to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} we 
-can see that the cross-section times branching ratio in this model is, with the exception of a few very small 
+can see that the \xsbr in this model is, with the exception of a few very small 
 areas, lower than the upper limits set by this analysis. This analysis on its own is,
 therefore, not sensitive enough to exclude any of the \mA-\tanb~region in this model. Note that
-at low \tanb, \mA$\neq$ \mH, and therefore \mH~is not in the studied range of $260-350$ GeV
-throughout the entire \mA-\tanb~plane shown here.
+at low \tanb, \mA$\neq$ \mH, and therefore \mH~is not in the studied range of $260$--$350\,\GeV$
+everywhere in the \mA-\tanb~plane shown here.
 
 The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb~region
-in this model by itself. The expected and observed 95\% CL exclusion contours are overlaid 
-on the cross-section times branching ratio for this process in the low \tanb~MSSM scenario in the right-hand side panel 
-of figure \ref{fig:HhhAndAZhlowtanb}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
-near \mA $ = 350$ GeV arises from the fact that near this mass the decay $\PHiggsps \rightarrow t\bar{t}$ becomes
+in this model. The expected and observed 95\% \ac{CL} exclusion contours are overlaid 
+on the \xsbr for this process in the low-\tanb~MSSM scenario in  
+figure \ref{fig:HhhAndAZhlowtanb}b. The sharp drop in \xsbr, and therefore exclusion,
+near \mA~$ = 350\,\GeV$ arises from the fact that near this mass the decay $\PHiggsps \rightarrow \Ptop\APtop$ becomes
 kinematically allowed, resulting in a reduction of the \AtoZh branching ratio.
@@
 \subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}}
-\caption{Cross-section times branching ratio of the \Htohhtobbtautau process (left) and of the
-\AtoZhtolltautau process (right) in the low-\tanb ~MSSM scenario. On the right-hand side
-plot the expected and observed 95\% CL exclusion limits for the \AtoZhtolltautau analysis in the low \tanb ~MSSM scenario
-have been overlaid on the cross-section times branching ratio. Areas where the cross-section times branching
-ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits} are excluded. The exclusion rapidly drops
-off at $m_A = 350$ GeV due to the turn-on of the $\PHiggsps \rightarrow$ \ttbar process.
+\caption[\xsbr of the \Htohhtobbtautau
+process and the \AtoZhtolltautau process in the low-\tanb ~MSSM scenario. The
+expected and observed 95\% CL exclusion limits for the \AtoZhtolltautau analysis
+in the low \tanb~MSSM scenario have been overlaid.]{The \xsbr of (a) the \Htohhtobbtautau process and (b) the
+\AtoZhtolltautau process in the low-\tanb~MSSM scenario. In (b) 
+the expected and observed 95\% \ac{CL} exclusion limits for the \AtoZhtolltautau analysis in the low-\tanb~MSSM scenario
+have been overlaid on the \xsbr. Areas where the 
+\xsbr is larger than the upper limits in figure \ref{fig:AZhUpperLimits} are excluded. The exclusion rapidly drops
+off at \mA~$ = 350\,\GeV$ due to the turn-on of the $\PHiggsps \rightarrow$ \ttbar process.
 No expected and observed exclusion contours
-have been overlaid on the lef-hand side plot as the cross-section times branching
-ratio is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
+have been overlaid on (a) as the 
+\xsbr is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
 \label{fig:HhhAndAZhlowtanb}
@@
 
-The combined interpretation of both analyses in this model is presented in the right-hand side panel of
-figure \ref{fig:HhhAZhMSSM2HDM}.
+The combined interpretation of both analyses in this model is presented figure 
+\ref{fig:HhhAZhMSSM2HDM}b.
 %The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
 %very sensitive in this model. 
-Combining the two analyses we do see that a slightly larger amount
+By combining the two analyses a slightly larger amount
 of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
-described for the plot on the right-hand-side of figure \ref{fig:HhhAndAZhlowtanb} are also visible in this figure. In a small region of phase
-space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
+described for the figure \ref{fig:HhhAndAZhlowtanb}b are also visible in this figure. In a small region of phase
+space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with $125\pm3\,\GeV$.
 This region is therefore excluded, as indicated by the red band.
@@
 \subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
-\subfloat[low \tanb ~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
-\caption{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
-interpreted in a type II 2HDM assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV (left) and interpreted
-in the low \tanb ~MSSM scenario (right). The shaded blue area bounded by
-the solid black line indicates the observed excluded region at 95\% confidence level.
+\subfloat[low-\tanb~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
+\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
+interpreted in a type-II 2HDM and in the low-\tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
+interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
+(b) in the low-\tanb~MSSM scenario. The shaded blue area bounded by
+the solid black line indicates the observed excluded region at 95\% \ac{CL}.
 The dashed black line indicates the expected exclusion, with the grey bands showing
-the $\pm 1\sigma$ and $2\sigma$ expected exclusion \cite{CMS-HIG-14-034}. The area
-bounded by the red line is the region of phase space where \mh $\neq 125 \pm 3$ 
-GeV and is therefore excluded.}
+the $\pm 1\sigma$ and $\pm2\sigma$ expected exclusion \cite{CMS-HIG-14-034}. The area
+bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$
+ and is therefore excluded.}
 \label{fig:HhhAZhMSSM2HDM}

### 2017-02-20 frontmatter.tex
Hhh edit

@@
 carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
-For the results presented in chapter \ref{chap:hhh} I 
+For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
+final states presented in the final public result, and I 
 was responsible for the statistical inference. This included

### 2017-02-20 MSSM/MSSM.tex
Editing some obvious things out of MSSM chapter

@@
 In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
-decaying to a pair of \Pgt leptons will be discussed. The results presented
+decaying to a pair of tau leptons will be discussed. The results presented
 here correspond to those from an analysis peformed on a dataset collected
-during the first half of the 2016 p--p running period of the \ac{LHC}. This dataset
-corresponds to an integrated luminosity of 12.9 fb$^{-1}$, and the analysis is
-detailed in Ref. \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
-states of the di-\Pgt pair were studied. The results of this search are 
-model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
-production in the gluon fusion (gg$\phi$) and b-associated (bb$\phi$) production 
+during the first half of the 2016 p-p running period of the \ac{LHC}. This dataset
+corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
+detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
+states of the di-tau pair were studied. The results of this search are 
+model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
+production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
 modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
-In addition to the upper limits on cross--section times branching ratio of these two processes, 
-the results are interpreted in MSSM benchmark scenarios.
+In addition to the upper limits on \xsbr of these two processes, 
+the results are interpreted in \ac{MSSM} benchmark scenarios.
 A very similar analysis, not described in detail here,
-was performed on a dataset corresponding to 2.3 fb$^{-1}$ collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period.  
+was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
 More information can be found in reference \cite{CMS-PAS-HIG-16-006}.
@@
 The dataset used for this analysis corresponds to an integrated 
-luminosity of 12.9 fb$^{-1}$ collected at a centre--of--mass
-energy of 13 TeV during the first half of
-the 2016 p--p running period of the \ac{LHC}. %Section
+luminosity of $12.9\,\invfb$ collected at a centre-of-mass
+energy of $13\,\TeV$ during the first half of
+the 2016 p-p running period of the \ac{LHC}. %Section
 %\ref{sec:mssm_combination} includes the combination of this
@@
 various \ac{MC} event generators. Signal samples
-for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow b\bar{b}\phi$
-production processes of $\PHiggs/\PHiggsps$ were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
-These samples were produced for a range of masses between 90 GeV and 3.2 TeV.
+for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\APbottom\phi$
+production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
+These samples were produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
 This range is slightly wider than the range in which MSSM Higgs sector
-benchmark computations are available, 90 GeV -- 2 TeV, and 
-improves on the mass range of 90 GeV to 1 TeV that was studied during Run 1 in the context of BSM Higgs searches.
-SM Higgs signal samples are used for the interpretation of the analysis results in 
-MSSM benchmark scenarios. These samples are generated using \texttt{Powheg} \cite{powheg1,powheg2,powheg3}.
+benchmark computations are available, $90\,\GeV$--$2\,\TeV$, and 
+improves on the mass range of $90\,\GeV$ to $1\,\TeV$ that was studied during Run 1 in the context of \ac{BSM} Higgs searches.
+\ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
+\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{Powheg} \cite{powheg1,powheg2,powheg3}.
 
 Single-top and \ttbar background samples are generated using \texttt{Powheg},
-with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di--boson background
+with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
 samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
@@
 fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
-only included in the \emu channel, is generated in part with \texttt{MadGraph 5} and in
+only included in the \emu channel, are generated in part with \texttt{MadGraph 5} and in
 part with \texttt{MadGraph5\_aMC@NLO}.
@@
 Parton showering and hadronisation are modelled using \texttt{PYTHIA 8.1} for all 
-samples, and  minimum--bias events generated with \texttt{PYTHIA 8.1} are
+samples, and  minimum-bias events generated with \texttt{PYTHIA 8.1} are
 added to all \ac{MC} samples to model additional interactions. A reweighting
-is then applied to the \ac{MC} samples to make the pile--up distribution match
-the pile--up distribution observed in data.
+is then applied to the \ac{MC} samples to make the pileup distribution match
+the pileup distribution observed in data.
 
@@
 on how the objects used are reconstructed, 
-and a more in--depth description of the identification criteria, 
+and a more in-depth description of the identification criteria, 
 is given in chapter \ref{chap:objects}.
@@
 While the lepton + hadronic tau cross triggers that are also available
-allow for a 3 (6) GeV lower \pT~threshold on the
-muon (electron), the benefit of using such a trigger is small as 
-most of the signals at high-mass, the region of interest in this
+allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
+muon (electron), the benefit of using such a trigger is small: 
+most of the signals at high mass, the region of interest in this
 analysis, have higher \pT~electrons and muons. This is illustrated
 in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
-\mutau channel, with the signal normalised to 4000 times its cross--section
-times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod}+}$ scenario overlaid.
+\mutau channel, with the signal normalised to 4000 times its \xsbr 
+ at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario overlaid.
 In the \emu channel two dedicated electron-muon cross triggers
@@
 hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
-on the hadronic taus in the \tautau channel is 5 GeV above the trigger \pT~threshold.
+on the hadronic taus in the \tautau channel is $5\,\GeV$ above the trigger \pT~threshold.
 In addition, a requirement is made on the $\eta$ of the electrons, muons and
@@
 originated from the primary vertex. This reduces the number of selected particles
-which come from pile--up interactions.
+which come from pileup interactions.
 Additional identification and isolation criteria
@@
 the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
-corresponds to an integrated luminosity of 2.3 fb$^{-1}$.
+corresponds to an integrated luminosity of $2.3\,\invfb$.
 
@@
 and $\eta$ of the electron in the \etau channel, with the signal
-overlaid.]{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
+overlaid.]{(a) The \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
 The gluon fusion (dashed blue line)
 and b-associated (dashed purple line) signals are overlaid. The signals are normalised to 4000 times their
-cross-section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod+}}$ scenario.}
+\xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.}
 \label{fig:mt_muonpt}
@@
 if there are muons and electrons, other than those in the selected pair,
-with \pT~$>10$ GeV and passing loose ID and isolation requirements.
-This also reduces backgrounds from \WZ events. The application
+with \pT~$>10\,\GeV$ and passing loose ID and isolation requirements.
+This also reduces backgrounds from di-boson events. The application
 of these vetos means that the selection of the pair with the
@@
 the event would not pass the electron (muon) veto.
-In addition to these extra electron and muon vetos, \Zee events are 
+In addition to these extra electron and muon vetoes, \Zee events are 
 reduced in the \etau channel by rejecting events
-where an opposite--sign pair of electrons of \pT~$>15$ GeV
+where an opposite-sign pair of electrons of \pT~$>15\,\GeV$
 and passing very loose ID and isolation requirements can be formed. 
@@
 The offline event selection requires an oppositely charged
-muon and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
-The minimum \pT~of the muon is required to be 23 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+muon and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
+The minimum \pT~of the muon is required to be $23\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
 Additional ``medium'' identification requirements are placed on the muon, and the impact
-parameters of the muon must satisfy $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm. The muon is also
+parameters of the muon must satisfy $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$. The muon is also
 required to be isolated, with $I_{\text{rel}}^{\mu}<0.15$, where the isolation variable
@@
 
-The hadronic tau needs to have a \pT~greater than 30 GeV, $|\eta|<2.3$,
+The hadronic tau needs to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
 is required to be reconstructed by the HPS algorithm and to pass the medium
 working point of the MVA isolation discriminator. The impact parameter $d_{z}$ is
-required to be less than 0.2 cm. Finally the hadronic tau is required
-to satisfy the very loose working point of the anti--electron discriminator
-and the tight working point of the anti--muon discriminator.
+required to be less than $0.2\,\cm$. Finally the hadronic tau is required
+to satisfy the very loose working point of the anti-electron discriminator
+and the tight working point of the anti-muon discriminator.
 
@@
 the isolation selection that maximises it. The second figure of merit
-is the uncertainty interval on the best-fit value for a maximum--likelihood fit
+is the uncertainty interval on the best-fit value for a maximum-likelihood fit
 to the \Ztautau signal strength, which should be minimised by the choice of
@@
 is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
-size of the error interval from the maximum--likelihood fit to the \Ztautau signal strength shown in 
+size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
 \ref{fig:mssm_selection_mt_muons}b. As both figures of merit do not
@@
 \caption[The $S/\sqrt{B}$ for \Ztautau signal and
-the size of the error interval on the best--fit value of a
-maximum--likelihood fit to the \Ztautau signal strength, for various 
+the size of the error interval on the best-fit value of a
+maximum-likelihood fit to the \Ztautau signal strength, for various 
 isolation selections.]{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
-the best--fit value of a maximum--likelihood fit to the \Ztautau signal strength,
-for various selections of the $\Delta\beta$--corrected
+the best-fit value of a maximum-likelihood fit to the \Ztautau signal strength,
+for various selections of the $\Delta\beta$-corrected
 isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
-the $\Delta\beta$--corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
-the $\Delta\beta$--corrected isolation variable including electrons and muons in the isolation
+the $\Delta\beta$-corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
+the $\Delta\beta$-corrected isolation variable including electrons and muons in the isolation
 sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
-the tracker--based relative isolation (solid squares).}
+the tracker-based relative isolation (solid squares).}
 \label{fig:mssm_selection_mt_muons}
@@
 choice of hadronic tau isolation working point provide two competing
-effects and therefore they are optimised in a 2D--optimisation. 
-The pre--fit expected upper limits on $\sigma\times$BR for both gg$\phi$ and bb$\phi$
+effects and therefore they are optimised in a 2D-optimisation. 
+The pre-fit expected upper limits on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
 production with decay into $\Pgt\Pgt$ at several mass points 
-in the 90 GeV -- 3.2 TeV range are used as a figure of merit.
+in the $90\,\GeV$--$3.2\,\TeV$ range are used as a figure of merit.
 Because of the use of such a wide range of signal masses, it
@@
 for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
-figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on $\sigma\times$BR for
-the gluon fusion production process, for a mass $m_{\phi} = 160$ GeV, with
-figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9$ TeV.
+figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on \xsbr for
+the gluon fusion production process, for a mass $m_{\phi} = 160\,\GeV$, with
+figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9\,\TeV$.
 Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
-tau isolation working point selection on both the gg$\phi$ and bb$\phi$ production processes.
+tau isolation working point selection on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.
 
@@
 \end{center}
-\caption[Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$
+\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
 production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
-working point and \mT~selection, for two mass points.]{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
+working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$ production process with decay into $\Pgt\Pgt$,
 as a function of tau isolation working point (from very loose to very very tight) and
-of \mT~selection from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
-for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
+of \mT~selection from \mT~$<20\,\GeV$ to \mT~$<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
 hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
-\end{center}
-\caption[Pre-fit expected limits on $\sigma \times$ BR for the gg$\phi$ and bb$\phi$
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
+\end{center}
+\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
 processes
@@
 \mutau channel for an increasingly looser \mT~selection and tau isolation
-working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
-(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
-at the tight working point and \mT$<30$ GeV in green, the medium working point and \mT$<40$ GeV in red,
-the loose working point and \mT$<50$ GeV in blue and the very loose working point and \mT$<60$ GeV in black. Loosening
+working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
+(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
+at the tight working point and \mT~$<30\,\GeV$ in green, the medium working point and \mT~$<40\,\GeV$ in red,
+the loose working point and \mT~$<50\,\GeV$ in blue and the very loose working point and \mT~$<60\,\GeV$ in black. Loosening
 the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
@@
 
-From these figures
-we observe that looser selections are preferred for higher masses. This behaviour can be
+These figures show that looser selections are preferred for higher masses. This behaviour can be
 explained by considering the function of each of the selections. Tightening the hadronic
@@
 the \Wjets background. As the backgrounds are concentrated at the lower
-end of the spectrum of mass--like discriminating variables, such tighter
+end of the spectrum of mass-like discriminating variables, such tighter
 selections are preferred where signal and backgrounds overlap. For higher masses the
@@
 to reduce an already low background.
-The selection was optimised for masses around 800 GeV - 1 TeV, by
-using the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.
+The selection was optimised for masses around $800\,\GeV$--$1\,\TeV$, by
+using the medium hadronic tau isolation working point and a selection on \mT~$<40\,\GeV$.
 
 The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
-raising the \pT~selection by 10 GeV from the minimum of 20 GeV does not affect the sensivity
+raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensivity
 of the analysis for high mass points, while recovering some of the loss of loosening 
-tau isolation working point and \mT~cut. The reason for this is that when using \pT$>30$ GeV 
+tau isolation working point and \mT~cut. The reason for this is that when using \pT~$>30\,\GeV$ 
 fewer background events are selected. The effect of the increased hadronic tau \pT~selection on the 
-upper limits for the gg$\phi$ production process is shown
-in figure \ref{fig:mssm_tauptcut}a, and on the bb$\phi$ production process
-in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the gg$\phi$ limits
-obtained by increasing the \pT~selection is sizeable, for bb$\phi$ events the effect is much
+upper limits for the $\Pg\Pg\phi$ production process is shown
+in figure \ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
+in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
+obtained by increasing the \pT~selection is sizeable, for $\Pbottom\Pbottom\phi$ events the effect is much
 less pronounced.
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
-\end{center}
-\caption[Pre-fit expected limits on $\sigma\times$BR in the
-\mutau channel for gg$\phi$ and bb$\phi$ prouduction, comparing
-different hadronic tau \pT~cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
-limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
-hadronic tau \pT~selection of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
+\end{center}
+\caption[Pre-fit expected limits on \xsbr in the
+\mutau channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production, comparing
+different hadronic tau \pT~cuts.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
+limits when using the medium hadronic tau isolation working point and \mT~$<40\,\GeV$ selection using a minimum
+hadronic tau \pT~selection of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
 circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
-the gg$\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
-the effect on the bb$\phi$ production process is less pronounced.}
+the $\Pg\Pg\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
+the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
 \label{fig:mssm_tauptcut}
@@
 The offline event selection requires an oppositely charged
-electron and hadronically decaying tau, which are well--separated ($\Delta R > 0.5$).
-The minimum \pT~of the electron is required to be 26 GeV, with $|\eta| < 2.1$. %due to trigger conditions
+electron and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
+The minimum \pT~of the electron is required to be $26\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
 The impact parameters of the electron are required to satisfy
-$d_{xy} < 0.045$ cm and $d_{z} < 0.2$ cm, and the electron
+$d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$, and the electron
 must pass additional identification criteria. The working point of the
@@
 
-The hadronic tau is required to have a \pT~greater than 30 GeV, $|\eta|<2.3$,
+The hadronic tau is required to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
 and is required to be reconstructed by the HPS algorithm and to pass the medium
 working point of the MVA isolation discriminator. The impact parameter $d_{z}$ of the
-hadronic tau must be less than 0.2 cm.
+hadronic tau must be less than $0.2\,\cm$.
 Finally, the hadronic tau must 
-pass the tight working point of the anti--electron discriminator
-and the loose working point of the anti--muon discriminator.
+pass the tight working point of the anti-electron discriminator
+and the loose working point of the anti-muon discriminator.
 
@@
 A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
-The value of \mT~$< 50$ GeV that is used is obtained by performing a 2D optimisation where the \mT~selection
+The value of \mT~$< 50\,\GeV$ that is used is obtained by performing a 2D optimisation where the \mT~selection
 and hadronic tau isolation working point are varied at the same time. The same considerations as
 for the \mutau channel apply, as illustrated in figure \ref{fig:mssm_gradcuts_et}.
-The choice of the hadronic tau \pT~selection of 30 GeV is
+The choice of the hadronic tau \pT~selection of $30\,\GeV$ is
 made to recover some of the sensitivity lost at low mass by using looser \mT~and hadronic
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
-\end{center}
-\caption[Pre-fit expected limits on $\sigma\times$ BR in the \etau
-channel for gg$\phi$ and bb$\phi$ production for an increasingly
-looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
-(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
-at the tight working point and \mT$<40$ GeV in green, the medium working point and \mT$<50$ GeV in red,
-the loose working point and \mT$<60$ GeV in blue and the very loose working point and \mT$<70$ GeV in black. Loosening
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
+\end{center}
+\caption[Pre-fit expected limits on \xsbr in the \etau
+channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production for an increasingly
+looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ and
+(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
+at the tight working point and \mT~$<40\,\GeV$ in green, the medium working point and \mT~$<50\,\GeV$ in red,
+the loose working point and \mT~$<60\,\GeV$ in blue and the very loose working point and \mT~$<70\,\GeV$ in black. Loosening
 the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
-\end{center}
-\caption[Pre-fit expected limits on $\sigma\times$BR in the \etau
-channel for gg$\phi$ and bb$\phi$ production comparing different
-hadronic tau isolation cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
+\end{center}
+\caption[Pre-fit expected limits on \xsbr in the \etau
+channel for $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ production comparing different
+hadronic tau isolation cuts.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
 limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
-hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
+hadronic tau \pT~cut of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
 circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
-the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
-the effect on the bb$\phi$ production process is less pronounced.}
+the $\Pg\Pg\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
+the effect on the $\Pbottom\Pbottom\phi$ production process is less pronounced.}
 \label{fig:mssm_tauptcut_et}
@@
 The offline event selection requires both hadronic taus to be oppositely charged, separated
-by $\Delta R > 0.5$, have \pT~of at least 40 GeV and satisfy $|\eta|<2.1$. Both taus need
-to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than 0.2 cm.
+by $\Delta R > 0.5$, have \pT~of at least $40\,\GeV$ and satisfy $|\eta|<2.1$. Both taus need
+to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than $0.2\,\cm$.
 Both taus need to pass the tight working point of the isolation discriminator, the very loose 
-working point of the anti--electron discriminator and the loose working point of the anti--muon discriminator. 
+working point of the anti-electron discriminator and the loose working point of the anti-muon discriminator. 
 The tight working point of the isolation discriminator is chosen such that
-the channel is near-optimal at high mass, while not losing too much sensitivity in the low-intermediate mass range.
-This is illustrated in figure \ref{fig:mssm_tauid_tt} for the gg$\phi$ process.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
-\end{center}
-\caption[Expected upper limits for the gg$\phi$ and bb$\phi$ process
+the channel is near-optimal at high mass, while not losing too much sensitivity in the low--intermediate mass range.
+This is illustrated in figure \ref{fig:mssm_tauid_tt} for the $\Pg\Pg\phi$ process.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
+\end{center}
+\caption[Expected upper limits for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ process
 in the \tautau channel, comparing different hadronic tau isolation working
-points.]{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
+points.]{Expected upper limits for (a) the $\Pg\Pg\phi$ process and (b) the $\Pbottom\Pbottom\phi$ process 
 in the \tautau channel, using the 
@@
 Offline, the electron and muon are required to be oppositely charged
-and separated by $\Delta R >$0.3.
-The electron needs to have a minimum \pT~of 13 GeV and have $|\eta|< 2.5$. As
+and separated by $\Delta R >0.3$.
+The electron needs to have a minimum \pT~of $13\,\GeV$ and have $|\eta|< 2.5$. As
 in the \etau channel the electron's impact parameters have to 
-satisfy $d_{xy} < 0.045$ cm and $d_{z}<0.2$ cm. The additional
+satisfy $d_{xy} < 0.045\,\cm$ and $d_{z}<0.2\,\cm$. The additional
 identification requirement is identical to the criterium applied to electrons in the \etau channel.
@@
 
-The muon needs to have a \pT~of at least 10 GeV, $|\eta|<2.4$ and 
-its impact parameters need to be $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm.
+The muon needs to have a \pT~of at least $10\,\GeV$, $|\eta|<2.4$ and 
+its impact parameters need to be $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$.
 In addition to the kinematic requirements the muon must
@@
 
-Because a combination of triggers is used, one with electron \pT~$>$ 23 GeV and muon \pT~$>8$ GeV
-and one with muon \pT~$>$ 23 GeV and electron \pT~$>$ 13 GeV, the object firing
+Because a combination of triggers is used, one with electron \pT~$> 23\,\GeV$ and muon \pT~$>8\,\GeV$ 
+and one with muon \pT~$> 23\,\GeV$ and electron \pT~$> 13\,\GeV$, the object firing
 the higher \pT~trigger leg needs to have a transverse momentum
-of at least 24 GeV on top of the requirements already discussed. This avoids
+of at least $24\,\GeV$ on top of the requirements already discussed. This avoids
 events in the lower part of the trigger turn-on curve being selected.
@@
 \ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
-for \emu events. The selection used, $D_{\zeta} > -20$ GeV, rejects $\ttbar$, \Wjets and diboson
+for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and diboson
 events. 
@@
 As the analysis targets both the gluon fusion
-and the b--associated production modes, 
+and the b-associated production modes, 
 the sensitivity to the signal can be increased by categorising
-based on the number of b--tagged jets in the event.
+based on the number of b-tagged jets in the event.
 
@@
 \subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
-\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
+\subfloat[Number of b-tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
 \end{center}
 \caption[Number of jets and number of b-tagged jets in the \mutau channel, 
-with the signal overlaid.]{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
-blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
-are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
-scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
+with the signal overlaid.]{(a) Number of jets and (b) number of b-tagged jets in the \mutau channel. The gluon fusion signal (dashed
+blue line) and b-associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
+are normalised to 100 times their \xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$
+scenario. It is visible how the signal-sensitive bins motivate the choice of categories.}
 \label{fig:mssm_cats_mt}
@@
 in the \mutau channel, with figure \ref{fig:mssm_cats_mt}b showing
-the number of b--tagged jets in that channel. The gluon fusion
-and b--associated signals are overlaid on these distributions, normalised
-to 100 times their cross--section times branching ratio at \mA=1 TeV and 
-\tanb=50 in the $m_{\text{h}}^{\text{mod+}}$ scenario. From the distribution of the
+the number of b-tagged jets in that channel. The gluon fusion
+and b-associated signals are overlaid on these distributions, normalised
+to 100 times their \xsbr at \mA~$=1\,\TeV$ and 
+\tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. From the distribution of the
 gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
 see that the vast majority of these signal events do not have any b-tagged jets. To
-target this production mode we can use a category which requires 0 b-tagged jets.
-From the b--associated signal in the same figure we also see that the majority of bb$\phi$
+target this production mode we can use a category which requires zero b-tagged jets.
+From the b-associated signal in the same figure we also see that the majority of $\Pbottom\Pbottom\phi$
 signal events do not have any b-tagged jets either: either the b-jets in these events 
 are too soft, or they do not pass the b-tagging requirements. This means that the category
-which requires 0 b-tagged jets
-is also sensitive to some of the bb$\phi$ signal. To target
-the bb$\phi$ signal, we then define another category with at least one b-tagged jet. 
-From the bb$\phi$ signal in figure \ref{fig:mssm_cats_mt}b we can also see that there is not
-such a large proportion of events with more than 1 b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
-we see that the \ttbar background starts to become more sizeable for events with more than
-one jet. The definition of the category that targets the bb$\phi$ signal is therefore chosen with the inclusion
+which requires zero b-tagged jets
+is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal. To target
+the $\Pbottom\Pbottom\phi$ signal, another category with at least one b-tagged jet is defined. 
+From the $\Pbottom\Pbottom\phi$ signal in figure \ref{fig:mssm_cats_mt}b it can be seen that there is not
+such a large proportion of events with more than one b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
+it is visible that the \ttbar background starts to become more sizeable for events with more than
+one jet. The definition of the category that targets the $\Pbottom\Pbottom\phi$ signal is therefore chosen with the inclusion
 of the jet veto, such that the region where the \ttbar background becomes larger is excluded, 
-while retaining a large proportion of the bb$\phi$ signal.
+while retaining a large proportion of the $\Pbottom\Pbottom\phi$ signal.
 
@@
 \setlength{\itemsep}{-\baselineskip}
-\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal.
-\item \textbf{B-tag}: At least 1 b--tagged jet, at most 1 
-jet with \pT$>30$ GeV. This second requirement, the jet veto, reduces the \ttbar background. 
+\item \textbf{No b-tag}: zero b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
+\item \textbf{b-Tag}: At least one b-tagged jet, at most one 
+jet with \pT~$>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
 Due to the different phase space considered for
-b--tagging than for default jet reconstruction this requirement does not necessarily
-mean there will be only one b--tagged jet in the event.
+b-tagging than for default jet reconstruction this requirement does not necessarily
+mean there will be only one b-tagged jet in the event.
 \end{itemize}
@@
 to the \mT~defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
-The \mTtot~variable provides good separation between signal and QCD multi--jet events
+The \mTtot~variable provides good separation between signal and QCD multijet events
 in the \etau, \mutau and \tautau channels, and between
@@
 background in the no b-tag category of the \tautau channel with the gluon fusion
-signal at 400 GeV, 1 TeV and 2 TeV overlaid. Figure \ref{fig:mttot_sigseps}b
+signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$ overlaid. Figure \ref{fig:mttot_sigseps}b
 shows the total transverse mass distribution of the \ttbar background in the b-tag category of the \emu channel with
@@
 of the \emu channel, for \ttbar and b-associated signal.]{Total transverse mass distributions in (a) the no b-tag category of the \tautau
-channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
-category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
+channel, for QCD and gluon fusion signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$ overlaid and (b) in the b-tag
+category of the \emu channel, for \ttbar and b-associated signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$. 
 The total transverse mass variable separates the signal and these backgrounds well.}
@@
 A discrepancy between the track reconstruction efficiency
-in data and \ac{MC} for electrons and muons was found. It is corrected for using $\eta$--dependent
+in data and \ac{MC} for electrons and muons was found. It is corrected for using $\eta$-dependent
 scale factors.% \cite{CMS-PAS-HIG-16-037}.
@@
 Identification and isolation efficiencies in data and \ac{MC} are measured
-for electrons, muons and hadronic taus. A tag--and--probe
+for electrons, muons and hadronic taus. A tag-and-probe
 method using \Zeenog (\Zmmnog) events is used to measure
 the efficiencies for electrons (muons). The hadronic tau identification
-and isolation efficiency is measured using a tag--and--probe method
-making use of $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
+and isolation efficiency is measured using a tag-and-probe method
+making use of $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
 \subsubsection*{Trigger efficiency}
 The electron, muon and hadronic tau trigger efficiencies are also measured
-using tag--and--probe methods with the types of events as described for the identification
+using tag-and-probe methods with the types of events as described for the identification
 and isolation efficiencies. Because no trigger simulation is applied to
 the \ac{MC} samples, the efficiency $\epsilon_{\text{Data}}$ is simply applied
-to the \ac{MC} events. Because two electron/muon cross--triggers are 
+to the \ac{MC} events. Because two electron-muon cross triggers are 
 used to select events in the \emu channel, the efficiencies of the different
@@
 minimum \pT~of
-23 GeV on the muon leg and 12 GeV on the electron leg, and the
-other having a minimum \pT~of 23 GeV on the electron leg and 8 GeV on the muon
+$23\,\GeV$ on the muon leg and $12\,\GeV$ on the electron leg, and the
+other having a minimum \pT~of $23\,\GeV$ on the electron leg and $8\,\GeV$ on the muon
 leg, the combined efficiency of the two triggers becomes:
@@
 \end{equation}
-\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
-The $\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rates,
-after applying the anti--electron and anti--muon discriminators, are measured
-using a tag--and--probe method with \Zeenog and \Zmmnog events. Scale
+\subsubsection*{$\Pe\rightarrow\Pgth$ fake rate and $\Pgm\rightarrow\Pgth$ fake rate}
+The $\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates,
+after applying the anti-electron and anti-muon discriminators, are measured
+using a tag-and-probe method with \Zeenog and \Zmmnog events. Scale
 factors, applied to \ac{MC} events where the tau is faked by an electron or muon,
@@
 about these corrections is given in section \ref{sec:objects_met_recoilcorr}.
-\subsubsection*{B-tag scale factors}
-To correct for the difference in b--tagging efficiency
-and light jet mis--tagging rates between data and \ac{MC} events,
+\subsubsection*{b-Tag scale factors}
+To correct for the difference in b-tagging efficiency
+and light jet mis-tagging rates between data and \ac{MC} events,
 \pT- and $\eta$-dependent scale factors are derived as 
 described in reference \cite{cms-btag-run2}. They 
-are applied using the promote--demote method
+are applied using the promote-demote method
 as outlined in equation \ref{eqn:promotedemote}.
-\subsubsection*{Top-quark \pT~reweighting}
-A reweighting which was derived during \ac{LHC} Run-1
+\subsubsection*{Top quark \pT~reweighting}
+A reweighting which was derived during \ac{LHC} Run 1
 to better match the top quark \pT~distribution in \ac{MC}
 to that observed in data is applied to \ttbar events. Despite
-the fact that the correction was derived during Run-1, it still
+the fact that the correction was derived during Run 1, it still
 improves the data/\ac{MC} agreement in a \ttbar enriched
 control region in the \emu channel, defined as 
-\MET>80 GeV and $D_{\zeta}<-20$ GeV. The improvement in data/\ac{MC} agreement
+\MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$. The improvement in data/\ac{MC} agreement
 by applying the top quark \pT~reweighting is illustrated in figure \ref{fig:mssm_corrs_toppt}.
@@
 \begin{center}
-\subfloat[Without top-quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notoppt.png}}
-\subfloat[With top-quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
+\subfloat[Without top quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notoppt.png}}
+\subfloat[With top quark \pT~reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
 \end{center}
 \caption[\mTtot~distribution in the \ttbar
-enriched control region, with and without applying top quark \pT~reweighting.]{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,
+enriched control region, with and without applying top quark \pT~reweighting.]{\mTtot~distribution in the \ttbar enriched control region \MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$ in the \emu channel,
 (a) without applying top quark \pT~reweighting and (b) with top quark \pT~reweighting.
-The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
+The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross section uncertainty.}
 \label{fig:mssm_corrs_toppt}
@@
 do not model the data well for events with high di-lepton
-mass and high Z \pT, a reweighting is applied to correct for this.
+mass and high \PZ boson \pT, a reweighting is applied to correct for this.
 These weights are derived in bins of $\PZ/\Pphotonx$ mass and \pT~
@@
 \end{center}
-\caption[The mismodelling in the \PZ \pT~distribution as observed
+\caption[The mismodelling in the \PZ boson \pT~distribution as observed
 in \Zmm events, and the impact of applying the Drell-Yan shape reweighting
-on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mismodelling in the \PZ \pT~distribution as observed
+on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mismodelling in the \PZ boson \pT~distribution as observed
 in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
@@
 is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
-it has two real taus in the final state, like the signal that we are searching for. 
+it has two real taus in the final state, like the signal being searched for. 
 Smaller backgrounds 
@@
 might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
-Production of QCD multijet events, labelled `QCD' on the plots in figure \ref{fig:mssm_bkgs_overview}, is a background when 
+Production of QCD multijet events, labelled `QCD' on the graphs in figure \ref{fig:mssm_bkgs_overview}, is a background when 
 two jets are misreconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
@@
 The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
-as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW decays into $\Pgt\Pgn$ with the tau 
+as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW boson decays into $\Pgt\Pgn$ with the tau 
 decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
@@
 that it is more correct to split a background process
-into different sub--processes that should be treated separately in the fit to data.
+into different sub-processes that should be treated separately in the fit to data.
 Taking the \mutau 
-channel as an example, a sample of Drell--Yan events
+channel as an example, a sample of Drell-Yan events
 will contain \Ztautau events, where one of the taus decays
@@
 where a jet mimics a hadronic tau. In such cases dividing
-events from the same production process into sub--samples
+events from the same production process into sub-samples
 based on generator information allows for a more correct
@@
 
-To determine the generator--level particle
+To determine the generator-level particle
 that a reconstructed electron, muon, or hadronic tau
@@
 from tau decays; and generator-level hadronic taus. These generator-level
-hadronic taus are rebuilt by summing the four--momenta
+hadronic taus are rebuilt by summing the four-momenta
 of the visible decay products of the generator-level tau.
@@
 generator-level particles in the cone at all it is said to 
-have originated from pile--up or a jet at generator level.
-
-The generator--level object type matched to a 
+have originated from pileup or a jet at generator level.
+
+The generator-level object type matched to a 
 reconstructed particle is used to perform the splitting
@@
 The estimates of the normalisations of the two backgrounds are tied
-together due to the presence of some QCD contamination in the \Wjets--dominated
+together due to the presence of some QCD contamination in the \Wjets-dominated
 control region. The shape of the \Wjets background is taken
-from the \ac{MC} samples. The QCD shape taken from same--sign
+from the \ac{MC} samples. The QCD shape taken from same-sign
 data, that is events selected in observed data with the opposite charge requirement
@@
 \label{sec:mssm_bkgs_mtet_wjetsnorm}
-The \Wjets normalisation is derived using a high-\mT~ control region, where
-selected events are required to satisfy \mT$>70$ GeV. The 
+The \Wjets normalisation is derived using a high-\mT~control region, where
+selected events are required to satisfy \mT~$>70\,\GeV$. The 
 \Wjets
@@
 Because of this contribution from QCD events in the high \mT~region we
-have, for \mT$>70$ GeV:
+have, for \mT~$>70\,\GeV$:
 \begin{equation}\label{eqn:wjets_ss_norm}
@@
 $R_{\text{QCD}}^{\text{OS/SS}}$, and on these two ratios not being too similar to each other. 
-The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti--isolated
+The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti-isolated
 control region in data; this measurement is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
@@
 requirement itself is removed, but the jet requirements still stand. Events with at least one 
-jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
+jet with \pT~$>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with \pT~$>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
 region is determined by the estimate given by the number of \Wjets events
-estimated in the 1-jet selection, multiplied by an extrapolation factor 
-$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$.
+estimated in the one-jet selection, multiplied by an extrapolation factor 
+$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
 \begin{figure}[h!]
@@
 \label{sec:mssm_bkgs_etmt_qcdosss}
-The ratio of opposite--sign to same--sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$, is measured
+The ratio of opposite-sign to same-sign QCD events, $R_{\text{QCD}}^{\text{OS/SS}}$, is measured
 in two anti-isolated sidebands by performing a fit to the distribution of the
 visible mass of the di-tau pair in 
-opposite-sign events. The QCD template, which is taken from same--sign events 
+opposite-sign events. The QCD template, which is taken from same-sign events 
 assuming $R_{\text{QCD}}^{\text{OS/SS}} = 1$ is treated as the signal, and a binned maximum
@@
 When performing the same fits in the no b-tag and b-tag categories to determine differences between
-this pre-categorisation opposite--sign to same--sign ratio, and the ratio as measured in categories it is found that 
+this pre-categorisation opposite-sign to same-sign ratio, and the ratio as measured in categories it is found that 
 the fit is not stable in the b-tag category due to the number of events in this region being too small.
@@
 in the \mutau channel for the sideband near the signal region, before
-and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
+and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband near the signal region, (a) before
 the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
-is 1.180$\pm$0.044.}
+is $1.180\pm0.044$.}
 \label{fig:mssm_qcdosss_mtnear}
@@
 \end{center}
-\caption[The visible mass distribution of the di-$\tau$ pair in the
+\caption[The visible mass distribution of the di-tau pair in the
 \mutau channel for the sideband further away from the signal region,
-before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
+before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband further away from the signal region, (a) before
 the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength 
-is 1.184$\pm$0.035.}
+is $1.184\pm0.035$.}
 \label{fig:mssm_qcdosss_mtfar}
@@
 \end{center}
-\caption[The visible mass distribution of the di-$\tau$ pair in
+\caption[The visible mass distribution of the di-tau pair in
 the \etau channel for the sideband near the signal region,
-before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength is 1.015$\pm$0.059.}
+before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \etau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength is $1.015\pm0.059$.}
 \label{fig:mssm_qcdosss_etnear}
@@
 \end{center}
-\caption[The visible mass distribution of the di-$\tau$ pair
+\caption[The visible mass distribution of the di-tau pair
 in the \etau channel for the sideband further away from the signal
 region, before and after the maximum likelihood fit to the QCD signal 
-strength.]{The visible mass distribution of the di-$\tau$ pair in the \etau channel for the sideband further away from the signal region, (a) before
+strength.]{The visible mass distribution of the di-tau pair in the \etau channel for the sideband further away from the signal region, (a) before
 the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength
-is 1.127$\pm$0.045.}
+is $1.127\pm0.045$.}
 \label{fig:mssm_qcdosss_etfar}
@@
 The QCD normalisation is estimated by inverting the opposite-sign requirement
-of the di-tau pair in the signal region. The yield is taken from the same--sign
-region with otherwise identical cuts to the opposite--sign region. The contributions
+of the di-tau pair in the signal region. The yield is taken from the same-sign
+region with otherwise identical cuts to the opposite-sign region. The contributions
 from other backgrounds in this region are subtracted to give an estimate of the number
-of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
+of QCD events in the same-sign region. For all backgrounds apart from \Wjets the
 yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
@@
 \end{equation}
-Because opposite--sign and same--sign QCD events do not
+Because opposite-sign and same-sign QCD events do not
 necessarily appear in equal amounts the number of QCD
 events obtained by subtracting other backgrounds from the
-observed number of events in the same--sign region is multiplied
+observed number of events in the same-sign region is multiplied
 by $R_{\text{QCD}}^{\text{OS/SS}}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
@@
 The normalisation and shape 
-of this background are estimated from a sideband with loosened 
+of this background are estimated from a sideband with relaxed 
 isolation requirements with respect to the signal region. 
@@
 This sideband is slightly further away from the signal region than the
-`tight--medium' sideband. %The bias from using this looser
+`tight-medium' sideband. %The bias from using this looser
 %sideband has been assessed and has a less than 1$\sigma$ effect.
@@
 is estimated by inverting the charge requirement
-of the pair, considering the same--sign region
+of the pair, considering the same-sign region
 with otherwise identical cuts to the signal region.
@@
 Like for the \etau and \mutau channels, the number of
-QCD events with opposite--sign \emu pairs is not
+QCD events with opposite-sign \emu pairs is not
 necessarily equal to the number of QCD events
-with same--sign \emu pairs and therefore the ratio
-of opposite--sign to same--sign pairs is measured by inverting
+with same-sign \emu pairs and therefore the ratio
+of opposite-sign to same-sign pairs is measured by inverting
 the isolation requirements on the electron or muon. Both
@@
 least one of them needs to fail the nominal isolation requirement.
-The opposite--sign to same--sign ratio is parameterised in terms
+The opposite-sign to same-sign ratio is parameterised in terms
 of lepton kinematics and the separation in $\Delta R$ between the
-two leptons. These ratios are then applied to the estimate in the same--sign region
+two leptons. These ratios are then applied to the estimate in the same-sign region
 to give an estimate in the signal region. The statistical uncertainty
@@
 uncertainties are added in quadrature. 
-The opposite--sign to same--sign ratios are measured
+The opposite-sign to same-sign ratios are measured
 before applying the categorisation, and because \ac{MC} studies suggest
-that the opposite--sign to same--sign ratio is different in the b-tag
+that the opposite-sign to same-sign ratio is different in the b-tag
 category than in the no b-tag category, an extra scale factor of 
-1.45/2.20 $\pm$ 0.16 is applied to the QCD estimate in the b-tag category. This is 
+$1.45/2.20\pm0.16$ is applied to the QCD estimate in the b-tag category. This is 
 the ratio between the OS/SS ratio as measured in the b-tag category and 
@@
 region with a \ttbar purity of 91\%. This control region
-is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
+is defined as $D_{\zeta} < -20\,\GeV$ and \MET~$>80\,\GeV$ in 
 the \emu channel, and it is shown in figure \ref{fig:mssm_corrs_toppt}b.
@@
 \label{sec:mssm_bkgs_other}
-For all channels the di--boson plus 
-single--top background is small.
+For all channels the di-boson plus 
+single-top background is small.
 Both normalisation and shape are estimated from \ac{MC}
@@
 \ac{MC} samples. In the \emu channel the $\PW\Pphoton$ background
-is also added to the \Wjets background component. For plotting purposes the single-top plus
-di-boson and \Wjets backgrounds are drawn together as the `electroweak' contribution for all channels, even though
-they are considered as separate components in the fit.
+is also added to the \Wjets background component. %For plotting purposes the single-top plus
+%di-boson and \Wjets backgrounds are drawn together as the `electroweak' contribution for all channels, even though
+%they are considered as separate components in the fit.
 
@@
 is estimated using \ac{MC} samples.
-\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
-The uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate
+\subsubsection*{$\text{jet}\rightarrow\Pgth$ fake rate}
+The uncertainty on the $\text{jet}\rightarrow\Pgth$ fake rate
 is 20\% \cite{cms-tau-2015}. This uncertainty is applied
@@
 channel, and the \ttbar background without real hadronic taus.
-\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
-The $\Pe\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 10-30\%,
+\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rate}
+The $\Pe\rightarrow\Pgth$ fake rate uncertainty ranges from $10$--$30$\%,
 depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
 applied to the \Zellell background with the hadronic tau faked by an electron.
-The $\Pgm\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 20-30\%, depending
+The $\Pgm\rightarrow\Pgth$ fake rate uncertainty ranges from $20$--$30$\%, depending
 on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
@@
 \subsubsection*{Jet energy scale uncertainty}
-The uncertainties on the jet-energy corrections are applied
+The uncertainties on the jet energy corrections are applied
 by shifting the jet energy up and down by the \pT-and $\eta$-dependendent
@@
 each category. Where the change in normalisation is non-negligible the
-uncertainty is applied. It ranges from 1--10\% depending on process and category.
-\subsubsection*{B-tag scale factors}
+uncertainty is applied. It ranges from $1$--$10$\% depending on process and category.
+\subsubsection*{b-Tag scale factors}
 Uncertainties on the b-tagging efficiency and light jet mis-tagging
@@
 evaluated. If the change in normalisation is non-negligible this
-uncertainty is applied. The uncertainty varies from 1--5\%.
+uncertainty is applied. The uncertainty varies from $1$--$5$\%.
 \subsubsection*{\MET~resolution and response}
@@
 to 6\% \cite{CMS-PAS-HIG-16-037}.
-\item di-boson and single-top: The uncertainty on the di-boson and
-single-top production cross-sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
+\item di-boson and single-top: The combined uncertainty on the di-boson and
+single-top production cross sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
 \item \Wjets: In the \mutau and \etau channels the statistical uncertainties
@@
 \item QCD: In the \emu channel the uncertainty on the QCD estimate
-is taken as the uncertainty on the measured opposite--sign to same--sign
-ratio, which is 23\% in the no b-tag category and 34 \% in the b-tag category. In the
+is taken as the uncertainty on the measured opposite-sign to same-sign
+ratio, which is 23\% in the no b-tag category and 34\% in the b-tag category. In the
 \tautau channel the statistical uncertainty on the QCD estimate is derived from
@@
 extrapolation factor from the anti-isolated sideband into the signal region is found
-to be 12\% in the no b-tag category and 14 \% in the b-tag category. For the \etau and
+to be 12\% in the no b-tag category and 14\% in the b-tag category. For the \etau and
 \mutau channels the statistical
@@
 region used to derive the QCD estimate is accounted for by the inclusion of these control
-regions in the fit. The uncertainty on the opposite--sign to same--sign ratio, based on
+regions in the fit. The uncertainty on the opposite-sign to same-sign ratio, based on
 the studies described in section \ref{sec:mssm_bkgs_etmt_qcdosss} is found to be 4\% (60\%) in the 
@@
 For interpretations of the results in MSSM benchmark scenarios, theory
-uncertainties on the SM and MSSM Higgs cross--section predictions are taken into account.
+uncertainties on the SM and MSSM Higgs cross section predictions are taken into account.
 The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
@@
 1.6\% for ZH and 1.9\% for WH.
-For the MSSM Higgs cross--sections used in the models, the uncertainties
+For the MSSM Higgs cross sections used in the models, the uncertainties
 due to different choices of factorisation and renormalisation scale
-are computed, separately for each \mA-\tanb~point, following the prescription in Refs. \cite{pdf-lhc,alphas-uncs}.
+are computed, separately for each \mA-\tanb~point, following the prescription in references \cite{pdf-lhc,alphas-uncs}.
 
@@
 signals and to the \Ztautau background in the \emu channel.
-\subsubsection*{High-\pT~$\Pgt_{h}$ ID efficiency}
-An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
+\subsubsection*{High-\pT~$\Pgth$ ID efficiency}
+An additional $\Pgth$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\TeV}$
 is applied to account for the extrapolation from the tau ID efficiency
-measurement, which uses mostly taus close to the Z peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
+measurement, which uses mostly taus close to the \PZ peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
 uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
@@
 \begin{center}
-\subfloat[gg$\phi$ signal at $m_{\phi} = 3.2$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
+\subfloat[$\Pg\Pg\phi$ signal at $m_{\phi} = 3.2\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
 \subfloat[\Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ZTT.pdf}}
@@
 On the \Wjets background in the \etau and \mutau channels a shape 
-uncertainty of $\frac{-20\% \times p_{\text{T}}}{\text{GeV}}$ is 
-applied. This uncertainty is derived from variations in the data/MC ratio
-for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~in 
+uncertainty of $\frac{-20\% \times p_{\text{T}}}{\GeV}$ is 
+applied. This uncertainty is derived from variations in the data/\ac{MC} ratio
+for the $\text{jet}\rightarrow\Pgth$ fake rate as a function of jet \pT~in 
 \Wjets events \cite{CMS-PAS-HIG-16-037}.
@@
 controls the \Wjets normalisation in all four regions. The QCD normalisation
-is fully correlated between the opposite--sign and same--sign low-\mT~regions. The
-same is true for the opposite--sign and same--sign high-\mT~regions. This means there are
+is fully correlated between the opposite-sign and same-sign low-\mT~regions. The
+same is true for the opposite-sign and same-sign high-\mT~regions. This means there are
 two freely floating nuisance parameters that govern the QCD normalisation: one
@@
 Because the analysis targets the two main MSSM production modes, gluon fusion and
-b-associated production, limits are set on these two signal processes. As we
-have seen in section \ref{sec:mssm_eventsel_categories}  we cannot fully separate the two signals by means
+b-associated production, limits are set on these two signal processes. As discussed
+in section \ref{sec:mssm_eventsel_categories} the two signals cannot be fully separated by means
 of the categorisation used. 
-However, in the upper limits on cross--section times branching ratio for the gg$\phi$
-process we should not make any assumptions about the presence or lack of the bb$\phi$
-process and vice versa. Therefore when calculating the upper limits on the gg$\phi$ (bb$\phi$)
-process, the contribution of the bb$\phi$ (gg$\phi$) process is profiled. This means it is floated
+However, in the upper limits on \xsbr for the $\Pg\Pg\phi$
+process no assumptions should be made about the presence or lack of the $\Pbottom\Pbottom\phi$
+process and vice versa. Therefore when calculating the upper limits on the $\Pg\Pg\phi$ ($\Pbottom\Pbottom\phi$)
+process, the contribution of the $\Pbottom\Pbottom\phi$ ($\Pg\Pg\phi$) process is profiled. This means it is floated
 in the fit like a nuisance parameter.
@@
 Because the analysis targets these two signal processes, it is possible
-to re-define the likelihood as a function of both the gg$\phi$ and bb$\phi$ signals:
+to re-define the likelihood as a function of both the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ signals:
 \begin{equation}\label{mssm_2D_likelihood}
-\mathcal{L}(\text{data}|\mu_{gg\phi},\mu_{bb\phi}, \theta) = \mathcal{L}(\text{data}|\mu_{gg\phi} \cdot s_{gg\phi}(\theta) + \mu_{bb\phi}\cdot s_{bb\phi}(\theta) + b(\theta)),
+\mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi},\mu_{\Pbottom\Pbottom\phi}, \theta) = \mathcal{L}(\text{data}|\mu_{\Pg\Pg\phi} \cdot s_{\Pg\Pg\phi}(\theta) + \mu_{\Pbottom\Pbottom\phi}\cdot s_{\Pbottom\Pbottom\phi}(\theta) + b(\theta)),
 \end{equation}
-where $s_{gg\phi}$ and $s_{bb\phi}$ are the signal expectations of the two
-production processes and the signal strength modifiers $\mu_{gg\phi}$ and $\mu_{bb\phi}$ now represent the cross--section times branching ratio of the
-two processes. Using this definition we can now perform a likelihood scan in two dimensions by 
-constructing a two-dimensional grid in $\mu_{gg\phi}$ and $\mu_{bb\phi}$, both required to be greater than or equal to 0. 
+where $s_{\Pg\Pg\phi}$ and $s_{\Pbottom\Pbottom\phi}$ are the signal expectations of the two
+production processes and the signal strength modifiers $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$ now represent the \xsbr of the
+two processes. Using this definition a likelihood scan in two dimensions can be performed.
+First a 2D grid in $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$, both required to be greater than or equal to 0, is constructed. 
 The negative log-likelihood,
@@
 is then evaluated at each point. The point in the 2D grid where the NLL reaches
-its lowest value gives the best fit value for $\mu_{gg\phi}$ and $\mu_{bb\phi}$.
+its lowest value gives the best fit value for $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$.
 68\% and 95\% confidence intervals are constructed as the values
-$\mu_{gg\phi}^{N\%}$ and $\mu_{bb\phi}^{N\%}$ for which:
+$\mu_{\Pg\Pg\phi}^{N\%}$ and $\mu_{\Pbottom\Pbottom\phi}^{N\%}$ for which:
 \begin{equation}\label{eqn:mssm_2D_deltaNLL}
 \begin{split}
-\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{68\%},\mu_{bb\phi}^{68\%}) = 0.5, ~\\
-\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{gg\phi}^{95\%},\mu_{bb\phi}^{95\%}) = 1.92.
+\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) = 0.5, ~\\
+\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) = 1.92.
 \end{split}
@@
 At each point in the \mA-\tanb~plane each MSSM scenario
-predicts a production cross--section, and corresponding branching
+predicts a production cross section, and corresponding branching
 ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
-masses of the light h and the scalar H are also given as a function of \mA~and \tanb.
+masses of the light \PHiggslight and the scalar \PHiggs are also given as a function of \mA~and \tanb.
 To interpret the results of this search in a particular scenario, the predicted
@@
 model is not strictly correct. Due to the existence of a Higgs boson with a 
-mass of 125 GeV, all MSSM benchmark scenarios must include a light Higgs boson
+mass of $125\,\GeV$, all \ac{MSSM} benchmark scenarios must include a light Higgs boson
 with very similar properties to the boson discovered during Run 1 of the \ac{LHC}.
-Therefore we should perform a test that distinguishes between a three-Higgs-signal-plus-background hypothesis, and
-a standard model Higgs-signal-plus-background hypothesis.
+Therefore a test that distinguishes between a three-Higgs-signal-plus-background hypothesis, and
+a standard model Higgs-signal-plus-background hypothesis, should be performed.
 
@@
 must be modified. Instead of testing for the compatibility of the data with
-a signal + background expectation modified by the signal strength modifier $\mu$ as
+a signal-plus-background expectation modified by the signal strength modifier $\mu$ as
 $\mu \cdot s(\theta) + b(\theta)$, a likelihood should be constructed as:
@@
 \end{equation}
-where $s_{\text{MSSM}}(\theta)$ corresponds to the MSSM signal expectation, that is the three-Higgs-signal, and $s_{\text{SM}}(\theta)$ 
-corresponds to the SM signal expectation.
+where $s_{\text{MSSM}}(\theta)$ corresponds to the \ac{MSSM} signal expectation, that is the three-Higgs-signal, and $s_{\text{SM}}(\theta)$ 
+corresponds to the \ac{SM} signal expectation.
 The signal strength modifier $\mu$ takes the role of distinguishing between
 the two hypotheses in this case. The model must not allow for the coexistence 
-of the SM and MSSM hypotheses; the MSSM hypothesis ($\mu=1$) has to be tested
-against the SM hypothesis ($\mu=0$).
+of the \ac{SM} and \ac{MSSM} hypotheses; the \ac{MSSM} hypothesis ($\mu=1$) has to be tested
+against the \ac{SM} hypothesis ($\mu=0$).
 
@@
 to use the profile likelihood ratio of equation \ref{eqn:hhh_profilelikelihood}:
-we need to test $\mu=1$ against $\mu=0$, and 
+a test of $\mu=1$ against $\mu=0$ has to be made, and 
 $\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
-general not 0. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011},
+general not zero. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011},
 \begin{equation}\label{eqn:mssm_tevatron_teststat}
@@
 \end{equation}
-In this test statistic we test a positive value of $\mu$ against $\mu=0$, thus we are able to define
-the desired `MSSMvsSM' test statistic, using $\mu=1$, as,
+In this test statistic a positive value of $\mu$ is tested against $\mu=0$, thus 
+the desired `MSSMvsSM' test statistic can be defined, using $\mu=1$, as,
 \begin{equation}\label{eqn:mssm_mssmvssm_stat}
@@
 to the Tevatron test statistic, and therefore the probability density functions need to be generated 
-with toy datasets. Using these probability density functions  we can then calculate $CL_s(\mu=1)$ as defined in equation \ref{eqn:hhh_cls}.
-If $CL_s < 0.05$ the MSSM hypothesis is excluded at 95\% CL. The generation of toy datasets and 
-calculation of corresponding $CL_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
+with toy datasets. Using these probability density functions $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
+If $\text{CL}_s < 0.05$ the MSSM hypothesis is excluded at 95\% CL. The generation of toy datasets and 
+calculation of corresponding $\text{CL}_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
 with interpolation between grid points performed to obtain a smooth exclusion contour.
-The pdfs for the SM and MSSM hypotheses, as well as the resulting $CL_s$ values,
+The probability distribution functions for the \ac{SM} and \ac{MSSM} hypotheses, as well as the resulting $\text{CL}_s$ values,
 are given for three illustrative \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
-there is no separation between the MSSM and SM pdfs, and so we cannot exclude this point. The separation
-between the pdfs in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
-with the SM hypothesis. This point is on the edge of being excluded. Finally the pdfs in figure \ref{fig:mssm_mssmvssm_toys}c
-are very well separated, and the observation is compatible with the SM hypothesis, meaning this point of the parameter space is excluded.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[\mA=1.2 TeV, \tanb=16]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_16.png}}
-\subfloat[\mA=1.2 TeV, \tanb=50]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_50.png}}~\\
-\subfloat[\mA=700 GeV, \tanb=60]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_700_tanb_60.png}}
-\end{center}
-\caption[Probability density functions for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$ scenario.]{Probability density functions, obtained by generating a large number of toy datasets, for the SM and MSSM hypotheses at three different points in the $m_{\text{h}}^{\text{mod+}}$
-scenario, each with different levels of separation between the MSSM and SM distributions.}
+there is no separation between the \ac{MSSM} and \ac{SM} distributions, and so this point cannot be excluded. The separation
+between the distributions in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
+with the \ac{SM} hypothesis. This point is on the edge of being excluded. Finally the distributions in figure \ref{fig:mssm_mssmvssm_toys}c
+are very well separated, and the observation is compatible with the \ac{SM} hypothesis, meaning this point of the parameter space is excluded.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[\mA~$=1.2\,\TeV$, \tanb~$=16$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_16.png}}
+\subfloat[\mA~$=1.2\,\TeV$, \tanb~$=50$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_1200_tanb_50.png}}~\\
+\subfloat[\mA~$=700\,\GeV$, \tanb~$=60$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/plot_mA_700_tanb_60.png}}
+\end{center}
+\caption[Probability density functions for the \ac{SM} and \ac{MSSM} hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.]{Probability density functions, obtained by generating a large number of toy datasets, for the \ac{SM} and \ac{MSSM} hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$
+scenario, each with different levels of separation between the \ac{MSSM} and \ac{SM} distributions.}
 \label{fig:mssm_mssmvssm_toys}
@@
 data has been performed, are shown in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em}.
-The signal of the 3 neutral Higgs bosons at \mA=1 TeV and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid 
+The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid 
 on the total transverse mass distributions. The signal peaks twice due to the presence of a light Higgs boson
-with mass compatible with 125 GeV in this model, which is necessary to incorporate the Higgs boson
-observed at 125 GeV.
+with mass compatible with $125\,\GeV$ in this model, which is necessary to incorporate the Higgs boson
+observed at $125\,\GeV$.
 
@@
 of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \mutau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
-and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid. Note that, to incorporate
-the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
-at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
-the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid. Note that, to incorporate
+the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{mod+}$ scenario includes a \PHiggslight boson
+at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps, and this is
+the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_results_mttot_mt}
@@
 categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \etau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
-and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
+and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
 %the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
@@
 of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
-and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
 %the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
@@
 the \emu channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \emu channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
-and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+of the \emu channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
 %the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
@@
 
-None of these distributions show a significant excess. The
-95\% CL upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
-for gluon fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
+None of these distributions show a significant excess of observed events over the background
+expectation. The
+95\% CL upper limits on \xsbr are shown in figure \ref{fig:mssm_results_limits}a
+for gluon fusion and in figure \ref{fig:mssm_results_limits}b for b-associated
 production. All channels and categories are combined. 
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
 \end{center}
@@
 b-associated production process, combining all final states and categories.]{Upper limits at 95\% CL for (a) the gluon fusion production
-process and (b) the b--associated production process. All four final states and 
+process and (b) the b-associated production process. All four final states and 
 all categories are combined for these limits. The green and yellow bands indicate
-the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_results_limits}
@@
 A comparison of the expected limits
-per channel is shown in figure \ref{fig:mssm_results_limits_breakdown}a for gg$\phi$ production
-and in figure \ref{fig:mssm_results_limits_breakdown}b for bb$\phi$ production.
+per channel is shown in figure \ref{fig:mssm_results_limits_breakdown}a for $\Pg\Pg\phi$ production
+and in figure \ref{fig:mssm_results_limits_breakdown}b for $\Pbottom\Pbottom\phi$ production.
 These figures show that the \mutau channel is the most sensitive at masses up to 
-200 GeV, beyond which the \tautau channel becomes more sensitive. The \etau
+$200\,\GeV$, beyond which the \tautau channel becomes more sensitive. The \etau
 channel is always slightly less sensitivie than the \mutau channel. The \emu channel
 is the least sensitive over a large part of the parameter space, until it overtakes the 
-\etau channel in sensitivity at 1.6 TeV and is slightly more sensitive than the
-\mutau channel at 3.2 TeV. The \emu channel becomes more sensitive at higher masses as
+\etau channel in sensitivity at $1.6\,\TeV$ and is slightly more sensitive than the
+\mutau channel at $3.2\,\TeV$. The \emu channel becomes more sensitive at higher masses as
 a narrower binning of the \mTtot~distribution is possible than for the other channels.
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_ggh.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_bbh.pdf}}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_ggh.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16037_limitcomp_bbh.pdf}}
 \end{center}
 \caption[Comparison of expected upper limits at 95\% CL for gluon fusion and 
-b-associated production per channel.]{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
+b-associated production per channel.]{Expected upper limits at 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
-and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
+and \emu (gold) channels. For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
 while the \tautau channel dominates for higher masses. The \etau channel is always
 slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
-until at around 1.6 TeV it starts to overtake the \etau channel, with the sensitivity at 3.2 TeV 
+until at around $1.6\,\TeV$ it starts to overtake the \etau channel, with the sensitivity at $3.2\,\TeV$ 
 being similar or slightly better than the \mutau channel.}
@@
 \label{sec:mssm_results_125GeV}
-As we set limits on MSSM Higgs boson production 
-down to masses of 90 GeV it is important to consider possible sensitivity
-to the 125 GeV SM Higgs boson. As the cross--section times branching ratio for gluon fusion
-production of the 125 GeV Higgs boson in the standard model, with decay into $\Pgt\Pgt$,
-is 3.05 pb \cite{YR4} and the expected limit on cross--section times
-branching ratio for MSSM gg$\phi$ production at around 125 GeV is around 20 pb
-the analysis is not yet sensitive to the SM Higgs boson. The
+As limits are set on \ac{MSSM} Higgs boson production 
+down to masses of $90\,\GeV$ it is important to consider possible sensitivity
+to the $125\,\GeV$ \ac{SM} Higgs boson. As the \xsbr for gluon fusion
+production of the $125\,\GeV$ Higgs boson in the \ac{SM}, with decay into $\Pgt\Pgt$,
+is $3.05\,\picobarn$ \cite{YR4} and the expected limit on \xsbr 
+for \ac{MSSM} $\Pg\Pg\phi$ production at around $125\,\GeV$ is around $20\,\picobarn$
+the analysis is not yet sensitive to the \ac{SM} Higgs boson. The
 limits shown in figure \ref{fig:mssm_results_greenband},
-which include the standard model Higgs boson as part of the backgrounds,
+which include the \ac{SM} Higgs boson as part of the backgrounds,
 are almost exactly the same as those shown in figure \ref{fig:mssm_results_limits}, which
-also indicates the current lack of sensitivity to the standard model Higgs boson.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-a.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-b.pdf}}
-\end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production processes, with the 125 GeV Higgs boson included as one of the backgrounds.]{Upper limits at 95\% CL for (a) the gluon fusion production
-process and (b) the b--associated production process. The SM, 125 GeV Higgs boson
+also indicates the current lack of sensitivity to the \ac{SM} Higgs boson.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-a.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_005-b.pdf}}
+\end{center}
+\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production processes, with the $125\,\GeV$ \ac{SM} Higgs boson included as one of the backgrounds.]{Upper limits at 95\% CL for (a) the gluon fusion production
+process and (b) the b-associated production process. The $125\,\GeV$ \ac{SM} Higgs boson
 is included as one of the backgrounds. All four final states and 
 all categories are combined for these limits. The light and dark green bands indicate
-the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
 \label{fig:mssm_results_greenband}
@@
 are shown in figure \ref{fig:mssm_results_2D_scans}
-for four mass points ranging from 100 GeV to 3.2 TeV. The black cross indicates the best-fit value, with the red diamond showing the expected
-best-fit value in the presence of the 125 GeV SM Higgs boson. The dark and light purple contours
+for four mass points ranging from $100\,\GeV$ to $3.2\,\TeV$. The black cross indicates the best-fit value, with the red diamond showing the expected
+best-fit value in the presence of the $125\,\GeV$ \ac{SM} Higgs boson. The dark and light purple contours
 indicate the 68\% and 95\% confidence interval, respectively. From the shape of the contours
-we can see the correlation between the gg$\phi$ and bb$\phi$ processes, illustrating
-the fact that we cannot fully disentangle the two processes.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{\phi} = 100$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-a.pdf}}
-\subfloat[$m_{\phi} = 700$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-g.pdf}}~\\
-\subfloat[$m_{\phi} = 1.6$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-i.pdf}}
-\subfloat[$m_{\phi} = 3.2$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-l.pdf}}
-\end{center}
-\caption[2D likelihood scans showing the best-fit value for cross--section 
-times branching ratio of both the gluon fusion and b-associated production 
-processes.]{2D likelihood scans showing the best-fit value (black cross) for cross--section times branching ratio 
-of both the gluon fusion (x-axis) and b- associated production (y-axis) processes. The red diamond indicates the
-expected best fit point for the presence of a 125 GeV SM Higgs boson, and the purple bands indicate the 68\% and
+the correlation between the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ processes is visible, illustrating
+the fact that the two processes are not fully disentangled by the chosen categorisation.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\phi} = 100\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-a.pdf}}
+\subfloat[$m_{\phi} = 700\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-g.pdf}}~\\
+\subfloat[$m_{\phi} = 1.6\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-i.pdf}}
+\subfloat[$m_{\phi} = 3.2\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_011-l.pdf}}
+\end{center}
+\caption[2D likelihood scans showing the best-fit value for 
+\xsbr of both the gluon fusion and b-associated production 
+processes.]{2D likelihood scans showing the best-fit value (black cross) for \xsbr 
+of both the gluon fusion ($x$ axis) and b-associated production ($y$ axis) processes. The red diamond indicates the
+expected best fit point for the presence of a $125\,\GeV$ \ac{SM} Higgs boson, and the purple bands indicate the 68\% and
 95\% confidence interval contours \cite{CMS-PAS-HIG-16-037}.}
@@
 \label{sec:mssm_results_modeldep}
-The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
+The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{\PHiggslight}}^{\text{mod+}}$
 scenario and the hMSSM scenario. Both scenarios are described in chapter \ref{chap:theory}.
@@
 observed (blue shaded area bounded by solid line) exclusion of the search presented in this chapter
-in the \mA-\tanb~ plane of the $m_{\text{h}}^{\text{mod+}}$ scenario. The red shaded band
+in the \mA-\tanb~plane of the $m_{\PHiggslight}^{\text{mod+}}$ scenario. The red shaded band
 indicates the area that is excluded due to the lack of a light Higgs boson with a mass compatible
-with 125 GeV. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
-limits at high \tanb~have been significantly improved, by around 300 GeV.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
+with $125\,\GeV$. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
+limits at high \tanb~have been significantly improved, by around $300\,\GeV$.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
 \subfloat[hMSSM scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
 \end{center}
-\caption[Exclusion in the $m_{h}^{\text{mod+}}$ scenario and the hMSSM
-scenario of the \AHtotautau analysis.]{Exclusion in (a) the $m_{h}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+\caption[Exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
+scenario of the \AHtotautau analysis.]{Exclusion in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
 obtained by the combination
@@
 expected exclusion. The light and dark grey bands indicate
-the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit.
-The red shaded area in the $m_{h}^{\text{mod}+}$ figure
-is excluded by the lack of a light Higgs boson with mass compatible with 125 GeV \cite{CMS-PAS-HIG-16-037}.}
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.
+The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
+is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_mhmodp_2016}
@@
 presented in this chapter in the \mA-\tanb~plane of the hMSSM scenario. 
-We should note again that this model, although defined for \tanb~ values
+It should be noted again that this model, although defined for \tanb~values
 upwards of 10, is only strictly valid for \tanb~below 10.
-The small excluded area around \mA=200 GeV is genuine. It is caused by the 
-production cross-section times branching ratio in the model, which is driven by
-two effects \cite{CMS-PAS-HIG-16-007}. On the one hand the branching ratio into taus decreases with decreasing
-\tanb, while on the other hand a negative top--bottom interference effect increases the
-gluon fusion cross--section with decreasing \tanb. Therefore the
-combined cross--section times branching ratio decreases with decreasing \tanb, until it
-increases again from a low value of \tanb~down to \tanb=1. The feature is 
+The small excluded area around \mA~$=200\,\GeV$ is genuine. It is caused by the 
+\xsbr in the model, which is driven by
+two effects as already discussed in section \ref{sec:theory_MSSM_H}. On the one hand the branching ratio into taus decreases with decreasing
+\tanb, while on the other hand a negative top-bottom interference effect increases the
+gluon fusion cross section with decreasing \tanb. Therefore the
+combined \xsbr decreases with decreasing \tanb, until it
+increases again from a low value of \tanb~$\sim 3$ down to \tanb=1. The feature is 
 thus expected to grow with more data.
@@
 \label{sec:mssm_combination}
-The results of the search for neutral Higgs bosons in the MSSM using the di-tau
+The results of the search for neutral Higgs bosons in the \ac{MSSM} using the di-tau
 final state, using a dataset
-corresponding to an integrated luminosity of 12.9 fb$^{-1}$, collected during the
+corresponding to an integrated luminosity of $12.9\,\invfb$, collected during the
 first half of 2016 and thus referred to as `2016 analysis', can be combined 
 with a previous search. This previous analysis
-was performed on a dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
-collected during 2015 (`2015 analysis'), and is detailed in Ref. \cite{CMS-PAS-HIG-16-006}.
-By combining the two analyses we should be able to set the most stringent
-limits on the two MSSM production modes, and in the \mA-\tanb~plane of 
-MSSM benchmark scenarios, available at the time of writing. It is also
+was performed on a dataset corresponding to an integrated luminosity of $2.3\,\invfb$ 
+collected during 2015 (`2015 analysis'), and is detailed in reference \cite{CMS-PAS-HIG-16-006}.
+By combining the two analyses it should be possible to set the most stringent
+limits on the two \ac{MSSM} production modes, and in the \mA-\tanb~plane of 
+\ac{MSSM} benchmark scenarios, available at the time of writing. It is also
 a first step on the way to combining the \AHtotautau analysis with
@@
 chapter \ref{chap:mssm} a shape analysis is performed, however a different
-discriminating variable is used. The variable used is the transverse component of the di-$\Pgt$ mass
+discriminating variable is used. The variable used is the transverse component of the di-tau mass
 as reconstructed using the \texttt{SVFit} algorithm, 
-denoted $m_{\text{T},\tau\tau}$. The transverse di-$\Pgt$ mass 
+denoted $m_{\text{T},\tau\tau}$. The transverse di-tau mass 
 distributions for the signal region categories of the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\end{center}
-\caption[Transverse component of the di-\Pgt mass for expected backgrounds
-and observed events in the no b-tag and b-tag categories of the \mutau channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption[Transverse component of the di-tau mass for expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \mutau channel.]{Transverse component of the di-tau mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
-The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
-in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
-and once at higher mass, for the heavy H and A.}
+The signal overlaid corresponds to the signal of the three Higgs bosons at \mA~$=1\,\TeV$ and \tanb~$=50$
+in the $m_{\text{\PHiggslight}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
+and once at higher mass, for the heavy \PHiggs and \PHiggsps.}
 \label{fig:mssm_hig16006_mtsv_mt}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\end{center}
-\caption[Transverse component of the di-\Pgt mass for expected backgrounds
-and observed events in the no b-tag and b-tag categories of the \etau channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption[Transverse component of the di-tau mass for expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \etau channel.]{Transverse component of the di-tau mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \etau channel.}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\end{center}
-\caption[Transverse component of the di-\Pgt mass for expected backgrounds
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption[Transverse component of the di-tau mass for expected backgrounds
 and observed events in the no b-tag and b-tag categories of the \tautau
-channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+channel.]{Transverse component of the di-tau mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \tautau channel.}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\end{center}
-\caption[Transverse component of the di-\Pgt mass for expected backgrounds
-and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\end{center}
+\caption[Transverse component of the di-tau mass for expected backgrounds
+and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-tau mass for expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
@@
 
-These distributions do not show any significant excesses. The upper limits
-on cross--section times branching ratio for the gluon fusion and b-associated production
+These distributions do not show any significant excesses of observed events over
+the background expectation. The upper limits
+on \xsbr for the gluon fusion and b-associated production
 processes are shown in figure \ref{fig:mssm_results_hig16006_limits}a
@@
 the expected limits per channel is given in figure \ref{fig:mssm_results_limits_breakdown_hig16006}.
-These follow a similar pattern to those given in figure \ref{fig:mssm_results_limits_breakdown}, notice
-however the \emu channel remains the least sensitive even at very high mass, as the
-transverse component of the di-$\Pgt$ mass exhibits a sizeable \ttbar tail in the \emu channel. The total
+These follow a similar pattern to those given in figure \ref{fig:mssm_results_limits_breakdown}. Notice
+however that the \emu channel remains the least sensitive even at very high mass, as the
+transverse component of the di-tau mass exhibits a sizeable \ttbar tail in the \emu channel. The total
 transverse mass collapses events from the tail into lower regions of the distribution, thus reducing the backgrounds
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-a.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-b.pdf}}
-\end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production process.]{Upper limits at 95\% CL for (a) the gluon fusion production
-process and (b) the b--associated production process. All four final states and 
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-a.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/Figure_006-b.pdf}}
+\end{center}
+\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production process.]{Upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+process and (b) the b-associated production process. All four final states and 
 all categories are combined for these limits. The green and yellow bands indicate
-the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit  \cite{CMS-PAS-HIG-16-006}.}
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-006}.}
 \label{fig:mssm_results_hig16006_limits}
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_ggH.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_bbH.pdf}}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_ggH.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_bbH.pdf}}
 \end{center}
 \caption[Expected upper limits at 95\% CL for the gluon fusion and b-associated
-production, comparing the combination of all channels with the per-channel limits.]{Expected upper limits at 95\% CL for (a) gluon fusion and (b) b--associated production,
+production, comparing the combination of all channels with the per-channel limits.]{Expected upper limits at 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
-and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
+and \emu (gold) channels. For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
 while the \tautau channel dominates for higher masses. The \etau channel is always
@@
 \midrule
-SM signal theory uncertainties & Correlated & The same recommende cross sections were used in 2015 and 2016..\\
+SM signal theory uncertainties & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
 \midrule
@@
 \midrule
-e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expected to behave the same in 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.\\
-\midrule
-$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet, while this had changed for the 2016 analysis.\\
-\midrule
-jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & Uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate should not be affected by changes in hadronic tau isolation working point.\\
+$\Pe\rightarrow\Pgth$ fake rate & Correlated & Expected to behave the same in 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.\\
+\midrule
+$\Pgm\rightarrow\Pgth$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet, while this had changed for the 2016 analysis.\\
+\midrule
+$\text{jet}\rightarrow\Pgth$ fake rate & Correlated & Uncertainty on the $\text{jet}\rightarrow\Pgth$ fake rate should not be affected by changes in hadronic tau isolation working point.\\
 \midrule
@@
 \midrule
-Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa.\\
-\midrule
-Statistical \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-Systematic \mbox{uncertainty} on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
+Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 signal region and vice versa.\\
+\midrule
+Statistical \mbox{uncertainty} on W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+Systematic \mbox{uncertainty} on W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~region with anti-isolated $\Pgth$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
 In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
@@
 \midrule
-bin--by--bin \mbox{uncertainties} for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible.\\
+bin-by-bin \mbox{uncertainties} for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible.\\
 \bottomrule
@@
 \label{sec:mssm_combination_results}
-The expected and observed upper limits on cross--section times branching ratio,
-for the combination of the 2015 and 2016 analyses, are shown in figure
+The expected and observed upper limits on \xsbr 
+for the combination of the 2015 and 2016 analyses are shown in figure
 \ref{fig:mssm_results_combination_limits}. The limits behave as expected
@@
 \begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_ggH_cmb.png}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_bbH_cmb.png}}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_ggH_cmb.png}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_bbH_cmb.png}}
 \end{center}
 \caption[Upper limits at 95\% CL for the gluon fusion and b-associated production
-process, obtained by combining all channels and categories of the 2015 nd the 2016 analyses.] {Upper limits at 95\% CL for (a) the gluon fusion production
-process and (b) the b--associated production process. These results
+process, obtained by combining all channels and categories of the 2015 nd the 2016 analyses.] {Upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+process and (b) the b-associated production process. These results
 combine all categories and all four final states from both the 2015
 and the 2016 analyses. The green and yellow bands indicate
-the $\pm 1\sigma$(68\%) and $\pm 2\sigma$(95\%) probability intervals on the expected limit.}
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.}
 \label{fig:mssm_results_combination_limits}
@@
 To get a better picture of how the sensitivity of the individual analyses compares
-with the combination, we should consider the comparison
-of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
+with the combination, the comparison 
+of expected limits in figure \ref{fig:mssm_results_combination_limits_comp} should be considered. The
 gluon fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
 higher masses the sensitivity is only very slightly improved with respect to the 
-analysis of the 12.9 fb$^{-1}$ dataset. However, for masses between 200 and 800 GeV
+analysis of the $12.9\,\invfb$ dataset. However, for masses between $200$ and $800\,\GeV$
 there is a larger improvement in sensitivity from combining the two analyses.
 This behaviour is expected since the 2016 analysis used a slightly different
-selection that made the analysis more optimal at masses above 800 GeV,
+selection that made the analysis more optimal at masses above $800\,\GeV$,
 and slightly less optimal below this mass. This
-effect is less visible on the b--associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_ggH_with_ratio.pdf}}
-\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_bbH_with_ratio.pdf}}
+effect is less visible on the b-associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_ggH_with_ratio.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_bbH_with_ratio.pdf}}
 \end{center}
 \caption[Comparison of the expected upper limits at 95\% CL for the 
-gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at 95\% CL for (a) the gluon fusion production
-process and (b) the b--associated production process. The green curve shows the results
-from combining the 2015 and 2016 analyses (integrated luminosity of 15.2 fb$^{-1}$),
-with the red line indicating the limits from the 2016 analysis only (integrated luminosity of 12.9 fb$^{-1}$)
-and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of 2.3 fb$^{-1}$).
+gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+process and (b) the b-associated production process. The green curve shows the results
+from combining the 2015 and 2016 analyses (integrated luminosity of $15.2\,\invfb$),
+with the red line indicating the limits from the 2016 analysis only (integrated luminosity of $12.9\,\invfb$)
+and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of $2.3\,\invfb$).
 The plotted relative difference is with respect to the limits from the 2016 analysis, showing how the combination

### 2017-02-20 MSSM/MSSM.tex
Sorting out some of the comments on theory chapter

@@
 In the \emu channel two dedicated electron-muon cross triggers
-are used. These have significantly lower online \pT~cuts 
+are used. These have significantly lower \pT~cuts 
 on the two leptons than the single lepton triggers. For the 
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
 \end{center}
@@
 \begin{center}
-\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
-\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
 \end{center}
@@
 \begin{center}
-\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
-\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
 \end{center}
@@
 \begin{center}
-\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
-\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
 \end{center}
@@
 \begin{center}
-\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
-\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
+\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
 \end{center}

### 2017-02-20 Theory/Theory.tex
Sorting out some of the comments on theory chapter

@@
 A more detailed introduction to \ac{QCD} can 
-be found in Ref. \cite{griffiths}.
+be found in reference \cite{griffiths}.
 
@@
 \Phi = \exp{\{\frac{i}{\sqrt{2}v}\vec{\theta}\cdot\vec{b}\}}\begin{pmatrix} 0 \\
-\frac{1}{\sqrt{2}} (v+h) \end{pmatrix}.
+\frac{1}{\sqrt{2}} (v+\PHiggs) \end{pmatrix}.
 \end{equation}
@@
 \Phi = \begin{pmatrix} 0 \\
-\frac{1}{\sqrt{2}}(v+h) \end{pmatrix}.
+\frac{1}{\sqrt{2}}(v+\PHiggs) \end{pmatrix}.
 \end{equation}
@@
 \begin{split}
-&\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}h\partial^{\mu}h -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu_{\text{SM}}^2h^2  + \\ 
+&\mathcal{L}_{\text{Higgs}} = -\frac{1}{2}\partial_{\mu}\PHiggs\partial^{\mu}\PHiggs -\frac{g^2v^2}{4}\PW_{\mu}^- \PW^{\mu +} - \frac{g^2+g'^2}{8}v^2\PZ_{\mu}\PZ^{\mu}  - \mu_{\text{SM}}^2\PHiggs^2  + \\
 &\text{terms of at least }\mathcal{O}(3)\text{ in the fields}.
@@
 we can see that these two masses are
-related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The remaining mass term is for the Higgs field $h$, 
-$m_{h} = \sqrt{2\mu_{\text{SM}}^2}$.
+related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The remaining mass term is for the Higgs field \PHiggs, 
+$M_{\PHiggs} = \sqrt{2\mu_{\text{SM}}^2}$. It is denoted $M_{\PHiggs}$ to avoid confusion with the mass of the heavy scalar
+\PHiggs boson in the \ac{MSSM} $m_{\PHiggs}$, which will be introduced in section \ref{sec:theory_MSSM_H}.
 Note that the photon does not acquire a mass.
@@
 The discovery was based on the observation of excesses in the 
-search for $\PHiggslight\rightarrow\gamma\gamma$ and $\PHiggslight\rightarrow \PZ\PZ\rightarrow 4\ell$, with a significance 
+search for $\PHiggs\rightarrow\gamma\gamma$ and $\PHiggs\rightarrow \PZ\PZ\rightarrow 4\ell$, with a significance 
 above 5$\sigma$.
-More data were collected and analysed during the remainder of 2012, and subsequent studies 
+More data were collected and analysed during the remainder of 2012, and subsequent studies of its properties,
+such as spin, parity \cite{ATLASspin,CMSspin} and couplings to other particles, 
 increased the confidence in the compatibility of this new state with the \ac{SM} Higgs boson. 
-The most precise measurement of the mass of the Higgs boson, \mh = $125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst)}\,\GeV$, 
+The most precise measurement of the mass of the Higgs boson, $M_{\PHiggs} = 125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst)}\,\GeV$, 
 comes from the ATLAS and CMS combined
@@
 show very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
-the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination, while
-the individual experiments did not reach a significance upwards of 5$\sigma$ in this channel during Run 1.
+the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination. During Run 1
+searches by the ATLAS and CMS Collaborations resulted in observed 
+significances of $4.5\sigma$ \cite{ATLAS-tautau} and $3.2\sigma$ \cite{SMHtautauCMS}, respectively. 
 %Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
@@
 \end{center}
-\caption[Tree-level Feynman diagrams for the dominant Higgs production modes at the LHC]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
+\caption[Tree-level Feynman diagrams for the dominant Higgs boson production modes at the LHC]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
 the \ac{LHC}.}
@@
 \begin{center}
-\subfloat[\ac{SM} H production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
-\subfloat[\ac{SM} H branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
+\subfloat[\ac{SM} \PHiggs production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
+\subfloat[\ac{SM} \PHiggs branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
 \end{center}
@@
 the branching ratios of
-$\PHiggslight \rightarrow \gamma\gamma$ and $\PHiggslight \rightarrow ZZ$, the two discovery
+$\PHiggs \rightarrow \gamma\gamma$ and $\PHiggs \rightarrow \PZ\PZ$, the two discovery
 channels, are smaller than the branching ratios into many other final states.
@@
 already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
-as has the decay in to $ZZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
-of $h\rightarrow WW$ are being performed \cite{CMSHWW2016,ATLASHWW2016}. Establishment of the decay of 
-$h\rightarrow b\bar{b}$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $h\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
+as has the decay in to $\PZ\PZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
+of $\PHiggs\rightarrow WW$ are being performed \cite{CMSHWW2016,ATLASHWW2016}. Establishing evidence for the decay of 
+$\PHiggs\rightarrow \Pbottom\Pbottom$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $\PHiggs\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
 is still to be achieved.
-Finally, searches for ttH production, which are important to probe directly the top-Higgs coupling, have also been carried 
+Finally, searches for $\Ptop\Ptop\PHiggs$ production, which are important to probe directly the top-Higgs coupling, have also been carried 
 out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
@@
 In addition, the running coupling constants of the electroweak and
-strong forces do not converge at the GUT scale. Another problem is that the force
+strong forces do not intersect at a common energy scale. Another problem is that the force
 of gravity does not appear in the \ac{SM}.
@@
 \begin{split}
-&m_{h_{\text{SM}}}^2  = (m_h^2)_0 + \Delta m_h^2,\\
-&\Delta m_h^2 \sim \mathcal{O}(\Lambda^2).
+&M_{H_{\text{SM}}}^2  = (M_H^2)_0 + \Delta M_H^2,\\
+&\Delta M_H^2 \sim \mathcal{O}(\Lambda^2).
 \end{split}
@@
 Thus assuming that there is no new physics all the way up to
-the Planck scale the observation \mh=125 GeV would only be compatible with $\Lambda$ of order $10^{19}$ GeV
-if there was extreme fine-tuning of the bare Higgs boson mass $(m_h^2)_0$.
+the Planck scale the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
+if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs}^2)_0$.
 
@@
 mass corrections with opposite sign, and so the symmetry between bosons and fermions 
-allows for the cancellation of $\Delta m_h^2$ terms. The cancellation
+allows for the cancellation of $\Delta M_{\PHiggs}^2$ terms. The cancellation
 would be exact if \ac{SUSY} was unbroken, but because this is not the case the
@@
 significantly altered by radiative corrections. The dominant effect is from
-incomplete cancellation of the stop- and top-loop corrections.
+incomplete cancellation of the stop- and top-loop corrections. This can increase the mass
+of the light Higgs boson up to a maximum of $135\,\GeV$.
 
@@
 
-The inclusive cross-section times branching ratios for production of a \PHiggs boson 
+The inclusive cross section times branching ratios (\xsbr) for production of a \PHiggs boson 
 and decays into various final states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
 example of a type-II \ac{2HDM}, for two values of \tanb. Figure \ref{fig:2hdm_Hxsbr}b 
-shows the inclusive cross-section times branching ratios for production and decay
+shows the inclusive \xsbr for production and decay
 of a \PHiggsps boson in the same type-II \ac{2HDM} example, at two \tanb~points. At
-low \tanb~the cross-section times branching ratios for \Htohh production and decay and \AtoZh production
+low \tanb~the \xsbr for \Htohh production and decay and \AtoZh production
 and decay are enhanced for $250\leq m_{\PHiggs}\leq 350\,\GeV$ and $220 \leq m_{\PHiggsps} \leq 350\,\GeV$, respectively.
@@
 \label{sec:theory_BSM_models_mhmodp}
-The $m_{h}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
-is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
-was used for interpretations of MSSM Higgs boson searches at LEP and the Tevatron, allows
+The $m_{\PHiggslight}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
+is a modification of the $m_{\PHiggslight}^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
+was used for interpretations of \ac{MSSM}
+ Higgs boson searches at LEP and the Tevatron, allows
 the mass of the light Higgs boson to reach the highest a-priori expected 
@@
 in this scenario where the mass of the light Higgs boson is compatible with the
-observed $125\,\GeV$ state. The modifications to the parameters of the $m_{h}^{\text{max}}$ 
-scenario address this issue. In the $m_{h}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
-to be 1 TeV. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
+observed $125\,\GeV$ state. The modifications to the parameters of the $m_{\PHiggslight}^{\text{max}}$ 
+scenario address this issue. In the $m_{\PHiggslight}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
+to be $1\,\TeV$. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
 %This gives better agreement with muon g-2 results while the mhmod- scenario
@@
 
-Figure \ref{fig:mhmodp_xs} shows the cross--sections of
+Figure \ref{fig:mhmodp_xs} shows the cross sections of
 gluon fusion and b-associated production of the \PHiggs boson 
 in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
-production dominates at low \tanb, while b-associated production has a larger cross--section
-at high \tanb. The behaviour of the production cross-sections of the \PHiggsps boson
+production dominates at low \tanb, while b-associated production has a larger cross section
+at high \tanb. The behaviour of the production cross sections of the \PHiggsps boson
 is similar.
@@
 \begin{center}
-\subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
-\subfloat[$\sigma(gg\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
+\subfloat[$\sigma(\Pg\Pg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
+\subfloat[$\sigma(\Pg\Pg\rightarrow \Pbottom\Pbottom\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
 \end{center}
-\caption[Production cross--sections of  gluon fusion and b--associated
-production of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario.]{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
-in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
+\caption[Production cross sections of  gluon fusion and b-associated
+production of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.]{Production cross section of (a) gluon fusion production and (b) b-associated production of the \PHiggs boson
+in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
 the b-associated production cross-section is larger at high \tanb.}
@@
 \begin{center}
-\subfloat[BR($\PHiggs \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
-\subfloat[BR($\PHiggsps \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
+\subfloat[$\mathcal{B}(\PHiggs \rightarrow \tau\tau)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
+\subfloat[$\mathcal{B}(\PHiggsps \rightarrow \tau\tau)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
 \end{center}
@@
 corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
-A large area of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ 
+A large area of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ 
 scenario contains a light Higgs boson with a mass compatible with
@@
 The mass of the light Higgs
-boson in the $m_{h}^{\text{mod}+}$ scenario is shown in 
+boson in the $m_{\PHiggslight}^{\text{mod}+}$ scenario is shown in 
 figure \ref{fig:mhmodp_mh}a, illustrating that the mass 
@@
 
-Two approches for the definition of an MSSM scenario that gives
+Two approches for the definition of an \ac{MSSM} scenario that gives
 access to the low-\tanb~region have been developed, they will be
@@
 \begin{center}
-\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
+\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
 \subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
@@
 \caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
-\tanb~in the $m_{h}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
-of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
+\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
+of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
 indicate masses lower than $122\,\GeV$. The figures shows that
 the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
-part of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
+part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
 the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere.}
@@
 
-The production cross--sections of the \PHiggs and \PHiggsps bosons are
-qualitatively similar to those in other MSSM scenarios. Gluon fusion is dominant
+The production cross sections of the \PHiggs and \PHiggsps bosons are
+qualitatively similar to those in other \ac{MSSM} scenarios. Gluon fusion is dominant
 at low \tanb, with b-associated production being more important at high \tanb.
@@
 of different searches performed with the \acs{CMS} detector during Run 1 of the \acs{LHC}
-in the $m_{h}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
+in the $m_{\PHiggslight}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
 and hMSSM scenarios (figure \ref{fig:bsm_summary}b). The direct search for heavier Higgs bosons decaying into pairs
 of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb, with searches for 
-heavy Higgs bosons decaying to $b\bar{b}$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
+heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
 Searches for heavy Higgs bosons decaying to WW and ZZ are able to exclude part of the low-\tanb-region. In the 
-hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA=$250--350\,\GeV$.
+hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250--350\,\GeV$.
 The red exclusion contour in figure \ref{fig:bsm_summary}b is the re-interpretation of the analysis presented in
@@
 Similar searches have been performed by ATLAS \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
-are being searched for in other channels too, with some results for decays into \ttbar \cite{ATLASHttbar}, 
+are being searched for in other channels too, with some results for decays into $\Ptop\Ptop$ \cite{ATLASHttbar}, 
 ZZ \cite{CMSHZZ2016,ATLASHZZ2016}, and WW \cite{ATLASHeavyHWW} already public.
@@
 \begin{center}
-\subfloat[$m_{h}^{\text{mod+}}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-a.pdf}}
+\subfloat[$m_{\PHiggslight}^{\text{mod+}}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-a.pdf}}
 \subfloat[hMSSM scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-b.pdf}}
 \end{center}
-\caption[Summary of the interpretations of Run 1 BSM Higgs searches at CMS in the $m_{h}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
+\caption[Summary of the interpretations of Run 1 BSM Higgs searches at CMS in the $m_{\PHiggslight}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{\PHiggslight}^{\text{mod+}}$ and (b) the
 hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
 scenarios. The results from \ac{MSSM} Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
-space than any of the other searches. The \ac{MSSM} Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
-of the high-\tanb~region, with searches for Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
+space than any of the other searches. The \ac{MSSM} Higgs to $\Pbottom\Pbottom$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
+of the high-\tanb~region, with searches for Higgs to $\PW\PW$ or $\PZ\PZ$ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{\PHiggslight}^{\text{mod+}}$ 
 scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around $300\,\GeV$ in the 
 hMSSM scenario are excluded instead by constraints from \ac{SM} Higgs boson measurements (magenta). In this scenario small
-areas of the low-\tanb~region are also excluded by the searches for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
-and the search for $H\rightarrow hh \rightarrow bb\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}
+areas of the low-\tanb~region are also excluded by the searches for $\PHiggs\rightarrow \PHiggslight\PHiggslight \rightarrow \Pbottom\Pbottom\tau\tau$ and $\PHiggsps\rightarrow \PZ\PHiggslight \rightarrow \ell\ell\tau\tau$ (red)
+and the search for $\PHiggs\rightarrow \PHiggslight\PHiggslight \rightarrow \Pbottom\Pbottom\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}
 \label{fig:bsm_summary}

### 2017-02-22 Hhh/Hhh.tex
Some more editing

@@
 reduce the contribution of \Zmm background events, the hadronic tau is 
-also required to pass the tight working point of the anti-$\Pgm$ discriminator
-and the loose working point of the cut-based anti-$\Pe$ discriminator.
+also required to pass the tight working point of the anti-muon discriminator
+and the loose working point of the cut-based anti-electron discriminator.
 
@@
 relative isolation is required to be $I_{\text{rel}}^{\Pe} < 0.1$. The requirements placed on the
-hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
-where the loose working point is required, and the anti-$\Pe$ discriminator, where the medium
+hadronic tau are similar to those required in the \mutau channel, apart from the anti-muon discriminator,
+where the loose working point is required, and the anti-electron discriminator, where the medium
 working point of the MVA discriminator is required.

### 2017-02-22 MSSM/MSSM.tex
Some more editing

@@
 here correspond to those from an analysis peformed on a dataset collected
-during the first half of the 2016 p-p running period of the \ac{LHC}. This dataset
-corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
-detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
+during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
+%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
+%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
+The \etau, \mutau, \tautau and \emu final
 states of the di-tau pair were studied. The results of this search are 
@@
 various \ac{MC} event generators. Signal samples
-for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\APbottom\phi$
+for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
 production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
@@
 \ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
-\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{Powheg} \cite{powheg1,powheg2,powheg3}.
-
-Single-top and \ttbar background samples are generated using \texttt{Powheg},
+\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{POWHEG} \cite{powheg1,powheg2,powheg3}.
+
+Single-top and \ttbar background samples are generated using \texttt{POWHEG},
 with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
@@
 matrix element generator. Samples containing both a mixture
-of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
+of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
 are generated. These exclusive samples increase the available number of
@@
 fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
-only included in the \emu channel, are generated in part with \texttt{MadGraph 5} and in
-part with \texttt{MadGraph5\_aMC@NLO}.
+only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
+with \texttt{MadGraph5\_aMC@NLO}.
 
@@
 followed by additional selection criteria. For the \etau
-and \mutau channels we only trigger on the electron or muon. 
-While the lepton + hadronic tau cross triggers that are also available
+and \mutau channels events are selected by only triggering on the electron or muon. 
+While the lepton + hadronic tau cross-triggers that are also available
 allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
@@
 in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
-\mutau channel, with the signal normalised to 4000 times its \xsbr 
- at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario overlaid.
-In the \emu channel two dedicated electron-muon cross triggers
+\mutau channel. The signal is overlaid, with a normalisation of 4000 times its \xsbr 
+ at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario.
+In the \emu channel two dedicated electron-muon cross-triggers
 are used. These have significantly lower \pT~cuts 
 on the two leptons than the single lepton triggers. For the 
-\tautau channel a di-tau cross-trigger is used.
+\tautau channel a di-tau trigger is used.
 
@@
 their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
-on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
+on the electrons and muons is $1\,\GeV$ above the \pT~threshold of the trigger. The
 hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
@@
 hadronic taus. This selection is driven by the $\eta$ range covered by the tracker and
-that is thus used for the reconstruction of the particles. For some of the
-channels the used trigger is restricted in $\eta$. If that is the case
-then the cut is chosen to align with the trigger restrictions.
+so the range that is used for the reconstruction of the particles. For some of the
+channels the trigger that is used is restricted in $\eta$. If that is the case
+the cut is chosen to be the same as the trigger restrictions.
 As an illustration figure \ref{fig:mt_muonpt}b shows
@@
 
-\subsection{Pair selection and vetos}
+\subsection{Pair selection and vetoes}
 \label{sec:mssm_eventsel_pairs}
@@
  is chosen, as isolated candidates are less likely 
-to be jets misreconstructed
+to be jets mis-reconstructed
 as leptons or hadronic taus.
@@
 To prevent overlap with other channels, events are rejected
-if there are muons and electrons, other than those in the selected pair,
+if there are muons or electrons, other than those in the selected pair,
 with \pT~$>10\,\GeV$ and passing loose ID and isolation requirements.
 This also reduces backgrounds from di-boson events. The application
-of these vetos means that the selection of the pair with the
+of these vetoes means that the selection of the pair with the
 two most isolated candidates is only important where hadronic
@@
 \label{sec:mssm_eventsel_mt}
-The trigger only requires a muon at \ac{L1}, while at the level of the \ac{HLT}
-loose identification and isolation criteria are applied to this muon.
+The trigger only requires a muon at \ac{L1}, to which loose identification and
+isolation criteria are applied at the level of the \ac{HLT}
 
 The offline event selection requires an oppositely charged
-muon and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
-The minimum \pT~of the muon is required to be $23\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
+muon and hadronically decaying tau, which are separated by $\Delta R > 0.5$.
+The muon is required to have \pT~$> 23\,\GeV$, and $|\eta| < 2.1$. %due to trigger conditions
 Additional ``medium'' identification requirements are placed on the muon, and the impact
-parameters of the muon must satisfy $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$. The muon is also
+parameters must satisfy $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$. The muon is also
 required to be isolated, with $I_{\text{rel}}^{\mu}<0.15$, where the isolation variable
@@
 
-The hadronic tau needs to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
-is required to be reconstructed by the HPS algorithm and to pass the medium
+The hadronic tau needs to have \pT~$>30\,\GeV$ and $|\eta|<2.3$.
+It is required to be reconstructed by the HPS algorithm and to pass the medium
 working point of the MVA isolation discriminator. The impact parameter $d_{z}$ is
@@
 
-The selection on the muon's relative isolation is chosen after comparing
+The selection on the relative isolation of the muon is chosen after comparing
 the performance of several isolation variables, using different relative isolation selections.
 This was based on a simple \mutau channel
-event selection as described above, only varying the isolation requirements.
+event selection as described above, with only the isolation being varied.
 The selection was optimised based on two figures of merit, both of
-which consider \Ztautau as the signal and the other backgrounds
-as background. The first figure of merit used is the number of signal events divided by the
+which consider \Ztautau, instead of the Higgs processes, as the signal.
+The first figure of merit used is the number of signal events divided by the
 square root of the number of background events, $S/\sqrt{B}$, after
-the selection. The aim with this figure of merit is to choose
-the isolation selection that maximises it. The second figure of merit
+the selection. The aim is to identify 
+the isolation selection that maximises $S/\sqrt{B}$. The second figure of merit
 is the uncertainty interval on the best-fit value for a maximum-likelihood fit
@@
 to the one given for electrons in equation \ref{eqn:electron_reliso} with 
-isolation cone sizes of $\Delta R$ 0.3 and 0.4. In addition
+isolation cone sizes of 0.3 and 0.4 in $\Delta R$. In addition
 to this a very similar
@@
 size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
-\ref{fig:mssm_selection_mt_muons}b. As both figures of merit do not
-change so much with varying isolation requirements we can see that this analysis
-is not so sensitive to fake, nonisolated muons. The choice of isolation variable is therefore
+\ref{fig:mssm_selection_mt_muons}b. Both figures of merit do not
+change significantly when varying the isolation requirements meaning that this analysis
+is not so sensitive to fake, non-isolated muons. The choice of isolation variable is therefore
 driven mostly by simplicity and consistency with other \ac{CMS} analyses.
@@
 for various selections of the $\Delta\beta$-corrected
-isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
-the $\Delta\beta$-corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
+isolation variable with a cone size of $\Delta R = 0.4$ (solid circles) and $\Delta R = 0.3$ (open circles),
 the $\Delta\beta$-corrected isolation variable including electrons and muons in the isolation
@@
 choice of hadronic tau isolation working point provide two competing
-effects and therefore they are optimised in a 2D-optimisation. 
-The pre-fit expected upper limits on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
+effects and therefore they are optimised simultaneously.
+The ``pre-fit'' expected upper limits, determined without the fit
+to the real observed data, on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
 production with decay into $\Pgt\Pgt$ at several mass points 
@@
 Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
-tau isolation working point selection on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
-\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
+tau isolation working point selections on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
+\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
 %\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}

### 2017-02-22 Theory/Theory.tex
Some more editing

@@
 \mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
-m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
--(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix},
+m_{\PHiggsps}^2\sin{\beta}^2 + m_{\PZ}^2\cos{\beta}^2 & -(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta}\\
+-(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta} & m_{\PHiggsps}^2\cos{\beta}^2+m_{\PZ}^2\sin{\beta}^2 \end{pmatrix},
 \end{equation}
@@
 \begin{equation}\label{eqn:scalarmass}
-m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}].
+m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\cos{2\beta}^2}].
 \end{equation}
@@
 \begin{equation}\label{eqn:mh_upper}
-m_{h} \leq m_{Z},
+m_{\PHiggslight} \leq m_{\PZ},
 \end{equation}
@@
 \begin{equation}\label{eqn:alpha_constraint}
-\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.
+\cos{(\beta-\alpha)}^2 = \frac{m_{\PHiggslight}^2(m_{\PZ}^2-m_{\PHiggslight}^2)}{m_{\PHiggsps}^2(m_{\PHiggs}^2-m_{\PHiggslight}^2)}.
 \end{equation}
 
-The requirement that $m_h$ be less than the mass of the Z boson, $91.2\,\GeV$, seems 
+The requirement that $m_{\PHiggslight}$ be less than the mass of the \PZ boson, $91.2\,\GeV$, seems 
 problematic at first, as it is known that there is a Higgs state with a mass of $125\,\GeV$. However,
-the tree-level masses and couplings of the Higgs bosons in the MSSM can be
+the tree-level masses and couplings of the Higgs bosons in the \ac{MSSM} can be
 significantly altered by radiative corrections. The dominant effect is from
@@
 
-In the \textit{decoupling limit}, when \mA$>>m_{Z}$ and $\cos{(\beta-\alpha)}$ tends
+In the \textit{decoupling limit}, when $m_{\PHiggsps} \gg m_{\PZ}$ and $\cos{(\beta-\alpha)}$ tends
 to 0, the mixing
@@
 Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
-in the $m_{h}^{\text{mod+}}$ scenario
+in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
 which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
-The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
+The branching ratio into di-tau pairs is large for \tanb~$= 30$. The branching ratios 
  of the \PHiggsps boson follow a similar pattern.
@@
 \end{center}
-\caption{Branching ratios of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario,
+\caption[Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario]{Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario,
 at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $b\bar{b}$ (red) 
@@
 vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
-bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
+bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW or \PZ associated
 production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
@@
 Due to the negative top-bottom loop interference effect the gluon fusion cross section decreases with increasing \tanb~up
-to around \tanb=3, when the cross section starts to increase with increasing \tanb~again.
+to around \tanb~$=3$, when the cross section starts to increase with increasing \tanb~again.
 
@@
 of the different Higgs states to bosons and fermions. In its most general
-form, there are 9 free parameters in the potential of a CP-conserving 2HDM. 
+form, there are nine free parameters in the potential of a CP-conserving 2HDM. 
 These are taken as \tanb, the mixing angle $\alpha$, already discussed in 
@@
 \end{center}
-\caption[Inclusive production cross--section times branching ratio for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production cross--section times branching ratio for an example
+\caption[Inclusive production \xsbr for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production \xsbr for an example
 of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
@@
 A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
-trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_t$, $A_b$ and $A_{\Pgt}$) and the 
+trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_{\Ptop}$, $A_{\Pbottom}$ and $A_{\Pgt}$) and the 
 stop, sbottom and stau mixing parameters ($X_t$, $X_b$ and $X_{\tau}$) are also fixed.
@@
 Some of these parameters can be related to each other. For example,
-$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as:
+$X_{\Ptop}$, $X_{\Pbottom}$ and $X_{\Pgt}$ can be expressed as:
 \begin{equation}\label{eqn:trilinear_couplings}
 \begin{split}
-&X_t = A_t-\mu_{\text{MSSM}}\cot{\beta},\\
-&X_b = A_b-\mu_{\text{MSSM}}\tan{\beta},\\
+&X_{\Ptop} = A_{\Ptop}t-\mu_{\text{MSSM}}\cot{\beta},\\
+&X_{\Pbottom} = A_{\Pbottom}-\mu_{\text{MSSM}}\tan{\beta},\\
 &X_{\Pgt} = A_{\Pgt} - \mu_{\text{MSSM}}\tan{\beta}.
@@
 The $m_{\PHiggslight}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
-is a modification of the $m_{\PHiggslight}^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
+is a modification of the $m_{\PHiggslight}^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_{\PHiggslight}^{\text{max}}$ scenario, which
 was used for interpretations of \ac{MSSM}
@@
 The remaining parameters are set as $\mu_{\text{MSSM}}=200\,\GeV$, $m_{\tilde{g}} = 1.5\,\TeV$,
-$m_{\tilde{\ell}_3} = 1\,\TeV$, and $A_b=A_t=A_{\Pgt}$. 
+$m_{\tilde{\ell}_3} = 1\,\TeV$, and $A_{\Pbottom}=A_{\Ptop}=A_{\Pgt}$. 
 %Figure \ref{fig:mhmodp_mh}a
@@
 gluon fusion and b-associated production of the \PHiggs boson 
-in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
+in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. Gluon fusion 
 production dominates at low \tanb, while b-associated production has a larger cross section
@@
 Two approches for the definition of an \ac{MSSM} scenario that gives
-access to the low-\tanb~region have been developed, they will be
+access to the low \tanb~region have been developed, they will be
 discussed in the next sections.
 
-\subsubsection{The low-\tanb-scenario}
+\subsubsection{The low-\tanb~scenario}
 \label{sec:theory_BSM_model_lowtb}
-In the low-\tanb-scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
+In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
 the radiative corrections are tuned to obtain light 
 Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
-Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1-4 and 
+Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1--4 and 
 \mA~$150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
@@
 space, 
-$M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
+$M_{\text{SUSY}}$ is not fixed but varies between a few $\TeV$ and $100\,\TeV$, while
 varying the parameter $X_t$ as:
@@
 \begin{split}
-\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2,\\
-2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
-8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
+\tan{\beta} \leq 2 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 2,\\
+2 < \tan{\beta} \leq 8.6 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
+8.6 < \tan{\beta} &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.
 \end{split}
 \end{equation}
-The other trilinear couplings are set to 2 TeV, with $\mu_{\text{MSSM}}$ set to 1.5 TeV and $M_2$ to 2 TeV.
+The other trilinear couplings are set to $2\,\TeV$, with $\mu_{\text{MSSM}}$ set to $1.5\,\TeV$ and $M_2$ to $2\,\TeV$.
 
@@
 taken into account, as this is the element that involves the stop-top correction
-and so $\Delta\mathcal{M}^2_{22} >> \Delta\mathcal{M}^2_{12},\Delta\mathcal{M}^2_{11}$. 
+and so $\Delta\mathcal{M}^2_{22} \gg \Delta\mathcal{M}^2_{12},\Delta\mathcal{M}^2_{11}$. 
 Finally, all SUSY particles are assumed to be heavy enough not to be
@@
 \label{eqn:hmssm_deltam22}
-\Delta\mathcal{M}^2_{22} = \frac{m_h^2(m_A^2+m_Z^2 - m_h^2) - m_A^2m_Z^2\text{cos}^22\beta}{m_Z^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_h^2},
+\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_{\PHiggslight}^2},
 \end{equation}
@@
 \begin{split}
-&m^2_H = \frac{(m_A^2+m_Z^2-m_h^2)(m_z^2\cos{\beta}^2+m_A^2\sin{\beta}^2 - m_A^2m_Z^2\cos{2\beta}^2}{m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2-m_h^2},\\
-&\tan{\alpha} = -\frac{(m_Z^2+m_A^2)\cos{\beta}\sin{\beta}}{m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2-m_h^2}.
+&m^2_{\PHiggs} = \frac{(m_{\PHiggsps}^2+m_{\PZ}^2-m_{\PHiggslight}^2)(m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggsps}^2m_{\PZ}^2\cos{2\beta}^2}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2},\\
+&\tan{\alpha} = -\frac{(m_{\PZ}^2+m_{\PHiggsps}^2)\cos{\beta}\sin{\beta}}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2}.
 \end{split}
 \end{equation}
-Combining this with the Hhh coupling,
+Combining this with the $\PHiggs$-$\PHiggslight\PHiggslight$ coupling,
 \begin{equation}
 \label{eqn:hmssm_Hhh}
-\lambda_{Hhh} = \lambda_{Hhh,tree} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_Z^2\sin{\beta}}\cos{\alpha}^2,
+\lambda_{\PHiggs\PHiggslight\PHiggslight} = \lambda_{\PHiggs\PHiggslight\PHiggslight,\text{tree}} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_{\PZ}^2\sin{\beta}}\cos{\alpha}^2,
 \end{equation}
@@
 is only well defined in regions where the denominator in equations
-\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_Z^2\cos{\beta}^2+m_A^2\sin{\beta}^2 - m_h^2$, is nonzero. 
+\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggslight}^2$, is nonzero. 
 This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
@@
 heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
-Searches for heavy Higgs bosons decaying to WW and ZZ are able to exclude part of the low-\tanb-region. In the 
+Searches for heavy Higgs bosons decaying to $\PW\PW$ and $\PZ\PZ$ are able to exclude part of the low \tanb~region. In the 
 hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250--350\,\GeV$.
@@
 have been performed with the \acs{CMS} detector. The results of these searches will be presented in chapter \ref{chap:mssm}. 
-Similar searches have been performed by ATLAS \cite{ATLASMSSMtautau2016}. Neutral BSM Higgs bosons
+Similar searches have been performed by ATLAS \cite{ATLASMSSMtautau2016}. Neutral \ac{BSM} Higgs bosons
 are being searched for in other channels too, with some results for decays into $\Ptop\Ptop$ \cite{ATLASHttbar}, 
-ZZ \cite{CMSHZZ2016,ATLASHZZ2016}, and WW \cite{ATLASHeavyHWW} already public.
+$\PZ\PZ$ \cite{CMSHZZ2016,ATLASHZZ2016}, and $\PW\PW$ \cite{ATLASHeavyHWW} already public.
 In addition, searches for charged

### 2017-02-22 MSSM/MSSM.tex
More editing

@@
 production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
-working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$ production process with decay into $\Pgt\Pgt$,
-as a function of tau isolation working point (from very loose to very very tight) and
-of \mT~selection from \mT~$<20\,\GeV$ to \mT~$<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi\rightarrow\Pgt\Pgt$ process,
+as a function of the tau isolation working point (from very loose to very very tight) and
+of the \mT~selection from $\mTm<20\,\GeV$ to $\mTm<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
 for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
@@
 (b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
-at the tight working point and \mT~$<30\,\GeV$ in green, the medium working point and \mT~$<40\,\GeV$ in red,
-the loose working point and \mT~$<50\,\GeV$ in blue and the very loose working point and \mT~$<60\,\GeV$ in black. Loosening
-the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
+at the tight working point and $\mTm<30\,\GeV$ in green, the medium working point and $\mTm<40\,\GeV$ in red,
+the loose working point and $\mTm<50\,\GeV$ in blue and the very loose working point and $\mTm<60\,\GeV$ in black. Loosening
+the tau isolation working point and \mT~selection improves the limits at higher mass and
 degrades them at low mass.}
@@
 The selection was optimised for masses around $800\,\GeV$--$1\,\TeV$, by
-using the medium hadronic tau isolation working point and a selection on \mT~$<40\,\GeV$.
+using the medium hadronic tau isolation working point and a selection on $\mTm<40\,\GeV$.
 
@@
 of the analysis for high mass points, while recovering some of the loss of loosening 
-tau isolation working point and \mT~cut. The reason for this is that when using \pT~$>30\,\GeV$ 
-fewer background events are selected. The effect of the increased hadronic tau \pT~selection on the 
+the tau isolation working point and \mT~cut. The reason for this is that when using $\pTm >30\,\GeV$ 
+the loss of background events exceeds the loss of signal events. The effect of the increased hadronic tau \pT~selection on the 
 upper limits for the $\Pg\Pg\phi$ production process is shown
-in figure \ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
-in figure \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
-obtained by increasing the \pT~selection is sizeable, for $\Pbottom\Pbottom\phi$ events the effect is much
+in figure~\ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
+in figure~ \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
+obtained by increasing the \pT~selection is sizeable; for $\Pbottom\Pbottom\phi$ events the effect is much
 less pronounced.
@@
 different hadronic tau \pT~cuts.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
-limits when using the medium hadronic tau isolation working point and \mT~$<40\,\GeV$ selection using a minimum
+limits when using the medium hadronic tau isolation working point and $\mTm <40\,\GeV$ selection using a minimum
 hadronic tau \pT~selection of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
-circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
+circles show the limits using the tight tau isolation working point and $\mTm<30\,\GeV$. The limits on
 the $\Pg\Pg\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
@@
 a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
-criteria are made on the electron with the \ac{HLT}.
+criteria are applied to the electron with the \ac{HLT}.
 
 The offline event selection requires an oppositely charged
-electron and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
-The minimum \pT~of the electron is required to be $26\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
-The impact parameters of the electron are required to satisfy
+electron and hadronically decaying tau, which are separated by $\Delta R > 0.5$.
+The minimum electron is required to have $\pTm >26\,\GeV$ and $|\eta| < 2.1$. %due to trigger conditions
+The impact parameters are required to satisfy
 $d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$, and the electron
-must pass additional identification criteria. The working point of the
-MVA identification discriminator that is used corresponds to a cut on the discriminator
-which selects electrons from \Zee events with 80\% efficiency. In addition the
+must pass additional identification criteria. The chosen working point of the
+MVA identification discriminator was designed
+to select electrons from \Zee events with 80\% efficiency. In addition the
 electron needs to be isolated, $I_{\text{rel}}^{\Pe} < 0.1$, with the relative isolation variable calculated with a cone size of 0.3.
 
-The hadronic tau is required to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
-and is required to be reconstructed by the HPS algorithm and to pass the medium
+The hadronic tau is required to have $\pTm > 30\,\GeV$, $|\eta|<2.3$,
+to be reconstructed by the HPS algorithm and to pass the medium
 working point of the MVA isolation discriminator. The impact parameter $d_{z}$ of the
@@
 A topological selection on the \mT~variable is also made in this channel to reject \Wjets events. 
-The value of \mT~$< 50\,\GeV$ that is used is obtained by performing a 2D optimisation where the \mT~selection
-and hadronic tau isolation working point are varied at the same time. The same considerations as
+The value of $\mTm< 50\,\GeV$ that is used is obtained by performing a simultaneous optimisation of the \mT~selection
+and hadronic tau isolation working point. The same considerations as
 for the \mutau channel apply, as illustrated in figure \ref{fig:mssm_gradcuts_et}.
@@
 (b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
-at the tight working point and \mT~$<40\,\GeV$ in green, the medium working point and \mT~$<50\,\GeV$ in red,
-the loose working point and \mT~$<60\,\GeV$ in blue and the very loose working point and \mT~$<70\,\GeV$ in black. Loosening
-the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
+at the tight working point and $\mTm<40\,\GeV$ in green, the medium working point and $\mTm<50\,\GeV$ in red,
+the loose working point and $\mTm<60\,\GeV$ in blue and the very loose working point and $\mTm <70\,\GeV$ in black. Loosening
+the tau isolation working point and \mT~selection improves the limits at higher mass and
 degrades them at low mass.}
@@
 hadronic tau isolation cuts.]{Pre-fit expected limits on \xsbr in the \etau channel for (a) $\Pg\Pg\phi$ production and (b) $\Pbottom\Pbottom\phi$ production. The
-limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
+limits using the medium hadronic tau isolation working point and $\mTm<40$ GeV selection using a minimum
 hadronic tau \pT~cut of $20\,\GeV$ (red circles), $30\,\GeV$ (blue circles) and $40\,\GeV$ (black circles) are shown. The green
-circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
+circles show the limits using the tight tau isolation working point and $\mTm<40\,\GeV$. The limits on
 the $\Pg\Pg\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
@@
 \label{sec:mssm_eventsel_tt}
-The trigger in the \tautau channel requires two hadronic taus at \ac{L1} and the \ac{HLT}
-applies loose identification and isolation criteria to these hadronic taus.
+The trigger in the \tautau channel requires two hadronic taus at \ac{L1} to which loose identification
+and isolation criteria are applied in the \ac{HLT}
 
 The offline event selection requires both hadronic taus to be oppositely charged, separated
-by $\Delta R > 0.5$, have \pT~of at least $40\,\GeV$ and satisfy $|\eta|<2.1$. Both taus need
+by $\Delta R > 0.5$, to have $\pTm>40\,\GeV$ and to satisfy $|\eta|<2.1$. Both taus need
 to be reconstructed by the HPS algorithm, and their impact parameter $d_{z}$ must be less than $0.2\,\cm$.
@@
 The tight working point of the isolation discriminator is chosen such that
-the channel is near-optimal at high mass, while not losing too much sensitivity in the low--intermediate mass range.
-This is illustrated in figure \ref{fig:mssm_tauid_tt} for the $\Pg\Pg\phi$ process.
+the channel is near-optimal at high mass, while not losing too much sensitivity in the low to intermediate mass range.
+This is illustrated in figure \ref{fig:mssm_tauid_tt}a for the $\Pg\Pg\phi$ process and in figure \ref{fig:mssm_tauid_tt}b for the $\Pbottom\Pbottom\phi$ process.
 
@@
 medium (green), tight (red) and very tight working point of the tau isolation discriminator.
-The pattern is roughly the same as in the \etau and \mutau channels, with looser selections preferred at high
+The pattern is similar to that in the \etau and \mutau channels, with looser selections preferred at high
 mass.}
@@
 that both require an electron and muon at \ac{L1} and apply loose ID and
-isolation requirements to these objects at \ac{HLT}. The \pT~requirements on
+isolation requirements to these objects in the \ac{HLT}. The \pT~requirements on
 the electron and muon are different in the two triggers, thus using the combination of the two
@@
 Offline, the electron and muon are required to be oppositely charged
-and separated by $\Delta R >0.3$.
-The electron needs to have a minimum \pT~of $13\,\GeV$ and have $|\eta|< 2.5$. As
-in the \etau channel the electron's impact parameters have to 
-satisfy $d_{xy} < 0.045\,\cm$ and $d_{z}<0.2\,\cm$. The additional
-identification requirement is identical to the criterium applied to electrons in the \etau channel.
+and separated by $\Delta R > 0.3$.
+The electron needs to have $\pTm>13\,\GeV$ and $|\eta|< 2.5$. As
+in the \etau channel the impact parameters have to 
+satisfy $d_{xy} < 0.045\,\cm$ and $d_{z}<0.2\,\cm$. The same selection 
+on the MVA identification discriminator as in the \etau channel is applied.
 The electron also needs to be isolated, $I_{\text{rel}}^{\Pe}<0.15$, where the relative isolation variable is calculated
@@
 
-The muon needs to have a \pT~of at least $10\,\GeV$, $|\eta|<2.4$ and 
+The muon needs to have $\pTm>10\,\GeV$, $|\eta|<2.4$ and 
 its impact parameters need to be $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$.
-In addition to the kinematic requirements the muon must
-pass the medium identification criteria and be isolated with $I_{\text{rel}}^{\Pgm} < 0.2$,
+In addition to these requirements the muon must
+pass the ``medium'' identification criteria and be isolated with $I_{\text{rel}}^{\Pgm} < 0.2$,
 where the relative isolation variable is calculated using a cone size of 0.4.
 
-Because a combination of triggers is used, one with electron \pT~$> 23\,\GeV$ and muon \pT~$>8\,\GeV$ 
-and one with muon \pT~$> 23\,\GeV$ and electron \pT~$> 13\,\GeV$, the object firing
+Because a combination of triggers is used, one with electron $\pTm > 23\,\GeV$ and muon $\pTm>8\,\GeV$ 
+and one with muon $\pTm > 23\,\GeV$ and electron $\pTm > 13\,\GeV$, the object firing
 the higher \pT~trigger leg needs to have a transverse momentum
@@
 \end{align}
-This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy \pT+\MET~onto 
+This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy, \pT+\MET, onto 
 the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
@@
 \ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
-for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and diboson
+for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and di-boson
 events. 
@@
 \caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
-in the \emu channel.]{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
-\emu channel\cite{CMS-PAS-HIG-16-037}.}
+in the \emu channel.]{(a) Reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
+\emu channel \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_dzeta}
@@
 are normalised to 100 times their \xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$
-scenario. It is visible how the signal-sensitive bins motivate the choice of categories.}
+scenario. The signal-sensitive bins motivate the choice of categories.}
 \label{fig:mssm_cats_mt}
@@
 to 100 times their \xsbr at \mA~$=1\,\TeV$ and 
-\tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. From the distribution of the
-gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
-see that the vast majority of these signal events do not have any b-tagged jets. To
-target this production mode we can use a category which requires zero b-tagged jets.
-From the b-associated signal in the same figure we also see that the majority of $\Pbottom\Pbottom\phi$
-signal events do not have any b-tagged jets either: either the b-jets in these events 
+\tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. 
+The distribution of the
+gluon fusion signal in figure \ref{fig:mssm_cats_mt}b shows that
+the vast majority of these signal events do not have any b-tagged jets. To
+target this production mode a category which requires nob-tagged jets can be used.
+The same figure also shows that the majority of $\Pbottom\Pbottom\phi$
+signal events do not have any b-tagged jets: either the b-jets in these events 
 are too soft, or they do not pass the b-tagging requirements. This means that the category
-which requires zero b-tagged jets
-is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal. To target
+which requires no b-tagged jets
+is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal. To target the remainder of 
 the $\Pbottom\Pbottom\phi$ signal, another category with at least one b-tagged jet is defined. 
-From the $\Pbottom\Pbottom\phi$ signal in figure \ref{fig:mssm_cats_mt}b it can be seen that there is not
-such a large proportion of events with more than one b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
-it is visible that the \ttbar background starts to become more sizeable for events with more than
+The $\Pbottom\Pbottom\phi$ signal in figure \ref{fig:mssm_cats_mt}b shows that there is not
+such a large proportion of events with more than one b-tagged jet. Figure \ref{fig:mssm_cats_mt}a
+shows that the \ttbar background starts to become larger for events with more than
 one jet. The definition of the category that targets the $\Pbottom\Pbottom\phi$ signal is therefore chosen with the inclusion
-of the jet veto, such that the region where the \ttbar background becomes larger is excluded, 
+of a jet veto, such that the region where the \ttbar background becomes larger is excluded, 
 while retaining a large proportion of the $\Pbottom\Pbottom\phi$ signal.
@@
 \setlength{\itemsep}{-\baselineskip}
-\item \textbf{No b-tag}: zero b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
+\item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
 \item \textbf{b-Tag}: At least one b-tagged jet, at most one 
-jet with \pT~$>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
-Due to the different phase space considered for
-b-tagging than for default jet reconstruction this requirement does not necessarily
-mean there will be only one b-tagged jet in the event.
+jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
+Due to the lower \pT~requirement considered for
+b-tagging compared with the requirement for the jet veto, it is still possible for there
+to be more than one b-tagged jet in the event.
 \end{itemize}

### 2017-02-23 MSSM/MSSMThesisResources/plotLimitGrid.py
Adding script / root files for plotting combined interpretations

@@ -1,0 +1,350 @@
+#!/usr/bin/env python
+import CombineHarvester.CombineTools.plotting as plot
+import ROOT
+import argparse
+
+ROOT.PyConfig.IgnoreCommandLineOptions = True
+ROOT.gROOT.SetBatch(ROOT.kTRUE)
+
+parser = argparse.ArgumentParser(
+    formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+parser.add_argument(
+    'input', help="""ROOT file containing the output of the
+    combineTool.py AsymptoticGrid or HybridNewGrid methods""")
+parser.add_argument(
+    '--output', '-o', default='limit_grid_output', help="""Name of the output
+    plot without file extension""")
+parser.add_argument(
+    '--contours', default='exp-2,exp-1,exp0,exp+1,exp+2,obs', help="""List of
+    contours to plot. These must correspond to the names of the TGraph2D
+    objects in the input file""")
+parser.add_argument(
+    '--bin-method', default='BinEdgeAligned', help="""One of BinEdgeAligned or
+    BinCenterAligned. See plotting.py documentation for details.""")
+parser.add_argument(
+    '--debug-output', '-d', help="""If specified, write the contour TH2s and
+    TGraphs into this output ROOT file""")
+parser.add_argument(
+    '--CL', default=0.95, help="""Confidence level for contours""")
+parser.add_argument(
+    '--x-title', default='m_{A} (GeV)', help="""Title for the x-axis""")
+parser.add_argument(
+    '--y-title', default='tan#beta', help="""Title for the y-axis""")
+parser.add_argument(
+    '--x-range', default=None, type=str, help="""x-axis range""")
+parser.add_argument(
+    '--y-range', default=None, type=str, help="""y-axis range""")
+parser.add_argument(
+    '--cms-sub', default='Internal', help="""Text below the CMS logo""")
+parser.add_argument(
+    '--scenario-label', default='', help="""Scenario name to be drawn in top
+    left of plot""")
+parser.add_argument(
+    '--title-right', default='', help="""Right header text above the frame""")
+parser.add_argument(
+    '--title-left', default='', help="""Left header text above the frame""")
+parser.add_argument(
[…]

### 2017-02-23 MSSM/MSSM.tex
Adding combined model interpretations

@@
 
-Interpretations in MSSM benchmark scenarios to be added.
+Figure \ref{fig:mssm_mhmodp_20152016}a shows the exclusion obtained in the $m_{\PHiggslight}^{\text{mod+}}$ 
+scenario by combining the 2015 and 2016 analyses. Figure \ref{fig:mssm_mhmodp_20152016}b shows this exclusion
+in the hMSSM scenario. On both figures the expected and observed exclusion from the
+2016 analysis only are overlaid, which shows how the combination increases the
+size of the excluded area. In the hMSSM scenario the feature already visible in figure \ref{fig:mssm_mhmodp_2016}b
+has grown by combining the two datasets. Future analyses using even more data will be able to fully close
+the gap between the two excluded regions.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_mhmodp_cmb.pdf}}~\\
+\subfloat[hMSSM scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_hMSSM_cmb.pdf}}
+\end{center}
+\caption[Exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
+scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusion in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+obtained by the combination
+of all channels of the 2015 and 2016 \AHtotautau analyses. The blue shaded area bounded by the 
+solid black line is the observed exclusion, with the dashed black line the
+expected exclusion. The light and dark grey bands indicate
+the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.
+The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
+is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$. The dashed (solid)
+blue lines indicate the expected (observed) exclusion from the 2016 analysis alone.}
+\label{fig:mssm_mhmodp_20152016}
+\end{figure}

### 2017-02-23 MSSM/MSSM.tex
More MSSM chapter editing

@@
 m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
-(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}.
+(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2},
 \end{equation}
-
-$m_{\text{T}}(1,2)$ is defined as,
+where $m_{\text{T}}(1,2)$ is defined as,
 \begin{equation}\label{eqn:mttot_12}
@@
 \end{equation}
-
 This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
@@
 The separation between signal and backgrounds is illustrated in figure
-\ref{fig:mttot_sigseps}, where figure \ref{fig:mttot_sigseps}a shows the total transverse mass
+\ref{fig:mttot_sigseps}. Figure \ref{fig:mttot_sigseps}a shows the total transverse mass
 distribution of the QCD
@@
 
-\section{\acs{MC} to data correction factors}
+\section{\acl{MC} simulation to data correction factors}
 \label{sec:mssm_mccorrs}
-Because \ac{MC} samples are used for the signal prediction, and 
+Because simulated samples are used for the signal prediction, and 
 to estimate some of the backgrounds, it is important to correct for possible 
 mis-modelling with respect to the data. Dedicated control regions in
-data are used to derive the \ac{MC} to data correction factors
-that are applied to the \ac{MC} samples. Where efficiencies
+data are used to derive the \ac{MC} simulation to data correction factors
+that are applied to the simulated samples. Where efficiencies
 are involved this scale factor is derived by measuring the efficiency
-in data and in \ac{MC} and constructing the scale factor as $\text{SF}=\frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
+in data and in simulation and constructing the scale factor as $\text{SF}=\frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
 \subsubsection*{Tracking efficiency}
 A discrepancy between the track reconstruction efficiency
-in data and \ac{MC} for electrons and muons was found. It is corrected for using $\eta$-dependent
+in data and simulation for electrons and muons was found. It is corrected for using $\eta$-dependent
 scale factors.% \cite{CMS-PAS-HIG-16-037}.
-\subsubsection*{Electron, muon and tau ID and isolation}
-Identification and isolation efficiencies in data and \ac{MC} are measured
+\subsubsection*{Electron, muon and tau identification and isolation}
+Identification and isolation efficiencies in data and simulation are measured
 for electrons, muons and hadronic taus. A tag-and-probe
@@
 and isolation efficiencies. Because no trigger simulation is applied to
-the \ac{MC} samples, the efficiency $\epsilon_{\text{Data}}$ is simply applied
-to the \ac{MC} events. Because two electron-muon cross triggers are 
+the simulated samples, the efficiency $\epsilon_{\text{Data}}$ is simply applied
+to the simulated events. Because two electron-muon cross-triggers are 
 used to select events in the \emu channel, the efficiencies of the different
-cross trigger legs need to be combined. With one of the cross triggers having a
+cross-trigger legs need to be combined. With one of the cross-triggers having a
 minimum \pT~of
@@
 using a tag-and-probe method with \Zeenog and \Zmmnog events. Scale
-factors, applied to \ac{MC} events where the tau is faked by an electron or muon,
-are derived as the ratio between the fake rate in data and the fake rate in \ac{MC} events.
+factors, applied to simulated events where the tau is faked by an electron or muon,
+are derived as the ratio between the fake rate in data and the fake rate in simulation.
 \subsubsection*{\MET~recoil corrections}
-Differences in \MET~resolution and response between data and \ac{MC} 
+Differences in \MET~resolution and response between data and simulation
 are accounted for by the application of recoil corrections
@@
 To correct for the difference in b-tagging efficiency
-and light jet mis-tagging rates between data and \ac{MC} events,
+and light jet mis-tagging rates between data and simulation,
 \pT- and $\eta$-dependent scale factors are derived as 
@@
 \subsubsection*{Top quark \pT~reweighting}
-A reweighting which was derived during \ac{LHC} Run 1
-to better match the top quark \pT~distribution in \ac{MC}
+A reweighting which was derived during Run 1
+to better match the top quark \pT~distribution in simulation
 to that observed in data is applied to \ttbar events. Despite
 the fact that the correction was derived during Run 1, it still
-improves the data/\ac{MC} agreement in a \ttbar enriched
+improves the agreement with data in a \ttbar enriched
 control region in the \emu channel, defined as 
-\MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$. The improvement in data/\ac{MC} agreement
-by applying the top quark \pT~reweighting is illustrated in figure \ref{fig:mssm_corrs_toppt}.
+\MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$. This
+is illustrated in figure \ref{fig:mssm_corrs_toppt}.
 \begin{figure}[h!]
@@
 \end{center}
-\caption[\mTtot~distribution in the \ttbar
-enriched control region, with and without applying top quark \pT~reweighting.]{\mTtot~distribution in the \ttbar enriched control region \MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$ in the \emu channel,
-(a) without applying top quark \pT~reweighting and (b) with top quark \pT~reweighting.
+\caption[The \mTtot~distribution in the \ttbar
+enriched control region, with and without applying top quark \pT~reweighting.]{The \mTtot~distribution in the \ttbar enriched control region \MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$ in the \emu channel,
+(a) without applying the top quark \pT~reweighting and (b) with the top quark \pT~reweighting.
 The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross section uncertainty.}
@@
 \subsubsection*{Drell-Yan shape reweighting}
-As the \ac{MC} samples used for the \Ztautau estimate
-do not model the data well for events with high di-lepton
-mass and high \PZ boson \pT, a reweighting is applied to correct for this.
-These weights are derived in bins of $\PZ/\Pphotonx$ mass and \pT~
-using \Zmm events in data, in such a way that they do not
+As the \ac{MC} generator used for the \Ztautau estimate
+does not model the data well for events with high di-lepton
+mass and high \pT, a reweighting is applied to correct for this.
+These weights are derived in bins of di-lepton mass and 
+\pT~using \Zmm events in data in such a way that they do not
 change the overall Drell-Yan normalisation. The weights
 are then applied to the \Ztautau and \Zellell background processes.
-The mismodelling can be seen in figure \ref{fig:dyrwt}a, which
-shows the observed data and expected background distribution of the \PZ \pT~in
+The mis-modelling can be seen in figure \ref{fig:dyrwt}a, which
+shows the observed data and expected background distribution of the di-lepton \pT~in
 \Zmm events. The overall effect of the reweighting, which is derived
@@
 shape in the no b-tag category of the \etau channel is shown in figure \ref{fig:dyrwt}b.
+While the correction factor can be up to 20\% this figure shows
+that the total effect on the \Ztautau background distribution is small.
 \begin{figure}[h!]
@@
 \end{center}
-\caption[The mismodelling in the \PZ boson \pT~distribution as observed
+\caption[The mis-modelling in the di-lepton \pT~distribution as observed
 in \Zmm events, and the impact of applying the Drell-Yan shape reweighting
-on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mismodelling in the \PZ boson \pT~distribution as observed
+on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mis-modelling in the di-lepton \pT~distribution as observed
 in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
@@
 from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
-might pass the selection if for example a jet is misreconstructed as a hadronic tau and only one of the leptons is reconstructed. 
-Production of QCD multijet events, labelled `QCD' on the graphs in figure \ref{fig:mssm_bkgs_overview}, is a background when 
-two jets are misreconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
+might pass the selection if, for example, one of the leptons or a jet is mis-reconstructed as a hadronic tau.
+Production of QCD multijet events, labelled `QCD' in figure \ref{fig:mssm_bkgs_overview}, is a background when 
+two jets are mis-reconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
 As is visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
 This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
-always contain real b-jets. The decay products of one or both of the \PW bosons, and additional jets in the event, can 
+always contain b-jets. The decay products of one or both of the \PW bosons, and additional jets in the event, can 
 then form \etau, \mutau, \tautau and \emu pairs.\\
-The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW decay and a jet misreconstructed
-as a hadronic tau form a pair. In the \tautau channel it is a background when the \PW boson decays into $\Pgt\Pgn$ with the tau 
-decaying hadronically and an additional jet in the event is misreconstructed as a hadronic tau, or when two jets are
-reconstructed as hadronic taus.
+The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
+as a hadronic tau form a pair. In the \tautau channel it is a background when one \Pgth originates from a $\PW \rightarrow \Pgt\Pgn$ decay
+and the other from an additional jet in the event being mis-reconstruced as a hadronic tau. 
 In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
-channel this background is smaller. Backgrounds that are small in all channels are the di-boson and single-top backgrounds. In 
-figures showing the backgrounds the di-boson and single-top backgrounds are drawn together with the \Wjets 
-background and is referred to as the `Electroweak' component.
+channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In
+figures the di-boson and single-top backgrounds are drawn together with the \Wjets 
+background and labelled collectively as the `Electroweak' component.
 
@@
 To estimate these backgrounds a mixture of data-driven 
-methods and \ac{MC} samples is employed. The QCD background
+methods and predictions from simulation is employed. The QCD background
 is estimated using data-driven techniques in all four channels.
-In the \mutau and \etau channels the \Wjets background is also
+In the \mutau and \etau channels the \Wjets background yield is also
 estimated using data-driven techniques. The control regions used
@@
 In the \emu and \tautau channels the \Wjets background is estimated using
-\ac{MC} samples. The \Ztautau and \Zellell backgrounds are estimated
-using \ac{MC} samples for all four channels. A \Zmm control region
+simulation. The \Ztautau and \Zellell backgrounds are estimated
+using simulation for all four channels. A \Zmm control region
 is considered in a simultaneous fit with the signal region to correct and
@@
 The \ttbar, di-boson and single-top backgrounds are estimated
-using \ac{MC} samples, with cross-checks in control regions in data.
+using simulation, with cross-checks in control regions in data.
 The rest of this section describes the background estimation methods
@@
 \label{sec:mssm_bkgs_genmatch}
-For backgrounds estimated from \ac{MC}, it is possible
-that it is more correct to split a background process
-into different sub-processes that should be treated separately in the fit to data.
+For backgrounds estimated from simulation, it can be
+beneficial to split a background process into different
+components that are allowed to vary independently, and be
+subject to different systematic uncertainties, in the fit to data.
 Taking the \mutau 
@@
 hadronically and the other tau decays to a muon, but also
-\Zmm events where one of the muons fakes a tau, or with an 
-additional jet in the event faking a hadronic tau and one of the
-muons not being properly reconstructed. Similarly, \ttbar background
+\Zmm events where one of the muons fakes a tau. 
+Similarly, \ttbar background
 events can be split into those with genuine taus, and those
-where a jet mimics a hadronic tau. In such cases dividing
-events from the same production process into sub-samples
-based on generator information allows for a more correct
+where a jet fakes a hadronic tau. In such cases dividing
+events from the same production process into separate components
+based on generator information allows for a correct
 treatment of systematic uncertainties.
 
-To determine the generator-level particle
+To determine the simulated particle
 that a reconstructed electron, muon, or hadronic tau
 originates from, reconstructed objects are matched
-to a set of generator level objects within a cone of $\Delta R = 0.2$.
-Five categories of generator-level object are considered for matching:
+to a set of simulated objects within a cone of $\Delta R = 0.2$.
+Five categories of simulated object are considered for matching:
 prompt electrons and muons,
 that is electrons and muons not originating from a hadron, tau or muon decay; electrons and muons
-from tau decays; and generator-level hadronic taus. These generator-level
-hadronic taus are rebuilt by summing the four-momenta
-of the visible decay products of the generator-level tau.
-
-If there is at least one generator-level object
+from tau decays; and simulated hadronic taus. These simulated
+hadronic taus are built by summing the four-momenta
+of the visible decay products of the simulated tau lepton.
+
+If there is at least one simulated object
 within a cone of $\Delta R = 0.2$ around the direction of the reconstructed
-object, the generator-level object nearest the reconstructed particle is chosen
+object, the simulated object nearest the reconstructed particle is chosen
 as the one the reconstructed particle is matched to. 
 If there are no 
-generator-level particles in the cone at all it is said to 
-have originated from pileup or a jet at generator level.
-
-The generator-level object type matched to a 
+simulated objects in the cone at all the reconstructed object is said to 
+have originated from a jet.
+
+The type of simulated object matched to a 
 reconstructed particle is used to perform the splitting
-of background samples, where this is used it is indicated.
+of background samples. In what follows, it is indicated where this 
+procedure is used.
 
@@
 \label{sec:mssm_bkgs_ztt}
-For all channels, both shape and normalisation of the \Ztautau background 
+For all channels, both the shape and normalisation of the \Ztautau background 
 are estimated from the Drell-Yan
-\ac{MC} samples described in section \ref{sec:mssm_datasets}.
+simulation.
 For the \mutau and \etau channels, events from these samples 
 in which the reconstructed hadronic tau is matched to 
-a generator-level hadronic tau are considered part of the \Ztautau
+a simulated hadronic tau are considered part of the \Ztautau
 background. In the \tautau channel both reconstructed
-hadronic taus are required to be matched to a generator-level hadronic tau, and
+hadronic taus are required to be matched to a simulated hadronic tau, and
 in the \emu channel the \Ztautau component of the Drell-Yan background 
 is taken as those events where the reconstructed electron is not matched to
-a prompt electron at generator level and the reconstructed
+a simulated prompt electron and the reconstructed
 muon is not matched to a prompt muon. 
-Events in the Drell-Yan samples selected in the event selection
-but not satisfying the generator matching requirements are considered
-as the, much smaller, \Zll background.
-
-To correct and constrain the \Ztautau normalisation in the
-b-tag and no b-tag categories of all channels, \Zmm control
-regions are considered in a simultaneous fit with the signal region. More detail is given in 
-section \ref{sec:mssm_sigext_ctrl}.
+Events in the Drell-Yan simulation 
+that do not satisfy the generator matching requirements are considered
+as the much smaller \Zll background.
+%To correct and constrain the \Ztautau normalisation in the
+%b-tag and no b-tag categories of all channels, \Zmm control
+%regions are considered in a simultaneous fit with the signal region. More detail is given in 
+%section \ref{sec:mssm_sigext_ctrl}.
 
@@
 \label{sec:mssm_bkgs_mtet_wjetsqcd}
-A data--driven approach is used for the estimation of
+A data-driven approach is used for the estimation of
 both the \Wjets and QCD backgrounds in the \etau and \mutau channels. 
@@
 control region. The shape of the \Wjets background is taken
-from the \ac{MC} samples. The QCD shape taken from same-sign
-data, that is events selected in observed data with the opposite charge requirement
-on the di-$\Pgt$ pair inverted but otherwise identical cuts to the signal region. Contributions
+from simulation. The QCD shape taken from same-sign
+data, that is, events selected in observed data with the opposite charge requirement
+on the di-tau pair inverted but otherwise identical cuts to the signal region. Contributions
 from other backgrounds in this region are subtracted.
@@
 The \Wjets normalisation is derived using a high-\mT~control region, where
-selected events are required to satisfy \mT~$>70\,\GeV$. The 
+selected events are required to satisfy $\mTm>70\,\GeV$. The 
 \Wjets
 contribution in this region is enhanced, however there is still
-some contribution from QCD events in this region. This is visible in 
+some contamination from QCD events. This is visible in 
 figure \ref{fig:mssm_bkgs_wjets_mutau_mt} which shows the \mT~distribution in the
@@
 \caption{Distribution of the transverse mass \mT~in the \mutau channel, indicating
-the signal region and the high \mT~control region. This distribution is plotted
+the signal region and the high-\mT~control region. This distribution is shown
 before dividing the events into categories \cite{CMS-PAS-HIG-16-037}.}
@@
 
-Because of this contribution from QCD events in the high \mT~region we
-have, for \mT~$>70\,\GeV$:
+Because of this contribution from QCD events in the high-\mT~region we
+have, for $\mTm>70\,\GeV$:\\
+\begin{minipage}{\textwidth}
+\begin{equation*}
+\begin{split}
+N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
+ high } m_{\text{T}}} &=
+N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} + N_{\text{W}}^{\text{SS, high } m_{\text{T}}}\\
+N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
+ high } m_{\text{T}}}  &= N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
+N_{\text{W}}^{\text{OS, high } m_{\text{T}}}\\
+&= R_{\text{QCD}}^{\text{OS/SS}}\cdot N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} +
+R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
+\end{split}
+\end{equation*}
+~\vspace{-\baselineskip}
 \begin{equation}\label{eqn:wjets_ss_norm}
-\begin{split}
-&N_{\text{data}}^{\text{SS, high } m_{\text{T}}} - N_{\text{other}}^{\text{SS,
- high } m_{\text{T}}}  =
-N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} + N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
-&N_{\text{data}}^{\text{OS, high } m_{\text{T}}} - N_{\text{other}}^{\text{OS,
- high } m_{\text{T}}}  = N_{\text{QCD}}^{\text{OS, high } m_{\text{T}}} +
-N_{\text{W}}^{\text{OS, high } m_{\text{T}}} \\
-& = R_{\text{QCD}}^{\text{OS/SS}}\cdot N_{\text{QCD}}^{\text{SS, high } m_{\text{T}}} +
-R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}} ~\\
-&\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}}  = \frac{N_{\text{data}}^{\text{OS,
+\Rightarrow N_{\text{W}}^{\text{SS, high } m_{\text{T}}} = \frac{N_{\text{data}}^{\text{OS,
  high } m_{\text{T}}}  - N_{\text{other}}^{\text{OS, high } m_{\text{T}}}  -
@@
 N_{\text{other}}^{\text{SS, high } m_{\text{T}}} )}{R_{\text{W}}^{\text{OS/SS}} -
-R_{\text{QCD}}^{\text{OS/SS}}} ,
-\end{split}
+R_{\text{QCD}}^{\text{OS/SS}}},
 \end{equation}
+\end{minipage}
+
 where $R_{\text{W}}^{\text{OS/SS}}$ is the ratio between opposite-sign and same-sign \Wjets events

### 2017-02-24 MSSM/MSSM.tex
Another round of MSSM editing

@@
 \begin{center}
-\subfloat[\Zmm events]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_tt_inclusive_zmm_2016_log_noweight.png}}
+\subfloat[\Zmm events]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/Zmmnoweight2.png}}
 \subfloat[Effect of Drell-Yan shape reweighting on \Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_zttweight_et_nobtag.pdf}}
@@
 and $R_{\text{QCD}}^{\text{OS/SS}}$ the ratio between opposite-sign and same-sign QCD events. Using 
-equation \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
-opposite-sign, high \mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS, high } m_{T}}$. 
+equation~\ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
+opposite-sign, high-\mT~region is given by $R_{\text{W}}^{\text{OS/SS}}\cdot N_{\text{W}}^{\text{SS, high } m_{\text{T}}}$. 
 This is extrapolated to the number of \Wjets events in the signal region at low \mT~as:
 \begin{equation}\label{eqn:wjets_os_norm}
-N_{\text{W}}^{\text{OS, low} m_{T}} = \frac{N_{\text{W,MC}}^{\text{OS, low} m_{T}}}{N_{\text{W,MC}}^{\text{OS, high} m_{T}}}\cdot R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high }m_{T}},
+N_{\text{W}}^{\text{OS, low } m_{\text{T}}} = \frac{N_{\text{W,MC}}^{\text{OS, low } m_{\text{T}}}}{N_{\text{W,MC}}^{\text{OS, high } m_{\text{T}}}}\cdot R_{\text{W}}^{\text{OS/SS}} \cdot N_{\text{W}}^{\text{SS, high }m_{\text{T}}},
 \end{equation}
-which means the estimate of the number of \Wjets events in the opposite-sign, high \mT, region
-is multiplied by a high \mT-to-low \mT~extrapolation factor determined from the \ac{MC} samples.
+which means the estimate of the number of \Wjets events in the opposite-sign, high-\mT, region
+is multiplied by a high-\mT to low-\mT~extrapolation factor determined from simulation.
 
@@
 control region in data; this measurement is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
-taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
+taken from the \Wjets simulation, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
 is close to 1.
@@
 the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
-the high-\mT~region in the no b-tag category (figure \ref{fig:bkgs_highmtctrl}a) is compared with the high-\mT~region in the 
-b-tag category (figure \ref{fig:bkgs_highmtctrl}b) of the \etau channel. It is clear that the \ttbar 
+the high-\mT~region in the no b-tag category, figure \ref{fig:bkgs_highmtctrl}a, is compared with the high-\mT~region in the 
+b-tag category, figure \ref{fig:bkgs_highmtctrl}b, of the \etau channel. It is clear that the \ttbar 
 background is much larger than the \Wjets background in the b-tag high-\mT~control region.
@@
 of \Wjets events in this category is made with a relaxed category selection where the b-tagging
-requirement itself is removed, but the jet requirements still stand. Events with at least one 
-jet with \pT~$>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with \pT~$>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
+requirement itself is removed, but the jet requirements remain. Events with at least one 
+jet with $\pTm>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with $\pTm>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
 region is determined by the estimate given by the number of \Wjets events
-estimated in the one-jet selection, multiplied by an extrapolation factor 
-$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
+estimated in this one-jet selection, multiplied by an extrapolation factor 
+$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
 \begin{figure}[h!]
@@
 assuming $R_{\text{QCD}}^{\text{OS/SS}} = 1$ is treated as the signal, and a binned maximum
-likelihood fit to the QCD signal strength is performed while allowing the other
-backgrounds to float within reasonable normalisation uncertainties. The
-resulting best fit value of the signal strengh parameter is taken as $R_{\text{QCD}}^{\text{OS/SS}}$.
-Of the two sidebands used, one is nearer the signal region ($0.15<I_{\text{rel}}^{\Pgm}<0.25$ for the \mutau channel and $0.1<I_{\text{rel}}^{\Pe}<0.2$ for the \etau channel)
-and one further away ($0.25<I_{\text{rel}}^{\Pgm}<0.5$ for the \mutau channel and $0.2<I_{\text{rel}}^{\Pe}<0.5$ for the \etau channel). The results of the fits,
+likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ is performed while allowing the other
+backgrounds to float within reasonable normalisation uncertainties. 
+Of the two sidebands used, one is nearer the signal region, $0.15<I_{\text{rel}}^{\Pgm}<0.25$ for the \mutau channel and $0.1<I_{\text{rel}}^{\Pe}<0.2$ for the \etau channel,
+and one further away, $0.25<I_{\text{rel}}^{\Pgm}<0.5$ for the \mutau channel and $0.2<I_{\text{rel}}^{\Pe}<0.5$ for the \etau channel. The results of the fits,
 performed before the categorisation of events into the b-tag and no b-tag categories, are shown in figures \ref{fig:mssm_qcdosss_mtnear} and \ref{fig:mssm_qcdosss_mtfar}
@@
 The value of $R_{\text{QCD}}^{\text{OS/SS}}$ is found to be consistent between the two sidebands within 10\% (1\%) in the \etau (\mutau) channel.
-Adding this uncertainty in quadrature to the uncertainty on the fit in the sidebands nearest the signal region we find
+Adding this uncertainty in quadrature to the uncertainty on the fit in the sidebands nearest the signal region gives
 an overall uncertainty of 12\% in the \etau channel and 4\% in the \mutau channel.
-When performing the same fits in the no b-tag and b-tag categories to determine differences between
-this pre-categorisation opposite-sign to same-sign ratio, and the ratio as measured in categories it is found that 
-the fit is not stable in the b-tag category due to the number of events in this region being too small.
+The same fits can be performed in the no b-tag and b-tag categories to test if $R_{\text{QCD}}^{\text{OS/SS}}$
+varies with the category selection, however it is found that
+the fit is not stable in the b-tag category due to the small number of events.
 The uncertainty on the ratio is increased for the b-tag category to cover the differences.
-The uncertainties are already large enough to cover differences between the pre-categorisation $R_{\text{QCD}}^{\text{OS/SS}}$ and the
+The uncertainties are already large enough to cover differences between the inclusive $R_{\text{QCD}}^{\text{OS/SS}}$ and the
 fits as performed in the no b-tag category. Therefore $R_{\text{QCD}}^{\text{OS/SS}}$ in the \mutau channel is taken to be
@@
 \end{center}
-\caption[The visible mass distribution of the di-$\tau$ pair
+\caption[The visible mass distribution of the di-tau pair
 in the \mutau channel for the sideband near the signal region, before
-and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
-is $1.180\pm0.044$.}
+and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ and (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$
+is $1.18\pm0.04$.}
 \label{fig:mssm_qcdosss_mtnear}
@@
 \mutau channel for the sideband further away from the signal region,
-before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength 
-is $1.184\pm0.035$.}
+before and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible mass distribution of the di-tau pair in the \mutau channel for the sideband further away from the signal region, (a) before
+the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$
+is $1.18\pm0.04$.}
 \label{fig:mssm_qcdosss_mtfar}
@@
 the \etau channel for the sideband near the signal region,
-before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-tau pair in the \etau channel for the sideband near the signal region, (a) before
-the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength is $1.015\pm0.059$.}
+before and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible mass distribution of the di-tau pair in the \etau channel for the sideband near the signal region, (a) before
+the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ and (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$ is $1.02\pm0.06$.}
 \label{fig:mssm_qcdosss_etnear}
@@
 in the \etau channel for the sideband further away from the signal
-region, before and after the maximum likelihood fit to the QCD signal 
-strength.]{The visible mass distribution of the di-tau pair in the \etau channel for the sideband further away from the signal region, (a) before
-the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength
-is $1.127\pm0.045$.}
+region, before and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible 
+mass distribution of the di-tau pair in the \etau channel for the sideband further away from the signal region, (a) before
+the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ and (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$
+is $1.13\pm0.05$.}
 \label{fig:mssm_qcdosss_etfar}
@@
 The QCD normalisation is estimated by inverting the opposite-sign requirement
-of the di-tau pair in the signal region. The yield is taken from the same-sign
+of the di-tau pair in the signal region. The yield is taken from this same-sign
 region with otherwise identical cuts to the opposite-sign region. The contributions
 from other backgrounds in this region are subtracted to give an estimate of the number
-of QCD events in the same-sign region. For all backgrounds apart from \Wjets the
-yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
+of same-sign QCD events. For all backgrounds apart from \Wjets the
+yields to subtract are estimated using simulation. The number of \Wjets events
 expected in this region is given by
@@
 Because opposite-sign and same-sign QCD events do not
-necessarily appear in equal amounts the number of QCD
-events obtained by subtracting other backgrounds from the
-observed number of events in the same-sign region is multiplied
-by $R_{\text{QCD}}^{\text{OS/SS}}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
+necessarily appear in equal amounts the number of same-sign QCD
+events estimated as above is multiplied
+by $R_{\text{QCD}}^{\text{OS/SS}}$ 
 to obtain an estimate of the number of QCD events in the signal region.
@@
 isolation requirements with respect to the signal region. 
-In the no b-tag category the sideband used is determined
-by having the tau with highest \pT~pass the tight working
+In the no b-tag category the sideband used is defined
+by having the \Pgth with highest \pT~pass the tight working
 point of the tau ID discriminator, as in the nominal selection.
-The other hadronic tau in the pair is required to fail the tight working point,
+The other \Pgth is required to fail the tight working point,
 but pass the medium working point. This sideband is 
@@
 \begin{equation}\label{eqn:tautau_qcd}
-R_{QCD}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
+R_{\text{QCD}}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
 \end{equation}
-This correction factor takes the ratio between the observed data with other
-backgrounds subtracted in the region equivalent to the signal region, but with the
-charge requirement of the pair inverted, and the region equivalent to the sideband
-with loosened isolation but with the charge requirement on the pair inverted.
+This correction factor takes the ratio between the background-subtracted data in regions 
+equivalent to the signal region and the sideband with relaxed isolation, but with the
+charge requirement on the pair inverted.
 
@@
 provide a background estimate. Therefore a sideband where
-the highest \pT~tau passes the tight working point of the
-tau ID discriminator, and the other tau passes the loose working
+the highest \pT~\Pgth passes the tight working point of the
+tau ID discriminator, and the other \Pgth passes the loose working
 point of the discriminator, but not the tight working point, is used.
-This sideband is slightly further away from the signal region than the
-`tight-medium' sideband. %The bias from using this looser
+%This sideband is slightly further away from the signal region than the
+%`tight-medium' sideband. %The bias from using this looser
 %sideband has been assessed and has a less than 1$\sigma$ effect.
@@
 Other backgrounds present in this region are subtracted.
-Like for the \etau and \mutau channels, the number of
+As for the \etau and \mutau channels, the number of
 QCD events with opposite-sign \emu pairs is not
@@
 least one of them needs to fail the nominal isolation requirement.
-The opposite-sign to same-sign ratio is parameterised in terms
+The OS/SS ratio is parameterised in terms
 of lepton kinematics and the separation in $\Delta R$ between the
-two leptons. These ratios are then applied to the estimate in the same-sign region
+two leptons. These ratios are then applied to events in the same-sign region
 to give an estimate in the signal region. The statistical uncertainty
-on the measurement is 13\%. Cross-checking the measurement 
-using QCD \ac{MC} samples, it is observed that there is a 19\% difference
+in the measurement is 13\%. Cross-checking the measurement 
+using QCD simulation, it is observed that there is a 19\% difference
 between the OS/SS ratio in the signal region and the sideband, the two
 uncertainties are added in quadrature. 
-The opposite-sign to same-sign ratios are measured
-before applying the categorisation, and because \ac{MC} studies suggest
-that the opposite-sign to same-sign ratio is different in the b-tag
+The OS/SS ratios are measured
+before applying the categorisation, and because studies of simulated events suggest
+that the OS/SS ratio is different in the b-tag
 category than in the no b-tag category, an extra scale factor of 
-$1.45/2.20\pm0.16$ is applied to the QCD estimate in the b-tag category. This is 
+$0.66\pm0.16$ is applied to the QCD estimate in the b-tag category. This is 
 the ratio between the OS/SS ratio as measured in the b-tag category and 
@@
 \label{sec:mssm_bkgs_tt}
-The \ttbar shape and normalisation are estimated from \ac{MC} 
-samples and are checked against data in a control
+The \ttbar shape and normalisation are estimated from simulation
+and are checked against data in a control
 region with a \ttbar purity of 91\%. This control region
@@
 \ttbar normalisation uncertainty covers the observed
-discrepancy between data and \ac{MC}, no scale factor is applied.
+discrepancy between data and simulation, no scale factor is applied.
 In the \mutau, \etau and \tautau channels
 the \ttbar contribution is split into
-two components, one with real taus and 
-one without, for fitting purposes. The component with real taus is composed
+two components, one with real hadronic taus and 
+one without, for fitting purposes. The component with real hadronic taus is composed
 of \ttbar events in which the hadronic tau is matched
-to a generator level tau. In the fully hadronic channel
-both taus need to be generator matched to a hadronically
-decaying tau.
+to a simulated hadronic tau. In the fully hadronic channel
+both hadronic taus need to be matched to simulated hadronic taus.
 
@@
 \label{sec:mssm_bkgs_other}
-For all channels the di-boson plus 
-single-top background is small.
-Both normalisation and shape are estimated from \ac{MC}
-samples. For the \etau, \mutau and \tautau channels
+For all channels the di-boson and
+single-top backgrounds are small.
+Both normalisation and shape are estimated from simulation.
+For the \etau, \mutau and \tautau channels
 this background contribution is split into a component
 where the hadronically decaying tau originates from a real
-tau, and one where it does not, for purposes of the fit. This is done in a similar
+hadronic tau, and one where it does not. This is done in a similar
 way as for the \ttbar background.
@@
 is less important than in the \etau and \mutau channels, and both
-its shape and normalisation are estimated from the
-\ac{MC} samples. In the \emu channel the $\PW\Pphoton$ background
+its shape and normalisation are estimated from 
+simulation. In the \emu channel the $\PW{+}\Pphoton$ background
 is also added to the \Wjets background component. %For plotting purposes the single-top plus

### 2017-02-24 Conclusion/Conclusion.tex
More editing, plus additional cosmetic fixes from quick skim

@@
 
-The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
+The search for a heavy Higgs boson decaying to a final state of $\Pbottom\Pbottom\Pgt\Pgt$ via two
 $125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
@@
 The results of this search are upper limits on production cross section times branching 
-ratio, in a mass range $260<m_H<350\,\GeV$. A combination with a search for \AtoZhtolltautau
+ratio, in a mass range $260<m_{\PHiggs}<350\,\GeV$. A combination with a search for \AtoZhtolltautau
 yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well

### 2017-02-24 Detector/Detector.tex
More editing, plus additional cosmetic fixes from quick skim

@@
 switched off while collisions are ongoing. In 2012 the data-taking 
-efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.4\%
+efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%
 From all of the data that is recorded only a subset is used for analysis. Data is 
@@
 was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
-the certification efficiency was 95.4\%, resulting in $36.3\,\invfb$ of data marked good %FIXME: certification efficiency
+the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
 for use in analyses.

### 2017-02-24 Hhh/Hhh.tex
More editing, plus additional cosmetic fixes from quick skim

@@
 is taken. Similar additional vetoes as in the \mutau channel are applied.
-The event is rejected if an opposite-charge pair of electrons with \pT~ $> 15\,\GeV$, passing looser ID and
+The event is rejected if an opposite-charge pair of electrons with $\pTm > 15\,\GeV$, passing looser ID and
 isolation requirements than the signal electron requirements, can be formed. To prevent overlap with other channels and to reduce the di-boson
@@
 \label{sec:hhh_datamc}
-\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
+Simulated samples are used for the estimation of some of the backgrounds and the signal, 
 and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
@@
 The difference between
-the efficiencies in data and simulated events are applied to \ac{MC} events as a
+the efficiencies in data and simulated events are applied to simulated events as a
 scale factor $\text{SF} = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
@@
 an energy scaling that is applied to reconstructed hadronic taus matched
-to simulated hadronic tau decays in \ac{MC} events.
+to simulated hadronic tau decays in simulation.
 
@@
 Differences in \MET~resolution and response between data and simulation are accounted for by
-applying recoil corrections to \Zellell, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
+applying recoil corrections to \Zellell, \Wjets and signal simulation. Section \ref{sec:objects_met_recoilcorr} 
 gives more details on how these corrections are derived.
@@
 derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
-b-/c-jets and light jets. In this analysis the ``promote/demote'' method
+b-/c-jets and light jets. In this analysis the ``promote-demote'' method
 is used to apply these.
@@
 Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
-the b-tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
+the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
 under consideration.
@@
 yield after the initial event selection, before subdividing into categories, as
-estimated in the \Ztautau \ac{MC} sample is scaled by the efficiency with which 
+estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
 such events pass the category selection in the embedded sample. The shape of
@@
 \subsection{\texorpdfstring{\ttbar}{ttbar}}
-Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
+Both the \ttbar shape and normalisation are estimated using simulation.
 These are checked against data in dedicated control regions. One such control
@@
 from the data in this region, and a high-\mT~to low-\mT~extrapolation
- factor is determined from the \Wjets \ac{MC} 
-sample. The yield in the signal region is given by the data yield in the high-\mT~sideband, with
+ factor is determined from the \Wjets simulation.
+The yield in the signal region is given by the data yield in the high-\mT~sideband, with
 other backgrounds subtracted, multiplied by this extrapolation factor.
@@
 events are small. Both shapes and normalisations are
-estimated using \ac{MC} samples.
+estimated using simulated samples.
 
@@
 \subsubsection*{Luminosity uncertainty}
-The uncertainty on the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during
+The uncertainty in the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during
 2012. This uncertainty is applied to all processes in which
@@
 \subsubsection*{Identification, isolation and trigger efficiencies}
-A systematic uncertainty on the efficiency measurements
-for the leptons is derived by combining the separate uncertainties on these measurements
+A systematic uncertainty in the efficiency measurements
+for the leptons is derived by combining the separate uncertainties in these measurements
 in quadrature. For electrons and muons this leads to a 2\% uncertainty. For hadronic taus a 6\% 
@@
 \subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates}
-The uncertainty on both the $\Pe\rightarrow\Pgth$ fake rate measurement and the
+The uncertainty in both the $\Pe\rightarrow\Pgth$ fake rate measurement and the
 $\Pgm\rightarrow\Pgth$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\Pgm\rightarrow\Pgth$
@@
 \subsubsection*{\MET~resolution and response}
-Uncertainties on the \MET~resolution and response are estimated by varying
+Uncertainties in the \MET~resolution and response are estimated by varying
 the recoil correction parameters within their estimated uncertainties. This 
@@
 \item \Zellell: As this is a very small background after requiring two jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between $20$--$90$\%.
-\item \ttbar: The uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
-\item Di-boson and single top: The combined uncertainty on the di-boson and single-top cross sections is 15\% \cite{SMHtautauCMS}.
-\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region.
+\item \ttbar: The uncertainty in the \ttbar cross section is 10\% \cite{toppp}.
+\item Di-boson and single top: The combined uncertainty in the di-boson and single-top cross sections is 15\% \cite{8TeVdib,8TeVst}.
+\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region.
 The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.
@@
 \subsubsection*{Jet energy scale}
-The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT-and $\eta$-dependent uncertainty \cite{cms-jec-2011}.
+The uncertainty in the jet energy corrections are applied by shifting the jet energy up and down by the \pT-and $\eta$-dependent uncertainty \cite{cms-jec-2011}.
 Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.
@@
 This applies to the
-luminosity uncertainty and the uncertainties on b-tagging efficiency
-and light jet mis-tagging rate.
+luminosity uncertainty and the uncertainties in the b-tagging efficiency
+and the light jet mis-tagging rate.
 
@@
 and take the quartic couplings to be zero.
-For the interpretation shown here the assumption that \mA=\mH=\mHplus~$=300\,\GeV$ is made.
+For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.
 
@@
 \caption[Search for \Htohhtobbtautau and search for \AtoZhtolltautau
-interpreted in a type-II 2HDM, assuming \mA=\mH=\mHplus~$=300\,\GeV$.]{Search for (a) \Htohhtobbtautau and (b) \AtoZhtolltautau interpreted in a type-II 
-\ac{2HDM}, assuming \mA=\mH=\mHplus~$= 300\,\GeV$. The expected (dashed line)
+interpreted in a type-II 2HDM, assuming $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$.]{Search for (a) \Htohhtobbtautau and (b) \AtoZhtolltautau interpreted in a type-II 
+\ac{2HDM}, assuming $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$. 
+The expected (dashed line)
 and observed (solid line) exclusion contours at 95\% \ac{CL} are overlaid

### 2017-02-24 MSSM/MSSM.tex
More editing, plus additional cosmetic fixes from quick skim

@@
 before they are combined so as to preserve the correct
-fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
+fractions of events with each jet multiplicity. The $\PW{+}\Pphoton$ background samples,
 only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
@@
 Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
-tau isolation working point selections on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.
+tau isolation working point selections on both the $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$ production processes.
 
@@
 \item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
-\item \textbf{b-Tag}: At least one b-tagged jet, at most one 
+\item \textbf{B-tag}: At least one b-tagged jet, at most one 
 jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
 \end{center}
@@
 \subsubsection*{Luminosity uncertainty}
-The uncertainty on the luminosity measurement amounts to 6.2\% for
+The uncertainty in the luminosity measurement amounts to 6.2\% for
 data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
 applied to all processes for which the normalisation is estimated 
-using \ac{MC} samples.
+using simulation.
 \subsubsection*{Identification, isolation and trigger efficiencies}
-The combined uncertainty on the electron and muon identification, isolation, and
-trigger efficiencies amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
-isolation uncertainty amounts to 6\% in the \etau and \mutau channels
-and 12\% in the \tautau channel, with an additional 7\% uncertainty
-on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
-uncertainty is split between a part that is correlated between the channels, 
+The combined uncertainty in the electron and muon identification, isolation, and
+trigger efficiencies amounts to 2\%. For hadronic taus the identification and
+isolation uncertainty amounts to 6\% per \Pgth in the \etau, \mutau and \tautau channels,
+with an additional 7\% uncertainty
+in the tau trigger efficiency added in quadrature for the \tautau channel. This
+uncertainty is split between a part that is correlated between the channels and a
+part that is not, The correlated part amounts to 
 a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
 part amounts to 3\% (9.2\%) for the \etau and \mutau (\tautau) channels.
-The uncertainties on lepton/hadronic tau identificiation, isolation and 
+The uncertainties on lepton and hadronic tau identification, isolation and 
 trigger efficiency are applied to all processes for which the normalisation
-is estimated using \ac{MC} samples.
+is estimated using simulation.
 \subsubsection*{$\text{jet}\rightarrow\Pgth$ fake rate}
-The uncertainty on the $\text{jet}\rightarrow\Pgth$ fake rate
+The uncertainty in the $\text{jet}\rightarrow\Pgth$ fake rate
 is 20\% \cite{cms-tau-2015}. This uncertainty is applied
-to those backgrounds where the normalisation is estimated from \ac{MC} and
-where the hadronic taus are mimicked by jets, that is the \Zellell background
+to those backgrounds where the normalisation is estimated using simulation and
+where the hadronic taus are faked by jets, that is the \Zellell background
 with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
 channel, and the \ttbar background without real hadronic taus.
-\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rate}
-The $\Pe\rightarrow\Pgth$ fake rate uncertainty ranges from $10$--$30$\%,
+\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates}
+The $\Pe\rightarrow\Pgth$ fake rate uncertainty ranges from $10$--$30$\%
 depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
-applied to the \Zellell background with the hadronic tau faked by an electron.
-The $\Pgm\rightarrow\Pgth$ fake rate uncertainty ranges from $20$--$30$\%, depending
-on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
-background with the hadronic tau faked by a muon.
+applied to the \Zellell background in which the hadronic tau is faked by an electron.
+The $\Pgm\rightarrow\Pgth$ fake rate uncertainty ranges from $20$--$30$\% depending
+on the anti-muon discriminator used. This uncertainty is applied to the \Zellell
+background in which the hadronic tau is faked by a muon.
 \subsubsection*{Jet energy scale uncertainty}
-The uncertainties on the jet energy corrections are applied
-by shifting the jet energy up and down by the \pT-and $\eta$-dependendent
+The uncertainty in the jet energy corrections is applied
+by shifting the jet energy up and down by a \pT-and $\eta$-dependendent
 uncertainty, and evaluating the change in the process normalisation in
-each category. Where the change in normalisation is non-negligible the
-uncertainty is applied. It ranges from $1$--$10$\% depending on process and category.
+each category. The uncertainty ranges from $0$--$10$\% depending on process and category.
 \subsubsection*{b-Tag scale factors}
-Uncertainties on the b-tagging efficiency and light jet mis-tagging
-rates are given as a function of jet \pT-and $\eta$-for the 
+Uncertainties in the b-tagging efficiency and light jet mis-tagging
+rates are given as a function of jet \pT and $\eta$ for the 
 medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
-The b-tagging scale factors are are varied within these uncertainties
+The b-tagging scale factors are varied within these uncertainties
 and the overall change in normalisation for each process in each category is
-evaluated. If the change in normalisation is non-negligible this
-uncertainty is applied. The uncertainty varies from $1$--$5$\%.
+evaluated. The uncertainty varies from $0$--$5$\%.
 \subsubsection*{\MET~resolution and response}
-Uncertainties on the \MET~resolution and response are estimated
+Uncertainties in the \MET~resolution and response are estimated
 by varying the recoil correction parameters within their
-uncertainty and evaluating the effect on process
+uncertainties and evaluating the effect on process
 normalisations. The uncertainty amounts to around 2\%.
@@
 fit with the signal region to correct the \Ztautau normalisation,
-the Drell-Yan cross section is not applied as an uncertainty. In the no b-tag (b-tag) category a 3\% (5\%)
-extrapolation uncertainty from \Zmm to \Ztautau is applied \cite{CMS-PAS-HIG-16-037}.
-\item \Zellell: The uncertainty on the Drell-Yan cross-section
-is to 4\% \cite{CMS-PAS-HIG-16-037}.
-\item \ttbar: The uncertainty on the \ttbar production cross-section amounts
-to 6\% \cite{CMS-PAS-HIG-16-037}.
-\item di-boson and single-top: The combined uncertainty on the di-boson and
-single-top production cross sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
+the Drell-Yan cross section uncertainty is not applied. In the no b-tag (b-tag) category a 3\% (5\%)
+extrapolation uncertainty from the kinematic phase space of the \Zmm to the \Ztautau selection is applied.
+\item \Zellell: The uncertainty in the Drell-Yan cross section
+is 4\% \cite{fewz31}.
+\item \ttbar: The uncertainty in the \ttbar production cross section amounts
+to 6\% \cite{toppp}.
+\item Di-boson and single-top: The combined uncertainty on the di-boson and
+single-top production cross sections amounts to 5\% \cite{mcfm,hathor1,hathor2}.
 \item \Wjets: In the \mutau and \etau channels the statistical uncertainties
-on the observed data and subtracted backgrounds in the control regions are taken into account by
+in the observed data and subtracted backgrounds in the control regions are taken into account by
 the inclusion of these control regions in the fit. The statistical
-uncertainty on $R_{W}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag
+uncertainty in $R_{\PW}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag
 category in both the \etau and \mutau channels, and 11\% (14\%) in the b-tag
-category of the \mutau (\etau) channel. The systematic uncertainty on
+category of the \mutau (\etau) channel. The systematic uncertainty in
 this ratio amounts to 8\% (10\%) in the no b-tag (b-tag) category of both channels.
-The statistical uncertainty on the low \mT/high \mT~ratio is 2\% in the no b-tag
+The statistical uncertainty in the low-\mT to high-\mT~ratio is 2\% in the no b-tag
 category of both channels and 14\% (17\%) in the b-tag category of the \mutau (\etau) channel.
-The systematic uncertainty on this ratio amounts to 20\%. As the \Wjets background
-in the \tautau and \emu channels is estimated from \ac{MC} a 4\% theoretical
-production cross-section uncertainty is applied.
-\item QCD: In the \emu channel the uncertainty on the QCD estimate
+The systematic uncertainty in this ratio amounts to 20\%. As the \Wjets background
+in the \tautau and \emu channels is estimated from simulation a 4\% theoretical
+production cross section uncertainty is applied \cite{fewz31}.
+\item QCD: In the \emu channel the uncertainty in the QCD estimate
 is taken as the uncertainty on the measured opposite-sign to same-sign
 ratio, which is 23\% in the no b-tag category and 34\% in the b-tag category. In the
-\tautau channel the statistical uncertainty on the QCD estimate is derived from
+\tautau channel the statistical uncertainty in the QCD estimate is derived from
 the uncertainties on the observations and subtracted backgrounds in the
 sidebands used to derive the estimate. This uncertainty amounts to 3\% in the no b-tag
-category and 20\% in the b-tag category. An additional systematic uncertainty on the
+category and 20\% in the b-tag category. An additional systematic uncertainty in the
 extrapolation factor from the anti-isolated sideband into the signal region is found
@@
 \mutau channels the statistical
-uncertainties on the observation and subtracted \ac{MC} backgrounds in the control
-region used to derive the QCD estimate is accounted for by the inclusion of these control
-regions in the fit. The uncertainty on the opposite-sign to same-sign ratio, based on
+uncertainties in the observation and subtracted backgrounds in the control
+regions used to derive the QCD estimate is accounted for by the inclusion of these control
+regions in the fit. The uncertainty in the opposite-sign to same-sign ratio, based on
 the studies described in section \ref{sec:mssm_bkgs_etmt_qcdosss} is found to be 4\% (60\%) in the 
@@
 For interpretations of the results in MSSM benchmark scenarios, theory
-uncertainties on the SM and MSSM Higgs cross section predictions are taken into account.
+uncertainties in the SM and MSSM Higgs cross section predictions are taken into account.
 The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
@@
 \subsubsection*{Drell-Yan shape reweighting}
-An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
+An uncertainty in the Drell-Yan shape reweighting based on \Zmm events
 is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
@@
 The control regions used for estimation of the 
-\Wjets and QCD background contributions in the signal regions, discussed
-in section \ref{sec:mssm_bkgs_etmt_ctrl}, are included in the fit. They
+\Wjets and QCD background contributions in the signal regions
+ are included in the fit. They
 are added to the likelihood as single-bin counting experiments. In a given
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
 \end{center}
@@
 of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid. Note that, to incorporate
-the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{mod+}$ scenario includes a \PHiggslight boson
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid. Note that, to incorporate
+the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes a \PHiggslight boson
 at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps, and this is
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
 \end{center}
@@
 of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
-and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
-%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{\text{mod+}}$ scenario includes a h boson
 %at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
 \end{center}
@@
 of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
 %the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
 \end{center}
@@
 of the \emu channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
 %the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
 \end{center}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
 \end{center}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_tt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
 \end{center}
@@
 \subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
-\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
 \end{center}
@@
 \midrule
-B-tagging & Uncorrelated & Scale factors used in the 2015 and 2016 analysis measured via different methods.\\
+b-Tagging & Uncorrelated & Scale factors used in the 2015 and 2016 analysis measured via different methods.\\
 \midrule
@@
 \midrule
-Di--boson $\sigma$ & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
+Di-boson and single-top $\sigma$ & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
 \midrule
@@
 \midrule
-Statistical \mbox{uncertainty} on W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-Systematic \mbox{uncertainty} on W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~region with anti-isolated $\Pgth$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
+Statistical \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+Systematic \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~region with anti-isolated $\Pgth$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
 In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
 \midrule
-Statistical \mbox{uncertainty} on W low/high-\mT~\mbox{ratio} (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-Systematic \mbox{uncertainty} on W low/high-\mT~\mbox{ratio} (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately.}\\
+Statistical \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+Systematic \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately.}\\
 \midrule

### 2017-02-24 Objects/Objects.tex
Some more editing
More editing, plus additional cosmetic fixes from quick skim

@@
 collisions at $\sqrt{s} = 7\,\TeV$ and found to be $ > 98.5\%$ for tracks
-with \pT $ > 500\,\MeV$ and $ > 99 \%$ for tracks with \pT $ > 2\,\GeV$ \cite{cms-trk-7tev}.
+with $\pTm > 500\,\MeV$ and $ > 99 \%$ for tracks with $\pTm > 2\,\GeV$ \cite{cms-trk-7tev}.
 %The tracking software at CMS is commonly referred to as the Combinatorial Track Finder (CTF), which is an adaptation of the combinatorial Kalman filter [29–31], which in turn is an extension of the Kalman filter [32] to allow pattern recognition and track fitting to occur in the same frame- work.
@@
 a muon candidate track. The trajectory is then extrapolated to the muon systems and
-considered a muon if at least one muon segment, a track stub in the \ac{DTs} or \ac{CSCs}, is found.
+considered a muon if at least one muon segment, a track stub in the \acp{DT} or \acp{CSC}, is found.
 Due to the requirement of a single muon segment this method is more efficient than the global muon
@@
 \ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter \ref{chap:mssm}. 
-The \ac{CSV} algorithm takes \ac{PF} jets with \pT~$> 20\,\GeV$ and $|\eta|<2.4$ as input and 
+The \ac{CSV} algorithm takes \ac{PF} jets with $\pTm> 20\,\GeV$ and $|\eta|<2.4$ as input and 
 uses a likelihood-based discriminator to determine 
@@
 can be determined as a minimum requirement on the discriminator such that the
-probability of misidentifying light-flavour jets with \pT~$> 30\,\GeV$ is around
+probability of misidentifying light-flavour jets with $\pTm> 30\,\GeV$ is around
 10\%, 1\% and 0.1\% respectively \cite{cms-btag-paper,cms-btag-run2}.
@@
 will give rise to an energy imbalance in the transverse plane, and so their
-presence can be inferred from missing energy,\MET, in the event.
+presence can be inferred from missing energy, \MET, in the event.
 
@@
 are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
-and simulated events, using convolutions of gaussians. Corrections are then applied to the \ac{MC}
+and simulated events, using convolutions of gaussians. Corrections are then applied to the simulation
 as
@@
 direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
-originated from the \Pgth production vertex within $d_Z < 0.2\,\cm$. The second term denotes the sum
-of the transverse momenta of photons with \pT $ > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
+originated from the \Pgth production vertex within $d_z < 0.2\,\cm$. The second term denotes the sum
+of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
 of the \Pgth. The effect of pileup on this term is accounted for by subtracting the sum of the momenta of charged
@@
 
-In order to reduce the $\Pe\rightarrow$\Pgth and $\Pgm\rightarrow$\Pgth fake rates, 
+In order to reduce the $\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates, 
 anti-electron and anti-muon discriminators are used. 

### 2017-02-24 Theory/Theory.tex
More editing, plus additional cosmetic fixes from quick skim

@@
 \PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
-\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
-\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
+\PHiggs & $\cos{(\beta-\alpha)}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
+\PHiggslight & $\sin{(\beta-\alpha)}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
 \bottomrule
@@
 
-\subsection{\acl{2HDM}s}
+\subsection{Two Higgs doublet models}
 \label{sec:theory_2HDM}
@@
 
-The inclusive cross section times branching ratios (\xsbr) for production of a \PHiggs boson 
+The inclusive cross section times branching ratio (\xsbr) for production of a \PHiggs boson 
 and decays into various final states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
@@
 \begin{center}
-\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
-\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
+\subfloat[\PHiggs boson]{\includegraphics[width=0.516\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
+\subfloat[\PHiggsps boson]{\includegraphics[width=0.484\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
 \end{center}
@@
 \begin{split}
-&X_{\Ptop} = A_{\Ptop}t-\mu_{\text{MSSM}}\cot{\beta},\\
+&X_{\Ptop} = A_{\Ptop}-\mu_{\text{MSSM}}\cot{\beta},\\
 &X_{\Pbottom} = A_{\Pbottom}-\mu_{\text{MSSM}}\tan{\beta},\\
@@
 
-\subsection{The $m_{h}^{\text{mod+}}$ scenario}
+\subsection{The $m_{\PHiggslight}^{\text{mod+}}$ scenario}
 \label{sec:theory_BSM_models_mhmodp}
@@
 scenario address this issue. In the $m_{\PHiggslight}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
-to be $1\,\TeV$. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
+to be $1\,\TeV$. The stop mixing parameter is positive, $X_{\Ptop}= 1.5 M_{\text{SUSY}}$.
 %This gives better agreement with muon g-2 results while the mhmod- scenario
@@
 \end{center}
-\caption[Branching ratio of \PHiggs and \PHiggsps into $\tau\tau$.]{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
+\caption[Branching ratio of the \PHiggs and \PHiggsps bosons into $\tau\tau$.]{Branching ratio of (a) the \PHiggs boson and (b) the \PHiggsps boson into $\tau\tau$. The branching
 ratios into $\tau\tau$ are enhanced at high \tanb.}
@@
 Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
-Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1--4 and 
-\mA~$150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
+Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
+\mA~$=150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
 
@@
 %\end{figure}
-To obtain \mh$\approx125\,\GeV$ over a large part of the parameter
+To obtain \mh~$\approx125\,\GeV$ over a large part of the parameter
 space, 
 $M_{\text{SUSY}}$ is not fixed but varies between a few $\TeV$ and $100\,\TeV$, while
-varying the parameter $X_t$ as:
+varying the parameter $X_{\Ptop}$ as:
 \begin{equation}
@@
 \end{center}
-\caption[Branching fractions of \Htohh and \AtoZh in the low-\tanb~scenario.]{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
+\caption[Branching ratios of \Htohh and \AtoZh in the low-\tanb~scenario.]{Branching ratios of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
 areas where both are significantly enhanced \cite{MSSM-lowtanb}.}
-\label{fig:lowtbhigh_br}.
+\label{fig:lowtbhigh_br}
 \end{figure}
@@
 The hMSSM scenario \cite{hMSSM-1,hMSSM-2} uses a different approach, in
-which \mh$=125\,\GeV$ by construction.
+which \mh~$=125\,\GeV$ by construction.
 
@@
 \label{eqn:hmssm_deltam22}
-\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_{\PHiggslight}^2},
+\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggslight}^2},
 \end{equation}
@@
 of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb, with searches for 
-heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high \tanb-region.
-Searches for heavy Higgs bosons decaying to $\PW\PW$ and $\PZ\PZ$ are able to exclude part of the low \tanb~region. In the 
-hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250--350\,\GeV$.
+heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high-\tanb~region.
+Searches for heavy Higgs bosons decaying to $\PW\PW$ and $\PZ\PZ$ are able to exclude part of the low-\tanb~region. In the 
+hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250$--$350\,\GeV$.
 The red exclusion contour in figure \ref{fig:bsm_summary}b is the re-interpretation of the analysis presented in

### 2017-02-27 Conclusion/Conclusion.tex
More editing

--- 2017-02-17 Conclusion/Conclusion.tex
@@
 
-The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
+The search for a heavy Higgs boson decaying to a final state of $\Pbottom\Pbottom\Pgt\Pgt$ via two
 $125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
-centre of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
-state can access areas of the MSSM phase space not easily accessible via other channels.
+centre-of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
+state can access areas of the \ac{MSSM} parameter space not easily accessible via other channels.
 To separate more signal-like and more background-like events, a categorisation based on the number of 
-b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
+b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-jet
 mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
-the reconstruction of the 4-body mass.
+the reconstruction of the four-body mass.
 The resulting mass variable provides good separation between the signal and the dominant
@@
 The results of this search are upper limits on production cross section times branching 
-ratio, in a mass range $260<m_H<350\,\GeV$. A combination with a search for \AtoZhtolltautau
-yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well
+ratio, in a mass range of $260<m_{\PHiggs}<350\,\GeV$. A combination with a search for \AtoZhtolltautau
+yields exclusion in the lowest \tanb~region of the low-\tanb~\ac{MSSM} scenario, as well
 as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.
 
-Searches for a heavy neutral Higgs boson decaying into pairs of tau leptons were performed
+Searches for heavy neutral Higgs bosons decaying into pairs of tau leptons were performed
 using $2.3\,\invfb$ of data recorded during the 2015
@@
 the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
-The hadronic tau isolation working point, as well as the topological selection on 
-the \mT~variable, are chosen to optimise the search sensitivity for signal
+The hadronic tau isolation working point and the topological selection on 
+the \mT~variable are chosen to optimise the search sensitivity for signal
 masses of around $1\,\TeV$.
@@
 gluon fusion and b-associated production processes. The results are also
-interpreted in MSSM benchmark scenarios, where the analyses exclude large areas
+interpreted in \ac{MSSM} benchmark scenarios, where the analyses exclude large areas
 of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
@@
 performed. This combination improves on the results of the 2016 analysis alone, thus
-setting the most stringent limits on this process to date.
+setting the most stringent limits on $\PHiggsps/\PHiggs$ to date.
 
 As more data are collected during the remainder of Run 2, and in the 
-future, searches for MSSM Higgs bosons in the di-tau final
+future, searches for \ac{MSSM} Higgs bosons in the di-tau final
 state will continue. If no such Higgs bosons are found, these searches
 will be able to exclude even more of the \mA-\tanb~plane in specific
-MSSM benchmark scenarios, although not all of the \mA-\tanb~plane
+\ac{MSSM} benchmark scenarios, although not all of the \mA-\tanb~plane
 will become accessible. A projection of the results of the 2015 \ac{MSSM}
-analysis to an integrated luminosity of $300\,\invfb$ and $3000\,\invfb$, presented at ECFA \cite{HTT-projection}, is
+analysis to integrated luminosities of $300\,\invfb$ and $3000\,\invfb$ \cite{HTT-projection} is
 shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
@@
 as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
-is very low in the high \mA-low \tanb~corner. This region can be accessed 
+is very low in the high-\mA and low-tanb~corner. This region can be accessed 
 via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
-has an enhanced branching ratio in this region. To fully cover the still
-available phase space it will therefore start to become more and more
+has an enhanced branching ratio in this region. To fully cover this
+parameter space it will therefore start to become more and more
 important to combine searches for heavy Higgs bosons in different final states.
 Doing this will give the best sensitivity to possible
-heavy Higgs bosons - or in the absence of these particles exclusion
+heavy Higgs bosons, or in the absence of these particles exclusion
 of the scenarios that predict them.
@@
 \end{center}
-\caption[The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
-at 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{h}^{\text{mod+}}$ scenario
- at 95\% CL of the 2015 MSSM analysis (pink)
-projected to an integrated luminosity of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
+\caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
+at the 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
+ at the 95\% CL of the 2015 MSSM analysis (pink)
+projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
 under several assumptions of how the systematic uncertainties scale. Even with an integrated 

### 2017-02-27 MSSM/MSSM.tex
More editing

@@
 
-\section{Datasets and \acs{MC} samples}
+\section{Datasets and Monte Carlo samples}
 \label{sec:mssm_datasets}
@@
 to better match the top quark \pT~distribution in simulation
-to that observed in data is applied to \ttbar events. Despite
+to that observed in data is applied to \ttbar events \cite{topptrwt}. Despite
 the fact that the correction was derived during Run 1, it still
@@
 \subsubsection*{Signal theory uncertainties}
-For interpretations of the results in MSSM benchmark scenarios, theory
-uncertainties in the SM and MSSM Higgs cross section predictions are taken into account.
-The uncertainties for the SM signal processes are described in more detail in reference \cite{YR4}.
-Uncertainties due to different renormalisation scales
+For interpretations of the results in \ac{MSSM} benchmark scenarios, theory
+uncertainties in the \ac{SM} and \ac{MSSM} Higgs boson cross section predictions are taken into account.
+The uncertainties for the \ac{SM} signal processes are described in more detail in reference \cite{YR4}.
+Uncertainties due to different renormalisation and factorisation scales
 amount to 3.9\% for gluon fusion,
-0.4\% for VBF, 2.8\% for ZH and 0.5\% for WH. The uncertainties
-due to different choices of pdf set and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for vector boson fusion,
+0.4\% for \ac{VBF}, 2.8\% for ZH and 0.5\% for WH. The uncertainties
+due to different choices of pdf set and $\alpha_s$ amount to 3.2\% for gluon fusion, 2.1\% for \ac{VBF},
 1.6\% for ZH and 1.9\% for WH.
-For the MSSM Higgs cross sections used in the models, the uncertainties
-due to different choices of factorisation and renormalisation scale
+For the MSSM Higgs boson cross sections used in the models, the uncertainties
+due to different choices of factorisation and renormalisation scale and the choice of pdf set
 are computed, separately for each \mA-\tanb~point, following the prescription in references \cite{pdf-lhc,alphas-uncs}.
@@
 \label{sec:mssm_uncs_shape}
-\subsubsection*{$\Pgt_{h}$ energy scale}
-The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}, affecting
+\subsubsection*{$\Pgth$ energy scale}
+The energy of hadronic taus is varied up and down by 3\%, affecting
 the shape of the total transverse mass distribution.
-The uncertainty is applied to the signal samples and to
+The uncertainty is applied to the signals and to
 backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels, namely
-\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
+\Ztautau, and the components of the \ttbar, single-top and di-boson backgrounds with real 
 hadronic taus.
 \subsubsection*{Electron energy scale}
-The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This 
+The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps. This 
 uncertainty is applied to the
 signals and to the \Ztautau background in the \emu channel.
-\subsubsection*{High-\pT~$\Pgth$ ID efficiency}
+\subsubsection*{High-\pT~$\Pgth$ identification efficiency}
 An additional $\Pgth$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\TeV}$
 is applied to account for the extrapolation from the tau ID efficiency
-measurement, which uses mostly taus close to the \PZ peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
-uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
-The shape difference between the nominal, up- and down- shapes for this uncertainty in the no b-tag category
+measurement, which mostly uses di-tau events close to the \PZ peak, to taus with higher transverse momenta. This
+uncertainty is applied to signals and backgrounds with real taus in the \etau, \mutau and \tautau channels.
+The shape difference between the nominal, up and down shapes for this uncertainty in the no b-tag category
 of the \tautau channel can be seen for a high-mass signal sample in figure \ref{fig:mssm_highpttauid_shapes}a and
@@
 background.]{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
-\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is much
+\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is
 larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
@@
 An uncertainty in the Drell-Yan shape reweighting based on \Zmm events
-is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
-\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
+is applied as 100\% of the correction to the \Ztautau background.
+\subsubsection*{$\text{Jet}\rightarrow\Pgth$ fake rate shape reweighting}
 On the \Wjets background in the \etau and \mutau channels a shape 
-uncertainty of $\frac{-20\% \times p_{\text{T}}}{\GeV}$ is 
-applied. This uncertainty is derived from variations in the data/\ac{MC} ratio
+uncertainty of $\frac{20\% \times p_{\text{T}}}{\GeV}$ is 
+applied. This uncertainty is derived from variations in the data to simulation ratio
 for the $\text{jet}\rightarrow\Pgth$ fake rate as a function of jet \pT~in 
-\Wjets events \cite{CMS-PAS-HIG-16-037}.
+\Wjets events.
 
@@
 \label{sec:mssm_signalextraction}
-The total transverse mass \mTtot~is used as discriminating variable in this analysis.
-All bins of the distribution are used to perform a shape analysis. The general statistical
+The total transverse mass \mTtot~is used as the discriminating variable for signal extraction in this analysis.
+Binned distributions of this variable are used to perform a shape analysis. The general statistical
 methods, including the incorporation of nuisance parameters in the fit, were 
@@
 \label{sec:mssm_sigext_ctrl}
-The control regions used for estimation of the 
+The control regions used for the estimation of the 
 \Wjets and QCD background contributions in the signal regions
@@
 normalisation is fully correlated between the three control 
-regions and the signal region. One common, freely floating, nuisance parameter
+regions and the signal region. One common, unconstrained, nuisance parameter
 controls the \Wjets normalisation in all four regions. The QCD normalisation
 is fully correlated between the opposite-sign and same-sign low-\mT~regions. The
-same is true for the opposite-sign and same-sign high-\mT~regions. This means there are
-two freely floating nuisance parameters that govern the QCD normalisation: one
-that controls the QCD normalisation in the two low-\mT~regions, and one
+same is true for the QCD normalisation in the opposite-sign and same-sign high-\mT~regions. This means there are
+two unconstrained nuisance parameters that govern the QCD normalisation: one
+that controls the normalisation in the two low-\mT~regions, and one
 that controls it in the two high-\mT~regions.
@@
 to the \Ztautau normalisation in the no b-tag categories of all four
-channels, again being controlled by a freely floating nuisance parameter. 
+channels, again being controlled by an unconstrained nuisance parameter. 
 The same is true for the \Zmm control region in the b-tag category
@@
 \label{sec:mssm_sigext_profile}
-Because the analysis targets the two main MSSM production modes, gluon fusion and
+Because the analysis targets the two main \ac{MSSM} production modes, gluon fusion and
 b-associated production, limits are set on these two signal processes. As discussed
@@
 process and vice versa. Therefore when calculating the upper limits on the $\Pg\Pg\phi$ ($\Pbottom\Pbottom\phi$)
-process, the contribution of the $\Pbottom\Pbottom\phi$ ($\Pg\Pg\phi$) process is profiled. This means it is floated
-in the fit like a nuisance parameter.
+process, the contribution of the $\Pbottom\Pbottom\phi$ ($\Pg\Pg\phi$) process is profiled. This means it is allowed
+to vary freely in the fit like a nuisance parameter.
 
 Because the analysis targets these two signal processes, it is possible
-to re-define the likelihood as a function of both the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ signals:
+to redefine the likelihood as a function of both the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ signals:
 \begin{equation}\label{mssm_2D_likelihood}
@@
 two processes. Using this definition a likelihood scan in two dimensions can be performed.
-First a 2D grid in $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$, both required to be greater than or equal to 0, is constructed. 
+First a 2D grid in $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$, both required to be greater than or equal to zero, is constructed. 
 The negative log-likelihood,
@@
 is then evaluated at each point. The point in the 2D grid where the NLL reaches
-its lowest value gives the best fit value for $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$.
-68\% and 95\% confidence intervals are constructed as the values
+its lowest value gives the best fit values for $\mu_{\Pg\Pg\phi}$ and $\mu_{\Pbottom\Pbottom\phi}$. The
+68\% and 95\% confidence level regions are constructed as the values
 $\mu_{\Pg\Pg\phi}^{N\%}$ and $\mu_{\Pbottom\Pbottom\phi}^{N\%}$ for which:
@@
 \begin{split}
-\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) = 0.5, ~\\
-\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) = 1.92.
+\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) = 1.14, ~\\
+\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) = 3.00.
 \end{split}
@@
 \label{sec:mssm_sigext_mssmvssm}
-The results of the search are interpreted in MSSM benchmark
+The results of the search are interpreted in \ac{MSSM} benchmark
 scenarios, with the interpretation made in the \mA-\tanb~plane.
-At each point in the \mA-\tanb~plane each MSSM scenario
-predicts a production cross section, and corresponding branching
+At each point in the \mA-\tanb~plane each \ac{MSSM} scenario
+predicts a production cross section, and a corresponding branching
 ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
@@
 signal from the three neutral Higgs bosons is combined into a single signal template\footnote{Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
-which give the \mTtot~distributions for all channels and categories with an example three-Higgs signal overlaid.}.
+which give the \mTtot~distributions for all channels and categories with an example three-Higgs boson signal overlaid.}.
 In this way the compatibility of the data with all three Higgs bosons, not just a single one, is tested.
@@
 The signal strength modifier $\mu$ takes the role of distinguishing between
-the two hypotheses in this case. The model must not allow for the coexistence 
+the two hypotheses in this case. The model must not allow for the non-physical coexistence 
 of the \ac{SM} and \ac{MSSM} hypotheses; the \ac{MSSM} hypothesis ($\mu=1$) has to be tested
@@
 The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, can not be applied
-to the Tevatron test statistic, and therefore the probability density functions need to be generated 
+to this test statistic, and therefore the probability density functions need to be generated 
 with toy datasets. Using these probability density functions $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
-If $\text{CL}_s < 0.05$ the MSSM hypothesis is excluded at 95\% CL. The generation of toy datasets and 
+If $\text{CL}_s < 0.05$ the \ac{MSSM} hypothesis is excluded at the 95\% CL. The generation of toy datasets and 
 calculation of corresponding $\text{CL}_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
@@
 \end{center}
-\caption[Probability density functions for the \ac{SM} and \ac{MSSM} hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.]{Probability density functions, obtained by generating a large number of toy datasets, for the \ac{SM} and \ac{MSSM} hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$
+\caption[Distributions of the test statistic for the SM and MSSM hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.]{Distributions of the test statistic, obtained by generating a large number of toy datasets, for the \ac{SM} and \ac{MSSM} hypotheses at three different points in the $m_{\PHiggslight}^{\text{mod+}}$
 scenario, each with different levels of separation between the \ac{MSSM} and \ac{SM} distributions.}
@@
 \label{sec:mssm_results}
-\subsection{Model--independent results}
+\subsection{Model-independent results}
 \label{sec:mssm_results_modelindep}
@@
 data has been performed, are shown in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em}.
-The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid 
+The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid 
 on the total transverse mass distributions. The signal peaks twice due to the presence of a light Higgs boson
@@
 and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid. Note that, to incorporate
-the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes a \PHiggslight boson
-at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps, and this is
+the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes an \PHiggslight boson
+at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps bosons, and this is
 the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
@@
 expectation. The
-95\% CL upper limits on \xsbr are shown in figure \ref{fig:mssm_results_limits}a
+95\% \ac{CL} upper limits on \xsbr are shown in figure \ref{fig:mssm_results_limits}a
 for gluon fusion and in figure \ref{fig:mssm_results_limits}b for b-associated
@@
 \end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion production process and the
-b-associated production process, combining all final states and categories.]{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at the 95\% CL for the gluon fusion production process and the
+b-associated production process, combining all final states and categories.]{Upper limits at the 95\% CL for (a) the gluon fusion production
 process and (b) the b-associated production process. All four final states and 
 all categories are combined for these limits. The green and yellow bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_results_limits}
@@
 $200\,\GeV$, beyond which the \tautau channel becomes more sensitive. The \etau
-channel is always slightly less sensitivie than the \mutau channel. The \emu channel
-is the least sensitive over a large part of the parameter space, until it overtakes the 
+channel is always slightly less sensitive than the \mutau channel. The \emu channel
+is the least sensitive over a large part of the mass range, until it overtakes the 
 \etau channel in sensitivity at $1.6\,\TeV$ and is slightly more sensitive than the
@@
 a narrower binning of the \mTtot~distribution is possible than for the other channels.
-The \mTtot~distribution for the high mass signals is therefore wide enough not to
-fall entirely into the last bin used for the fit. This means at high mass this channel
+The \mTtot~distribution for the high mass signals is therefore wide enough to span
+more than the highest \mTtot~bin used in the fit.
+This means at high mass this channel
 benefits more from the shape discrimination between signal and backgrounds than
@@
 \end{center}
-\caption[Comparison of expected upper limits at 95\% CL for gluon fusion and 
-b-associated production per channel.]{Expected upper limits at 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
-comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
+\caption[Comparison of expected upper limits at the 95\% CL for gluon fusion and 
+b-associated production per channel.]{Expected upper limits at the 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
+comparing the combination of all channels (green) with the \mutau (red), \etau (blue), \tautau (black)
 and \emu (gold) channels. For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
@@
 slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
-until at around $1.6\,\TeV$ it starts to overtake the \etau channel, with the sensitivity at $3.2\,\TeV$ 
+until at around $1.6\,\TeV$ where it starts to overtake the \etau channel, with the sensitivity at $3.2\,\TeV$ 
 being similar or slightly better than the \mutau channel.}
@@
 
-\subsection{Sensitivity to the standard model Higgs boson}
+\subsection{Sensitivity to the \acs{SM} Higgs boson}
 \label{sec:mssm_results_125GeV}
@@
 is $3.05\,\picobarn$ \cite{YR4} and the expected limit on \xsbr 
-for \ac{MSSM} $\Pg\Pg\phi$ production at around $125\,\GeV$ is around $20\,\picobarn$
+for \ac{MSSM} $\Pg\Pg\phi$ production at $125\,\GeV$ is around $20\,\picobarn$
 the analysis is not yet sensitive to the \ac{SM} Higgs boson. The
 limits shown in figure \ref{fig:mssm_results_greenband},
-which include the \ac{SM} Higgs boson as part of the backgrounds,
+which include the \ac{SM} Higgs boson as part of the background,
 are almost exactly the same as those shown in figure \ref{fig:mssm_results_limits}, which
@@
 \end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production processes, with the $125\,\GeV$ \ac{SM} Higgs boson included as one of the backgrounds.]{Upper limits at 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production processes, with the $125\,\GeV$ \ac{SM} Higgs boson included as one of the backgrounds.]{Upper limits at the 95\% CL for (a) the gluon fusion production
 process and (b) the b-associated production process. The $125\,\GeV$ \ac{SM} Higgs boson
@@
 all categories are combined for these limits. The light and dark green bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
 \label{fig:mssm_results_greenband}
@@
 best-fit value in the presence of the $125\,\GeV$ \ac{SM} Higgs boson. The dark and light purple contours
-indicate the 68\% and 95\% confidence interval, respectively. From the shape of the contours
+indicate the 68\% and 95\% confidence level regions, respectively. From the shape of the contours
 the correlation between the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$ processes is visible, illustrating
@@
 of both the gluon fusion ($x$ axis) and b-associated production ($y$ axis) processes. The red diamond indicates the
-expected best fit point for the presence of a $125\,\GeV$ \ac{SM} Higgs boson, and the purple bands indicate the 68\% and
-95\% confidence interval contours \cite{CMS-PAS-HIG-16-037}.}
+expected best-fit point for the presence of a $125\,\GeV$ \ac{SM} Higgs boson, and the purple bands indicate the 68\% and
+95\% confidence level regions \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_results_2D_scans}
@@
 
-\subsection{Interpretation in MSSM benchmark scenarios}
+\subsection{Interpretations in MSSM benchmark scenarios}
 \label{sec:mssm_results_modeldep}
@@
 
-Figure \ref{fig:mssm_mhmodp_2016}a shows the expected (dashed line and grey bands) and
-observed (blue shaded area bounded by solid line) exclusion of the search presented in this chapter
-in the \mA-\tanb~plane of the $m_{\PHiggslight}^{\text{mod+}}$ scenario. The red shaded band
+Figure \ref{fig:mssm_mhmodp_2016}a shows the expected and
+observed exclusions of the search presented in this chapter
+in the \mA-\tanb~parameter space of the $m_{\PHiggslight}^{\text{mod+}}$ scenario. The red shaded band
 indicates the area that is excluded due to the lack of a light Higgs boson with a mass compatible
-with $125\,\GeV$. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
-limits at high \tanb~have been significantly improved, by around $300\,\GeV$.
+with $125\,\GeV$ in the model. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
+limits at high \tanb~have been significantly improved, by around $300\,\GeV$ for a given \tanb~value..
 
@@
 \end{center}
-\caption[Exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
-scenario of the \AHtotautau analysis.]{Exclusion in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
+scenario of the \AHtotautau analysis.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
 obtained by the combination
-of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
+of all channels. The blue shaded area bounded by the 
 solid black line is the observed exclusion, with the dashed black line the
 expected exclusion. The light and dark grey bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion in the \ac{SM} hypothesis.
 The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
-is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ \cite{CMS-PAS-HIG-16-037}.}
+is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model \cite{CMS-PAS-HIG-16-037}.}
 \label{fig:mssm_mhmodp_2016}
@@
 
-Figure \ref{fig:mssm_mhmodp_2016}b shows the expected (dashed line and grey bands)
-and observed (blue shaded area bounded by solid line) exclusion of the search
-presented in this chapter in the \mA-\tanb~plane of the hMSSM scenario. 
+Figure \ref{fig:mssm_mhmodp_2016}b shows the expected
+and observed exclusions
+in the \mA-\tanb~plane of the hMSSM scenario. 
 It should be noted again that this model, although defined for \tanb~values
-upwards of 10, is only strictly valid for \tanb~below 10.
-The small excluded area around \mA~$=200\,\GeV$ is genuine. It is caused by the 
+upwards of ten, is only strictly valid for \tanb~below ten.
+A small additional excluded area around \mA~$=200\,\GeV$ is visible.
+It is caused by the 
 \xsbr in the model, which is driven by
@@
 \label{sec:mssm_combination}
-The results of the search for neutral Higgs bosons in the \ac{MSSM} using the di-tau
-final state, using a dataset
+The results of the search for neutral Higgs bosons decaying to di-tau pairs in the \ac{MSSM}, 
+using a dataset
 corresponding to an integrated luminosity of $12.9\,\invfb$, collected during the
-first half of 2016 and thus referred to as `2016 analysis', can be combined 
+first half of 2016 and thus referred to as the `2016 analysis', can be combined 
 with a previous search. This previous analysis
 was performed on a dataset corresponding to an integrated luminosity of $2.3\,\invfb$ 
-collected during 2015 (`2015 analysis'), and is detailed in reference \cite{CMS-PAS-HIG-16-006}.
+collected during 2015 (the `2015 analysis'), and is detailed in reference \cite{CMS-PAS-HIG-16-006}.
 By combining the two analyses it should be possible to set the most stringent
-limits on the two \ac{MSSM} production modes, and in the \mA-\tanb~plane of 
-\ac{MSSM} benchmark scenarios, available at the time of writing. It is also
-a first step on the way to combining the \AHtotautau analysis with
+limits, at the time of writing, on the two \ac{MSSM} production modes, and in the \mA-\tanb~plane of 
+\ac{MSSM} benchmark scenarios. It is also
+a first step on the way to combining this \AHtotautau analysis with
 searches for charged Higgs bosons or heavy neutral Higgs bosons in 
@@
 denoted $m_{\text{T},\tau\tau}$. The transverse di-tau mass 
-distributions for the signal region categories of the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
+distributions for the signal region categories of the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt}--\ref{fig:mssm_hig16006_mtsv_em}.
 \begin{figure}[h!]
@@
 \end{center}
-\caption[Transverse component of the di-tau mass for expected backgrounds
-and observed events in the no b-tag and b-tag categories of the \mutau channel.]{Transverse component of the di-tau mass for expected backgrounds and
+\caption[Transverse component of the di-tau mass for the expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \mutau channel.]{Transverse component of the di-tau mass for the expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
@@
 in the $m_{\text{\PHiggslight}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
-and once at higher mass, for the heavy \PHiggs and \PHiggsps.}
+and once at higher mass, for the heavy \PHiggs and \PHiggsps bosons.}
 \label{fig:mssm_hig16006_mtsv_mt}
@@
 \end{center}
-\caption[Transverse component of the di-tau mass for expected backgrounds
-and observed events in the no b-tag and b-tag categories of the \etau channel.]{Transverse component of the di-tau mass for expected backgrounds and
+\caption[Transverse component of the di-tau mass for the expected backgrounds
+and observed events in the no b-tag and b-tag categories of the \etau channel.]{Transverse component of the di-tau mass for the expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \etau channel.}
@@
 \end{center}
-\caption[Transverse component of the di-tau mass for expected backgrounds
+\caption[Transverse component of the di-tau mass for the expected backgrounds
 and observed events in the no b-tag and b-tag categories of the \tautau
-channel.]{Transverse component of the di-tau mass for expected backgrounds and
+channel.]{Transverse component of the di-tau mass for the expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \tautau channel.}
@@
 \end{center}
-\caption[Transverse component of the di-tau mass for expected backgrounds
-and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-tau mass for expected backgrounds and
+\caption[Transverse component of the di-tau mass for the expected backgrounds
+and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-tau mass for the expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
@@
 processes are shown in figure \ref{fig:mssm_results_hig16006_limits}a
-and b, respectively. All channels and categories are combined. A comparison of
+and \ref{fig:mssm_results_hig16006_limits}b, respectively. All channels and categories are combined. A comparison of
 the expected limits per channel is given in figure \ref{fig:mssm_results_limits_breakdown_hig16006}.
@@
 \end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production process.]{Upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production process.]{Upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
 process and (b) the b-associated production process. All four final states and 
 all categories are combined for these limits. The green and yellow bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit \cite{CMS-PAS-HIG-16-006}.}
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-006}.}
 \label{fig:mssm_results_hig16006_limits}
@@
 \end{center}
-\caption[Expected upper limits at 95\% CL for the gluon fusion and b-associated
-production, comparing the combination of all channels with the per-channel limits.]{Expected upper limits at 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
-comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
+\caption[Expected upper limits at the 95\% CL for the gluon fusion and b-associated
+production, comparing the combination of all channels with the per-channel limits.]{Expected upper limits at the 95\% \ac{CL} for (a) gluon fusion and (b) b-associated production,
+comparing the combination of all channels (green) with the \mutau (red), \etau (blue), \tautau (black)
 and \emu (gold) channels. For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
@@
 \label{sec:mssm_combination_procedure}
-The idea of combining the two analyses is to combine the 
+The procedure for combining the two analyses is to combine the 
 individual likelihoods to improve the analysis sensitivity and
@@
 
-The choice of correlation scheme is decided on
+The choice of correlation scheme is chosen
 based on the procedure used for the ATLAS and \ac{CMS}
 Higgs combinations \cite{MassComb,CouplComb}. This means
-uncertainties are either considered 100\% correlated or fully uncorrelated. Partial
+uncertainties are either considered 100\% (anti-)correlated or fully uncorrelated. Partial
 correlations are not taken into account, with a small number of exceptions. The
@@
 \midrule
-Luminosity & Partially \mbox{correlated} & Recommended by the CMS collaborators who perform the luminosity measurement, after dedicated studies.\\
-\midrule
-Jet energy scale & Fully \mbox{correlated} & Recommended by the CMS collaborators who derive jet energy corrections, after dedicated studies.\\
-\midrule
-b-Tagging & Uncorrelated & Scale factors used in the 2015 and 2016 analysis measured via different methods.\\
-\midrule
-Mis-tagging & Partially \mbox{correlated} & Recommended by the CMS collaborators responsible for deriving b-tagging scale factors, after dedicated studies.\\
+Luminosity & Partially \mbox{correlated} & \ac{CMS}-internal recommendation based on dedicated studies.\\
+\midrule
+Jet energy scale & Fully \mbox{correlated} & \ac{CMS}-internal recommendation based on dedicated studies.\\
+\midrule
+b-Tagging & Uncorrelated & Scale factors used in the 2015 and 2016 analyses measured via different methods.\\
+\midrule
+Mis-tagging & Partially \mbox{correlated} & \ac{CMS}-internal recommendation based on dedicated studies.\\
 \midrule
@@
 \midrule
-Tau ID/isolation/trigger& Uncorrelated & \scriptsize{On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite an observed downward correction of 8\% on the yield of backgrounds with real hadronic taus.}\\
-\midrule
-High-\pT~tau ID \mbox{efficiency} & Correlated & This should not be affected by the lack of tau ID scale factor and covers the same underlying issue in both analyses.\\
-\midrule
-Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016.\\
-\midrule
-Electron energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016.\\
-\midrule
-Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, are used in 2014 and 2016 to derive the correction.
+Tau ID/isolation/trigger& Uncorrelated & \scriptsize{The \ac{L1} trigger was replaced between 2015 and 2016.
+The analyses received different tau ID scale factors, implying different behaviour of the hadronic tau selection criteria.}\\
+\midrule
+High-\pT~tau ID \mbox{efficiency} & Correlated & This should not be affected by the difference of tau ID scale factor and covers the same underlying issue in both analyses.\\
+\midrule
+Tau energy scale & Correlated & There is no reason to expect a different energy scale between 2015 and 2016 as the tau energy reconstruction remained the same.\\
+\midrule
+Electron energy scale & Correlated & There is no reason to expect a different energy scale between 2015 and 2016.\\
+\midrule
+Drell-Yan shape & Correlated & \scriptsize{The same simulated samples are used in 2015 and 2016 to derive the correction.
 The weights derived for the 2015 analysis and the 2016 analysis are very similar.}\\
 \midrule
-W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & \scriptsize{Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
-The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point.}\\
-\midrule
-MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016.\\
+\PW $\text{jet}\rightarrow\Pgth$ fake rate shape & Uncorrelated & \scriptsize{Correction not applied in the 2016 dataset while it was applied for the 2015 analysis.
+The uncertainties have a different functional form, possibly due to different $\text{jet}\rightarrow\Pgth$ fake rates as a result of the use of a different tau isolation working point.}\\
+\midrule
+MET uncertainties & Correlated & The same MVA \MET BDT training was used both for 2015 and 2016.\\
 \midrule
@@
 \midrule
-Di-boson and single-top $\sigma$ & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
+Di-boson and single-top $\sigma$& Correlated & The same recommended cross sections were used in 2015 and 2016.\\
 \midrule
@@
 SM signal theory uncertainties & Correlated & The same recommended cross sections were used in 2015 and 2016.\\
-\midrule
-\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in the 2015 analysis as no fits to the \Zmm control region were included.}\\
-\midrule
-\Ztautau \mbox{extrapolation}& N/A & \scriptsize{Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance.}\\
 \midrule
@@
 \midrule
-$\Pe\rightarrow\Pgth$ fake rate & Correlated & Expected to behave the same in 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.\\
-\midrule
-$\Pgm\rightarrow\Pgth$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet, while this had changed for the 2016 analysis.\\
+\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in the 2015 analysis as no fits to the \Zmm control region were included.}\\
+\midrule
+\Ztautau \mbox{extrapolation}& N/A & \scriptsize{Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance.}\\
+\midrule
+$\Pe\rightarrow\Pgth$ fake rate & Correlated & \scriptsize{Expected to behave the same in the 2015 and 2016 datasets, the same anti-electron discriminator was used and the uncertainty on the fake rate should not be affected by the use of a different hadronic tau ID discriminator working point.}\\
+\midrule
+$\Pgm\rightarrow\Pgth$ fake rate & Uncorrelated & \scriptsize{Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet, while this had changed for the 2016 analysis.}\\
 \midrule
@@
 \midrule
-QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-isolated sideband in 2015 and 2016 analyses.\\
-\midrule
-QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband.\\
+QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of different anti-isolated sidebands in 2015 and 2016 analyses.\\
+\midrule
+QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sidebands.\\
 \midrule
@@
 \midrule
-Statistical \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-Systematic \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~region with anti-isolated $\Pgth$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses we could expect a different event composition in this region.
-In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
-\midrule
-Statistical \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-Systematic \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately.}\\
-\midrule
-QCD OS/SS \mbox{ratio} statistical \mbox{uncertainty} (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated.\\
-\midrule
-QCD OS/SS \mbox{ratio} systematic \mbox{uncertainty} (\etau and \mutau) & Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
+\scriptsize{Statistical \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)}& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+\scriptsize{Systematic \mbox{uncertainty} in W opposite-sign to same-sign ratio (\etau and \mutau)}& Uncorrelated & \scriptsize{Uncertainty based on high \mT~region with anti-isolated $\Pgth$, but because of the tau \pT~cuts being different in the 2015 and 2016 analyses a different event composition can be expected in this region.}\\
+\midrule
+\scriptsize{Statistical \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau)}& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+\scriptsize{Systematic \mbox{uncertainty} in W low/high-\mT~\mbox{ratio} (\etau and \mutau) }& Uncorrelated & Different \mT~selections were used in the 2015 and 2016 analyses.\\
+\midrule
+\scriptsize{QCD OS/SS \mbox{ratio} statistical \mbox{uncertainty} (\etau and \mutau) }& Uncorrelated & Statistical uncertainties should not be correlated.\\
+\midrule
+\scriptsize{QCD OS/SS \mbox{ratio} systematic \mbox{uncertainty} (\etau and \mutau) }& Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses.
 Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.}\\
 \midrule
-bin-by-bin \mbox{uncertainties} for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible.\\
+\scriptsize{bin-by-bin \mbox{uncertainties} for templates with low numbers of events} & Uncorrelated & These are statistically independent.\\
 \bottomrule
@@
 for the combination of the 2015 and 2016 analyses are shown in figure
-\ref{fig:mssm_results_combination_limits}. The limits behave as expected
-from the individual 2015 and 2016 limits.
+\ref{fig:mssm_results_combination_limits}. The expected and observed limits
+exhibit similar trends as 
+the individual 2015 and 2016 limits.
 
@@
 \end{center}
-\caption[Upper limits at 95\% CL for the gluon fusion and b-associated production
-process, obtained by combining all channels and categories of the 2015 nd the 2016 analyses.] {Upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production
+process, obtained by combining all channels and categories of the 2015 and the 2016 analyses.]{Upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
 process and (b) the b-associated production process. These results
@@
 and the 2016 analyses. The green and yellow bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.}
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit.}
 \label{fig:mssm_results_combination_limits}
@@
 higher masses the sensitivity is only very slightly improved with respect to the 
-analysis of the $12.9\,\invfb$ dataset. However, for masses between $200$ and $800\,\GeV$
+analysis of the $12.9\,\invfb$ dataset alone. However, for masses between $200$ and $800\,\GeV$
 there is a larger improvement in sensitivity from combining the two analyses.
-This behaviour is expected since the 2016 analysis used a slightly different
+This behaviour is expected since the 2016 analysis used a different
 selection that made the analysis more optimal at masses above $800\,\GeV$,
@@
 \end{center}
-\caption[Comparison of the expected upper limits at 95\% CL for the 
-gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at 95\% \ac{CL} for (a) the gluon fusion production
+\caption[Comparison of the expected upper limits at the 95\% CL for the 
+gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
 process and (b) the b-associated production process. The green curve shows the results
@@
 and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of $2.3\,\invfb$).
-The plotted relative difference is with respect to the limits from the 2016 analysis, showing how the combination
-improves on those limits by between a few per cent at high mass up to 40\% at low mass.}
+The relative difference is shown with respect to the limits from the 2016 analysis, showing how the combination
+improves on those limits by between a few percent at high mass up to 40\% at low mass.}
 \label{fig:mssm_results_combination_limits_comp}
@@
 scenario by combining the 2015 and 2016 analyses. Figure \ref{fig:mssm_mhmodp_20152016}b shows this exclusion
-in the hMSSM scenario. On both figures the expected and observed exclusion from the
+in the hMSSM scenario. On both figures the expected and observed exclusions from the
 2016 analysis only are overlaid, which shows how the combination increases the
@@
 \end{center}
-\caption[Exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
-scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusion in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+\caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
+scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
 obtained by the combination
@@
 expected exclusion. The light and dark grey bands indicate
-the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion in the \ac{SM} hypothesis.
 The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
-is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$. The dashed (solid)
+is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$ in the model. The dashed (solid)
 blue lines indicate the expected (observed) exclusion from the 2016 analysis alone.}

### 2017-02-27 MSSM/UncOv.tex
Adding a few more figs to MSSM chapter
More editing

@@
     & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
-     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
+     & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
+    \multicolumn{10}{l}{\textbf{Integrated luminosity 13 TeV}} \\
     All from MC    & 6.2\%  &6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\MET \textbf{scale} }\\
+    \multicolumn{10}{l}{\MET~\textbf{scale} }\\
     ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ, VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
+    TT(T/J),VV(T/J) & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
     \midrule
-    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
+    \multicolumn{4}{l}{\MET~\textbf{resolution}} \\
     ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat; TTT,TTJ,VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
+    TT(T/J),VV(T/J) & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
     \midrule
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
+    \multicolumn{10}{l}{\textbf{b-Tagging efficiency} }\\
     All from MC & 0--3\% & 0--3\% & 0--3\% & 0--2\% & 1--3\% &  0--3\%& 0--3\% & 0--3\%& Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
+    \multicolumn{10}{l}{\textbf{light jet mis-tagging rate } }\\
     All from MC & & & & & 1--7\% & & & & Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
+    \multicolumn{10}{l}{\textbf{High}-$p_{\text{T}}$ $\Pgth$\textbf{ ID efficiency } } \\
     ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
+    \multicolumn{10}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting} }\\
     TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
     \midrule
-    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
+    \multicolumn{10}{l}{\textbf{Drell-Yan reweighting } }\\
     ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
+    \multicolumn{10}{l}{\textbf{Jet} $\rightarrow\Pgth$ \textbf{fake rate reweighting } }\\
     W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
@@
     TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
-    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
+    \multicolumn{10}{l}{\textbf{Normalisation, di-boson + single-top} } \\
     VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
-   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\
+   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\Pgth$ }\\
     ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Cats:C,chns:U        \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
+    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\Pgth$ } \\
     ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Cats:C,chns:U  \\
@@
     & \multicolumn{4}{|c}{\textbf{No b-tag}} & \multicolumn{4}{|c}{\textbf{B-tag}} & \textbf{Correlation}           \\
-     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\
+     & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\
+    \multicolumn{10}{l}{\textbf{Integrated luminosity 13 TeV}} \\
     All from MC    & 6.2\%  & 6.2\%  & 6.2\%    & 6.2\% & 6.2\% & 6.2\% & 6.2\% & 6.2\% & Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\MET \textbf{scale}}\\
+    \multicolumn{10}{l}{\MET~\textbf{scale}}\\
     ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ                         \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
+    TT(T/J),VV(T/J) & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
     \midrule
-    \multicolumn{10}{l}{\MET \textbf{resolution}} \\
+    \multicolumn{10}{l}{\MET~\textbf{resolution}} \\
     ZTT,W     & 2\% & & 2\% & &2\% &  & 2\% & & Corr. between chn/cat, TTT,TTJ,VVT,VVJ          \\
-    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
+    TT(T/J),VV(T/J) & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\
     \midrule
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\
+    \multicolumn{10}{l}{\textbf{b-Tagging efficiency} }\\
     All from MC & 0--3\% & 0--3\% & 0--4\% & 0--4\% & 1--4\% & 0--2\% & 0--2\% & 0--2\% & Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\
+    \multicolumn{10}{l}{\textbf{Light jet mis-tagging rate } }\\
     All from MC & & & & & 0--3\% & & & & Fully correlated\\
@@
     \midrule
-    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\
+    \multicolumn{10}{l}{\textbf{High}-$p_{\text{T}}$ $\Pgth$\textbf{ ID efficiency } } \\
     ZTT,TTT,VVT, signal    & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\
+    \multicolumn{10}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting} }\\
     TTT,TTJ  & shape & shape & shape & shape & shape & shape & shape & shape & Fully correlated    \\
     \midrule
-    \multicolumn{10}{l}{\textbf{DY reweighting } }\\
+    \multicolumn{10}{l}{\textbf{Drell-Yan reweighting } }\\
     ZTT       & shape & shape & shape & shape  & shape & shape & shape & shape &Fully correlated              \\
     \midrule
-    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
+    \multicolumn{10}{l}{\textbf{Jet} $\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\
     W         & shape &  &  &   & shape &  &  &  &Fully correlated              \\
@@
     TTT,TTJ     & 6\% & 6\% & 6\% & 6\%   & 6\% & 6\% &6\% & 6\%  & Fully correlated                \\
-    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\
+    \multicolumn{10}{l}{\textbf{Normalisation, di-boson + single-top} } \\
     VVT,VVJ     & 5\% & 5\% & 5\% & 5\%   & 5\% & 5\% & 5\% & 5\% & Fully correlated         \\
-   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\
+   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\Pgth$ }\\
     ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Cats:C,chns:U       \\
-    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\
+    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\Pgth$ } \\
     ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Cats:C,chns:U       \\
@@
 or background events in the \tautau channel.}
-{\scriptsize
+{\tiny
 \begin{tabular}{l|cc|p{5cm}}
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
+    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\
     All from MC      & 6.2\%      & 6.2\%  & Fully correlated                           \\
@@
     \midrule
-    \multicolumn{4}{l}{\MET \textbf{scale}} \\
+    \multicolumn{4}{l}{\MET~\textbf{scale}} \\
     ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
@@
     \midrule
-    \multicolumn{4}{l}{\MET \textbf{resolution}} \\
+    \multicolumn{4}{l}{\MET~\textbf{resolution}} \\
     ZTT,W     & 2\%     & 2\% & Correlated between chn/cat,                          \\
@@
     \midrule
-    \multicolumn{4}{l}{Tau-lepton identification and trigger} \\
+    \multicolumn{4}{l}{\textbf{Tau-lepton identification and trigger}} \\
     ZTT,TTT,VVT, signal         & 10\%    & 10\%  & Fully correlated                      \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\
+    \multicolumn{4}{l}{\textbf{b-Tagging efficiency} }\\
     All from MC   & 0--4\%     & 0--11\%  & Fully correlated                  \\
     \midrule
-   \multicolumn{4}{l}{\textbf{B-mistag rate}} \\
+   \multicolumn{4}{l}{\textbf{Light jet mis-tagging rate}} \\
     All from MC    &  0--1\%    & 0--12\%  & Fully correlated                  \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\
+    \multicolumn{4}{l}{\textbf{High}-$p_{\text{T}}$ $\Pgth$ \textbf{ID efficiency}} \\
     ZTT,TTT,VVT, signal       & shape      & shape & Correlated between categories, uncorrelated between channels   \\
     \midrule
-    \multicolumn{4}{l}{\textbf{DY reweighting } } \\
+    \multicolumn{4}{l}{\textbf{Drell-Yan reweighting } } \\
     ZTT       & shape      & shape & Fully correlated                       \\
     \midrule
-    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\
+    \multicolumn{4}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting } } \\
     TTT,TTJ & shape & shape & Fully correlated                  \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}}\\
     VVT,VVJ &  5\%        & 5\%       & Fully correlated                        \\
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\Pgth$}\\
     ZL & 10\%     & 10\%       & Correlated between categories, uncorrelated between channels                        \\
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\Pgth$}\\
     ZJ,W,TTJ & 20\%     & 20\%       & Correlated bewteen categories, uncorrelated between channels     \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\
     W & 4\% & 4\% & Fully correlated \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
+    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\
     All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
@@
     \midrule
-    \multicolumn{4}{l}{\MET \textbf{scale}} \\
+    \multicolumn{4}{l}{\MET~\textbf{scale}} \\
     ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
@@
     \midrule
-   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
+   \multicolumn{4}{l}{\MET~\textbf{resolution}} \\
     ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
+    \multicolumn{4}{l}{\textbf{b-Tagging efficiency}} \\
     All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
     \midrule
-    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
+    \multicolumn{4}{l}{\textbf{Light jet mis-tagging rate}}\\
     All from MC      &     & 0--10\% & Fully correlated                    \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
+    \multicolumn{4}{l}{\textbf{Drell-Yan reweighting }}\\
      ZTT       & shape      & shape & Fully correlated                       \\
    \midrule
-    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
+    \multicolumn{4}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting}}\\
     TT & shape & shape  & Fully correlated                 \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
+    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}} \\
     VV        & 5\%       & 5\% & Fully correlated                       \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\
     W+jets & 4\% & 4\% & Fully correlated\\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
+    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\
     All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
@@
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
+    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}} \\
     VV        & 5\%       & 5\% & Fully correlated                       \\
     \midrule
-    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
+    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\
     W+jets & 4\% & 4\% & Fully correlated\\

### 2017-02-27 Theory/Theory.tex
More editing

@@
 strong coupling strength decreases at 
-high energy (or short distances), making the force weaker. 
+high energy, or short distances, making the force weaker. 
 A more detailed introduction to \ac{QCD} can 
@@
 \begin{equation}\label{eqn:ewk_propagators_W}
-\PW^{\pm} &= \frac{1}{\sqrt{2}}(W_{\mu}^1 \mp i W_{\mu}^2),
+\PW_{\mu}^{\pm} &= \frac{1}{\sqrt{2}}(\PW_{\mu}^1 \mp i \PW_{\mu}^2),
 \end{equation}
 \begin{equation}\label{eqn:ewk_propagators_phot}
-A_{\mu} &= W_{\mu}^3\sin{\theta_W} + B_{\mu}\cos{\theta_W},
+\text{A}_{\mu} &= \PW_{\mu}^3\sin{\theta_W} + B_{\mu}\cos{\theta_W},
 \end{equation}
 \begin{equation}\label{eqn:ewk_propagators_Z}
-Z_{\mu} &= W_{\mu}^3\cos{\theta_W} - B_{\mu}\sin{\theta_W}.
+\PZ_{\mu} &= \PW_{\mu}^3\cos{\theta_W} - \text{B}_{\mu}\sin{\theta_W}.
 \end{equation}
-In these equations $A_{\mu}$ is the photon field and $Z_{\mu}$ the \PZ field.
+In these equations $\text{A}_{\mu}$ is the photon field and $\PZ_{\mu}$ the \PZ field.
 The weak mixing angle $\theta_W$ is related to the weak (g) and electromagnetic (g')
@@
 The idea is to add a field that is symmetric under gauge transformations, but
-has a nonzero vacuum expectation value and thus breaks the symmetry spontaneously.
+has a non-zero vacuum expectation value and thus breaks the symmetry spontaneously.
 According to Goldstone's theorem \cite{goldstone-theorem,goldstone-theorem-2} a 
@@
 
-Under a local $SU(2)\times U(1)$ transformation, the field transforms as,
+Under a local SU(2)$\times$U(1) transformation, the field transforms as,
 \begin{equation}\label{eqn:hfield_trsf}
@@
 \begin{equation}\label{eqn:H_cov_deriv}
-D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{W_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'B_{\mu}.
+D_{\mu} = \partial_{\mu} - \frac{i}{2}g\vec{\PW_{\mu}}\cdot\vec{\sigma} - \frac{i}{2}g'\text{B}_{\mu}.
 \end{equation}
 In the vacuum state, $V(\Phi^{\dagger}\Phi) =0$, $\Phi^{\dagger}\Phi=\frac{\mu_{\text{SM}}^2}{2\lambda}$ and so
-$\Phi$ has to be nonzero.
+$\Phi$ has to be non-zero.
 Now choosing $\phi^+$ = 0 and taking $\phi^0$ to be real, this means:
@@
 and using the definitions of $\PW_{\mu}^{\pm}$ and $\PZ_{\mu}$ from 
-equations \ref{eqn:ewk_propagators_W}-\ref{eqn:ewk_propagators_Z}, the Lagrangian becomes
+equations \ref{eqn:ewk_propagators_W}--\ref{eqn:ewk_propagators_Z}, the Lagrangian becomes
 \begin{equation}\label{eqn:completed_lagrangian}
@@
 Using these developments it is also possible to add mass terms for the fermions
-through Yukawa couplings between the fermion- and Higgs fields, which are of the form
+through Yukawa couplings between the fermion and Higgs fields, which are of the form
 \begin{equation}\label{eqn:yukawa_coupl}
@@
 a large range of possible masses needed to be covered in Higgs boson searches. 
-Searches for the Higgs boson at the \ac{LEP} did not lead
-to its observation. However, masses below $114.4\,\GeV$ were excluded at 95\% \ac{CL} \cite{LEP-Higgs},
+Searches for the Higgs boson at the \ac{LEP} collider did not lead
+to its observation. However, masses below $114.4\,\GeV$ were excluded at the 95\% \ac{CL} \cite{LEP-Higgs},
 providing a lower search limit. Subsequent searches at the 
@@
 comes from the ATLAS and CMS combined
-mass measurement using the full Run 1 dataset \cite{MassComb}.
-The combined ATLAS and CMS production- and decay rate measurements, also using the full Run 1 dataset,
+mass measurement using the full dataset collected up to the end of 2012 \cite{MassComb}.
+The combined ATLAS and CMS production and decay rate measurements, also using the full dataset collected up to the end of 2012,
 show very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
-the $\PHiggslight \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination. During Run 1
-searches by the ATLAS and CMS Collaborations resulted in observed 
-significances of $4.5\sigma$ \cite{ATLAS-tautau} and $3.2\sigma$ \cite{SMHtautauCMS}, respectively. 
+the $\PHiggs \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination. During the 2010--2012
+LHC running period searches by the ATLAS and CMS Collaborations resulted in observed 
+significances of $4.5\sigma$ \cite{ATLAS-tautau} and $3.2\sigma$ \cite{SMHtautauCMS} for this process, respectively. 
 %Despite the good agreement with the \ac{SM}, some discrepancies do remain, 
@@
 Figure \ref{fig:theory_smhprod} shows Feynman diagrams of the dominant Higgs boson production modes
-at the \ac{LHC}. From the production cross sections for each mode, shown in figure
-\ref{fig:theory_smhxsbr}a, we see that gluon fusion production is by far dominant. The other modes
+at the \ac{LHC}. The production cross sections for each mode, shown in figure
+\ref{fig:theory_smhxsbr}a, show that gluon fusion production is by far dominant. The other modes
 shown have cross sections at least an order of magnitude smaller, but are of importance due to their topologies.
@@
 
-Considering the branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b, we observe that
+The branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b show that
 the branching ratios of
@@
 
-During Run 2 of the LHC, \ac{SM} Higgs boson measurements, and searches for the 
+Since the re-start of the LHC in 2015, \ac{SM} Higgs boson measurements, and searches for the 
 \ac{SM} Higgs boson in decay channels not previously established, have 
@@
 as has the decay in to $\PZ\PZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
-of $\PHiggs\rightarrow WW$ are being performed \cite{CMSHWW2016,ATLASHWW2016}. Establishing evidence for the decay of 
+of $\PHiggs\rightarrow \PW\PW$ have been performed \cite{CMSHWW2016,ATLASHWW2016}. Establishing evidence for the decay of 
 $\PHiggs\rightarrow \Pbottom\Pbottom$ \cite{CMSVBFHbb2016,ATLASVHbb2016} and of $\PHiggs\rightarrow \mu\mu$ \cite{ATLASHmm2016} 
 is still to be achieved.
-Finally, searches for $\Ptop\Ptop\PHiggs$ production, which are important to probe directly the top-Higgs coupling, have also been carried 
-out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As the Run 2 dataset
-keeps growing studies at the \acs{LHC} will continue to test the compatibility of the Higgs boson with the \ac{SM}.
+Finally, searches for $\Ptop\Ptop\PHiggs$ production, which are important to directly probe the top-Higgs coupling, have also been carried 
+out \cite{CMSttH2016,CMSttHmultilep2016,ATLASttHbb2016,ATLASttHmultilep2016}. As more data
+are collected studies at the \acs{LHC} will continue to test the compatibility of the Higgs boson with the \ac{SM}.
 
@@
 \label{sec:theory_BSM}
-The \ac{SM} has been successfully tested to high accuraccy \cite{pdg-2014}. However,
+The \ac{SM} has been successfully tested to high accuracy \cite{pdg-2014}. However,
 some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
 For example, it does not provide a candidate for dark matter, which is estimated
-to make up 25\% of the matter energy density in the universe.
+to make up 25\% of the matter-energy density in the universe.
 In addition, the running coupling constants of the electroweak and
@@
 This is the energy scale at which new physics must enter.
-We know that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
+It is known that $\Lambda \leq \mathcal{O}(10^{19})$, the Planck scale, as quantum 
 gravitational effects start to become important in that region. The energy scale $\Lambda$ enters
@@
 \begin{split}
-&M_{H_{\text{SM}}}^2  = (M_H^2)_0 + \Delta M_H^2,\\
-&\Delta M_H^2 \sim \mathcal{O}(\Lambda^2).
+&M_{\PHiggs_{\text{SM}}}^2  = (M_H^2)_0 + \Delta M_{\PHiggs}^2,\\
+&\Delta M_{\PHiggs}^2 \sim \mathcal{O}(\Lambda^2).
 \end{split}
@@
 \end{equation}
-Using this we can define
+This can be used to define
 \begin{equation}\label{eqn:tanb_def}
@@
 doublets, three become longitudinal states of the $\PW^{\pm}$ and \PZ bosons.
-The remaining 5 degrees of freedom lead to five physical Higgs bosons, a charged
+The remaining five degrees of freedom lead to five physical Higgs bosons: a charged
 Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
-and the neutral scalars \PHiggslight and \PHiggs. These arise from mixing of the
+and the neutral scalars \PHiggslight and \PHiggs. These arise from the mixing of the
 fields as:
@@
 \mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
-m_{\PHiggsps}^2\sin{\beta}^2 + m_{\PZ}^2\cos{\beta}^2 & -(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta}\\
--(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta} & m_{\PHiggsps}^2\cos{\beta}^2+m_{\PZ}^2\sin{\beta}^2 \end{pmatrix},
+m_{\PHiggsps}^2\sin{\beta}^2 + m_{\PZ}^2\text{cos}^2\beta & -(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta}\\
+-(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta} & m_{\PHiggsps}^2\text{cos}^2\beta+m_{\PZ}^2\text{sin}^2{\beta} \end{pmatrix},
 \end{equation}
@@
 \begin{equation}\label{eqn:scalarmass}
-m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\cos{2\beta}^2}].
+m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\text{cos}^2 2\beta}].
 \end{equation}
@@
 \begin{equation}\label{eqn:alpha_constraint}
-\cos{(\beta-\alpha)}^2 = \frac{m_{\PHiggslight}^2(m_{\PZ}^2-m_{\PHiggslight}^2)}{m_{\PHiggsps}^2(m_{\PHiggs}^2-m_{\PHiggslight}^2)}.
+\text{cos}^2(\beta-\alpha) = \frac{m_{\PHiggslight}^2(m_{\PZ}^2-m_{\PHiggslight}^2)}{m_{\PHiggsps}^2(m_{\PHiggs}^2-m_{\PHiggslight}^2)}.
 \end{equation}
@@
 The tree-level couplings of the neutral Higgs bosons to bosons and fermions 
-are modified with respect to the couplings of the Higgs boson in the \ac{SM}, by the multiplicative factors
+are modified with respect to the couplings of the Higgs boson in the \ac{SM} by the multiplicative factors
 given in table \ref{tab:mssm_couplings} \cite{YR4}.
@@
 with negligible couplings to bosons for the two remaining neutral
-Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
+Higgs bosons; couplings to down-type quarks and leptons enhanced by a factor \tanb;
 and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
@@
 vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
-bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW or \PZ associated
-production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
+bosons is suppressed with respect to the \ac{SM} expectation, \ac{VBF} and \PW or \PZ associated
+production ($\PW\PHiggs$ or $\PZ\PHiggs$) are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
 the dominant production mode at low \tanb.
@@
 Due to the negative top-bottom loop interference effect the gluon fusion cross section decreases with increasing \tanb~up
-to around \tanb~$=3$, when the cross section starts to increase with increasing \tanb~again.
+to around \tanb~$=3$, where the cross section starts to increase with increasing \tanb~again.
 
@@
 \begin{center}
-\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.png}}
+\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.pdf}}
 \subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
@@
 \caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
-production of neutral Higgs bosons in the MSSM \cite{CMS-PAS-HIG-16-037}.}
+production of neutral Higgs bosons in the MSSM. The squarks in the gluon fusion production loop do not contribute to production of the \PHiggsps boson.}
 \label{fig:production_mssm}
@@
 form, there are nine free parameters in the potential of a CP-conserving 2HDM. 
-These are taken as \tanb, the mixing angle $\alpha$, already discussed in 
+These are taken as \tanb~and the mixing angle $\alpha$, already discussed in 
 the context of the \ac{MSSM}, the masses of the five Higgs bosons,
@@
 proportional to $\cos{(\beta-\alpha)}$ and there are no corrections
-from \ac{SUSY} particles to make the branching ratios nonzero.
+from \ac{SUSY} particles to make the branching ratios non-zero.
 
@@
 shows the inclusive \xsbr for production and decay
-of a \PHiggsps boson in the same type-II \ac{2HDM} example, at two \tanb~points. At
+of an \PHiggsps boson in the same type-II \ac{2HDM} example, at two values of \tanb. At
 low \tanb~the \xsbr for \Htohh production and decay and \AtoZh production
@@
 SUSY-breaking parameters that affect the Higgs
-sector, it us usual to define benchmark scenarios 
+sector, it is usual to define benchmark scenarios 
 in which the only free parameters are \mA~and \tanb.
@@
 The parameters that need to be fixed in the benchmark scenarios are the 
-\ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks.
-In addition, the higgsino mass parameter $\mu_{\text{MSSM}}$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
-A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
-trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_{\Ptop}$, $A_{\Pbottom}$ and $A_{\Pgt}$) and the 
-stop, sbottom and stau mixing parameters ($X_t$, $X_b$ and $X_{\tau}$) are also fixed.
+\ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks;
+the higgsino mass parameter $\mu_{\text{MSSM}}$; the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$;
+the masses of the stau, $m_{\tilde{\ell}_3}$, and the gluino, $m_{\tilde{g}}$; the 
+trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_{\Ptop}$, $A_{\Pbottom}$ and $A_{\Pgt}$); and the 
+stop, sbottom and stau mixing parameters ($X_{\Ptop}$, $X_{\Pbottom}$ and $X_{\tau}$).
 
@@
 and the masses of the first and second generation sleptons to $500\,\GeV$. The trilinear
-couplings of the first and second generation squarks and sleptons are taken to be 0.
+couplings of the first and second generation squarks and sleptons are taken to be zero.
 %Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
@@
 The mass of the light Higgs boson in the \ac{MSSM} is said to
-be compatible with $125\,\GeV$, if the light Higgs boson mass lies within a 
-mass window of $\pm 3\,\GeV$ mass window around $125\,\GeV$. This mass window
+be compatible with $125\,\GeV$ if the light Higgs boson mass lies within 
+$\pm 3\,\GeV$ around $125\,\GeV$. This mass window
 corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
@@
 In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
-the radiative corrections are tuned to obtain light 
-Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
+the radiative corrections are tuned to obtain a light 
+Higgs boson mass of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
 Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
@@
 \subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
-\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
+\subfloat[Low-\tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
 \end{center}
 \caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
-\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
+\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
 of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
-indicate masses lower than $122\,\GeV$. The figures shows that
+indicate masses lower than $122\,\GeV$. The figures show that
 the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
@@
 
-The branching fractions of \Htohh and \AtoZh in the low-\tanb~scenario are shown in
+The branching ratios of \Htohh and \AtoZh in the low-\tanb~scenario are shown in
 figure \ref{fig:lowtbhigh_br}. For both decay channels there are areas in the \mA-\tanb~plane
@@
 \label{eqn:hmssm_deltam22}
-\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggslight}^2},
+\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggslight}^2}.
 \end{equation}
 
-This means we can write,
+This can be used to write,
 \begin{equation}
@@
 is only well defined in regions where the denominator in equations
-\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggslight}^2$, is nonzero. 
+\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggslight}^2$, is non-zero. 
 This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
@@
 \label{sec:theory_BSMH_status}
-With the data collected during 
-Run 1 of the \ac{LHC} many searches for BSM Higgs
+With the data collected by the \ac{LHC}
+experiments up to the end of 2012 many searches for \ac{BSM} Higgs
 bosons were performed. Figure \ref{fig:bsm_summary} shows the interpetations
-of different searches performed with the \acs{CMS} detector during Run 1 of the \acs{LHC}
+of different searches performed with the \acs{CMS} detector up to the end of 2012
 in the $m_{\PHiggslight}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
@@
 hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250$--$350\,\GeV$.
-The red exclusion contour in figure \ref{fig:bsm_summary}b is the re-interpretation of the analysis presented in
+The red exclusion contour in figure \ref{fig:bsm_summary}b is the reinterpretation of the analysis presented in
 chapter \ref{chap:hhh}.
 
-In Run 2 of the \acs{LHC} searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
+Since the re-start of the \acs{LHC} in 2015 searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
 have been performed with the \acs{CMS} detector. The results of these searches will be presented in chapter \ref{chap:mssm}. 
@@
 \end{center}
-\caption[Summary of the interpretations of Run 1 BSM Higgs searches at CMS in the $m_{\PHiggslight}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{\PHiggslight}^{\text{mod+}}$ and (b) the
+\caption[Summary of the interpretations of BSM Higgs boson searches using data up to the end of 2012 at CMS in the $m_{\PHiggslight}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of \ac{BSM} Higgs boson searches at \acs{CMS} using data
+collected up to the end of 2012 in (a) the $m_{\PHiggslight}^{\text{mod+}}$ and (b) the
 hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
-scenarios. The results from \ac{MSSM} Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
+scenarios. The results from \ac{MSSM} Higgs boson searches with decays into tau leptons are shown in blue and exclude more of the parameter
 space than any of the other searches. The \ac{MSSM} Higgs to $\Pbottom\Pbottom$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part

### 2017-02-27 backmatter.tex
Adding some bits on MSSM scenarios to theory chapter
Adding more on 2HDMs and SM H measurements
Adding some more stuff
Own theory chapter edits
Adding some MSSM chapter stuff
Detailed edit of detector chapter
Adding some more of the crap at the beginning, plus editing
Some more editing
More editing, plus additional cosmetic fixes from quick skim
More editing

--- 2017-01-17 backmatter.tex
@@
 \begin{acronym}[CERN]
+\acro{EM}[EM]{electromagnetic}
+\acro{QFT}[QFT]{quantum field theory}
+\acro{QCD}[QCD]{quantum chromodynamics}
+\acro{QED}[QED]{quantum electrodynamics}
+\acro{LEP}[LEP]{Large Electron-Positron}
+\acro{VBF}[VBF]{vector boson fusion}
 \acro{MC}[MC]{Monte Carlo}
+\acro{CKM}[CKM]{Cabibbo-Kobayashi-Maskawa}
 \acro{CMS}[CMS]{Compact Muon Solenoid}
-\acro{LHC}[LHC]{Large Hadron Colider}
+\acro{LHC}[LHC]{Large Hadron Collider}
 \acro{CERN}[CERN]{the European Organisation for Nuclear Research }
@@
 \acro{LS1}[LS1]{Long Shutdown 1}
-\acro{MSSM}[MSSM]{Minimal Supersymmetric standard model}
-\acro{SUSY}[SUSY]{Supersymmetry}
-\acro{2HDM}[2HDM]{Two Higgs Doublet Model}
-\acro{ECAL}[ECAL]{Electromagnetic calorimeter}
-\acro{HCAL}[HCAL]{Hadron calorimeter}
+\acro{MSSM}[MSSM]{minimal supersymmetric standard model}
+\acro{SM}[SM]{standard model}
+\acro{SUSY}[SUSY]{supersymmetry}
+\acro{2HDM}[2HDM]{two Higgs doublet model}
+\acro{ECAL}[ECAL]{electromagnetic calorimeter}
+\acro{HCAL}[HCAL]{hadron calorimeter}
 \acro{TIB}[TIB]{Tracker Inner Barrel}
@@
 \acro{EB}[EB]{ECAL Barrel}
-\acro{EE}[EE]{ECAL Endcaps}
+\acro{EE}[EE]{ECAL Endcap}
 \acro{HB}[HB]{Hadron Barrel Calorimeter}
@@
 \acro{HF}[HF]{Hadron Forward Calorimeter}
-\acro{BSM}[BSM]{Beyond the Standard Model}
+\acro{BSM}[BSM]{beyond the standard model}
 \acro{L1}[L1]{Level-1}
 \acro{HLT}[HLT]{High-level trigger}
-\acro{CSCs}[CSCs]{Cathode Strip Chambers}
-\acro{DT}[DT]{Drift Tube}
-\acro{RPCs}[RPCs]{Resistive Plate Chambers}
+\acro{CSC}[CSC]{Cathode Strip Chamber}
+\acro{DT}[DT]{Drift Tube chamber}
+\acro{RPC}[RPC]{Resistive Plate Chamber}
 \acro{DAQ}[DAQ]{Data Acquisition}
@@
 \acro{RF}[RF]{radio frequency}
-\acro{PF}[PF]{Particle Flow}
-\acro{BDTs}[BDTs]{Boosted Decision Trees}
+\acro{PF}[PF]{particle flow}
+\acro{BDT}[BDT]{boosted decision tree}
 \acro{KF}[KF]{Kalman Filter}
@@
 \acro{CSV}[CSV]{Combined Secondary Vertex}
-
+\acro{CL}[CL]{confidence level}
 \acro{IVF}[IVF]{Inclusive Vertex Finder}
@@
 \appendix
+\renewcommand{\chaptername}{Appendix}
 \chapter{\texorpdfstring{Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
@@
 indicates that the uncertainty is correlated between categories but uncorrelated between
-the different decay channels.
+the different decay channels. For brevity the backgrounds are denoted with shorthand notations.
+`ZTT' indicates the \Ztautau component. 'ZJ' is reserved for the \Zellell background
+in which the tau is faked by a jet. The \Zellell background in which the tau is faked
+by an electron or muon is indicated as 'ZL'. `W' indicates the \Wjets process. `TT' denotes
+the \ttbar background, with  `TTT' and `TTJ'
+indicating the \ttbar background with real hadronic taus and without real hadronic taus, respectively. 
+The di-boson and single-top backgrounds are denoted `VV', with
+`VVT' and `VVJ' indicating the di-boson plus single-top background with real hadronic taus
+and without real hadronic taus, respectively. The QCD multijet background is denoted `QCD'.
 \input{MSSM/UncOv}

### 2017-02-27 frontmatter.tex
More editing

@@
   %\thispagestyle{empty}
-The \ac{CMS} detector is a general-purpose detector located at the Large Hadron
+The Compact Muon Solenoid (CMS) detector is a general-purpose detector located at the Large Hadron
 Collider at CERN. It was designed to test the predictions of the standard model 
@@
 The analyses presented in this thesis are searches for neutral
-Higgs bosons with tau leptons in the final state, and use proton-proton collision data recorded
-by \acs{CMS} during 2012, 2015 and 2016. The searches are performed in the
-context of the \ac{MSSM}. One of the analyses, using $19.7\,\invfb$ collected
+Higgs bosons with tau leptons in the final state. These searches use proton-proton collision data recorded
+by CMS during 2012, 2015 and 2016. The searches are performed in the
+context of the minimal supersymmetric standard model (MSSM). One of the analyses, using $19.7\,\invfb$ 
+of data collected
 during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
-decaying into two $125\,\GeV$ \ac{MSSM} Higgs bosons with \ac{SM}-like properties,
+decaying into two $125\,\GeV$ Higgs bosons with standard model-like properties,
 with two b-quarks and two tau leptons in the final state. The other analyses use 
-$2.3\,\invfb$ collected during 2015 and $12.9\,\invfb$ collected during 2016, both
-at $\sqrt{s}=13\,\TeV$. These are searches for neutral \ac{MSSM}
-Higgs bosons in the mass range of $90\,\GeV$--$3.2\,\TeV$ directly decaying
+$2.3\,\invfb$ of data collected during 2015 and $12.9\,\invfb$ of data collected during 2016, both
+at $\sqrt{s}=13\,\TeV$. These are searches for neutral MSSM
+Higgs bosons in the mass range of \mbox{$90\,\GeV$--$3.2\,\TeV$} directly decaying
 into pairs of tau leptons. 
-No significant excess is observed in any of the searches. Upper limits at 95\% confidence 
-level are set on the cross section times branching ratio for the Higgs production process
-in consideration. In addition, limits are set in the \mA-\tanb~parameter space of 
-several \ac{MSSM} benchmark scenarios, and in the \cosba-\tanb~parameter space of an example
-of a two Higgs doublet model.
+No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
+level are set on the cross section times branching ratio for the production of Higgs bosons in the \ac{MSSM}.
+In addition, limits are set in the \mA-\tanb~parameter space of 
+several \ac{MSSM} benchmark scenarios, and in the \cosba-\tanb~parameter space of 
+a two Higgs doublet model.
 
@@
 was responsible for the statistical inference. This included
-the interpretation of the results in MSSM and two Higgs doublet model benchmark scenarios. The 
-work is included in Ref. \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
+the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
+work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
 I was responsible for all stages of the analysis, including the optimisation
 of object selection and event categorisation, as well as studies of background
-methods for three out of four channels presented in the final version of the analysis,
+methods for three out of four channels in the public result of the analysis,
 evaluation of systematic uncertainties in all four channels, and production of the statistical

### 2017-02-27 Hhh/Hhh.tex
Edit done

@@
 four-vector of the \PZ boson candidate with the four-vector of the \PHiggslight candidate as obtained by using the 
-\texttt{SVFit} algorithm. The expected and observed 95\% \ac{CL} upper limits, for
+\texttt{SVFit} algorithm. The expected and observed upper limits at the 95\% \ac{CL}, for
 all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}.
@@
 \includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_010-a.pdf}
-\caption[The 95\% confidence level expected and observed upper limits on the 
-\xsbr for the \AtoZhtolltautau process.]{The 95\% confidence level expected (dashed) and observed (solid)
-upper limits on the \xsbr for the \AtoZhtolltautau process.
+\caption[The expected and observed upper limits at the 95 \% CL on the 
+\xsbr for the \AtoZhtolltautau process.]{The expected (dashed) and observed (solid)
+upper limits at the 95\% \ac{CL} on the \xsbr for the \AtoZhtolltautau process.
 The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$
@@
 \acf{CL} $1-\alpha$. Upper limits at the LHC are generally
-quoted at 95\% \ac{CL}. %, therefore the upper limit on cross-section times branching ratio
+quoted at the 95\% \ac{CL}. %, therefore the upper limit on cross-section times branching ratio
 %for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
@@
 None of these distributions show hints of an excess of observed events above the background expectation. 
-The model-independent 95\% \ac{CL} expected and observed upper limits
+The model-independent expected and observed upper limits at the 95\% \ac{CL}
 on \xsbr are shown in 
@@
 \subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
-\caption[Expected and observed 95\% CL upper limits on 
-\xsbr for the \Htohhtobbtautau process.]{Expected and observed 95\% \ac{CL} upper limits on \xsbr  
+\caption[Expected and observed upper limits at the 95\% CL on 
+\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
 for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.
-(b) Shows the expected 95\% \ac{CL} upper limits on \xsbr for the \Htohhtobbtautau
+(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
 process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
@@
 \begin{center}
-\caption{Couplings in the type-II 2HDM}
+\caption{Couplings in the type-II 2HDM.}
 \begin{tabular}{@{}ll@{}}
@@
 The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
-shows the observed and expected exclusion at 95\% \ac{CL} for the \Htohh
+shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
 and \AtoZh analyses, overlaid on the \xsbr.
@@
 The expected (dashed line)
-and observed (solid line) exclusion contours at 95\% \ac{CL} are overlaid
+and observed (solid line) exclusion contours at the 95\% \ac{CL} are overlaid
 on the \xsbr of the searched-for process.
@@
 %2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
-%and observed (solid line) exclusion contours at 95\% confidence level are overlaid
+%and observed (solid line) exclusion contours at the 95\% confidence level are overlaid
 %on the cross--section of $gg\rightarrow \PHiggsps$ production
@@
 The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb~region
-in this model. The expected and observed 95\% \ac{CL} exclusion contours are overlaid 
+in this model. The expected and observed exclusion contours at the 95\% \ac{CL} are overlaid 
 on the \xsbr for this process in the low-\tanb~MSSM scenario in  

### 2017-02-27 MSSM/MSSM.tex
Edit done

@@
 \end{center}
-\caption[Distributions of \mTtot~inthe no b-tag and b-tag 
+\caption[Distributions of \mTtot~in the no b-tag and b-tag 
 categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
@@
 \begin{center}
-\caption{Correlations between nuisance parameters in the 2015 and 2016 analysis}
+\caption{Correlations between nuisance parameters in the 2015 and 2016 analyses.}
 {\footnotesize

### 2017-02-27 MSSM/UncOv.tex
Edit done

@@
 \begin{center}
-\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
-or background events in the $\mu \tau_{h}$ channel.} 
+\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \mutau channel]{\footnotesize Systematic uncertainties that affect the estimated number of signal
+or background events in the \mutau channel.} 
  {\tiny
@@
 \begin{center}
-\caption{\footnotesize Systematic uncertainties that affect the estimated number of signal
+\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \etau channel.]{\footnotesize Systematic uncertainties that affect the estimated number of signal
 or background events in the \etau channel.}
@@
 \caption{Systematic uncertainties that affect the estimated number of
-or background events in the $Z\rightarrow\mu\mu$ channel.}
+background events in the $\PZ\rightarrow\mu\mu$ channel.}
 {\scriptsize

### 2017-02-27 Objects/Objects.tex
More editing
Edit done

@@
 
-\section{\acl{PF}}
+\section{Particle flow}
 \label{sec:objects_pf}
@@
 \begin{center}
-\caption{Summary of hadronic tau decay modes, indicating the branching fraction, and intermediate resonances where relevant \cite{pdg-2014}.}
+\caption[Summary of hadronic tau decay modes.]{Summary of hadronic tau decay modes, indicating the branching fraction, and intermediate resonances where relevant \cite{pdg-2014}.}
 \begin{tabular}{@{}lll@{}}
@@
 \caption[Figures of the jet$\rightarrow$\Pgth fake rate in QCD MC events
-versus $\Pgt_{h}$ identification efficiency for \htotautau MC events, the real
-$\Pgt_{h}$ identification efficiecny for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
+versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
+$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
 working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
-efficiency for simulated \htotautau events, comparing the MVA-based isolation discriminator in red with the cut-based 
+efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, comparing the MVA-based isolation discriminator in red with the cut-based 
 isolation discriminator in pink. Tighter working points give lower hadronic tau identification

### 2017-02-27 Theory/Theory.tex
Fixing another typo
Edit done

@@
 table \ref{tab:theory_fermions}.
+%Symmetries of the Lagrangian describing a physical system lead
+%to conserved quantities, as shown by Noether's theorem \cite{noethersthm}.
+%This is and important concept for the description of particle interactions
+%under different forces: invariance (symmetry) under a certain 
+%transformation group is imposed on 
+%the Lagrangians describing the fundamental forces. This is brought
+%about as local gauge invariance, where the Lagrangians 
+%are required to be invariant under a local phase transformation
+%plus a gauge transformation. The local phase transformation
+%might introduce additional derivatives of potentials, taken care of by gauge transf.
+
+The symmetries governing the forces in the \ac{SM} imply the presence
+of spin-1 bosons which carry the forces. The gluon (\Pgluon) mediates 
+the strong nuclear force, while the \ac{EM} force is mediated
+by the photon (\Pphoton), and the weak force by the $\PW^{\pm}$ and \PZ bosons.
+
 \begin{table}[htp]
 \begin{center}
-\caption{The fundamental fermions}
+\caption{The fundamental fermions.}
 \begin{tabular}{@{}llll@{}}
 \toprule
- & \textbf{$1^{\text{st}}$ generation} & \textbf{$2^{\text{nd}}$ generation} & \textbf{$3^{\text{d}}$ generation}\\
+ & \textbf{$1^{\text{st}}$ generation} & \textbf{$2^{\text{nd}}$ generation} & \textbf{$3^{\text{rd}}$ generation}\\
 \midrule
@@
 \end{table}
-%Symmetries of the Lagrangian describing a physical system lead
-%to conserved quantities, as shown by Noether's theorem \cite{noethersthm}.
-%This is and important concept for the description of particle interactions
-%under different forces: invariance (symmetry) under a certain 
-%transformation group is imposed on 
-%the Lagrangians describing the fundamental forces. This is brought
-%about as local gauge invariance, where the Lagrangians 
-%are required to be invariant under a local phase transformation
-%plus a gauge transformation. The local phase transformation
-%might introduce additional derivatives of potentials, taken care of by gauge transf.
-
-The symmetries governing the forces in the \ac{SM} imply the presence
-of spin-1 bosons which carry the forces. The gluon (\Pgluon) mediates 
-the strong nuclear force, while the \ac{EM} force is mediated
-by the photon (\Pphoton), and the weak force by the $\PW^{\pm}$ and \PZ bosons.
 
@@
 %\end{equation}
-
 The SU(2) part of the symmetry is built from the weak
@@
 \end{equation}
-
-The associated gauge fields are the three weak isospin fields $W_{\mu}^{i}$ and the
-weak hypercharge field $B_{\mu}$. These four fields mix to form the physical \Pphoton,
+The associated gauge fields are the three weak isospin fields $\PW_{\mu}^{i}$ and the
+weak hypercharge field $\text{B}_{\mu}$. These four fields mix to form the physical \Pphoton,
 \PZ and $\PW^{\pm}$ states as
@@
 \begin{equation}\label{eqn:ewk_propagators_phot}
-\text{A}_{\mu} &= \PW_{\mu}^3\sin{\theta_W} + B_{\mu}\cos{\theta_W},
+\text{A}_{\mu} &= \PW_{\mu}^3\sin{\theta_W} + \text{B}_{\mu}\cos{\theta_W},
 \end{equation}
@@
 In these equations $\text{A}_{\mu}$ is the photon field and $\PZ_{\mu}$ the \PZ field.
-The weak mixing angle $\theta_W$ is related to the weak (g) and electromagnetic (g')
+The weak mixing angle $\theta_W$ is related to the weak ($g$) and electromagnetic ($g'$)
 coupling constants as
@@
 \begin{split}
-&g\sin{\theta_W} = g'\cos{\theta_W}\\
-&\Rightarrow \sin{\theta_W} = \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}
+g\sin{\theta_W} &= g'\cos{\theta_W}\\
+\Rightarrow \sin{\theta_W} &= \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}.
 \end{split}
 \end{equation}
-
 Neutral weak-current interactions were discovered in 1973 at the Gargamelle
 bubble chamber experiment at \acs{CERN} \cite{gargamelle}. This discovery was 
-followed 10 years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
-and UA2 Collaborations at \acs{CERN}, confirming the predicitions from electroweak unification.
+followed ten years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
+and UA2 Collaborations at \acs{CERN}, confirming the predictions from electroweak unification.
 It should be noted that the weak force only couples to the left-handed parts
@@
 A similar problem exists for fermions, as they are known to have mass but again the introduction
-of mass terms would break gauge invariance of the Lagrangian. 
+of mass terms would break the gauge invariance of the Lagrangian. 
 To be able to introduce mass terms electroweak symmetry must be broken. In the 
@@
 Denoting the 
-remaining, broken, generators as $\vec{b}$, and parameterising the field as an expansion around the
+remaining, broken, generators as $\vec{b}$ and parameterising the field as an expansion around the
 vacuum state gives
@@
 $m_{\PW} = \frac{gv}{2}$ and $m_{\PZ} = \frac{1}{2}v\sqrt{g^2+g'^2}$. Using equation \ref{eqn:thetaw} 
-we can see that these two masses are
+it can be seen that these two masses are
 related as $\frac{m_{\PW}}{m_{\PZ}} = \cos{\theta_W}$. The remaining mass term is for the Higgs field \PHiggs, 
 $M_{\PHiggs} = \sqrt{2\mu_{\text{SM}}^2}$. It is denoted $M_{\PHiggs}$ to avoid confusion with the mass of the heavy scalar
-\PHiggs boson in the \ac{MSSM} $m_{\PHiggs}$, which will be introduced in section \ref{sec:theory_MSSM_H}.
+\PHiggs boson in the \ac{MSSM}, $m_{\PHiggs}$, which will be introduced in section \ref{sec:theory_MSSM_H}.
 Note that the photon does not acquire a mass.
@@
 providing a lower search limit. Subsequent searches at the 
-Tevatron also did not lead to discovery of the Higgs boson, but did exclude 
-an additional mass range of $140$--$186\,\GeV$ at 95\% \ac{CL} \cite{TEV-Higgs}.
+Tevatron also did not lead to the discovery of the Higgs boson, but did exclude 
+an additional mass range of $140$--$186\,\GeV$ at the 95\% \ac{CL} \cite{TEV-Higgs}.
 
@@
 increased the confidence in the compatibility of this new state with the \ac{SM} Higgs boson. 
-The most precise measurement of the mass of the Higgs boson, $M_{\PHiggs} = 125.09 \pm 0.21 \text{ (stat) } \pm 0.11 \text{ (syst)}\,\GeV$, 
+The most precise measurement of the mass of the Higgs boson, \mbox{$M_{\PHiggs} = 125.09 \pm 0.21 \text{ (stat)} \pm 0.11 \text{ (syst)}\,\GeV$}, 
 comes from the ATLAS and CMS combined
 mass measurement using the full dataset collected up to the end of 2012 \cite{MassComb}.
-The combined ATLAS and CMS production and decay rate measurements, also using the full dataset collected up to the end of 2012,
+The combined ATLAS and CMS production and decay rate measurements, using the same dataset,
 show very good agreement with the \ac{SM} predictions \cite{CouplComb}. In addition, 
-the $\PHiggs \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination. During the 2010--2012
-LHC running period searches by the ATLAS and CMS Collaborations resulted in observed 
+the $\PHiggs \rightarrow \Pgt\Pgt$ decay was observed with a significance of 5.5$\sigma$ through this combination. 
+The individual searches by the ATLAS and CMS Collaborations resulted in observed 
 significances of $4.5\sigma$ \cite{ATLAS-tautau} and $3.2\sigma$ \cite{SMHtautauCMS} for this process, respectively. 
@@
 \begin{center}
-\subfloat[\ac{SM} \PHiggs production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
-\subfloat[\ac{SM} \PHiggs branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
+\subfloat[\ac{SM} Higgs boson production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
+\subfloat[\ac{SM} Higgs boson branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
 \end{center}
@@
 
-The branching ratios of the \ac{SM} Higgs boson in figure \ref{fig:theory_smhxsbr}b show that
+Figure \ref{fig:theory_smhxsbr}b shows that
 the branching ratios of
@@
 channels, are smaller than the branching ratios into many other final states.
-These two channels are thus not sensitive as a result of the size of their branching ratio, but
+These two channels are thus not sensitive as a result of the size of their branching ratios, but
 rather due to the small backgrounds in these analyses as well as the excellent photon and lepton energy resolution the detectors provide.
 
-Since the re-start of the LHC in 2015, \ac{SM} Higgs boson measurements, and searches for the 
+Since the restart of the LHC in 2015, \ac{SM} Higgs boson measurements, and searches for the 
 \ac{SM} Higgs boson in decay channels not previously established, have 
-already been performed. The decay in to $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
-as has the decay in to $\PZ\PZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
+already been performed. The decay into $\gamma\gamma$ has been re-established \cite{CMSHgamgam2016,ATLASHgamgam2016},
+as has the decay into $\PZ\PZ\rightarrow 4\ell$ \cite{CMSHZZ2016,ATLASHZZ2016}, and measurements
 of $\PHiggs\rightarrow \PW\PW$ have been performed \cite{CMSHWW2016,ATLASHWW2016}. Establishing evidence for the decay of 
@@
 \begin{split}
-&M_{\PHiggs_{\text{SM}}}^2  = (M_H^2)_0 + \Delta M_{\PHiggs}^2,\\
+&M_{\PHiggs_{\text{SM}}}^2  = (M_{\PHiggs})_0^2 + \Delta M_{\PHiggs}^2,\\
 &\Delta M_{\PHiggs}^2 \sim \mathcal{O}(\Lambda^2).
@@
 the Planck scale the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
-if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs}^2)_0$.
+if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs})_0^2$.
 
@@
 allows for the cancellation of $\Delta M_{\PHiggs}^2$ terms. The cancellation
-would be exact if \ac{SUSY} was unbroken, but because this is not the case the
+would be exact if \ac{SUSY} were unbroken, but because this is not the case the
 cancellation is not complete. Therefore if the \ac{SUSY} breaking scale, where
@@
 
-\subsection{The Higgs sector of the \ac{MSSM}}
+\subsection{The Higgs sector of the \acs{MSSM}}
 \label{sec:theory_MSSM_H}
@@
 \begin{equation}\label{mssm_chargedhigss_mass}
-m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2,
+m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2.
 \end{equation}
@@
 given in table \ref{tab:mssm_couplings} \cite{YR4}.
-
 \begin{table}[htp]
@@
 \begin{center}
-\caption[Tree-level couplings in the MSSM, as multiplicative factors with respect to the couplings of the Higgs boson in the SM]{Tree-level couplings in the MSSM, as multiplicative factors with
+\caption[Tree-level couplings in the MSSM, as multiplicative factors with respect to the couplings of the Higgs boson in the SM.]{Tree-level couplings in the MSSM, as multiplicative factors with
 respect to the couplings of the Higgs boson in the \ac{SM}.}
@@
 In the \textit{decoupling limit}, when $m_{\PHiggsps} \gg m_{\PZ}$ and $\cos{(\beta-\alpha)}$ tends
-to 0, the mixing
+to zero, the mixing
 angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
@@
 \caption[Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario]{Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario,
-at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $b\bar{b}$ (red) 
+at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $\Pbottom\APbottom$ (red) 
 and $\mu\mu$ (yellow) is enhanced at high \tanb, while the branching ratio into 
-WW (grey) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
+WW (brown) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
 \label{fig:mssm_brtautau}
@@
 \begin{center}
-\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.pdf}}
-\subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
+\subfloat[Gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.pdf}}
+\subfloat[b-Associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
 \end{center}
 \caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
-production of neutral Higgs bosons in the MSSM. The squarks in the gluon fusion production loop do not contribute to production of the \PHiggsps boson.}
+production of neutral Higgs bosons in the MSSM. The squarks in the gluon fusion production loop do not contribute to the production of the \PHiggsps boson.}
 \label{fig:production_mssm}
@@
 
-The behaviour of the \ac{2HDM} couplings in the \textit{alignment} limit,
+The behaviour of the \ac{2HDM} couplings in the \textit{alignment limit},
 where $\cos{(\beta-\alpha)} = 0$, differs from that of the \ac{MSSM} couplings.
@@
 
-The inclusive cross section times branching ratio (\xsbr) for production of a \PHiggs boson 
+The inclusive cross section times branching ratio (\xsbr) for production of an \PHiggs boson 
 and decays into various final states is shown in figure \ref{fig:2hdm_Hxsbr}a for an 
@@
 \begin{equation}
-M_1 = \frac{5}{3}M_2\tan{\theta_w}^2.
+M_1 = \frac{5}{3}M_2\tan{\theta_W}^2.
 \end{equation}
@@
 in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
-the b-associated production cross-section is larger at high \tanb.}
+the b-associated production cross section is larger at high \tanb. These values are based on the
+calculations in reference \cite{YR3}.}
 \label{fig:mhmodp_xs}
@@
 \end{center}
-\caption[Branching ratio of the \PHiggs and \PHiggsps bosons into $\tau\tau$.]{Branching ratio of (a) the \PHiggs boson and (b) the \PHiggsps boson into $\tau\tau$. The branching
-ratios into $\tau\tau$ are enhanced at high \tanb.}
+\caption[Branching ratios of the \PHiggs and \PHiggsps bosons into $\tau\tau$.]{Branching ratios of (a) the \PHiggs boson and (b) the \PHiggsps boson into $\tau\tau$. The branching
+ratios into $\tau\tau$ are enhanced at high \tanb. These values are based on the
+calculations in reference \cite{YR3}.}
 \label{fig:mhmodp_br}
@@
 be compatible with $125\,\GeV$ if the light Higgs boson mass lies within 
-$\pm 3\,\GeV$ around $125\,\GeV$. This mass window
+$\pm 3\,\GeV$ of $125\,\GeV$. This mass window
 corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
@@
 $125\,\GeV$. However, at low values of \tanb~this is not the case.
-The mass of the light Higgs
-boson in the $m_{\PHiggslight}^{\text{mod}+}$ scenario is shown in 
-figure \ref{fig:mhmodp_mh}a, illustrating that the mass 
-is not within $\pm 3\,\GeV$ of $125\,\GeV$ at low \tanb. The low \tanb~regime can be re-opened
+This is illustrated in figure \ref{fig:mhmodp_mh}a, where the mass of the light Higgs
+boson in the $m_{\PHiggslight}^{\text{mod}+}$ scenario is shown.
+The low \tanb~regime can be re-opened
 if $M_{\text{SUSY}}$ is allowed to be greater than $3\,\TeV$ \cite{MSSM-reopen}. 
@@
 %\end{figure}
-
 %where the ±3 GeV variation corresponds to a rough estimate of the theoretical uncertainty of the MSSM prediction for mh, due to the unknown effect of higher-order correction
@@
 \tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
-of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
+of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low-\tanb~scenario. The white areas
 indicate masses lower than $122\,\GeV$. The figures show that
@@
 part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
-the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere.}
+the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere. These values are based on the calculations in reference \cite{YR3}.}
 \label{fig:mhmodp_mh}
@@
 \begin{split}
-&m^2_{\PHiggs} = \frac{(m_{\PHiggsps}^2+m_{\PZ}^2-m_{\PHiggslight}^2)(m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggsps}^2m_{\PZ}^2\cos{2\beta}^2}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2},\\
-&\tan{\alpha} = -\frac{(m_{\PZ}^2+m_{\PHiggsps}^2)\cos{\beta}\sin{\beta}}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2}.
+m^2_{\PHiggs} &= \frac{(m_{\PHiggsps}^2+m_{\PZ}^2-m_{\PHiggslight}^2)(m_{\PZ}^2\text{cos}^2\beta+m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta)}{m_{\PZ}^2\text{cos}^2\beta+m_{\PHiggsps}^2\text{sin}^2\beta-m_{\PHiggslight}^2},\\
+\tan{\alpha} &= -\frac{(m_{\PZ}^2+m_{\PHiggsps}^2)\cos{\beta}\sin{\beta}}{m_{\PZ}^2\text{cos}^2\beta+m_{\PHiggsps}^2\text{sin}^2\beta-m_{\PHiggslight}^2}.
 \end{split}
@@
 \label{eqn:hmssm_Hhh}
-\lambda_{\PHiggs\PHiggslight\PHiggslight} = \lambda_{\PHiggs\PHiggslight\PHiggslight,\text{tree}} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_{\PZ}^2\sin{\beta}}\cos{\alpha}^2,
+\lambda_{\PHiggs\PHiggslight\PHiggslight} = \lambda_{\PHiggs\PHiggslight\PHiggslight,\text{tree}} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_{\PZ}^2\sin{\beta}}\text{cos}^2\alpha,
 \end{equation}
@@
 is only well defined in regions where the denominator in equations
-\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggslight}^2$, is non-zero. 
+\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\text{cos}^2\beta+m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggslight}^2$, is non-zero. 
 This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
 a minimum accessible \mA~of around $151\,\GeV$ for \tanb=1. In addition, the scenario
-can be formulated, but is not strictly valid, for values of \tanb~upwards of 10 \cite{CMS-PAS-HIG-16-007}.
+can be formulated, but is not strictly valid, for values of \tanb~upwards of ten \cite{CMS-PAS-HIG-16-007}.
 The reason for this is that direct higher order SUSY corrections to down-type
@@
 
-The branching ratios of \PHiggs and \PHiggsps into $\tau\tau$ follow a similar
+The branching ratios of the \PHiggs and \PHiggsps bosons into $\tau\tau$ follow a similar
 pattern as in other MSSM scenarios, with large branching ratios at high \tanb.
@@
 bosons were performed. Figure \ref{fig:bsm_summary} shows the interpetations
-of different searches performed with the \acs{CMS} detector up to the end of 2012
-in the $m_{\PHiggslight}^{\text{mod+}}$ (figure \ref{fig:bsm_summary}a)
-and hMSSM scenarios (figure \ref{fig:bsm_summary}b). The direct search for heavier Higgs bosons decaying into pairs
-of tau leptons (shown in dark blue) sets the most stringent limits at high \tanb, with searches for 
+of different searches performed with the \acs{CMS} detector during this period
+in the $m_{\PHiggslight}^{\text{mod+}}$ (figure~\ref{fig:bsm_summary}a)
+and hMSSM (figure~\ref{fig:bsm_summary}b) scenarios. The direct search for heavier Higgs bosons decaying into pairs
+of tau leptons sets the most stringent limits at high \tanb, with searches for 
 heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high-\tanb~region.
@@
 
-Since the re-start of the \acs{LHC} in 2015 searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
+Since the restart of the \acs{LHC} in 2015 searches for \AHtotautau, setting more stringent limits than those shown in figure \ref{fig:bsm_summary},
 have been performed with the \acs{CMS} detector. The results of these searches will be presented in chapter \ref{chap:mssm}. 
@@
 \end{center}
-\caption[Summary of the interpretations of BSM Higgs boson searches using data up to the end of 2012 at CMS in the $m_{\PHiggslight}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of \ac{BSM} Higgs boson searches at \acs{CMS} using data
+\caption[Summary of the interpretations of BSM Higgs boson searches using data up to the end of 2012 at CMS in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM scenario.]{Summary of the interpretations of \ac{BSM} Higgs boson searches at \acs{CMS} using data
 collected up to the end of 2012 in (a) the $m_{\PHiggslight}^{\text{mod+}}$ and (b) the

### 2017-02-27 backmatter.tex
Edit done

@@
 \renewcommand{\chaptername}{Appendix}
-\chapter{\texorpdfstring{Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
+\chapter{\texorpdfstring{Systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
 \label{appendix:uncerts}

### 2017-02-27 frontmatter.tex
Edit done

@@
 No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
-level are set on the cross section times branching ratio for the production of Higgs bosons in the \ac{MSSM}.
+level are set on the cross section times branching ratio for the production of Higgs bosons in the MSSM.
 In addition, limits are set in the \mA-\tanb~parameter space of 
-several \ac{MSSM} benchmark scenarios, and in the \cosba-\tanb~parameter space of 
+several MSSM benchmark scenarios, and in the \cosba-\tanb~parameter space of 
 a two Higgs doublet model.
@@
 \tableofcontents
-%\listoffigures
-%\listoftables
+\listoffigures
+\listoftables
 

### 2017-02-28 Hhh/Hhh.tex
A few more minor changes before sending off to supervisors

@@
 The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
-expectations \cite{CMS-HIG-14-034}.}
+probability intervals on the expected limit \cite{CMS-HIG-14-034}.}
 \label{fig:AZhUpperLimits}
@@
 \xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
-for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.
+for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
+probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
 (b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
@@
 The dashed black line indicates the expected exclusion, with the grey bands showing
-the $\pm 1\sigma$ and $\pm2\sigma$ expected exclusion \cite{CMS-HIG-14-034}. The area
+the $\pm 1\sigma$ and $\pm2\sigma$ probability intervals on the expected exclusion \cite{CMS-HIG-14-034}. The area
 bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$

### 2017-02-28 MSSM/MSSM.tex
A few more minor changes before sending off to supervisors

@@
 \begin{split}
-\Delta(\text{NLL})_{68\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) = 1.14, ~\\
-\Delta(\text{NLL})_{95\%} = \text{NLL}(\text{best fit}) - \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) = 3.00.
+\Delta(\text{NLL})_{68\%} &= \text{NLL}(\mu_{\Pg\Pg\phi}^{68\%},\mu_{\Pbottom\Pbottom\phi}^{68\%}) - \text{NLL}(\text{best fit}) = 1.14, ~\\
+\Delta(\text{NLL})_{95\%} &= \text{NLL}(\mu_{\Pg\Pg\phi}^{95\%},\mu_{\Pbottom\Pbottom\phi}^{95\%}) - \text{NLL}(\text{best fit}) = 3.00.
 \end{split}
@@
 expected exclusion. The light and dark grey bands indicate
-the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion in the \ac{SM} hypothesis.
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected exclusion under the \ac{SM} hypothesis.
 The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure

### 2017-03-03 Conclusion/Conclusion.tex
Own final read through

@@
 as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
-is very low in the high-\mA and low-tanb~corner. This region can be accessed 
+is very low in the high-\mA~and low-tanb~corner. This region can be accessed 
 via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which

### 2017-03-03 Detector/Detector.tex
Own final read through

@@
 Franco-Swiss border near Geneva. It
-is installed in the tunnel that previously hosted the Large Electron Positron accelerator \cite{lep-design}
+is installed in the tunnel that previously hosted the \acf{LEP} accelerator \cite{lep-design}
 that was operated by \acf{CERN} between 1989 and 2000.
@@
 switched off while collisions are ongoing. In 2012 the data-taking 
-efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%
+efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%.
 From all of the data that is recorded only a subset is used for analysis. Data is 
@@
 inside the experiment. The $y$ axis points vertically upward, the $x$ axis
-points radially inward toward the centre of the \ac{LHC} ring. The $z$ axis
+points radially inward toward the centre of the \ac{LHC} ring. The \mbox{$z$ axis}
 points along the beam direction. As such the transverse momentum and energy, 
@@
 and the polar angle $\theta$ is measured with respect to the $z$ axis. A coordinate
-more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$.%Look up: differences in eta are lorentz-invariant
+more frequently used than the polar angle is the pseudorapidity $\eta = -\ln{[\tan{\frac{\theta}{2}}]}$. %Look up: differences in eta are lorentz-invariant
 Distances in the $\eta$-$\phi$ plane are given as $\Delta R = \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.
@@
 around $25\,\cm$ long and $122$--$183\,\micron$ 
-wide providing 6 measurements of $r$ and $\phi$, with a resolution
+wide providing six measurements of $r$ and $\phi$, with a resolution
 of $35$--$53\,\micron$. Beyond the $z$ range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
@@
 Some of the strip modules in the detector carry a second strip detector module mounted back-to-back with a stereo angle %FIXME WTF?
-of $100\,$mrad, in order to provide measurements of the $z$ coordinate in the barrel. This is achieved with a resolution of $230$--$530\,\micron$.
+of $100\,$mrad, in order to provide measurements of the \mbox{$z$ coordinate} in the barrel. This is achieved with a resolution of $230$--$530\,\micron$.
 
@@
 good energy resolution, is highly granular and has a fast response, all qualities 
-which are needed to be able to detect $\PHiggslight\rightarrow \Pphoton\Pphoton$ decays.
+which are needed to be able to detect $\PHiggs\rightarrow \Pphoton\Pphoton$ decays.
 
@@
 and the amplification of the photodetectors, are temperature dependent.
-This nominal operating temperature, is ensured by 
+This nominal operating temperature is ensured by 
 supplying the detector with water at the same temperature.
@@
 As in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
-map on the granularity of the tiles in the \ac{HB}, and are read out via the same mechanism. %by feeding the light
+map the granularity of the tiles in the \ac{HB}, and are read out via the same mechanism. %by feeding the light
 %to a hybrid photodiode via wavelength-shifting fibres.
@@
 resolution are key to the success of the experiment, as muons are
-very important for the detection of $\PHiggslight\rightarrow \PZ\PZ \rightarrow 4\ell$ decays. In addition to that,
+very important for the detection of $\PHiggs\rightarrow \PZ\PZ \rightarrow 4\ell$ decays. In addition to that,
 muons appear in the final states of many of the \ac{BSM} signatures the experiment is searching for.
@@
 Anode wires between the cathode planes
-run along the $\phi$ direction and provide a measurement of
+run along the \mbox{$\phi$ direction} and provide a measurement of
 $\eta$. The resolution of the $r$--$\phi$ measurement is $40$--$120\,\micron$ \cite{cms-muon-7tev}.
@@
 
-To obtain precise muon momentum resolution information from 
+To obtain precise muon momentum resolution, information from 
 the tracker hits has to be combined with measurements in the
@@
 
-The trigger system consists of two stages: the \ac{L1} trigger and the \ac{HLT}. which only makes use of
+The trigger system consists of two stages: the \ac{L1} trigger and the \ac{HLT}. 
 The \ac{L1} trigger only makes use of front-end electronics and reduces the event rate 

### 2017-03-03 Hhh/Hhh.tex
Own final read through

@@
 In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
-a pair of b-jets and the other decaying to a pair of tau leptons is discussed. In this analysis, which 
+a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
 uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
@@
 of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
-of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner \htotautau final state.
+of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.
 
@@
 After applying the \mT~selection, events are divided into three categories to maximise
-sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), 2jet-1tag 
-(at least two jets, exactly one of which is b-tagged), 2jet-2tag (at least two jets, at least two of which are b-tagged).
+sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
+(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
 Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
@@
 \end{center}
-\caption[Reconstruced di-tau invariant mass and di-jet invariant mass in
-the 2jet-2tag category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the 2jet-2tag category of the \mutau
+\caption[Reconstructed di-tau invariant mass and di-jet invariant mass in
+the \mbox{2jet-2tag} category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the \mbox{2jet-2tag} category of the \mutau
 channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
@@
 \begin{align}\label{eqn:promotedemote}
-&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
-&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
+P(\text{demote}) &= 1 - \text{SF} \text{  for SF < 1 }  \notag \\
+P(\text{promote}) &= \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
 \end{align}
@@
 kinematic fit mass for \ttbar events is shown in figure 
-\ref{fig:kinfitvsmjj}b. From this figure we can see that the mass distribution for
+\ref{fig:kinfitvsmjj}b. This figure shows that the mass distribution for
 background events is less affected by the kinematic fit, although due to the
@@
 Contributions from other backgrounds are subtracted 
-from the data in this region, and a high-\mT~to low-\mT~extrapolation
+from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
  factor is determined from the \Wjets simulation.
@@
 in the 2jet-1tag and 2jet-2tag categories is relaxed from the medium to the loose 
-working point for the purposes of shape estimation.
+working point for the purpose of shape estimation.
 \subsection{QCD multijet}
@@
 \item Di-boson and single top: The combined uncertainty in the di-boson and single-top cross sections is 15\% \cite{8TeVdib,8TeVst}.
-\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region.
+\item \Wjets: As the \Wjets yield is estimated from a high-\mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region.
 The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.
@@
 values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
-as discussed in section \ref{sec:hhh_uncs}. The functional form of the probability density function
+as discussed in section~\ref{sec:hhh_uncs}. The functional form of the probability density function
 depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
@@
 Shape uncertainties are accounted for using a vertical template morphing
-technique \cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
+technique~\cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
 templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
@@
 \xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
-for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
+for the \mbox{\Htohhtobbtautau} process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
 probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
@@
 For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.
-
 The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
@@
 
+The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
+shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
+and \AtoZh analyses, overlaid on the \xsbr.
+The exclusion contours have some interesting features, most of which can be explained by the couplings
+in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
+of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
 \begin{table}[htp]
@@
 \end{table}
-
-The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
-shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
-and \AtoZh analyses, overlaid on the \xsbr.
-The exclusion contours have some interesting features, most of which can be explained by the couplings
-in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
-of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
 which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
@@
 
-The combined interpretation of both analyses in this model is presented figure 
+The combined interpretation of both analyses in this model is presented in figure 
 \ref{fig:HhhAZhMSSM2HDM}b.
@@
 of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
-described for the figure \ref{fig:HhhAndAZhlowtanb}b are also visible in this figure. In a small region of phase
+described for figure \ref{fig:HhhAndAZhlowtanb}b are also visible in this figure. In a small region of phase
 space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with $125\pm3\,\GeV$.
@@
 interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
-(b) in the low-\tanb~MSSM scenario. The shaded blue area bounded by
+(b) in the low-\tanb~MSSM scenario. The blue shaded area bounded by
 the solid black line indicates the observed excluded region at 95\% \ac{CL}.

### 2017-03-03 MSSM/MSSM.tex
Own final read through

@@
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
-\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
-%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
-%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
-\end{center}
-\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
-production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
-working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi\rightarrow\Pgt\Pgt$ process,
-as a function of the tau isolation working point (from very loose to very very tight) and
-of the \mT~selection from $\mTm<20\,\GeV$ to $\mTm<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
-for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
-hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
-\label{fig:mssm_selection_mt_taumt}
-\end{figure}
-~
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
-\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
-\end{center}
-\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
-processes
-in the
-\mutau channel for an increasingly looser \mT~selection and tau isolation
-working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
-(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
-at the tight working point and $\mTm<30\,\GeV$ in green, the medium working point and $\mTm<40\,\GeV$ in red,
-the loose working point and $\mTm<50\,\GeV$ in blue and the very loose working point and $\mTm<60\,\GeV$ in black. Loosening
-the tau isolation working point and \mT~selection improves the limits at higher mass and
-degrades them at low mass.}
-\label{fig:mssm_gradcuts_mt}
-\end{figure}
-
 These figures show that looser selections are preferred for higher masses. This behaviour can be
@@
 \begin{center}
+\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
+\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
+%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
+%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
+\end{center}
+\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
+production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
+working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi\rightarrow\Pgt\Pgt$ process,
+as a function of the tau isolation working point (from very loose to very very tight) and
+of the \mT~selection from $\mTm<20\,\GeV$ to $\mTm<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
+for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
+hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
+\label{fig:mssm_selection_mt_taumt}
+\end{figure}
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
+\end{center}
+\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
+processes
+in the
+\mutau channel for an increasingly looser \mT~selection and tau isolation
+working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
+(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
+at the tight working point and $\mTm<30\,\GeV$ in green, the medium working point and $\mTm<40\,\GeV$ in red,
+the loose working point and $\mTm<50\,\GeV$ in blue and the very loose working point and $\mTm<60\,\GeV$ in black. Loosening
+the tau isolation working point and \mT~selection improves the limits at higher mass and
+degrades them at low mass.}
+\label{fig:mssm_gradcuts_mt}
+\end{figure}
+\clearpage
+\begin{figure}[h!]
+\begin{center}
 \subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
@@
 \label{sec:mssm_eventsel_et}
-For selection of events in the \etau channel, the first step is
+For the selection of events in the \etau channel, the first step is
 a trigger that only requires an electron at \ac{L1}. Loose ID and isolation
@@
 electron and hadronically decaying tau, which are separated by $\Delta R > 0.5$.
-The minimum electron is required to have $\pTm >26\,\GeV$ and $|\eta| < 2.1$. %due to trigger conditions
+The electron is required to have $\pTm >26\,\GeV$ and $|\eta| < 2.1$. %due to trigger conditions
 The impact parameters are required to satisfy
@@
 \end{figure}
+\clearpage
 \begin{figure}[h!]
@@
 The tight working point of the isolation discriminator is chosen such that
-the channel is near-optimal at high mass, while not losing too much sensitivity in the low to intermediate mass range.
+the selection is near-optimal at high mass, while not losing too much sensitivity in the low to intermediate mass range.
 This is illustrated in figure \ref{fig:mssm_tauid_tt}a for the $\Pg\Pg\phi$ process and in figure \ref{fig:mssm_tauid_tt}b for the $\Pbottom\Pbottom\phi$ process.
@@
 in the \tautau channel, using the 
-medium (green), tight (red) and very tight working point of the tau isolation discriminator.
+medium (green), tight (red) and very tight (blue) working point of the tau isolation discriminator.
 The pattern is similar to that in the \etau and \mutau channels, with looser selections preferred at high
@@
 D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
-\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
-\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
+\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
+\text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
 \end{align}
@@
 \end{figure}
-~\clearpage
+
 \subsection{Categorisation}
@@
 m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
-(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2},
+(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}\,,
 \end{equation}
@@
 \begin{equation}\label{eqn:mttot_12}
-m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}.
+m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}\,.
 \end{equation}
@@
 of the \emu channel, for \ttbar and b-associated signal.]{Total transverse mass distributions in (a) the no b-tag category of the \tautau
-channel, for QCD and gluon fusion signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$ overlaid and (b) in the b-tag
+channel, for QCD and gluon fusion signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$ and (b) in the b-tag
 category of the \emu channel, for \ttbar and b-associated signal at $400\,\GeV$, $1\,\TeV$ and $2\,\TeV$. 
@@
 and isolation efficiency is measured using a tag-and-probe method
-making use of $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
+making use of \mbox{$\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$} events.
 \subsubsection*{Trigger efficiency}
@@
 \begin{split}
-\epsilon_{\text{data}}  = \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele12}) + \epsilon_{\text{data}}(\text{Mu8})\cdot\epsilon_{\text{data}}(\text{Ele23})~\\ - \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele23}).
+\epsilon_{\text{Data}}  = \epsilon_{\text{Data}}(\text{Mu23})\cdot\epsilon_{\text{Data}}(\text{Ele12}) + \epsilon_{\text{Data}}(\text{Mu8})\cdot\epsilon_{\text{Data}}(\text{Ele23})~\\ - \epsilon_{\text{Data}}(\text{Mu23})\cdot\epsilon_{\text{Data}}(\text{Ele23}).
 \end{split}
@@
 \caption[The \mTtot~distribution in the \ttbar
-enriched control region, with and without applying top quark \pT~reweighting.]{The \mTtot~distribution in the \ttbar enriched control region \MET~$>80\,\GeV$ and $D_{\zeta}<-20\,\GeV$ in the \emu channel,
+enriched control region, with and without applying top quark \pT~reweighting.]{The \mTtot~distribution in the \ttbar enriched control region \MET~$>80\,\GeV$ and \mbox{$D_{\zeta}<-20\,\GeV$} in the \emu channel,
 (a) without applying the top quark \pT~reweighting and (b) with the top quark \pT~reweighting.
@@
 \caption[The mis-modelling in the di-lepton \pT~distribution as observed
-in \Zmm events, and the impact of applying the Drell-Yan shape reweighting
+in \mbox{\Zmm} events, and the impact of applying the Drell-Yan shape reweighting
 on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mis-modelling in the di-lepton \pT~distribution as observed
@@
 simulation.
-For the \mutau and \etau channels, events from these samples 
+For the \mutau and \etau channels, events
 in which the reconstructed hadronic tau is matched to 
@@
 that do not satisfy the generator matching requirements are considered
-as the much smaller \Zll background.
+as the much smaller \Zellell background.
 %To correct and constrain the \Ztautau normalisation in the
@@
 \end{center}
-\caption{Distribution of the transverse mass \mT~in the \mutau channel, indicating
+\caption[Distribution of the transverse mass \mT~in the \mutau channel, indicating the signal region and the high-\mT~control region]{Distribution of the transverse mass \mT~in the \mutau channel, indicating
 the signal region and the high-\mT~control region. This distribution is shown
@@
 which means the estimate of the number of \Wjets events in the opposite-sign, high-\mT, region
-is multiplied by a high-\mT to low-\mT~extrapolation factor determined from simulation.
-
-The use of the method presented relies on knowledge of $R_{\text{W}}^{\text{OS/SS}}$,
+is multiplied by a high-\mT~to low-\mT~extrapolation factor determined from simulation.
+
+The use of the method presented relies on knowledge of $R_{\text{W}}^{\text{OS/SS}}$ and 
 $R_{\text{QCD}}^{\text{OS/SS}}$, and on these two ratios not being too similar to each other. 
 The ratio $R_{\text{QCD}}^{\text{OS/SS}}$ is measured in an anti-isolated
-control region in data; this measurement is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{\text{W}}^{\text{OS/SS}}$ is 
+control region in data; this measurement is described later in this section. $R_{\text{W}}^{\text{OS/SS}}$ is 
 taken from the \Wjets simulation, and is found to be between 4 and 5, while $R_{\text{QCD}}^{\text{OS/SS}}$
@@
 by having the \Pgth with highest \pT~pass the tight working
-point of the tau ID discriminator, as in the nominal selection.
+point of the tau isolation discriminator, as in the nominal selection.
 The other \Pgth is required to fail the tight working point,
@@
 the highest \pT~\Pgth passes the tight working point of the
-tau ID discriminator, and the other \Pgth passes the loose working
+tau isolation discriminator, and the other \Pgth passes the loose working
 point of the discriminator, but not the tight working point, is used.
@@
 uncertainty is split between a part that is correlated between the channels and a
-part that is not, The correlated part amounts to 
+part that is not. The correlated part amounts to 
 a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
@@
 The uncertainty in the $\text{jet}\rightarrow\Pgth$ fake rate
-is 20\% \cite{cms-tau-2015}. This uncertainty is applied
+measurement is 20\% \cite{cms-tau-2015}. This uncertainty is applied
 to those backgrounds where the normalisation is estimated using simulation and
@@
 Uncertainties in the b-tagging efficiency and light jet mis-tagging
-rates are given as a function of jet \pT and $\eta$ for the 
+rates are given as a function of jet \pT~and $\eta$ for the 
 medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
@@
 to 6\% \cite{toppp}.
-\item Di-boson and single-top: The combined uncertainty on the di-boson and
+\item Di-boson and single-top: The combined uncertainty in the di-boson and
 single-top production cross sections amounts to 5\% \cite{mcfm,hathor1,hathor2}.
@@
 this ratio amounts to 8\% (10\%) in the no b-tag (b-tag) category of both channels.
-The statistical uncertainty in the low-\mT to high-\mT~ratio is 2\% in the no b-tag
+The statistical uncertainty in the low-\mT~to high-\mT~ratio is 2\% in the no b-tag
 category of both channels and 14\% (17\%) in the b-tag category of the \mutau (\etau) channel.
@@
 \tautau channel the statistical uncertainty in the QCD estimate is derived from
-the uncertainties on the observations and subtracted backgrounds in the
+the uncertainties in the observations and subtracted backgrounds in the
 sidebands used to derive the estimate. This uncertainty amounts to 3\% in the no b-tag
@@
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
-\end{center}
-\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
-of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid. Note that, to incorporate
-the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes an \PHiggslight boson
-at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps bosons, and this is
-the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_results_mttot_mt}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
-\end{center}
-\caption[Distributions of \mTtot~in the no b-tag and b-tag 
-categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
-and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
-%the observed Higgs boson at 125 GeV, the $m_{h}^{\text{mod+}}$ scenario includes a h boson
-%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
-%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_results_mttot_et}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
-\end{center}
-\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
-of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
-%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
-%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
-%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_results_mttot_tt}
-\end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
-\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
-\end{center}
-\caption[Distributions of \mTtot~in the no b-tag and b-tag categories of 
-the \emu channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
-of the \emu channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
-and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
-%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
-%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
-%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_results_mttot_em}
-\end{figure}
-
 None of these distributions show a significant excess of observed events over the background
@@
 production. All channels and categories are combined.
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
-\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
-\end{center}
-\caption[Upper limits at the 95\% CL for the gluon fusion production process and the
-b-associated production process, combining all final states and categories.]{Upper limits at the 95\% CL for (a) the gluon fusion production
-process and (b) the b-associated production process. All four final states and 
-all categories are combined for these limits. The green and yellow bands indicate
-the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
-\label{fig:mssm_results_limits}
-\end{figure}
 
@@
 the other channels.
-
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
+\end{center}
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
+of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid. Note that, to incorporate
+the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes an \PHiggslight boson
+at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps bosons, and this is
+the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_mt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
+\end{center}
+\caption[Distributions of \mTtot~in the no b-tag and b-tag 
+categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{\text{mod+}}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_et}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
+\end{center}
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
+of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_tt}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
+\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
+\end{center}
+\caption[Distributions of \mTtot~in the no b-tag and b-tag categories of 
+the \emu channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
+of the \emu channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
+and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
+%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
+%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
+%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_mttot_em}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
+\end{center}
+\caption[Upper limits at the 95\% CL for the gluon fusion production process and the
+b-associated production process, combining all final states and categories.]{Upper limits at the 95\% CL for (a) the gluon fusion production
+process and (b)~the b-associated production process. All four final states and 
+all categories are combined for these limits. The green and yellow bands indicate
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037}.}
+\label{fig:mssm_results_limits}
+\end{figure}
 \begin{figure}[h!]
@@
 comparing the combination of all channels (green) with the \mutau (red), \etau (blue), \tautau (black)
-and \emu (gold) channels. For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
-while the \tautau channel dominates for higher masses. The \etau channel is always
-slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
-until at around $1.6\,\TeV$ where it starts to overtake the \etau channel, with the sensitivity at $3.2\,\TeV$ 
-being similar or slightly better than the \mutau channel.}
+and \emu (gold) channels.} %For masses below $200\,\GeV$ the \mutau channel is the most sensitive,
+%while the \tautau channel dominates for higher masses. The \etau channel is always
+%slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
+%until at around $1.6\,\TeV$ where it starts to overtake the \etau channel, with the sensitivity at $3.2\,\TeV$ 
+%being similar or slightly better than the \mutau channel.}
 \label{fig:mssm_results_limits_breakdown}
@@
 \end{center}
-\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production processes, with the $125\,\GeV$ \ac{SM} Higgs boson included as one of the backgrounds.]{Upper limits at the 95\% CL for (a) the gluon fusion production
+\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production processes, with the $125\,\GeV$ SM Higgs boson included as one of the backgrounds.]{Upper limits at the 95\% CL for (a) the gluon fusion production
 process and (b) the b-associated production process. The $125\,\GeV$ \ac{SM} Higgs boson
 is included as one of the backgrounds. All four final states and 
-all categories are combined for these limits. The light and dark green bands indicate
+all categories are combined for these limits. The dark and light green bands indicate
 the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-037-addit}.}
@@
 with $125\,\GeV$ in the model. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
-limits at high \tanb~have been significantly improved, by around $300\,\GeV$ for a given \tanb~value..
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
-\subfloat[hMSSM scenario]{\includegraphics[width=0.65\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
+limits at high \tanb~have been significantly improved, by around $300\,\GeV$ for a given \tanb~value.
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}}~\\
+\subfloat[hMSSM scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}}
 \end{center}
 \caption[Exclusions in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
-scenario of the \AHtotautau analysis.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
+scenario of the \mbox{\AHtotautau} analysis.]{Exclusions in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
 obtained by the combination
@@
 \caption[Transverse component of the di-tau mass for the expected backgrounds
-and observed events in the no b-tag and b-tag cateogires of the \emu channel.]{Transverse component of the di-tau mass for the expected backgrounds and
+and observed events in the no b-tag and b-tag categories of the \emu channel.]{Transverse component of the di-tau mass for the expected backgrounds and
 observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
@@
 process and (b) the b-associated production process. All four final states and 
-all categories are combined for these limits. The green and yellow bands indicate
+all categories of the 2015 analysis are combined for these limits. The green and yellow bands indicate
 the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit \cite{CMS-PAS-HIG-16-006}.}
@@
 \end{figure}
-
+\clearpage
 \begin{figure}[h!]
@@
 \end{figure}
-\clearpage
 
@@
 
-The choice of correlation scheme is chosen
+The correlation scheme is chosen
 based on the procedure used for the ATLAS and \ac{CMS}
@@
 for the combination of the 2015 and 2016 analyses are shown in figure
-\ref{fig:mssm_results_combination_limits}. The expected and observed limits
+\ref{fig:mssm_results_combination_limits}. These limits
 exhibit similar trends as 
 the individual 2015 and 2016 limits.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_ggH_cmb.png}}
-\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_bbH_cmb.png}}
-\end{center}
-\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production
-process, obtained by combining all channels and categories of the 2015 and the 2016 analyses.]{Upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
-process and (b) the b-associated production process. These results
-combine all categories and all four final states from both the 2015
-and the 2016 analyses. The green and yellow bands indicate
-the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit.}
-\label{fig:mssm_results_combination_limits}
-\end{figure}
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_ggH_with_ratio.pdf}}
-\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_bbH_with_ratio.pdf}}
-\end{center}
-\caption[Comparison of the expected upper limits at the 95\% CL for the 
-gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
-process and (b) the b-associated production process. The green curve shows the results
-from combining the 2015 and 2016 analyses (integrated luminosity of $15.2\,\invfb$),
-with the red line indicating the limits from the 2016 analysis only (integrated luminosity of $12.9\,\invfb$)
-and the blue line indicating the limits from the 2015 analysis only (integrated luminosity of $2.3\,\invfb$).
-The relative difference is shown with respect to the limits from the 2016 analysis, showing how the combination
-improves on those limits by between a few percent at high mass up to 40\% at low mass.}
-\label{fig:mssm_results_combination_limits_comp}
-\end{figure}
-
 Figure \ref{fig:mssm_mhmodp_20152016}a shows the exclusion obtained in the $m_{\PHiggslight}^{\text{mod+}}$ 
@@
 the gap between the two excluded regions.
-
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_ggH_cmb.png}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_090117_bbH_cmb.png}}
+\end{center}
+\caption[Upper limits at the 95\% CL for the gluon fusion and b-associated production
+process, obtained by combining all channels and categories of the 2015 and the 2016 analyses.]{Upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
+process and (b) the b-associated production process. These results
+combine all categories and all four final states from both the 2015
+and the 2016 analyses. The green and yellow bands indicate
+the $\pm 1\sigma$ and $\pm 2\sigma$ probability intervals on the expected limit.}
+\label{fig:mssm_results_combination_limits}
+\end{figure}
+\begin{figure}[h!]
+\begin{center}
+\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_ggH_with_ratio.pdf}}
+\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_combination_comparison_bbH_with_ratio.pdf}}
+\end{center}
+\caption[Comparison of the expected upper limits at the 95\% CL for the 
+gluon fusion and b-associated production process, comparing the 2015 and 2016 analyses with a combination.]{Comparison of the expected upper limits at the 95\% \ac{CL} for (a) the gluon fusion production
+process and (b) the b-associated production process. The green curve shows the results
+from combining the 2015 and 2016 analyses,
+with the red line indicating the limits from the 2016 analysis only
+and the blue line indicating the limits from the 2015 analysis only.
+The relative difference is shown with respect to the limits from the 2016 analysis.}%, showing how the combination
+%improves on those limits by between a few percent at high mass up to 40\% at low mass.}
+\label{fig:mssm_results_combination_limits_comp}
+\end{figure}
 \begin{figure}[h!]

### 2017-03-03 Objects/Objects.tex
Own final read through

@@
 Primary vertices are reconstructed by clustering
-tracks that are compatible with have originated from the same vertex, then fitting 
+tracks that are compatible with having originated from the same vertex, then fitting 
 these tracks for the position of the vertex. The clustering 
@@
 vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
-vertex position. The analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} take the primary
+vertex position. The analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} take the primary
 vertex of the hard scatter to be the reconstructed vertex with the largest scalar \pT~sum of the associated
@@
 A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
-that will be described in section \ref{sec:objects_pf}.%FIXME don't say this, they're more similar now
+that will be described in section \ref{sec:objects_pf}. %FIXME don't say this, they're more similar now
 Depending on the thickness of the intervening material, electrons lose up to an average of 86\% of their energy 
@@
 \caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
-and misidentified electrons at $8\,\TeV$, for data and MC]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
+and misidentified electrons at $8\,\TeV$, for data and simulation]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
 misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
@@
 
-Following this, remaining tracks lead to charged hadrons. The track is
+After this, remaining tracks lead to charged hadrons. The track is
 given the momentum from the track fit, assuming the mass of a charged pion. If
@@
 modelled in simulation, the b-tagging efficiency for different jet
-flavours is different in data and \ac{MC} simulation. Scale factors can be detemined
+flavours is different in data and \ac{MC} simulation. Scale factors can be determined
 as the ratio of tagging efficiencies between the two, which are applied to the simulated events in order to match the data.
@@
 \Zmm events, in a sample corresponding to $42\,\invpb$ of data collected
-at $\sqrt{s}=13\,\TeV$.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
+at \mbox{$\sqrt{s}=13\,\TeV$}.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~(black circles) for
 \Zmm events, which contain no genuine \MET~, in a sample corresponding to $42\,\invpb$ of data collected at $\sqrt{s}=13\,\TeV$. The 
@@
 %\label{sec:objects_tau_iso}
-Requiring the reconstructed \Pgth to be isolated reduces the jet $\rightarrow$\Pgth fake rate. Isolation
+Requiring the reconstructed \Pgth to be isolated reduces the $\text{jet}\rightarrow\Pgth$ fake rate. Isolation
 discriminators can be defined using the isolation sum,
@@
 direction of the \Pgth are taken into account and the charged particle tracks are required to be compatible with having
-originated from the \Pgth production vertex within $d_z < 0.2\,\cm$. The second term denotes the sum
+originated from the \Pgth production vertex. This is achieved by requiring the longitudinal impact parameter
+with respect to the primary vertex to be $d_z < 0.2\,\cm$. The second term of equation \ref{eqn:cutbased_iso} denotes the sum
 of the transverse momenta of photons with $\pTm > 0.5$ GeV within a cone of $\Delta R = 0.5$ centred around the direction
@@
 Figure \ref{fig:tau_efficiency}a compares the \Pgth identification efficiency with the
-jet$\rightarrow$\Pgth fake rate for different working points of the
+$\text{jet}\rightarrow\Pgth$ fake rate for different working points of the
 MVA isolation discriminator, as well as the cut-based isolation discriminator based
@@
 versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
-$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
+$\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the \mbox{$\Pe\rightarrow\Pgth$} fake rate for different
 working points of the anti-electron discriminator.]{(a) The jet$\rightarrow$\Pgth fake rate in simulated QCD multijet events versus \Pgth identification
@@
 the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
-the \pT~of the \Pe.}
+the \pT~of the electron.}
 \label{fig:tau_efficiency}

### 2017-03-03 Theory/Theory.tex
Own final read through

@@
 The SU(2) part of the symmetry is built from the weak
-isospin generators $I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$,
+isospin generators \mbox{$I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$},
 where $\sigma_i$ are the Pauli spin matrices. The U(1)
@@
 Tevatron also did not lead to the discovery of the Higgs boson, but did exclude 
-an additional mass range of $140$--$186\,\GeV$ at the 95\% \ac{CL} \cite{TEV-Higgs}.
+an additional mass range of $140$--$186\,\GeV$ at the \mbox{95\% \ac{CL} \cite{TEV-Higgs}}.
 
@@
 \begin{equation}\label{eqn:scalarmass}
-m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\text{cos}^2 2\beta}].
+m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\text{cos}^2 2\beta}~].
 \end{equation}
@@
 
-Figure \ref{fig:mhmodp_br} shows the branching ratio of the \PHiggs and \PHiggsps 
-into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
+Figure \ref{fig:mhmodp_br} shows the branching ratios of the \PHiggs and \PHiggsps 
+bosons into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
 high \tanb, showing how this decay channel is useful for MSSM Higgs boson searches.
@@
 corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
-A large area of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ 
+A large area of the \mbox{\mA-\tanb}~plane in the $m_{\PHiggslight}^{\text{mod+}}$ 
 scenario contains a light Higgs boson with a mass compatible with
@@
 
-\subsubsection{The low-\tanb~scenario}
-\label{sec:theory_BSM_model_lowtb}
-In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
-the radiative corrections are tuned to obtain a light 
-Higgs boson mass of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
-Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
-\mA~$=150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
-
 \begin{figure}[h!]
@@
 \end{figure}
+
+\subsubsection{The low-\tanb~scenario}
+\label{sec:theory_BSM_model_lowtb}
+In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
+the radiative corrections are tuned to obtain a light 
+Higgs boson mass of around $125\,\GeV$ in most of the \mbox{\mA-\tanb}~plane considered.
+Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
+\mA~$=150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.
+
 %\begin{figure}[h!]
@@
 experiments up to the end of 2012 many searches for \ac{BSM} Higgs
-bosons were performed. Figure \ref{fig:bsm_summary} shows the interpetations
+bosons were performed. Figure \ref{fig:bsm_summary} shows the interpretations
 of different searches performed with the \acs{CMS} detector during this period

### 2017-03-03 frontmatter.tex
A few more minor changes before sending off to supervisors
Own final read through

@@
 level are set on the cross section times branching ratio for the production of Higgs bosons in the MSSM.
-In addition, limits are set in the \mA-\tanb~parameter space of 
-several MSSM benchmark scenarios, and in the \cosba-\tanb~parameter space of 
+In addition, limits are set in the \mbox{\mA-\tanb}~parameter space of 
+several MSSM benchmark scenarios, and in the \mbox{\cosba-\tanb}~parameter space of 
 a two Higgs doublet model.
@@
 including those made by myself, include the relevant reference in the figure caption.
-The work for the analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} was 
+The work for the analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
 carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
@@
 the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
-work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
+work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter~\ref{chap:mssm}
 I was responsible for all stages of the analysis, including the optimisation
@@
 result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
-The work presented in chapter \ref{sec:mssm_combination} has
+The work presented in chapter~\ref{sec:mssm_combination} has
 not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
@@
 %% I don't want a page number on the following blank page either.
-\thispagestyle{empty}
+%\thispagestyle{empty}

### 2017-03-08 Conclusion/Conclusion.tex
Final bits before submission

@@
 based on the presence of b-tagged jets to separate
-the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
+the gluon fusion and b-associated Higgs boson production modes in the \ac{MSSM}. 
 The hadronic tau isolation working point and the topological selection on 
-the \mT~variable are chosen to optimise the search sensitivity for signal
+the transverse mass between the electron or muon and the missing transverse energy are chosen to optimise the search sensitivity for signal
 masses of around $1\,\TeV$.
-The sensitivity is maximised by using the \mTtot~variable for signal extraction.
-This variable separates the dominant backgrounds
+The sensitivity is maximised by using the total transverse mass for signal extraction. This variable, which is 
+the combination of the transverse
+mass between the two legs of the di-tau candidate and the transverse masses between each of the legs
+of the di-tau candidate and the missing transverse energy,
+separates the dominant backgrounds
 and the high-mass signal well.
@@
 performed. This combination improves on the results of the 2016 analysis alone, thus
-setting the most stringent limits on $\PHiggsps/\PHiggs$ to date.
+setting the most stringent limits on $\PHiggsps/\PHiggs$ production to date.
 
@@
 as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
-is very low in the high-\mA~and low-tanb~corner. This region can be accessed 
+is very low in the high-\mA~and low-\tanb~corner. This region can be accessed 
 via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
@@
 \caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
-at the 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
+at the 95\% CL of the 2015 MSSM analysis, projected to integrated luminosities of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
  at the 95\% CL of the 2015 MSSM analysis (pink)
 projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
-under several assumptions of how the systematic uncertainties scale. Even with an integrated 
+under several assumptions of how the systematic uncertainties scale. In scenario ``S1''
+all systematic uncertainties are kept constant with integrated luminosity, while in scenario ``S2'' 
+the theoretial uncertainties are scaled down by a factor $\frac{1}{2}$ and experimental
+systematic uncertainties scale down by the square root of the integrated luminosity until they reach
+a lower limit. In the ``Stat. Only'' scenario all systematic uncertainties are neglected. Even with an integrated 
 luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
-in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
+in this \ac{MSSM} benchmark scenario using this analysis alone \cite{HTT-projection}.}
 \label{fig:mssm_projection_fig}

### 2017-03-08 Detector/Detector.tex
Final bits before submission

@@
 efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%.
-From all of the data that is recorded only a subset is used for analysis. Data is 
+Only a subset of the recorded data is used for analysis.
+Data are
 certified as good for use in analyses if it is known that all relevant sub-detectors
@@
 which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
-The main use of the preshower detectors is to identifiy neutral pions decaying to two photons in the 
+The main use of the preshower detectors is to identify neutral pions decaying to two photons in the 
 endcaps. Additionally,

### 2017-03-08 Hhh/Hhh.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

@@
 running period of the LHC. 
-Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
-\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
+Signal and background events are generated using several different \ac{MC} event generators. The \texttt{MadGraph}
+\cite{madgraph} matrix element generator is used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
 events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
-were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
+are used for the \Wjets and \Zellell backgrounds. This increases the number of background events
 in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
@@
 
-Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
-were generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
+Single top samples are produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
+are generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
  mass is $350\,\GeV$ because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
@@
 due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
-of the two muons originiating from the \PZ boson have been removed. This technique is also applied to 
+of the two muons originating from the \PZ boson have been removed. This technique is also applied to 
 a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
@@
 This section gives an overview of the event selection; a detailed description of the physics
-objecs used in this analysis is given in chapter \ref{chap:objects}.
+objects used in this analysis is given in chapter \ref{chap:objects}.
 
@@
 is applied.
-In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
+In this equation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
 angle between this light lepton and the missing transverse energy. The \mT~distributions for the \etau
@@
 from events where the di-tau or di-jet mass is not compatible with
-$125\,\GeV$, requirements are made on the di-jet invariant mass, and the di-tau
+$125\,\GeV$, requirements are made on $m_{jj}$, the di-jet invariant mass, and on $m_{\Pgt\Pgt}$, the di-tau
 invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
@@
 The kinematic observables related to the hadronic taus and jets
-are varied within their uncertainties to fulfill these 
+are varied within their uncertainties to fulfil these 
 constraints. A $\chi^2$ cost term is introduced for each
@@
 \end{equation}
-The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$.
+The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.
 
@@
 \begin{itemize}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item \Ztautau : The inclusive normalisation of the embedded samples has a 3.3\% uncertainty, which is derived
@@
 \begin{equation} \label{eqn:hhh_likelihood}
-\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
+\mathcal{L}(\text{data}|\mu, \theta) = \Pi_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
 \end{equation}
@@
 
-The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
+The first term in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
 in all channels and categories. The parameter $s$ represents the number of expected signal events
@@
 \end{figure}
-
+\clearpage
 %\begin{figure}[h!]
@@
 particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.
-
-The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
-shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
-and \AtoZh analyses, overlaid on the \xsbr.
-The exclusion contours have some interesting features, most of which can be explained by the couplings
-in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
-of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
 \begin{table}[htp]
@@
 \end{table}
+
+The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
+shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
+and \AtoZh analyses, overlaid on the \xsbr.
+The exclusion contours have some interesting features, most of which can be explained by the couplings
+in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
+of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
 which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
@@
 the analysis is not yet sensitive enough to actually observe it.
+
 %Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 

### 2017-03-08 MSSM/MSSM.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

@@
 In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
-decaying to a pair of tau leptons will be discussed. The results presented
-here correspond to those from an analysis peformed on a dataset collected
+decaying to a pair of tau leptons is discussed. The results presented
+here correspond to those from an analysis performed on a dataset collected
 during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
@@
 
-Signal and background events were generated using
+Signal and background events are generated using
 various \ac{MC} event generators. Signal samples
 for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
-production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
-These samples were produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
+production processes of the \PHiggs or \PHiggsps bosons are generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
+These samples are produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
 This range is slightly wider than the range in which MSSM Higgs sector
@@
 Single-top and \ttbar background samples are generated using \texttt{POWHEG},
-with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
-samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
-\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
+while for the generation of di-boson background samples \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} is used.
+%and part of the W+$\gamma$ background, which is included in the \emu channel only.
+\Wjets and \mbox{\Zll} backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
 matrix element generator. Samples containing both a mixture
@@
 The optimisation of some of the selections will also be discussed there. Note that 
-the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
+the optimisations are all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
 corresponds to an integrated luminosity of $2.3\,\invfb$.
@@
 The trigger only requires a muon at \ac{L1}, to which loose identification and
-isolation criteria are applied at the level of the \ac{HLT}
+isolation criteria are applied at the level of the \ac{HLT}.
 
@@
 The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
-raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensivity
+raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensitivity
 of the analysis for high mass points, while recovering some of the loss of loosening 
@@
 The trigger in the \tautau channel requires two hadronic taus at \ac{L1} to which loose identification
-and isolation criteria are applied in the \ac{HLT}
+and isolation criteria are applied in the \ac{HLT}.
 
@@
 the vast majority of these signal events do not have any b-tagged jets. To
-target this production mode a category which requires nob-tagged jets can be used.
+target this production mode a category which requires no b-tagged jets can be used.
 The same figure also shows that the majority of $\Pbottom\Pbottom\phi$
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
@@
 always contain b-jets. The decay products of one or both of the \PW bosons, and additional jets in the event, can 
-then form \etau, \mutau, \tautau and \emu pairs.\\
+then form \etau, \mutau, \tautau and \emu pairs.
+
 The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
@@
 background. In the \tautau channel both reconstructed
-hadronic taus are required to be matched to a simulated hadronic tau, and
-in the \emu channel the \Ztautau component of the Drell-Yan background 
+hadronic taus are required to be matched to a simulated hadronic tau. 
+In the \emu channel the \Ztautau component of the Drell-Yan background 
 is taken as those events where the reconstructed electron is not matched to
@@
 \end{center}
-\caption[Distribution of the transverse mass \mT~in the \mutau channel, indicating the signal region and the high-\mT~control region]{Distribution of the transverse mass \mT~in the \mutau channel, indicating
+\caption[Distribution of the transverse mass \mT~in the \mutau channel, indicating the signal region and the high-\mT~control region.]{Distribution of the transverse mass \mT~in the \mutau channel, indicating
 the signal region and the high-\mT~control region. This distribution is shown
@@
 in the final result as described in section \ref{sec:hhh_results_extraction}.
+
+Overview tables of the systematic uncertainties per category of each
+channel can be found in appendix \ref{appendix:uncerts}. The correlations
+between the different channels and categories for these uncertainties
+are also indicated.
 
@@
 The uncertainty in the jet energy corrections is applied
-by shifting the jet energy up and down by a \pT-and $\eta$-dependendent
+by shifting the jet energy up and down by a \pT- and $\eta$-dependent
 uncertainty, and evaluating the change in the process normalisation in
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item \Ztautau: As the \Zmm control region is included in the simultaneous
@@
 
-Overview tables of the systematic uncertainties per category of each
-channel can be found in appendix \ref{appendix:uncerts}. The correlations
-between the different channels and categories for these uncertainties
-is also indicated.
-
 \section{Signal extraction}
@@
 Higgs combinations \cite{MassComb,CouplComb}. This means
-uncertainties are either considered 100\% (anti-)correlated or fully uncorrelated. Partial
+uncertainties are either considered 100\% \mbox{(anti-)correlated} or fully uncorrelated. Partial
 correlations are not taken into account, with a small number of exceptions. The

### 2017-03-08 MSSM/UncOv.tex
Final bits before submission

@@
 \begin{center}
-\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \mutau channel]{\footnotesize Systematic uncertainties that affect the estimated number of signal
+\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \mutau channel.]{\footnotesize Systematic uncertainties that affect the estimated number of signal
 or background events in the \mutau channel.} 

### 2017-03-08 Objects/Objects.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width of the supercluster in units of $\eta$ crystals (illustrated in figure \ref{fig:ele_id_vars}a). 
@@
 \caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
-and misidentified electrons at $8\,\TeV$, for data and simulation]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
+and misidentified electrons at $8\,\TeV$, for data and simulation.]{(a) $\sigma_{i\eta,i\eta}$ and (b) $1/E_{\text{SC}} - 1/p_{e}$ for real (black points)  and 
 misidentified (yellow triangles) electrons in a dataset corresponding to $19.7\,\invfb$
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item Reconstruction by either the global or tracker muon reconstruction algorithms.
@@
 can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
-\ac{ECAL} endcaps, first and second \ac{PS} layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
+\ac{ECAL} endcaps, first and second preshower layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
 clustering employed in the \ac{HF}.
@@
 clusters are established by extrapolating the track from its last measured
-tracker hit to the \ac{PS} layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
+tracker hit to the preshower layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
 %typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
@@
 will give rise to an energy imbalance in the transverse plane, and so their
-presence can be inferred from missing energy, \MET, in the event.
+presence can be inferred from missing transverse energy, \MET, in the event.
 
@@
 \begin{equation}\label{eqn:objects_met_corr}
-\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - p_{\text{T,jet}}).
+\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{  corr}} - \vec{p}_{\text{T,jet}}),
 \end{equation}
-
+where `corr' refers to the corrected values.
 %The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature.
@@
 constituents selected as the di-tau candidate.
+
+Two \acp{BDT} trained on \Zmm events are used to compute this correction.
+The first one corrects the direction of the hadronic recoil, the second
+one uses a data sample with the corrected recoil direction to compute a correction
+to the magnitude of the hadronic recoil. This \ac{BDT} regression uses the magnitude of the hadronic
+recoil, its azimuthal angle and the scalar \pT~sum of all \ac{PF} particles for several 
+different \MET~definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
+the performance of the MVA \MET~in data collected at $\sqrt{s}=13\,\TeV$ compared with 
+the \ac{PF} \MET. Figure \ref{fig:objects_mvamet}a indicates the lower MVA \MET~values for events without genuine
+\MET and figure \ref{fig:objects_mvamet}b shows the improved resolution at high pileup.
+
+In the process of calculating the corrections to the hadronic recoil using the MVA \MET~algorithm, an event-by-event
+estimator of the likelihood that the \MET~is due to unseen objects rather than induced
+by mismeasurement of jet energy is also determined~\cite{cms-met-run1}.
 
@@
 
-Two \acp{BDT} trained on \Zmm events are used to compute this correction.
-The first one corrects the direction of the hadronic recoil, the second
-one uses a data sample with the corrected recoil direction to compute a correction
-to the magnitude of the hadronic recoil. This \ac{BDT} regression uses the magnitude of the hadronic
-recoil, its azimuthal angle and the scalar \pT~sum of all \ac{PF} particles for several 
-different \MET~definitions \cite{cms-met-run1} as input. Figure \ref{fig:objects_mvamet} shows
-the performance of the MVA \MET~in data collected at $\sqrt{s}=13\,\TeV$ compared with 
-the \ac{PF} \MET. Figure \ref{fig:objects_mvamet}a indicates the lower MVA \MET~values for events without genuine
-\MET and figure \ref{fig:objects_mvamet}b shows the improved resolution at high pileup.
-
-In the process of calculating the corrections to the hadronic recoil using the MVA \MET~algorithm, an event-by-event
-estimator of the likelihood that the \MET~is due to unseen objects rather than induced
-by mismeasurement of jet energy is also determined \cite{cms-met-run1}.
 %Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
@@
 \label{sec:objects_met_recoilcorr}
-To correct for the mismodelling of \MET~in simulated events, recoil corrections are determined. 
+To correct for the mis-modelling of \MET~in simulated events, recoil corrections are determined. 
 The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{\text{ leptons}/\nu}$ 
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item \textbf{One prong + 0 \Ppizero :} One charged particle, no strips.
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
@@
 \begin{itemize}
-\setlength{\itemsep}{-\baselineskip}
+\setlength{\itemsep}{-0.5\baselineskip}
 \item Kinematic variables of the \Pgth candidate and \ac{GSF} track, including visible mass of the \Pgth.
@@
 \end{center}
-\caption[Figures of the jet$\rightarrow$\Pgth fake rate in QCD MC events
+\caption[Figures of the jet$\rightarrow$\Pgth fake rate in simulated QCD events
 versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
@@
 the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
-the \pT~of the electron.}
+the \pT~of the electron \cite{cms-tau-2015}.}
 \label{fig:tau_efficiency}

### 2017-03-08 Theory/Theory.tex
Final bits before submission

@@
 %\end{equation}
-The SU(2) part of the symmetry is built from the weak
+The SU(2)$_{\text{L}}$ part of the symmetry is built from the weak
 isospin generators \mbox{$I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$},
-where $\sigma_i$ are the Pauli spin matrices. The U(1)
+where $\sigma_i$ are the Pauli spin matrices. The U(1)$_{\text{Y}}$
 symmetry comes from the weak hypercharge generator $Y$, which
@@
 \end{center}
-\caption[Tree-level Feynman diagrams for the dominant Higgs boson production modes at the LHC]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
+\caption[Tree-level Feynman diagrams for the dominant Higgs boson production modes at the LHC.]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
 the \ac{LHC}.}
@@
 \end{center}
-\caption[SM Higgs boson production cross sections at $\sqrt{s}=13\,\TeV$ and SM Higgs boson branching ratios, for Higgs boson masses between $120$ and $130\,\GeV$]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13\,\TeV$ and (b) \ac{SM}
+\caption[SM Higgs boson production cross sections at $\sqrt{s}=13\,\TeV$ and SM Higgs boson branching ratios, for Higgs boson masses between $120$ and $130\,\GeV$.]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13\,\TeV$ and (b) \ac{SM}
 Higgs boson branching ratios, for Higgs boson masses between $120$ and $130\,\GeV$ \cite{YR4}.}
@@
 \end{center}
-\caption[Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario]{Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario,
+\caption[Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario.]{Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario,
 at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $\Pbottom\APbottom$ (red) 
@@
 \end{center}
-\caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
+\caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM.]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
 production of neutral Higgs bosons in the MSSM. The squarks in the gluon fusion production loop do not contribute to the production of the \PHiggsps boson.}
@@
 \end{center}
-\caption[Inclusive production \xsbr for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production \xsbr for an example
+\caption[Inclusive production \xsbr for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps bosons.]{Inclusive production \xsbr for an example
 of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
@@
 \begin{center}
-\subfloat[$\sigma(\Pg\Pg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
-\subfloat[$\sigma(\Pg\Pg\rightarrow \Pbottom\Pbottom\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
+\subfloat[$\sigma(\Pg\Pg\rightarrow \PHiggs)$ (pb)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
+\subfloat[$\sigma(\Pg\Pg\rightarrow \Pbottom\Pbottom\PHiggs)$ (pb)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
 \end{center}
@@
 
-Two approches for the definition of an \ac{MSSM} scenario that gives
+Two approaches for the definition of an \ac{MSSM} scenario that gives
 access to the low \tanb~region have been developed, they will be
@@
 \caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
-\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
+\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, in $\GeV$ as a function 
 of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low-\tanb~scenario. The white areas
@@
 \ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\text{cos}^2\beta+m_{\PHiggsps}^2\text{sin}^2\beta - m_{\PHiggslight}^2$, is non-zero. 
-This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
+This leads to a minimum accessible \mA~value of \mh~at high \tanb, and
 a minimum accessible \mA~of around $151\,\GeV$ for \tanb=1. In addition, the scenario

### 2017-03-08 frontmatter.tex
Final bits before submission

@@
 \begin{declaration}
-  \vspace*{1cm}
+%  \vspace*{1cm}
   I declare that the work in this thesis is mine. Figures and results taken from other sources
@@
 of object selection and event categorisation, as well as studies of background
-methods for three out of four channels in the public result of the analysis,
-evaluation of systematic uncertainties in all four channels, and production of the statistical
+methods for three out of four final states in the public result,
+evaluation of systematic uncertainties in all four final states, and production of the statistical
 results, including model interpretations. This work is included in the most recent
@@
 %% Acknowledgements
-%\begin{acknowledgements}
-%\end{acknowledgements}
+\begin{acknowledgements}
+I would like to thank Imperial College and the Imperial College HEP group 
+for giving me the opportunity to carry out this research, and especially
+for the valuable experience of spending two years at CERN. Thanks
+to my supervisors, David Colling for helping secure this funding and his support, and Gavin Davies
+for many useful discussions and general advice.
+The work in this thesis would not have come to fruition without Rebecca, who taught me 
+all the important aspects of doing an analysis as well as always being
+ready to discuss ideas, and I am very grateful to her for that. My thanks extend
+to Andrew in this regard, who was also always available to discuss physics and coding issues.
+I would also like to thank the people I've worked with in the CMS $\PHiggs\rightarrow\tau\tau$ group,
+particularly those involved in the most recent MSSM result.
+
+Thanks to my friends, nearby and far away, for all of the good times and laughter.
+Most importantly, I would like to thank those closest to me for their love: My mother, who is always there
+for me despite the fact I live so far away; my father, whose love of science I inherited and who
+would certainly be a little bit jealous of the computing power I get to play with on a daily basis; my sister, 
+who always understands me as she's followed a similar path; and Andrew, for making the days so much brighter.
+
+\begin{flushright}
+Adinda de Wit
+\end{flushright}
+\end{acknowledgements}
 

### 2017-05-08 Hhh/Hhh.tex
First part of first round of corrections

@@
 \label{chap:hhh}
+The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
+new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
+generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
+of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
+the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
+of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
+of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.
+
 In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
@@
 Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.
-
-The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
-new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
-generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
-of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
-the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
-of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
-of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.
 
@@
 In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
-required. No b-tagging requirements are applied at this stage, these will be discussed 
+required. No b-tagging requirements are applied at this stage; these will be discussed 
 in more detail in section \ref{sec:hhh_selection_categories}.
@@
 large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
-events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back,
+events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back, and
 therefore \mT~will be large. For \Ztautau and \htotautau events, the neutrinos in the $\tau\rightarrow\ell\nu\nu$ decay 
@@
 The 2jet-0tag category does not collect much of the signal and is dominated by 
-backgrounds, the 2jet-2tag category is the most sensitive to signal. 
+backgrounds, and the 2jet-2tag category is the most sensitive to signal. 
 Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
@@
 \begin{center}
-\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log.pdf}}
-\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log.pdf}}
+\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log_corrs.pdf}}
+\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log_corrs.pdf}}
 \end{center}
@@
 In signal events the di-tau pair and di-jet pair 
-are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
+are the decay products of a $125\,\GeV$ Higgs boson, and therefore their invariant
 masses should be close to $125\,\GeV$. To reduce background contributions
@@
 which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
-By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
+By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$, a 
 large number of background events can be rejected, while retaining
@@
 \begin{center}
-\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
-\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
+\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012_corrs.pdf}}
+\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012_corrs.pdf}}
 \end{center}
@@
 
-\section{\acl{MC} simulation to data correction factors}
+\section{\acl{MC} simulation-to-data correction factors}
 \label{sec:hhh_datamc}
 Simulated samples are used for the estimation of some of the backgrounds and the signal, 
-and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
+and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation-to-data 
 correction factors used for this are estimated in dedicated control regions.
@@
 To correct for the differences in b-tagging efficiency and light jet mis-tagging
-rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
+rates between data and simulation, \pT-and $\eta$-dependent scale factors are 
 derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
-b-/c-jets and light jets. In this analysis the ``promote-demote'' method
-is used to apply these.
+b-/c-jets and light jets.
 
-In this method a demotion or promotion probability is assigned to every
+In this analysis the ``promote-demote'' method
+is used to apply these scale factors. In this method a demotion 
+or promotion probability is assigned to every
 jet as:
@@
 \end{align}
-Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
+where `SF' is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
 the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
@@
 constraints. A $\chi^2$ cost term is introduced for each
-observable that is varied with respect to the measurement,
+observable that is varied with respect to the measurement;
 the aim of the fit is to minimise the sum of these $\chi^2$ terms.
@@
 that uncertainties in the energy measurement directly translate to
-uncertainties in the momentum measurement, therefore $\vec{\beta} = \vec{p}/E$ is
+uncertainties in the momentum measurement, and therefore $\vec{\beta} = \vec{p}/E$ is
 also kept constant.
@@
 \begin{equation}\label{eqn:kinfit_recoilmeas}
-\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 1}}^{\text{meas}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}},
+\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 1}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilfit}
-\vec{p_{\text{T,recoil}}}^{\text{fit}} = -\vec{p_{\text{T,\PHiggs}}}^{\text{fit}} = - \vec{p_{\text{T},\Pbottom 1}}^{\text{fit}} - \vec{p_{\text{T},\Pbottom 2}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_1}}^{\text{fit}} - \vec{p_{\text{T},\Pgt_2}}^{\text{fit}}.
+\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\Pbottom 1}^{\text{ fit}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilchi2}
-\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{meas}}),
+\chi^2_{\text{recoil}} = (\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}})^T V_{\text{recoil}}^{-1}(\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}}),
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilcov}
-V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
+V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
 \end{equation}
@@
 The \Ztautau background is estimated using the embedded samples
-described in section \ref{sec:hhh_datasets}. To estimate the 
-yield of \Ztautau in each category the total
-yield after the initial event selection, before subdividing into categories, as
-estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
-such events pass the category selection in the embedded sample. The shape of
+described in section \ref{sec:hhh_datasets}. The yield of
+\Ztautau in each category is evaluated in two steps. In the first
+step the total yield after the initial event selection, before subdividing into categories,
+is evaluated in the simulated \Ztautau sample. In the second step the yield obtained 
+in the first step is scaled by the efficiency with which such events pass the 
+category selection in the embedded sample.
+The shape of
 the \Ztautau background is taken from the embedded sample after applying the full
@@
 
-The first term in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
+The first factor in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
 in all channels and categories. The parameter $s$ represents the number of expected signal events
@@
 
-The second term in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
+The second factor in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
 probability density functions of the uncertainties on the nominal
@@
 \begin{equation}\label{eqn:hhh_pvaluebkg}
-1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
+1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
 \end{equation}

### 2017-05-08 MSSM/MSSM.tex
First part of first round of corrections

@@
 production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
-modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
+modes and decay into $\Pgt\Pgt$. 
 In addition to the upper limits on \xsbr of these two processes, 
@@
 followed by additional selection criteria. For the \etau
-and \mutau channels events are selected by only triggering on the electron or muon. 
+and \mutau channels, events are selected by only triggering on the electron or muon. 
 While the lepton + hadronic tau cross-triggers that are also available
@@
 After applying trigger
-requirements, identification criteria and kinematic cuts
+requirements, identification criteria and kinematic cuts,
 more than one possible candidate pair can exist. If
@@
 \begin{equation}\label{eqn:reltrkiso}
-I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{tracks from PV within cone of 0.3 of the muon}}}{p_{\text{T}}^{\mu}}, \end{equation} 
+I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{trkPV}}}{p_{\text{T}}^{\mu}}, \end{equation} 
+where `trkPV' refers to tracks from the primary vertex which are within a cone of $\Delta R=0.3$ of the muon,
 is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
@@
 \begin{align}\label{eqn:mssm_em_dzeta}
-D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
-\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
+&D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
+&\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
 \text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
@@
 
-\section{\acl{MC} simulation to data correction factors}
+\section{\acl{MC} simulation-to-data correction factors}
 \label{sec:mssm_mccorrs}
@@
 mis-modelling with respect to the data. Dedicated control regions in
-data are used to derive the \ac{MC} simulation to data correction factors
+data are used to derive the \ac{MC} simulation-to-data correction factors
 that are applied to the simulated samples. Where efficiencies
@@
 In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
-channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In
-figures the di-boson and single-top backgrounds are drawn together with the \Wjets 
+channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In all
+figures in this chapter the di-boson and single-top backgrounds are drawn together with the \Wjets 
 background and labelled collectively as the `Electroweak' component.
@@
 estimated in this one-jet selection, multiplied by an extrapolation factor 
-$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
+$N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}/N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}$.
 \begin{figure}[h!]
@@
 \begin{equation}\label{eqn:tautau_qcd}
-R_{\text{QCD}}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
+R_{\text{QCD}}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{nominal isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
 \end{equation}
@@
 \label{sec:mssm_uncs}
-As for the analysis presented in chapter \ref{chap:hhh}
+As for the \Htohhtobbtautau analysis
 two types of systematic uncertainty are considered. Normalisation
@@
 
-\subsection{MSSMvsSM hypothesis testing}
+\subsection{MSSM vs SM hypothesis testing}
 \label{sec:mssm_sigext_mssmvssm}
@@
 $\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
-general not zero. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011},
+general not zero. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011,TEV-Higgs},
 \begin{equation}\label{eqn:mssm_tevatron_teststat}
@@
 
-The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, can not be applied
+The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, cannot be applied
 to this test statistic, and therefore the probability density functions need to be generated 
-with toy datasets. Using these probability density functions $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
-If $\text{CL}_s < 0.05$ the \ac{MSSM} hypothesis is excluded at the 95\% CL. The generation of toy datasets and 
+with toy datasets. Using these probability density functions, $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
+If $\text{CL}_s < 0.05$, the \ac{MSSM} hypothesis is excluded at the 95\% CL. The generation of toy datasets and 
 calculation of corresponding $\text{CL}_s$ values is performed for many points in a grid in the \mA-\tanb~plane,

### 2017-05-08 Objects/Objects.tex
First part of first round of corrections

@@
 vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
-vertex position. The analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} take the primary
+vertex position. The \Htohhtobbtautau and \AHtotautau analyses, described in chapters \ref{chap:hhh} and \ref{chap:mssm},
+take the primary
 vertex of the hard scatter to be the reconstructed vertex with the largest scalar \pT~sum of the associated
@@
 
-For the analysis presented in chapter \ref{chap:mssm}, ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
+For the \AHtotautau analysis, ``medium'' muon requirements were applied \cite{CMS-PAS-HIG-16-037}.
 These requirements include:
@@
 
-In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
+In the \Htohhtobbtautau analysis, where Run 1 data 
 was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
@@
 on the jet energy and substructure.
-For the analysis presented in chapter \ref{chap:mssm} a
+For the \AHtotautau analysis a
 \ac{CHS} technique \cite{cms-jets-run2} is employed, 
 which means charged hadronic \ac{PF} candidates not associated with the primary vertex 
-are not considered in the jet clustering. For the analysis presented in
-chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
+are not considered in the jet clustering. For the 
+\Htohhtobbtautau analysis a dedicated identification algorithm \cite{cms-jets-puid} 
 based on vertex information and jet shape information was used to reject jets due to pileup.
@@
 from these secondary vertices.
-For the analysis presented in chapter \ref{chap:hhh}
+For the \Htohhtobbtautau analysis 
 the \ac{CSV} algorithm \cite{cms-btag-paper} has been used, with the upgraded
-\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter \ref{chap:mssm}. 
+\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the \AHtotautau analysis. 
 The \ac{CSV} algorithm takes \ac{PF} jets with $\pTm> 20\,\GeV$ and $|\eta|<2.4$ as input and 
@@
 measurement of the \MET~at high pileup can be obtained by using the MVA \MET~
-algorithm, used for \MET~reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
-\ref{chap:mssm}. This algorithm computes a correction to the hadronic
+algorithm, used for \MET~reconstruction in the \Htohhtobbtautau and \AHtotautau analyses.
+This algorithm computes a correction to the hadronic
 recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
@@
 Two \acp{BDT} trained on \Zmm events are used to compute this correction.
-The first one corrects the direction of the hadronic recoil, the second
+The first one corrects the direction of the hadronic recoil, and the second
 one uses a data sample with the corrected recoil direction to compute a correction
@@
 is projected onto the axes parallel, $u_{\parallel}$, and perpendicular, $u_{\perp}$, to the \pT~of the boson producing the leptons
-and neutrinos. For the analyses
-presented in chapters \ref{chap:hhh} and \ref{chap:mssm} it is measured in \Zmm events, where no neutrinos
+and neutrinos. For the \Htohhtobbtautau and \AHtotautau analyses 
+it is measured in \Zmm events, where no neutrinos
 are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
@@
 \item Track-related variables such as impact parameters, quality of the track, and information about decay vertices.
-\item Information about photons: the momentum weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
+\item Information about photons: the momentum-weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
 \item \Pgth-related kinematic quantities, plus the reconstructed decay mode.  

### 2017-05-08 Theory/Theory.tex
First part of first round of corrections

@@
 there is not one, but two Higgs doublets. The addition of a second
-Higgs doublet can not just be motivated by \ac{SUSY}, but also by other models.
+Higgs doublet cannot just be motivated by \ac{SUSY}, but also by other models.
 An important point is that despite the presence of a second 
@@
 hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250$--$350\,\GeV$.
-The red exclusion contour in figure \ref{fig:bsm_summary}b is the reinterpretation of the analysis presented in
+The red exclusion contour in figure \ref{fig:bsm_summary}b is the reinterpretation of the \Htohhtobbtautau analysis presented in
 chapter \ref{chap:hhh}.

### 2017-05-08 frontmatter.tex
First part of first round of corrections

@@
 \begin{declaration}
-%  \vspace*{1cm}
   I declare that the work in this thesis is mine. Figures and results taken from other sources
@@
 including those made by myself, include the relevant reference in the figure caption.
-The work for the analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
+Chapters \ref{chap:theory}--\ref{chap:objects} do not contain original work by myself, however they 
+give information on the theoretical background, the CMS detector and the standard reconstruction algorithms
+used within the CMS collaboration which underpin my own work described in later chapters.
+The work for the \Htohhtobbtautau and \AHtotautau analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
 carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
-For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
-final states presented in the final public result, and I 
-was responsible for the statistical inference. This included
+For the results of the \Htohhtobbtautau analysis I contributed to the data analysis of the \etau and \mutau
+final states of the di-tau pair. I 
+was responsible for the statistical inference of the analyses in the \etau, \mutau and \tautau final states
+of the di-tau pair. This included
 the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
-work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter~\ref{chap:mssm}
+work is included in reference \cite{CMS-HIG-14-034}. For the results of the \AHtotautau analysis
 I was responsible for all stages of the analysis, including the optimisation
 of object selection and event categorisation, as well as studies of background
-methods for three out of four final states in the public result,
-evaluation of systematic uncertainties in all four final states, and production of the statistical
+methods for the \etau, \mutau and \tautau final states in the public result,
+evaluation of systematic uncertainties in the \etau, \mutau, \tautau and \emu final states, and production of the statistical
 results, including model interpretations. This work is included in the most recent
@@
 result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
-The work presented in chapter~\ref{sec:mssm_combination} has
+The work on the combination of \AHtotautau analyses presented in chapter~\ref{sec:mssm_combination} has
 not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
+\enlargethispage{2\baselineskip}
 

### 2017-06-05 Conclusion/Conclusion.tex
Corrections

@@
 $125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
-centre-of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
+centre-of-mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
 state can access areas of the \ac{MSSM} parameter space not easily accessible via other channels.
@@
 the theoretial uncertainties are scaled down by a factor $\frac{1}{2}$ and experimental
-systematic uncertainties scale down by the square root of the integrated luminosity until they reach
+systematic uncertainties scaled down by the square root of the integrated luminosity until they reach
 a lower limit. In the ``Stat. Only'' scenario all systematic uncertainties are neglected. Even with an integrated 

### 2017-06-05 Detector/Detector.tex
Corrections

@@
 
-The pixel tracker will be upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade is needed to
-maintain the performance of the tracker as the pileup increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?
+The pixel tracker was upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade was needed to
+maintain the performance of the tracker as the pileup increases throughout the remainder of Run 2 \cite{cms-pixel-upgrade}. %or just replaced?
 
@@
 and additional particles in the event, and the constant term comes
-from calibration errors and the non-uniformity of the longitudinal response.
+from crystal-to-crystal intercalibration errors, the non-uniformity of the longitudinal response and 
+energy leakage from the back of the crystals.
 
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{./Detector/Plots/CMSTrigger.png}
+\includegraphics[width=\textwidth]{./Detector/Plots/CMSTrigger.png}
 \caption[Schematic of the different components of the L1 trigger.]{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}

### 2017-06-05 Hhh/Hhh.tex
Corrections

@@
 These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
-For these results I contributed to the analysis of the \etau and \mutau channels,
-and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
+For these results I contributed to the analysis of the \etau and \mutau channels, studying alternative \ttbar
+background rejection methods and other uses of the kinmeatic fit variable which are not further discussed.
+My main contribution was the statistical inference for the \Htohh analysis, which included limit setting and performing the model interpretations
 of the \Htohh and \AtoZh analyses, plus their combination.
@@
 running period of the LHC. 
-Signal and background events are generated using several different \ac{MC} event generators. The \texttt{MadGraph}
+Signal and background events are generated using several different \ac{MC} event generators. With the exception
+of the embedded samples described later in this section, all of these simulated
+samples are centrally produced for use by all CMS analyses. The \texttt{MadGraph}
 \cite{madgraph} matrix element generator is used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
 events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
-are used for the \Wjets and \Zellell backgrounds. This increases the number of background events
+are used for the \Wjets and \Zellell backgrounds. This increases the number of simulated background events
 in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
@@
 
-To better model the \Ztautau background an embedding technique is used. In this method, 
+To better model the \Ztautau background an embedding technique is used \cite{SMHtautauCMS}. In this method, 
 \Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
@@
 from the HPS algorithm. Additionally,
-the combined isolation is required to be
+the isolation sum (equation \ref{eqn:cutbased_iso}) is required to be
 at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
@@
 \begin{center}
-\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012.pdf}}
-\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012.pdf}}
+\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012_corrs.pdf}}
+\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012_corrs.pdf}}
 \end{center}
-\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels.}
+\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels. The signal
+at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 100, is overlaid.}
 \label{fig:Hhh_selection_mt}
@@
 (at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
-Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
+Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator. The
+typical b-tagging efficiency at this working point is 70\% \cite{BTV8TeV}.
 The 2jet-0tag category does not collect much of the signal and is dominated by 
@@
 $m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
-$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
+$m(\text{j}_{1},\text{j}_{2}) = m_{\PHiggslight} = 125\,\GeV$.
 The kinematic observables related to the hadronic taus and jets
@@
 
-For b-jets, the reconstructed direction in $\eta$ and $\phi$ is 
+For jets, the reconstructed direction in $\eta$ and $\phi$ is 
 assumed to be measured accurately in comparison with their energy.
@@
 \begin{align}\label{eqn:kinfit_prefit}
-m_{\PHiggslight}^2 &= E_{\PHiggslight}^2 - \vec{p_{\PHiggslight}}^2 = (E_{\Pbottom 1}+E_{\Pbottom 2})^2 - (\vec{p_{\Pbottom 1}} + \vec{p_{\Pbottom 2}})^2 \notag\\
-& = 2E_{\Pbottom 1}E_{\Pbottom 2} + m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2\vec{p_{\Pbottom 1}}\vec{p_{\Pbottom 2}} \notag\\
-& = m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
-&\Rightarrow (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}}) = \frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2 - m_{\Pbottom 2}^2}{2E_{\Pbottom 1}E_{\Pbottom 2}}.
+m_{\PHiggslight}^2 &= E_{\PHiggslight}^2 - \vec{p_{\PHiggslight}}^2 = (E_{\text{j} 1}+E_{\text{j} 2})^2 - (\vec{p_{\text{j} 1}} + \vec{p_{\text{j} 2}})^2 \notag\\
+& = 2E_{\text{j} 1}E_{\text{j} 2} + m_{\text{j} 1}^2 +m_{\text{j} 2}^2 - 2\vec{p_{\text{j} 1}}\vec{p_{\text{j} 2}} \notag\\
+& = m_{\text{j} 1}^2 +m_{\text{j} 2}^2 - 2E_{\text{j} 1}E_{\text{j} 2}(1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})\notag\\
+&\Rightarrow (1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}}) = \frac{m_{\PHiggslight}^2 - m_{\text{j} 1}^2 - m_{\text{j} 2}^2}{2E_{\text{j} 1}E_{\text{j} 2}}.
 \end{align}
 When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
-rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})$ 
+rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})$ 
 and
@@
 \begin{align}\label{eqn:kinfit_variation}
-m_{\PHiggslight}^2 &= m_{\Pbottom 1}^2 + m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
-&= m_{\Pbottom 1}^2 +\frac{E_{\Pbottom 2,\text{fit}}^2}{\gamma_{\Pbottom 2}^2} +2\mathcal{A}E_{\Pbottom 1}E_{\Pbottom 2,\text{fit}}\notag\\
-\Rightarrow E_{\Pbottom 2}^{\text{fit}}& = \frac{(-2E_{\Pbottom 1}\mathcal{A} + \sqrt{4E_{\Pbottom 1}^2\mathcal{A} - 4(m_{\Pbottom 1}^2-m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^{-2}})\gamma_{\Pbottom 2}^2}{2}\notag\\
-&= - E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2+\sqrt{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^4 - (m_{\Pbottom 1}^2 - m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^2}\notag\\
-&\Rightarrow E_{\Pbottom 2}^{\text{fit}} = E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2(-1 + \sqrt{1+\frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2}{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^2}}).
+m_{\PHiggslight}^2 &= m_{\text{j} 1}^2 + m_{\text{j} 2}^2 - 2E_{\text{j} 1}E_{\text{j} 2}(1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})\notag\\
+&= m_{\text{j} 1}^2 +\frac{E_{\text{j} 2,\text{fit}}^2}{\gamma_{\text{j} 2}^2} +2\mathcal{A}E_{\text{j} 1}E_{\text{j} 2,\text{fit}}\notag\\
+\Rightarrow E_{\text{j} 2}^{\text{fit}}& = \frac{(-2E_{\text{j} 1}\mathcal{A} + \sqrt{4E_{\text{j} 1}^2\mathcal{A} - 4(m_{\text{j} 1}^2-m_{\PHiggslight}^2)\gamma_{\text{j} 2}^{-2}})\gamma_{\text{j} 2}^2}{2}\notag\\
+&= - E_{\text{j} 1}\mathcal{A}\gamma_{\text{j} 2}^2+\sqrt{E_{\text{j} 1}^2\mathcal{A}\gamma_{\text{j} 2}^4 - (m_{\text{j} 1}^2 - m_{\PHiggslight}^2)\gamma_{\text{j} 2}^2}\notag\\
+&\Rightarrow E_{\text{j} 2}^{\text{fit}} = E_{\text{j} 1}\mathcal{A}\gamma_{\text{j} 2}^2(-1 + \sqrt{1+\frac{m_{\PHiggslight}^2 - m_{\text{j} 1}^2}{E_{\text{j} 1}^2\mathcal{A}\gamma_{\text{j} 2}^2}}).
 \end{align}
 
-The fitting procedure additionally modifies the masses of the b-jets as 
+The fitting procedure additionally modifies the masses of the jets as 
 ~\vspace{-0.5\baselineskip}
 \begin{equation}\label{eqn:kinfit_bjetmass}
-m_{\Pbottom_{1,2}}^{\text{fit}} = m_{\Pbottom{1,2}}\frac{E_{\Pbottom{1,2}}^{\text{fit}}}{E_{\Pbottom{1,2}}}.
+m_{\text{j}_{1,2}}^{\text{fit}} = m_{\text{j}{1,2}}\frac{E_{\text{j}{1,2}}^{\text{fit}}}{E_{\text{j}{1,2}}}.
 \end{equation}
-The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.
+The $\chi^2$ term for each jet is calculated as $\chi_{\text{j} 1,2}^2 = \frac{E_{\text{j} 1,2}^{\text{fit}}-E_{\text{j} 1,2}^{\text{meas}}}{\sigma_{\text{j} 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.
 
 For taus only the visible decay products are measured. Assuming these point in 
-the same direction as the original tau, a similar procedure as for the b-jets can be employed to constrain the energy of the second tau
+the same direction as the original tau, a similar procedure as for the jets can be employed to constrain the energy of the second tau
 when varying the energy of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.
@@
 \begin{equation}\label{eqn:kinfit_recoilmeas}
-\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 1}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
+\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\text{j} 1}^{\text{ meas}} - \vec{p}_{\text{T},\text{j} 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilfit}
-\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\Pbottom 1}^{\text{ fit}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
+\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\text{j} 1}^{\text{ fit}} - \vec{p}_{\text{T},\text{j} 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
 \end{equation}
@@
 \begin{equation}\label{eqn:kinfit_recoilcov}
-V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
+V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\text{j} {1}} - V_{\text{j} 2},
 \end{equation}
- from the covariance matrices of the b-jets and
+ from the covariance matrices of the jets and
 the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
-while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
+while the covariance matrices of the jets can be written in terms of the position, momentum, and energy resolution of the jets. 
 The total $\chi^2$ term that needs to be minimised in the fit can then be written as
@@
 \begin{equation}\label{eqn:kinfit_chitot}
-\chi^2 = \chi^2_{\Pbottom 1} + \chi^2_{\Pbottom 2} + \chi^2_{\text{recoil}}.
+\chi^2 = \chi^2_{\text{j} 1} + \chi^2_{\text{j} 2} + \chi^2_{\text{recoil}}.
 \end{equation}
-The results of the kinematic fit are the tau and b-jet four-vectors with their energies and momenta
+The results of the kinematic fit are the tau and jet four-vectors with their energies and momenta
 set to the best fit values found for them in the fit. These can then be added together to find
@@
 for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
-shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between four-body mass and
+shown in figure \ref{fig:Hhh_selection_masscuts}. This comparison between four-body mass and
 kinematic fit mass for \ttbar events is shown in figure 
@@
 \subsection{\texorpdfstring{\ttbar}{ttbar}}
-Both the \ttbar shape and normalisation are estimated using simulation.
+The \ttbar shape and normalisation are both estimated using simulation.
+%Both the \ttbar shape and normalisation are estimated using simulation.
 These are checked against data in dedicated control regions. One such control
@@
 this control region and applied to the yield estimate from simulation in the signal region. 
-%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
+The resulting scale factor is $1.033 \pm 0.013\text{ (stat.)}\pm 0.088\text{ (syst.)}$. The
+statistical and systematic uncertainties are added in quadrature to give a 9\% uncertainty,
+which is applied to the \ttbar process.
+
 \subsection{\texorpdfstring{\Wjets}{W + jets}}
@@
 events are small. Both shapes and normalisations are
-estimated using simulated samples.
+estimated using simulated samples. Dedicated $\Pe\rightarrow\Pgth$
+fake rate corrections, described in section \ref{sec:hhh_datamc}, are
+applied to adjust the \Zee normalisation. The $\Pgm\rightarrow\Pgth$ 
+fake rate correction was found to be close to 1 and therefore the \Zmm
+normalisation is not subject to such an additional correction factor.
 
@@
 the yield of a process, while shape uncertainties affect both the yield of a process and the 
-shape of its kinematic fit mass distribution. 
+shape of the kinematic fit mass distribution. 
 Section \ref{sec:hhh_results_extraction}
@@
 $\Pgm\rightarrow\Pgth$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\Pgm\rightarrow\Pgth$
-fake rate correction is close to 1, which is why it is not applied, but the uncertainty is 
+fake rate correction is close \mbox{to 1,} which is why it is not applied, but the uncertainty is 
 taken into account.
@@
 \item \Ztautau : The inclusive normalisation of the embedded samples has a 3.3\% uncertainty, which is derived
-from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples.
+from combining the estimated normalisation uncertainty on the embedded samples themselves and the uncertainty on the \ttbar embedded samples.
 In addition, an uncertainty of $5$--$6$\% for extrapolation from the inclusive selection to the category selection is applied.
 \item \Zellell: As this is a very small background after requiring two jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between $20$--$90$\%.
-\item \ttbar: The uncertainty in the \ttbar cross section is 10\% \cite{toppp}.
+\item \ttbar: The uncertainty in the measured \ttbar scale factor 9\%. 
 \item Di-boson and single top: The combined uncertainty in the di-boson and single-top cross sections is 15\% \cite{8TeVdib,8TeVst}.
@@
 
-The second factor in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
+The second factor in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$, represents the full set of 
 probability density functions of the uncertainties on the nominal
@@
 observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
-respectively.
+respectively. The numbers of observed events, compared with the background expectation, are given in appendix \ref{appendix:yields_bbtautau}.
 

### 2017-06-05 Hhh/Hhhyields.tex
Corrections

\begin{table}[h!]
\begin{center}
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{7}{c}{\mutau channel} \\
\hline
& \multicolumn{6}{c}{$\sqrt{s}$ = 8~\TeV} \\
Process & \multicolumn{2}{c}{2jet-0tag} & \multicolumn{2}{c}{2jet-1tag} & \multicolumn{2}{c}{2jet-2tag}\\
\hline
QCD                                   & 207     & 33       & 42        & 13 	& 4	& 2 \\
\ttbar                                & 89 	& 9        & 197       & 16     & 109 & 9   \\
Di-bosons + single top                & 38       & 7       & 17        & 2      & 4 &0.6     \\
\Wjets                                & 346     & 32       & 54        & 18     &1 & 7    \\
$\PZ\rightarrow \ell\ell$ (lepton/jet faking $\Pgt$)& 84        & 15        & 6         & 1  &  1 & 0.6       \\
$\PZ\rightarrow \Pgt\Pgt$            & 865       & 56       & 95        & 10  & 12 & 3       \\
\hline
Total Background                      & 1629      & 40       & 410       & 18 & 131 & 14        \\
\hline
\Htohhtobbtautau             & 1        & 0.2        & 5          & 0.3     & 3 & 0.2  \\
\hline
Data                                  & \multicolumn{2}{c}{1622     }& \multicolumn{2}{c}{405      } & \multicolumn{2}{c}{134}\\
\hline
\end{tabular}
\end{center}
\caption{ Number of events observed in data in the 2jet-0tag, 2jet-1tag and 2jet-2tag \mbox{categories} in the \mutau channel, compared
with the background expectation. The signal expectations at \mH~$=300\,\GeV$, \tanb~$=2$ are given for comparison.
The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:hhh_mt_yields}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{7}{c}{\etau channel} \\
\hline
& \multicolumn{6}{c}{$\sqrt{s}$ = 8~\TeV} \\
Process & \multicolumn{2}{c}{2jet-0tag} & \multicolumn{2}{c}{2jet-1tag} & \multicolumn{2}{c}{2jet-2tag}\\
\hline
QCD                                   & 219     & 33       & 24        & 8 	& 4	& 5 \\
\ttbar                                & 46 	& 5       & 109       & 9     & 59 & 6   \\
Di-bosons + single top                & 17       & 3       & 8        & 1      & 2 &0.4     \\
\Wjets                                & 186     & 16       & 35       & 13     &3 & 3    \\
$\PZ\rightarrow \ell\ell$ (lepton/jet faking $\Pgt$)& 158        & 26        & 15         & 3  &  1 & 0.5       \\
$\PZ\rightarrow \Pgt\Pgt$            & 393       & 38       & 44        & 5  & 4 & 1       \\
\hline
Total Background                      & 1019      & 31       & 236       & 13 & 73 & 7        \\
\hline
\Htohhtobbtautau             & 1        & 0.1        & 2          & 0.1     & 2 & 0.1  \\
\hline
Data                                  & \multicolumn{2}{c}{1022     }& \multicolumn{2}{c}{237      } & \multicolumn{2}{c}{67}\\
\hline
\end{tabular}
\end{center}
\caption{ Number of events observed in data in the 2jet-0tag, 2jet-1tag and 2jet-2tag \mbox{categories} in the \etau channel, compared
with the background expectation. The signal expectations at \mH~$=300\,\GeV$, \tanb~$=2$ are given for comparison.
The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:hhh_et_yields}
\end{table}

### 2017-06-05 MSSM/MSSM.tex
Corrections

@@
 Signal and background events are generated using
-various \ac{MC} event generators. Signal samples
+various \ac{MC} event generators. All of these simulated samples
+are centrally produced for use by all CMS analyses. Signal samples
 for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
@@
 The `inclusive' and `exclusive' samples are reweighted
-before they are combined so as to preserve the correct
-fractions of events with each jet multiplicity. The $\PW{+}\Pphoton$ background samples,
+before they are combined so that the 
+fraction of events with each jet multiplicity is the same as in the
+inclusive sample only. The $\PW{+}\Pphoton$ background samples,
 only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
@@
 change significantly when varying the isolation requirements meaning that this analysis
-is not so sensitive to fake, non-isolated muons. The choice of isolation variable is therefore
+is not so sensitive to fake, non-isolated muons. The choice of isolation variable, $\Delta\beta$
+corrected isolation as in equation \ref{eqn:electron_reliso} with a cone size of $\Delta R=0.4$, is therefore
 driven mostly by simplicity and consistency with other \ac{CMS} analyses.
@@
 \begin{align}\label{eqn:mssm_em_dzeta}
-&D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
-&\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
-\text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
+&D_{\zeta} = P_{\zeta}^{\text{miss}} - 0.85 P_{\zeta}^{\text{vis}}, \notag \\
+&\text{where } P_{\zeta}^{\text{miss}} = \vec{E}_{\text{T}}^{\text{miss}}\cdot\frac{\vec{\zeta}}{|\vec{\zeta}|} 
+\text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\cdot\frac{\vec{\zeta}}{|\vec{\zeta}|}.
 \end{align}
@@
 of the visible decay products in the transverse plane. This definition is illustrated in figure
-\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
+\ref{fig:mssm_dzeta}a. In \Ztautau and \AHtotautau events, the neutrinos from the $\tau\rightarrow\ell\nu\nu$ decay 
+are more likely to travel in the same direction as the visible decay products of the tau. This means the missing
+energy is not expected to point in the opposite direction of the momentum sum of 
+the visible tau decay products, making $D_{\zeta}$ more likely to be positive. In decays of
+di-boson, \ttbar and \Wjets events, leptons and neutrinos are more likely to be emitted back-to-back
+and therefore $D_{\zeta}$ is not preferentially positive.
+Figure \ref{fig:mssm_dzeta}b shows the $D_{\zeta}$ distribution
 for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and di-boson
@@
 \begin{center}
-\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
+\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta_adapted_ok.png}}
 \subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
@@
 \caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
-in the \emu channel.]{(a) Reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
-\emu channel \cite{CMS-PAS-HIG-16-037}.}
+in the \emu channel.]{(a) Reconstruction of $D_{\zeta}$ (adapted from \cite{cdf-dzeta}) and (b) $D_{\zeta}$ distribution in the 
+\emu channel \cite{CMS-PAS-HIG-16-037}. The events shown in (b) were selected according to the requirements described in this section.}
 \label{fig:mssm_dzeta}
@@
 the sensitivity to the signal can be increased by categorising
-based on the number of b-tagged jets in the event.
-
-\begin{figure}[h!]
-\begin{center}
-\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
-\subfloat[Number of b-tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
-\end{center}
-\caption[Number of jets and number of b-tagged jets in the \mutau channel, 
-with the signal overlaid.]{(a) Number of jets and (b) number of b-tagged jets in the \mutau channel. The gluon fusion signal (dashed
-blue line) and b-associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
-are normalised to 100 times their \xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$
-scenario. The signal-sensitive bins motivate the choice of categories.}
-\label{fig:mssm_cats_mt}
-\end{figure}
+based on the number of b-tagged jets in the event. Jets
+are considered b-tagged if they pass the medium working point
+of the \ac{CSV}v2 discriminator; the typical b-tagging efficiency at this
+working point is 69\% \cite{cms-btag-run2}.
 
@@
 \end{itemize}
+
+\begin{figure}[h!]
+\begin{center}
+\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
+\subfloat[Number of b-tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
+\end{center}
+\caption[Number of jets and number of b-tagged jets in the \mutau channel, 
+with the signal overlaid.]{(a) Number of jets and (b) number of b-tagged jets in the \mutau channel. The gluon fusion signal (dashed
+blue line) and b-associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
+are normalised to 100 times their \xsbr at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$
+scenario. The signal-sensitive bins motivate the choice of categories. The events shown in these
+figures were selected according to the requirements described in section \ref{sec:mssm_eventsel_mt}.}
+\label{fig:mssm_cats_mt}
+\end{figure}
 
@@
 to estimate some of the backgrounds, it is important to correct for possible 
-mis-modelling with respect to the data. Dedicated control regions in
-data are used to derive the \ac{MC} simulation-to-data correction factors
+mis-modelling with respect to the data. Dedicated control regions 
+are used to derive the \ac{MC} simulation-to-data correction factors
 that are applied to the simulated samples. Where efficiencies
@@
 about these corrections is given in section \ref{sec:objects_met_recoilcorr}.
-\subsubsection*{b-Tag scale factors}
-To correct for the difference in b-tagging efficiency
-and light jet mis-tagging rates between data and simulation,
-\pT- and $\eta$-dependent scale factors are derived as 
-described in reference \cite{cms-btag-run2}. They 
-are applied using the promote-demote method
-as outlined in equation \ref{eqn:promotedemote}.
 \subsubsection*{Top quark \pT~reweighting}
@@
 (a) without applying the top quark \pT~reweighting and (b) with the top quark \pT~reweighting.
-The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross section uncertainty.}
+The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross section uncertainty.
+The remaining disagreement between data and simulation after applying the reweighting is covered by
+an associated systematic uncertainty which is further discussed in section \ref{sec:mssm_uncs_shape}.}
 \label{fig:mssm_corrs_toppt}
@@
 
+\subsubsection*{b-Tag scale factors}
+To correct for the difference in b-tagging efficiency
+and light jet mis-tagging rates between data and simulation,
+\pT- and $\eta$-dependent scale factors are derived as 
+described in reference \cite{cms-btag-run2}. They 
+are applied using the promote-demote method
+as outlined in equation \ref{eqn:promotedemote}.
 \subsubsection*{Drell-Yan shape reweighting}
@@
 reweighting on the total transverse
-mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.}
+mass distribution of the \Ztautau background in the no b-tag category of the \etau channel. The events shown in (a) were selected 
+by requiring two oppositely charged muons, passing kinematic cuts, identification and isolation requirements equivalent to the selections
+applied to muons as described in section \ref{sec:mssm_eventsel_mt}.}
 \label{fig:dyrwt}
@@
 
+\clearpage
+
 \subsection{\texorpdfstring{\Wjets and QCD in the \etau and \mutau channels}{W+jets and QCD in the e tau and mu tau channels}}
@@
 control region. The shape of the \Wjets background is taken
-from simulation. The QCD shape taken from same-sign
+from simulation. The QCD shape is taken from same-sign
 data, that is, events selected in observed data with the opposite charge requirement
@@
 Because of this contribution from QCD events in the high-\mT~region we
-have, for $\mTm>70\,\GeV$:\\
+can construct two equations relating the QCD and \Wjets yields to the observed
+data. One of the equations relates these yields in the opposite-sign high-\mT~region,
+the other relates them in the same-sign high-\mT~region. Additionally 
+relating the opposite-sign yields to the same-sign yields using the
+ratios of opposite-sign to same-sign QCD and \Wjets events gives enough
+information to solve these equations for the yield of same-sign \Wjets events.
+Writing the yield of process $x$ in region $y$ as $N_x^y$, this means, for $\mTm>70\,\GeV$:\\
 \begin{minipage}{\textwidth}
@@
 in the no b-tag category.
+\clearpage
 
@@
 process no assumptions should be made about the presence or lack of the $\Pbottom\Pbottom\phi$
-process and vice versa. Therefore when calculating the upper limits on the $\Pg\Pg\phi$ ($\Pbottom\Pbottom\phi$)
+process and vice versa. Therefore, when calculating the upper limits on the $\Pg\Pg\phi$ ($\Pbottom\Pbottom\phi$)
 process, the contribution of the $\Pbottom\Pbottom\phi$ ($\Pg\Pg\phi$) process is profiled. This means it is allowed
@@
 are very well separated, and the observation is compatible with the \ac{SM} hypothesis, meaning this point of the parameter space is excluded.
+\clearpage
 
@@
 \end{figure}
-\clearpage
-
+
+\vspace{-1\baselineskip}
 \section{Results}
@@
 with mass compatible with $125\,\GeV$ in this model, which is necessary to incorporate the Higgs boson
-observed at $125\,\GeV$.
+observed at $125\,\GeV$. The numbers of observed events, compared with the background expectation, are given in 
+appendix \ref{appendix:yields_mssm}.
+
+Out of the 400 nuisance parameters in this analysis, in the fit to data 14 are pulled by more than one standard deviation and 
+none by more than two standard deviations. It is reasonable for a small fraction of the pulls to be greater than one standard deviation.
+In the low-mass region the dominant systematic uncertainties are the uncertainty related to the Drell-Yan shape reweighting, 
+the QCD OS/SS ratio uncertainties, the \Pgth identification efficiency uncertainty, and the high-\mT~to low-\mT~extrapolation uncertainty for the \Wjets background.
+Above around $800\,\GeV$ the analysis becomes more statistically limited. In this region dominant uncertainties are due to the limited numbers of available simulated events in the 
+background templates, the Drell-Yan shape reweighting uncertainty, the high-\pT~\Pgth identification efficiency uncertainty and the \Pgth energy scale uncertainty.
 
@@
 \etau channel in sensitivity at $1.6\,\TeV$ and is slightly more sensitive than the
-\mutau channel at $3.2\,\TeV$. The \emu channel becomes more sensitive at higher masses as
+\mutau channel at $3.2\,\TeV$. The \emu channel becomes more sensitive than the 
+other channels at higher masses as
 a narrower binning of the \mTtot~distribution is possible than for the other channels.
@@
 \end{figure}
+
 \begin{figure}[h!]
@@
 \clearpage
-
 \subsection{Sensitivity to the \acs{SM} Higgs boson}

### 2017-06-05 MSSM/MSSMyields.tex
Corrections

\begin{table}[h!]
\begin{center}
{\footnotesize
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{5}{c}{\mutau channel} \\
\hline
& \multicolumn{4}{c}{$\sqrt{s}$ = 13~\TeV} \\
Process & \multicolumn{2}{c}{No b-tag} & \multicolumn{2}{c}{B-tag}\\
\hline
QCD                                   & 8019       & 492       & 146        & 43        \\
\ttbar (jet faking $\Pgth$)             & 406        & 73        & 83         & 15        \\
\ttbar (genuine $\Pgth$)             & 447        & 21        & 212        & 9         \\
Di-bosons + single top (jet faking $\Pgth$)    & 245        & 13        & 37         & 2         \\
Di-bosons + single top (genuine $\Pgth$)    & 352        & 23        & 63         & 4         \\
\Wjets                            & 8506       & 616       & 116        & 43        \\
$\PZ$+jets (jet faking $\Pgth$)       & 961        & 189       & 12         & 2         \\
$\PZ$+jets (l faking $\Pgth$)         & 4138       & 888       & 41         & 9         \\
$\PZ\rightarrow \Pgt\Pgt$            & 34467      & 896       & 437        & 25        \\
\hline
Total Background                      & 57541      & 301       & 1146       & 36        \\
\hline
A/H$\rightarrow\Pgt\Pgt$             & 259        & 27        & 6          & 0.5       \\
\hline
Data                                  & \multicolumn{2}{c}{57564     }& \multicolumn{2}{c}{1136      }\\
\hline
\end{tabular}
}
\end{center}
\caption{ Number of events observed in data in the b-tag and no b-tag categories in the \mutau
compared with the background expectation. The signal
expectation, for \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario, is also shown. The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:mssm_mt_yields}
\end{table}

\begin{table}[h!]
\begin{center}
{\footnotesize
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{5}{c}{\etau channel} \\
\hline
& \multicolumn{4}{c}{$\sqrt{s}$ = 13~\TeV} \\
Process & \multicolumn{2}{c}{No b-tag} & \multicolumn{2}{c}{B-tag}\\
\hline
QCD                                   & 5963       & 734       & 82         & 42        \\
\ttbar (jet faking $\Pgth$)             & 262        & 48        & 45         & 8         \\
\ttbar (genuine $\Pgth$)             & 317        & 17        & 150        & 7         \\
Di-bosons + single top (jet faking $\Pgth$)    & 166        & 9         & 24         & 1         \\
Di-bosons + single top (genuine $\Pgth$)    & 238        & 15        & 38         & 2         \\
$\PW$+jets                            & 6778       & 639       & 88         & 47        \\
$\PZ$+jets (jet faking $\Pgth$)       & 734        & 128       & 9          & 2         \\
$\PZ$+jets (l faking $\Pgth$)         & 4517       & 733       & 54         & 8         \\
$\PZ\rightarrow \Pgth\Pgth$            & 12907      & 631       & 174        & 13        \\
\hline
Total Background                      & 31883      & 239       & 664        & 30        \\
\hline
A/H$\rightarrow\Pgt\Pgt$             & 130        & 13        & 4          & 0.3       \\
\hline
Data                                  & \multicolumn{2}{c}{31907     }& \multicolumn{2}{c}{675       }\\
\hline
\end{tabular}
}
\end{center}
\caption{ Number of events observed in data in the b-tag and no b-tag categories in the \etau channel,
compared with the background expectation. The signal
expectation, for \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario, is also shown. The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:mssm_et_yields}
\end{table}

\begin{table}[h!]
\begin{center}
{\footnotesize
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{5}{c}{\tautau channel} \\
\hline
& \multicolumn{4}{c}{$\sqrt{s}$ = 13~\TeV} \\
Process & \multicolumn{2}{c}{No b-tag} & \multicolumn{2}{c}{B-tag}\\
\hline
QCD multijet                                   & 12489      & 368       & 186        & 18        \\
\ttbar (jet faking $\Pgth$)             & 20         & 3         & 6          & 0.9       \\
\ttbar (genuine $\Pgth$)             & 33         & 3         & 17         & 1         \\
Di-bosons + single top (jet faking $\Pgth$)    & 16         & 0.9       & 3          & 0.2       \\
Di-bosons + single top (genuine $\Pgth$)    & 51         & 5         & 6          & 0.6       \\
$\PW$+jets                            & 409        & 63        & 4          & 0.7       \\
$\PZ$+jets (jet faking $\Pgth$)       & 52         & 9         & 1          & 0.2       \\
$\PZ$+jets (l faking $\Pgth$)         & 124        & 27        & 2          & 0.5       \\
$\PZ\rightarrow \Pgt\Pgt$            & 4127       & 359       & 72         & 7         \\
\hline
Total Background                      & 17321      & 132       & 297        & 16        \\
\hline
A/H$\rightarrow\Pgt\Pgt$             & 107        & 12        & 6          & 0.6       \\
\hline
Data                                  & \multicolumn{2}{c}{17314     }& \multicolumn{2}{c}{298       }\\
\hline
\end{tabular}
}
\end{center}
\caption{ Number of events observed in data in the b-tag and no b-tag categories in the \tautau channel, compared with the background expectation. The signal
expectation, for \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario, is also shown. The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:mssm_tt_yields}
\end{table}

\begin{table}[h!]
\begin{center}
{\footnotesize
\begin{tabular}{lr@{$ \,\,\pm\,\, $}lr@{$ \,\,\pm\,\, $}l}
\hline
\multicolumn{5}{c}{\emu channel} \\
\hline
& \multicolumn{4}{c}{$\sqrt{s}$ = 13~\TeV} \\
Process & \multicolumn{2}{c}{No b-tag} & \multicolumn{2}{c}{B-tag}\\
\hline
QCD multijet                                   & 9511       & 653       & 205        & 35        \\
\ttbar                         & 6709       & 210       & 2733       & 65        \\
Di-bosons + single top                & 3798       & 200       & 550        & 30        \\
$\PW$+jets                            & 1675       & 98        & 29         & 2         \\
$\PZ\rightarrow \ell\ell$            & 560        & 32        & 11         & 2         \\
$\PZ\rightarrow \Pgt\Pgt$            & 42463      & 627       & 583        & 29        \\
\hline
Total Background                      & 64717      & 264       & 4112       & 62        \\
\hline
A/H$\rightarrow\Pgt\Pgt$             & 192        & 20        & 5          & 0.3       \\
\hline
Data                                  & \multicolumn{2}{c}{64743     }& \multicolumn{2}{c}{4081      }\\
\hline
\end{tabular}
}
\end{center}
\caption{ Number of events observed in data in the b-tag and no b-tag categories in the and \emu channel, compared with the background expectation. The signal
expectation, for \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario, is also shown. The uncertainties
correspond to the post-fit systematic uncerainties, taking into account correlations between them.}
\label{tab:mssm_em_yields}
\end{table}

### 2017-06-05 Objects/Objects.tex
Corrections

@@
 the sum of these two terms. It is estimated as the sum of charged hadronic \pT~for hadrons not associated
-with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
+with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$. This factor
+is the average ratio of neutral to charged particles, which is measured in jets 
+by studying the fraction of energy carried by charged and neutral constituents \cite{cms-pf-2010-2}.
 
@@
 In the \Htohhtobbtautau analysis, where Run 1 data 
-was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
+were used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
 In addition to having to be reconstructed by the global muon algorithm, selections
@@
 object $i$ and the beam. The smallest of these distances
-is determined and if this is a distance between an object i and an object j, objects
-i and j are combined. If the smallest distance is a $d_{iB}$, object i
+is determined and if this is a distance between an object $i$ and an object $j$, objects
+$i$ and $j$ are combined. If the smallest distance is a $d_{iB}$, object $i$
 is called a jet and removed from the list of objects. In the anti-\kT~algorithm
@@
 where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
-between the objects i and j in rapidity-azimuthal angle space. The radius
+between the objects $i$ and $j$ in rapidity-azimuthal angle space. The radius
 parameter $R$ was chosen as 0.5 during Run~1 \cite{cms-jec-2011} and as 0.4 during Run~2 \cite{cms-jets-run2}. 
@@
 
+The three prong + 1 \Ppizero decay mode, which would reconstruct the 
+\Ptaupm $\rightarrow$ h$^{\pm}$h$^{\mp}$h$^{\pm}$\Ppizero\Pnut decay, 
+suffers from large contamination by jets and is therefore not considered.
+
 %\subsection{Isolation and discrimination against light leptons}
@@
 tracks not compatible with having originated from the production vertex of the hadronic tau, multiplied by
-a $\Delta \beta$ factor of 0.2.%FIXME rephrase
+a $\Delta \beta$ factor of 0.2. This factor accounts for the fraction of neutral to charged energy. To determine 
+it, the photon energy sum discussed above is fitted as a function of the quantity $\Sigma p_{\text{T}}^{\text{charged}} (d_Z > 0.2 \text{ cm})$.
+The slope of this linear fit is taken as the $\Delta \beta$ factor.
 
@@
 An MVA \Pgth isolation discriminator combines isolation variables with tau lifetime information into a \ac{BDT} to discriminate between \Pgth decays and quark and gluon jets.
-Some of the variables used as input are:
+The variables used as inputs are:
 \begin{itemize}
 \setlength{\itemsep}{-0.5\baselineskip}
-\item Isolation sums, including those in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
-\item Track-related variables such as impact parameters, quality of the track, and information about decay vertices.
+\item Isolation sums of charged and neutral particles, in addition to the isolation sums in equations \ref{eqn:cutbased_iso} and \ref{eqn:ptouter_iso}.
+\item Track-related variables: the impact parameters, quality of the track, information about decay vertices.
 \item Information about photons: the momentum-weighted $\Delta R$, $\Delta \eta$ and $\Delta \phi$ of photons in strips inside or outside the signal cone, in addition to the number of signal and isolation photons found.
-\item \Pgth-related kinematic quantities, plus the reconstructed decay mode.  
+\item \Pgth-related variables: the reconstructed decay mode and \Pgth kinematics.  
+\item The ratio of the total electromagnetic energy to the total energy within the \Pgth signal cone.
 %\item The charged-and neutral-particle isolation sums
@@
 anti-electron and anti-muon discriminators are used. 
-The anti-electron discriminator is a \ac{BDT}-based discriminator trained using input variables such as:
+The anti-electron discriminator is a \ac{BDT}-based discriminator trained using the following input variables:
 \begin{itemize}
 \setlength{\itemsep}{-0.5\baselineskip}
-\item Kinematic variables of the \Pgth candidate and \ac{GSF} track, including visible mass of the \Pgth.
-\item Energy and momentum ratios such as the fraction of electromagnetic energy, \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
-\item Photon-related variables, such as the momentum-weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the \Pgth energy carried by photons, and the number of photons found in strips.
+\item Kinematic variables of the \Pgth candidate and the \ac{GSF} track, plus the visible mass of the \Pgth candidate.
+\item Energy and momentum ratios: the fraction of electromagnetic energy, plus the \ac{ECAL} and \ac{HCAL} energy relative to track momentum.
+\item Photon-related variables: the momentum-weighted $\Delta \eta$ and $\Delta \phi$ between photons, the fraction of the \Pgth energy carried by photons, the ratio of
+the energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker, and the number of photons found in strips.
 \item Information on the quality of the track.
+%\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
+%\item $(p_{in} - p_{out})/p_{in}$
+%\item $\chi^2/Ndof$ of the GSF track fit
+%\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
+%similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
 %\item \pT, $\eta$ of the $\Pgt_{h}$ candidate
 %\item \pT, $\eta$, $\sigma_{p_{\text{T}}}/p_{\text{T}}$ of the \ac{GSF} track
-%\item Distance in $\eta$ and $\phi$ of the \ac{GSF} track to the nearest boundary between \ac{ECAL} modules.
 %\item Electromagnetic energy fraction $E_{\text{ECAL}}/(E_{\text{ECAL}}+E_{\text{HCAL}})$
+%\item The ratio between the total \ac{ECAL} energy and inner track momentum
 %\item Ratio of \ac{ECAL} and \ac{HCAL} energy fractions relative to the momentum of the leading charged track
@@
 %\item The fraction of $\Pgt_{h}$ energy carried by photons (calculated separately for photons inside and outside the $\Pgt_h$ signal cone)
-%\item $(p_{in} - p_{out})/p_{in}$
-%\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
-%\item The ratio between the total \ac{ECAL} energy and inner track momentum
 %\item The ratio of energies of bremsstrahlung photons measured in the \ac{ECAL} and the tracker
 %\item The visible mass of the $\Pgt_h$ candidate, for photons and charged particles within the $\Pgt_h$ signal cone
-%\item $\chi^2/Ndof$ of the GSF track fit
-%\item $N_{hits}^{GSF}-N_{hits}^{KF}/N_{hits}^{GSF}+N_{hits}^{KF}$, With $N_{hits}^{GSF}$ the number of hits associated with the track in the \ac{GSF} track reconstruction algorithm, and
-%similarly $N_{hits}^{KF}$ for the \ac{KF} track reconstruction algorithm.
+%\item The number of photons in any of the strips associated with the $\Pgt_h$ candidate, calculated separately for photons inside and outside the $\Pgt_h$ signal cone
 \end{itemize}
@@
 \begin{center}
-\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
+\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.png}}\\
 \subfloat[Real \Pgth efficiency for anti-\Pe discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
@@
 \caption[Figures of the jet$\rightarrow$\Pgth fake rate in simulated QCD events
-versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the real
+versus $\Pgth$ identification efficiency for simulated $\PHiggs\rightarrow\Pgt\Pgt$ events, the 
 $\Pgth$ identification efficiency for different working points of the anti-electron discriminator, and the \mbox{$\Pe\rightarrow\Pgth$} fake rate for different
@@
 efficiencies and lower fake rates, and for the same \Pgth identification efficiency the fake rate
-from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real \Pgth identification
-efficiency for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
-the $\Pe\rightarrow$\Pgth fake rate for different working points of the anti-electron discriminator, as a function of
-the \pT~of the electron \cite{cms-tau-2015}.}
+from the MVA-based discriminator is lower than from the cut-based discriminator. Figure adapted from \cite{cms-tau-2015}. (b) The \Pgth identification
+efficiency in simulated \Ztautau events for different working points of the anti-electron discriminator as a function of the \pT~of the \Pgth, and (c)
+the $\Pe\rightarrow$\Pgth fake rate in simulated \Zee events for different working points of the anti-electron discriminator, as a function of
+the \pT~of the electron \cite{cms-tau-2015}. Note that the efficiencies and fake rates are fully derived from simulation and serve to give
+an indication of the efficiencies of the different working points relative to each other.}
 \label{fig:tau_efficiency}

### 2017-06-05 Theory/Theory.tex
Corrections

@@
 The \ac{SM} has been successfully tested to high accuracy \cite{pdg-2014}. However,
-some issues remain that cannot be addressed by the \ac{SM} alone \cite{griffiths}.
+some issues remain that cannot be addressed by the \ac{SM} alone.
 For example, it does not provide a candidate for dark matter, which is estimated
-to make up 25\% of the matter-energy density in the universe.
+to make up 25\% of the matter-energy density in the universe \cite{Bertone:2004pz}.
 In addition, the running coupling constants of the electroweak and
-strong forces do not intersect at a common energy scale. Another problem is that the force
-of gravity does not appear in the \ac{SM}.
+strong forces do not intersect at a common energy scale \cite{GUT-LEP}. Another problem is that the force
+of gravity does not appear in the \ac{SM} \cite{Carlip:2001wq}.
 
 These points aside, the most important issue concerning
-the Higgs sector of the \ac{SM} is the hierarchy problem.
+the Higgs sector of the \ac{SM} is the hierarchy problem \cite{SUSY-primer}.
 The \ac{SM}
@@
 \end{equation}
-Thus assuming that there is no new physics all the way up to
-the Planck scale the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
+Thus, assuming that there is no new physics all the way up to
+the Planck scale, the observation $M_{\PHiggs}=125\,\GeV$ would only be compatible with $\Lambda$ of order $10^{19}\,\GeV$
 if there was extreme fine-tuning of the bare Higgs boson mass $(M_{\PHiggs})_0^2$.

### 2017-06-05 backmatter.tex
Own final read through
Final bits before submission
Corrections

@@
 
-\chapter*{List of Acronyms}
-\addcontentsline{toc}{chapter}{List of Acronyms}
-\begin{acronym}[CERN]
+\chapter*{List of acronyms}
+\addcontentsline{toc}{chapter}{List of acronyms}
+\markboth{LIST OF ACRONYMS}{}
+\begin{acronym}
+\acro{2HDM}[2HDM]{two Higgs doublet model}
+\acro{BDT}[BDT]{boosted decision tree}
+\acro{BSM}[BSM]{beyond the standard model}
+\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
+\acro{CHS}[CHS]{charged hadron subtraction}
+\acro{CKM}[CKM]{Cabibbo-Kobayashi-Maskawa}
+\acro{CL}[CL]{confidence level}
+\acro{CMS}[CMS]{Compact Muon Solenoid}
+\acro{CSC}[CSC]{cathode strip chamber}
+\acro{CSV}[CSV]{combined secondary vertex}
+\acro{CTF}[CTF]{combinatorial track finder}
+\acro{DA}[DA]{deterministic annealing}
+\acro{DAQ}[DAQ]{data acquisition}
+\acro{DT}[DT]{drift tube chamber}
+\acro{EB}[EB]{ECAL barrel}
+\acro{ECAL}[ECAL]{electromagnetic calorimeter}
+\acro{EE}[EE]{ECAL endcap}
 \acro{EM}[EM]{electromagnetic}
+\acro{GSF}[GSF]{gaussian sum filter}
+\acro{HB}[HB]{hadron barrel calorimeter}
+\acro{HCAL}[HCAL]{hadron calorimeter}
+\acro{HE}[HE]{hadron endcap calorimeter}
+\acro{HF}[HF]{hadron forward calorimeter}
+\acro{HLT}[HLT]{high-level trigger}
+\acro{HO}[HO]{hadron outer calorimeter}
+\acro{IVF}[IVF]{inclusive vertex finder}
+\acro{KF}[KF]{Kalman filter}
+\acro{L1}[L1]{level-1}
+\acro{LEP}[LEP]{Large Electron-Positron}
+\acro{LHC}[LHC]{Large Hadron Collider}
+\acro{LS1}[LS1]{Long Shutdown 1}
+\acro{MC}[MC]{Monte Carlo}
+\acro{MPF}[MPF]{missing transverse energy projection fraction}
+\acro{MSSM}[MSSM]{minimal supersymmetric standard model}
+\acro{QCD}[QCD]{quantum chromodynamics}
+\acro{PF}[PF]{particle flow}
+\acro{PS}[PS]{Proton Synchrotron}
+\acro{PSB}[PSB]{Proton Synchrotron Booster}
+\acro{QED}[QED]{quantum electrodynamics}
 \acro{QFT}[QFT]{quantum field theory}
-\acro{QCD}[QCD]{quantum chromodynamics}
-\acro{QED}[QED]{quantum electrodynamics}
-\acro{LEP}[LEP]{Large Electron-Positron}
+\acro{RF}[RF]{radio frequency}
+\acro{RPC}[RPC]{resistive plate chamber}
+\acro{SM}[SM]{standard model}
+\acro{SPS}[SPS]{Super Proton Synchrotron}
+\acro{SUSY}[SUSY]{supersymmetry}
+\acro{TEC}[TEC]{tracker endcap}
+\acro{TIB}[TIB]{tracker inner barrel}
+\acro{TID}[TID]{tracker inner disk}
+\acro{TOB}[TOB]{tracker outer barrel}
+\acro{UE}[UE]{underlying event}
 \acro{VBF}[VBF]{vector boson fusion}
-\acro{MC}[MC]{Monte Carlo}
-\acro{CKM}[CKM]{Cabibbo-Kobayashi-Maskawa}
-\acro{CMS}[CMS]{Compact Muon Solenoid}
-\acro{LHC}[LHC]{Large Hadron Collider}
-\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
-\acro{PS}[PS]{Proton Synchrotron}
-\acro{SPS}[SPS]{Super Proton Synchrotron}
-\acro{PSB}[PSB]{Proton Synchrotron Booster}
-\acro{LS1}[LS1]{Long Shutdown 1}
-\acro{MSSM}[MSSM]{minimal supersymmetric standard model}
-\acro{SM}[SM]{standard model}
-\acro{SUSY}[SUSY]{supersymmetry}
-\acro{2HDM}[2HDM]{two Higgs doublet model}
-\acro{ECAL}[ECAL]{electromagnetic calorimeter}
-\acro{HCAL}[HCAL]{hadron calorimeter}
-\acro{TIB}[TIB]{Tracker Inner Barrel}
-\acro{TID}[TID]{Tracker Inner Disk}
-\acro{TOB}[TOB]{Tracker Outer Barrel}
-\acro{TEC}[TEC]{Tracker EndCap}
-\acro{EB}[EB]{ECAL Barrel}
-\acro{EE}[EE]{ECAL Endcap}
-\acro{HB}[HB]{Hadron Barrel Calorimeter}
-\acro{HO}[HO]{Hadron Outer Calorimeter}
-\acro{HE}[HE]{Hadron Endcap Calorimeter}
-\acro{HF}[HF]{Hadron Forward Calorimeter}
-\acro{BSM}[BSM]{beyond the standard model}
-\acro{L1}[L1]{Level-1}
-\acro{HLT}[HLT]{High-level trigger}
-\acro{CSC}[CSC]{Cathode Strip Chamber}
-\acro{DT}[DT]{Drift Tube chamber}
-\acro{RPC}[RPC]{Resistive Plate Chamber}
-\acro{DAQ}[DAQ]{Data Acquisition}
 \acro{WLCG}[WLCG]{Worldwide LHC Computing Grid}
-\acro{RF}[RF]{radio frequency}
-\acro{PF}[PF]{particle flow}
-\acro{BDT}[BDT]{boosted decision tree}
-\acro{KF}[KF]{Kalman Filter}
-\acro{CTF}[CTF]{Combinatorial Track Finder}
-\acro{GSF}[GSF]{Gaussian Sum Filter}
-%\acro{KF}[KF]{Kalman Filter}
-\acro{DA}[DA]{Deterministic Annealing}
-\acro{CHS}[CHS]{charged hadron subtraction}
-\acro{CSV}[CSV]{Combined Secondary Vertex}
-\acro{CL}[CL]{confidence level}
-\acro{IVF}[IVF]{Inclusive Vertex Finder}
-\acro{UE}[UE]{underlying event}
-\acro{MPF}[MPF]{missing transverse energy projection fraction}
 \end{acronym}
@@
 \renewcommand{\chaptername}{Appendix}
+\chapter{\texorpdfstring{Event yields in the \Htohhtobbtautau analysis}{Event yields in the H to hh to bbtautau analysis}}
+\label{appendix:yields_bbtautau}
+The numbers of observed and expected events in the \Htohhtobbtautau analysis \mbox{(chapter \ref{chap:hhh})}
+are given in table \ref{tab:hhh_mt_yields} for the \mutau channel and in table \ref{tab:hhh_et_yields} for the \etau channel. The background
+expectations are given after the fit to data has been performed. The uncertainties also correspond
+to the values obtained after performing the fit to data, with the correlations between the different
+systematic uncertainties taken into account. 
+\input{Hhh/Hhhyields}
+
 \chapter{\texorpdfstring{Systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
@@
 
+\chapter{\texorpdfstring{Event yields in the MSSM \AHtotautau analysis}{Event yields in the MSSM A/H to tautau analysis}}
+\label{appendix:yields_mssm}
+The numbers of observed and expected events in the MSSM \AHtotautau analysis \mbox{(chapter \ref{chap:mssm})}
+are given in table \ref{tab:mssm_mt_yields} for the \mutau channel, in table \ref{tab:mssm_et_yields} for the 
+\etau channel, in table \ref{tab:mssm_tt_yields} for the \tautau channel 
+and in table \ref{tab:mssm_em_yields} for the \emu channel. The background
+expectations are given after the fit to data has been performed. The uncertainties also correspond
+to the values obtained after performing the fit to data, with the correlations between the different
+systematic uncertainties taken into account. 
+\input{MSSM/MSSMyields}
+
 %% If you have time and interest to generate a (decent) index,

### 2017-06-05 frontmatter.tex
Corrections

@@
 \begin{declaration}
+\small
   I declare that the work in this thesis is mine. Figures and results taken from other sources
@@
 For the results of the \Htohhtobbtautau analysis I contributed to the data analysis of the \etau and \mutau
-final states of the di-tau pair. I 
+final states of the di-tau pair, with studies of alternative \ttbar background rejection methods and
+other uses of the kinematic fit variable. These studies are not further discussed in this thesis. I 
 was responsible for the statistical inference of the analyses in the \etau, \mutau and \tautau final states
